### 2018-04-03 doc/draft-01/biharm-evals.tex
add documentation files with some preliminary notes I've started adding things as I derive them

\documentclass[preprint,12pt]{article} 
\usepackage{b}
\usepackage[a4paper]{geometry}
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}
\usepackage[small,it]{caption}
\usepackage{empheq}

\usepackage{subcaption}

\usepackage{cleveref}
\crefname{equation}{}{}
\Crefname{equation}{}{}
\crefname{eqnarray}{}{}
\Crefname{eqnarray}{}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\xx{{\bf x}}
\def\yy{{\bf y}}
\def\ss{{\bf s}}
\def\tt{{\bf t}}
\def\uu{{\bf u}}
\def\ff{{\bf f}}
\def\GG{{\bf G}}
\def\II{{\bf I}}
\def\TT{{\bf T}}
\def\bsigma{{\boldsymbol \sigma}}
\def\bnu{{\boldsymbol \nu}}
\def\btau{{\boldsymbol \tau}}
\def\bigo{\mathcal{O}}
\def\littleo{o}

\newtheorem{remark}{Remark}
\newtheorem{proposition}{Proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{An integral equation method for the biharmonic
Dirichlet eigenvalue problem in two dimensions}
\author{Askham and Rachh}
\date{\today}

\begin{document}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

Results of some quick googling:

Finite element methods.
\begin{itemize}
\item Stokes eigenvalue problem: nonconforming finite
  element methods \cite{jia2009approximation}.
\end{itemize}

Integral equation methods.
\begin{itemize}
\item Book on elastodynamic eigenvalue problems
  \cite{kitahara2014boundary}
\end{itemize}
\section{Mathematical Preliminaries}

\subsection{Notation}

Bold symbols are vectors or tensors.
$\xx = (x_1,x_2)^\intercal$ then $\xx^\bot = (-x_2,x_1)^\intercal$.
Similarly, $\nabla^\intercal = (-\partial_{x_2},\partial_{x_1})^\intercal$

\subsection{Green's functions}

$\Delta$
\begin{equation}
  G_L(\xx,\yy) = -\frac{1}{2\pi} \log |\xx-\yy|
\end{equation}

$\Delta + k^2$
\begin{equation}
  G_H(\xx,\yy) = \frac{i}{4} H_0^{(1)}(k|\xx-\yy|)
\end{equation}

$\Delta(\Delta + k^2)$
\begin{equation}
  G_{BH}(\xx,\yy) = -\frac{1}{k^2}
  \left (\frac{1}{2\pi} \log |\xx-\yy| +
  \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \right )
\end{equation}

\section{Integral Equation Formulation}

\subsection{The Helmholtz Stokeslet formulation}

In this section, we review the derivation of the
modified Stokeslet, but for the imaginary parameter
regime --- which we will call the Helmholtz Stokeslet ---
which is the appropriate setting for the Stokes
eigenvalue problem.
The original modified Stokeslet is more well known,
and is of particular interest for its application to
numerical simulations of the unsteady Stokes equations
\cite{pozrikidis1992boundary,biros2002embedded}.

To begin, we restate the Stokes eigenvalue
problem as
\begin{align}
  \nabla p - \Delta \uu - k^2 \uu &= 0 \; , \label{eq:helmstokes}\\
  \nabla \cdot \uu &= 0 \; . \label{eq:helmstokescty}
\end{align}
Consider the solution of this problem where a
$\delta$ centered at $\yy$ with strength $\ff$
has been added to the right-hand side, i.e.

\begin{align}
  \nabla p - \Delta \uu - k^2 \uu &= \delta_\yy \ff \; ,
  \label{eq:helmstokes_charge} \\
  \nabla \cdot \uu &= 0 \; .
\end{align}
Note that

\begin{equation}
  \Delta G_L(\xx,\yy) = \delta_\yy(\xx) \; .
\end{equation}
If we substitute this expression into
\eqref{eq:helmstokes_charge} and take the divergence,
we obtain

\begin{equation}
  p = \nabla G_L(\xx,\yy) \cdot \ff \; .
\end{equation}
We then have, formally,

\begin{align}
  \uu &= - (\Delta + k^2)^{-1} ( \Delta G_L \ff
  - \nabla (\nabla G_L \cdot \ff ) ) \\
  &= \left ( -\Delta + \nabla \otimes \nabla \right )
  G_{BH} \ff \; .
\end{align}
The tensor

\begin{equation}
  \GG = - \II \Delta G_{BH} + \nabla \otimes \nabla G_{BH}
\end{equation}
is then the equivalent of a Stokeslet
\cite{pozrikidis1992boundary} for the problem
\eqref{eq:helmstokes}.

A related object is the stresslet, which is defined
in terms of the stress tensor of a velocity, pressure
pair induced by a Stokeslet. For these tensors, we find
that it is more convenient to express them in index notation
with the Einstein index summing convention.
Recall that the stress tensor $\bsigma$ is defined as

\begin{equation}
  \sigma_{ij} = -p \delta_{ij} + \left ( \partial_{x_j}u_i
  +\partial_{x_i} u_j \right ) \; ,
\end{equation}
where $\delta_{ij}$ is the standard Kronecker delta notation.
The stresslet $\TT$ is defined to be

\begin{align}
  T_{ijk} &= - \partial_{x_j} G_L \delta_{ik}
  + \partial_{x_k} \left ( -\Delta G_{BH} \delta_{ij} +
  \partial_{x_i} \left(\partial_{x_j} G_{BH} \right) \right)
  \nonumber \\
  & \qquad+ \partial_{x_i} \left ( -\Delta G_{BH} \delta_{kj} +
  \partial_{x_k} \left(\partial_{x_j} G_{BH} \right) \right)
  \; .
\end{align}
Let $u_i = G_{ij} f_j$ and $p = \partial_{x_i} G_L f_i$ be a
solution of the Stokes equations induced by a Stokeslet.
Then the corresponding stress tensor is given by
$\sigma_{ik} = T_{ijk} f_j$.

For the layer potentials of the next section, the following
formulas are useful. Let $\bnu$ be a given vector. When
summing over the third index, we obtain

\begin{equation}
  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla G_L
  + \partial_\nu \left ( -\Delta G_{BH} \II
  + \nabla \otimes \nabla G_{BH} \right)
  + \nabla \otimes \left ( -\Delta G_{BH} \bnu
  + \partial_{\nu} \nabla G_{BH} \right) \; .
\end{equation}
%\begin{align}
% -\Delta G_{BH} \bnu
% + \partial_{\nu} \nabla G_{BH} &=
% ( (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_1 G_{BH} +
% (\partial_{x_1x_1}\nu_1 + \partial_{x_2x_1} \nu_2 )G_{BH},
% (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_2 G_{BH} +
% (\partial_{x_1x_2}\nu_1 + \partial_{x_2x_2} \nu_2 )G_{BH}) \\
% &= (-\partial_{x_2} \partial_\tau G_{BH},
% \partial_{x_1} \partial_\tau G_{BH})
%\end{align}
%\begin{equation}
%  \begin{pmatrix}
%    -\partial_{x_2x_2} & \partial_{x_1x_2} \\
%    \partial_{x_1x_2} & -\partial_{x_1x_1}
%  \end{pmatrix} = -\nabla^\bot \otimes \nabla^\bot
%\end{equation}
Let $\btau = \bnu^\bot$. Then

\begin{equation}
  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla G_L
  - \nabla^\bot \otimes \nabla^\bot \partial_\nu G_{BH}
  +\nabla \otimes \nabla^\bot \partial_\tau G_{BH} \; .
\end{equation}

\subsection{Layer potentials}

\bibliographystyle{plain}
\bibliography{refs}

\end{document}

### 2018-04-03 src/helmbhrouts.f

@@ -10,7 +10,7 @@ cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
 c
 c     Evaluates the Green function 
 c
-c     G(x,y) = (i*H_0^(1)(zk*r)/4 - log(r)/(2*pi))/zk^2 ,
+c     G(x,y) = (i*H_0^(1)(zk*r)/4 + log(r)/(2*pi))/zk^2 ,
 c
 c     where H_0^(1) is the Hankel function of the first kind and
 c     r = sqrt( (x_1-y_1)^2 + (x_2-y_2)^2),

### 2018-04-21 doc/draft-01/biharm-evals.tex
fix a typo
update to working version of stokes and stresslet evaluators

@@
 \def\TT{{\bf T}}
+\def\SS{{\bf S}}
+\def\DD{{\bf D}}
 \def\bsigma{{\boldsymbol \sigma}}
+\def\bmu{{\boldsymbol \mu}}
 \def\bnu{{\boldsymbol \nu}}
@@
 $\xx = (x_1,x_2)^\intercal$ then $\xx^\bot = (-x_2,x_1)^\intercal$.
-Similarly, $\nabla^\intercal = (-\partial_{x_2},\partial_{x_1})^\intercal$
+Similarly, $\nabla^\bot = (-\partial_{x_2},\partial_{x_1})^\intercal$
 
@@
 
+We now use the Stokeslet and stresslet definitions
+of the previous section to define the standard single
+and double layer potentials of the Stokes eigenvalue
+problem. The single layer potential is defined to
+be
+
+\begin{equation}
+  \SS \bmu (\xx) = \int_\Gamma \GG (\xx,\yy) \bmu(\yy)
+  \, dS(\yy) \; .
+\end{equation}
+The double layer potential is defined to be
+
+\begin{equation}
+  \DD \bmu (\xx) = \int_\Gamma \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy)
+  \right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
+\end{equation}
+where $\bnu$ denotes the outward unit normal to the boundary.
+If we write $\bmu = \bnu \mu_\nu + \btau \mu_\tau$,
+where $\btau = \bmu^\bot$ is the positively oriented unit
+tangent to the curve, then we have
+
+\begin{align}
+  \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy) \right )^\intercal
+  \bmu(\yy) &= \left ( - \nabla G_L(\xx,\yy) + 2 \nabla^\bot
+  \partial_{\nu\tau} G_{BH}(\xx,\yy) \right ) \mu_\nu(\yy) \nonumber \\
+  & \qquad+
+  \nabla^\bot \left (\partial_{\tau\tau}-\partial_{\nu\nu} \right )
+  G_{BH}(\xx,\yy) \mu_\tau(\yy) \; .
+\end{align}
+
 \bibliographystyle{plain}

### 2018-04-21 src/chunks_helmstokes_kerndefs.f90

@@ -1,204 +1,336 @@
 
-subroutine zchker_helmstokes_s1(zk,src,targ,src_normal, &
-     pars2,val,grad,hess)
-  implicit real *8 (a-h,o-z)
+subroutine fgreensdummy(par0,src,targ, &
+     pars1,pars2,val,grad,hess)
+  implicit none
+  complex *16, intent(in) :: par0
+  complex *16, intent(in) :: pars1(*), pars2(*)
+  real *8, intent(in) :: src(2), targ(2)
+  complex *16, intent(out) :: val, grad(2), hess(2,2)
+
+  return
+end subroutine fgreensdummy
+  
+subroutine zhelmstokes_kern(zk,src,targ,&
+     src_normal,targ_normal,q1,q2,fgreens,&
+     pars1,pars2,val)
+  !
+  ! Note that this routine returns a 2 x 2
+  ! matrix (as opposed to scalar output)
+  ! fgreens is ignored
+  !
+  ! The output is a linear combo of the
+  ! single and double layer potentials
+  ! with coefficients cs = q1(1) and cd = q2(1)
+  !
+  ! If either coefficient is smaller than
+  ! 1d-16, it is ignored
+  !
+  implicit none
+  complex *16, intent(in) :: zk
+  complex *16, intent(in) :: q1(*), q2(*)
+  complex *16, intent(in) :: pars1(*), pars2(*)  
+  real *8, intent(in) :: src(2), targ(2)
+  real *8, intent(in) :: src_normal(2), targ_normal(2)  
+  external fgreens
+  complex *16, intent(out) :: val(2,2)
+  ! local
+  complex *16 :: mats(2,2), matd(2,2), cs, cd
+  complex *16 :: stressmat(2,2,2), nu(2)
+  integer :: ifs, ifd, ifstress
+  real *8 :: small
+  character :: trans
+  data small / 1d-16 /
+
+  ifs = 1
+  ifd = 1
+  
+  mats(:,:) = 0.0d0
+  matd(:,:) = 0.0d0
+
+  cs = q1(1)
+  cd = q2(1)
+
+  if (abs(cs) .lt. small) ifs = 0
[…]

### 2018-04-21 src/cmat_build.f90

@@ -1,0 +1,1371 @@
+
+        !
+        !     This file contains several subroutines for constructing
+        !     matrices corresponding to layer potentials with
+        !     complex-valued kernels, i.e. helmholtz, etc.
+        !
+        !     The important subroutines are as follows:
+        !
+        !       zbuildmat - 
+        !
+        !
+
+      subroutine zget_neumann(wgeo, fincoming, par0, src, pars1, &
+          pars2, uinc)
+        implicit real *8 (a-h,o-z)
+        real *8, intent(in) :: wgeo(*), src(2)
+        complex *16, intent(in) :: par0, pars1(*), pars2(*)
+        complex *16, intent(out) :: uinc(*)
+
+        real *8 :: dnorm(10)
+        complex *16 :: val, grad(2), hess(2,2)
+
+        !
+        ! evaluate the dirichlet data on the boundary contained
+        ! in wgeo using the function fincoming
+        !
+
+        call chunkunpack1(wgeo, k, nch, ichunks, iadjs, iders, &
+            iders2, ihs)
+
+        do i = 1,k*nch
+          ind = 2*(i-1)
+          xp = wgeo(iders+ind)
+          yp = wgeo(iders+ind+1)
+          sc = sqrt(xp**2+yp**2)
+          dnorm(1) = yp/sc
+          dnorm(2) = -xp/sc
+          call fincoming(par0, src, wgeo(ichunks+ind), pars1, &
+              pars2, val, grad, hess)
+          uinc(i) = (dnorm(1)*grad(1) + dnorm(2)*grad(2))
+        enddo
+
+      end subroutine
+
+
+
+
+      subroutine zget_dirichlet(wgeo, fincoming, par0, src, pars1, &
+          pars2, uinc)
+        implicit real *8 (a-h,o-z)
+        real *8, intent(in) :: wgeo(*), src(2)
+        complex *16, intent(in) :: par0, pars1(*), pars2(*)
+        complex *16, intent(out) :: uinc(*)
+
+        complex *16 :: val, grad(2), hess(2,2)
+
+        !
+        ! evaluate the dirichlet data on the boundary contained
+        ! in wgeo using the function fincoming
+        !
+
+        call chunkunpack1(wgeo, k, nch, ichunks, iadjs, iders, &
+            iders2, ihs)
+
+        do i = 1,k*nch
+          ind = 2*(i-1)
+          call fincoming(par0, src, wgeo(ichunks+ind), pars1, &
[…]

### 2018-04-21 src/hbhrouts2d.f

@@ -12,7 +12,7 @@ cc details. You should have received a copy of the GNU General Public
 cc License along with this program; 
 cc if not, see <http://www.gnu.org/licenses/>.
 
-      subroutine hbhpotgrad2dall_cdq(beta,source,ns,ifcharge,
+      subroutine hbhpotgrad2dall_cdq(zk,source,ns,ifcharge,
      1     charge,ifdipole,dipstr,dipvec,ifquad,quadstr,quadvec,
      2     target,ifpot,pot,ifgrad,grad,ifhess,hess)
 cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
@@ -22,22 +22,13 @@ c
 cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
       implicit none
 c     global variables
-      real *8 beta, source(2,*), charge(*), dipstr(*)
-      real *8 dipvec(2,*), quadstr(*), quadvec(3,*)
+      complex *16 zk
+      real *8 source(2,*)
+      complex *16 charge(*), dipstr(*)
+      complex *16 dipvec(2,*), quadstr(*), quadvec(3,*)
       real *8 target(2)
-      real *8 pot, grad(2), hess(3)
+      complex *16 pot, grad(2), hess(3)
       integer ns, ifcharge, ifdipole, ifquad, ifpot, ifgrad, ifhess
-c     local variables
-      real *8 potloc,gradloc(2),hessloc(3),der3(4),der4(5),der5(6)
-      integer ifpotloc, ifgradloc, ifhessloc, ifder3, ifder4, ifder5
-      integer i
-
-      ifpotloc = 1
-      ifgradloc = 1
-      ifhessloc = 1
-      ifder3 = 1
-      ifder4 = 1
-      ifder5 = 0
 
       if (ifpot .eq. 1) pot = 0.0d0
       if (ifgrad .eq. 1) then
@@ -50,8 +41,46 @@ c     local variables
          hess(3) = 0.0d0
       endif
 
+      call hbhpotgrad2dall_cdq_add(zk,source,ns,ifcharge,
+     1     charge,ifdipole,dipstr,dipvec,ifquad,quadstr,quadvec,
+     2     target,ifpot,pot,ifgrad,grad,ifhess,hess)
+
+      
+
+      return
+      end
+
+      subroutine hbhpotgrad2dall_cdq_add(zk,source,ns,ifcharge,
[…]

### 2018-04-21 src/helmbhrouts.f

@@ -62,7 +62,7 @@ c     local variables
       integer ifders
       real *8 rscale
       integer nmax, ifder, j
-      complex *16 z, eye, eyeo4, hvec(0:10), diffs(0:5), ders(0:5)
+      complex *16 z, eye, eyeo4, hvec(0:10), diffs(0:10), ders(0:10)
       complex *16 zkh, ztemp, zkr
       data eye /(0.0d0,1.0d0)/
       data eyeo4 /(0.0d0,0.25d0)/

### 2018-04-24 doc/draft-01/biharm-evals.tex
add minor changes to manuscript
Including results for condition number and updating document

--- 2018-04-03 doc/draft-01/biharm-evals.tex
@@
 
-\def\xx{{\bf x}}
-\def\yy{{\bf y}}
-\def\ss{{\bf s}}
-\def\tt{{\bf t}}
-\def\uu{{\bf u}}
-\def\ff{{\bf f}}
+\def\br{{\boldsymbol r}}
+\def\bn{{\boldsymbol n}}
+\def\xx{{\boldsymbol x}}
+\def\bx{{\boldsymbol x}}
+\def\yy{{\boldsymbol y}}
+\def\by{{\boldsymbol y}}
+\def\ss{{\boldsymbol s}}
+\def\tt{{\boldsymbol t}}
+\def\uu{{\boldsymbol u}}
+\def\bu{{\boldsymbol u}}
+\def\bl{{\boldsymbol \ell}}
+\def\ff{{\boldsymbol f}}
 \def\GG{{\bf G}}
+\def\Gbh{{G_{BH}}}
 \def\II{{\bf I}}
@@
 
+\subsection{The Farkas integral representation}
+
+As mentioned in the introduction, there are existing 
+integral representations for the solution of the Dirichlet problem for the Helmholtz-biharmonic equation
+\begin{align}
+ \Delta (\Delta + k^2) w &= 0 \mbox{ in } D \; , \label{eq:biharmD1}\\
+ w &= f \mbox{ on }
+ \Gamma \label{eq:biharmD2} \; , \\ 
+ \frac{\partial w}{\partial n} &= g \mbox{ on } 
+ \Gamma \, , \label{eq:biharmD3}
+\end{align}
+In \cite{Farkas89}, 
+the solution is given as the sum of two layer potentials, i.e.
+\begin{equation}
+  w(\xx) = \int_\Gamma K_1^F (\xx,\yy) \sigma_1(\yy) \, dS(\yy)
+  + \int_\Gamma K_2^F(\xx,\yy) \sigma_2(\yy) \, dS(\yy) \; ,
+  \label{eq:farkRep}
+\end{equation}
+where $\sigma_1$ and $\sigma_2$ are unknown densities.
+
+The integral kernels, $K_1^F$ and $K_2^F$ are based on
+derivatives of the Green's function for the biharmonic equation.
+For two points on the plane, $\xx$ and $\yy$, let $\br = \yy - \xx$. Then 
+\begin{align}
+  K_1^F(\xx,\yy) &= \partial_{n_{y}n_{y}n_{y}}\Gbh(\xx,\yy)
+  + 3 \partial_{n_{y}\tau_{y}\tau_{y}}\Gbh(\xx,\yy) + k^{2} \partial_{n_{y}}\Gbh(\xx,\yy)\; , \label{eq:kf1} \\
+  K_2^F(\xx,\yy) &= -\partial_{n_{y}n_{y}}\Gbh(\xx,\yy)
+  + \partial_{\tau_{y}\tau_{y}}\Gbh(\xx,\yy) \label{eq:kf2} \; .
+\end{align}
+More explicitly, we have
+
+\begin{align}
+  K_1^F(\xx,\yy) &=  -\dfrac{\br \cdot \bn(\yy)}{|\br|^2}  \cdot \left( \frac{3 i}{2} H_0^{(1)}(k|\br|) - \frac{5 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{6}{\pi k^2 |\br|^2} + \frac{1}{2\pi}  \right) +     \\
+  & \quad \dfrac{\left(\br \cdot \bn(\yy)\right)^3}{|\br|^4} \cdot \left( 2i H_0^{(1)}(k|\br|) - \frac{7 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{8}{\pi k^2 |\br|^2}  \right) \, , \nonumber \\
+  K_2^F(\xx,\yy) &=  -\left(\frac{1}{2}-\dfrac{\left(\br \cdot \bn(\yy)\right)^2}{|\br|^2} \right)  \cdot \left( \frac{i}{2} H_0^{(1)}(k|\br|) - \frac{i}{k|\br|} H_1^{(1)}(k|\br|) + \frac{2}{\pi k^2 |\br|^2}  \right)\; .
+\end{align}
+
+On enforcing the Dirichlet boundary conditions for
+$w$, we obtain the integral equation
+\begin{equation}
+  \begin{split}
+    \begin{pmatrix}
+      f(\xx) \\
+      g(\xx)
+    \end{pmatrix} &= 
+    \int_\Gamma
+    \begin{pmatrix}
+      K_{11}^F(\xx,\yy) & K_{12}^F(\xx,\yy) \\
+      K_{21}^F(\xx,\yy) & K_{22}^F(\xx,\yy)
+    \end{pmatrix}
+    \begin{pmatrix}
+      \sigma_1(\yy)\\
+      \sigma_2(\yy)
+    \end{pmatrix}
+    \, dS(\yy) \\
+    &\quad + \begin{pmatrix}
+      1/2 & 0 \\
+      -\kappa(\xx) & 1/2
+    \end{pmatrix}
+    \begin{pmatrix}
+      \sigma_1(\xx)\\
+      \sigma_2(\xx)
+    \end{pmatrix} \; , \label{eq:farkIntEq} 
+  \end{split}
+\end{equation}
+where $\kappa$ denotes the signed curvature as
+a function on $\Gamma$ and $\xx$ is a point on $\Gamma$. 
+The kernels are given
+by $K_{11}^F = K_1^F$, $K_{12}^F = K_2^F$,
+\begin{align}
+  K_{21}^F(\xx,\yy) &= \left(K_1^F(\xx,\yy)\right )_{n_x} \nonumber \\
+  &= \bn(\xx) \cdot \nabla_{\xx} K_{21}^{F}(\xx,\yy) \; \label{eq:farkK21},\\
+  K_{22}^F(\xx,\yy) &= \left(K_2^F(\xx,\yy)\right )_{n_x} \nonumber \\
+  &= \bn(\xx) \cdot \nabla_{\xx} K_{22}^{F}(\xx,\yy) \label{eq:farkK22} \; .
+\end{align}
+For a sufficiently smooth and simply connected domain,
+the integral equation \cref{eq:farkIntEq} is invertible.
+The case of a multiply connected domain is not treated
+fully in \cite{Farkas89}, but some of the issues are
+considered.
+
+As mentioned above, the kernels $K^F_1$ and $K^F_2$ are
+constructed with the goal that the $K^F_{ij}$ are
+as smooth as possible. Suppose that the boundary
+$\Gamma$ is of class $C^k$. Then, the kernels,
+$K^F_{ij}(\xx,\yy)$, are $C^{k-2}$ functions on the boundary
+for each $\yy \in \Gamma$.
+Therefore, on a smooth
+boundary, these kernels are smooth. However, on a
+domain with a corner, we note 
+that the kernel $K_{21}^F$
+has a singularity with strength $r^{-2}$ (see~\cref{fig:ker21plot}). 
+This singularity, in addition to the term in \cref{eq:farkIntEq}
+which explicitly involves the
+curvature, makes the representation \cref{eq:farkRep}
+unstable for domains with high curvature (or
+corners).
+
+\section{Integral equation derivation} \label{sec:anapp}
+
+%\subsection{Adapting the completed double layer representation
+%to solve the Dirichlet problem}
+We would like to adapt the completed double layer representation
+for solutions of Stokes flow \cref{eq:biharmV1,eq:biharmV2,eq:biharmV3} to solve 
+the clamped plate problem \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}.
+Let $f$ and $g$ be the boundary data as in \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}. 
+By computing tangential derivatives of $f$ on each
+boundary component, we get the following related Helmholtz-Stokes problem:
+\begin{align}
+ \Delta (\Delta + \lambda^2) \tilde{w}  = 0 &\quad \bx \in D \, ,\nonumber\\
+ \frac{\partial \tilde{w}}{\partial \tau} = 
+ \frac{\partial f}{\partial \tau} 
+&\quad \bx \in \Gamma \label{eq:biharm5} \, ,\\ 
+ \frac{\partial \tilde{w}}{\partial n} = g &\quad \bx 
+\in \Gamma 
+\, . 
+\nonumber
+\end{align}
+There are two main issues to be addressed in using the completed
+double layer representation in this context. First,
+the representation is designed for 
+Helmholtz-Stokes flow, in which the quantities of interest are derivatives
+of the potential $\tilde{w}$ and not $\tilde{w}$ itself; the
+representation for $\tilde{w}$ may not be single-valued. 
+We will establish that, in the context of \cref{eq:biharm5},
+the stream function is necessarily single-valued. We also discuss
+some numerical issues related to evaluating the stream function.
+The second issue to address
+is that the solution $\tilde{w}$ only satisfies the original boundary 
+condition for the value of $\tilde{w}$ up to a constant on 
+each boundary component.
+In fact, for multiply connected domains, the completed double layer 
+representation is incomplete for the Dirichlet
+problem \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}. We present a remedy for this 
+issue and provide some physical intuition.
+%
+%\subsection{Single-valued stream functions}
+%To solve the Dirichlet problem \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3},
+%it is necessary to compute
+%a single-valued biharmonic potential.
+%In the case of a multiply connected domain,
+%there is no guarantee that a single-valued stream 
+%function exists for a given velocity field.
+%
+%Consider the following example.
+%Let $(r,\theta)$ denote standard polar coordinates. It is
+%easy to verify that the velocity field 
+%$\bu=\frac{1}{r}\hat{r}$ 
+%solves the equations of Stokes flow in an annulus centered at the 
+%origin. A stream function for this flow is $w=\theta$, which 
+%is not single-valued; indeed, there are no single-valued
+%stream functions which generate this flow. 
+%
+%Let $D$ be a multiply connected domain with boundary 
+%$\Gamma = \cup_{i=0}^N \Gamma_i$, as in the previous section.
+%We note that the gradient of a stream function is determined 
+%by the velocity field, i.e. 
+%
+%\begin{equation}
+%\nabla w = -\bu^\perp := \begin{pmatrix} 
+%  - u_2 \\ u_1 
+%\end{pmatrix} \; .
+%\end{equation}
+%Therefore, a velocity field has single-valued stream
+%functions if and only if $\bu^\perp$ is conservative.
+%Using standard results from multivariable calculus, 
+%we can  characterize such flows.
+%
+%\begin{proposition} 
+%Suppose that $\bu$ is a divergence-free velocity 
+%field which is $C^1$ on $D$ and continuous on 
+%$D\cup \Gamma$. The field $\bu^\perp$ 
+%is conservative if and only if 
+%
+%\begin{equation}
+% \int_{\Gamma_i} \bu\cdot \bn \, dS 
+%= 0 \quad i=0,1,\ldots N \, .
+%\label{eq:NecSuffStreamFuncExistence}
+%\end{equation}
+%
+%\end{proposition}
+%
+%The equalities \cref{eq:NecSuffStreamFuncExistence}
+%constitute $N$ linearly independent constraints on the 
+%boundary data because the divergence-free condition 
+%\cref{eq:MassConservation} implies that
+%$\int_{\Gamma} \bu \cdot \bn \, dS = 0$. 
+%It turns out that 
+%these conditions are satisfied when the Dirichlet 
+%problem is recast as a Stokes flow \cref{eq:biharm5}, as 
+%it is easily verified that
+%\begin{equation}
+% \int_{\Gamma_i} \bu\cdot \bn \, dS 
+%= \int_{\Gamma_i} \frac{\partial f}{\partial \tau} \, dS =0 \, .
+%\end{equation}
+%Thus, any stream function $\tilde{w}$ obtained for the Stokes
+%flow \cref{eq:biharm5} is necessarily single-valued.
+%% NOT GOING THIS WAY ANYMORE
+%%It can be shown using the Helmholtz Hodge decomposition that the 
+%%conditions \cref{eq:NecSuffStreamFuncExistence} are sufficient for 
+%%the existence of a single-valued stream function. 
+%
+%\subsection{Evaluating the stream function} \label{subsec:stream}
+%
+%Given compatible boundary data for the velocity field $\bu$, 
+%the completed double layer representation for Stokes flow 
+%\cref{eq:IntRepStokes} guarantees the existence of
+%a solution density $\boldsymbol\mu$ 
+%and a corresponding stream function $\tilde{w}$. The Goursat 
+%function formula 
+%for $\tilde{w}$, see \cref{sec:stokeslayer},
+%is necessarily single-valued, as explained above,
+%but it is not immediately obvious from the formula 
+%that this should be true.
+%
+%The difficulty in the representation of $\tilde{w}$ 
+%comes from the part
+%of the stream function corresponding to the double layer potential
+% \cref{eq:wDL}. The 
+%second term in the expression for the double layer potential is
+%\begin{equation}
+% v_1(z) = \mbox{Re}\left[\frac{1}{4\pi i}\int_{\Gamma}\left(
+%\overline{\rho\left(\xi\right)}d\xi+\rho\left(\xi\right)
+%\overline{d\xi}\right)\log\left(\xi-z\right)\right] \, .
+%\end{equation}
+%To compute this term, in a na\"{i}ve numerical implementation,
+%the question of which is the appropriate branch of the 
+%logarithm to use would arise at many steps.
+%To avoid this complication, it is possible instead to compute
+%$v_1$, up to a constant, as the harmonic conjugate of the
+%function 
+%\begin{equation}
+% v_2 = \frac{1}{4\pi}\int_{\Gamma}\left(\overline{\rho\left(\xi\right)}
+%d\xi+\rho\left(\xi\right)\overline{d\xi}\right)\log
+%\left(\left|\xi-z\right|\right) \, . \label{eq:harmconjg}
+%\end{equation}
+%
+%We will use this approach to evalute $v_1$ numerically.
+%As a result of the Cauchy-Riemann equations, the 
+%harmonic conjugate of $v_2$, satisfies the following
+%Neumann problem for the Laplace equation:
+%\begin{align}
+% \Delta v_1 &= 0 &\quad x\in D \, ,\\
+% \frac{\partial v_1}{\partial n} &= -\frac{\partial v_2}{\partial \tau} 
+%&\quad x\in\Gamma \, .
+%\end{align}
+%It is possible then to use standard integral equation
+%methods to compute $v_1$. 
+%
+%Let $v_1 = S^L_\Gamma \sigma$, where $S^L_\Gamma \sigma$ 
+%is the single layer potential for Laplace's equation, given by
+%\begin{equation}
+%S^L_\Gamma\sigma (\bx) = -\frac{1}{2\pi} \int_{\Gamma} \log 
+%\left|\bx - \by \right|\sigma(\by)\, dS \left(\by \right) \, ,
+%\end{equation}
+%where $\sigma\in \mathcal{X}= C^{0,\alpha}\left(\Gamma\right)$, for 
+%some $\alpha \in (0,1)$, is an unknown density 
+%(see \cite{kress1999linear, guenther1988partial}).
+%Imposing the Neumann boundary conditions results in the 
+%following boundary integral equation for $\sigma$:
+%\begin{align}
+%-\frac{\partial v_2}{\partial \tau} (\bx) &= \frac{1}{2} \sigma \left(\bx\right) - \frac{1}{2\pi}\oint_{\Gamma} 
+%\frac{\partial}{\partial n_x}  
+%\log \left| \bx - \by \right |\sigma(\by)\, dS \left(\by \right) 
+%\, , \\
+%-\frac{\partial v_2}{\partial \tau} &= \left( \frac{1}{2}I_{\mathcal{X}} + K^L_\Gamma  \right) \sigma 
+%\, ,
+%\label{eq:BlockSystemRow2P1tmp}
+%\end{align}
+%where the operator $K^L_\Gamma$ is compact, so that the integral equation
+%is second kind.
+%For a derivation of this result, see \cite{kress1999linear}.
+%
+%It is well known that the operator $\frac{1}{2}I_{\mathcal{X}} + K^L_\Gamma$ 
+%has a one dimensional null space. Thus,
+%we choose to solve the above integral equation subject to 
+%the constraint $\int_{\Gamma} \sigma \, dS = 0$. 
+%Furthermore, it is known that solving the Neumann problem subject 
+%to the above constraint is equivalent
+%to solving
+%\begin{align}
+%\left( \frac{1}{2}I_{\mathcal{X}} + K^L_\Gamma  + W_\Gamma \right) \sigma 
+%= -\frac{\partial v_2}{\partial \tau}
+%\label{eq:BlockSystemRow2P1} 
+%\end{align}
+%where $W_\Gamma\sigma = \int_{\Gamma} \sigma \, dS$. 
+%To prove this, we need 
+%the following property of 
+%the Green's function for Laplace's equation.
+%\begin{align}
+%-\frac{1}{2\pi}\oint_{\gamma} \frac{\partial}{\partial n_{\by}}  
+%\log \left|\bx - \by\right|\, dS \left(\by \right) 
+%&=-\frac{1}{2}\quad\bx\in\gamma \, , \label{eq:DLP2}
+%\end{align}
+%Using the above property, it follows that
+%\begin{align}
+% \int_{\Gamma} K^L_\Gamma \sigma \, dS(\x) 
+%= -\frac{1}{2}\int_{\Gamma} \sigma \left(\bx\right) \, dS(\x) 
+%\label{eq:KLint}
+%\end{align}
+%Integrating equation \cref{eq:BlockSystemRow2P1} and using 
+%equation \cref{eq:KLint}, we get
+%\begin{align}
+%\int_{\Gamma} \left( \frac{1}{2}I_{\mathcal{X}} + 
+%K^L_\Gamma  + L \right) \sigma \, dS(\x) 
+%&= -\int_{\Gamma} \frac{\partial v_2}{\partial \tau} \, dS(\x) \\
+%\left|\Gamma\right| L\sigma  &= 0 
+%\end{align}
+%which proves the result.
+
+\subsection{Making the representation complete}
+As mentioned above, the solution $\tilde{w}$ of 
+the auxiliary Helmholtz-Stokes problem \cref{eq:biharm5}
+only satisfies the boundary conditions of the 
+original Dirichlet problem \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}
+up to a constant on each boundary component. For a simply
+connected domain, this constant can be recovered from the
+fact that adding an arbitrary constant to a stream function
+does not change the velocity field. 
+Thus, in simply connected domains, there is an equivalence in the 
+solutions of \cref{eq:biharm5} and \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}.
+
+To analyze the case of a multiply connected domain,
+we first consider
+radially symmetric solutions on an annulus centered at the
+origin. Let $w\left(r\right)$ be a 
+radially symmetric biharmonic-Stokes
+potential. Then $w(r)$ solves the ordinary differential
+equation (ODE)
+\begin{equation}
+\Delta_{r} (\Delta_{r} + k^2)w = 0 \, ,
+\end{equation}
+where $\Delta_{r}$ is the radial component of the Laplacian in polar
+coordinates given by
+$$
+\Delta_{r} = \frac{1}{r}\frac{d}{dr} r \frac{d}{dr} \, .
+$$
+Four linearly independent solutions of this ODE are $1$, $\log{(r)}$, 
+$J_{0}(kr)$, and $H_{0}(kr)$, 
+where $J_{0}$ is the order zero Bessel function of the first kind, and $H_{0}$ is the order zero Hankel function of the first kind.
+For each solution, we can compute the associated velocity field 
+$\bu = \nabla^{\perp} w$. By construction, $\bu$ satisfies 
+the continuity condition \cref{eq:MassConservation}. 
+For the momentum equation \cref{eq:StokesFlowEq} to be 
+satisfied, we need that $\Delta\bu + k^2 \bu$ is a conservative
+vector field, which 
+is equivalent to the condition that 
+$\int_{\gamma} (\Delta\bu + k^2 \bu) \cdot d\bl = 0$ 
+for any closed 
+loop $\gamma$ in the annulus. For $\tilde{w}=1$, $J_{0}(kr)$, and $H_{0}(kr)$,
+the corresponding velocity field satisfies
+$\Delta \bu + k^2 \bu=0$ so that $\Delta \bu$
+is trivially a conservative vector field. 
+On the other hand, for $\tilde{w}=\log{(r)}$, the corresponding velocity field
+satisfies $\Delta \bu + k^2 \bu=\frac{k^2}{r} \hat{\theta}$.
+By considering a curve $\gamma$ encircling the origin,
+we see that $\Delta \bu + k^2 \bu$ is not a conservative vector
+field and that any pressure for the velocity field 
+associated with $\log\left(r\right)$ is not single-valued.
+%
+%The above analysis
+%can be extended to show that any solution of the biharmonic equation 
+%of the form $\log{|r-r_{j}|}$ where $r_{j}$ is located in one of the holes of a multiply connected
+%domain.
+%cannot be represented as a Stokes velocity field. 
+%In simply connected 
+%domains, since there are no holes, corresponding to each solution of the modified biharmonic equation with clamped plate
+%boundary conditions, there exists a solution to . For multiply connected domains with genus $N$, 
+%the set of stream functions for Stokes velocity fields
+%misses an $N$ dimensional space of solutions, corresponding 
+%to biharmonic charges located in the holes of the domain.
+%Following this reasoning, we obtain a complete representation
+%for biharmonic potentials on multiply connected domains
+%by adding $N$ charges, one per each hole of the domain,
+%to the representation for $w$. The details of this approach, and
+%the proof that it is sufficient, is in the next section.
+
 \bibliographystyle{plain}

### 2018-04-24 src/cgmres.f

@@ -1,0 +1,635 @@
+ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+c
+c       This is the end of the debugging routines and the beginning 
+c       of the complex GMRES routines
+c
+ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+c
+c
+c
+c
+c
+        subroutine cgmres(ier,n,a,multa,p1,p2,p3,p4,y,eps,numit,
+     1     x,niter,errs,ngmrec,w)
+        implicit real *8 (a-h,o-z)
+        dimension errs(1)
+        complex *16 a(n,n),x(1),y(1),w(1)
+c
+        external multa
+c
+c     This subroutine solves a complex linear system Ax=y by means
+c     of GMRES algorithm. This is a memory management routine for 
+c     cgmres1 which performs the actual work.
+c
+c     Input parameters:
+c
+c     n - the dimensionality of the linear system
+c     y - the right hand side
+c     a - the matrix of the system (or whatever other parameter)
+c     eps - the required accuracy
+c     multa - the user-defined matrix-vector multiplication subroutine
+c
+c     the calling sequence for multa must be
+c
+c     multa(a,p1,p2,p3,p4,x,y,n)               (1)
+c
+c       in (1), a is a matrix the system or whatever other parameter,
+c       par1, par2 are whatever other parameters, x is an input vector,
+c       y is a product Ax, and n is the dimensionality of a, x, and y.
+c
+c     numit - the maximum number of iteration permitted
+c     ngmrec - the maximum number of iteration 
+c            which GMRES algorithm needs to be restarted
+c
+c     w - must be at least (ngmrec*2+4)*n complex *16 elements long
+c
+c     Output parameters:
+c
+c     ier - error return code
+c        ier=0 normal execution of the subroutine
+c        ier=4 means that the maximum number iterations numit
+c           has been reached without achieving the required accuracy eps
+c        ier=8 means that the errors failed to decrease before the maximum
+c           number of iterations has been reached or the required accuracy
+c           eps has benn reached. 
[…]

### 2018-04-24 src/chunks_helmstokes_kerndefs_fark.f90

@@ -1,0 +1,196 @@
+
+!***************************************************************
+!
+! Kernels and Green's functions for implementing the
+! integral equations for the helmholtz stokes 
+! The integral equations are the extension of
+! one's presented in Peter Farkas' thesis and the Jiang Quaife Kropinski
+! paper
+!
+!***************************************************************
+
+subroutine zfark_kernel(par0, src, targ, src_normal, &
+     targ_normal, q1, q2, fgreen, pars1, pars2, val)
+  implicit real *8 (a-h,o-z)
+  real *8 src(2), targ(2), src_normal(2)
+  real *8 targ_normal(2), pars1(*), pars2(*)
+  complex *16 par0, q1, q2, g, dnyg, dnxg, dnxdnyg
+  complex *16 val
+
+  complex *16 val2, grad2(10), hess2(2,2), vec(10)
+
+  call fgreen(par0, src, targ, src_normal, pars2, val2, &
+       grad2, hess2)
+
+  val = val2
+
+  return
+end subroutine zfark_kernel
+!--------------------------------
+!
+subroutine zfark_kernelp(par0, src, targ, src_normal, &
+     targ_normal, q1, q2, fgreen, pars1, pars2, val)
+  implicit real *8 (a-h,o-z)
+  real *8 src(2), targ(2), src_normal(2)
+  real *8 targ_normal(2), pars1(*), pars2(*)
+  complex *16 par0, q1, q2, g, dnyg, dnxg, dnxdnyg
+  complex *16 val
+
+  complex *16 val2, grad2(2), hess2(2,2)
+
+  call fgreen(par0, src, targ, src_normal, pars2, val2, &
+       grad2, hess2)
+
+  val = targ_normal(1)*grad2(1) + targ_normal(2)*grad2(2)
+
+  return
+end subroutine zfark_kernelp
+
+!----------------------------------
+subroutine zhfark_ck2(zk,src,targ,src_normal, &
+     pars2,val,grad,hess)
+  implicit real *8 (a-h,o-z)
[…]

### 2018-04-24 src/cmat_build.f90

@@ -1,0 +1,1107 @@
+
+        !
+        !     This file contains several subroutines for constructing
+        !     matrices corresponding to layer potentials with
+        !     complex-valued kernels, i.e. helmholtz, etc.
+        !
+        !     The important subroutines are as follows:
+        !
+        !       zbuildmat - 
+        !
+        !
+
+      subroutine zget_neumann(wgeo, fincoming, par0, src, pars1, &
+          pars2, uinc)
+        implicit real *8 (a-h,o-z)
+        real *8, intent(in) :: wgeo(*), src(2)
+        complex *16, intent(in) :: par0, pars1(*), pars2(*)
+        complex *16, intent(out) :: uinc(*)
+
+        real *8 :: dnorm(10)
+        complex *16 :: val, grad(2), hess(2,2)
+
+        !
+        ! evaluate the dirichlet data on the boundary contained
+        ! in wgeo using the function fincoming
+        !
+
+        call chunkunpack1(wgeo, k, nch, ichunks, iadjs, iders, &
+            iders2, ihs)
+
+        do i = 1,k*nch
+          ind = 2*(i-1)
+          xp = wgeo(iders+ind)
+          yp = wgeo(iders+ind+1)
+          sc = sqrt(xp**2+yp**2)
+          dnorm(1) = yp/sc
+          dnorm(2) = -xp/sc
+          call fincoming(par0, src, wgeo(ichunks+ind), pars1, &
+              pars2, val, grad, hess)
+          uinc(i) = (dnorm(1)*grad(1) + dnorm(2)*grad(2))
+        enddo
+
+      end subroutine
+
+
+
+
+      subroutine zget_dirichlet(wgeo, fincoming, par0, src, pars1, &
+          pars2, uinc)
+        implicit real *8 (a-h,o-z)
+        real *8, intent(in) :: wgeo(*), src(2)
+        complex *16, intent(in) :: par0, pars1(*), pars2(*)
+        complex *16, intent(out) :: uinc(*)
+
+        complex *16 :: val, grad(2), hess(2,2)
+
+        !
+        ! evaluate the dirichlet data on the boundary contained
+        ! in wgeo using the function fincoming
+        !
+
+        call chunkunpack1(wgeo, k, nch, ichunks, iadjs, iders, &
+            iders2, ihs)
+
+        do i = 1,k*nch
+          ind = 2*(i-1)
+          call fincoming(par0, src, wgeo(ichunks+ind), pars1, &
+              pars2, val, grad, hess)
+          uinc(i) = val
[…]

### 2018-04-24 src/hbhrouts2d.f

@@ -22,13 +22,14 @@ c
 cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
       implicit none
 c     global variables
-      real *8 beta, source(2,*), charge(*), dipstr(*)
+      real *8 source(2,*), charge(*), dipstr(*)
+      complex *16 beta
       real *8 dipvec(2,*), quadstr(*), quadvec(3,*)
       real *8 target(2)
-      real *8 pot, grad(2), hess(3)
+      complex *16 pot, grad(2), hess(3)
       integer ns, ifcharge, ifdipole, ifquad, ifpot, ifgrad, ifhess
 c     local variables
-      real *8 potloc,gradloc(2),hessloc(3),der3(4),der4(5),der5(6)
+      complex *16 potloc,gradloc(2),hessloc(3),der3(4),der4(5),der5(6)
       integer ifpotloc, ifgradloc, ifhessloc, ifder3, ifder4, ifder5
       integer i
 
@@ -126,13 +127,14 @@ c
 cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
       implicit none
 c     global variables
-      real *8 beta, source(2,*), charge(*), dipstr(*)
+      real *8 source(2,*), charge(*), dipstr(*)
+      complex *16 beta
       real *8 dipvec(2,*), quadstr(*), quadvec(3,*)
       real *8 target(2)
-      real *8 pot, grad(2), hess(3)
+      complex *16 pot, grad(2), hess(3)
       integer ns, ifcharge, ifdipole, ifquad, ifpot, ifgrad, ifhess
 c     local variables
-      real *8 pottemp, gradtemp(2), hesstemp(3)
+      complex *16 pottemp, gradtemp(2), hesstemp(3)
 
       call hbhpotgrad2dall_cdq(beta,source,ns,ifcharge,
      1     charge,ifdipole,dipstr,dipvec,ifquad,quadstr,quadvec,
@@ -162,14 +164,16 @@ c
 cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
       implicit none
 c     global variables
-      real *8 beta, source(2,*), charge(*), dipstr(*)
+      real *8 source(2,*), charge(*), dipstr(*)
+      complex *16 beta
       real *8 dipvec(2,*), quadstr(*), quadvec(3,*)
       real *8 target(2)
[…]

### 2018-04-24 src/prini.f

@@ -1,113 +1,124 @@
-ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-c
-c    $Date: 2010-11-16 11:26:35 -0800 (Tue, 16 Nov 2010) $
-c    $Revision: 1452 $
-c
-c
-c
-ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-c       Printing routines
-ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
-C
-C
-C
+C 
+C 
+C 
+C 
         SUBROUTINE PRINI(IP1,IQ1)
+        save
         CHARACTER *1 MES(1), AA(1)
-         save
         REAL *4 A(1)
         REAL *8 A2(1)
         REAL *8 A4(1)
-ccc        INTEGER *4 IA(1)
-        INTEGER IA(1)
-        INTEGER *4 IA1(1)
+        INTEGER *4 IA(1)
         INTEGER *2 IA2(1)
-        data IP/0/,IQ/0/
+        logical *1 la(1)
         IP=IP1
         IQ=IQ1
+  
         RETURN
-
-C
-C
-C
-C
-C
+  
+C 
+C 
+C 
+C 
+C 
         ENTRY PRIN(MES,A,N)
         CALL  MESSPR(MES,IP,IQ)
         IF(IP.NE.0 .AND. N.NE.0) WRITE(IP,1200)(A(J),J=1,N)
         IF(IQ.NE.0 .AND. N.NE.0) WRITE(IQ,1200)(A(J),J=1,N)
  1200 FORMAT(6(2X,E11.5))
          RETURN
-C
-C
-C
-C
+C 
+C 
+C 
+C 
         ENTRY PRIN2(MES,A2,N)
         CALL MESSPR(MES,IP,IQ)
         IF(IP.NE.0 .AND. N.NE.0) WRITE(IP,1400)(A2(J),J=1,N)
         IF(IQ.NE.0 .AND. N.NE.0) WRITE(IQ,1400)(A2(J),J=1,N)
  1400 FORMAT(6(2X,E11.5))
         RETURN
-C
-C
-C
-C
+C 
+C 
+C 
+C 
+        ENTRY PRIN2_long(MES,A2,N)
+        CALL MESSPR(MES,IP,IQ)
[…]

### 2018-04-24 test/test1.f

@@ -1,0 +1,485 @@
+      program main
+      implicit real *8 (a-h,o-z)
+
+      call prini(6,13)
+      call prin2('Enter n*',n,0)
+      read *, n
+
+      call biharmdmatgen()
+
+      return
+      end
+
+c------------------------------------------------------     
+c
+      subroutine biharmdmatgen()
+
+      implicit real *8 (a-h,o-z)
+
+      real *8, allocatable :: chunks(:,:,:)
+      real *8, allocatable :: ders(:,:,:)
+      real *8, allocatable :: rn(:,:,:)
+      real *8 sc
+      real *8, allocatable :: ders2(:,:,:),dsdta(:,:)
+      real *8, allocatable :: hs(:)
+      integer, allocatable :: adjs(:,:)
+      real *8, allocatable :: ck(:)
+
+      real *8, allocatable :: wgeos(:)
+      real *8, allocatable :: wgeos3(:)
+
+      complex *16, allocatable :: work(:),workspace(:)
+      complex *16, allocatable :: rhs(:),soln(:),soln2(:)
+      integer, allocatable :: nchs(:)
+
+      complex *16 zk
+
+c     matrix formation, eigenvalue calculation
+
+      real *8, allocatable :: whts(:,:)
+      complex *16, allocatable :: xmat(:,:),xmat2(:,:)
+      complex *16 p1(10),p2,p3,p4
+      real *8, allocatable :: cms(:,:)
+      
+      real *8, allocatable :: xs(:),ys(:),cxs(:),cys(:),qwts(:)
+      real *8, allocatable :: dxdt(:),dydt(:),dsdt(:),rnx(:),rny(:)
+      real *8, allocatable :: rkappa(:)
+
+      integer novers(1000), iparsindeces(1000)
+      integer ifcloseds(1000)
+      real *8 chsmalls(1000), tas(1000), tbs(1000)
+      real *8 epss(1000), pars(10 000), pars1(100),pars2(100)
+
+      real *8 src(2),targ(2)
+      
+      complex *16, allocatable :: pot(:,:)
+      complex *16, allocatable :: pottau(:,:)
+      complex *16, allocatable :: grad(:,:,:)
[…]

### 2018-04-24 test/test2.f

@@ -1,0 +1,505 @@
+      program main
+      implicit real *8 (a-h,o-z)
+
+      call prini(6,13)
+      call prin2('Enter n*',n,0)
+      read *, n
+
+      call biharmdmatgen()
+
+      return
+      end
+
+c------------------------------------------------------     
+c
+      subroutine biharmdmatgen()
+
+      implicit real *8 (a-h,o-z)
+
+      real *8, allocatable :: chunks(:,:,:)
+      real *8, allocatable :: ders(:,:,:)
+      real *8, allocatable :: rn(:,:,:)
+      real *8 sc
+      real *8, allocatable :: ders2(:,:,:),dsdta(:,:)
+      real *8, allocatable :: hs(:)
+      integer, allocatable :: adjs(:,:)
+      real *8, allocatable :: ck(:)
+
+      real *8, allocatable :: wgeos(:)
+      real *8, allocatable :: wgeos3(:)
+
+      complex *16, allocatable :: work(:),workspace(:)
+      complex *16, allocatable :: rhs(:),soln(:),soln2(:)
+      integer, allocatable :: nchs(:)
+
+      complex *16 zk
+
+c     matrix formation, eigenvalue calculation
+
+      real *8, allocatable :: whts(:,:)
+      complex *16, allocatable :: xmat(:,:),xmat2(:,:)
+      complex *16 p1(10),p2,p3,p4
+      real *8, allocatable :: cms(:,:)
+      
+      real *8, allocatable :: xs(:),ys(:),cxs(:),cys(:),qwts(:)
+      real *8, allocatable :: dxdt(:),dydt(:),dsdt(:),rnx(:),rny(:)
+      real *8, allocatable :: rkappa(:)
+
+      integer novers(1000), iparsindeces(1000)
+      integer ifcloseds(1000)
+      real *8 chsmalls(1000), tas(1000), tbs(1000)
+      real *8 epss(1000), pars(10 000), pars1(100),pars2(100)
+
+      real *8 src(2),targ(2),verts(2,10000),widths(10000)
+      
+      complex *16, allocatable :: pot(:,:)
+      complex *16, allocatable :: pottau(:,:)
[…]

### 2018-04-24 test/test3.f

@@ -1,0 +1,538 @@
+      program main
+      implicit real *8 (a-h,o-z)
+
+      call prini(6,13)
+      call prin2('Enter n*',n,0)
+      read *, n
+
+      call biharmdmatgen()
+
+      return
+      end
+
+c------------------------------------------------------     
+c
+      subroutine biharmdmatgen()
+
+      implicit real *8 (a-h,o-z)
+
+      real *8, allocatable :: chunks(:,:,:)
+      real *8, allocatable :: ders(:,:,:)
+      real *8, allocatable :: rn(:,:,:)
+      real *8 sc
+      real *8, allocatable :: ders2(:,:,:),dsdta(:,:)
+      real *8, allocatable :: hs(:)
+      integer, allocatable :: adjs(:,:)
+      real *8, allocatable :: ck(:)
+
+      real *8, allocatable :: wgeos(:)
+      real *8, allocatable :: wgeos3(:)
+
+      complex *16, allocatable :: work(:),workspace(:)
+      complex *16, allocatable :: rhs(:),soln(:),soln2(:)
+      integer, allocatable :: nchs(:)
+
+      complex *16 zk
+
+c     matrix formation, eigenvalue calculation
+
+      real *8, allocatable :: whts(:,:)
+      complex *16, allocatable :: xmat(:,:),xmat2(:,:)
+      complex *16 p1(10),p2,p3,p4
+      real *8, allocatable :: cms(:,:)
+      
+      real *8, allocatable :: xs(:),ys(:),cxs(:),cys(:),qwts(:)
+      real *8, allocatable :: dxdt(:),dydt(:),dsdt(:),rnx(:),rny(:)
+      real *8, allocatable :: rkappa(:)
+
+      integer novers(1000), iparsindeces(1000)
+      integer ifcloseds(1000)
+      real *8 chsmalls(1000), tas(1000), tbs(1000)
+      real *8 epss(1000), pars(10 000), pars1(100),pars2(100)
+
+      real *8 src(2),targ(2),verts(2,10000),widths(10000)
+      
+      complex *16, allocatable :: pot(:,:)
+      complex *16, allocatable :: pottau(:,:)
[…]

### 2018-04-24 test/test4.f

@@ -1,0 +1,577 @@
+      program main
+      implicit real *8 (a-h,o-z)
+      real *8 w(1000000)
+
+      call prini(6,13)
+      call prin2('Enter icase*',n,0)
+      read *, icase
+
+
+      aa = 1
+      bb = 0.5
+
+ 2100 format('data for ff=',e11.5)
+ 2110 format('npts=',i7)
+ 2120 format('sing=')
+ 2130 format(2x,e11.5)
+ 2150 format('c  ')
+
+      ff = 2.5*2**(icase-1.0d0)
+      
+      ising = 1
+
+      iw2 = 26+icase
+      call biharmdmatgen(iw2,aa,bb,ff,ntot,w(ising))
+      
+
+      iw = 16 + icase
+      write(iw,2100) ff
+      write(iw,2110) ntot
+      write(iw,2150)
+      write(iw,2120)
+      do i=1,ntot
+
+      write(iw,2130) w(ising+2*i-2)
+
+      enddo
+
+      stop
+      end
+
+c------------------------------------------------------     
+c
+      subroutine biharmdmatgen(ifile,aa,bb,ff,ntot,sing)
+
+      implicit real *8 (a-h,o-z)
+
+      real *8, allocatable :: chunks(:,:,:)
+      real *8, allocatable :: ders(:,:,:)
+      real *8, allocatable :: rn(:,:,:)
+      real *8 sc
+      real *8, allocatable :: ders2(:,:,:),dsdta(:,:)
+      real *8, allocatable :: hs(:)
+      integer, allocatable :: adjs(:,:)
+      real *8, allocatable :: ck(:)
+
+      real *8, allocatable :: wgeos(:)
+      real *8, allocatable :: wgeos3(:)
+
+      complex *16, allocatable :: work(:),workspace(:)
+      complex *16, allocatable :: rhs(:),soln(:),soln2(:)
+      integer, allocatable :: nchs(:)
+
+      complex *16 zk
+
+c     matrix formation, eigenvalue calculation
+
+      real *8, allocatable :: whts(:,:)
+      complex *16, allocatable :: xmat(:,:),xmat2(:,:)
+      complex *16 p1(10),p2,p3,p4
+      real *8, allocatable :: cms(:,:)
+      
[…]

### 2018-04-24 test/test4Data/plot26.py

@@ -1,0 +1,11 @@
+#!/usr/bin/python
+import matplotlib.pyplot as pt
+import numpy as np
+
+x = np.loadtxt("plot26.dat")
+x = x.reshape(np.size(x)/2,2)
+x1=x[:,0]
+x2=x[:,1]
+pt.plot(x1,x2,"kx")
+pt.title("a                               ")
+pt.show()

### 2018-04-24 test/test4Data/plot27.py

@@ -1,0 +1,11 @@
+#!/usr/bin/python
+import matplotlib.pyplot as pt
+import numpy as np
+
+x = np.loadtxt("plot27.dat")
+x = x.reshape(np.size(x)/2,2)
+x1=x[:,0]
+x2=x[:,1]
+pt.plot(x1,x2,"kx")
+pt.title("a                               ")
+pt.show()

### 2018-04-24 test/test4Data/plot28.py

@@ -1,0 +1,11 @@
+#!/usr/bin/python
+import matplotlib.pyplot as pt
+import numpy as np
+
+x = np.loadtxt("plot28.dat")
+x = x.reshape(np.size(x)/2,2)
+x1=x[:,0]
+x2=x[:,1]
+pt.plot(x1,x2,"kx")
+pt.title("a                               ")
+pt.show()

### 2018-04-24 test/test4Data/plot29.py

@@ -1,0 +1,11 @@
+#!/usr/bin/python
+import matplotlib.pyplot as pt
+import numpy as np
+
+x = np.loadtxt("plot29.dat")
+x = x.reshape(np.size(x)/2,2)
+x1=x[:,0]
+x2=x[:,1]
+pt.plot(x1,x2,"kx")
+pt.title("a                               ")
+pt.show()

### 2018-04-24 test/test4Data/plot30.py

@@ -1,0 +1,11 @@
+#!/usr/bin/python
+import matplotlib.pyplot as pt
+import numpy as np
+
+x = np.loadtxt("plot30.dat")
+x = x.reshape(np.size(x)/2,2)
+x1=x[:,0]
+x2=x[:,1]
+pt.plot(x1,x2,"kx")
+pt.title("a                               ")
+pt.show()

### 2018-04-24 test/testg1g2.f

@@ -1,0 +1,155 @@
+
+      program testg1g2
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+c        this subroutine tests the greens function
+c        in the farkas representation for the helmholtz stokes
+c        equation with the formula in the jiang-quaife-kropinski
+c        paper
+cccccc
+
+      implicit real *8 (a-h,o-z)
+      real *8 dtoobig, dtoosmall
+      complex *16 eye
+      data eye / (0.0d0,1.0d0) /
+      complex *16 zk
+      real *8 rr,rnsrc(2),rntarg(2),source(2),targ(2)
+      complex *16 val,grad(2),hess(4),val2
+     
+      call prini(6,13)
+      call prin2('Enter n*',n,0)
+      read *, n
+
+      done = 1
+      pi = atan(done)*4
+
+
+
+      zk = 1 + hkrand(0)
+      source(1) = hkrand(0)
+      source(2) = hkrand(0)
+
+      targ(1) = hkrand(0) + 2.0d0
+      targ(2) = hkrand(0)
+
+
+      thet = 2.0d0*pi*hkrand(0)
+      rnsrc(1) = cos(thet) 
+      rnsrc(2) = sin(thet) 
+
+
+      thet = 2.0d0*pi*hkrand(0)
+      rntarg(1) = cos(thet) 
+      rntarg(2) = sin(thet)
+
+cc      call prin2('rnsrc=*',rnsrc,2)
+
+
+      call zhfark_ck1(zk,source,targ,rnsrc,pars2,val,
+     1   grad,hess)
+      
+      call helmstokes_fark_g1_jiang(zk,source,targ,rnsrc,val2)
+      
+
+cc      call prin2('val=*',val,2)
+cc      call prin2('val2=*',val2,2)
+
+      err = abs(val-val2)
+      call prin2('error kernel1=*',err,1)
+
+
+      val = 0
+      val2 = 0
+      call zhfark_ck2(zk,source,targ,rnsrc,pars2,val,
+     1   grad,hess)
+      
+      call helmstokes_fark_g2_jiang(zk,source,targ,rnsrc,val2)
+      
+
+cc      call prin2('val=*',val,2)
+cc      call prin2('val2=*',val2,2)
+
[…]

### 2018-04-24 doc/draft-01/biharm-evals.tex

@@
 
-\title{An integral equation method for the biharmonic
-Dirichlet eigenvalue problem in two dimensions}
+\title{A Fredholm operator approach to the plate
+buckling eigenvalue problem}
 \author{Askham and Rachh}
@@
 \subsection{Layer potentials}
+
+We now use the Stokeslet and stresslet definitions
+of the previous section to define the standard single
+and double layer potentials of the Stokes eigenvalue
+problem. The single layer potential is defined to
+be
+
+\begin{equation}
+  \SS \bmu (\xx) = \int_\Gamma \GG (\xx,\yy) \bmu(\yy)
+  \, dS(\yy) \; .
+\end{equation}
+The double layer potential is defined to be
+
+\begin{equation}
+  \DD \bmu (\xx) = \int_\Gamma \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy)
+  \right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
+\end{equation}
+where $\bnu$ denotes the outward unit normal to the boundary.
+If we write $\bmu = \bnu \mu_\nu + \btau \mu_\tau$,
+where $\btau = \bmu^\bot$ is the positively oriented unit
+tangent to the curve, then we have
+
+\begin{align}
+  \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy) \right )^\intercal
+  \bmu(\yy) &= \left ( - \nabla G_L(\xx,\yy) + 2 \nabla^\bot
+  \partial_{\nu\tau} G_{BH}(\xx,\yy) \right ) \mu_\nu(\yy) \nonumber \\
+  & \qquad+
+  \nabla^\bot \left (\partial_{\tau\tau}-\partial_{\nu\nu} \right )
+  G_{BH}(\xx,\yy) \mu_\tau(\yy) \; .
+\end{align}
 

### 2018-04-24 src/hbhrouts2d.f
Adding back hbhrouts2d.f 2a871b.. version

@@ -1,0 +1,689 @@
+cc Copyright (C) 2017: Travis Askham
+cc Contact: askhamwhat@gmail.com
+cc 
+cc This program is free software; you can redistribute it and/or modify 
+cc it under the terms of the GNU General Public License as published by 
+cc the Free Software Foundation; either version 2 of the License, or 
+cc (at your option) any later version.  This program is distributed in 
+cc the hope that it will be useful, but WITHOUT ANY WARRANTY; without 
+cc even the implied warranty of MERCHANTABILITY or FITNESS FOR A 
+cc PARTICULAR PURPOSE.  See the GNU General Public License for more 
+cc details. You should have received a copy of the GNU General Public 
+cc License along with this program; 
+cc if not, see <http://www.gnu.org/licenses/>.
+
+      subroutine hbhpotgrad2dall_cdq(beta,source,ns,ifcharge,
+     1     charge,ifdipole,dipstr,dipvec,ifquad,quadstr,quadvec,
+     2     target,ifpot,pot,ifgrad,grad,ifhess,hess)
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+c
+c
+c
+cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+      implicit none
+c     global variables
+      real *8 source(2,*), charge(*), dipstr(*)
+      complex *16 beta
+      real *8 dipvec(2,*), quadstr(*), quadvec(3,*)
+      real *8 target(2)
+      complex *16 pot, grad(2), hess(3)
+      integer ns, ifcharge, ifdipole, ifquad, ifpot, ifgrad, ifhess
+c     local variables
+      complex *16 potloc,gradloc(2),hessloc(3),der3(4),der4(5),der5(6)
+      integer ifpotloc, ifgradloc, ifhessloc, ifder3, ifder4, ifder5
+      integer i
+
+      ifpotloc = 1
+      ifgradloc = 1
+      ifhessloc = 1
+      ifder3 = 1
+      ifder4 = 1
+      ifder5 = 0
+
+      if (ifpot .eq. 1) pot = 0.0d0
+      if (ifgrad .eq. 1) then
+         grad(1) = 0.0d0
+         grad(2) = 0.0d0
+      endif
+      if (ifhess .eq. 1) then
[…]

### 2018-06-14 test/test10Data/plot23.py
Including test10Data

@@ -1,0 +1,11 @@
+#!/usr/bin/python
+import matplotlib.pyplot as pt
+import numpy as np
+
+x = np.loadtxt("plot23.dat")
+x = x.reshape(np.size(x)/2,2)
+x1=x[:,0]
+x2=x[:,1]
+pt.plot(x1,x2,"kx")
+pt.title("a                               ")
+pt.savefig("plot23.pdf")

### 2018-06-14 test/test8.f

@@ -1,0 +1,227 @@
+      implicit real *8 (a-h,o-z)
+      real *8 pars(1000),roots(1000)
+
+      external fdet1,fdet2
+
+      call prini(6,13)
+      call prin2('Enter n*',n,0)
+      read *, n
+
+      r1 = 1.0d0
+      r2 = 1.7d0
+
+      pars(1) = r1
+      pars(2) = r2
+
+
+c
+cc       find neumann eigenfunctions using bisection
+c
+c
+
+      x = 5.0d0
+      call fdet1(x,pars,f)
+
+      a = 1.0d0
+      b = 3.0d1
+
+      h = 1.0d-2
+
+      nmax = 10
+      call findroots(fdet1,pars,a,b,h,nmax,roots,nroots)
+
+      call prinf('nroots=*',nroots,1)
+      call prin2('roots=*',roots,nroots)
+
+      f = 0
+      call fdet1(roots(1),pars,f)
+      call prin2('f=*',f,1)
+
+
+      a = 1.0d0
+      b = 3.0d1
+      h = 1.0d-2
+
+      nmax = 100
+      call findroots(fdet2,pars,a,b,h,nmax,roots,nroots)
+
+      call prinf('nroots=*',nroots,1)
+      call prin2_long('roots=*',roots,nroots)
+
+      call fdet2(roots,pars,f)
+      call prin2('f=*',f,1)
+
+      return
+      end
+c----------------------------------      
+
+      subroutine fdet1(x,pars,f)
+      implicit real *8 (a-h,o-z)
+      integer ifexpon
+      real *8 pars(*),xtmp(6)
+      complex *16 h1,h0,z1,z2
+
+      ifexpon = 1
+      r1 = pars(1)
+      r2 = pars(2)
+
+      z1 = x*r1
+
+      h0 = 0
+      h1 = 0
+      ifexpon = 1 
+      call hank103(z1,h0,h1,ifexpon)
+      
+      a11 = real(h1)
+      a12 = imag(h1)
+
+      z2 = cmplx(x*r2,0)
+
+      h1 = 0
+      call hank103(z2,h0,h1,ifexpon)
+      a21 = -real(h1)
+      a22 = -imag(h1)
+
+      f = a11*a22 - a12*a21
+
+      xtmp(1) = r1
+      xtmp(2) = r2
+      xtmp(3) = a11
+      xtmp(4) = a12
+      xtmp(5) = a21
+      xtmp(6) = a22
[…]

### 2018-06-14 test/test9Data/plot24.py

@@ -1,0 +1,19 @@
+#!/usr/bin/python
+import matplotlib.pyplot as pt
+import numpy as np
+
+x = np.loadtxt("plot24.dat1")
+x = x.reshape(np.size(x)/2,2)
+x1=x[:,0]
+x2=x[:,1]
+
+y = np.loadtxt("plot24.dat2")
+y = y.reshape(np.size(y)/2,2)
+y1=y[:,0]
+y2=y[:,1]
+
+pt.plot(x1,x2,"k.")
+pt.plot(y1,y2,"gx")
+pt.title("a                               ")
+pt.axes().set_aspect("equal")
+pt.show()

### 2018-06-14 test/test9Data/plot26.py

@@ -1,0 +1,19 @@
+#!/usr/bin/python
+import matplotlib.pyplot as pt
+import numpy as np
+
+pt.rc("font", size=16)
+x = np.loadtxt("plot26.dat1")
+x = x.reshape(  200,  200, order="F")
+y = np.loadtxt("plot26.dat2")
+f=open("plot26.dat3","r")
+iss = 0
+nd =     4
+for i in range(nd):
+    nn = int(f.readline())
+    pt.fill(y[iss:iss+nn,0],y[iss:iss+nn,1],facecolor="w")
+    iss=iss+nn
+
+pt.imshow(x, extent=[-0.20, 1.20,-0.20, 0.70])
+cb=pt.colorbar(shrink=.9)
+pt.savefig("plot26.pdf")

### 2018-06-14 test/test9Data/plot37.py

@@ -1,0 +1,19 @@
+#!/usr/bin/python
+import matplotlib.pyplot as pt
+import numpy as np
+
+pt.rc("font", size=16)
+x = np.loadtxt("plot37.dat1")
+x = x.reshape(  300,  300, order="F")
+y = np.loadtxt("plot37.dat2")
+f=open("plot37.dat3","r")
+iss = 0
+nd =     4
+for i in range(nd):
+    nn = int(f.readline())
+    pt.fill(y[iss:iss+nn,0],y[iss:iss+nn,1],facecolor="w")
+    iss=iss+nn
+
+pt.imshow(x, extent=[-0.20, 1.20,-0.20, 0.70])
+cb=pt.colorbar(shrink=.9)
+pt.savefig("plot37.pdf")

### 2018-06-14 test/test9Data/plot38.py

@@ -1,0 +1,19 @@
+#!/usr/bin/python
+import matplotlib.pyplot as pt
+import numpy as np
+
+pt.rc("font", size=16)
+x = np.loadtxt("plot38.dat1")
+x = x.reshape(  300,  300, order="F")
+y = np.loadtxt("plot38.dat2")
+f=open("plot38.dat3","r")
+iss = 0
+nd =     4
+for i in range(nd):
+    nn = int(f.readline())
+    pt.fill(y[iss:iss+nn,0],y[iss:iss+nn,1],facecolor="w")
+    iss=iss+nn
+
+pt.imshow(x, extent=[-0.20, 1.20,-0.20, 0.70])
+cb=pt.colorbar(shrink=.9)
+pt.savefig("plot38.pdf")

### 2018-06-14 test/test9Data/plot39.py

@@ -1,0 +1,19 @@
+#!/usr/bin/python
+import matplotlib.pyplot as pt
+import numpy as np
+
+pt.rc("font", size=16)
+x = np.loadtxt("plot39.dat1")
+x = x.reshape(  300,  300, order="F")
+y = np.loadtxt("plot39.dat2")
+f=open("plot39.dat3","r")
+iss = 0
+nd =     4
+for i in range(nd):
+    nn = int(f.readline())
+    pt.fill(y[iss:iss+nn,0],y[iss:iss+nn,1],facecolor="w")
+    iss=iss+nn
+
+pt.imshow(x, extent=[-0.20, 1.20,-0.20, 0.70])
+cb=pt.colorbar(shrink=.9)
+pt.savefig("plot39.pdf")

### 2018-06-14 test/test9Data/plot47.py

@@ -1,0 +1,19 @@
+#!/usr/bin/python
+import matplotlib.pyplot as pt
+import numpy as np
+
+pt.rc("font", size=16)
+x = np.loadtxt("plot47.dat1")
+x = x.reshape(  100,  100, order="F")
+y = np.loadtxt("plot47.dat2")
+f=open("plot47.dat3","r")
+iss = 0
+nd =     4
+for i in range(nd):
+    nn = int(f.readline())
+    pt.fill(y[iss:iss+nn,0],y[iss:iss+nn,1],facecolor="w")
+    iss=iss+nn
+
+pt.imshow(x, extent=[-0.20, 1.20,-0.20, 0.70])
+cb=pt.colorbar(shrink=.9)
+pt.savefig("plot47.pdf")

### 2018-06-14 test/test9Data/plot48.py

@@ -1,0 +1,19 @@
+#!/usr/bin/python
+import matplotlib.pyplot as pt
+import numpy as np
+
+pt.rc("font", size=16)
+x = np.loadtxt("plot48.dat1")
+x = x.reshape(  100,  100, order="F")
+y = np.loadtxt("plot48.dat2")
+f=open("plot48.dat3","r")
+iss = 0
+nd =     4
+for i in range(nd):
+    nn = int(f.readline())
+    pt.fill(y[iss:iss+nn,0],y[iss:iss+nn,1],facecolor="w")
+    iss=iss+nn
+
+pt.imshow(x, extent=[-0.20, 1.20,-0.20, 0.70])
+cb=pt.colorbar(shrink=.9)
+pt.savefig("plot48.pdf")

### 2018-06-14 doc/draft-01/biharm-evals.tex
Updating tex file

@@
 \def\br{{\boldsymbol r}}
+\def\bh{{\boldsymbol h}}
 \def\bn{{\boldsymbol n}}
+\def\bT{{\boldsymbol T}}
 \def\xx{{\boldsymbol x}}
@@
 \def\littleo{o}
+\newcommand\dwdn{\frac{\partial w}{\partial n}}
+\newcommand{\cC}{\mathcal C}
 
@@
 \newtheorem{proposition}{Proposition}
+\newtheorem{lem}{Lemma}
 
@@
 \end{itemize}
+
+Consider the pure bending of an isotropic and homogeneous thin clamped
+plate. 
+Let $\Omega$ denote the midline of the thin plate, $\Gamma$ denote the 
+boundary of $\Omega$ and $w$ denote the vertical displacement.
+In this setup, the buckling eigenvalue problem consists of finding 
+eigenvalues $k^{2}$ and corresponding non-trivial eigenfunctions
+(or buckling modes) $w$ which satisfy the homogeneous Dirichlet
+modified Biharmonic problem (with an imaginary parameter $k$) given by
+\begin{align}
+\Delta (\Delta + k^2) w &= 0 \quad \text{in} \quad \Omega \label{eq:buck1} \\
+w &= 0 \quad \text{on} \quad \Gamma \label{eq:buck2}\\
+\dwdn &=0 \quad \text{on} \quad \Gamma \label{eq:buck3} \,.
+\end{align}
+It is well-known from classical potential theory that, 
+for the buckling eigenvalue problem, there
+exists a countable collection of eigenfrequencies 
+$0 < k_{1}^{2} \leq k_{2}^2 \leq \ldots \uparrow \infty$
+counting multiplicites.
+\begin{remark}
+For notational convenience,  
+we will refer to the modified Biharmonic problem
+with imaginary parameter as the Helmholtz-Biharmonic problem.
+\end{remark}
+
 \section{Mathematical Preliminaries}
 
-\subsection{Notation}
+In this paper, vector-valued
+quantities are denoted by bold, lower-case letters
+(e.g. $\bh$), while tensor-valued quantities are bold
+and upper-case (e.g. $\mathbf{T}$). 
+Subscript indices of non-bold characters (e.g. $h_j$ or $T_{jkl}$)
+are used to denote the entries within a vector ($\bh$) or tensor ($\bT$).
+We use the standard Einstein summation convention; in other words, 
+there is an implied sum taken over the repeated indices of 
+any term (e.g. the symbol $a_{j} b_{j}$ is used to represent the sum
+$\sum_{j} a_{j} b_{j}$).
+$\xx = (x_1,x_2)^\intercal$ then $\xx^\bot = (-x_2,x_1)^\intercal$.
+Similarly, $\nabla^\bot = (-\partial_{x_2},\partial_{x_1})^\intercal$.
 
-Bold symbols are vectors or tensors.
-$\xx = (x_1,x_2)^\intercal$ then $\xx^\bot = (-x_2,x_1)^\intercal$.
-Similarly, $\nabla^\bot = (-\partial_{x_2},\partial_{x_1})^\intercal$
-
-\subsection{Green's functions}
-
-$\Delta$
-\begin{equation}
-  G_L(\xx,\yy) = -\frac{1}{2\pi} \log |\xx-\yy|
-\end{equation}
-
-$\Delta + k^2$
-\begin{equation}
-  G_H(\xx,\yy) = \frac{i}{4} H_0^{(1)}(k|\xx-\yy|)
-\end{equation}
-
-$\Delta(\Delta + k^2)$
+\subsection{The Farkas integral representation}
+Following the treatment of \cite{askham}, the fundamental solution
+of the Helmholtz-Biharmonic equation is given by
 \begin{equation}
@@
   \left (\frac{1}{2\pi} \log |\xx-\yy| +
-  \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \right )
+  \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \right ) \, , 
 \end{equation}
+where $k$ is the Helmholtz paramater in the Helmholtz-Biharmonic equation,
+and $H_{0}^{1}(r)$ is the Hankel function of the first kind of order zero.
 
-\section{Integral Equation Formulation}
+In \cite{Farkas89}, Farkas derived integral equation formulations
+for the solution of the Dirichlet problem for the biharmonic equation ($k=0$). 
+In this formulation, the solution 
+$w$ is represented as a sum of two layer potentials
+\begin{equation}
+  w(\xx) = \int_\Gamma K_1^F (\xx,\yy) \sigma_1(\yy) \, dS(\yy)
+  + \int_\Gamma K_2^F(\xx,\yy) \sigma_2(\yy) \, dS(\yy) \; ,
+  \label{eq:farkRep}
+\end{equation}
+where $\sigma_{1}$, and $\sigma_{2}$ are unknown densities, and the kernels
+$K_{1}^{F}$, and $K_{2}^{F}$ are linear combinations of derivatives of
+the biharmonic Green's function and appropriately chosen to get second kind integral equations
+for the unknown densities $\sigma_{1}$ and $\sigma_{2}$ on imposing the boundary conditions.
 
-\subsection{The Helmholtz Stokeslet formulation}
+In \cite{shidongmodbi}, Jiang extended the Farkas formulation for the solution of the modified
+biharmonic equation, albeit for different boundary conditions. With minor modifications, their formulation
+can also be adopted for the solution of the Dirichlet problem for the Helmholtz-biharmonic equation
+\begin{align}
+\Delta (\Delta + k^2) w &= 0 \quad \text{in} \quad \Omega \label{eq:helmbi} \\
+w &= f \quad \text{on} \quad \Gamma \\
+\dwdn &=g \quad \text{on} \quad \Gamma \,,
+\end{align}
+where $f,g$ are prescribed functions on the boundary.
+
+For two points on the plane, $\xx$ and $\yy$, let $\br = \yy - \xx$. Let the kernels $K_{1}^{F}$, and 
+$K_{2}^{F}$ be defined by 
+\begin{align}
+  K_1^F(\xx,\yy) &= \partial_{n_{y}n_{y}n_{y}}\Gbh(\xx,\yy)
+  + 3 \partial_{n_{y}\tau_{y}\tau_{y}}\Gbh(\xx,\yy) + k^{2} \partial_{n_{y}}\Gbh(\xx,\yy)\; , \label{eq:kf1} \\
+  K_2^F(\xx,\yy) &= -\partial_{n_{y}n_{y}}\Gbh(\xx,\yy)
+  + \partial_{\tau_{y}\tau_{y}}\Gbh(\xx,\yy) \label{eq:kf2} \; .
+\end{align}
+More explicitly, we have
+\begin{align}
+  K_1^F(\xx,\yy) &=  -\dfrac{\br \cdot \bn(\yy)}{|\br|^2}  \cdot \left( \frac{3 i}{2} H_0^{(1)}(k|\br|) - \frac{5 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{6}{\pi k^2 |\br|^2} + \frac{1}{2\pi}  \right) +     \\
+  & \quad \dfrac{\left(\br \cdot \bn(\yy)\right)^3}{|\br|^4} \cdot \left( 2i H_0^{(1)}(k|\br|) - \frac{7 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{8}{\pi k^2 |\br|^2}  \right) \, , \nonumber \\
+  K_2^F(\xx,\yy) &=  -\left(\frac{1}{2}-\dfrac{\left(\br \cdot \bn(\yy)\right)^2}{|\br|^2} \right)  \cdot \left( \frac{i}{2} H_0^{(1)}(k|\br|) - \frac{i}{k|\br|} H_1^{(1)}(k|\br|) + \frac{2}{\pi k^2 |\br|^2}  \right)\; .
+\end{align}
+
+On enforcing the Dirichlet boundary conditions for
+$w$, we obtain the integral equation
+\begin{equation}
+  \begin{split}
+    \begin{pmatrix}
+      f(\xx) \\
+      g(\xx)
+    \end{pmatrix} &= 
+    \int_\Gamma
+    \begin{pmatrix}
+      K_{11}^F(\xx,\yy) & K_{12}^F(\xx,\yy) \\
+      K_{21}^F(\xx,\yy) & K_{22}^F(\xx,\yy)
+    \end{pmatrix}
+    \begin{pmatrix}
+      \sigma_1(\yy)\\
+      \sigma_2(\yy)
+    \end{pmatrix}
+    \, dS(\yy) \\
+    &\quad + \begin{pmatrix}
+      1/2 & 0 \\
+      -\kappa(\xx) & 1/2
+    \end{pmatrix}
+    \begin{pmatrix}
+      \sigma_1(\xx)\\
+      \sigma_2(\xx)
+    \end{pmatrix} \; , \label{eq:farkIntEq} 
+  \end{split}
+\end{equation}
+where $\kappa$ is the signed curvature at $\xx \in \Gamma$.
+The kernels are given
+by $K_{11}^F = K_1^F$, $K_{12}^F = K_2^F$,
+\begin{align}
+  K_{21}^F(\xx,\yy) &= \left(K_1^F(\xx,\yy)\right )_{n_x} \nonumber \\
+  &= \bn(\xx) \cdot \nabla_{\xx} K_{21}^{F}(\xx,\yy) \; \label{eq:farkK21},\\
+  K_{22}^F(\xx,\yy) &= \left(K_2^F(\xx,\yy)\right )_{n_x} \nonumber \\
+  &= \bn(\xx) \cdot \nabla_{\xx} K_{22}^{F}(\xx,\yy) \label{eq:farkK22} \; .
+\end{align}
+
+The following lemma shows that the integral equation~\cref{eq:farkIntEq} is invertible for smooth domains
+whenever $k$ is not a buckling eigenfrequency.
+
+\begin{lem}
+Suppose that $\Omega \subset \R^2$ is a simply connected region whose boundary $\Gamma$ is $\cC^{2}$. 
+Furthermore, suppose that $k$ is not a buckling eigenfrequency of $\Omega$, i.e., the only solution $w$ to~\cref{eq:buck1,eq:buck2,eq:buck3} is  $w \equiv 0$.
+Suppose further that $f,g \in \cC^{2}(\Gamma)$.
+Then there exists a unique solution $\sigma_{1},\sigma_{2} \in \cC^{2}$ which satisfies~\cref{eq:farkIntEq}. 
+Furthermore, $w(\bx)$ defined via~\cref{eq:farkRep} satisfies the Helmholtz-Biharmonic equation~\cref{eq:helmbi}
+along with the boundary conditions $w(\bx)=f(\bx)$ and $\dwdn(\bx) = g(\bx)$ for $\bx \in\Gamma$. 
+\end{lem}
+
+\begin{proof}
+The proof is a minor modification of the one presented in~\ref{eq:shidongmodbi} and is contained in~\cref{sec:app}.
+\end{proof}
+
+The kernels $K^F_1$ and $K^F_2$ are
+constructed with the goal that the $K^F_{ij}$ are
+as smooth as possible. Suppose that the boundary
+$\Gamma$ is of class $C^k$. Then, the kernels,
+$K^F_{ij}(\xx,\yy)$, are $C^{k-2}$ functions on the boundary
+for each $\yy \in \Gamma$.
+Therefore, on a smooth
+boundary, these kernels are smooth. However, on a
+domain with a corner, we note 
+that the kernel $K_{21}^F$
+has a singularity with strength $r^{-2}$ (see~\cref{fig:ker21plot}). 
+This singularity, in addition to the term in \cref{eq:farkIntEq}
+which explicitly involves the
+curvature, makes the representation \cref{eq:farkRep}
+unstable for domains with high curvature (or
+corners).
+
+\subsection{Helmholtz-Stokes flow in a plane}
 
@@
 the solution is given as the sum of two layer potentials, i.e.
-\begin{equation}
-  w(\xx) = \int_\Gamma K_1^F (\xx,\yy) \sigma_1(\yy) \, dS(\yy)
-  + \int_\Gamma K_2^F(\xx,\yy) \sigma_2(\yy) \, dS(\yy) \; ,
-  \label{eq:farkRep}
-\end{equation}
 where $\sigma_1$ and $\sigma_2$ are unknown densities.
@@
 derivatives of the Green's function for the biharmonic equation.
-For two points on the plane, $\xx$ and $\yy$, let $\br = \yy - \xx$. Then 
-\begin{align}
-  K_1^F(\xx,\yy) &= \partial_{n_{y}n_{y}n_{y}}\Gbh(\xx,\yy)
-  + 3 \partial_{n_{y}\tau_{y}\tau_{y}}\Gbh(\xx,\yy) + k^{2} \partial_{n_{y}}\Gbh(\xx,\yy)\; , \label{eq:kf1} \\
-  K_2^F(\xx,\yy) &= -\partial_{n_{y}n_{y}}\Gbh(\xx,\yy)
-  + \partial_{\tau_{y}\tau_{y}}\Gbh(\xx,\yy) \label{eq:kf2} \; .
-\end{align}
-More explicitly, we have
-
-\begin{align}
-  K_1^F(\xx,\yy) &=  -\dfrac{\br \cdot \bn(\yy)}{|\br|^2}  \cdot \left( \frac{3 i}{2} H_0^{(1)}(k|\br|) - \frac{5 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{6}{\pi k^2 |\br|^2} + \frac{1}{2\pi}  \right) +     \\
-  & \quad \dfrac{\left(\br \cdot \bn(\yy)\right)^3}{|\br|^4} \cdot \left( 2i H_0^{(1)}(k|\br|) - \frac{7 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{8}{\pi k^2 |\br|^2}  \right) \, , \nonumber \\
-  K_2^F(\xx,\yy) &=  -\left(\frac{1}{2}-\dfrac{\left(\br \cdot \bn(\yy)\right)^2}{|\br|^2} \right)  \cdot \left( \frac{i}{2} H_0^{(1)}(k|\br|) - \frac{i}{k|\br|} H_1^{(1)}(k|\br|) + \frac{2}{\pi k^2 |\br|^2}  \right)\; .
-\end{align}
-
-On enforcing the Dirichlet boundary conditions for
-$w$, we obtain the integral equation
-\begin{equation}
-  \begin{split}
-    \begin{pmatrix}
-      f(\xx) \\
-      g(\xx)
-    \end{pmatrix} &= 
-    \int_\Gamma
-    \begin{pmatrix}
-      K_{11}^F(\xx,\yy) & K_{12}^F(\xx,\yy) \\
-      K_{21}^F(\xx,\yy) & K_{22}^F(\xx,\yy)
-    \end{pmatrix}
-    \begin{pmatrix}
-      \sigma_1(\yy)\\
-      \sigma_2(\yy)
-    \end{pmatrix}
-    \, dS(\yy) \\
-    &\quad + \begin{pmatrix}
-      1/2 & 0 \\
-      -\kappa(\xx) & 1/2
-    \end{pmatrix}
-    \begin{pmatrix}
-      \sigma_1(\xx)\\
-      \sigma_2(\xx)
-    \end{pmatrix} \; , \label{eq:farkIntEq} 
-  \end{split}
-\end{equation}
-where $\kappa$ denotes the signed curvature as
-a function on $\Gamma$ and $\xx$ is a point on $\Gamma$. 
-The kernels are given
-by $K_{11}^F = K_1^F$, $K_{12}^F = K_2^F$,
-\begin{align}
-  K_{21}^F(\xx,\yy) &= \left(K_1^F(\xx,\yy)\right )_{n_x} \nonumber \\
-  &= \bn(\xx) \cdot \nabla_{\xx} K_{21}^{F}(\xx,\yy) \; \label{eq:farkK21},\\
-  K_{22}^F(\xx,\yy) &= \left(K_2^F(\xx,\yy)\right )_{n_x} \nonumber \\
-  &= \bn(\xx) \cdot \nabla_{\xx} K_{22}^{F}(\xx,\yy) \label{eq:farkK22} \; .
-\end{align}
-For a sufficiently smooth and simply connected domain,
-the integral equation \cref{eq:farkIntEq} is invertible.
-The case of a multiply connected domain is not treated
-fully in \cite{Farkas89}, but some of the issues are
-considered.
-
-As mentioned above, the kernels $K^F_1$ and $K^F_2$ are
-constructed with the goal that the $K^F_{ij}$ are
-as smooth as possible. Suppose that the boundary
-$\Gamma$ is of class $C^k$. Then, the kernels,
-$K^F_{ij}(\xx,\yy)$, are $C^{k-2}$ functions on the boundary
-for each $\yy \in \Gamma$.
-Therefore, on a smooth
-boundary, these kernels are smooth. However, on a
-domain with a corner, we note 
-that the kernel $K_{21}^F$
-has a singularity with strength $r^{-2}$ (see~\cref{fig:ker21plot}). 
-This singularity, in addition to the term in \cref{eq:farkIntEq}
-which explicitly involves the
-curvature, makes the representation \cref{eq:farkRep}
-unstable for domains with high curvature (or
-corners).
 

### 2018-06-22 doc/draft-01/01intro.tex
reorganize paper

--- 2018-04-24 doc/draft-01/biharm-evals.tex
@@
-\documentclass[preprint,12pt]{article} 
-\usepackage{b}
-\usepackage[a4paper]{geometry}
-\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}
-\usepackage[small,it]{caption}
-\usepackage{empheq}
-
-\usepackage{subcaption}
-
-\usepackage{cleveref}
-\crefname{equation}{}{}
-\Crefname{equation}{}{}
-\crefname{eqnarray}{}{}
-\Crefname{eqnarray}{}{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\def\br{{\boldsymbol r}}
-\def\bn{{\boldsymbol n}}
-\def\xx{{\boldsymbol x}}
-\def\bx{{\boldsymbol x}}
-\def\yy{{\boldsymbol y}}
-\def\by{{\boldsymbol y}}
-\def\ss{{\boldsymbol s}}
-\def\tt{{\boldsymbol t}}
-\def\uu{{\boldsymbol u}}
-\def\bu{{\boldsymbol u}}
-\def\bl{{\boldsymbol \ell}}
-\def\ff{{\boldsymbol f}}
-\def\GG{{\bf G}}
-\def\Gbh{{G_{BH}}}
-\def\II{{\bf I}}
-\def\TT{{\bf T}}
-\def\bsigma{{\boldsymbol \sigma}}
-\def\bnu{{\boldsymbol \nu}}
-\def\btau{{\boldsymbol \tau}}
-\def\bigo{\mathcal{O}}
-\def\littleo{o}
-
-\newtheorem{remark}{Remark}
-\newtheorem{proposition}{Proposition}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\title{An integral equation method for the biharmonic
-Dirichlet eigenvalue problem in two dimensions}
-\author{Askham and Rachh}
-\date{\today}
-
-\begin{document}
-
-\maketitle
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Introduction}
@@
 \end{itemize}
-\section{Mathematical Preliminaries}
 
-\subsection{Notation}
-
-Bold symbols are vectors or tensors.
-$\xx = (x_1,x_2)^\intercal$ then $\xx^\bot = (-x_2,x_1)^\intercal$.
-Similarly, $\nabla^\bot = (-\partial_{x_2},\partial_{x_1})^\intercal$
-
-\subsection{Green's functions}
-
-$\Delta$
-\begin{equation}
-  G_L(\xx,\yy) = -\frac{1}{2\pi} \log |\xx-\yy|
-\end{equation}
-
-$\Delta + k^2$
-\begin{equation}
-  G_H(\xx,\yy) = \frac{i}{4} H_0^{(1)}(k|\xx-\yy|)
-\end{equation}
-
-$\Delta(\Delta + k^2)$
-\begin{equation}
-  G_{BH}(\xx,\yy) = -\frac{1}{k^2}
-  \left (\frac{1}{2\pi} \log |\xx-\yy| +
-  \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \right )
-\end{equation}
-
-\section{Integral Equation Formulation}
-
-\subsection{The Helmholtz Stokeslet formulation}
-
-In this section, we review the derivation of the
-modified Stokeslet, but for the imaginary parameter
-regime --- which we will call the Helmholtz Stokeslet ---
-which is the appropriate setting for the Stokes
-eigenvalue problem.
-The original modified Stokeslet is more well known,
-and is of particular interest for its application to
-numerical simulations of the unsteady Stokes equations
-\cite{pozrikidis1992boundary,biros2002embedded}.
-
-To begin, we restate the Stokes eigenvalue
-problem as
-\begin{align}
-  \nabla p - \Delta \uu - k^2 \uu &= 0 \; , \label{eq:helmstokes}\\
-  \nabla \cdot \uu &= 0 \; . \label{eq:helmstokescty}
-\end{align}
-Consider the solution of this problem where a
-$\delta$ centered at $\yy$ with strength $\ff$
-has been added to the right-hand side, i.e.
+Consider the pure bending of an isotropic and homogeneous thin clamped
+plate. 
+Let $\Omega$ denote the midline of the thin plate, $\Gamma$ denote the 
+boundary of $\Omega$ and $w$ denote the vertical displacement.
+The buckling problem consists of finding 
+values $k^{2}$ such that the boundary value problem
 
 \begin{align}
-  \nabla p - \Delta \uu - k^2 \uu &= \delta_\yy \ff \; ,
-  \label{eq:helmstokes_charge} \\
-  \nabla \cdot \uu &= 0 \; .
+\Delta (\Delta + k^2) w &= 0 \quad \text{in} \quad \Omega \label{eq:buck1} \\
+w &= 0 \quad \text{on} \quad \Gamma \label{eq:buck2}\\
+\dwdn &=0 \quad \text{on} \quad \Gamma \label{eq:buck3} \,.
 \end{align}
-Note that
-
-\begin{equation}
-  \Delta G_L(\xx,\yy) = \delta_\yy(\xx) \; .
-\end{equation}
-If we substitute this expression into
-\eqref{eq:helmstokes_charge} and take the divergence,
-we obtain
-
-\begin{equation}
-  p = \nabla G_L(\xx,\yy) \cdot \ff \; .
-\end{equation}
-We then have, formally,
-
-\begin{align}
-  \uu &= - (\Delta + k^2)^{-1} ( \Delta G_L \ff
-  - \nabla (\nabla G_L \cdot \ff ) ) \\
-  &= \left ( -\Delta + \nabla \otimes \nabla \right )
-  G_{BH} \ff \; .
-\end{align}
-The tensor
-
-\begin{equation}
-  \GG = - \II \Delta G_{BH} + \nabla \otimes \nabla G_{BH}
-\end{equation}
-is then the equivalent of a Stokeslet
-\cite{pozrikidis1992boundary} for the problem
-\eqref{eq:helmstokes}.
-
-A related object is the stresslet, which is defined
-in terms of the stress tensor of a velocity, pressure
-pair induced by a Stokeslet. For these tensors, we find
-that it is more convenient to express them in index notation
-with the Einstein index summing convention.
-Recall that the stress tensor $\bsigma$ is defined as
-
-\begin{equation}
-  \sigma_{ij} = -p \delta_{ij} + \left ( \partial_{x_j}u_i
-  +\partial_{x_i} u_j \right ) \; ,
-\end{equation}
-where $\delta_{ij}$ is the standard Kronecker delta notation.
-The stresslet $\TT$ is defined to be
-
-\begin{align}
-  T_{ijk} &= - \partial_{x_j} G_L \delta_{ik}
-  + \partial_{x_k} \left ( -\Delta G_{BH} \delta_{ij} +
-  \partial_{x_i} \left(\partial_{x_j} G_{BH} \right) \right)
-  \nonumber \\
-  & \qquad+ \partial_{x_i} \left ( -\Delta G_{BH} \delta_{kj} +
-  \partial_{x_k} \left(\partial_{x_j} G_{BH} \right) \right)
-  \; .
-\end{align}
-Let $u_i = G_{ij} f_j$ and $p = \partial_{x_i} G_L f_i$ be a
-solution of the Stokes equations induced by a Stokeslet.
-Then the corresponding stress tensor is given by
-$\sigma_{ik} = T_{ijk} f_j$.
-
-For the layer potentials of the next section, the following
-formulas are useful. Let $\bnu$ be a given vector. When
-summing over the third index, we obtain
-
-\begin{equation}
-  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla G_L
-  + \partial_\nu \left ( -\Delta G_{BH} \II
-  + \nabla \otimes \nabla G_{BH} \right)
-  + \nabla \otimes \left ( -\Delta G_{BH} \bnu
-  + \partial_{\nu} \nabla G_{BH} \right) \; .
-\end{equation}
-%\begin{align}
-% -\Delta G_{BH} \bnu
-% + \partial_{\nu} \nabla G_{BH} &=
-% ( (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_1 G_{BH} +
-% (\partial_{x_1x_1}\nu_1 + \partial_{x_2x_1} \nu_2 )G_{BH},
-% (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_2 G_{BH} +
-% (\partial_{x_1x_2}\nu_1 + \partial_{x_2x_2} \nu_2 )G_{BH}) \\
-% &= (-\partial_{x_2} \partial_\tau G_{BH},
-% \partial_{x_1} \partial_\tau G_{BH})
-%\end{align}
-%\begin{equation}
-%  \begin{pmatrix}
-%    -\partial_{x_2x_2} & \partial_{x_1x_2} \\
-%    \partial_{x_1x_2} & -\partial_{x_1x_1}
-%  \end{pmatrix} = -\nabla^\bot \otimes \nabla^\bot
-%\end{equation}
-Let $\btau = \bnu^\bot$. Then
-
-\begin{equation}
-  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla G_L
-  - \nabla^\bot \otimes \nabla^\bot \partial_\nu G_{BH}
-  +\nabla \otimes \nabla^\bot \partial_\tau G_{BH} \; .
-\end{equation}
-
-\subsection{Layer potentials}
-
-\subsection{The Farkas integral representation}
-
-As mentioned in the introduction, there are existing 
-integral representations for the solution of the Dirichlet problem for the Helmholtz-biharmonic equation
-\begin{align}
- \Delta (\Delta + k^2) w &= 0 \mbox{ in } D \; , \label{eq:biharmD1}\\
- w &= f \mbox{ on }
- \Gamma \label{eq:biharmD2} \; , \\ 
- \frac{\partial w}{\partial n} &= g \mbox{ on } 
- \Gamma \, , \label{eq:biharmD3}
-\end{align}
-In \cite{Farkas89}, 
-the solution is given as the sum of two layer potentials, i.e.
-\begin{equation}
-  w(\xx) = \int_\Gamma K_1^F (\xx,\yy) \sigma_1(\yy) \, dS(\yy)
-  + \int_\Gamma K_2^F(\xx,\yy) \sigma_2(\yy) \, dS(\yy) \; ,
-  \label{eq:farkRep}
-\end{equation}
-where $\sigma_1$ and $\sigma_2$ are unknown densities.
-
-The integral kernels, $K_1^F$ and $K_2^F$ are based on
-derivatives of the Green's function for the biharmonic equation.
-For two points on the plane, $\xx$ and $\yy$, let $\br = \yy - \xx$. Then 
-\begin{align}
-  K_1^F(\xx,\yy) &= \partial_{n_{y}n_{y}n_{y}}\Gbh(\xx,\yy)
-  + 3 \partial_{n_{y}\tau_{y}\tau_{y}}\Gbh(\xx,\yy) + k^{2} \partial_{n_{y}}\Gbh(\xx,\yy)\; , \label{eq:kf1} \\
-  K_2^F(\xx,\yy) &= -\partial_{n_{y}n_{y}}\Gbh(\xx,\yy)
-  + \partial_{\tau_{y}\tau_{y}}\Gbh(\xx,\yy) \label{eq:kf2} \; .
-\end{align}
-More explicitly, we have
-
-\begin{align}
-  K_1^F(\xx,\yy) &=  -\dfrac{\br \cdot \bn(\yy)}{|\br|^2}  \cdot \left( \frac{3 i}{2} H_0^{(1)}(k|\br|) - \frac{5 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{6}{\pi k^2 |\br|^2} + \frac{1}{2\pi}  \right) +     \\
-  & \quad \dfrac{\left(\br \cdot \bn(\yy)\right)^3}{|\br|^4} \cdot \left( 2i H_0^{(1)}(k|\br|) - \frac{7 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{8}{\pi k^2 |\br|^2}  \right) \, , \nonumber \\
-  K_2^F(\xx,\yy) &=  -\left(\frac{1}{2}-\dfrac{\left(\br \cdot \bn(\yy)\right)^2}{|\br|^2} \right)  \cdot \left( \frac{i}{2} H_0^{(1)}(k|\br|) - \frac{i}{k|\br|} H_1^{(1)}(k|\br|) + \frac{2}{\pi k^2 |\br|^2}  \right)\; .
-\end{align}
-
-On enforcing the Dirichlet boundary conditions for
-$w$, we obtain the integral equation
-\begin{equation}
-  \begin{split}
-    \begin{pmatrix}
-      f(\xx) \\
-      g(\xx)
-    \end{pmatrix} &= 
-    \int_\Gamma
-    \begin{pmatrix}
-      K_{11}^F(\xx,\yy) & K_{12}^F(\xx,\yy) \\
-      K_{21}^F(\xx,\yy) & K_{22}^F(\xx,\yy)
-    \end{pmatrix}
-    \begin{pmatrix}
-      \sigma_1(\yy)\\
-      \sigma_2(\yy)
-    \end{pmatrix}
-    \, dS(\yy) \\
-    &\quad + \begin{pmatrix}
-      1/2 & 0 \\
-      -\kappa(\xx) & 1/2
-    \end{pmatrix}
-    \begin{pmatrix}
-      \sigma_1(\xx)\\
-      \sigma_2(\xx)
-    \end{pmatrix} \; , \label{eq:farkIntEq} 
-  \end{split}
-\end{equation}
-where $\kappa$ denotes the signed curvature as
-a function on $\Gamma$ and $\xx$ is a point on $\Gamma$. 
-The kernels are given
-by $K_{11}^F = K_1^F$, $K_{12}^F = K_2^F$,
-\begin{align}
-  K_{21}^F(\xx,\yy) &= \left(K_1^F(\xx,\yy)\right )_{n_x} \nonumber \\
-  &= \bn(\xx) \cdot \nabla_{\xx} K_{21}^{F}(\xx,\yy) \; \label{eq:farkK21},\\
-  K_{22}^F(\xx,\yy) &= \left(K_2^F(\xx,\yy)\right )_{n_x} \nonumber \\
-  &= \bn(\xx) \cdot \nabla_{\xx} K_{22}^{F}(\xx,\yy) \label{eq:farkK22} \; .
-\end{align}
-For a sufficiently smooth and simply connected domain,
-the integral equation \cref{eq:farkIntEq} is invertible.
-The case of a multiply connected domain is not treated
-fully in \cite{Farkas89}, but some of the issues are
-considered.
-
-As mentioned above, the kernels $K^F_1$ and $K^F_2$ are
-constructed with the goal that the $K^F_{ij}$ are
-as smooth as possible. Suppose that the boundary
-$\Gamma$ is of class $C^k$. Then, the kernels,
-$K^F_{ij}(\xx,\yy)$, are $C^{k-2}$ functions on the boundary
-for each $\yy \in \Gamma$.
-Therefore, on a smooth
-boundary, these kernels are smooth. However, on a
-domain with a corner, we note 
-that the kernel $K_{21}^F$
-has a singularity with strength $r^{-2}$ (see~\cref{fig:ker21plot}). 
-This singularity, in addition to the term in \cref{eq:farkIntEq}
-which explicitly involves the
-curvature, makes the representation \cref{eq:farkRep}
-unstable for domains with high curvature (or
-corners).
-
-\section{Integral equation derivation} \label{sec:anapp}
-
-%\subsection{Adapting the completed double layer representation
-%to solve the Dirichlet problem}
-We would like to adapt the completed double layer representation
-for solutions of Stokes flow \cref{eq:biharmV1,eq:biharmV2,eq:biharmV3} to solve 
-the clamped plate problem \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}.
-Let $f$ and $g$ be the boundary data as in \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}. 
-By computing tangential derivatives of $f$ on each
-boundary component, we get the following related Helmholtz-Stokes problem:
-\begin{align}
- \Delta (\Delta + \lambda^2) \tilde{w}  = 0 &\quad \bx \in D \, ,\nonumber\\
- \frac{\partial \tilde{w}}{\partial \tau} = 
- \frac{\partial f}{\partial \tau} 
-&\quad \bx \in \Gamma \label{eq:biharm5} \, ,\\ 
- \frac{\partial \tilde{w}}{\partial n} = g &\quad \bx 
-\in \Gamma 
-\, . 
-\nonumber
-\end{align}
-There are two main issues to be addressed in using the completed
-double layer representation in this context. First,
-the representation is designed for 
-Helmholtz-Stokes flow, in which the quantities of interest are derivatives
-of the potential $\tilde{w}$ and not $\tilde{w}$ itself; the
-representation for $\tilde{w}$ may not be single-valued. 
-We will establish that, in the context of \cref{eq:biharm5},
-the stream function is necessarily single-valued. We also discuss
-some numerical issues related to evaluating the stream function.
-The second issue to address
-is that the solution $\tilde{w}$ only satisfies the original boundary 
-condition for the value of $\tilde{w}$ up to a constant on 
-each boundary component.
-In fact, for multiply connected domains, the completed double layer 
-representation is incomplete for the Dirichlet
-problem \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}. We present a remedy for this 
-issue and provide some physical intuition.
-%
-%\subsection{Single-valued stream functions}
-%To solve the Dirichlet problem \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3},
-%it is necessary to compute
-%a single-valued biharmonic potential.
-%In the case of a multiply connected domain,
-%there is no guarantee that a single-valued stream 
-%function exists for a given velocity field.
-%
-%Consider the following example.
-%Let $(r,\theta)$ denote standard polar coordinates. It is
-%easy to verify that the velocity field 
-%$\bu=\frac{1}{r}\hat{r}$ 
-%solves the equations of Stokes flow in an annulus centered at the 
-%origin. A stream function for this flow is $w=\theta$, which 
-%is not single-valued; indeed, there are no single-valued
-%stream functions which generate this flow. 
-%
-%Let $D$ be a multiply connected domain with boundary 
-%$\Gamma = \cup_{i=0}^N \Gamma_i$, as in the previous section.
-%We note that the gradient of a stream function is determined 
-%by the velocity field, i.e. 
-%
-%\begin{equation}
-%\nabla w = -\bu^\perp := \begin{pmatrix} 
-%  - u_2 \\ u_1 
-%\end{pmatrix} \; .
-%\end{equation}
-%Therefore, a velocity field has single-valued stream
-%functions if and only if $\bu^\perp$ is conservative.
-%Using standard results from multivariable calculus, 
-%we can  characterize such flows.
-%
-%\begin{proposition} 
-%Suppose that $\bu$ is a divergence-free velocity 
-%field which is $C^1$ on $D$ and continuous on 
-%$D\cup \Gamma$. The field $\bu^\perp$ 
-%is conservative if and only if 
-%
-%\begin{equation}
-% \int_{\Gamma_i} \bu\cdot \bn \, dS 
-%= 0 \quad i=0,1,\ldots N \, .
-%\label{eq:NecSuffStreamFuncExistence}
-%\end{equation}
-%
-%\end{proposition}
-%
-%The equalities \cref{eq:NecSuffStreamFuncExistence}
-%constitute $N$ linearly independent constraints on the 
-%boundary data because the divergence-free condition 
-%\cref{eq:MassConservation} implies that
-%$\int_{\Gamma} \bu \cdot \bn \, dS = 0$. 
-%It turns out that 
-%these conditions are satisfied when the Dirichlet 
-%problem is recast as a Stokes flow \cref{eq:biharm5}, as 
-%it is easily verified that
-%\begin{equation}
-% \int_{\Gamma_i} \bu\cdot \bn \, dS 
-%= \int_{\Gamma_i} \frac{\partial f}{\partial \tau} \, dS =0 \, .
-%\end{equation}
-%Thus, any stream function $\tilde{w}$ obtained for the Stokes
-%flow \cref{eq:biharm5} is necessarily single-valued.
-%% NOT GOING THIS WAY ANYMORE
-%%It can be shown using the Helmholtz Hodge decomposition that the 
-%%conditions \cref{eq:NecSuffStreamFuncExistence} are sufficient for 
-%%the existence of a single-valued stream function. 
-%
-%\subsection{Evaluating the stream function} \label{subsec:stream}
-%
-%Given compatible boundary data for the velocity field $\bu$, 
-%the completed double layer representation for Stokes flow 
-%\cref{eq:IntRepStokes} guarantees the existence of
-%a solution density $\boldsymbol\mu$ 
-%and a corresponding stream function $\tilde{w}$. The Goursat 
-%function formula 
-%for $\tilde{w}$, see \cref{sec:stokeslayer},
-%is necessarily single-valued, as explained above,
-%but it is not immediately obvious from the formula 
-%that this should be true.
-%
-%The difficulty in the representation of $\tilde{w}$ 
-%comes from the part
-%of the stream function corresponding to the double layer potential
-% \cref{eq:wDL}. The 
-%second term in the expression for the double layer potential is
-%\begin{equation}
-% v_1(z) = \mbox{Re}\left[\frac{1}{4\pi i}\int_{\Gamma}\left(
-%\overline{\rho\left(\xi\right)}d\xi+\rho\left(\xi\right)
-%\overline{d\xi}\right)\log\left(\xi-z\right)\right] \, .
-%\end{equation}
-%To compute this term, in a na\"{i}ve numerical implementation,
-%the question of which is the appropriate branch of the 
-%logarithm to use would arise at many steps.
-%To avoid this complication, it is possible instead to compute
-%$v_1$, up to a constant, as the harmonic conjugate of the
-%function 
-%\begin{equation}
-% v_2 = \frac{1}{4\pi}\int_{\Gamma}\left(\overline{\rho\left(\xi\right)}
-%d\xi+\rho\left(\xi\right)\overline{d\xi}\right)\log
-%\left(\left|\xi-z\right|\right) \, . \label{eq:harmconjg}
-%\end{equation}
-%
-%We will use this approach to evalute $v_1$ numerically.
-%As a result of the Cauchy-Riemann equations, the 
-%harmonic conjugate of $v_2$, satisfies the following
-%Neumann problem for the Laplace equation:
-%\begin{align}
-% \Delta v_1 &= 0 &\quad x\in D \, ,\\
-% \frac{\partial v_1}{\partial n} &= -\frac{\partial v_2}{\partial \tau} 
-%&\quad x\in\Gamma \, .
-%\end{align}
-%It is possible then to use standard integral equation
-%methods to compute $v_1$. 
-%
-%Let $v_1 = S^L_\Gamma \sigma$, where $S^L_\Gamma \sigma$ 
-%is the single layer potential for Laplace's equation, given by
-%\begin{equation}
-%S^L_\Gamma\sigma (\bx) = -\frac{1}{2\pi} \int_{\Gamma} \log 
-%\left|\bx - \by \right|\sigma(\by)\, dS \left(\by \right) \, ,
-%\end{equation}
-%where $\sigma\in \mathcal{X}= C^{0,\alpha}\left(\Gamma\right)$, for 
-%some $\alpha \in (0,1)$, is an unknown density 
-%(see \cite{kress1999linear, guenther1988partial}).
-%Imposing the Neumann boundary conditions results in the 
-%following boundary integral equation for $\sigma$:
-%\begin{align}
-%-\frac{\partial v_2}{\partial \tau} (\bx) &= \frac{1}{2} \sigma \left(\bx\right) - \frac{1}{2\pi}\oint_{\Gamma} 
-%\frac{\partial}{\partial n_x}  
-%\log \left| \bx - \by \right |\sigma(\by)\, dS \left(\by \right) 
-%\, , \\
-%-\frac{\partial v_2}{\partial \tau} &= \left( \frac{1}{2}I_{\mathcal{X}} + K^L_\Gamma  \right) \sigma 
-%\, ,
-%\label{eq:BlockSystemRow2P1tmp}
-%\end{align}
-%where the operator $K^L_\Gamma$ is compact, so that the integral equation
-%is second kind.
-%For a derivation of this result, see \cite{kress1999linear}.
-%
-%It is well known that the operator $\frac{1}{2}I_{\mathcal{X}} + K^L_\Gamma$ 
-%has a one dimensional null space. Thus,
-%we choose to solve the above integral equation subject to 
-%the constraint $\int_{\Gamma} \sigma \, dS = 0$. 
-%Furthermore, it is known that solving the Neumann problem subject 
-%to the above constraint is equivalent
-%to solving
-%\begin{align}
-%\left( \frac{1}{2}I_{\mathcal{X}} + K^L_\Gamma  + W_\Gamma \right) \sigma 
-%= -\frac{\partial v_2}{\partial \tau}
-%\label{eq:BlockSystemRow2P1} 
-%\end{align}
-%where $W_\Gamma\sigma = \int_{\Gamma} \sigma \, dS$. 
-%To prove this, we need 
-%the following property of 
-%the Green's function for Laplace's equation.
-%\begin{align}
-%-\frac{1}{2\pi}\oint_{\gamma} \frac{\partial}{\partial n_{\by}}  
-%\log \left|\bx - \by\right|\, dS \left(\by \right) 
-%&=-\frac{1}{2}\quad\bx\in\gamma \, , \label{eq:DLP2}
-%\end{align}
-%Using the above property, it follows that
-%\begin{align}
-% \int_{\Gamma} K^L_\Gamma \sigma \, dS(\x) 
-%= -\frac{1}{2}\int_{\Gamma} \sigma \left(\bx\right) \, dS(\x) 
-%\label{eq:KLint}
-%\end{align}
-%Integrating equation \cref{eq:BlockSystemRow2P1} and using 
-%equation \cref{eq:KLint}, we get
-%\begin{align}
-%\int_{\Gamma} \left( \frac{1}{2}I_{\mathcal{X}} + 
-%K^L_\Gamma  + L \right) \sigma \, dS(\x) 
-%&= -\int_{\Gamma} \frac{\partial v_2}{\partial \tau} \, dS(\x) \\
-%\left|\Gamma\right| L\sigma  &= 0 
-%\end{align}
-%which proves the result.
-
-\subsection{Making the representation complete}
-As mentioned above, the solution $\tilde{w}$ of 
-the auxiliary Helmholtz-Stokes problem \cref{eq:biharm5}
-only satisfies the boundary conditions of the 
-original Dirichlet problem \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}
-up to a constant on each boundary component. For a simply
-connected domain, this constant can be recovered from the
-fact that adding an arbitrary constant to a stream function
-does not change the velocity field. 
-Thus, in simply connected domains, there is an equivalence in the 
-solutions of \cref{eq:biharm5} and \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}.
-
-To analyze the case of a multiply connected domain,
-we first consider
-radially symmetric solutions on an annulus centered at the
-origin. Let $w\left(r\right)$ be a 
-radially symmetric biharmonic-Stokes
-potential. Then $w(r)$ solves the ordinary differential
-equation (ODE)
-\begin{equation}
-\Delta_{r} (\Delta_{r} + k^2)w = 0 \, ,
-\end{equation}
-where $\Delta_{r}$ is the radial component of the Laplacian in polar
-coordinates given by
-$$
-\Delta_{r} = \frac{1}{r}\frac{d}{dr} r \frac{d}{dr} \, .
-$$
-Four linearly independent solutions of this ODE are $1$, $\log{(r)}$, 
-$J_{0}(kr)$, and $H_{0}(kr)$, 
-where $J_{0}$ is the order zero Bessel function of the first kind, and $H_{0}$ is the order zero Hankel function of the first kind.
-For each solution, we can compute the associated velocity field 
-$\bu = \nabla^{\perp} w$. By construction, $\bu$ satisfies 
-the continuity condition \cref{eq:MassConservation}. 
-For the momentum equation \cref{eq:StokesFlowEq} to be 
-satisfied, we need that $\Delta\bu + k^2 \bu$ is a conservative
-vector field, which 
-is equivalent to the condition that 
-$\int_{\gamma} (\Delta\bu + k^2 \bu) \cdot d\bl = 0$ 
-for any closed 
-loop $\gamma$ in the annulus. For $\tilde{w}=1$, $J_{0}(kr)$, and $H_{0}(kr)$,
-the corresponding velocity field satisfies
-$\Delta \bu + k^2 \bu=0$ so that $\Delta \bu$
-is trivially a conservative vector field. 
-On the other hand, for $\tilde{w}=\log{(r)}$, the corresponding velocity field
-satisfies $\Delta \bu + k^2 \bu=\frac{k^2}{r} \hat{\theta}$.
-By considering a curve $\gamma$ encircling the origin,
-we see that $\Delta \bu + k^2 \bu$ is not a conservative vector
-field and that any pressure for the velocity field 
-associated with $\log\left(r\right)$ is not single-valued.
-%
-%The above analysis
-%can be extended to show that any solution of the biharmonic equation 
-%of the form $\log{|r-r_{j}|}$ where $r_{j}$ is located in one of the holes of a multiply connected
-%domain.
-%cannot be represented as a Stokes velocity field. 
-%In simply connected 
-%domains, since there are no holes, corresponding to each solution of the modified biharmonic equation with clamped plate
-%boundary conditions, there exists a solution to . For multiply connected domains with genus $N$, 
-%the set of stream functions for Stokes velocity fields
-%misses an $N$ dimensional space of solutions, corresponding 
-%to biharmonic charges located in the holes of the domain.
-%Following this reasoning, we obtain a complete representation
-%for biharmonic potentials on multiply connected domains
-%by adding $N$ charges, one per each hole of the domain,
-%to the representation for $w$. The details of this approach, and
-%the proof that it is sufficient, is in the next section.
-
-\bibliographystyle{plain}
-\bibliography{refs}
-
-\end{document}
+has a non-trivial solution. In a slight abuse of notation,
+these values $k^2$ and the corresponding
+solutions are often referred to as ``eigenvalues'' and ``eigenfunctions'',
+respectively.
+It is well-known from classical potential theory that, 
+for the buckling problem, there exists a countable collection of
+such values $0 < k_{1}^{2} \leq k_{2}^2 \leq \ldots \uparrow \infty$,
+counting multiplicites.
+\begin{remark}
+For notational convenience,  
+we will refer to the modified Biharmonic problem
+with imaginary parameter as the Helmholtz-Biharmonic problem.
+\end{remark}

### 2018-06-22 doc/draft-01/02prelim.tex
reorganize paper

--- 2018-06-14 doc/draft-01/biharm-evals.tex
@@
-\documentclass[preprint,12pt]{article} 
-\usepackage{b}
-\usepackage[a4paper]{geometry}
-\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}
-\usepackage[small,it]{caption}
-\usepackage{empheq}
-
-\usepackage{subcaption}
-
-\usepackage{cleveref}
-\crefname{equation}{}{}
-\Crefname{equation}{}{}
-\crefname{eqnarray}{}{}
-\Crefname{eqnarray}{}{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\def\br{{\boldsymbol r}}
-\def\bh{{\boldsymbol h}}
-\def\bn{{\boldsymbol n}}
-\def\bT{{\boldsymbol T}}
-\def\xx{{\boldsymbol x}}
-\def\bx{{\boldsymbol x}}
-\def\yy{{\boldsymbol y}}
-\def\by{{\boldsymbol y}}
-\def\ss{{\boldsymbol s}}
-\def\tt{{\boldsymbol t}}
-\def\uu{{\boldsymbol u}}
-\def\bu{{\boldsymbol u}}
-\def\bl{{\boldsymbol \ell}}
-\def\ff{{\boldsymbol f}}
-\def\GG{{\bf G}}
-\def\Gbh{{G_{BH}}}
-\def\II{{\bf I}}
-\def\TT{{\bf T}}
-\def\SS{{\bf S}}
-\def\DD{{\bf D}}
-\def\bsigma{{\boldsymbol \sigma}}
-\def\bmu{{\boldsymbol \mu}}
-\def\bnu{{\boldsymbol \nu}}
-\def\btau{{\boldsymbol \tau}}
-\def\bigo{\mathcal{O}}
-\def\littleo{o}
-\newcommand\dwdn{\frac{\partial w}{\partial n}}
-\newcommand{\cC}{\mathcal C}
-
-\newtheorem{remark}{Remark}
-\newtheorem{proposition}{Proposition}
-\newtheorem{lem}{Lemma}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\title{A Fredholm operator approach to the plate
-buckling eigenvalue problem}
-\author{Askham and Rachh}
-\date{\today}
-
-\begin{document}
-
-\maketitle
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-
-Results of some quick googling:
-
-Finite element methods.
-\begin{itemize}
-\item Stokes eigenvalue problem: nonconforming finite
-  element methods \cite{jia2009approximation}.
-\end{itemize}
-
-Integral equation methods.
-\begin{itemize}
-\item Book on elastodynamic eigenvalue problems
-  \cite{kitahara2014boundary}
-\end{itemize}
-
-Consider the pure bending of an isotropic and homogeneous thin clamped
-plate. 
-Let $\Omega$ denote the midline of the thin plate, $\Gamma$ denote the 
-boundary of $\Omega$ and $w$ denote the vertical displacement.
-In this setup, the buckling eigenvalue problem consists of finding 
-eigenvalues $k^{2}$ and corresponding non-trivial eigenfunctions
-(or buckling modes) $w$ which satisfy the homogeneous Dirichlet
-modified Biharmonic problem (with an imaginary parameter $k$) given by
-\begin{align}
-\Delta (\Delta + k^2) w &= 0 \quad \text{in} \quad \Omega \label{eq:buck1} \\
-w &= 0 \quad \text{on} \quad \Gamma \label{eq:buck2}\\
-\dwdn &=0 \quad \text{on} \quad \Gamma \label{eq:buck3} \,.
-\end{align}
-It is well-known from classical potential theory that, 
-for the buckling eigenvalue problem, there
-exists a countable collection of eigenfrequencies 
-$0 < k_{1}^{2} \leq k_{2}^2 \leq \ldots \uparrow \infty$
-counting multiplicites.
-\begin{remark}
-For notational convenience,  
-we will refer to the modified Biharmonic problem
-with imaginary parameter as the Helmholtz-Biharmonic problem.
-\end{remark}
-
 \section{Mathematical Preliminaries}
@@
 $\sum_{j} a_{j} b_{j}$).
-$\xx = (x_1,x_2)^\intercal$ then $\xx^\bot = (-x_2,x_1)^\intercal$.
+If $\xx = (x_1,x_2)^\intercal$, then $\xx^\bot = (-x_2,x_1)^\intercal$.
 Similarly, $\nabla^\bot = (-\partial_{x_2},\partial_{x_1})^\intercal$.
 
-\subsection{The Farkas integral representation}
-Following the treatment of \cite{askham}, the fundamental solution
-of the Helmholtz-Biharmonic equation is given by
+\subsection{Fundamental solution}
+
+The fundamental solution of the Helmholtz-Biharmonic equation is
+given by 
 \begin{equation}
@@
 and $H_{0}^{1}(r)$ is the Hankel function of the first kind of order zero.
+
+\subsection{A Farkas-style integral representation}
 
@@
 derivatives of the Green's function for the biharmonic equation.
-
-\section{Integral equation derivation} \label{sec:anapp}
-
-%\subsection{Adapting the completed double layer representation
-%to solve the Dirichlet problem}
-We would like to adapt the completed double layer representation
-for solutions of Stokes flow \cref{eq:biharmV1,eq:biharmV2,eq:biharmV3} to solve 
-the clamped plate problem \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}.
-Let $f$ and $g$ be the boundary data as in \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}. 
-By computing tangential derivatives of $f$ on each
-boundary component, we get the following related Helmholtz-Stokes problem:
-\begin{align}
- \Delta (\Delta + \lambda^2) \tilde{w}  = 0 &\quad \bx \in D \, ,\nonumber\\
- \frac{\partial \tilde{w}}{\partial \tau} = 
- \frac{\partial f}{\partial \tau} 
-&\quad \bx \in \Gamma \label{eq:biharm5} \, ,\\ 
- \frac{\partial \tilde{w}}{\partial n} = g &\quad \bx 
-\in \Gamma 
-\, . 
-\nonumber
-\end{align}
-There are two main issues to be addressed in using the completed
-double layer representation in this context. First,
-the representation is designed for 
-Helmholtz-Stokes flow, in which the quantities of interest are derivatives
-of the potential $\tilde{w}$ and not $\tilde{w}$ itself; the
-representation for $\tilde{w}$ may not be single-valued. 
-We will establish that, in the context of \cref{eq:biharm5},
-the stream function is necessarily single-valued. We also discuss
-some numerical issues related to evaluating the stream function.
-The second issue to address
-is that the solution $\tilde{w}$ only satisfies the original boundary 
-condition for the value of $\tilde{w}$ up to a constant on 
-each boundary component.
-In fact, for multiply connected domains, the completed double layer 
-representation is incomplete for the Dirichlet
-problem \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}. We present a remedy for this 
-issue and provide some physical intuition.
-%
-%\subsection{Single-valued stream functions}
-%To solve the Dirichlet problem \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3},
-%it is necessary to compute
-%a single-valued biharmonic potential.
-%In the case of a multiply connected domain,
-%there is no guarantee that a single-valued stream 
-%function exists for a given velocity field.
-%
-%Consider the following example.
-%Let $(r,\theta)$ denote standard polar coordinates. It is
-%easy to verify that the velocity field 
-%$\bu=\frac{1}{r}\hat{r}$ 
-%solves the equations of Stokes flow in an annulus centered at the 
-%origin. A stream function for this flow is $w=\theta$, which 
-%is not single-valued; indeed, there are no single-valued
-%stream functions which generate this flow. 
-%
-%Let $D$ be a multiply connected domain with boundary 
-%$\Gamma = \cup_{i=0}^N \Gamma_i$, as in the previous section.
-%We note that the gradient of a stream function is determined 
-%by the velocity field, i.e. 
-%
-%\begin{equation}
-%\nabla w = -\bu^\perp := \begin{pmatrix} 
-%  - u_2 \\ u_1 
-%\end{pmatrix} \; .
-%\end{equation}
-%Therefore, a velocity field has single-valued stream
-%functions if and only if $\bu^\perp$ is conservative.
-%Using standard results from multivariable calculus, 
-%we can  characterize such flows.
-%
-%\begin{proposition} 
-%Suppose that $\bu$ is a divergence-free velocity 
-%field which is $C^1$ on $D$ and continuous on 
-%$D\cup \Gamma$. The field $\bu^\perp$ 
-%is conservative if and only if 
-%
-%\begin{equation}
-% \int_{\Gamma_i} \bu\cdot \bn \, dS 
-%= 0 \quad i=0,1,\ldots N \, .
-%\label{eq:NecSuffStreamFuncExistence}
-%\end{equation}
-%
-%\end{proposition}
-%
-%The equalities \cref{eq:NecSuffStreamFuncExistence}
-%constitute $N$ linearly independent constraints on the 
-%boundary data because the divergence-free condition 
-%\cref{eq:MassConservation} implies that
-%$\int_{\Gamma} \bu \cdot \bn \, dS = 0$. 
-%It turns out that 
-%these conditions are satisfied when the Dirichlet 
-%problem is recast as a Stokes flow \cref{eq:biharm5}, as 
-%it is easily verified that
-%\begin{equation}
-% \int_{\Gamma_i} \bu\cdot \bn \, dS 
-%= \int_{\Gamma_i} \frac{\partial f}{\partial \tau} \, dS =0 \, .
-%\end{equation}
-%Thus, any stream function $\tilde{w}$ obtained for the Stokes
-%flow \cref{eq:biharm5} is necessarily single-valued.
-%% NOT GOING THIS WAY ANYMORE
-%%It can be shown using the Helmholtz Hodge decomposition that the 
-%%conditions \cref{eq:NecSuffStreamFuncExistence} are sufficient for 
-%%the existence of a single-valued stream function. 
-%
-%\subsection{Evaluating the stream function} \label{subsec:stream}
-%
-%Given compatible boundary data for the velocity field $\bu$, 
-%the completed double layer representation for Stokes flow 
-%\cref{eq:IntRepStokes} guarantees the existence of
-%a solution density $\boldsymbol\mu$ 
-%and a corresponding stream function $\tilde{w}$. The Goursat 
-%function formula 
-%for $\tilde{w}$, see \cref{sec:stokeslayer},
-%is necessarily single-valued, as explained above,
-%but it is not immediately obvious from the formula 
-%that this should be true.
-%
-%The difficulty in the representation of $\tilde{w}$ 
-%comes from the part
-%of the stream function corresponding to the double layer potential
-% \cref{eq:wDL}. The 
-%second term in the expression for the double layer potential is
-%\begin{equation}
-% v_1(z) = \mbox{Re}\left[\frac{1}{4\pi i}\int_{\Gamma}\left(
-%\overline{\rho\left(\xi\right)}d\xi+\rho\left(\xi\right)
-%\overline{d\xi}\right)\log\left(\xi-z\right)\right] \, .
-%\end{equation}
-%To compute this term, in a na\"{i}ve numerical implementation,
-%the question of which is the appropriate branch of the 
-%logarithm to use would arise at many steps.
-%To avoid this complication, it is possible instead to compute
-%$v_1$, up to a constant, as the harmonic conjugate of the
-%function 
-%\begin{equation}
-% v_2 = \frac{1}{4\pi}\int_{\Gamma}\left(\overline{\rho\left(\xi\right)}
-%d\xi+\rho\left(\xi\right)\overline{d\xi}\right)\log
-%\left(\left|\xi-z\right|\right) \, . \label{eq:harmconjg}
-%\end{equation}
-%
-%We will use this approach to evalute $v_1$ numerically.
-%As a result of the Cauchy-Riemann equations, the 
-%harmonic conjugate of $v_2$, satisfies the following
-%Neumann problem for the Laplace equation:
-%\begin{align}
-% \Delta v_1 &= 0 &\quad x\in D \, ,\\
-% \frac{\partial v_1}{\partial n} &= -\frac{\partial v_2}{\partial \tau} 
-%&\quad x\in\Gamma \, .
-%\end{align}
-%It is possible then to use standard integral equation
-%methods to compute $v_1$. 
-%
-%Let $v_1 = S^L_\Gamma \sigma$, where $S^L_\Gamma \sigma$ 
-%is the single layer potential for Laplace's equation, given by
-%\begin{equation}
-%S^L_\Gamma\sigma (\bx) = -\frac{1}{2\pi} \int_{\Gamma} \log 
-%\left|\bx - \by \right|\sigma(\by)\, dS \left(\by \right) \, ,
-%\end{equation}
-%where $\sigma\in \mathcal{X}= C^{0,\alpha}\left(\Gamma\right)$, for 
-%some $\alpha \in (0,1)$, is an unknown density 
-%(see \cite{kress1999linear, guenther1988partial}).
-%Imposing the Neumann boundary conditions results in the 
-%following boundary integral equation for $\sigma$:
-%\begin{align}
-%-\frac{\partial v_2}{\partial \tau} (\bx) &= \frac{1}{2} \sigma \left(\bx\right) - \frac{1}{2\pi}\oint_{\Gamma} 
-%\frac{\partial}{\partial n_x}  
-%\log \left| \bx - \by \right |\sigma(\by)\, dS \left(\by \right) 
-%\, , \\
-%-\frac{\partial v_2}{\partial \tau} &= \left( \frac{1}{2}I_{\mathcal{X}} + K^L_\Gamma  \right) \sigma 
-%\, ,
-%\label{eq:BlockSystemRow2P1tmp}
-%\end{align}
-%where the operator $K^L_\Gamma$ is compact, so that the integral equation
-%is second kind.
-%For a derivation of this result, see \cite{kress1999linear}.
-%
-%It is well known that the operator $\frac{1}{2}I_{\mathcal{X}} + K^L_\Gamma$ 
-%has a one dimensional null space. Thus,
-%we choose to solve the above integral equation subject to 
-%the constraint $\int_{\Gamma} \sigma \, dS = 0$. 
-%Furthermore, it is known that solving the Neumann problem subject 
-%to the above constraint is equivalent
-%to solving
-%\begin{align}
-%\left( \frac{1}{2}I_{\mathcal{X}} + K^L_\Gamma  + W_\Gamma \right) \sigma 
-%= -\frac{\partial v_2}{\partial \tau}
-%\label{eq:BlockSystemRow2P1} 
-%\end{align}
-%where $W_\Gamma\sigma = \int_{\Gamma} \sigma \, dS$. 
-%To prove this, we need 
-%the following property of 
-%the Green's function for Laplace's equation.
-%\begin{align}
-%-\frac{1}{2\pi}\oint_{\gamma} \frac{\partial}{\partial n_{\by}}  
-%\log \left|\bx - \by\right|\, dS \left(\by \right) 
-%&=-\frac{1}{2}\quad\bx\in\gamma \, , \label{eq:DLP2}
-%\end{align}
-%Using the above property, it follows that
-%\begin{align}
-% \int_{\Gamma} K^L_\Gamma \sigma \, dS(\x) 
-%= -\frac{1}{2}\int_{\Gamma} \sigma \left(\bx\right) \, dS(\x) 
-%\label{eq:KLint}
-%\end{align}
-%Integrating equation \cref{eq:BlockSystemRow2P1} and using 
-%equation \cref{eq:KLint}, we get
-%\begin{align}
-%\int_{\Gamma} \left( \frac{1}{2}I_{\mathcal{X}} + 
-%K^L_\Gamma  + L \right) \sigma \, dS(\x) 
-%&= -\int_{\Gamma} \frac{\partial v_2}{\partial \tau} \, dS(\x) \\
-%\left|\Gamma\right| L\sigma  &= 0 
-%\end{align}
-%which proves the result.
-
-\subsection{Making the representation complete}
-As mentioned above, the solution $\tilde{w}$ of 
-the auxiliary Helmholtz-Stokes problem \cref{eq:biharm5}
-only satisfies the boundary conditions of the 
-original Dirichlet problem \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}
-up to a constant on each boundary component. For a simply
-connected domain, this constant can be recovered from the
-fact that adding an arbitrary constant to a stream function
-does not change the velocity field. 
-Thus, in simply connected domains, there is an equivalence in the 
-solutions of \cref{eq:biharm5} and \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}.
-
-To analyze the case of a multiply connected domain,
-we first consider
-radially symmetric solutions on an annulus centered at the
-origin. Let $w\left(r\right)$ be a 
-radially symmetric biharmonic-Stokes
-potential. Then $w(r)$ solves the ordinary differential
-equation (ODE)
-\begin{equation}
-\Delta_{r} (\Delta_{r} + k^2)w = 0 \, ,
-\end{equation}
-where $\Delta_{r}$ is the radial component of the Laplacian in polar
-coordinates given by
-$$
-\Delta_{r} = \frac{1}{r}\frac{d}{dr} r \frac{d}{dr} \, .
-$$
-Four linearly independent solutions of this ODE are $1$, $\log{(r)}$, 
-$J_{0}(kr)$, and $H_{0}(kr)$, 
-where $J_{0}$ is the order zero Bessel function of the first kind, and $H_{0}$ is the order zero Hankel function of the first kind.
-For each solution, we can compute the associated velocity field 
-$\bu = \nabla^{\perp} w$. By construction, $\bu$ satisfies 
-the continuity condition \cref{eq:MassConservation}. 
-For the momentum equation \cref{eq:StokesFlowEq} to be 
-satisfied, we need that $\Delta\bu + k^2 \bu$ is a conservative
-vector field, which 
-is equivalent to the condition that 
-$\int_{\gamma} (\Delta\bu + k^2 \bu) \cdot d\bl = 0$ 
-for any closed 
-loop $\gamma$ in the annulus. For $\tilde{w}=1$, $J_{0}(kr)$, and $H_{0}(kr)$,
-the corresponding velocity field satisfies
-$\Delta \bu + k^2 \bu=0$ so that $\Delta \bu$
-is trivially a conservative vector field. 
-On the other hand, for $\tilde{w}=\log{(r)}$, the corresponding velocity field
-satisfies $\Delta \bu + k^2 \bu=\frac{k^2}{r} \hat{\theta}$.
-By considering a curve $\gamma$ encircling the origin,
-we see that $\Delta \bu + k^2 \bu$ is not a conservative vector
-field and that any pressure for the velocity field 
-associated with $\log\left(r\right)$ is not single-valued.
-%
-%The above analysis
-%can be extended to show that any solution of the biharmonic equation 
-%of the form $\log{|r-r_{j}|}$ where $r_{j}$ is located in one of the holes of a multiply connected
-%domain.
-%cannot be represented as a Stokes velocity field. 
-%In simply connected 
-%domains, since there are no holes, corresponding to each solution of the modified biharmonic equation with clamped plate
-%boundary conditions, there exists a solution to . For multiply connected domains with genus $N$, 
-%the set of stream functions for Stokes velocity fields
-%misses an $N$ dimensional space of solutions, corresponding 
-%to biharmonic charges located in the holes of the domain.
-%Following this reasoning, we obtain a complete representation
-%for biharmonic potentials on multiply connected domains
-%by adding $N$ charges, one per each hole of the domain,
-%to the representation for $w$. The details of this approach, and
-%the proof that it is sufficient, is in the next section.
-
-\bibliographystyle{plain}
-\bibliography{refs}
-
-\end{document}

### 2018-06-22 doc/draft-01/biharm-evals.tex
reorganize paper

--- 2018-04-24 doc/draft-01/biharm-evals.tex
@@
 
-\title{An integral equation method for the biharmonic
-Dirichlet eigenvalue problem in two dimensions}
+\title{A Fredholm operator approach to the plate
+buckling problem}
 \author{Askham and Rachh}
@@
 
-\section{Introduction}
-
-Results of some quick googling:
-
-Finite element methods.
-\begin{itemize}
-\item Stokes eigenvalue problem: nonconforming finite
-  element methods \cite{jia2009approximation}.
-\end{itemize}
-
-Integral equation methods.
-\begin{itemize}
-\item Book on elastodynamic eigenvalue problems
-  \cite{kitahara2014boundary}
-\end{itemize}
-\section{Mathematical Preliminaries}
-
-\subsection{Notation}
-
-Bold symbols are vectors or tensors.
-$\xx = (x_1,x_2)^\intercal$ then $\xx^\bot = (-x_2,x_1)^\intercal$.
-Similarly, $\nabla^\bot = (-\partial_{x_2},\partial_{x_1})^\intercal$
-
-\subsection{Green's functions}
-
-$\Delta$
-\begin{equation}
-  G_L(\xx,\yy) = -\frac{1}{2\pi} \log |\xx-\yy|
-\end{equation}
-
-$\Delta + k^2$
-\begin{equation}
-  G_H(\xx,\yy) = \frac{i}{4} H_0^{(1)}(k|\xx-\yy|)
-\end{equation}
-
-$\Delta(\Delta + k^2)$
-\begin{equation}
-  G_{BH}(\xx,\yy) = -\frac{1}{k^2}
-  \left (\frac{1}{2\pi} \log |\xx-\yy| +
-  \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \right )
-\end{equation}
-
-\section{Integral Equation Formulation}
-
-\subsection{The Helmholtz Stokeslet formulation}
-
-In this section, we review the derivation of the
-modified Stokeslet, but for the imaginary parameter
-regime --- which we will call the Helmholtz Stokeslet ---
-which is the appropriate setting for the Stokes
-eigenvalue problem.
-The original modified Stokeslet is more well known,
-and is of particular interest for its application to
-numerical simulations of the unsteady Stokes equations
-\cite{pozrikidis1992boundary,biros2002embedded}.
-
-To begin, we restate the Stokes eigenvalue
-problem as
-\begin{align}
-  \nabla p - \Delta \uu - k^2 \uu &= 0 \; , \label{eq:helmstokes}\\
-  \nabla \cdot \uu &= 0 \; . \label{eq:helmstokescty}
-\end{align}
-Consider the solution of this problem where a
-$\delta$ centered at $\yy$ with strength $\ff$
-has been added to the right-hand side, i.e.
-
-\begin{align}
-  \nabla p - \Delta \uu - k^2 \uu &= \delta_\yy \ff \; ,
-  \label{eq:helmstokes_charge} \\
-  \nabla \cdot \uu &= 0 \; .
-\end{align}
-Note that
-
-\begin{equation}
-  \Delta G_L(\xx,\yy) = \delta_\yy(\xx) \; .
-\end{equation}
-If we substitute this expression into
-\eqref{eq:helmstokes_charge} and take the divergence,
-we obtain
-
-\begin{equation}
-  p = \nabla G_L(\xx,\yy) \cdot \ff \; .
-\end{equation}
-We then have, formally,
-
-\begin{align}
-  \uu &= - (\Delta + k^2)^{-1} ( \Delta G_L \ff
-  - \nabla (\nabla G_L \cdot \ff ) ) \\
-  &= \left ( -\Delta + \nabla \otimes \nabla \right )
-  G_{BH} \ff \; .
-\end{align}
-The tensor
-
-\begin{equation}
-  \GG = - \II \Delta G_{BH} + \nabla \otimes \nabla G_{BH}
-\end{equation}
-is then the equivalent of a Stokeslet
-\cite{pozrikidis1992boundary} for the problem
-\eqref{eq:helmstokes}.
-
-A related object is the stresslet, which is defined
-in terms of the stress tensor of a velocity, pressure
-pair induced by a Stokeslet. For these tensors, we find
-that it is more convenient to express them in index notation
-with the Einstein index summing convention.
-Recall that the stress tensor $\bsigma$ is defined as
-
-\begin{equation}
-  \sigma_{ij} = -p \delta_{ij} + \left ( \partial_{x_j}u_i
-  +\partial_{x_i} u_j \right ) \; ,
-\end{equation}
-where $\delta_{ij}$ is the standard Kronecker delta notation.
-The stresslet $\TT$ is defined to be
-
-\begin{align}
-  T_{ijk} &= - \partial_{x_j} G_L \delta_{ik}
-  + \partial_{x_k} \left ( -\Delta G_{BH} \delta_{ij} +
-  \partial_{x_i} \left(\partial_{x_j} G_{BH} \right) \right)
-  \nonumber \\
-  & \qquad+ \partial_{x_i} \left ( -\Delta G_{BH} \delta_{kj} +
-  \partial_{x_k} \left(\partial_{x_j} G_{BH} \right) \right)
-  \; .
-\end{align}
-Let $u_i = G_{ij} f_j$ and $p = \partial_{x_i} G_L f_i$ be a
-solution of the Stokes equations induced by a Stokeslet.
-Then the corresponding stress tensor is given by
-$\sigma_{ik} = T_{ijk} f_j$.
-
-For the layer potentials of the next section, the following
-formulas are useful. Let $\bnu$ be a given vector. When
-summing over the third index, we obtain
-
-\begin{equation}
-  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla G_L
-  + \partial_\nu \left ( -\Delta G_{BH} \II
-  + \nabla \otimes \nabla G_{BH} \right)
-  + \nabla \otimes \left ( -\Delta G_{BH} \bnu
-  + \partial_{\nu} \nabla G_{BH} \right) \; .
-\end{equation}
-%\begin{align}
-% -\Delta G_{BH} \bnu
-% + \partial_{\nu} \nabla G_{BH} &=
-% ( (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_1 G_{BH} +
-% (\partial_{x_1x_1}\nu_1 + \partial_{x_2x_1} \nu_2 )G_{BH},
-% (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_2 G_{BH} +
-% (\partial_{x_1x_2}\nu_1 + \partial_{x_2x_2} \nu_2 )G_{BH}) \\
-% &= (-\partial_{x_2} \partial_\tau G_{BH},
-% \partial_{x_1} \partial_\tau G_{BH})
-%\end{align}
-%\begin{equation}
-%  \begin{pmatrix}
-%    -\partial_{x_2x_2} & \partial_{x_1x_2} \\
-%    \partial_{x_1x_2} & -\partial_{x_1x_1}
-%  \end{pmatrix} = -\nabla^\bot \otimes \nabla^\bot
-%\end{equation}
-Let $\btau = \bnu^\bot$. Then
-
-\begin{equation}
-  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla G_L
-  - \nabla^\bot \otimes \nabla^\bot \partial_\nu G_{BH}
-  +\nabla \otimes \nabla^\bot \partial_\tau G_{BH} \; .
-\end{equation}
-
-\subsection{Layer potentials}
-
-\subsection{The Farkas integral representation}
-
-As mentioned in the introduction, there are existing 
-integral representations for the solution of the Dirichlet problem for the Helmholtz-biharmonic equation
-\begin{align}
- \Delta (\Delta + k^2) w &= 0 \mbox{ in } D \; , \label{eq:biharmD1}\\
- w &= f \mbox{ on }
- \Gamma \label{eq:biharmD2} \; , \\ 
- \frac{\partial w}{\partial n} &= g \mbox{ on } 
- \Gamma \, , \label{eq:biharmD3}
-\end{align}
-In \cite{Farkas89}, 
-the solution is given as the sum of two layer potentials, i.e.
-\begin{equation}
-  w(\xx) = \int_\Gamma K_1^F (\xx,\yy) \sigma_1(\yy) \, dS(\yy)
-  + \int_\Gamma K_2^F(\xx,\yy) \sigma_2(\yy) \, dS(\yy) \; ,
-  \label{eq:farkRep}
-\end{equation}
-where $\sigma_1$ and $\sigma_2$ are unknown densities.
-
-The integral kernels, $K_1^F$ and $K_2^F$ are based on
-derivatives of the Green's function for the biharmonic equation.
-For two points on the plane, $\xx$ and $\yy$, let $\br = \yy - \xx$. Then 
-\begin{align}
-  K_1^F(\xx,\yy) &= \partial_{n_{y}n_{y}n_{y}}\Gbh(\xx,\yy)
-  + 3 \partial_{n_{y}\tau_{y}\tau_{y}}\Gbh(\xx,\yy) + k^{2} \partial_{n_{y}}\Gbh(\xx,\yy)\; , \label{eq:kf1} \\
-  K_2^F(\xx,\yy) &= -\partial_{n_{y}n_{y}}\Gbh(\xx,\yy)
-  + \partial_{\tau_{y}\tau_{y}}\Gbh(\xx,\yy) \label{eq:kf2} \; .
-\end{align}
-More explicitly, we have
-
-\begin{align}
-  K_1^F(\xx,\yy) &=  -\dfrac{\br \cdot \bn(\yy)}{|\br|^2}  \cdot \left( \frac{3 i}{2} H_0^{(1)}(k|\br|) - \frac{5 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{6}{\pi k^2 |\br|^2} + \frac{1}{2\pi}  \right) +     \\
-  & \quad \dfrac{\left(\br \cdot \bn(\yy)\right)^3}{|\br|^4} \cdot \left( 2i H_0^{(1)}(k|\br|) - \frac{7 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{8}{\pi k^2 |\br|^2}  \right) \, , \nonumber \\
-  K_2^F(\xx,\yy) &=  -\left(\frac{1}{2}-\dfrac{\left(\br \cdot \bn(\yy)\right)^2}{|\br|^2} \right)  \cdot \left( \frac{i}{2} H_0^{(1)}(k|\br|) - \frac{i}{k|\br|} H_1^{(1)}(k|\br|) + \frac{2}{\pi k^2 |\br|^2}  \right)\; .
-\end{align}
-
-On enforcing the Dirichlet boundary conditions for
-$w$, we obtain the integral equation
-\begin{equation}
-  \begin{split}
-    \begin{pmatrix}
-      f(\xx) \\
-      g(\xx)
-    \end{pmatrix} &= 
-    \int_\Gamma
-    \begin{pmatrix}
-      K_{11}^F(\xx,\yy) & K_{12}^F(\xx,\yy) \\
-      K_{21}^F(\xx,\yy) & K_{22}^F(\xx,\yy)
-    \end{pmatrix}
-    \begin{pmatrix}
-      \sigma_1(\yy)\\
-      \sigma_2(\yy)
-    \end{pmatrix}
-    \, dS(\yy) \\
-    &\quad + \begin{pmatrix}
-      1/2 & 0 \\
-      -\kappa(\xx) & 1/2
-    \end{pmatrix}
-    \begin{pmatrix}
-      \sigma_1(\xx)\\
-      \sigma_2(\xx)
-    \end{pmatrix} \; , \label{eq:farkIntEq} 
-  \end{split}
-\end{equation}
-where $\kappa$ denotes the signed curvature as
-a function on $\Gamma$ and $\xx$ is a point on $\Gamma$. 
-The kernels are given
-by $K_{11}^F = K_1^F$, $K_{12}^F = K_2^F$,
-\begin{align}
-  K_{21}^F(\xx,\yy) &= \left(K_1^F(\xx,\yy)\right )_{n_x} \nonumber \\
-  &= \bn(\xx) \cdot \nabla_{\xx} K_{21}^{F}(\xx,\yy) \; \label{eq:farkK21},\\
-  K_{22}^F(\xx,\yy) &= \left(K_2^F(\xx,\yy)\right )_{n_x} \nonumber \\
-  &= \bn(\xx) \cdot \nabla_{\xx} K_{22}^{F}(\xx,\yy) \label{eq:farkK22} \; .
-\end{align}
-For a sufficiently smooth and simply connected domain,
-the integral equation \cref{eq:farkIntEq} is invertible.
-The case of a multiply connected domain is not treated
-fully in \cite{Farkas89}, but some of the issues are
-considered.
-
-As mentioned above, the kernels $K^F_1$ and $K^F_2$ are
-constructed with the goal that the $K^F_{ij}$ are
-as smooth as possible. Suppose that the boundary
-$\Gamma$ is of class $C^k$. Then, the kernels,
-$K^F_{ij}(\xx,\yy)$, are $C^{k-2}$ functions on the boundary
-for each $\yy \in \Gamma$.
-Therefore, on a smooth
-boundary, these kernels are smooth. However, on a
-domain with a corner, we note 
-that the kernel $K_{21}^F$
-has a singularity with strength $r^{-2}$ (see~\cref{fig:ker21plot}). 
-This singularity, in addition to the term in \cref{eq:farkIntEq}
-which explicitly involves the
-curvature, makes the representation \cref{eq:farkRep}
-unstable for domains with high curvature (or
-corners).
-
-\section{Integral equation derivation} \label{sec:anapp}
-
-%\subsection{Adapting the completed double layer representation
-%to solve the Dirichlet problem}
-We would like to adapt the completed double layer representation
-for solutions of Stokes flow \cref{eq:biharmV1,eq:biharmV2,eq:biharmV3} to solve 
-the clamped plate problem \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}.
-Let $f$ and $g$ be the boundary data as in \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}. 
-By computing tangential derivatives of $f$ on each
-boundary component, we get the following related Helmholtz-Stokes problem:
-\begin{align}
- \Delta (\Delta + \lambda^2) \tilde{w}  = 0 &\quad \bx \in D \, ,\nonumber\\
- \frac{\partial \tilde{w}}{\partial \tau} = 
- \frac{\partial f}{\partial \tau} 
-&\quad \bx \in \Gamma \label{eq:biharm5} \, ,\\ 
- \frac{\partial \tilde{w}}{\partial n} = g &\quad \bx 
-\in \Gamma 
-\, . 
-\nonumber
-\end{align}
-There are two main issues to be addressed in using the completed
-double layer representation in this context. First,
-the representation is designed for 
-Helmholtz-Stokes flow, in which the quantities of interest are derivatives
-of the potential $\tilde{w}$ and not $\tilde{w}$ itself; the
-representation for $\tilde{w}$ may not be single-valued. 
-We will establish that, in the context of \cref{eq:biharm5},
-the stream function is necessarily single-valued. We also discuss
-some numerical issues related to evaluating the stream function.
-The second issue to address
-is that the solution $\tilde{w}$ only satisfies the original boundary 
-condition for the value of $\tilde{w}$ up to a constant on 
-each boundary component.
-In fact, for multiply connected domains, the completed double layer 
-representation is incomplete for the Dirichlet
-problem \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}. We present a remedy for this 
-issue and provide some physical intuition.
-%
-%\subsection{Single-valued stream functions}
-%To solve the Dirichlet problem \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3},
-%it is necessary to compute
-%a single-valued biharmonic potential.
-%In the case of a multiply connected domain,
-%there is no guarantee that a single-valued stream 
-%function exists for a given velocity field.
-%
-%Consider the following example.
-%Let $(r,\theta)$ denote standard polar coordinates. It is
-%easy to verify that the velocity field 
-%$\bu=\frac{1}{r}\hat{r}$ 
-%solves the equations of Stokes flow in an annulus centered at the 
-%origin. A stream function for this flow is $w=\theta$, which 
-%is not single-valued; indeed, there are no single-valued
-%stream functions which generate this flow. 
-%
-%Let $D$ be a multiply connected domain with boundary 
-%$\Gamma = \cup_{i=0}^N \Gamma_i$, as in the previous section.
-%We note that the gradient of a stream function is determined 
-%by the velocity field, i.e. 
-%
-%\begin{equation}
-%\nabla w = -\bu^\perp := \begin{pmatrix} 
-%  - u_2 \\ u_1 
-%\end{pmatrix} \; .
-%\end{equation}
-%Therefore, a velocity field has single-valued stream
-%functions if and only if $\bu^\perp$ is conservative.
-%Using standard results from multivariable calculus, 
-%we can  characterize such flows.
-%
-%\begin{proposition} 
-%Suppose that $\bu$ is a divergence-free velocity 
-%field which is $C^1$ on $D$ and continuous on 
-%$D\cup \Gamma$. The field $\bu^\perp$ 
-%is conservative if and only if 
-%
-%\begin{equation}
-% \int_{\Gamma_i} \bu\cdot \bn \, dS 
-%= 0 \quad i=0,1,\ldots N \, .
-%\label{eq:NecSuffStreamFuncExistence}
-%\end{equation}
-%
-%\end{proposition}
-%
-%The equalities \cref{eq:NecSuffStreamFuncExistence}
-%constitute $N$ linearly independent constraints on the 
-%boundary data because the divergence-free condition 
-%\cref{eq:MassConservation} implies that
-%$\int_{\Gamma} \bu \cdot \bn \, dS = 0$. 
-%It turns out that 
-%these conditions are satisfied when the Dirichlet 
-%problem is recast as a Stokes flow \cref{eq:biharm5}, as 
-%it is easily verified that
-%\begin{equation}
-% \int_{\Gamma_i} \bu\cdot \bn \, dS 
-%= \int_{\Gamma_i} \frac{\partial f}{\partial \tau} \, dS =0 \, .
-%\end{equation}
-%Thus, any stream function $\tilde{w}$ obtained for the Stokes
-%flow \cref{eq:biharm5} is necessarily single-valued.
-%% NOT GOING THIS WAY ANYMORE
-%%It can be shown using the Helmholtz Hodge decomposition that the 
-%%conditions \cref{eq:NecSuffStreamFuncExistence} are sufficient for 
-%%the existence of a single-valued stream function. 
-%
-%\subsection{Evaluating the stream function} \label{subsec:stream}
-%
-%Given compatible boundary data for the velocity field $\bu$, 
-%the completed double layer representation for Stokes flow 
-%\cref{eq:IntRepStokes} guarantees the existence of
-%a solution density $\boldsymbol\mu$ 
-%and a corresponding stream function $\tilde{w}$. The Goursat 
-%function formula 
-%for $\tilde{w}$, see \cref{sec:stokeslayer},
-%is necessarily single-valued, as explained above,
-%but it is not immediately obvious from the formula 
-%that this should be true.
-%
-%The difficulty in the representation of $\tilde{w}$ 
-%comes from the part
-%of the stream function corresponding to the double layer potential
-% \cref{eq:wDL}. The 
-%second term in the expression for the double layer potential is
-%\begin{equation}
-% v_1(z) = \mbox{Re}\left[\frac{1}{4\pi i}\int_{\Gamma}\left(
-%\overline{\rho\left(\xi\right)}d\xi+\rho\left(\xi\right)
-%\overline{d\xi}\right)\log\left(\xi-z\right)\right] \, .
-%\end{equation}
-%To compute this term, in a na\"{i}ve numerical implementation,
-%the question of which is the appropriate branch of the 
-%logarithm to use would arise at many steps.
-%To avoid this complication, it is possible instead to compute
-%$v_1$, up to a constant, as the harmonic conjugate of the
-%function 
-%\begin{equation}
-% v_2 = \frac{1}{4\pi}\int_{\Gamma}\left(\overline{\rho\left(\xi\right)}
-%d\xi+\rho\left(\xi\right)\overline{d\xi}\right)\log
-%\left(\left|\xi-z\right|\right) \, . \label{eq:harmconjg}
-%\end{equation}
-%
-%We will use this approach to evalute $v_1$ numerically.
-%As a result of the Cauchy-Riemann equations, the 
-%harmonic conjugate of $v_2$, satisfies the following
-%Neumann problem for the Laplace equation:
-%\begin{align}
-% \Delta v_1 &= 0 &\quad x\in D \, ,\\
-% \frac{\partial v_1}{\partial n} &= -\frac{\partial v_2}{\partial \tau} 
-%&\quad x\in\Gamma \, .
-%\end{align}
-%It is possible then to use standard integral equation
-%methods to compute $v_1$. 
-%
-%Let $v_1 = S^L_\Gamma \sigma$, where $S^L_\Gamma \sigma$ 
-%is the single layer potential for Laplace's equation, given by
-%\begin{equation}
-%S^L_\Gamma\sigma (\bx) = -\frac{1}{2\pi} \int_{\Gamma} \log 
-%\left|\bx - \by \right|\sigma(\by)\, dS \left(\by \right) \, ,
-%\end{equation}
-%where $\sigma\in \mathcal{X}= C^{0,\alpha}\left(\Gamma\right)$, for 
-%some $\alpha \in (0,1)$, is an unknown density 
-%(see \cite{kress1999linear, guenther1988partial}).
-%Imposing the Neumann boundary conditions results in the 
-%following boundary integral equation for $\sigma$:
-%\begin{align}
-%-\frac{\partial v_2}{\partial \tau} (\bx) &= \frac{1}{2} \sigma \left(\bx\right) - \frac{1}{2\pi}\oint_{\Gamma} 
-%\frac{\partial}{\partial n_x}  
-%\log \left| \bx - \by \right |\sigma(\by)\, dS \left(\by \right) 
-%\, , \\
-%-\frac{\partial v_2}{\partial \tau} &= \left( \frac{1}{2}I_{\mathcal{X}} + K^L_\Gamma  \right) \sigma 
-%\, ,
-%\label{eq:BlockSystemRow2P1tmp}
-%\end{align}
-%where the operator $K^L_\Gamma$ is compact, so that the integral equation
-%is second kind.
-%For a derivation of this result, see \cite{kress1999linear}.
-%
-%It is well known that the operator $\frac{1}{2}I_{\mathcal{X}} + K^L_\Gamma$ 
-%has a one dimensional null space. Thus,
-%we choose to solve the above integral equation subject to 
-%the constraint $\int_{\Gamma} \sigma \, dS = 0$. 
-%Furthermore, it is known that solving the Neumann problem subject 
-%to the above constraint is equivalent
-%to solving
-%\begin{align}
-%\left( \frac{1}{2}I_{\mathcal{X}} + K^L_\Gamma  + W_\Gamma \right) \sigma 
-%= -\frac{\partial v_2}{\partial \tau}
-%\label{eq:BlockSystemRow2P1} 
-%\end{align}
-%where $W_\Gamma\sigma = \int_{\Gamma} \sigma \, dS$. 
-%To prove this, we need 
-%the following property of 
-%the Green's function for Laplace's equation.
-%\begin{align}
-%-\frac{1}{2\pi}\oint_{\gamma} \frac{\partial}{\partial n_{\by}}  
-%\log \left|\bx - \by\right|\, dS \left(\by \right) 
-%&=-\frac{1}{2}\quad\bx\in\gamma \, , \label{eq:DLP2}
-%\end{align}
-%Using the above property, it follows that
-%\begin{align}
-% \int_{\Gamma} K^L_\Gamma \sigma \, dS(\x) 
-%= -\frac{1}{2}\int_{\Gamma} \sigma \left(\bx\right) \, dS(\x) 
-%\label{eq:KLint}
-%\end{align}
-%Integrating equation \cref{eq:BlockSystemRow2P1} and using 
-%equation \cref{eq:KLint}, we get
-%\begin{align}
-%\int_{\Gamma} \left( \frac{1}{2}I_{\mathcal{X}} + 
-%K^L_\Gamma  + L \right) \sigma \, dS(\x) 
-%&= -\int_{\Gamma} \frac{\partial v_2}{\partial \tau} \, dS(\x) \\
-%\left|\Gamma\right| L\sigma  &= 0 
-%\end{align}
-%which proves the result.
-
-\subsection{Making the representation complete}
-As mentioned above, the solution $\tilde{w}$ of 
-the auxiliary Helmholtz-Stokes problem \cref{eq:biharm5}
-only satisfies the boundary conditions of the 
-original Dirichlet problem \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}
-up to a constant on each boundary component. For a simply
-connected domain, this constant can be recovered from the
-fact that adding an arbitrary constant to a stream function
-does not change the velocity field. 
-Thus, in simply connected domains, there is an equivalence in the 
-solutions of \cref{eq:biharm5} and \cref{eq:biharmD1,eq:biharmD2,eq:biharmD3}.
-
-To analyze the case of a multiply connected domain,
-we first consider
-radially symmetric solutions on an annulus centered at the
-origin. Let $w\left(r\right)$ be a 
-radially symmetric biharmonic-Stokes
-potential. Then $w(r)$ solves the ordinary differential
-equation (ODE)
-\begin{equation}
-\Delta_{r} (\Delta_{r} + k^2)w = 0 \, ,
-\end{equation}
-where $\Delta_{r}$ is the radial component of the Laplacian in polar
-coordinates given by
-$$
-\Delta_{r} = \frac{1}{r}\frac{d}{dr} r \frac{d}{dr} \, .
-$$
-Four linearly independent solutions of this ODE are $1$, $\log{(r)}$, 
-$J_{0}(kr)$, and $H_{0}(kr)$, 
-where $J_{0}$ is the order zero Bessel function of the first kind, and $H_{0}$ is the order zero Hankel function of the first kind.
-For each solution, we can compute the associated velocity field 
-$\bu = \nabla^{\perp} w$. By construction, $\bu$ satisfies 
-the continuity condition \cref{eq:MassConservation}. 
-For the momentum equation \cref{eq:StokesFlowEq} to be 
-satisfied, we need that $\Delta\bu + k^2 \bu$ is a conservative
-vector field, which 
-is equivalent to the condition that 
-$\int_{\gamma} (\Delta\bu + k^2 \bu) \cdot d\bl = 0$ 
-for any closed 
-loop $\gamma$ in the annulus. For $\tilde{w}=1$, $J_{0}(kr)$, and $H_{0}(kr)$,
-the corresponding velocity field satisfies
-$\Delta \bu + k^2 \bu=0$ so that $\Delta \bu$
-is trivially a conservative vector field. 
-On the other hand, for $\tilde{w}=\log{(r)}$, the corresponding velocity field
-satisfies $\Delta \bu + k^2 \bu=\frac{k^2}{r} \hat{\theta}$.
-By considering a curve $\gamma$ encircling the origin,
-we see that $\Delta \bu + k^2 \bu$ is not a conservative vector
-field and that any pressure for the velocity field 
-associated with $\log\left(r\right)$ is not single-valued.
-%
-%The above analysis
-%can be extended to show that any solution of the biharmonic equation 
-%of the form $\log{|r-r_{j}|}$ where $r_{j}$ is located in one of the holes of a multiply connected
-%domain.
-%cannot be represented as a Stokes velocity field. 
-%In simply connected 
-%domains, since there are no holes, corresponding to each solution of the modified biharmonic equation with clamped plate
-%boundary conditions, there exists a solution to . For multiply connected domains with genus $N$, 
-%the set of stream functions for Stokes velocity fields
-%misses an $N$ dimensional space of solutions, corresponding 
-%to biharmonic charges located in the holes of the domain.
-%Following this reasoning, we obtain a complete representation
-%for biharmonic potentials on multiply connected domains
-%by adding $N$ charges, one per each hole of the domain,
-%to the representation for $w$. The details of this approach, and
-%the proof that it is sufficient, is in the next section.
+\input{01intro}
+\input{02prelim}
+\input{03inteq}
+\input{04analyze}
+\input{05results}
+\input{06conclude}
 

### 2018-06-22 doc/draft-01/01intro.tex
update manuscript, reorganize intro

@@
 \section{Introduction}
-
-Results of some quick googling:
-
-Finite element methods.
-\begin{itemize}
-\item Stokes eigenvalue problem: nonconforming finite
-  element methods \cite{jia2009approximation}.
-\end{itemize}
-
-Integral equation methods.
-\begin{itemize}
-\item Book on elastodynamic eigenvalue problems
-  \cite{kitahara2014boundary}
-\end{itemize}
 
@@
 plate. 
-Let $\Omega$ denote the midline of the thin plate, $\Gamma$ denote the 
+Let $\Omega$ denote the midline of the plate, $\Gamma$ denote the 
 boundary of $\Omega$ and $w$ denote the vertical displacement.
@@
 \begin{align}
-\Delta (\Delta + k^2) w &= 0 \quad \text{in} \quad \Omega \label{eq:buck1} \\
-w &= 0 \quad \text{on} \quad \Gamma \label{eq:buck2}\\
-\dwdn &=0 \quad \text{on} \quad \Gamma \label{eq:buck3} \,.
+\Delta (\Delta + k^2) w &= 0 \quad \text{in} \quad \Omega \label{eq:buck1} \; , \\
+w &= 0 \quad \text{on} \quad \Gamma \label{eq:buck2} \; ,\\
+\dwdn &=0 \quad \text{on} \quad \Gamma \label{eq:buck3} 
 \end{align}
 has a non-trivial solution. In a slight abuse of notation,
-these values $k^2$ and the corresponding
-solutions are often referred to as ``eigenvalues'' and ``eigenfunctions'',
+these values and the corresponding solutions are often
+referred to as ``eigenvalues'' and ``eigenfunctions'',
 respectively. 
-It is well-known from classical potential theory that, 
-for the buckling problem, there exists a countable collection of
-such values $0 < k_{1}^{2} \leq k_{2}^2 \leq \ldots \uparrow \infty$,
+It is well known that the buckling problem has a
+countable collection of such values
+$0 < k_{1}^{2} \leq k_{2}^2 \leq \ldots \uparrow \infty$,
 counting multiplicites.
+
+The eigenvalues (and eigenfunctions)
+of the boundary value problem \cref{eq:buck1,eq:buck2,eq:buck3}
+describe the critical buckling load (and deflection)
+of a thin plate under
+a compressive force applied along the edge. While the
+isotropy and homogeneity assumptions are restrictive,
+the equations are still of interest in materials design
+(CITATIONS). The analytical properties of the eigenvalues and
+eigenfunctions are also of interest from a mathematical
+perspective, often as they contrast with the eigenvalues
+and eigenmodes of an idealized drum (CITATIONS).
+
+Numerical simulations have long played an important
+in the analyses described above and there are a number
+of available methods (note that some of the references
+included here are written in terms of the related
+Stokes eigenvalue problem, which has equivalent
+eigenvalues on simply connected domains).
+The differential equation can
+be discretized directly, resulting in a discrete
+generalized eigenvalue problem for the buckling
+eigenvalues \cite{jia2009approximation}. Integral
+equation methods \cite{kitahara2014boundary} are
+a natural choice for this problem, because (a) the
+fourth order term induces strong
+ill-conditioning when the differential equation
+is discretized directly and (b) the problem is reduced
+to one defined on the domain alone, requiring fewer
+degrees of freedom to resolve the solution.
+
 \begin{remark}
-For notational convenience,  
-we will refer to the modified Biharmonic problem
-with imaginary parameter as the Helmholtz-Biharmonic problem.
+  When $k = i\alpha$, the differential equation
+  \cref{eq:buck1} is known as the modified biharmonic
+  equation. As there appears to be no preferred
+  name for the equation with real-valued $k$,
+  we will refer to \cref{eq:buck1} as the
+  Helmholtz-biharmonic equation.
 \end{remark}

### 2018-06-23 doc/draft-01/01intro.tex
update paper, build out introduction

@@
 \begin{align}
-\Delta (\Delta + k^2) w &= 0 \quad \text{in} \quad \Omega \label{eq:buck1} \; , \\
-w &= 0 \quad \text{on} \quad \Gamma \label{eq:buck2} \; ,\\
-\dwdn &=0 \quad \text{on} \quad \Gamma \label{eq:buck3} 
+\Delta (\Delta + k^2) w &= 0 \quad \textrm{in} \quad \Omega \label{eq:buck1} \; , \\
+w &= 0 \quad \textrm{on} \quad \Gamma \label{eq:buck2} \; ,\\
+\dwdn &=0 \quad \textrm{on} \quad \Gamma \label{eq:buck3} 
 \end{align}
@@
 perspective, often as they contrast with the eigenvalues
-and eigenmodes of an idealized drum (CITATIONS).
+and eigenmodes of an idealized drum (CITATIONS). For instance,
+it is well-known that the first eigenfunction of the
+drum problem (i.e. the eigenvalue problem of the Laplace
+equation with homogeneous Dirichlet boundary conditions)
+is either nonpositive or nonnegative on any domain.
+In contrast, it is possible for the first buckling
+eigenfunction of a convex domain with analytic boundary
+to take both positive and negative values \cite{antunes2011buckling}.
 
@@
 Stokes eigenvalue problem, which has equivalent
-eigenvalues on simply connected domains).
-The differential equation can
-be discretized directly, resulting in a discrete
-generalized eigenvalue problem for the buckling
-eigenvalues \cite{jia2009approximation}. Integral
-equation methods \cite{kitahara2014boundary} are
-a natural choice for this problem, because (a) the
-fourth order term induces strong
-ill-conditioning when the differential equation
-is discretized directly and (b) the problem is reduced
-to one defined on the domain alone, requiring fewer
-degrees of freedom to resolve the solution.
+eigenvalues on simply connected domains). We do not
+seek to review the literature here but will provide
+some context for the present work. Finite element methods
+are ubiquitous in mechanical engineering applications
+and are flexible both with respect to the governing
+equations and the shape of the domain. Such a method
+would first obtain a ``weak'' form of the equations
+\cref{eq:buck1,eq:buck2,eq:buck3} and then 
+approximate the solution space in some
+finite dimensional basis, resulting in a discrete model
+for the buckling problem.
+The eigenvalues $k^2$ are then
+approximated by the eigenvalues of the discrete
+model \cite{johnson1974beam,rannacher1979nonconforming,
+  jia2009approximation,carstensen2014guaranteed}.
+Because of the fourth order term in \cref{eq:buck1},
+the system matrices resulting from a finite element
+discretization can have large condition numbers (growing
+like $h^4$ where $h$ is the diameter of a typical element
+in the discretization) which can cause numerical instability.
+
+Integral equation methods \cite{kress1989linear,
+  atkinson2009numerical,kitahara2014boundary} present
+a natural alternative to the finite element method
+for the buckling problem, because (a) the
+integral representation acts as an analytical preconditioner
+for the fourth order term and (b) the problem is reduced
+to one defined on the boundary of the domain alone,
+requiring fewer degrees of freedom to resolve the solution
+on a complex domain. In an integral equation method,
+the solution $w$ is represented in terms of a sum of
+two layer potentials (which a priori satisfy
+\cref{eq:buck1}) with unknown densities. Substituting this
+representation into the boundary conditions
+\cref{eq:buck2,buck3} results in an integral equation
+for the unknown densities, which
+is in turn discretized using numerical quadrature.
+Unlike the original equation \cref{eq:buck1} and the weak
+formulation used in a finite element method, the integral
+equation for the unknown densities has a nonlinear dependence
+on the parameter $k^2$. In an integral equation method, then,
+the eigenvalues are found by searching for the values
+of $k^2$ where the discrete system for the unknown densities
+is no longer invertible.
+
+While integral equation methods for the buckling problem
+have been considered previously, the existing formulations
+have resulted in first kind integral equations, i.e. equations
+in which the operator is compact \cite{kitahara2014boundary,
+  antunes2011buckling}. This is unsatisfying from a theoretical
+perspective, because such operators are never invertible
+(though, they are injective precisely when $k^2$ is an
+eigenvalue \cite{kitahara2014boundary}) so that the
+relation between the non-invertibility of the discrete system
+and the eigenvalues is obscured. Further, such representations
+create numerical challenges because common measures of the
+``non-invertibility'' of a matrix, like the smallest singular
+value or the determinant, converge to zero for all values of
+$k^2$ as the boundary is refined.
+
+Second kind integral equations, i.e. equations in which the
+operator is Fredholm ...
 

### 2018-06-23 doc/draft-01/02prelim.tex
update paper, build out introduction

@@
 
-\subsection{Fundamental solution}
+\subsection{Green's functions}
 
-The fundamental solution of the Helmholtz-Biharmonic equation is
-given by 
+Let $L_x$ denote a linear differential operator. A fundamental
+solution $G(\xx,\yy)$ of $L_x$ satisfies the equation
+$L_x G(\xx,\yy) = \delta_y(\xx)$ in the distributional sense, i.e.
+for sufficiently smooth $f$
 \begin{equation}
-  G_{BH}(\xx,\yy) = -\frac{1}{k^2}
+  L_x \int_{\R^2} G(\xx,\yy) f(\yy) \, dy = f(\xx) \; .
+\end{equation}
+We consider here
+``free-space'' Green's functions, i.e. fundamental solutions which satisfy
+some natural growth or decay conditions as $|\xx-\yy| \to \infty$.
+The Green's function of the Helmholtz-biharmonic equation
+\cref{eq:buck1} is given by 
+\begin{equation}
+  \Gbh(\xx,\yy) = -\frac{1}{k^2}
   \left (\frac{1}{2\pi} \log |\xx-\yy| +
@@
 and $H_{0}^{1}(r)$ is the Hankel function of the first kind of order zero.
+Note that this is a scaled difference of the Green's function for
+Laplace, i.e.
+
+\begin{equation}
+  \Glap(\xx,\yy) = -\frac{1}{2\pi} \log |\xx-\yy| \; ,
+\end{equation}
+and the Green's function for the Helmholtz equation
+
+\begin{equation}
+  \Ghelm(\xx,\yy) = \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \; .
+\end{equation}
 
@@
 \begin{equation}
-  w(\xx) = \int_\Gamma K_1^F (\xx,\yy) \sigma_1(\yy) \, dS(\yy)
-  + \int_\Gamma K_2^F(\xx,\yy) \sigma_2(\yy) \, dS(\yy) \; ,
+  w(\xx) = \int_\Gamma \Kfark_1 (\xx,\yy) \sigma_1(\yy) \, dS(\yy)
+  + \int_\Gamma \Kfark_2(\xx,\yy) \sigma_2(\yy) \, dS(\yy) \; ,
   \label{eq:farkRep}
@@
 
-In \cite{shidongmodbi}, Jiang extended the Farkas formulation for the solution of the modified
+In \cite{jiang2013second}, Jiang extended the Farkas formulation for the solution of the modified
 biharmonic equation, albeit for different boundary conditions. With minor modifications, their formulation
@@
 \begin{align}
-  K_1^F(\xx,\yy) &= \partial_{n_{y}n_{y}n_{y}}\Gbh(\xx,\yy)
+  \Kfark_1(\xx,\yy) &= \partial_{n_{y}n_{y}n_{y}}\Gbh(\xx,\yy)
   + 3 \partial_{n_{y}\tau_{y}\tau_{y}}\Gbh(\xx,\yy) + k^{2} \partial_{n_{y}}\Gbh(\xx,\yy)\; , \label{eq:kf1} \\
-  K_2^F(\xx,\yy) &= -\partial_{n_{y}n_{y}}\Gbh(\xx,\yy)
+  \Kfark_2(\xx,\yy) &= -\partial_{n_{y}n_{y}}\Gbh(\xx,\yy)
   + \partial_{\tau_{y}\tau_{y}}\Gbh(\xx,\yy) \label{eq:kf2} \; .
@@
 \begin{align}
-  K_1^F(\xx,\yy) &=  -\dfrac{\br \cdot \bn(\yy)}{|\br|^2}  \cdot \left( \frac{3 i}{2} H_0^{(1)}(k|\br|) - \frac{5 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{6}{\pi k^2 |\br|^2} + \frac{1}{2\pi}  \right) +     \\
+  \Kfark_1(\xx,\yy) &=  -\dfrac{\br \cdot \bn(\yy)}{|\br|^2}  \cdot \left( \frac{3 i}{2} H_0^{(1)}(k|\br|) - \frac{5 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{6}{\pi k^2 |\br|^2} + \frac{1}{2\pi}  \right) +     \\
   & \quad \dfrac{\left(\br \cdot \bn(\yy)\right)^3}{|\br|^4} \cdot \left( 2i H_0^{(1)}(k|\br|) - \frac{7 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{8}{\pi k^2 |\br|^2}  \right) \, , \nonumber \\
-  K_2^F(\xx,\yy) &=  -\left(\frac{1}{2}-\dfrac{\left(\br \cdot \bn(\yy)\right)^2}{|\br|^2} \right)  \cdot \left( \frac{i}{2} H_0^{(1)}(k|\br|) - \frac{i}{k|\br|} H_1^{(1)}(k|\br|) + \frac{2}{\pi k^2 |\br|^2}  \right)\; .
+  \Kfark_2(\xx,\yy) &=  -\left(\frac{1}{2}-\dfrac{\left(\br \cdot \bn(\yy)\right)^2}{|\br|^2} \right)  \cdot \left( \frac{i}{2} H_0^{(1)}(k|\br|) - \frac{i}{k|\br|} H_1^{(1)}(k|\br|) + \frac{2}{\pi k^2 |\br|^2}  \right)\; .
 \end{align}
@@
     \begin{pmatrix}
-      K_{11}^F(\xx,\yy) & K_{12}^F(\xx,\yy) \\
-      K_{21}^F(\xx,\yy) & K_{22}^F(\xx,\yy)
+      \Kfark_{11}(\xx,\yy) & \Kfark_{12}(\xx,\yy) \\
+      \Kfark_{21}(\xx,\yy) & \Kfark_{22}(\xx,\yy)
     \end{pmatrix}
@@
 The kernels are given
-by $K_{11}^F = K_1^F$, $K_{12}^F = K_2^F$,
+by $\Kfark_{11} = \Kfark_1$, $\Kfark_{12} = \Kfark_2$,
 \begin{align}
-  K_{21}^F(\xx,\yy) &= \left(K_1^F(\xx,\yy)\right )_{n_x} \nonumber \\
+  \Kfark_{21}(\xx,\yy) &= \left(\Kfark_1(\xx,\yy)\right )_{n_x} \nonumber \\
   &= \bn(\xx) \cdot \nabla_{\xx} K_{21}^{F}(\xx,\yy) \; \label{eq:farkK21},\\
-  K_{22}^F(\xx,\yy) &= \left(K_2^F(\xx,\yy)\right )_{n_x} \nonumber \\
+  \Kfark_{22}(\xx,\yy) &= \left(\Kfark_2(\xx,\yy)\right )_{n_x} \nonumber \\
   &= \bn(\xx) \cdot \nabla_{\xx} K_{22}^{F}(\xx,\yy) \label{eq:farkK22} \; .
@@
 \begin{proof}
-The proof is a minor modification of the one presented in~\ref{eq:shidongmodbi} and is contained in~\cref{sec:app}.
+  The proof is a minor modification of the one presented in~\ref{eq:shidongmodbi}
+  and is contained in~\cref{sec:farkproof}.
 \end{proof}
 
-The kernels $K^F_1$ and $K^F_2$ are
-constructed with the goal that the $K^F_{ij}$ are
+The kernels $\Kfark_1$ and $\Kfark_2$ are
+constructed with the goal that the $\Kfark_{ij}$ are
 as smooth as possible. Suppose that the boundary
 $\Gamma$ is of class $C^k$. Then, the kernels,
-$K^F_{ij}(\xx,\yy)$, are $C^{k-2}$ functions on the boundary
+$\Kfark_{ij}(\xx,\yy)$, are $C^{k-2}$ functions on the boundary
 for each $\yy \in \Gamma$.
@@
 domain with a corner, we note 
-that the kernel $K_{21}^F$
+that the kernel $\Kfark_{21}$
 has a singularity with strength $r^{-2}$ (see~\cref{fig:ker21plot}). 
@@
 
-\subsection{Helmholtz-Stokes flow in a plane}
+\subsection{An integral representation for the Stokes eigenvalue
+  problem}
+
+The Stokes eigenvalue problem (with ``no-slip'' boundary conditions)
+seeks values $k^2$ such that the equations
+\begin{align}
+  \nabla p - \Delta \uu - k^2 \uu &= 0 \quad \textrm{in} \quad \Omega
+  \; , \label{eq:helmstokes}\\
+  \nabla \cdot \uu &= 0 \quad \textrm{in} \quad \Omega
+  \; , \label{eq:helmstokescty} \\
+  \uu &= 0 \quad \textrm{on} \quad \Gamma \; \label{eq:helmstokesnoslip}
+\end{align}
+have a non-trivial solution. In the case that $k=i\alpha$ for
+some real-valued $\alpha$, the equations \cref{eq:helmstokes,eq:helmstokescty}
+are known as the modified Stokes equations and are of particular
+interest for their application to numerical simulations of unsteady
+flow
+\cite{pozrikidis1992boundary,biros2002embedded,jiang2013second}.
+In the absence of a preferred name for the case of real-valued $k$,
+we will refer to \cref{eq:helmstokes,eq:helmstokescty} as the
+Helmholtz-Stokes equations.
+
+\subsubsection{Stokeslets and stresslets}
 
@@
 modified Stokeslet, but for the imaginary parameter
-regime --- which we will call the Helmholtz Stokeslet ---
-which is the appropriate setting for the Stokes
+regime, which is the appropriate setting for the Stokes
 eigenvalue problem.
@@
 
-To begin, we restate the Stokes eigenvalue
-problem as
-\begin{align}
-  \nabla p - \Delta \uu - k^2 \uu &= 0 \; , \label{eq:helmstokes}\\
-  \nabla \cdot \uu &= 0 \; . \label{eq:helmstokescty}
-\end{align}
-Consider the solution of this problem where a
-$\delta$ centered at $\yy$ with strength $\ff$
-has been added to the right-hand side, i.e.
+ Consider the solution of
+\cref{eq:helmstokes,eq:helmstokescty} where a $\delta$-mass
+centered at $\yy$ with strength $\ff$
+has been added to the right-hand side of \cref{eq:helmstokes}, i.e.
 
@@
 \end{align}
-Note that
+Recall that
 
 \begin{equation}
-  \Delta G_L(\xx,\yy) = \delta_\yy(\xx) \; .
+  \Delta \Glap(\xx,\yy) = \delta_\yy(\xx) \; .
 \end{equation}
@@
 \begin{equation}
-  p = \nabla G_L(\xx,\yy) \cdot \ff \; .
+  p = \nabla \Glap(\xx,\yy) \cdot \ff \; .
 \end{equation}
@@
 \begin{align}
-  \uu &= - (\Delta + k^2)^{-1} ( \Delta G_L \ff
-  - \nabla (\nabla G_L \cdot \ff ) ) \\
+  \uu &= - (\Delta + k^2)^{-1} ( \Delta \Glap \ff
+  - \nabla (\nabla \Glap \cdot \ff ) ) \\
   &= \left ( -\Delta + \nabla \otimes \nabla \right )
-  G_{BH} \ff \; .
+  \Gbh \ff \; .
 \end{align}
@@
 \begin{equation}
-  \GG = - \II \Delta G_{BH} + \nabla \otimes \nabla G_{BH}
+  \GG = - \II \Delta \Gbh + \nabla \otimes \nabla \Gbh
 \end{equation}
@@
 \begin{align}
-  T_{ijk} &= - \partial_{x_j} G_L \delta_{ik}
-  + \partial_{x_k} \left ( -\Delta G_{BH} \delta_{ij} +
-  \partial_{x_i} \left(\partial_{x_j} G_{BH} \right) \right)
+  T_{ijk} &= - \partial_{x_j} \Glap \delta_{ik}
+  + \partial_{x_k} \left ( -\Delta \Gbh \delta_{ij} +
+  \partial_{x_i} \left(\partial_{x_j} \Gbh \right) \right)
   \nonumber \\
-  & \qquad+ \partial_{x_i} \left ( -\Delta G_{BH} \delta_{kj} +
-  \partial_{x_k} \left(\partial_{x_j} G_{BH} \right) \right)
+  & \qquad+ \partial_{x_i} \left ( -\Delta \Gbh \delta_{kj} +
+  \partial_{x_k} \left(\partial_{x_j} \Gbh \right) \right)
   \; .
 \end{align}
-Let $u_i = G_{ij} f_j$ and $p = \partial_{x_i} G_L f_i$ be a
+Let $u_i = G_{ij} f_j$ and $p = \partial_{x_i} \Glap f_i$ be a
 solution of the Stokes equations induced by a Stokeslet.
@@
 \begin{equation}
-  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla G_L
-  + \partial_\nu \left ( -\Delta G_{BH} \II
-  + \nabla \otimes \nabla G_{BH} \right)
-  + \nabla \otimes \left ( -\Delta G_{BH} \bnu
-  + \partial_{\nu} \nabla G_{BH} \right) \; .
+  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla \Glap
+  + \partial_\nu \left ( -\Delta \Gbh \II
+  + \nabla \otimes \nabla \Gbh \right)
+  + \nabla \otimes \left ( -\Delta \Gbh \bnu
+  + \partial_{\nu} \nabla \Gbh \right) \; .
 \end{equation}
 %\begin{align}
-% -\Delta G_{BH} \bnu
-% + \partial_{\nu} \nabla G_{BH} &=
-% ( (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_1 G_{BH} +
-% (\partial_{x_1x_1}\nu_1 + \partial_{x_2x_1} \nu_2 )G_{BH},
-% (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_2 G_{BH} +
-% (\partial_{x_1x_2}\nu_1 + \partial_{x_2x_2} \nu_2 )G_{BH}) \\
-% &= (-\partial_{x_2} \partial_\tau G_{BH},
-% \partial_{x_1} \partial_\tau G_{BH})
+% -\Delta \Gbh \bnu
+% + \partial_{\nu} \nabla \Gbh &=
+% ( (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_1 \Gbh +
+% (\partial_{x_1x_1}\nu_1 + \partial_{x_2x_1} \nu_2 )\Gbh,
+% (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_2 \Gbh +
+% (\partial_{x_1x_2}\nu_1 + \partial_{x_2x_2} \nu_2 )\Gbh) \\
+% &= (-\partial_{x_2} \partial_\tau \Gbh,
+% \partial_{x_1} \partial_\tau \Gbh)
 %\end{align}
@@
 \begin{equation}
-  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla G_L
-  - \nabla^\bot \otimes \nabla^\bot \partial_\nu G_{BH}
-  +\nabla \otimes \nabla^\bot \partial_\tau G_{BH} \; .
+  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla \Glap
+  - \nabla^\bot \otimes \nabla^\bot \partial_\nu \Gbh
+  +\nabla \otimes \nabla^\bot \partial_\tau \Gbh \; .
 \end{equation}
 
-\subsection{Layer potentials}
+\subsubsection{Layer potentials and integral representation}
 
@@
   \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy) \right )^\intercal
-  \bmu(\yy) &= \left ( - \nabla G_L(\xx,\yy) + 2 \nabla^\bot
-  \partial_{\nu\tau} G_{BH}(\xx,\yy) \right ) \mu_\nu(\yy) \nonumber \\
+  \bmu(\yy) &= \left ( - \nabla \Glap(\xx,\yy) + 2 \nabla^\bot
+  \partial_{\nu\tau} \Gbh(\xx,\yy) \right ) \mu_\nu(\yy) \nonumber \\
   & \qquad+
   \nabla^\bot \left (\partial_{\tau\tau}-\partial_{\nu\nu} \right )
-  G_{BH}(\xx,\yy) \mu_\tau(\yy) \; .
+  \Gbh(\xx,\yy) \mu_\tau(\yy) \; .
 \end{align}
-
-\subsection{The Farkas integral representation}
-
-As mentioned in the introduction, there are existing 
-integral representations for the solution of the Dirichlet problem for the Helmholtz-biharmonic equation
-\begin{align}
- \Delta (\Delta + k^2) w &= 0 \mbox{ in } D \; , \label{eq:biharmD1}\\
- w &= f \mbox{ on }
- \Gamma \label{eq:biharmD2} \; , \\ 
- \frac{\partial w}{\partial n} &= g \mbox{ on } 
- \Gamma \, , \label{eq:biharmD3}
-\end{align}
-In \cite{Farkas89}, 
-the solution is given as the sum of two layer potentials, i.e.
-where $\sigma_1$ and $\sigma_2$ are unknown densities.
-
-The integral kernels, $K_1^F$ and $K_2^F$ are based on
-derivatives of the Green's function for the biharmonic equation.

### 2018-06-24 doc/draft-01/01intro.tex
in which our hero updates the introduction and adds some references

@@
 
+\begin{remark}
+  When $k = i\alpha$, the differential equation
+  \cref{eq:buck1} is known as the modified biharmonic
+  equation. As there appears to be no preferred
+  name for the equation with real-valued $k$,
+  we will refer to \cref{eq:buck1} as the
+  Helmholtz-biharmonic equation.
+\end{remark}
+
 The eigenvalues (and eigenfunctions)
@@
 Numerical simulations have long played an important
-in the analyses described above and there are a number
+role in the analyses described above and there are a number
 of available methods (note that some of the references
@@
 are ubiquitous in mechanical engineering applications
-and are flexible both with respect to the governing
+and are flexible with respect to both the governing
 equations and the shape of the domain. Such a method
@@
 discretization can have large condition numbers (growing
-like $h^4$ where $h$ is the diameter of a typical element
+like $1/h^4$ where $h$ is the diameter of a typical element
 in the discretization) which can cause numerical instability.
@@
 representation into the boundary conditions
-\cref{eq:buck2,buck3} results in an integral equation
+\cref{eq:buck2,eq:buck3} results in an integral equation
 for the unknown densities, which
@@
 ``non-invertibility'' of a matrix, like the smallest singular
-value or the determinant, converge to zero for all values of
-$k^2$ as the boundary is refined.
+value or the determinant, converge rapidly to zero for all
+values of $k^2$ as the boundary is refined.
 
-Second kind integral equations, i.e. equations in which the
-operator is Fredholm ...
+Second kind integral equations, i.e. integral equations
+of the form $\mathcal{I} + \mathcal{K}$ where $\mathcal{K}$
+is compact, have a more satisfying theory
+\cite{reed1972methods}, which translates
+well to numerical implementation
+\cite{bornemann2010numerical,zhao2015robust}.
+In \cite{zhao2015robust}, Zhao and Barnett demonstrated
+that the eigenvalues of the drum problem can be
+computed with such a framework, resulting in
+spectrally accurate numerical methods.
+In this paper, we develop a second kind integral
+equation for the buckling problem, based on the
+approach in \cite{rachh2017integral}. This allows
+for a robust approach to computing the eigenvalues
+of the buckling problem, model after the approach for
+the drum problem in \cite{zhao2015robust}, which we
+demonstrate with a number of examples.
 
-\begin{remark}
-  When $k = i\alpha$, the differential equation
-  \cref{eq:buck1} is known as the modified biharmonic
-  equation. As there appears to be no preferred
-  name for the equation with real-valued $k$,
-  we will refer to \cref{eq:buck1} as the
-  Helmholtz-biharmonic equation.
-\end{remark}
+The rest of this paper is organized as follows ...

### 2018-07-12 doc/draft-01/01intro.tex

@@
 value or the determinant, converge rapidly to zero for all
-values of $k^2$ as the boundary is refined.
+values of $k^2$ as the boundary is refined. Therefore, the
+measure of whether $k^2$ is an approximate eigenvalue is
+{\em relative to the current grid} for first kind equations.
 
@@
 is compact, have a more satisfying theory
-\cite{reed1972methods}, which translates
-well to numerical implementation
-\cite{bornemann2010numerical,zhao2015robust}.
+\cite{reed1972methods,kress1989linear},
+which translates well to numerical implementation
+\cite{atkinson2009numerical,bornemann2010numerical,
+  hackbusch2012integral,zhao2015robust}. Two facts are
+of particular importance here: with an appropriately
+chosen representation, (a) the Fredholm determinant of the
+integral equation will be a well-defined analytic function
+of $k^2$ with zeros precisely at the eigenvalues and (b) the 
+determinant of the matrix resulting from
+a Nystr\"{o}m discretization of the integral equation
+will converge to the Fredholm determinant of the operator
+\cite{bornemann2010numerical}.
 In \cite{zhao2015robust}, Zhao and Barnett demonstrated
@@
 computed with such a framework, resulting in
-spectrally accurate numerical methods.
+methods which are spectrally accurate with respect
+to both the sampling of the boundary and the sampling
+in $k^2$. There are natural extensions of existing second
+kind integral
+equations for the biharmonic \cite{farkas1989mathematical}
+and modified biharmonic \cite{jiang2013second} equations
+which would be appropriate for the buckling problem, but
+these representations suffer from instability for
+high curvature domains, limiting their applicability
+\cite{rachh2017integral}.
 In this paper, we develop a second kind integral
-equation for the buckling problem, based on the
-approach in \cite{rachh2017integral}. This allows
+equation for the buckling problem based on Stokeslet
+and stresslet inspired kernels, as was done for the
+$k=0$ case in \cite{rachh2017integral}. This allows
 for a robust approach to computing the eigenvalues
-of the buckling problem, model after the approach for
+of the buckling problem, modeled after the approach for
 the drum problem in \cite{zhao2015robust}, which we
-demonstrate with a number of examples.
+demonstrate with a number of examples from the
+literature.
 

### 2018-07-12 doc/draft-01/08append.tex

\appendix

\section{Proof of the invertibility of the Farkas representation}
\label{sec:farkproof}

### 2018-07-12 doc/draft-01/08append.tex
Updating appendix A

@@
 \section{Proof of the invertibility of the Farkas representation}
+In this appendix, we prove~\cref{lem:farkinv} which is restated here
+as~\cref{lem:farkinv_app}.
+
+In the following lemma, we present an integral indentity involving the
+Green's function of the Helmholtz-biharmonic equation.
+\begin{lem}
+Suppose that $\Gbh$ is the Green's function of the Helmholtz-biharmonic equation 
+with Helmholtz parameter $k$. Suppose that $v:\R^{2} \to \R$ is a compactly supported smooth
+function. Then
+\begin{equation}
+\int_{\R^{2}} \Gbh(\xx,\yy) \Delta (\Delta + k^2) v(\yy) d\yy = v(\xx)
+\end{equation}
+\end{lem}
+\begin{proof}
+Suppose that $r>0$. 
+Let $B_{r}(\xx)$ denote the ball of radius $r$ centered at the origin
+and let $\partial B_{r}(\xx)$ denote its boundary.
+Then applying Green's second identity twice, we get 
+\begin{align}
+\int_{\R^{2} \setminus B_{r}(\xx)} \Gbh(\xx,\yy) \Delta (\Delta +k^{2}) v(\yy)
+&=
+\int_{\R^{2} \setminus B_{r}(\xx)} \Delta \Gbh (\xx,\yy) (\Delta + k^2) 
+v(\yy) + \\
+& \hspace{5ex}\int_{\partial B_{r}(\xx)} \Gbh(\xx,\yy) (\Delta + k^{2})
+\frac{\partial}{\partial n}v(\yy) \, dS - \\
+& \hspace{5ex}\int_{\partial B_{r}(\xx)} \frac{\partial }{\partial n} \Gbh(\xx,\yy) 
+(\Delta + k^2) v \, dS \\
+&= \int_{\R^{2} \setminus B_{r}(\xx)} \Delta (\Delta + k^2)G(\xx,\yy) v(\yy)
+d\yy  - \nonumber \\
+& \hspace{5ex}\int_{\partial B_{r}(\xx)} (\Delta + k^2) 
+\frac{\partial }{\partial n} \Gbh(\xx,\yy) v \, dS + \nonumber\\
+& \hspace{5ex}\int_{\partial B_{r}(\xx)} (\Delta + k^2) 
+\Gbh(\xx,\yy) \frac{\partial}{\partial n}v \, dS - \nonumber \\
+& \hspace{5ex}\int_{\partial B_{r}(\xx)}  
+\frac{\partial }{\partial n} \Gbh(\xx,\yy) \Delta v\, dS + \\
+& \hspace{5ex}
+\int_{\partial B_{r}(\xx)} \Gbh(\xx,\yy) \Delta \frac{\partial v}{\partial n}
+\, dS \nonumber
+\end{align}
+For all $\yy \in \partial B_{r}(x)$, there exists a constant $C$ such that
+$\Gbh$ satisfies the following equations
+\begin{align}
+(\Delta + k^2) \frac{\partial }{\partial n} G(\xx,\yy) &= 
+-\frac{1}{2\pi r} \label{eq:estapp1}\\
+\left|(\Delta + k^2) G(\xx,\yy) \right| &\leq C \log{(r)} \label{eq:estapp2}\\
+\left|\frac{\partial }{\partial n} G(\xx,\yy) \right| &\leq C r\log{(r)} 
+\label{eq:estapp3}\\
+\left| G(\xx,\yy) \right| &\leq C r^{2} \log{(r)} \label{eq:estapp4}\, .
+\end{align}
+Furthermore, $\Gbh$ satisfies $\Delta (\Delta + k^2) \Gbh(\xx,\yy) = 0$
+for all $\yy \in \R^{2} \setminus B_{r}(\xx)$.
+Using the estimates in~\cref{eq:estapp1,eq:estapp2,eq:estapp3,eq:estapp4}, 
+and the smoothness of $v$, we get
+\begin{equation}
+\int_{\R^{2} \setminus B_{r}(\xx)} \Gbh(\xx,\yy) \Delta (\Delta + k^2) v(\yy) 
+d \yy = \frac{1}{2\pi r} \int_{\partial B_{r}(\xx)} v(\yy) dS + 
+O(r \log(r)) \, \label{eq:estapp5}.
+\end{equation}
+The result then follows by taking the limit $r\to 0$ in~\cref{eq:estapp5}. 
+\end{proof}
 \label{sec:farkproof}

### 2018-08-02 doc/draft-01/05numerics.tex
Updating paper

\section{Numerical methods}
Recall that we compute the buckling eigenmodes via computing the zeros
of the determinant of linear system corresponding to a Nystr\"{o}m 
discretization of the integral operator $A(k)$ in~\cref{eq:inteqfinal}.
As in section~\cref{sec:spec}, let $\tilde{A}_{k}$ denote the discretized
linear system.
Thus, the three main ingredients for the fast and accurate computation
of buckling eigenvalues (and its corresponding eigenfunctions) are
high order Nystr\"{o}m discretizations of the integral operator 
$A(k)$; for a given parameter $k$, the rapid evaluation of the determinant 
$\tilde{A}_{k}$; and finding the zeros of $\text{det}(\tilde{A}_{k})$ (which
is non-linear in $k$) while minimizing the function evaluations.

For discretizing the integral operator using the
Nystr\"{o}m method, we divide the boundary $\Gamma$ into
panels and represent the unknown density and the
boundary data by their values at scaled Gauss-Legendre
nodes on each panel. 
Let $n_{p}$ denote the number of Gauss-Legendre panels.
We discretize each panel using 16 scaled Gauss-Legendre nodes.
Then $n_{d} = 16 n_{p}$ is the number of discretization points 
on the boundary.
Let $\bx_{j}$ denote the discretization nodes, $w_{j}$ denote the
appropriately scaled Gauss-Legendre quadrature weights for smooth functions,
and $\bmu_{j}$ denote the unknown density at $\bx_{j}$.
When forming the linear system, we use scaled unknowns, 
$\bmu_{j} \sqrt{w_{j}}$, so that the spectral properties of the 
discrete system with respect to the $l_2$ norm
are approximations of the spectral properties of the continuous
system as on operator on $L_2$ (for more on this point of view, 
see \cite{bremer2012}).
The integral kernels $K_{ij}$ in~\cref{eq:inteqfinal} 
are either smooth or have a weak (logarithmic) singularity. 
For the smooth kernels, we use standard 
Gauss-Legendre quadrature rule.
For kernels with a logarithmic singularity, we use order $20$ 
generalized Gaussian quadrature rule~\cite{bremer2010,bremer2010u}.
Note that the resulting discretized linear system $\tilde{A}_{k}$ 
is a dense matrix of size $M=2n_{d}+N+1$, 
where $N$ is the number of connected components.

For small problems ($M \leq 10^3$), we directly compute
$\text{det}(\tilde{A}_{k})$ using standard linear algebra routines
from LAPACK. 
However, since the matrix $\tilde{A}_{k}$ is dense,
the computational complexity of computing $\text{det}(\tilde{A}_{k})$ 
using LAPACK routines is $O(M^3)$.
Moreover, for evaluating the buckling eigenmodes, $\text{det}(\tilde{A}_{k})$
must be evaluated for many different values of $k$.
Thus, for larger problems, we use the HIFIE method for evaluating
$\text{det}(\tilde{A}_{k})$. 
This method exploits the rank structure of $\tilde{A}_{k}$ (large blocks
of $\tilde{A}_{k}$ corresponding to interactions between well-separated
clusters are low-rank) and evaluates the determinant in O($M \cdot \log{M})$ 
CPU-time.

### 2018-08-16 doc/draft-01/08append.tex
Updating appendix

@@
 \label{sec:farkproof}
+
+\section{Proof of invertibility of new representation}
+The proof proceeds as follows:
+\begin{itemize}
+\item Show uniqueness of solutions to the impedence, velocity, and surface
+traction boundary value problem in exterior domains for the Stokes-Helmholtz
+PDEs. In order to prove this, we need the following lemmas:
+\begin{itemize}
+\item Deriving Green's theorem for exterior domains
+\item Rellich's lemma
+\item Uniqueness proof
+\end{itemize}
+\item The proof for the clamped plate problem proceeds in the manner
+analogous to the Dirichlet biharmonic paper.
+\end{itemize}
+
+With this in mind, we first discuss the PDE theory for the impedence, 
+velocity and surface traction boundary value problems on unbounded
+domains for the Stokes-Helmholtz equation.
+We focus on the proof for the velocity boundary value problem. 
+The proofs for the surface traction and impedence problems is similar.
+
+Suppose that $\Omega$ is a bounded simply connected domain and that
+$E = \R^{2} \setminus \Omega$ is its exterior.
+Let $\Gamma = \partial \Omega$ denote the boundary of $E$.
+For a given function $\bh$ on the boundary, 
+the exterior velocity boundary value problem is given by:
+\begin{align}
+\Delta \bu + \omega^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
+\nabla \cdot \bu &= 0 \quad \bx \in E \, ,\\
+\bu &= \bh \quad \bx \in \Gamma \, . \\
+\end{align}
+Let $\sigma$ denote the stress tensor associated with the velocity
+field $\bu$, i.e.
+\begin{equation}
+\sigma = -p I + e(\bu) \, ,
+\end{equation}
+where $e(\bu)$ is the strain tensor given by
+\begin{equation}
+e(\bu) = D\bu + D\bu^{T} \, .
+\end{equation}
+Let $\bn$ denote the outward normal to the boundary $\Gamma$, then
+the surface traction $\ff$ on the boundary $\Gamma$ is given 
+by
+\begin{equation}
+\ff = \sigma \cdot \bn
+\end{equation}
+Analogous to the Helmholtz equation, we need to impose radiation conditions
+at $\infty$.
+We propose the following radiation conditions for the Stokes-Helmholtz 
+equation
+\begin{equation}
+\lim_{r\to \infty} \sqrt{r} \left| \ff - i \omega \bu \right| \to 0 \, ,
+\label{eq:radcond}
+\end{equation}
+uniformly in direction.
+
+\begin{lem}
+\label{lem:rep}
+Suppose that $\bu$ satisfies the Stokes-Helmholtz equation in 
+an unbounded region $E$ along with the radiaition 
+condition~\cref{eq:radcond}. 
+Then 
+\begin{equation}
+\label{eq:repinfest}
+\lim_{r\to\infty}
+\int_{|\by|=r} \left( |\ff|^2 + |\omega|^2 |\bu|^2 \right) ds +
+2 \text{Im}(\omega) \int_{E \cap B_{r}(0)} \left(|\omega|^2 |\bu|^2 + |e(\bu)|^2 \right)
+dV = -2 \text{Im} \left( \omega \int_{\Gamma} \bu \cdot \overline{\ff} ds  \right)
+\end{equation}
+\end{lem}
+
+\begin{proof}
+Since $\bu$ satisfies the radiation condition, we have that
+\begin{equation}
+\lim_{r\to\infty} \int_{|\by|=r} | \ff - i \omega \bu|^2 ds = 
+\lim_{r\to\infty} \int_{|\by| =r} \left( |\ff|^2 + |\omega|^2|\bu|^2 + 2 \text{Im} 
+\left( \omega \bu\cdot \ff \right) ds \label{eq:raddecayproof1}
+\right) = 0 \, . 
+\end{equation}
+Since $\bu$ satisfies the Stokes-Helmholtz equation $E \cap B_{r}(0)$,
+using a couple of applications of the divergence theorem, we have that
+\begin{equation}
+\int_{E\cap B_{r}(0)} |e(\bu)|^2 dV = -\int_{\Gamma} \bu \cdot \overline{\ff} ds
++ \int_{|\by|=r} \bu \cdot \overline{\ff} ds + \overline{\omega}^2 
+\int_{E \cap B_{r}(0)} |\bu|^2 dV \,. \label{eq:raddecayproof2}
+\end{equation}
+Combining~\cref{eq:raddecayproof1,eq:raddecayproof2}, we get
+\begin{equation}
+\lim_{r\to\infty} \int_{|\by|=r}\left(|\ff|^2 + |\omega|^2 |\bu|^2 \right) ds 
++ 2\text{Im}(k)\int_{E \cap B_{r}(0)} \left(|e(\bu)|^2 + |\omega|^2 |\bu|^2 
+\right) dV = -2\text{Im} \int_{\Gamma} \omega \bu \cdot \overline{\ff} dS \, .
+\end{equation}
+\end{proof}
+
+In the next lemma, we prove the analogue of Rellich's lemma for the Stokes-
+Helmholtz equation. 
+\begin{lem}
+\label{lem:rellich}
+Suppose that $\bu$ satisfies the Stokes-Helmholtz equation in an unbounded
+region $E$.  
+Suppose further that 
+\begin{equation}
+\lim_{r \to \infty} \int_{|\by|=r} |\bu|^2 dS = 0 
+\, . \label{eq:decayatinf}
+\end{equation}
+Then each component of $\bu$ is harmonic and has a convergent Laurent
+expansion in $E$.
+\end{lem}
+\begin{proof}
+We first note that each component of $\bu= (u_{1},u_{2})$ satisfies the 
+Helmholtz-Biharmonic equation in $E$, i.e.
+\begin{equation}
+\Delta (\Delta + \omega^2) u_{j} = 0 \quad j=1,2 \,. 
+\end{equation}
+For $r$ sufficiently large, we can express $u_{j}$ in the Fourier basis as
+\begin{equation}
+u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} a_{j,n}(r) e^{i n \theta}  \quad 
+j=1,2 \, .
+\end{equation}
+Using Parseval's identity then
+\begin{equation}
+\int_{|\by|=r} |\bu|^2 ds = r\sum_{n=-\infty}^{\infty} |a_{1,n}(r)|^2  +
+|a_{2,n}(r)|^2 \, .
+\end{equation}
+Since $\bu$ satisfies~\cref{eq:decayatinf}, we conclude that
+\begin{equation}
+\lim_{r\to\infty} r|a_{j,n}(r)|^2 = 0 \quad j=1,2 \, , \label{eq:adecay}
+\end{equation}
+Since $u_{j}$, $j=1,2$ satisfies the Helmholtz-biharmonic equation,
+the functions $a_{j,n}$ are linear combinations of 
+\begin{equation}
+r^{|n|}, r^{-|n|}, H^{1}_{n}(\omega r), H^{2}_{n}(\omega r) \, , \quad
+n\neq 0 \, ,
+\end{equation}
+and
+\begin{equation}
+1, \log{(r)}, H^{1}_{0}(\omega r), H^{2}_{0}(\omega r) \quad n=0 \, , 
+\end{equation} 
+where $H_{n}^{1,2}(\cdot)$ are the Hankel functions of the first and
+second kind of order $n$.
+Since $a_{j,n}(r)$ satisfy~\cref{eq:adecay}, and using the asymptotic 
+expansion of $H_{n}^{1,2}(r)$, we note that the projection of 
+$a_{j,n}$ on $r^{|n|}$, and $H_{n}^{j}(\omega r)$ must be zero. 
+Thus, 
+\begin{equation}
+u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} \frac{a_{j,n} e^{i n \theta}}{r^{|n|}} 
+\, .
+\end{equation}
+\end{proof}
+\begin{remark}
+Note that each component of $\bu$ is harmonic and thus $\bu$ then satisfies
+\begin{align}
+\omega^2 \bu &= \nabla p  \quad \label{eq:massconsred} \\
+\nabla \cdot \bu &= 0 \, .
+\end{align}
+Taking the inner product with $\nabla^{\perp}$ in~\cref{eq:massconsred}, 
+we note that $\bu$ satisfies both $\nabla^{\perp} \cdot \bu = 0$ 
+and $\nabla \cdot \bu = 0$.
+This remark will be useful for the impedence problem...
+\end{remark}
+\begin{remark}
+Note that in Rellich's lemma $\bu$ need not be a radiating solution. 
+All we know of $\bu$ is that it satifies the PDE in $E$.
+\end{remark}
+
+\begin{thm}
+(Uniqueness Dirichlet)
+Suppose that $\text{Im}(\omega)>0$ and 
+that $\bu$ is a radiating solution to the Stokes-Helmholtz
+equation in $E$ with $\bu =0$ on the boundary $\Gamma$, then
+$u \equiv 0$ in $E$.
+\end{thm}
+
+\begin{proof}
+Since $\bu = 0$ on $\Gamma$, it follows from~\cref{eq:repinfest} that
+\begin{equation}
+\lim_{r\to\infty}
+\int_{|\by|=r} \left( |\ff|^2 + |\omega|^2 |\bu|^2 \right) ds +
+2 \text{Im}(\omega) \int_{E \cap B_{r}(0)} \left(|\omega|^2 |\bu|^2 + |e(\bu)|^2 \right)
+dV = 0
+\end{equation} 
+In particular, this implies that
+\begin{equation}
+\lim_{r\to\infty} \int_{|\by|=r} |\bu|^2 ds = 0 \, .
+\end{equation}
+Thus, the conditions for $\bu$ in Rellich's lemma (~\cref{lem:rellich})
+are satisfied, and each component of $\bu$ is a harmonic function
+with $\bu \to 0$ as $r \to \infty$. Furthermore, since $\bu=0$ on
+$\Gamma$, from uniqueness of solutions to the Dirichlet problem
+on exterior domains, we conclude that $\bu \equiv 0$ in $E$.
+\end{proof}
+
+The proof for the Neumann problem proceeds in a similar manner.

### 2018-08-16 doc/draft-01/08append2.tex
Updating appendix

--- 2018-08-16 doc/draft-01/08append.tex
@@
 \begin{equation}
-e(\bu) = D\bu + D\bu^{T} \, .
+e(\bu) = \frac{1}{2}\left(D\bu + D\bu^{T} \right) \, .
 \end{equation}
@@
 using a couple of applications of the divergence theorem, we have that
-\begin{equation}
-\int_{E\cap B_{r}(0)} |e(\bu)|^2 dV = -\int_{\Gamma} \bu \cdot \overline{\ff} ds
+\begin{align}
+\int_{E\cap B_{r}(0)} |e(\bu)|^2 dV &= \int_{E\cap B_{r}(0)} \left< e(\bu), \overline{e(\bu)} \right> dV  \\
+&= \frac{1}{2}\left(\int_{E\cap B_{r}(0)} \left< e(\bu),\overline{D\bu} \right> + \left< e(\bu),\overline{D\bu}^{T} \right> \right) dV \\
+&= \int_{E\cap B_{r}(0)} \left< e(\bu),\overline{D\bu} \right> dV \\
+&= \int_{\partial }
+-\int_{\Gamma} \bu \cdot \overline{\ff} ds
 + \int_{|\by|=r} \bu \cdot \overline{\ff} ds + \overline{\omega}^2 
@@
 (Uniqueness Dirichlet)
-Suppose that $\text{Im}(\omega)>0$ and 
+Suppose that $\text{Im}(\omega)\geq 0$ and 
 that $\bu$ is a radiating solution to the Stokes-Helmholtz

### 2018-08-16 doc/draft-01/08append.tex
Adding mathematica notebook and appending appendix for estimate on  radiaiton condition

@@
 The proof for the Neumann problem proceeds in a similar manner.
+
+\begin{lem}
+If $\bu = \nabla^{\perp} H_{0}(\omega r)$ and $p\to 0$ as $r\to \infty$, 
+then
+\begin{equation}
+\lim_{r\to \inf} \sqrt(r) \left(\ff_{1} - i\omega \bu_{1} \right) = 0 \, .
+\end{equation}
+\end{lem}
+
+\begin{proof}
+If $\bu = \nabla^{\perp} H_{0}(\omega r) = (\partial_{y} H_{0}(\omega r), 
+-\partial_{x} H_{0}(\omega r))$, then
+\begin{equation}
+\nabla  p = (\Delta + \omega^2) \bu = (\Delta + \omega^2) \nabla^{\perp} 
+H_{0} (\omega r) = 0 \, .
+\end{equation}
+Since $p\to 0$ as $r\to \infty$, we conclude that $p=0$.
+\begin{align}
+\ff_{1} &= 2\partial_{x} u_{1} \cos(\theta) + \left( \partial_{x} u_{2} + 
+\partial_{y} u_{1} \right) \sin(\theta) \\
+&= 2 \partial_{xy} H_{0}(\omega r) \cdot \frac{x}{r} +
+\left[-\partial_{xx} H_{0}(\omega r) + \partial_{yy} H_{0}(\omega r) \right]
+\cdot \frac{y}{r} \, .
+\end{align}
+Based on the mathematica script (radcond1.nb in our mathematica folder), we
+get
+\begin{equation}
+\ff_{1} - i \omega u_{1} = \frac{ky}{r^2} \left( -kr \left(H_{0}(\omega r) + 
+i H_{1}(\omega r)\right) +
+2 H_{1}(\omega r)\right) \, .
+\end{equation}
+The result then follows from the asymptotic properties of Hankel functions since
+\begin{equation}
+H_{0}(z) = c \frac{e^{-iz}}{\sqrt{z}} + O(\frac{1}{z^{3/2}}) \quad 
+\text{and} \quad 
+H_{1}(z) = i \cdot c \frac{e^{-iz}}{\sqrt{z}} + O(\frac{1}{z^{3/2}}) \,,
+\end{equation}
+where $c$ is the same constant in both of these expansions.
+\end{proof}

### 2018-08-18 doc/draft-01/08append.tex
update text, add proof of radiation condition

--- 2018-08-16 doc/draft-01/08append.tex
@@
 \begin{align}
-\Delta \bu + \omega^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
+\Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
 \nabla \cdot \bu &= 0 \quad \bx \in E \, ,\\
@@
 \end{align}
-Let $\sigma$ denote the stress tensor associated with the velocity
+Let $\bsigma$ denote the stress tensor associated with the velocity
 field $\bu$, i.e.
 \begin{equation}
-\sigma = -p I + e(\bu) \, ,
+\bsigma = -p \II + \be(\bu) \, ,
 \end{equation}
-where $e(\bu)$ is the strain tensor given by
+where $\be(\bu)$ is the strain tensor given by
 \begin{equation}
-e(\bu) = D\bu + D\bu^{T} \, .
+e_{ij}(\bu) = \left( \partial_{x_j} u_i + \partial_{x_i} u_j \right)
 \end{equation}
@@
 equation
+
+\begin{definition}
+Let $(\bu,p)$ satisfy the Stokes-Helmholtz equations in
+the exterior of a bounded domain. We say that
+the pair $(\bu,p)$ satisfies the radiation condition if
+$p$ is bounded, $p \to 0$ as $\xx \to \infty$, and 
 \begin{equation}
-\lim_{r\to \infty} \sqrt{r} \left| \ff - i \omega \bu \right| \to 0 \, ,
+\lim_{r\to \infty} \sqrt{r} \left| \ff - i k \bu \right| \to 0 \, ,
 \label{eq:radcond}
@@
 uniformly in direction.
+\end{definition}
+
+\begin{proposition}
+Both the Helmholtz-Stokeslet \eqref{eq:stokeslet} and the
+kernel of the Helmholtz-Stokes double layer potential
+\eqref{eq:stokesdlkernel} satisfy the radiation condition
+\eqref{eq:radcond}.
+\end{proposition}
+
+\begin{proof}
+Without loss of generality, we assume that these
+kernels are centered at the origin. Let $r = |\xx|$.
+Consider the Stokeslet induced by an arbitrary charge
+$k^2 \bmu$. We have
+
+\begin{align}
+\bu (\xx) &= k^2 \GG(\xx,0) \bmu \\
+&= k^2 \left (-\II \Delta \Gbh(\xx,0)
++ \nabla \otimes \nabla \Gbh(\xx,0)\right ) \bmu \\
+&= -k^2 \left (\nabla^\perp \otimes \nabla^\perp \Gbh(\xx,0) \right) \bmu \\
+&= \left(\nabla^\perp \otimes \nabla^\perp \left ( \frac{1}{2\pi}
+\log r + \frac{i}{4} H_0^{(1)} (kr) \right ) \right)\bmu \; .
+\end{align}
+Note that derivatives of $\log r$ are $o(1/\sqrt{r})$
+and that the pressure associated with the Stokeslet is
+$p = \nabla \Glap(\xx) \cdot \bmu$. We then have
+
+\begin{align}
+\left | \sigma \cdot \bn - i k \bu \right | &=
+\left | p \bn + \partial_n \bu + \nabla (\bu \cdot \bn)
+- ik \bu \right | \\
+&\leq \left | \partial_n \bu - ik\bu \right | + \left | \nabla(\bu \cdot \bn) \right |
++ o(1/\sqrt{r}) \\
+&\leq \frac{1}{4} \left | \partial_n \left(\nabla^\perp \otimes
+\nabla^\perp \left (H_0^{(1)} (kr) \right ) \right)\bmu
+- i k \left(\nabla^\perp \otimes \nabla^\perp
+\left (H_0^{(1)} (kr) \right ) \right)\bmu \right | \\
+& \quad + \left | \nabla \left( \partial_\tau \left ( 
+\nabla^\perp \left (H_0^{(1)} (kr) \right ) \cdot \bmu  \right )
+\right) \right | + o(1/\sqrt{r}) \; .
+\end{align}
+Because $H_0^{(1)}(kr)$ has the asymptotic expansion
+
+\begin{equation}
+H_0^{(1)}(kr) = \sqrt{\frac{2}{\pi k r}} e^{i(rk-\pi/4)} \left ( 1 + O\left (
+\frac{1}{r} \right ) \right ) \;
+\end{equation}
+as $r\to \infty$, we have
+
+\begin{equation}
+\left | \partial_n \left(\nabla^\perp \otimes
+\nabla^\perp \left (H_0^{(1)} (kr) \right ) \right)\bmu
+- ik \left(\nabla^\perp \otimes \nabla^\perp
+\left (H_0^{(1)} (kr) \right ) \right)\bmu \right | =
+o ( 1/\sqrt{r} ) \; .
+\end{equation}
+Finally, because $H_0^{(1)}(kr)$ is radially symmetric,
+we have
+
+\begin{equation}
+\left | \nabla \left( \partial_\tau \left ( 
+\nabla^\perp \left (H_0^{(1)} (kr) \right ) \cdot \bmu  \right )
+\right) \right | = 0 \; ,
+\end{equation}
+so that the Stokeslet satisfies the radiation condition.
+
+The proof for the kernel of the double layer potential
+is similar.
+\end{proof}
 
@@
 \lim_{r\to\infty}
-\int_{|\by|=r} \left( |\ff|^2 + |\omega|^2 |\bu|^2 \right) ds +
-2 \text{Im}(\omega) \int_{E \cap B_{r}(0)} \left(|\omega|^2 |\bu|^2 + |e(\bu)|^2 \right)
-dV = -2 \text{Im} \left( \omega \int_{\Gamma} \bu \cdot \overline{\ff} ds  \right)
+\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) ds +
+2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |e(\bu)|^2 \right)
+dV = -2 \text{Im} \left( k \int_{\Gamma} \bu \cdot \overline{\ff} ds  \right)
 \end{equation}
@@
 \begin{equation}
-\lim_{r\to\infty} \int_{|\by|=r} | \ff - i \omega \bu|^2 ds = 
-\lim_{r\to\infty} \int_{|\by| =r} \left( |\ff|^2 + |\omega|^2|\bu|^2 + 2 \text{Im} 
-\left( \omega \bu\cdot \ff \right) ds \label{eq:raddecayproof1}
+\lim_{r\to\infty} \int_{|\by|=r} | \ff - i k \bu|^2 ds = 
+\lim_{r\to\infty} \int_{|\by| =r} \left( |\ff|^2 + |k|^2|\bu|^2 + 2 \text{Im} 
+\left( k \bu\cdot \ff \right) ds \label{eq:raddecayproof1}
 \right) = 0 \, . 
@@
 \int_{E\cap B_{r}(0)} |e(\bu)|^2 dV = -\int_{\Gamma} \bu \cdot \overline{\ff} ds
-+ \int_{|\by|=r} \bu \cdot \overline{\ff} ds + \overline{\omega}^2 
++ \int_{|\by|=r} \bu \cdot \overline{\ff} ds + \overline{k}^2 
 \int_{E \cap B_{r}(0)} |\bu|^2 dV \,. \label{eq:raddecayproof2}
@@
 \begin{equation}
-\lim_{r\to\infty} \int_{|\by|=r}\left(|\ff|^2 + |\omega|^2 |\bu|^2 \right) ds 
-+ 2\text{Im}(k)\int_{E \cap B_{r}(0)} \left(|e(\bu)|^2 + |\omega|^2 |\bu|^2 
-\right) dV = -2\text{Im} \int_{\Gamma} \omega \bu \cdot \overline{\ff} dS \, .
+\lim_{r\to\infty} \int_{|\by|=r}\left(|\ff|^2 + |k|^2 |\bu|^2 \right) ds 
++ 2\text{Im}(k)\int_{E \cap B_{r}(0)} \left(|e(\bu)|^2 + |k|^2 |\bu|^2 
+\right) dV = -2\text{Im} \int_{\Gamma} k \bu \cdot \overline{\ff} dS \, .
 \end{equation}
@@
 \begin{equation}
-\Delta (\Delta + \omega^2) u_{j} = 0 \quad j=1,2 \,. 
+\Delta (\Delta + k^2) u_{j} = 0 \quad j=1,2 \,. 
 \end{equation}
@@
 \begin{equation}
-r^{|n|}, r^{-|n|}, H^{1}_{n}(\omega r), H^{2}_{n}(\omega r) \, , \quad
+r^{|n|}, r^{-|n|}, H^{1}_{n}(k r), H^{2}_{n}(k r) \, , \quad
 n\neq 0 \, ,
@@
 \begin{equation}
-1, \log{(r)}, H^{1}_{0}(\omega r), H^{2}_{0}(\omega r) \quad n=0 \, , 
+1, \log{(r)}, H^{1}_{0}(k r), H^{2}_{0}(k r) \quad n=0 \, , 
 \end{equation} 
@@
 expansion of $H_{n}^{1,2}(r)$, we note that the projection of 
-$a_{j,n}$ on $r^{|n|}$, and $H_{n}^{j}(\omega r)$ must be zero. 
+$a_{j,n}$ on $r^{|n|}$, and $H_{n}^{j}(k r)$ must be zero. 
 Thus, 
@@
 \begin{align}
-\omega^2 \bu &= \nabla p  \quad \label{eq:massconsred} \\
+k^2 \bu &= \nabla p  \quad \label{eq:massconsred} \\
 \nabla \cdot \bu &= 0 \, .
@@
 (Uniqueness Dirichlet)
-Suppose that $\text{Im}(\omega)>0$ and 
+Suppose that $\text{Im}(k)>0$ and 
 that $\bu$ is a radiating solution to the Stokes-Helmholtz
@@
 \lim_{r\to\infty}
-\int_{|\by|=r} \left( |\ff|^2 + |\omega|^2 |\bu|^2 \right) ds +
-2 \text{Im}(\omega) \int_{E \cap B_{r}(0)} \left(|\omega|^2 |\bu|^2 + |e(\bu)|^2 \right)
+\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) ds +
+2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |e(\bu)|^2 \right)
 dV = 0
@@
 The proof for the Neumann problem proceeds in a similar manner.
+
+\begin{lem}
+If $\bu = \nabla^{\perp} H_{0}(k r)$ and $p\to 0$ as $r\to \infty$, 
+then
+\begin{equation}
+\lim_{r\to \inf} \sqrt(r) \left(\ff_{1} - ik \bu_{1} \right) = 0 \, .
+\end{equation}
+\end{lem}
+
+\begin{proof}
+If $\bu = \nabla^{\perp} H_{0}(k r) = (\partial_{y} H_{0}(k r), 
+-\partial_{x} H_{0}(k r))$, then
+\begin{equation}
+\nabla  p = (\Delta + k^2) \bu = (\Delta + k^2) \nabla^{\perp} 
+H_{0} (k r) = 0 \, .
+\end{equation}
+Since $p\to 0$ as $r\to \infty$, we conclude that $p=0$.
+\begin{align}
+\ff_{1} &= 2\partial_{x} u_{1} \cos(\theta) + \left( \partial_{x} u_{2} + 
+\partial_{y} u_{1} \right) \sin(\theta) \\
+&= 2 \partial_{xy} H_{0}(k r) \cdot \frac{x}{r} +
+\left[-\partial_{xx} H_{0}(k r) + \partial_{yy} H_{0}(k r) \right]
+\cdot \frac{y}{r} \, .
+\end{align}
+Based on the mathematica script (radcond1.nb in our mathematica folder), we
+get
+\begin{equation}
+\ff_{1} - i k u_{1} = \frac{ky}{r^2} \left( -kr \left(H_{0}(k r) + 
+i H_{1}(k r)\right) +
+2 H_{1}(k r)\right) \, .
+\end{equation}
+The result then follows from the asymptotic properties of Hankel functions since
+\begin{equation}
+H_{0}(z) = c \frac{e^{-iz}}{\sqrt{z}} + O(\frac{1}{z^{3/2}}) \quad 
+\text{and} \quad 
+H_{1}(z) = i \cdot c \frac{e^{-iz}}{\sqrt{z}} + O(\frac{1}{z^{3/2}}) \,,
+\end{equation}
+where $c$ is the same constant in both of these expansions.
+\end{proof}

### 2018-08-21 doc/draft-01/08append.tex
Updating appendix

@@
 \begin{equation}
-H_{0}(z) = c \frac{e^{-iz}}{\sqrt{z}} + O(\frac{1}{z^{3/2}}) \quad 
+H_{0}(z) = c \frac{e^{iz}}{\sqrt{z}} + O(\frac{1}{z^{3/2}}) \quad 
 \text{and} \quad 
-H_{1}(z) = i \cdot c \frac{e^{-iz}}{\sqrt{z}} + O(\frac{1}{z^{3/2}}) \,,
+H_{1}(z) = -i \cdot c \frac{e^{iz}}{\sqrt{z}} + O(\frac{1}{z^{3/2}}) \,,
 \end{equation}
@@
 \end{proof}
+
+The following lemma shows uniqueness for the impedance problem under
+the assumption that $\bu$ is complex analytic.
+
+\begin{lem}
+Suppose that $\bu$ satisfies the radiation
+condition~\cref{eq:radcond}. 
+Suppose further that the stress tensor $\ff$ and $\bu$ satisfy
+\begin{equation}
+\ff + i k \bu = 0 \quad \xx \in \Gamma \, .
+\end{equation}
+Then $\bu \equiv 0$ for $\xx \in E$.
+\end{lem}
+
+\begin{proof}
+Since $\bu$ satisfies the radiation condition at $\infty$ and $\ff = -ik u$
+on $\Gamma$, it follows from~\cref{eq:repinfest} that
+\begin{align}
+&
+\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) ds +
+2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |e(\bu)|^2 \right)
+dV +2 \text{Im} \left( k \int_{\Gamma} \bu \cdot \overline{\ff} ds  \right) \\
+&= 
+\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) ds +
+2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |e(\bu)|^2 \right)
+dV +2 \left( |k|^{2} \int_{\Gamma} |\bu|^{2} \overline{\ff} ds  \right) = 0 
+\, .
+\end{align}
+Since all the quantities are positive, this implies two things:
+\begin{equation}
+\int_{\Gamma} |\bu|^{2} = 0 \implies \bu = 0  \quad \xx \in \Gamma \, .
+\end{equation}
+along with the estimate
+\begin{equation}
+\lim_{r\to\infty} \int_{|\yy|=r} |\bu|^{2} ds \to 0 \, .
+\end{equation}
+The last equation implies the conditions for~\cref{lem:rellich}
+are satisfied, from which we conclude that the components of $\bu$ 
+are harmonic in $E$. 
+Thus, the components of $\bu$ satisfy
+\begin{equation}
+\Delta u_{j}=  0 \quad \xx \in E \,, \quad \text{and} \quad
+u_{j} = 0 \quad \xx \in \Gamma \, ,
+\end{equation}
+for $j=1,2$.
+Then $\bu \equiv 0$ follows from the uniqueness of solutions to the 
+Dirichlet problem for Laplace's equation.
+\end{proof}

### 2018-08-21 doc/draft-01/08append.tex
update appendix

--- 2018-08-18 doc/draft-01/08append.tex
@@
 
-\section{Proof of invertibility of new representation}
-The proof proceeds as follows:
-\begin{itemize}
-\item Show uniqueness of solutions to the impedence, velocity, and surface
-traction boundary value problem in exterior domains for the Stokes-Helmholtz
-PDEs. In order to prove this, we need the following lemmas:
-\begin{itemize}
-\item Deriving Green's theorem for exterior domains
-\item Rellich's lemma
-\item Uniqueness proof
-\end{itemize}
-\item The proof for the clamped plate problem proceeds in the manner
-analogous to the Dirichlet biharmonic paper.
-\end{itemize}
+\section{Existence and uniqueness results for the Stokes-Helmholtz PDE}
 
-With this in mind, we first discuss the PDE theory for the impedence, 
-velocity and surface traction boundary value problems on unbounded
-domains for the Stokes-Helmholtz equation.
-We focus on the proof for the velocity boundary value problem. 
-The proofs for the surface traction and impedence problems is similar.
+In this section, we develop some existence and uniqueness
+results for the Stokes-Helmholtz PDE.
+%
+The structure of this section follows that used
+by Colton and Kress \cite[Ch. 3]{colton1983integral}
+for the scalar Helmholtz equation.
+%
+Let $\Omega$ be a bounded simply connected
+domain and $E = \R^{2} \setminus \bar{\Omega}$ denote its
+exterior.
+%
+Let $\Gamma = \partial \Omega$ denote the boundary of $E$ and
+$\bnu(\yy)$ denote the exterior normal to the point $\yy$ on
+$\Gamma$, i.e. the normal vector pointing out of $E$ into $\Omega$.
+%
+For a given function $\bh$ defined on $\Gamma$,
+the exterior Dirichlet boundary value problem is to
+find a pair $(\bu,p)$ which satisfies:
+\begin{align}
+\Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\label{eq:helmstokes_ext}\\
+\nabla \cdot \bu &= 0 \quad \bx \in E \, , \\
+\bu &= \bh \quad \bx \in \Gamma \, .
+\end{align}
+In addition to the boundary condition on
+$\Gamma$, we must impose radiation conditions
+at $\infty$, analogous to the Helmholtz equation.
+%
 
-Suppose that $\Omega$ is a bounded simply connected domain and that
-$E = \R^{2} \setminus \Omega$ is its exterior.
-Let $\Gamma = \partial \Omega$ denote the boundary of $E$.
-For a given function $\bh$ on the boundary, 
-the exterior velocity boundary value problem is given by:
-\begin{align}
-\Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
-\nabla \cdot \bu &= 0 \quad \bx \in E \, ,\\
-\bu &= \bh \quad \bx \in \Gamma \, . \\
-\end{align}
 Let $\bsigma$ denote the stress tensor associated with the velocity
@@
 \begin{equation}
-e_{ij}(\bu) = \left( \partial_{x_j} u_i + \partial_{x_i} u_j \right)
+e_{ij}(\bu) = \left( \partial_{x_j} u_i + \partial_{x_i} u_j \right) \; .
 \end{equation}
-Let $\bn$ denote the outward normal to the boundary $\Gamma$, then
-the surface traction $\ff$ on the boundary $\Gamma$ is given 
-by
+%
+For a given curve $\gamma$, let $\bn$ denote its outward
+normal.
+%
+The normal component of the stress,
 \begin{equation}
-\ff = \sigma \cdot \bn
+\ff = \bsigma \cdot \bn \; ,
 \end{equation}
-Analogous to the Helmholtz equation, we need to impose radiation conditions
-at $\infty$.
-We propose the following radiation conditions for the Stokes-Helmholtz 
-equation
+gives the surface traction, which is the analog of
+the normal derivative for the scalar Helmholtz equation,
+i.e. specifying the surface traction on a boundary is
+the Neumann problem for the Stokes-Helmholtz PDE.
 
-\begin{definition}
+%
+Let $B_r(0)$ denote the disc of radius $r$ centered
+at the origin.
+%
+In general, we will use $\bnu$ and $\btau$ to refer
+to the outward normal and positively oriented
+tangent to the boundary curve $\Gamma$ and $\bn$ and
+$\bt$ to refer to the outward normal and positively
+oriented tangent of the circle $\partial B_r(0)$.
+%
+With this notation in hand, we now propose the following
+radiation condition.
+
+\begin{definition} \label{def:radcond}
 Let $(\bu,p)$ satisfy the Stokes-Helmholtz equations in
@@
 the pair $(\bu,p)$ satisfies the radiation condition if
-$p$ is bounded, $p \to 0$ as $\xx \to \infty$, and 
+$p$ is bounded, $p \to 0$ as $r = |\xx| \to \infty$, and 
 \begin{equation}
@@
 \end{equation}
-uniformly in direction.
+uniformly in direction where $\ff = \bsigma \cdot \bn$
+with $\bn = \xx/|\xx|$, i.e. $\ff$ is the surface
+traction on $\partial B_r(0)$.     
 \end{definition}
@@
 \begin{proposition}
-Both the Helmholtz-Stokeslet \eqref{eq:stokeslet} and the
-kernel of the Helmholtz-Stokes double layer potential
-\eqref{eq:stokesdlkernel} satisfy the radiation condition
-\eqref{eq:radcond}.
+The Helmholtz-Stokeslet, as in \eqref{eq:stokeslet}, satisfies
+the radiation condition in Definition \ref{def:radcond}.
+Assuming that a density $\bmu$ is integrable and satisfies
+$\int_\Gamma \bmu\cdot \bnu = 0$, where $\bnu$ denotes the
+outward normal to the curve $\Gamma$, the Helmholtz-Stokes
+double layer potential $\DD\bmu$, as in \eqref{eq:doublelayer},
+also satisfies the radiation condition.
 \end{proposition}
@@
 \begin{proof}
-Without loss of generality, we assume that these
-kernels are centered at the origin. Let $r = |\xx|$.
 Consider the Stokeslet induced by an arbitrary charge
-$k^2 \bmu$. We have
+$k^2 \bpsi$ at the origin. Let $r = |\xx|$,
+$\bn = \xx/|\xx|$, and $\bt = \bn^\perp$. We have
 
 \begin{align}
-\bu (\xx) &= k^2 \GG(\xx,0) \bmu \\
+\bu (\xx) &= k^2 \GG(\xx,0) \bpsi \\
 &= k^2 \left (-\II \Delta \Gbh(\xx,0)
-+ \nabla \otimes \nabla \Gbh(\xx,0)\right ) \bmu \\
-&= -k^2 \left (\nabla^\perp \otimes \nabla^\perp \Gbh(\xx,0) \right) \bmu \\
++ \nabla \otimes \nabla \Gbh(\xx,0)\right ) \bpsi \\
+&= -k^2 \left (\nabla^\perp \otimes \nabla^\perp \Gbh(\xx,0) \right) \bpsi \\
 &= \left(\nabla^\perp \otimes \nabla^\perp \left ( \frac{1}{2\pi}
-\log r + \frac{i}{4} H_0^{(1)} (kr) \right ) \right)\bmu \; .
+\log r + \frac{i}{4} H_0^{(1)} (kr) \right ) \right)\bpsi \; .
 \end{align}
-Note that derivatives of $\log r$ are $o(1/\sqrt{r})$
+Note that derivatives of $\log r$ are $\littleo (1/\sqrt{r})$
 and that the pressure associated with the Stokeslet is
-$p = \nabla \Glap(\xx) \cdot \bmu$. We then have
+$p = \nabla \Glap(\xx) \cdot \bpsi$. We then have
 
@@
 &\leq \left | \partial_n \bu - ik\bu \right | + \left | \nabla(\bu \cdot \bn) \right |
-+ o(1/\sqrt{r}) \\
++ \littleo (1/\sqrt{r}) \\
 &\leq \frac{1}{4} \left | \partial_n \left(\nabla^\perp \otimes
-\nabla^\perp \left (H_0^{(1)} (kr) \right ) \right)\bmu
+\nabla^\perp \left (H_0^{(1)} (kr) \right ) \right)\bpsi
 - i k \left(\nabla^\perp \otimes \nabla^\perp
-\left (H_0^{(1)} (kr) \right ) \right)\bmu \right | \\
-& \quad + \left | \nabla \left( \partial_\tau \left ( 
-\nabla^\perp \left (H_0^{(1)} (kr) \right ) \cdot \bmu  \right )
-\right) \right | + o(1/\sqrt{r}) \; .
+\left (H_0^{(1)} (kr) \right ) \right)\bpsi \right | \\
+& \quad + \left | \nabla \left( \partial_t \left ( 
+\nabla^\perp \left (H_0^{(1)} (kr) \right ) \cdot \bpsi  \right )
+\right) \right | + \littleo (1/\sqrt{r}) \; .
 \end{align}
@@
 \left | \partial_n \left(\nabla^\perp \otimes
-\nabla^\perp \left (H_0^{(1)} (kr) \right ) \right)\bmu
+\nabla^\perp \left (H_0^{(1)} (kr) \right ) \right)\bpsi
 - ik \left(\nabla^\perp \otimes \nabla^\perp
-\left (H_0^{(1)} (kr) \right ) \right)\bmu \right | =
+\left (H_0^{(1)} (kr) \right ) \right)\bpsi \right | =
 o ( 1/\sqrt{r} ) \; .
@@
 \begin{equation}
-\left | \nabla \left( \partial_\tau \left ( 
-\nabla^\perp \left (H_0^{(1)} (kr) \right ) \cdot \bmu  \right )
+\left | \nabla \left( \partial_t \left ( 
+\nabla^\perp \left (H_0^{(1)} (kr) \right ) \cdot \bpsi  \right )
 \right) \right | = 0 \; ,
@@
 
-The proof for the kernel of the double layer potential
-is similar.
+For the double layer potential, we only establish the
+decay of the pressure $p$; the rest of the terms
+in \eqref{eq:radcond} can be bounded using an argument
+like that for the Stokeslet above.
+Because $p$ is harmonic in the exterior of any disc
+containing $\Gamma$, it is sufficient to show that
+$|\nabla p| = \bigo (1/r^2)$. Let $\btau$ denote the
+positively oriented tangent to the curve $\Gamma$ and
+$\mu_\nu$ and $\mu_\tau$ denote $\bmu \cdot \bnu$ and
+$\bmu \cdot \btau$, respectively. Substituting $\DD \bmu$ into
+\eqref{eq:helmstokes_ext}, we obtain
+
+\begin{align}
+\nabla p^\DD(\xx) &= \Delta \DD \bmu(\xx) + k^2 \DD\bmu(\xx) \\
+&= \int_\Gamma \left (-k^2 \nabla \Glap (\xx,\yy) +
+2 \nabla^\perp \partial_{\nu\tau} \Glap (\xx,\yy) \right ) \mu_\nu(\yy)
+\, dS(\yy) \\
+& \qquad + \int_\Gamma \nabla^\perp (\partial_{\tau\tau}-\partial_{\nu\nu})\Glap \mu_\tau(\yy)
+\, dS(\yy) \; .
+\end{align}
+The other terms are higher-order derivatives
+of $\Glap$, so it is sufficient to show that the term
+
+\begin{align}
+|\nabla p_1(\xx)| &:= \left |-k^2 \nabla \int_\Gamma \Glap(\xx,\yy)
+\mu_\nu(\yy) \, dS(\yy) \right |
+\end{align}
+is $\bigo (1/r^2)$. In the following, let $z = x_1 + i x_2$ be the
+point corresponding to $\xx$ in the complex plane and let $R$
+be the radius of some disc containing $\Gamma$. If $|\xx| > 2R$,
+we can use a standard multipole expansion of $\log(z-(y_1+iy_2))$
+and the assumption that $\int_\Gamma \bmu \cdot \bnu = 0$
+to obtain
+\begin{align}
+|\nabla p_1(\xx)| &= \frac{k^2}{2\pi} \left |  \partial_z \int_\Gamma \log(z-(y_1+iy_2))
+\mu_\nu(\yy) dS(\yy) \right | \\
+&= \frac{k^2}{2\pi} \left |  \partial_z  \left ( \log(z) \int_\Gamma \mu_\nu(\yy) \, dS(\yy)
++ \sum_{l=1}^\infty \frac{1}{z^l} \int_\Gamma \left( y_1+iy_2 \right)^l \mu_\nu(\yy) \, dS(\yy)
+\right ) \right | \\
+&= \frac{k^2}{2\pi} \left | \sum_{l=1}^\infty \frac{-l}{z^{l+1}}
+\int_\Gamma \left( y_1+iy_2 \right)^l \mu_\nu(\yy) \, dS(\yy) \right | \\
+&= \bigo (1/r^2) \; .
+\end{align}
 \end{proof}
@@
 \label{lem:rep}
-Suppose that $\bu$ satisfies the Stokes-Helmholtz equation in 
-an unbounded region $E$ along with the radiaition 
+Suppose that $(\bu,p)$ satisfies the Stokes-Helmholtz equation in 
+an unbounded region $E$ along with the radiation 
 condition~\cref{eq:radcond}. 
@@
 \lim_{r\to\infty}
-\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) ds +
-2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |e(\bu)|^2 \right)
-dV = -2 \text{Im} \left( k \int_{\Gamma} \bu \cdot \overline{\ff} ds  \right)
+\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) dS +
+2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |e(\bu)|^2 \right)
+dV = -2 \Im \left( k \int_{\Gamma} \bu \cdot \overline{\ff} dS  \right)
 \end{equation}
@@
 \begin{proof}
-Since $\bu$ satisfies the radiation condition, we have that
+Since $(\bu,p)$ satisfies the radiation condition, we have that
 \begin{equation}
-\lim_{r\to\infty} \int_{|\by|=r} | \ff - i k \bu|^2 ds = 
-\lim_{r\to\infty} \int_{|\by| =r} \left( |\ff|^2 + |k|^2|\bu|^2 + 2 \text{Im} 
-\left( k \bu\cdot \ff \right) ds \label{eq:raddecayproof1}
+\lim_{r\to\infty} \int_{|\by|=r} | \ff - i k \bu|^2 dS = 
+\lim_{r\to\infty} \int_{|\by| =r} \left( |\ff|^2 + |k|^2|\bu|^2 + 2 \Im 
+\left( k \bu\cdot \overline{\ff} \right) dS \label{eq:raddecayproof1}
 \right) = 0 \, . 
@@
 \begin{equation}
-\int_{E\cap B_{r}(0)} |e(\bu)|^2 dV = -\int_{\Gamma} \bu \cdot \overline{\ff} ds
-+ \int_{|\by|=r} \bu \cdot \overline{\ff} ds + \overline{k}^2 
+\int_{E\cap B_{r}(0)} |e(\bu)|^2 dV = -\int_{\Gamma} \bu \cdot \overline{\ff} dS
++ \int_{|\by|=r} \bu \cdot \overline{\ff} dS + \overline{k}^2 
 \int_{E \cap B_{r}(0)} |\bu|^2 dV \,. \label{eq:raddecayproof2}
@@
 \begin{equation}
-\lim_{r\to\infty} \int_{|\by|=r}\left(|\ff|^2 + |k|^2 |\bu|^2 \right) ds 
-+ 2\text{Im}(k)\int_{E \cap B_{r}(0)} \left(|e(\bu)|^2 + |k|^2 |\bu|^2 
-\right) dV = -2\text{Im} \int_{\Gamma} k \bu \cdot \overline{\ff} dS \, .
+\lim_{r\to\infty} \int_{|\by|=r}\left(|\ff|^2 + |k|^2 |\bu|^2 \right) dS 
++ 2\Im(k)\int_{E \cap B_{r}(0)} \left(|e(\bu)|^2 + |k|^2 |\bu|^2 
+\right) dV = -2\Im \int_{\Gamma} k \bu \cdot \overline{\ff} dS \, .
 \end{equation}
@@
 \begin{equation}
-\int_{|\by|=r} |\bu|^2 ds = r\sum_{n=-\infty}^{\infty} |a_{1,n}(r)|^2  +
+\int_{|\by|=r} |\bu|^2 dS = r\sum_{n=-\infty}^{\infty} |a_{1,n}(r)|^2  +
 |a_{2,n}(r)|^2 \, .
@@
 (Uniqueness Dirichlet)
-Suppose that $\text{Im}(k)>0$ and 
+Suppose that $\Im(k)>0$ and 
 that $\bu$ is a radiating solution to the Stokes-Helmholtz
@@
 \lim_{r\to\infty}
-\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) ds +
-2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |e(\bu)|^2 \right)
+\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) dS +
+2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |e(\bu)|^2 \right)
 dV = 0
@@
 \begin{equation}
-\lim_{r\to\infty} \int_{|\by|=r} |\bu|^2 ds = 0 \, .
+\lim_{r\to\infty} \int_{|\by|=r} |\bu|^2 dS = 0 \, .
 \end{equation}

### 2018-08-22 doc/draft-01/08append.tex
update proofs and notation

--- 2018-08-21 doc/draft-01/08append.tex
@@
 
-\section{Existence and uniqueness results for the Stokes-Helmholtz PDE}
+\section{Existence and uniqueness results for the Helmholtz-Stokes PDE}
 
 In this section, we develop some existence and uniqueness
-results for the Stokes-Helmholtz PDE.
+results for the Helmholtz-Stokes PDE.
 %
@@
 %
-Let $\Gamma = \partial \Omega$ denote the boundary of $E$ and
+Let $\Gamma = \partial E$ denote the boundary of $E$ and
 $\bnu(\yy)$ denote the exterior normal to the point $\yy$ on
@@
 \begin{equation}
-\bsigma = -p \II + \be(\bu) \, ,
+\bsigma = -p \II + 2 \be(\bu) \, ,
 \end{equation}
@@
 \begin{equation}
-e_{ij}(\bu) = \left( \partial_{x_j} u_i + \partial_{x_i} u_j \right) \; .
+e_{ij}(\bu) = \frac{1}{2} \left( \partial_{x_j} u_i + \partial_{x_i} u_j \right) \; .
 \end{equation}
-%
-For a given curve $\gamma$, let $\bn$ denote its outward
-normal.
 %
@@
 \begin{equation}
-\ff = \bsigma \cdot \bn \; ,
+\ff = \bsigma \cdot \bnu \; ,
 \end{equation}
-gives the surface traction, which is the analog of
+gives the surface traction, which is the analogue of
 the normal derivative for the scalar Helmholtz equation,
 i.e. specifying the surface traction on a boundary is
-the Neumann problem for the Stokes-Helmholtz PDE.
+the Neumann problem for the Helmholtz-Stokes PDE.
 
@@
 Let $B_r(0)$ denote the disc of radius $r$ centered
-at the origin.
+at the origin and $\partial B_r(0)$ its boundary.
 %
-In general, we will use $\bnu$ and $\btau$ to refer
-to the outward normal and positively oriented
-tangent to the boundary curve $\Gamma$ and $\bn$ and
-$\bt$ to refer to the outward normal and positively
-oriented tangent of the circle $\partial B_r(0)$.
-%
-With this notation in hand, we now propose the following
-radiation condition.
+We propose the following radiation condition.
 
 \begin{definition} \label{def:radcond}
-Let $(\bu,p)$ satisfy the Stokes-Helmholtz equations in
+Let $(\bu,p)$ satisfy the Helmholtz-Stokes equations in
 the exterior of a bounded domain. We say that
-the pair $(\bu,p)$ satisfies the radiation condition if
+the pair $(\bu,p)$ is {\em radiating} if
 $p$ is bounded, $p \to 0$ as $r = |\xx| \to \infty$, and 
@@
 \end{equation}
-uniformly in direction where $\ff = \bsigma \cdot \bn$
-with $\bn = \xx/|\xx|$, i.e. $\ff$ is the surface
+uniformly in direction where $\ff = \bsigma \cdot \bnu$
+with $\bnu = \xx/|\xx|$, i.e. $\ff$ is the surface
 traction on $\partial B_r(0)$.     
@@
 Assuming that a density $\bmu$ is integrable and satisfies
-$\int_\Gamma \bmu\cdot \bnu = 0$, where $\bnu$ denotes the
+$\int_\Gamma \bmu\cdot \bnu dS = 0$, where $\bnu$ denotes the
 outward normal to the curve $\Gamma$, the Helmholtz-Stokes
@@
 $k^2 \bpsi$ at the origin. Let $r = |\xx|$,
-$\bn = \xx/|\xx|$, and $\bt = \bn^\perp$. We have
+$\bnu(\xx) = \xx/|\xx|$, and $\btau(\xx) = \bnu(\xx)^\perp$. We have
 
@@
 \begin{align}
-\left | \sigma \cdot \bn - i k \bu \right | &=
-\left | p \bn + \partial_n \bu + \nabla (\bu \cdot \bn)
+\left | \sigma \cdot \bnu(\xx) - i k \bu \right | &=
+\left | p \bnu(\xx) + \partial_{{\nu_x}} \bu + \nabla (\bu \cdot \bnu(\xx))
 - ik \bu \right | \\
-&\leq \left | \partial_n \bu - ik\bu \right | + \left | \nabla(\bu \cdot \bn) \right |
+&\leq \left | \partial_{{\nu_x}} \bu - ik\bu \right | + \left | \nabla(\bu \cdot \bnu(\xx)) \right |
 + \littleo (1/\sqrt{r}) \\
-&\leq \frac{1}{4} \left | \partial_n \left(\nabla^\perp \otimes
+&\leq \frac{1}{4} \left | \partial_{{\nu_x}} \left(\nabla^\perp \otimes
 \nabla^\perp \left (H_0^{(1)} (kr) \right ) \right)\bpsi
@@
 \left (H_0^{(1)} (kr) \right ) \right)\bpsi \right | \\
-& \quad + \left | \nabla \left( \partial_t \left ( 
+& \quad + \left | \nabla \left( \partial_{\tau_x} \left ( 
 \nabla^\perp \left (H_0^{(1)} (kr) \right ) \cdot \bpsi  \right )
@@
 \begin{equation}
-\left | \partial_n \left(\nabla^\perp \otimes
+\left | \partial_{{\nu_x}} \left(\nabla^\perp \otimes
 \nabla^\perp \left (H_0^{(1)} (kr) \right ) \right)\bpsi
@@
 \begin{equation}
-\left | \nabla \left( \partial_t \left ( 
+\left | \nabla \left( \partial_{\tau_x} \left ( 
 \nabla^\perp \left (H_0^{(1)} (kr) \right ) \cdot \bpsi  \right )
@@
 positively oriented tangent to the curve $\Gamma$ and
-$\mu_\nu$ and $\mu_\tau$ denote $\bmu \cdot \bnu$ and
-$\bmu \cdot \btau$, respectively. Substituting $\DD \bmu$ into
-\eqref{eq:helmstokes_ext}, we obtain
+$\mu_\nu(\yy)$ and $\mu_\tau(\yy)$ denote $\bmu(\yy) \cdot \bnu(\yy)$ and
+$\bmu(\yy) \cdot \btau(\yy)$, respectively. Substituting
+$\DD \bmu$ into \eqref{eq:helmstokes_ext}, we obtain
 
 \begin{align}
-\nabla p^\DD(\xx) &= \Delta \DD \bmu(\xx) + k^2 \DD\bmu(\xx) \\
+\nabla p^\DD(\xx) &= (\Delta + k^2) \DD \bmu(\xx) \\
 &= \int_\Gamma \left (-k^2 \nabla \Glap (\xx,\yy) +
@@
 
+\subsection{Uniqueness results}
+
 \begin{lem}
 \label{lem:rep}
-Suppose that $(\bu,p)$ satisfies the Stokes-Helmholtz equation in 
+Suppose that $(\bu,p)$ satisfies the Helmholtz-Stokes equation in 
 an unbounded region $E$ along with the radiation 
@@
 \int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) dS +
-2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |e(\bu)|^2 \right)
-dV = -2 \Im \left( k \int_{\Gamma} \bu \cdot \overline{\ff} dS  \right)
+2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
+dV = 2 \Im \left( k \int_{\Gamma} \bu \cdot \overline{\ff} dS  \right)
 \end{equation}
@@
 \end{equation}
-Since $\bu$ satisfies the Stokes-Helmholtz equation $E \cap B_{r}(0)$,
+Since $\bu$ satisfies the Helmholtz-Stokes equation $E \cap B_{r}(0)$,
 using a couple of applications of the divergence theorem, we have that
 \begin{equation}
-\int_{E\cap B_{r}(0)} |e(\bu)|^2 dV = -\int_{\Gamma} \bu \cdot \overline{\ff} dS
+\int_{E\cap B_{r}(0)} |2 \be(\bu)|^2 dV =
+\int_{\Gamma} \bu \cdot \overline{\ff} dS
 + \int_{|\by|=r} \bu \cdot \overline{\ff} dS + \overline{k}^2 
@@
 \lim_{r\to\infty} \int_{|\by|=r}\left(|\ff|^2 + |k|^2 |\bu|^2 \right) dS 
-+ 2\Im(k)\int_{E \cap B_{r}(0)} \left(|e(\bu)|^2 + |k|^2 |\bu|^2 
-\right) dV = -2\Im \int_{\Gamma} k \bu \cdot \overline{\ff} dS \, .
++ 2 \Im(k)\int_{E \cap B_{r}(0)} \left(|2\be(\bu)|^2 + |k|^2 |\bu|^2 
+\right) dV = 2\Im \left ( k \int_{\Gamma} \bu \cdot \overline{\ff} dS \right) \, .
 \end{equation}
@@
 
-In the next lemma, we prove the analogue of Rellich's lemma for the Stokes-
-Helmholtz equation. 
+In the next lemma, we prove the analogue of Rellich's lemma for the
+Helmholtz-Stokes equation. 
 \begin{lem}
 \label{lem:rellich}
-Suppose that $\bu$ satisfies the Stokes-Helmholtz equation in an unbounded
+Suppose that $\bu$ satisfies the Helmholtz-Stokes equation in an unbounded
 region $E$.  
@@
 \end{proof}
-\begin{remark}
+\begin{remark} \label{rmk:harmu}
 Note that each component of $\bu$ is harmonic and thus $\bu$ then satisfies
@@
 and $\nabla \cdot \bu = 0$.
-This remark will be useful for the impedence problem...
 \end{remark}
@@
 
-\begin{thm}
-(Uniqueness Dirichlet)
-Suppose that $\Im(k)>0$ and 
-that $\bu$ is a radiating solution to the Stokes-Helmholtz
+\begin{thrm}[Uniqueness of the Dirichlet Problem]
+Suppose that $\Im(k)\geq 0$ and 
+that $(\bu,p)$ is a radiating solution to the Helmholtz-Stokes
 equation in $E$ with $\bu =0$ on the boundary $\Gamma$, then
-$u \equiv 0$ in $E$.
-\end{thm}
+$\bu \equiv 0$ in $E$.
+\end{thrm}
 
@@
 \int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) dS +
-2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |e(\bu)|^2 \right)
+2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |\be(\bu)|^2 \right)
 dV = 0
@@
 with $\bu \to 0$ as $r \to \infty$. Furthermore, since $\bu=0$ on
-$\Gamma$, from uniqueness of solutions to the Dirichlet problem
+$\Gamma$, from uniqueness of solutions to the
+Dirichlet problem for Laplace's equation
 on exterior domains, we conclude that $\bu \equiv 0$ in $E$.
@@
 
-The proof for the Neumann problem proceeds in a similar manner.
-
-\begin{lem}
-If $\bu = \nabla^{\perp} H_{0}(k r)$ and $p\to 0$ as $r\to \infty$, 
-then
-\begin{equation}
-\lim_{r\to \inf} \sqrt(r) \left(\ff_{1} - ik \bu_{1} \right) = 0 \, .
-\end{equation}
-\end{lem}
+\begin{thrm}[Uniqueness of the Neumann Problem]
+Suppose that $\Im(k)\geq 0$ and 
+that $(\bu,p)$ is a radiating solution to the Helmholtz-Stokes
+equation in $E$ with $\ff = 0$ on the boundary $\Gamma$, then
+$\bu \equiv 0$ in $E$.
+\end{thrm}
 
 \begin{proof}
-If $\bu = \nabla^{\perp} H_{0}(k r) = (\partial_{y} H_{0}(k r), 
--\partial_{x} H_{0}(k r))$, then
+Since $\ff = 0$ on $\Gamma$, it follows
+from~\cref{eq:repinfest} that
 \begin{equation}
-\nabla  p = (\Delta + k^2) \bu = (\Delta + k^2) \nabla^{\perp} 
-H_{0} (k r) = 0 \, .
+\lim_{r\to\infty}
+\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) dS +
+2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |\be(\bu)|^2 \right)
+dV = 0
 \end{equation} 
-Since $p\to 0$ as $r\to \infty$, we conclude that $p=0$.
+In particular, this implies that
+\begin{equation}
+\lim_{r\to\infty} \int_{|\by|=r} |\bu|^2 dS = 0 \, .
+\end{equation}
+Thus, the conditions for $\bu$ in Rellich's lemma (~\cref{lem:rellich})
+are satisfied, and each component of $\bu$ is a harmonic function
+with $\bu \to 0$ as $r \to \infty$. Furthermore, as observed
+in \cref{rmk:harmu}, $k^2 \bu = \nabla p$. Then, the boundary
+condition becomes $0 = \ff = -p \bnu + 2 \nabla \partial_\nu p/k^2$.
+Because $0 = \btau \cdot \ff = 2\partial_{\tau\nu} p/k^2$,
+$\partial_\nu p $ is a constant on $\Gamma$. Using the
+fact that $(\bu,p)$ is radiating and the fact that $p$ is harmonic,
+the divergence theorem implies that $\partial_\nu p=0$ on $\Gamma$.
+Thus, $\ff = -p\bnu$ so that $p = 0$ on $\Gamma$. By the uniqueness
+of solutions to the Dirichlet problem for Laplace's equation,
+we have that $p=0$ so that $\uu \equiv 0$.
+
+\end{proof}
+
+\begin{thrm}[Uniqueness of the Impedance Problem]
+Suppose that $\Im(k) \geq 0$ and that
+$(\bu,p)$ is a radiating solution of the
+Helmholtz-Stokes equation in $E$ which satisfies
+the homogeneous impednace boundary condition
+\begin{equation}
+\ff - i k \bu = 0 \quad \xx \in \Gamma \, .
+\end{equation}
+Then $\bu \equiv 0$ for $\xx \in E$.
+\end{thrm}
+
+\begin{proof}
+Since $\bu$ satisfies the radiation condition at $\infty$ and $\ff = ik \bu$
+on $\Gamma$, it follows from~\cref{eq:repinfest} that
 \begin{align}
-\ff_{1} &= 2\partial_{x} u_{1} \cos(\theta) + \left( \partial_{x} u_{2} + 
-\partial_{y} u_{1} \right) \sin(\theta) \\
-&= 2 \partial_{xy} H_{0}(k r) \cdot \frac{x}{r} +
-\left[-\partial_{xx} H_{0}(k r) + \partial_{yy} H_{0}(k r) \right]
-\cdot \frac{y}{r} \, .
+0 &=
+\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) dS +
+2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
+dV \nonumber \\
+& \qquad - 2 \text{Im} \left( k \int_{\Gamma} \bu \cdot \overline{\ff} dS  \right) \\
+&= 
+\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) dS +
+2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
+dV \nonumber \\
+& \qquad + 2 \left( |k|^{2} \int_{\Gamma} |\bu|^{2} dS  \right)
+\, .
 \end{align}
-Based on the mathematica script (radcond1.nb in our mathematica folder), we
-get
+Because all of the quantities in the last expression above are
+nonnegative, we have that
 \begin{equation}
-\ff_{1} - i k u_{1} = \frac{ky}{r^2} \left( -kr \left(H_{0}(k r) + 
-i H_{1}(k r)\right) +
-2 H_{1}(k r)\right) \, .
+\int_{\Gamma} |\bu|^{2} = 0 \implies \bu = 0  \quad \xx \in \Gamma \, 
 \end{equation}
-The result then follows from the asymptotic properties of Hankel functions since
+and the estimate
 \begin{equation}
-H_{0}(z) = c \frac{e^{-iz}}{\sqrt{z}} + O(\frac{1}{z^{3/2}}) \quad 
-\text{and} \quad 
-H_{1}(z) = i \cdot c \frac{e^{-iz}}{\sqrt{z}} + O(\frac{1}{z^{3/2}}) \,,
+\lim_{r\to\infty} \int_{|\yy|=r} |\bu|^{2} dS \to 0 \, .
 \end{equation}
-where $c$ is the same constant in both of these expansions.
+The last equation implies the conditions for~\cref{lem:rellich}
+are satisfied, from which we conclude that the components
+of $\bu$ are harmonic in $E$. 
+Thus, the components of $\bu$ satisfy
+\begin{equation}
+\Delta u_{j}=  0 \quad \xx \in E \quad \text{and} \quad
+u_{j} = 0 \quad \xx \in \Gamma \, ,
+\end{equation}
+for $j=1,2$.
+Then $\bu \equiv 0$ follows from the uniqueness of solutions to the 
+Dirichlet problem for Laplace's equation.
 \end{proof}
+
+\subsection{Existence results}

### 2018-08-24 doc/draft-01/08append.tex
updating appendix

@@
 
+\begin{lem}
+Suppose that $\Omega$ is a multiply connected domain with outer boundary
+$\Gamma_{0}$ and $n-$ obstacle boundaries $\Gamma_{j}$, $j=1,2,\ldots n$. 
+Suppose that $k$ is a Stokes eigenvalue for the region $\Omega$ and 
+let $\bu$ be the corresponding eigenfunction. 
+Then, the stream function associated with the velocity $\bu$ defined by
+$w = \left(\nabla^{\perp} \right)^{-1} \bu$ exists and is single valued. 
+Furthermore, $k$ is also a buckling eigenvalue if and only if
+\begin{equation}
+\int_{\Gamma_{j}} w_{j} ds = 0 \quad \forall j=1,2,\ldots n \, .
+\end{equation}
+\end{lem}
+
+\begin{proof}
+Since $\bu$ is a Stokes eigenfunction, it satisfies
+\begin{equation}
+\int_{\Gamma_{j}} \bu \cdot \bn ds = 0 \quad j=1,2\ldots n \, .
+\end{equation}
+Thus, there exists a single valued stream function associated with the
+velocity field $\bu$ such that 
+\begin{equation}
+\nabla^{\perp} w = \bu \, .
+\end{equation}
+Furthermore, since $\bu$ satisfies the Helmholtz-Stokes equations, 
+$w$ satisfies
+\begin{align}
+\Delta (\Delta + k^{2} ) w &= 0 \, , \quad \bx \in \Omega \\
+\nabla^{\perp} w = \bu &=0 \, ,\quad \bx \in \Gamma \, ,
+\end{align}
+where $\Gamma = \cup_{j=0}^{n} \Gamma_{j}$ is the boundary of $\Omega$.
+In particular $w= c_{j}$ and $dw/dn = 0$ for $\bx \in \Gamma_{j}$ for
+some constant $c_{j}$.
+Thus $k$ is also a buckling eigenvalue if and only if 
+\begin{equation}
+c_{j} = \frac{1}{|\Gamma_{j}|}\int_{\Gamma_{j}} w ds =  0 \, .
+\end{equation}
+\end{proof}
+
+The above result can be restated as a 
+a uniqueness result for the 
+solutions to the Helmholtz-Stokes equations whenever $k$ is
+not a buckling value and the stream function associated with the
+velocity satisfies additional integral constraints.
+We state the result in the following lemma.
+\begin{lem}
+\label{lem:conshelmbieig}
+Suppose that $k$ is not a buckling eigenvalue. 
+Further suppose that $\bu$ satisfies
+\begin{align}
+\Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in \Omega \\
+\nabla \cdot \bu &=0 \quad \bx \in \Omega \\
+\bu &=0 \quad \bx \in \Gamma \\
+\frac{1}{|\Gamma_{j}|}
+\int_{\Gamma_{j}} \left(\nabla^{\perp} \right)^{-1} \bu &= c \quad
+j=0,1,2,\ldots n\, ,
+\end{align}
+where $c$ is a constant independent of the boundary component $\Gamma_{j}$.
+Then $\bu \equiv 0$ for all $\bx \in \Omega$.
+\end{lem}
+
+\begin{lem}
+Suppose that $k$ is not a buckling eigenvalue. 
+Let $\mathbf{K}_{\Gamma}$, $\mathbf{B}$, $\mathbf{D}$, 
+and $\mathbf{F}$ denote the operators defined in~\cref{eq:eqns}.
+Then the block system
+\begin{equation}
+\begin{bmatrix}
+-\frac{1}{2}\mathbf{I}_{\mathcal{X}\times\mathcal{X}} + 
+\mathbf{K}_{\Gamma} & \mathbf{B} \\
+\mathbf{D} & \mathbf{F} 
+\end{bmatrix} \, ,
+\label{eq:IntEqBiharm1newapp}
+\end{equation}
+is an invertible Fredholm operator.
+\end{lem}
+\begin{proof}
+It is simple to
+show that the linear system \cref{eq:IntEqBiharm1newapp}
+is Fredholm. The block which contains
+$-1/2 \mathbf{I}_{\mathcal{X}\times\mathcal{X}}
++ \mathbf{K}_\Gamma$ is Fredholm due to 
+\cref{lem:stokehelmsrep}. 
+The off-diagonal blocks,
+denoted by $\mathbf{B}$ and $\mathbf{D}$, 
+are trivially compact because either the domain 
+or range of the operator is finite dimensional. 
+Finally, $\mathbf{F}$ is 
+Fredholm because it is a finite-dimensional linear
+operator. 
+Therefore, the full system is Fredholm.
+
+Due to the Fredholm alternative,
+it is suffices to establish the injectivity of
+the system \cref{eq:IntEqBiharm1new} to prove that 
+it is invertible.
+
+Suppose that $\bmu,\bc$ satisfy
+\begin{equation}
+\begin{bmatrix}
+-\frac{1}{2}\mathbf{I}_{\mathcal{X}\times\mathcal{X}} + 
+\mathbf{K}_{\Gamma} & \mathbf{B} \\
+\mathbf{D} & \mathbf{F} 
+\end{bmatrix}  
+\bbmat
+\bmu \\
+\bc
+\ebmat
+=
+\bbmat
+0 \\ 0
+\ebmat \, ,
+\label{eq:IntEqBiharm1newapp2}
+\end{equation}
+then $w$ defined by~\cref{eq:wrep}, satsifies the Helmholtz-Biharmonic
+equation~\cref{eq:helmbi,eq:helmbibc1,eq:helmbibc2} 
+with boundary conditions $f=g=0$.
+Since $k$ is not a buckling eigenfrequency, we conclude that $w\equiv 0$ 
+for $\bx \in \Omega$.
+
+Let $\bu = \nabla^{\perp} w$ and let 
+$\bu^{\mu} = ik \mathbf{S} [\bmu] + \mathbf{D}[\bmu] = u 
+-\mathbf{B} \bc - \mathbf{W}[\bmu]$.
+For each $\ell = 1,\ldots,N$, 
+let $\tilde{\Gamma}_{\ell} \subset \Omega$ be a curve which satisfies 
+$n\left(z_{j}, \tilde{\Gamma}_{\ell}\right) = \delta_{j\ell}$, 
+where $n\left(z,\gamma\right)$ represents the winding number 
+of the curve $\gamma$ about z. 
+Because $\mathbf{u} = \nabla^{\perp} w$ and $w\equiv 0$ in $D$,
+we have 
+\begin{equation}
+\int_{\tilde{\Gamma}_\ell} (\Delta + k^2) \bu \cdot \boldsymbol{\tau} \, dS = 0 .
+\end{equation}
+We observe that $\bu^\mu$ corresponds
+to a Helmholtz-Stokes velocity field in $D$. Let $p$ be 
+its associated pressure. Then
+\begin{equation}
+\int_{\tilde{\Gamma}_k} (\Delta+k^2) \bu^\mu 
+\cdot \boldsymbol{\tau}
+\, dS = \int_{\tilde{\Gamma}_k} \nabla p \cdot \boldsymbol{\tau} \, dS = 0 \, .
+\end{equation}
+Further, a simple calculation shows that 
+\begin{equation}
+\int_{\tilde{\Gamma}_\ell} (\Delta + k^{2}) \nabla^{\perp} c_j 
+\log (r_j) \cdot \boldsymbol{\tau} \, dS = 
+2 \pi k^2 c_{j} \delta_{j\ell} \, ,
+\end{equation}
+for $j = 1, \ldots, N$.
+Combining these equations, we conclude that
+\begin{equation}
+0 = \int_{\tilde{\Gamma}_j} (\Delta +k^2) \bu \cdot 
+\boldsymbol{\tau} \, dS =
+\int_{\tilde{\Gamma}_j} (\Delta +k^2)( \mathbf{u}^\mu + \mathbf{B}\mathbf{c} )
+\cdot \boldsymbol{\tau} \, dS =  
+2\pi k^2 c_j \, .
+\end{equation}
+Thus $c_j = 0$ for $j=1,2,\ldots N$.
+
+The system of equations~\cref{eq:IntEqBiharm1newapp2} then reads
+\begin{align}
+\left(-\frac{1}{2}\mathbf{I}_{\mathcal{X}\times\mathcal{X}} 
++ \mathbf{K}_\Gamma \right) 
+\boldsymbol{\mu} &= 0 \, . \label{eq:IntEq1} \\
+\mathbf{B} \bmu &= -c_{0} \left(|\Gamma_{0}|, |\Gamma_{2}| \ldots |\Gamma_{n}| 
+\,. 
+\right)
+\end{align}
+This implies that $\bu^{\mu}$ defined above satisfies the
+Helmholtz-Stokes equation with the integral constraints
+\begin{equation}
+\frac{1}{|\Gamma_{j}|} 
+\int_{\Gamma_{j}} \left(\nabla^{\perp}\right)^{-1} \bu ds = -c_{0} 
+\, .
+\end{equation}
+From~\cref{lem:conshelmbieig}, we conclude that $\bu^{\mu} \equiv 0$ 
+for $\bx \in \Omega$.
+Using properties of the layer potentials, $\bu^{\mu}$ satisfies that
+Helmholtz-Stokes equation in $\R^{2} \setminus \Omega$
+along with the radiation condition~\cref{def:radcond}.
+Let $\bu^{\mu,+}, \ff^{\mu,+}$ denote the exterior limits, i.e.
+\begin{align}
+\bu^{\mu,+}(\bx_{0}) &=
+\lim_{\substack{\bx \to \bx_{0}\\ \bx \in \R^{2} \setminus \Omega}}
+\bu(\bx)\ , , \\ 
+\ff^{\mu,+}(\bx_{0}) &=
+\lim_{\substack{\bx \to \bx_{0}\\ \bx \in \R^{2} \setminus \Omega}}
+\ff(\bx) \, , \\ 
+\end{align}
+where $\bx_{0} \in \Gamma$.
+Using the jump conditions for the layer potentials, we conclude that
+\begin{equation}
+\ff^{\mu,+}(\bx) = ik \bmu (\bx) \quad \text{and} \quad 
+\bu^{\mu,+}(\bx) = \bmu
+(\bx) \quad \bx \in \Gamma \,. 
+\label{eq:bcaux}
+\end{equation}
+Thus, in the exterior of the outer-boundary $\Gamma_{0}$, 
+$\bu^{\mu,+}$ satisfies the Helmholtz-Stokes equation with the impendance
+boundary condition
+\begin{equation}
+\ff^{\mu,+} -ik \bu^{\mu,+} = 0 \quad \bx \in \Gamma_{0} \, .
+\end{equation}
+From uniqueness of solutions to the exterior impedance problem, we
+conclude that $\bu^{\mu,+}\equiv 0$ for $\bx$ in the exterior of 
+$\Gamma_{0}$.
+Thus $\bmu(\bx) = 0$ for $\bx \in \Gamma_{0}$.
+Let $D_{j}$ denote the interior region of the obstacle boundary
+$\Gamma_{j}$, for $j=1,2,\ldots n$. 
+Recall that $\bu^{\mu}$ satisfies the Stokes-Helmholtz equation in $D_{j}$.
+Using Green's identities for the Stokes-Helmholtz equations, we get 
+\begin{equation}
+\int_{D_{j}} |e(\bu^{\mu,+})|^{2}  - \overline{k}^{2} |\bu^{\mu,+}|^2) dV = 
+\int_{\Gamma_{j}} \bu^{\mu,+} \cdot \overline{\ff}^{\mu,+} dS \, .
+\end{equation}
+Taking the imaginary part of the above equation and using~\cref{eq:bcaux}, 
+we get
+\begin{equation}
+2 \text{Re}(k) \text{Im}(k) \int_{D_{j}} |\bu^{\mu,+}|^2 dV 
++ \text{Re}(k) \int_{\Gamma_{j}} |\bmu|^2 ds = 0 \, .
+\end{equation}
+This implies that $\bmu =0$ for all $\bx \in \Gamma_{j}$, $j=1,2,\ldots n$.
+
+Finally, because $\bmu =0$ for all $\bx \in \Gamma$ and 
+$c_{j}= 0$, $j=1,2,\ldots n$, 
+we get that $w \equiv c_{0}$ for all $\bx \in \Omega$. 
+Since $w\equiv 0$, it then follows that $c_{0} = 0$ as well, proving the 
+injectivity of the system.
+
+\end{proof}
 \subsection{Existence results}

### 2019-01-14 doc/draft-01/02prelim.tex
in which our hero updates the intro and adds some references
Updating paper
update text, add proof of radiation condition
update appendix
updating appendix
fix sign in def of bi-helmholtz green's function
update equation names

@@
 Similarly, $\nabla^\bot = (-\partial_{x_2},\partial_{x_1})^\intercal$.
+Upper-case script characters (e.g. $\mathcal{K}$) are reserved for
+operators on Banach spaces, with $\mathcal{I}$ denoting the
+identity.
 
@@
 some natural growth or decay conditions as $|\xx-\yy| \to \infty$.
-The Green's function of the Helmholtz-biharmonic equation
+The Green's function of the oscillatory biharmonic equation
 \cref{eq:buck1} is given by 
 \begin{equation}
-  \Gbh(\xx,\yy) = -\frac{1}{k^2}
+  \Gbh(\xx,\yy) = \frac{1}{k^2}
   \left (\frac{1}{2\pi} \log |\xx-\yy| +
@@
 \end{equation}
-where $k$ is the Helmholtz paramater in the Helmholtz-Biharmonic equation,
+where $k$ is the Helmholtz paramater in the oscillatory biharmonic equation,
 and $H_{0}^{1}(r)$ is the Hankel function of the first kind of order zero.
@@
 \begin{equation}
-  \Glap(\xx,\yy) = -\frac{1}{2\pi} \log |\xx-\yy| \; ,
+  \Glap(\xx,\yy) = \frac{1}{2\pi} \log |\xx-\yy| \; ,
 \end{equation}
@@
 \begin{equation}
-  \Ghelm(\xx,\yy) = \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \; .
+  \Ghelm(\xx,\yy) = -\frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \; .
 \end{equation}
@@
 biharmonic equation, albeit for different boundary conditions. With minor modifications, their formulation
-can also be adopted for the solution of the Dirichlet problem for the Helmholtz-biharmonic equation
+can also be adopted for the solution of the Dirichlet problem for the oscillatory biharmonic equation
 \begin{align}
 \Delta (\Delta + k^2) w &= 0 \quad \text{in} \quad \Omega \label{eq:helmbi} \\
-w &= f \quad \text{on} \quad \Gamma \\
-\dwdn &=g \quad \text{on} \quad \Gamma \,,
+w &= f \quad \text{on} \quad \Gamma \label{eq:helmbibc1} \\
+\dwdn &=g \quad \text{on} \quad \Gamma \label{eq:helmbibc2} \,,
 \end{align}
@@
 Then there exists a unique solution $\sigma_{1},\sigma_{2} \in \cC^{2}$ which satisfies~\cref{eq:farkIntEq}. 
-Furthermore, $w(\bx)$ defined via~\cref{eq:farkRep} satisfies the Helmholtz-Biharmonic equation~\cref{eq:helmbi}
+Furthermore, $w(\bx)$ defined via~\cref{eq:farkRep} satisfies the oscillatory biharmonic equation~\cref{eq:helmbi}
 along with the boundary conditions $w(\bx)=f(\bx)$ and $\dwdn(\bx) = g(\bx)$ for $\bx \in\Gamma$.
+\label{lem:farkinv}
 \end{lem}
@@
 we will refer to \cref{eq:helmstokes,eq:helmstokescty} as the
-Helmholtz-Stokes equations.
+oscillatory Stokes equations.
 
@@
 
-\begin{equation}
+\begin{equation} \label{eq:stokeslet}
   \GG = - \II \Delta \Gbh + \nabla \otimes \nabla \Gbh
@@
 
-\begin{equation}
+\begin{equation} \label{eq:doublelayer}
   \DD \bmu (\xx) = \int_\Gamma \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy)
@@
 
-\begin{align}
+\begin{align} \label{eq:stokesdlkernel}
   \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy) \right )^\intercal

### 2019-01-14 doc/draft-01/08append.tex
updating appendix
update equation names

@@
 In the following lemma, we present an integral indentity involving the
-Green's function of the Helmholtz-biharmonic equation.
+Green's function of the oscillatory biharmonic equation.
 \begin{lem}
-Suppose that $\Gbh$ is the Green's function of the Helmholtz-biharmonic equation 
+Suppose that $\Gbh$ is the Green's function of the oscillatory biharmonic equation 
 with Helmholtz parameter $k$. Suppose that $v:\R^{2} \to \R$ is a compactly supported smooth
@@
 
-\section{Existence and uniqueness results for the Helmholtz-Stokes PDE}
+\section{Existence and uniqueness results for the oscillatory Stokes PDE}
 
 In this section, we develop some existence and uniqueness
-results for the Helmholtz-Stokes PDE.
+results for the oscillatory Stokes PDE.
 %
@@
 i.e. specifying the surface traction on a boundary is
-the Neumann problem for the Helmholtz-Stokes PDE.
+the Neumann problem for the oscillatory Stokes PDE.
 
@@
 \begin{definition} \label{def:radcond}
-Let $(\bu,p)$ satisfy the Helmholtz-Stokes equations in
+Let $(\bu,p)$ satisfy the oscillatory Stokes equations in
 the exterior of a bounded domain. We say that
@@
 \begin{proposition}
-The Helmholtz-Stokeslet, as in \eqref{eq:stokeslet}, satisfies
+The oscillatory Stokeslet, as in \eqref{eq:stokeslet}, satisfies
 the radiation condition in Definition \ref{def:radcond}.
@@
 $\int_\Gamma \bmu\cdot \bnu dS = 0$, where $\bnu$ denotes the
-outward normal to the curve $\Gamma$, the Helmholtz-Stokes
+outward normal to the curve $\Gamma$, the oscillatory Stokes
 double layer potential $\DD\bmu$, as in \eqref{eq:doublelayer},
@@
 \label{lem:rep}
-Suppose that $(\bu,p)$ satisfies the Helmholtz-Stokes equation in 
+Suppose that $(\bu,p)$ satisfies the oscillatory Stokes equation in 
 an unbounded region $E$ along with the radiation 
@@
 \end{equation}
-Since $\bu$ satisfies the Helmholtz-Stokes equation $E \cap B_{r}(0)$,
+Since $\bu$ satisfies the oscillatory Stokes equation $E \cap B_{r}(0)$,
 using a couple of applications of the divergence theorem, we have that
@@
 In the next lemma, we prove the analogue of Rellich's lemma for the
-Helmholtz-Stokes equation. 
+oscillatory Stokes equation. 
 \begin{lem}
 \label{lem:rellich}
-Suppose that $\bu$ satisfies the Helmholtz-Stokes equation in an unbounded
+Suppose that $\bu$ satisfies the oscillatory Stokes equation in an unbounded
 region $E$.  
@@
 We first note that each component of $\bu= (u_{1},u_{2})$ satisfies the 
-Helmholtz-Biharmonic equation in $E$, i.e.
+oscillatory biharmonic equation in $E$, i.e.
 \begin{equation}
@@
 \end{equation}
-Since $u_{j}$, $j=1,2$ satisfies the Helmholtz-biharmonic equation,
+Since $u_{j}$, $j=1,2$ satisfies the oscillatory biharmonic equation,
 the functions $a_{j,n}$ are linear combinations of 
@@
 Suppose that $\Im(k)\geq 0$ and 
-that $(\bu,p)$ is a radiating solution to the Helmholtz-Stokes
+that $(\bu,p)$ is a radiating solution to the oscillatory Stokes
 equation in $E$ with $\bu =0$ on the boundary $\Gamma$, then
@@
 Suppose that $\Im(k)\geq 0$ and 
-that $(\bu,p)$ is a radiating solution to the Helmholtz-Stokes
+that $(\bu,p)$ is a radiating solution to the oscillatory Stokes
 equation in $E$ with $\ff = 0$ on the boundary $\Gamma$, then
@@
 $(\bu,p)$ is a radiating solution of the
-Helmholtz-Stokes equation in $E$ which satisfies
+oscillatory Stokes equation in $E$ which satisfies
 the homogeneous impednace boundary condition
@@
 \begin{equation}
-\int_{\Gamma_{j}} w_{j} ds = 0 \quad \forall j=1,2,\ldots n \, .
+\int_{\Gamma_{j}} w\, ds = 0 \quad \forall j=1,2,\ldots n \, .
 \end{equation}
@@
 \end{equation}
-Furthermore, since $\bu$ satisfies the Helmholtz-Stokes equations, 
+Furthermore, since $\bu$ satisfies the oscillatory Stokes equations, 
 $w$ satisfies
@@
 a uniqueness result for the 
-solutions to the Helmholtz-Stokes equations whenever $k$ is
+solutions to the oscillatory Stokes equations whenever $k$ is
 not a buckling value and the stream function associated with the
@@
 \end{equation}
-then $w$ defined by~\cref{eq:wrep}, satsifies the Helmholtz-Biharmonic
+then $w$ defined by~\cref{eq:wrep}, satsifies the oscillatory biharmonic
 equation~\cref{eq:helmbi,eq:helmbibc1,eq:helmbibc2} 
@@
 We observe that $\bu^\mu$ corresponds
-to a Helmholtz-Stokes velocity field in $D$. Let $p$ be 
+to a oscillatory Stokes velocity field in $D$. Let $p$ be 
 its associated pressure. Then
@@
 This implies that $\bu^{\mu}$ defined above satisfies the
-Helmholtz-Stokes equation with the integral constraints
+oscillatory Stokes equation with the integral constraints
 \begin{equation}
@@
 Using properties of the layer potentials, $\bu^{\mu}$ satisfies that
-Helmholtz-Stokes equation in $\R^{2} \setminus \Omega$
+oscillatory Stokes equation in $\R^{2} \setminus \Omega$
 along with the radiation condition~\cref{def:radcond}.
@@
 Thus, in the exterior of the outer-boundary $\Gamma_{0}$, 
-$\bu^{\mu,+}$ satisfies the Helmholtz-Stokes equation with the impendance
+$\bu^{\mu,+}$ satisfies the oscillatory Stokes equation with the impendance
 boundary condition
@@
 $\Gamma_{j}$, for $j=1,2,\ldots n$. 
-Recall that $\bu^{\mu}$ satisfies the Stokes-Helmholtz equation in $D_{j}$.
-Using Green's identities for the Stokes-Helmholtz equations, we get 
+Recall that $\bu^{\mu}$ satisfies the oscillatory Stokes equation in $D_{j}$.
+Using Green's identities for the oscillatory Stokes equations, we get 
 \begin{equation}

### 2019-01-14 doc/draft-01/08append2.tex
update equation names

@@
 \item Show uniqueness of solutions to the impedence, velocity, and surface
-traction boundary value problem in exterior domains for the Stokes-Helmholtz
+traction boundary value problem in exterior domains for the oscillatory Stokes
 PDEs. In order to prove this, we need the following lemmas:
@@
 velocity and surface traction boundary value problems on unbounded
-domains for the Stokes-Helmholtz equation.
+domains for the oscillatory Stokes equation.
 We focus on the proof for the velocity boundary value problem. 
@@
 at $\infty$.
-We propose the following radiation conditions for the Stokes-Helmholtz 
+We propose the following radiation conditions for the oscillatory Stokes 
 equation
@@
 \label{lem:rep}
-Suppose that $\bu$ satisfies the Stokes-Helmholtz equation in 
+Suppose that $\bu$ satisfies the oscillatory Stokes equation in 
 an unbounded region $E$ along with the radiaition 
@@
 \end{equation}
-Since $\bu$ satisfies the Stokes-Helmholtz equation $E \cap B_{r}(0)$,
+Since $\bu$ satisfies the oscillatory Stokes equation $E \cap B_{r}(0)$,
 using a couple of applications of the divergence theorem, we have that
@@
 
-In the next lemma, we prove the analogue of Rellich's lemma for the Stokes-
-Helmholtz equation. 
+In the next lemma, we prove the analogue of Rellich's lemma
+for the oscillatory Stokes equation. 
 \begin{lem}
 \label{lem:rellich}
-Suppose that $\bu$ satisfies the Stokes-Helmholtz equation in an unbounded
+Suppose that $\bu$ satisfies the oscillatory Stokes equation in an unbounded
 region $E$.  
@@
 Suppose that $\text{Im}(\omega)\geq 0$ and 
-that $\bu$ is a radiating solution to the Stokes-Helmholtz
+that $\bu$ is a radiating solution to the oscillatory Stokes
 equation in $E$ with $\bu =0$ on the boundary $\Gamma$, then

### 2019-01-16 doc/draft-01/02prelim.tex
add matlab files (things are still a bit rough) also added mathematica notebooks that are less crucial

@@
 
-Let $L_x$ denote a linear differential operator. A fundamental
-solution $G(\xx,\yy)$ of $L_x$ satisfies the equation
-$L_x G(\xx,\yy) = \delta_y(\xx)$ in the distributional sense, i.e.
+Let $\mathcal{L}_x$ denote a linear differential operator. A fundamental
+solution $G(\xx,\yy)$ of $\mathcal{L}_x$ satisfies the equation
+$\mathcal{L}_x G(\xx,\yy) = \delta_y(\xx)$ in the distributional sense, i.e.
 for sufficiently smooth $f$
 \begin{equation}
-  L_x \int_{\R^2} G(\xx,\yy) f(\yy) \, dy = f(\xx) \; .
+  \mathcal{L}_x \int_{\R^2} G(\xx,\yy) f(\yy) \, dy = f(\xx) \; .
 \end{equation}
@@
 \end{equation}
-
-\subsection{A Farkas-style integral representation}
-
-In \cite{Farkas89}, Farkas derived integral equation formulations
-for the solution of the Dirichlet problem for the biharmonic equation ($k=0$). 
-In this formulation, the solution 
-$w$ is represented as a sum of two layer potentials
-\begin{equation}
-  w(\xx) = \int_\Gamma \Kfark_1 (\xx,\yy) \sigma_1(\yy) \, dS(\yy)
-  + \int_\Gamma \Kfark_2(\xx,\yy) \sigma_2(\yy) \, dS(\yy) \; ,
-  \label{eq:farkRep}
-\end{equation}
-where $\sigma_{1}$, and $\sigma_{2}$ are unknown densities, and the kernels
-$K_{1}^{F}$, and $K_{2}^{F}$ are linear combinations of derivatives of
-the biharmonic Green's function and appropriately chosen to get second kind integral equations
-for the unknown densities $\sigma_{1}$ and $\sigma_{2}$ on imposing the boundary conditions.
-
-In \cite{jiang2013second}, Jiang extended the Farkas formulation for the solution of the modified
-biharmonic equation, albeit for different boundary conditions. With minor modifications, their formulation
-can also be adopted for the solution of the Dirichlet problem for the oscillatory biharmonic equation
-\begin{align}
-\Delta (\Delta + k^2) w &= 0 \quad \text{in} \quad \Omega \label{eq:helmbi} \\
-w &= f \quad \text{on} \quad \Gamma \label{eq:helmbibc1} \\
-\dwdn &=g \quad \text{on} \quad \Gamma \label{eq:helmbibc2} \,,
-\end{align}
-where $f,g$ are prescribed functions on the boundary.
-
-For two points on the plane, $\xx$ and $\yy$, let $\br = \yy - \xx$. Let the kernels $K_{1}^{F}$, and 
-$K_{2}^{F}$ be defined by 
-\begin{align}
-  \Kfark_1(\xx,\yy) &= \partial_{n_{y}n_{y}n_{y}}\Gbh(\xx,\yy)
-  + 3 \partial_{n_{y}\tau_{y}\tau_{y}}\Gbh(\xx,\yy) + k^{2} \partial_{n_{y}}\Gbh(\xx,\yy)\; , \label{eq:kf1} \\
-  \Kfark_2(\xx,\yy) &= -\partial_{n_{y}n_{y}}\Gbh(\xx,\yy)
-  + \partial_{\tau_{y}\tau_{y}}\Gbh(\xx,\yy) \label{eq:kf2} \; .
-\end{align}
-More explicitly, we have
-\begin{align}
-  \Kfark_1(\xx,\yy) &=  -\dfrac{\br \cdot \bn(\yy)}{|\br|^2}  \cdot \left( \frac{3 i}{2} H_0^{(1)}(k|\br|) - \frac{5 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{6}{\pi k^2 |\br|^2} + \frac{1}{2\pi}  \right) +     \\
-  & \quad \dfrac{\left(\br \cdot \bn(\yy)\right)^3}{|\br|^4} \cdot \left( 2i H_0^{(1)}(k|\br|) - \frac{7 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{8}{\pi k^2 |\br|^2}  \right) \, , \nonumber \\
-  \Kfark_2(\xx,\yy) &=  -\left(\frac{1}{2}-\dfrac{\left(\br \cdot \bn(\yy)\right)^2}{|\br|^2} \right)  \cdot \left( \frac{i}{2} H_0^{(1)}(k|\br|) - \frac{i}{k|\br|} H_1^{(1)}(k|\br|) + \frac{2}{\pi k^2 |\br|^2}  \right)\; .
-\end{align}
-
-On enforcing the Dirichlet boundary conditions for
-$w$, we obtain the integral equation
-\begin{equation}
-  \begin{split}
-    \begin{pmatrix}
-      f(\xx) \\
-      g(\xx)
-    \end{pmatrix} &= 
-    \int_\Gamma
-    \begin{pmatrix}
-      \Kfark_{11}(\xx,\yy) & \Kfark_{12}(\xx,\yy) \\
-      \Kfark_{21}(\xx,\yy) & \Kfark_{22}(\xx,\yy)
-    \end{pmatrix}
-    \begin{pmatrix}
-      \sigma_1(\yy)\\
-      \sigma_2(\yy)
-    \end{pmatrix}
-    \, dS(\yy) \\
-    &\quad + \begin{pmatrix}
-      1/2 & 0 \\
-      -\kappa(\xx) & 1/2
-    \end{pmatrix}
-    \begin{pmatrix}
-      \sigma_1(\xx)\\
-      \sigma_2(\xx)
-    \end{pmatrix} \; , \label{eq:farkIntEq} 
-  \end{split}
-\end{equation}
-where $\kappa$ is the signed curvature at $\xx \in \Gamma$.
-The kernels are given
-by $\Kfark_{11} = \Kfark_1$, $\Kfark_{12} = \Kfark_2$,
-\begin{align}
-  \Kfark_{21}(\xx,\yy) &= \left(\Kfark_1(\xx,\yy)\right )_{n_x} \nonumber \\
-  &= \bn(\xx) \cdot \nabla_{\xx} K_{21}^{F}(\xx,\yy) \; \label{eq:farkK21},\\
-  \Kfark_{22}(\xx,\yy) &= \left(\Kfark_2(\xx,\yy)\right )_{n_x} \nonumber \\
-  &= \bn(\xx) \cdot \nabla_{\xx} K_{22}^{F}(\xx,\yy) \label{eq:farkK22} \; .
-\end{align}
-
-The following lemma shows that the integral equation~\cref{eq:farkIntEq} is invertible for smooth domains
-whenever $k$ is not a buckling eigenfrequency.
-
-\begin{lem}
-Suppose that $\Omega \subset \R^2$ is a simply connected region whose boundary $\Gamma$ is $\cC^{2}$. 
-Furthermore, suppose that $k$ is not a buckling eigenfrequency of $\Omega$, i.e., the only solution $w$ to~\cref{eq:buck1,eq:buck2,eq:buck3} is  $w \equiv 0$.
-Suppose further that $f,g \in \cC^{2}(\Gamma)$.
-Then there exists a unique solution $\sigma_{1},\sigma_{2} \in \cC^{2}$ which satisfies~\cref{eq:farkIntEq}. 
-Furthermore, $w(\bx)$ defined via~\cref{eq:farkRep} satisfies the oscillatory biharmonic equation~\cref{eq:helmbi}
-along with the boundary conditions $w(\bx)=f(\bx)$ and $\dwdn(\bx) = g(\bx)$ for $\bx \in\Gamma$.
-\label{lem:farkinv}
-\end{lem}
-
-\begin{proof}
-  The proof is a minor modification of the one presented in~\ref{eq:shidongmodbi}
-  and is contained in~\cref{sec:farkproof}.
-\end{proof}
-
-The kernels $\Kfark_1$ and $\Kfark_2$ are
-constructed with the goal that the $\Kfark_{ij}$ are
-as smooth as possible. Suppose that the boundary
-$\Gamma$ is of class $C^k$. Then, the kernels,
-$\Kfark_{ij}(\xx,\yy)$, are $C^{k-2}$ functions on the boundary
-for each $\yy \in \Gamma$.
-Therefore, on a smooth
-boundary, these kernels are smooth. However, on a
-domain with a corner, we note 
-that the kernel $\Kfark_{21}$
-has a singularity with strength $r^{-2}$ (see~\cref{fig:ker21plot}). 
-This singularity, in addition to the term in \cref{eq:farkIntEq}
-which explicitly involves the
-curvature, makes the representation \cref{eq:farkRep}
-unstable for domains with high curvature (or
-corners).
 

### 2019-01-16 matlab/src/hbhdirmat.m

@@ -1,0 +1,136 @@
+
+function sysmat = hbhdirmat(chunker,nchs,ccs,zk,cs,cd,intparams)
+%HBHDIRMAT
+%
+% This function builds the system matrix for the Helmholtz biharmonic
+% Dirichlet problem on the given domain. This is the 'slow' version...
+%
+
+% geometry stuff
+
+disp('here 1')
+  
+k = chunker.k;
+nch = chunker.nch;
+
+whts = chunkwhts(chunker); whts = whts(:);
+rnorms = chunknormals(chunker); rnorms = reshape(rnorms,2,k*nch);
+
+ncomp = length(nchs);
+
+whtsbycomp = zeros(length(whts),ncomp);
+
+ind = 1;
+for i = 1:ncomp
+    whtsbycomp(ind:ind+nchs(i)*k-1,i) = whts(ind:ind+nchs(i)*k-1);
+    ind = ind+nchs(i)*k;
+end
+
+ngeo = 2*k*nch;
+nsys = 2*k*nch+ncomp;
+
+sysmat = zeros(nsys,nsys) + 1i*zeros(nsys,nsys);
+
+
+%% effect of sources in holes
+
+chunks = reshape(chunker.chunks,2,k*nch);
+logs = zeros(k*nch,ncomp);
+logperps = zeros(2*k*nch,ncomp);
+
+% outer boundary 'source' is just a constant
+
+logs(:,1) = 1;
+
+% get other sources if they exist
+
+if ncomp > 1
+    [val,grad] = glapfun(ccs(:,2:end),chunks);
+    logs(:,2:end) = val;
+    logperps(1:2:end,2:end) = -grad(:,:,2);
+    logperps(2:2:end,2:end) = grad(:,:,1);
+end
+
+% bottom right is integral of log charges
+
+sysmat(ngeo+1:end,ngeo+1:end) = whtsbycomp.'*logs;
+
+% top right is velocity due to log charges (grad perp of charges)
+
+sysmat(1:ngeo,ngeo+1:end) = logperps;
+
+%% effect of stokeslet-type layer potentials
+
+% form stokes densities to velocity field (standard stokes dirichlet mat)
+
+disp('here 3')
+
+fkern = @(s,t,sn,tn) helmstokessubmat(zk,s,t,sn,cs,cd);
+ndims(1) = 2; ndims(2) = 2;
[…]

### 2019-01-16 matlab/src/hbhdirmat_lap_pre.m

@@ -1,0 +1,59 @@
+
+function yylap = hbhdirmat_lap_pre(chunker,nchs,intparams)
+
+% geometry stuff
+
+k = chunker.k;
+nch = chunker.nch;
+
+whts = chunkwhts(chunker); whts = whts(:);
+rnorms = chunknormals(chunker); rnorms = reshape(rnorms,2,k*nch);
+
+ncomp = length(nchs);
+
+whtsbycomp = zeros(length(whts),ncomp);
+
+ind = 1;
+for i = 1:ncomp
+    whtsbycomp(ind:ind+nchs(i)*k-1,i) = whts(ind:ind+nchs(i)*k-1);
+    ind = ind+nchs(i)*k;
+end
+
+ngeo = 2*k*nch;
+
+% want whtsbycomp.'*S*(1/2+sprime+ones)^(-1)*Stau, use transpose trick
+
+% evaluate S^T*whtsbycomp 
+
+fkernS = @(s,t,sn,tn) glapkern(s,t,sn,tn,'s');
+ndims(1) = 1; ndims(2) = 1;
+tic; slap = chunkskernelmat(chunker,fkernS,ndims,intparams); toc
+%tic; [Std,Sinds] = chunkskernelmattd(chunker,fkernS,ndims,intparams); toc
+
+slapintstrans = slap.'*whtsbycomp;
+
+% then solve (1/2+sprime+ones)^(-T)*(S^T*whtsbycomp)
+
+fkernSprime = @(s,t,sn,tn) glapkern(s,t,sn,tn,'sprime');
+ndims(1) = 1; ndims(2) = 1;
+tic; sprime = chunkskernelmat(chunker,fkernSprime,ndims,intparams); toc
+
+sprime = sprime + 0.5*eye(ngeo/2,ngeo/2) + chunkonesmat(chunker);
+
+afun = @(x) sprime.'*x;
+
+yylap = zeros(size(slapintstrans));
+
+for i = 1:ncomp
+    yylap(:,i) = gmres(afun,slapintstrans(:,i),[],1.0e-12,50);
+end
+
+% finally evaluate stau^T*((1/2+sprime+ones)^(-T)*(S^T*whtsbycomp))
+
+ndim1 = 1;
+stau = zeros(size(slap));
+for i = 1:ngeo/2
+    stau(:,i) = chunkderf(chunker,slap(:,i),ndim1);
+end
+
+yylap = stau.'*yylap;

### 2019-01-16 matlab/src/hbhdirmat_pre.m

@@ -1,0 +1,109 @@
+
+function [stokestd,stokesinds,sysmatbl,sysmatbr,sysmattr] = hbhdirmat_pre(chunker,nchs,ccs,zk,cs,cd,intparams,varargin)
+%HBHDIRMAT
+%
+% This function builds the system matrix for the Helmholtz biharmonic
+% Dirichlet problem on the given domain. This is the 'slow' version...
+%
+
+
+
+% geometry stuff
+
+k = chunker.k;
+nch = chunker.nch;
+
+whts = chunkwhts(chunker); whts = whts(:);
+rnorms = chunknormals(chunker); rnorms = reshape(rnorms,2,k*nch);
+
+ncomp = length(nchs);
+
+whtsbycomp = zeros(length(whts),ncomp);
+
+ind = 1;
+for i = 1:ncomp
+    whtsbycomp(ind:ind+nchs(i)*k-1,i) = whts(ind:ind+nchs(i)*k-1);
+    ind = ind+nchs(i)*k;
+end
+
+ngeo = 2*k*nch;
+nsys = 2*k*nch+ncomp;
+
+%sysmat = zeros(nsys,nsys) + 1i*zeros(nsys,nsys);
+
+
+%% effect of sources in holes
+
+chunks = reshape(chunker.chunks,2,k*nch);
+logs = zeros(k*nch,ncomp);
+logperps = zeros(2*k*nch,ncomp);
+
+% outer boundary 'source' is just a constant
+
+logs(:,1) = 1;
+
+% get other sources if they exist
+
+if ncomp > 1
+    [val,grad] = glapfun(ccs(:,2:end),chunks);
+    logs(:,2:end) = val;
+    logperps(1:2:end,2:end) = -grad(:,:,2);
+    logperps(2:2:end,2:end) = grad(:,:,1);
+end
+
+% bottom right is integral of log charges
+
+sysmatbr = whtsbycomp.'*logs + 1i*0.0;
+
+% top right is velocity due to log charges (grad perp of charges)
+
+sysmattr = logperps + 1i*0.0;
+
+%% effect of stokeslet-type layer potentials
+
+% form stokes densities to velocity field (standard stokes dirichlet mat)
+% near and self only
+
+fkern = @(s,t,sn,tn) helmstokessubmat(zk,s,t,sn,cs,cd);
+ndims(1) = 2; ndims(2) = 2;
+[stokestd,stokesinds] = chunkskernelmattd(chunker,fkern,ndims,intparams);
[…]

### 2019-01-16 matlab/src/helmstokesstreamsubmat_wpre.m

@@ -1,0 +1,17 @@
+function mat = helmstokesstreamsubmat_wpre(zk,src,targ,src_norm,cs,cd,streammattd,streammatinds)
+
+[~,ns] = size(src);
+[~,nt] = size(targ);
+mat2 = zeros(1,2,nt,ns);
+
+mex_id_ = 'zhelmstokesallstreammatmany(i dcomplex[x], i int[x], i double[], i int[x], i double[], i dcomplex[], i dcomplex[x], i dcomplex[x], io dcomplex[])';
+[mat2] = bhdeiggateway(mex_id_, zk, ns, src, nt, targ, src_norm, cs, cd, mat2, 1, 1, 1, 1, 1);
+
+mat2 = reshape(mat2,1,2,nt,ns);
+
+mat = zeros(1*nt,2*ns);
+mat(:,1:2:2*ns) = reshape(mat2(:,1,:,:),nt,ns);
+mat(:,2:2:2*ns) = reshape(mat2(:,2,:,:),nt,ns);
+
+end
+

### 2019-01-16 matlab/src/proxy_circ_pts.m

@@ -1,0 +1,14 @@
+
+function [proxy,pnorm] = proxy_circ_pts(p)
+
+if nargin < 1
+    p = 64;
+end
+
+theta = (0:(p-1))*2*pi/p;
+
+proxy = [1.5*cos(theta); 1.5*sin(theta)];
+
+pnorm = [cos(theta); sin(theta)];
+
+end

### 2019-01-16 matlab/src/proxy_square_pts.m

@@ -1,0 +1,19 @@
+
+function [proxy,pnorm] = proxy_square_pts(p)
+
+if nargin < 1
+    p = 64;
+end
+
+po4 = p/4;
+
+pts = -1.5+3*(0:(po4-1))*1.0/po4;
+one = ones(size(pts));
+
+proxy = [pts, one*1.5, -pts, -1.5*one;
+    -1.5*one, pts, 1.5*one, -pts];
+
+pnorm = [one*0, one, one*0, -one;
+    -one, one*0, one, one*0];
+
+end

### 2019-01-16 matlab/src/pxyfun_sq.m

@@ -1,0 +1,31 @@
+
+function [Kpxy,nbr] = pxyfun_sq(kern,proxy,pnorm,x,xnorm,slf,nbr,l,ctr)
+%PXYFUN_SQ proxy surface utility for square proxy surface
+%
+% kern should be a kernel function of the form 
+% submat = kern(src, targ, srcn, targn, slf)
+%
+% src and targ are (2,_) arrays of points
+% srcn and targn are corresponding normals (same format)
+% slf is the indices of the subset of the sources to use
+%
+% proxy should be a reference set of proxy points
+% pnorm should be corresponding outward normals
+% 
+% x are the points of the geometry
+% xnorm are the corresponding normals
+%
+% slf is a set of indices passed by the routine (relevant sources)
+% nbr is a set of candidate points inside the proxy surface
+% l length of a box at this level of the tree
+% ctr center of this box
+%
+
+  pxy = bsxfun(@plus,proxy*l,ctr(:));
+  N = size(x,2);
+  Kpxy = kern(x,pxy,xnorm,pnorm,slf)*1.0/N;
+  dx = x(1,nbr) - ctr(1);
+  dy = x(2,nbr) - ctr(2);
+  dist = max(abs([dx; dy]),[],1);
+  nbr = nbr(dist/l < 1.5);
+end

### 2019-01-16 matlab/src/starfish.m

@@ -1,0 +1,34 @@
+
+function [fvals] = fcurve(t,varargin)
+
+narms = 5;
+amp = 0.3;
+if nargin > 1 && ~isempty(varargin{1})
+    narms = varargin{1};
+end
+if nargin > 2 && ~isempty(varargin{2})
+    amp = varargin{2};
+end
+
+fvals = zeros(length(t),6);
+ct = cos(t);
+st = sin(t);
+cnt = cos(narms*t);
+snt = sin(narms*t);
+
+xs = (1+amp*cnt).*ct;
+ys = (1+amp*cnt).*st;
+dxs = -(1+amp*cnt).*st-narms*amp*snt.*ct;
+dys = (1+amp*cnt).*ct-narms*amp*snt.*st;
+d2xs = -dys-narms*amp*(narms*cnt.*ct-snt.*st);
+d2ys = dxs-narms*amp*(narms*cnt.*st+snt.*ct);
+
+fvals(:,1) = xs;
+fvals(:,2) = ys;
+fvals(:,3) = dxs;
+fvals(:,4) = dys;
+fvals(:,5) = d2xs;
+fvals(:,6) = d2ys;
+
+end
+

### 2019-01-16 matlab/test/testchunkskernmat.m

@@ -1,0 +1,45 @@
+
+%TESTCHUNKSKERNMAT
+%
+% This file tests whether or not chunks 
+% lib is wrapped properly
+
+cparams.eps = 1.0e-6;
+cparams.nchmax = 100000;
+cparams.nover = 2;
+narms = 5;
+amp = 0.5;
+tic; chunker = chunkfunc(@(t) starfish(t,narms,amp),cparams); toc
+
+chunker.nch
+
+xs = chunker.chunks(1,:,:); xs = xs(:);
+ys = chunker.chunks(2,:,:); ys = ys(:);
+
+figure(1)
+clf
+scatter(xs,ys)
+axis equal
+
+fkern = @(s,t,sn,tn) glapkern(s,t,sn,tn,'D');
+ndims(1) = 1; ndims(2) = 1;
+intparams.intorder = chunker.k;
+tic; D = chunkskernelmat(chunker,fkern,ndims,intparams); toc
+
+%
+sysmat = eye(size(D))-2*D;
+
+tic; d1 = det(sysmat); toc
+
+% hifie
+npts = length(xs);
+xhifie = chunker.chunks(1:2,:);
+
+%
+tic; F = hifie2(sysmat,xhifie,10,1e-10); toc
+tic; d2 = exp(hifie_logdet(F)); toc
+
+d1
+d2
+
+%scatter(real(e),imag(e))

### 2019-01-16 matlab/test/testchunkskernmat2.m

@@ -1,0 +1,55 @@
+
+%TESTCHUNKSKERNMAT2
+%
+% This file tests whether or not chunks 
+% lib is wrapped properly
+
+cparams.eps = 1.0e-6;
+cparams.nchmax = 100000;
+cparams.nover = 0;
+narms = 5;
+amp = 0.5;
+tic; chunker = chunkfunc(@(t) starfish(t,narms,amp),cparams); toc
+
+chunker.nch
+chunker.k*chunker.nch
+
+xs = chunker.chunks(1,:,:); xs = xs(:);
+ys = chunker.chunks(2,:,:); ys = ys(:);
+
+tic; mat1 = chunknormonesmat(chunker); toc
+tic; mat2 = normalonesmatwrap(chunker); toc
+
+rnorms = chunknormals(chunker);
+rnx = rnorms(1,:,:); rnx = rnx(:);
+rny = rnorms(2,:,:); rny = rny(:);
+
+figure(1)
+clf
+scatter(xs,ys)
+axis equal
+hold on
+quiver(xs,ys,rnx,rny)
+
+%%
+
+zk = 1.0;
+cd = -2.0 + 1i*0.0;
+cs = 0.0 + 1i*0.0;
+fkern = @(s,t,sn,tn) helmstokessubmat(zk,s,t,sn,cs,cd);
+ndims(1) = 2; ndims(2) = 2;
+intparams.intorder = chunker.k;
+tic; matul = chunkskernelmat(chunker,fkern,ndims,intparams); toc
+
+normonesmat = chunknormonesmat(chunker);
+matul = eye(size(matul)) + matul + normonesmat;
+
+%%
+
+wgeo = chunkpack(chunker);
+
+nchs(1) = chunker.nch;
+ccs = zeros(2,1);
+
+q1 = cs; q2 = cd;
+tic; sysmat = zhbhstokesmatbuild(zk,wgeo,nchs,ccs,q1,q2); toc

### 2019-01-16 matlab/test/testchunkslib.m

@@ -1,0 +1,21 @@
+
+%TESTCHUNKSLIB
+%
+% This file tests whether or not chunks 
+% lib is wrapped properly
+
+cparams.eps = 1.0e-6;
+cparams.nchmax = 100000;
+narms = 10;
+amp = 0.5;
+tic; chunker = chunkfunc(@(t) starfish(t,narms,amp),cparams); toc
+
+chunker.nch
+
+xs = chunker.chunks(1,:,:); xs = xs(:);
+ys = chunker.chunks(2,:,:); ys = ys(:);
+
+figure(1)
+clf
+scatter(xs,ys)
+axis equal

### 2019-01-16 matlab/test/testhbhdirmatbuild.m

@@ -1,0 +1,54 @@
+
+%TESTHBHDIRMAT
+%
+% This file tests whether or not chunks 
+% lib is wrapped properly
+
+cparams.eps = 1.0e-6;
+cparams.nchmax = 100000;
+cparams.nover = 0;
+narms = 5;
+amp = 0.5;
+tic; chunker = chunkfunc(@(t) starfish(t,narms,amp),cparams); toc
+
+chunker.nch
+chunker.k*chunker.nch
+
+xs = chunker.chunks(1,:,:); xs = xs(:);
+ys = chunker.chunks(2,:,:); ys = ys(:);
+
+tic; mat1 = chunknormonesmat(chunker); toc
+tic; mat2 = normalonesmatwrap(chunker); toc
+
+rnorms = chunknormals(chunker);
+rnx = rnorms(1,:,:); rnx = rnx(:);
+rny = rnorms(2,:,:); rny = rny(:);
+
+figure(1)
+clf
+scatter(xs,ys)
+axis equal
+hold on
+quiver(xs,ys,rnx,rny)
+
+%%
+
+zk = 10.0;
+cd = -2.0 + 1i*0.0;
+cs = 0.0 + 1i*0.0;
+nchs = ones(1,1);
+nchs(1) = chunker.nch;
+ccs = zeros(2,1);
+
+intparams.intorder = chunker.k;
+
+start = tic; sysmat1 = hbhdirmat(chunker,nchs,ccs,zk,cs,cd,intparams); toc(start)
+
+%%
+
+wgeo = chunkpack(chunker);
+start = tic; sysmat2 = zhbhstokesmatbuild(zk,wgeo,nchs,ccs,cs,cd); toc(start)
+
+%%
+hold off
+spy(abs(sysmat1-sysmat2)>1.0e-12)   

### 2019-01-16 matlab/test/testmultichunkfunc.m

@@ -1,0 +1,125 @@
+
+%TESTMULTICHUNKFUNC
+%
+% This file tests whether or not multichunkfunc is properly wrapped
+
+ncomp = 2;
+k = 16;
+lpars = 1000; % make long enough for domain description (at least 2*nmodes+2 +20)
+
+type = 'rmodes';
+
+eps = 1.0e-13*ones(ncomp,1);
+ifclosed = ones(ncomp,1);
+novers = 2*ones(ncomp,1);
+chsmall = ones(ncomp,1);
+tas = 0*ones(ncomp,1);
+tbs = 2*pi*ones(ncomp,1);
+
+pars = zeros(lpars,1);
+ipars = zeros(ncomp,1);
+
+ccs = zeros(2,ncomp);
+
+% describe boundary components in ipars and pars
+
+% component 1
+nmodes = 6;
+cx = 0.0; cy = 0.0;
+ccs(1,1) = cx; ccs(2,1) = cy;
+ipars(1) = 1; % starting index of component 1
+ii = ipars(1);
+pars(ii) = nmodes + 0.1;
+pars(ii+1) = 6 + 0.1; % always 6 (internal convention)
+pars(ii+2) = 1 + 0.1; % sign of orientation
+pars(ii+3) = cx;
+pars(ii+4) = cy;
+pars(ii+5) = 0.25; % coeff of constant zero mode
+% cos and sin coeffs for higher modes
+pars(ii+6) = 0; pars(ii+7) = 0;
+pars(ii+8) = 0; pars(ii+9) = 0;
+pars(ii+10) = 0; pars(ii+11) = 0.01;
+pars(ii+12) = 0.02; pars(ii+13) = 0;
+pars(ii+14) = 0.01; pars(ii+15) = 0;
+pars(ii+16) = 0; pars(ii+17) = 0; % nmodes = 6
+
+%component 2
+nmodes = 5;
+cx = 0.0; cy = 0.0;
+ccs(1,2) = cx; ccs(2,2) = cy;
+ipars(2) = ii+19;
+ii = ipars(2);
+pars(ii) = nmodes + 0.1;
+pars(ii+1) = 6 + 0.1; % always 6 (internal convention)
+pars(ii+2) = 1 + 0.1; % sign of orientation
+pars(ii+3) = cx;
+pars(ii+4) = cy;
[…]

### 2019-01-16 matlab/test/testsubmateval.m

@@ -1,0 +1,17 @@
+%TESTSUBMATEVAL
+
+
+ns = 16;
+nt = 16;
+
+src = randn(2,ns);
+targ = randn(2,nt);
+src_norm = randn(2,ns);
+
+cs = 1.0;
+cd = 1.0;
+zk = 1.0;
+
+tic; mat = helmstokessubmat(zk,src,targ,src_norm,cs,cd); time2 = toc
+
+ns*nt/time2

### 2019-01-16 matlab/test/testwithflam.m

@@ -1,0 +1,123 @@
+
+%TESTWITHFLAM
+%
+% This file tests using the matrix routines with
+% FLAM (slow version of matrix build for now).
+
+cparams.eps = 1.0e-6;
+cparams.nchmax = 100000;
+cparams.nover = 2;
+narms = 5;
+amp = 0.5;
+tic; chunker = chunkfunc(@(t) starfish(t,narms,amp),cparams); toc
+
+chunker.nch
+chunker.k*chunker.nch
+
+xs = chunker.chunks(1,:,:); xs = xs(:);
+ys = chunker.chunks(2,:,:); ys = ys(:);
+
+%tic; mat1 = chunknormonesmat(chunker); toc
+%tic; mat2 = normalonesmatwrap(chunker); toc
+
+rnorms = chunknormals(chunker);
+rnx = rnorms(1,:,:); rnx = rnx(:);
+rny = rnorms(2,:,:); rny = rny(:);
+
+%figure(1)
+%clf
+%scatter(xs,ys)
+%axis equal
+%hold on
+%quiver(xs,ys,rnx,rny)
+
+% build matrix
+
+zk = 0.1;
+cd = -2.0 + 1i*0.0;
+cs = 0.0 + 1i*0.0;
+nchs = ones(1,1);
+nchs(1) = chunker.nch;
+ccs = zeros(2,1);
+
+intparams.intorder = chunker.k;
+
+%
+
+start = tic; sysmat1 = hbhdirmat(chunker,nchs,ccs,zk,cs,cd,intparams); toc(start)
+
+%%
+
+%fkern = @(s,t,sn,tn) helmstokessubmat(zk,s,t,sn,cs,cd);
+%ndims(1) = 2; ndims(2) = 2;
+%tic; [stokestd,inds] = chunkskernelmattd(chunker,fkern,ndims,intparams); toc
+
+%%
+
+start = tic; yylap = hbhdirmat_lap_pre(chunker,nchs,intparams); toc(start)
+
+%% 
+
+start = tic; stokestd = hbhdirmat_pre(chunker,nchs,ccs,zk,cs,cd,intparams,yylap); toc(start)
+
+%% hifie
+[ntot,~] = size(sysmat1);
+npts = length(xs);
+xhifie = zeros(2,ntot);
[…]

### 2019-01-23 doc/draft-01-stokes/01intro.tex
adding stokes paper stuff

--- 2018-07-12 doc/draft-01/01intro.tex
@@
   we will refer to \cref{eq:buck1} as the
-  Helmholtz-biharmonic equation.
+  oscillatory biharmonic equation.
 \end{remark}
@@
 \cite{rachh2017integral}.
+
 In this paper, we develop a second kind integral

### 2019-02-08 doc/draft-01-stokes/01intro.tex
clean up stokes manuscript, update matlab routines

--- 2018-06-24 doc/draft-01/01intro.tex
@@
 
-Consider the pure bending of an isotropic and homogeneous thin clamped
-plate. 
-Let $\Omega$ denote the midline of the plate, $\Gamma$ denote the 
-boundary of $\Omega$ and $w$ denote the vertical displacement.
-The buckling problem consists of finding 
-values $k^{2}$ such that the boundary value problem
+The planar incompressible Stokes equations describe
+creeping flow in two dimensions. Let $\Omega \subset \R^2$
+be a domain with $C^2$ boundary. The eigenvalue problem seeks
+values $k^2$ such that
 
 \begin{align}
-\Delta (\Delta + k^2) w &= 0 \quad \textrm{in} \quad \Omega \label{eq:buck1} \; , \\
-w &= 0 \quad \textrm{on} \quad \Gamma \label{eq:buck2} \; ,\\
-\dwdn &=0 \quad \textrm{on} \quad \Gamma \label{eq:buck3} 
+  -\Delta \uu + \nabla p &= k^2 \uu \quad \textrm{in} \quad
+  \Omega \label{eq:ostokes} \; , \\
+  \nabla \cdot \uu &= 0 \; , \label{eq:ostokescty}
 \end{align}
-has a non-trivial solution. In a slight abuse of notation,
-these values and the corresponding solutions are often
-referred to as ``eigenvalues'' and ``eigenfunctions'',
-respectively. 
-It is well known that the buckling problem has a
-countable collection of such values
-$0 < k_{1}^{2} \leq k_{2}^2 \leq \ldots \uparrow \infty$,
+subject to certain boundary conditions, has a non-trivial solution.
+Let $\bsigma(\uu,p)$ denote the Cauchy stress tensor
+associated with the flow (defined below) and let $\bnu$ denote
+the outward normal along the boundary.
+In this work, we consider both the Dirichlet boundary condition,
+\begin{equation}
+  \uu = \bz \quad \textrm{on} \quad \Gamma \label{eq:ostokes_dir} \; ,
+\end{equation}
+and the Neumann boundary condition,
+\begin{equation}
+  \bsigma( \uu, p ) \cdot \bnu  = \bz \; . \label{eq:ostokes_neu}
+\end{equation}
+It is well known that there is a countable collection of such
+values $0 < k_{1}^{2} \leq k_{2}^2 \leq \ldots \uparrow \infty$,
 counting multiplicites.
@@
   When $k = i\alpha$, the differential equation
-  \cref{eq:buck1} is known as the modified biharmonic
+  \cref{eq:ostokes} is known as the modified Stokes
   equation. As there appears to be no preferred
   name for the equation with real-valued $k$,
-  we will refer to \cref{eq:buck1} as the
-  Helmholtz-biharmonic equation.
+  we will refer to \cref{eq:ostokes} as the
+  oscillatory Stokes equation.
 \end{remark}
-
-The eigenvalues (and eigenfunctions)
-of the boundary value problem \cref{eq:buck1,eq:buck2,eq:buck3}
-describe the critical buckling load (and deflection)
-of a thin plate under
-a compressive force applied along the edge. While the
-isotropy and homogeneity assumptions are restrictive,
-the equations are still of interest in materials design
-(CITATIONS). The analytical properties of the eigenvalues and
-eigenfunctions are also of interest from a mathematical
-perspective, often as they contrast with the eigenvalues
-and eigenmodes of an idealized drum (CITATIONS). For instance,
-it is well-known that the first eigenfunction of the
-drum problem (i.e. the eigenvalue problem of the Laplace
-equation with homogeneous Dirichlet boundary conditions)
-is either nonpositive or nonnegative on any domain.
-In contrast, it is possible for the first buckling
-eigenfunction of a convex domain with analytic boundary
-to take both positive and negative values \cite{antunes2011buckling}.
-
-Numerical simulations have long played an important
-role in the analyses described above and there are a number
-of available methods (note that some of the references
-included here are written in terms of the related
-Stokes eigenvalue problem, which has equivalent
-eigenvalues on simply connected domains). We do not
-seek to review the literature here but will provide
-some context for the present work. Finite element methods
-are ubiquitous in mechanical engineering applications
-and are flexible with respect to both the governing
-equations and the shape of the domain. Such a method
-would first obtain a ``weak'' form of the equations
-\cref{eq:buck1,eq:buck2,eq:buck3} and then 
-approximate the solution space in some
-finite dimensional basis, resulting in a discrete model
-for the buckling problem.
-The eigenvalues $k^2$ are then
-approximated by the eigenvalues of the discrete
-model \cite{johnson1974beam,rannacher1979nonconforming,
-  jia2009approximation,carstensen2014guaranteed}.
-Because of the fourth order term in \cref{eq:buck1},
-the system matrices resulting from a finite element
-discretization can have large condition numbers (growing
-like $1/h^4$ where $h$ is the diameter of a typical element
-in the discretization) which can cause numerical instability.
-
-Integral equation methods \cite{kress1989linear,
-  atkinson2009numerical,kitahara2014boundary} present
-a natural alternative to the finite element method
-for the buckling problem, because (a) the
-integral representation acts as an analytical preconditioner
-for the fourth order term and (b) the problem is reduced
-to one defined on the boundary of the domain alone,
-requiring fewer degrees of freedom to resolve the solution
-on a complex domain. In an integral equation method,
-the solution $w$ is represented in terms of a sum of
-two layer potentials (which a priori satisfy
-\cref{eq:buck1}) with unknown densities. Substituting this
-representation into the boundary conditions
-\cref{eq:buck2,eq:buck3} results in an integral equation
-for the unknown densities, which
-is in turn discretized using numerical quadrature.
-Unlike the original equation \cref{eq:buck1} and the weak
-formulation used in a finite element method, the integral
-equation for the unknown densities has a nonlinear dependence
-on the parameter $k^2$. In an integral equation method, then,
-the eigenvalues are found by searching for the values
-of $k^2$ where the discrete system for the unknown densities
-is no longer invertible.
-
-While integral equation methods for the buckling problem
-have been considered previously, the existing formulations
-have resulted in first kind integral equations, i.e. equations
-in which the operator is compact \cite{kitahara2014boundary,
-  antunes2011buckling}. This is unsatisfying from a theoretical
-perspective, because such operators are never invertible
-(though, they are injective precisely when $k^2$ is an
-eigenvalue \cite{kitahara2014boundary}) so that the
-relation between the non-invertibility of the discrete system
-and the eigenvalues is obscured. Further, such representations
-create numerical challenges because common measures of the
-``non-invertibility'' of a matrix, like the smallest singular
-value or the determinant, converge rapidly to zero for all
-values of $k^2$ as the boundary is refined.
-
-Second kind integral equations, i.e. integral equations
-of the form $\mathcal{I} + \mathcal{K}$ where $\mathcal{K}$
-is compact, have a more satisfying theory
-\cite{reed1972methods}, which translates
-well to numerical implementation
-\cite{bornemann2010numerical,zhao2015robust}.
-In \cite{zhao2015robust}, Zhao and Barnett demonstrated
-that the eigenvalues of the drum problem can be
-computed with such a framework, resulting in
-spectrally accurate numerical methods.
-In this paper, we develop a second kind integral
-equation for the buckling problem, based on the
-approach in \cite{rachh2017integral}. This allows
-for a robust approach to computing the eigenvalues
-of the buckling problem, model after the approach for
-the drum problem in \cite{zhao2015robust}, which we
-demonstrate with a number of examples.
-
-The rest of this paper is organized as follows ...

### 2019-02-08 doc/draft-01-stokes/02prelim.tex
clean up stokes manuscript, update matlab routines

--- 2019-01-16 doc/draft-01/02prelim.tex
@@
 
+For a given velocity field $\bu$ and pressure $p$, let $\bsigma(\bu,p)$
+denote the Cauchy stress tensor, i.e.
+\begin{equation}
+\bsigma(\uu,p) = -p \II + 2 \be(\bu) \, ,
+\end{equation}
+where $\be(\bu)$ is the strain tensor given by
+\begin{equation}
+e_{ij}(\bu) = \frac{1}{2} \left( \partial_{x_j} u_i + \partial_{x_i} u_j \right) \; .
+\end{equation}
+When it is clear from context, we will drop the dependence of
+$\bsigma$ on $\bu$ and $p$.
+
 \subsection{Green's functions}
@@
   \mathcal{L}_x \int_{\R^2} G(\xx,\yy) f(\yy) \, dy = f(\xx) \; .
+  \nonumber
 \end{equation}
@@
 some natural growth or decay conditions as $|\xx-\yy| \to \infty$.
-The Green's function of the oscillatory biharmonic equation
-\cref{eq:buck1} is given by 
+The Green's function of the oscillatory biharmonic equation,
+\begin{equation}
+  \Delta ( \Delta + k^2 ) u = 0 \; , \label{eq:obiharm} \nonumber
+\end{equation}
+is given by 
 \begin{equation}
@@
   \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \right ) \, ,
+  \label{eq:Gbh}
 \end{equation}
@@
 \begin{equation}
-  \Glap(\xx,\yy) = \frac{1}{2\pi} \log |\xx-\yy| \; ,
+  \Glap(\xx,\yy) = \frac{1}{2\pi} \log |\xx-\yy| \; , \nonumber
 \end{equation}
@@
 \begin{equation}
-  \Ghelm(\xx,\yy) = -\frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \; .
+  \Ghelm(\xx,\yy) = -\frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \; . \nonumber
 \end{equation}
@@
 
-The Stokes eigenvalue problem (with ``no-slip'' boundary conditions)
-seeks values $k^2$ such that the equations
-\begin{align}
-  \nabla p - \Delta \uu - k^2 \uu &= 0 \quad \textrm{in} \quad \Omega
-  \; , \label{eq:helmstokes}\\
-  \nabla \cdot \uu &= 0 \quad \textrm{in} \quad \Omega
-  \; , \label{eq:helmstokescty} \\
-  \uu &= 0 \quad \textrm{on} \quad \Gamma \; \label{eq:helmstokesnoslip}
-\end{align}
-have a non-trivial solution. In the case that $k=i\alpha$ for
-some real-valued $\alpha$, the equations \cref{eq:helmstokes,eq:helmstokescty}
+In the case that $k=i\alpha$ for some real-valued $\alpha$,
+the equations \cref{eq:ostokes,eq:ostokescty}
 are known as the modified Stokes equations and are of particular
-interest for their application to numerical simulations of unsteady
-flow
-\cite{pozrikidis1992boundary,biros2002embedded,jiang2013second}.
-In the absence of a preferred name for the case of real-valued $k$,
-we will refer to \cref{eq:helmstokes,eq:helmstokescty} as the
-oscillatory Stokes equations.
+interest for their application to the analysis and numerical
+simulation of unsteady flow
+\cite{pozrikidis1992boundary,biros2002embedded,
+  jiang2013second,ladyzhenskaya1969mathematical}.
+The equations are well-studied in that setting and
+integral representations which lead to second kind
+integral equations have been developed. We review
+some of the relevant results here, translating to
+the present, oscillatory setting.
 
-\subsubsection{Stokeslets and stresslets}
+\subsubsection{Oscillatory Stokeslets and stresslets}
 
@@
  Consider the solution of
-\cref{eq:helmstokes,eq:helmstokescty} where a $\delta$-mass
+\cref{eq:ostokes,eq:ostokescty} where a $\delta$-mass
 centered at $\yy$ with strength $\ff$
-has been added to the right-hand side of \cref{eq:helmstokes}, i.e.
+has been added to the right-hand side of \cref{eq:ostokes}, i.e.
 
@@
   \nabla p - \Delta \uu - k^2 \uu &= \delta_\yy \ff \; ,
-  \label{eq:helmstokes_charge} \\
-  \nabla \cdot \uu &= 0 \; .
+  \label{eq:ostokes_charge}  \\
+  \nabla \cdot \uu &= 0 \; . \nonumber
 \end{align}
@@
 \begin{equation}
- \Delta \Glap(\xx,\yy) = \delta_\yy(\xx) \; .
+ \Delta \Glap(\xx,\yy) = \delta_\yy(\xx) \; . \label{eq:lapdelta}
 \end{equation}
-If we substitute this expression into
-\eqref{eq:helmstokes_charge} and take the divergence,
+If we substitute \eqref{eq:lapdelta} into
+\eqref{eq:ostokes_charge} and take the divergence,
 we obtain
@@
 \begin{equation}
-  p = \nabla \Glap(\xx,\yy) \cdot \ff \; .
+  p = \nabla \Glap(\xx,\yy) \cdot \ff \; . \nonumber
 \end{equation}
@@
   \uu &= - (\Delta + k^2)^{-1} ( \Delta \Glap \ff
-  - \nabla (\nabla \Glap \cdot \ff ) ) \\
+  - \nabla (\nabla \Glap \cdot \ff ) ) \nonumber \\
   &= \left ( -\Delta + \nabla \otimes \nabla \right )
-  \Gbh \ff \; .
+  \Gbh \ff \; . \nonumber
 \end{align}
@@
 
-\begin{equation} \label{eq:stokeslet}
+\begin{equation} \label{eq:ostokeslet}
   \GG = - \II \Delta \Gbh + \nabla \otimes \nabla \Gbh
@@
 \cite{pozrikidis1992boundary} for the problem
-\eqref{eq:helmstokes}.
+\eqref{eq:ostokes}.
 
 A related object is the stresslet, which is defined
-in terms of the stress tensor of a velocity, pressure
+in terms of the stress tensor of the velocity, pressure
 pair induced by a Stokeslet. For these tensors, we find
@@
   \sigma_{ij} = -p \delta_{ij} + \left ( \partial_{x_j}u_i
-  +\partial_{x_i} u_j \right ) \; ,
+  +\partial_{x_i} u_j \right ) \; , \nonumber
 \end{equation}
@@
   \partial_{x_k} \left(\partial_{x_j} \Gbh \right) \right)
-  \; .
+  \; . \label{eq:ostress} \nonumber
 \end{align}
@@
   + \nabla \otimes \left ( -\Delta \Gbh \bnu
-  + \partial_{\nu} \nabla \Gbh \right) \; .
+  + \partial_{\nu} \nabla \Gbh \right) \; . \nonumber
 \end{equation}
-%\begin{align}
-% -\Delta \Gbh \bnu
-% + \partial_{\nu} \nabla \Gbh &=
-% ( (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_1 \Gbh +
-% (\partial_{x_1x_1}\nu_1 + \partial_{x_2x_1} \nu_2 )\Gbh,
-% (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_2 \Gbh +
-% (\partial_{x_1x_2}\nu_1 + \partial_{x_2x_2} \nu_2 )\Gbh) \\
-% &= (-\partial_{x_2} \partial_\tau \Gbh,
-% \partial_{x_1} \partial_\tau \Gbh)
-%\end{align}
-%\begin{equation}
-%  \begin{pmatrix}
-%    -\partial_{x_2x_2} & \partial_{x_1x_2} \\
-%    \partial_{x_1x_2} & -\partial_{x_1x_1}
-%  \end{pmatrix} = -\nabla^\bot \otimes \nabla^\bot
-%\end{equation}
 Let $\btau = \bnu^\bot$. Then
@@
   +\nabla \otimes \nabla^\bot \partial_\tau \Gbh \; .
+  \nonumber
 \end{equation}
 
-\subsubsection{Layer potentials and integral representation}
+\subsubsection{Layer potentials}
 
@@
 and double layer potentials of the Stokes eigenvalue
-problem. The single layer potential is defined to
-be
+problem. For $\xx \in \R^2$, the single layer potential
+is defined to be
 
-\begin{equation}
-  \SS \bmu (\xx) = \int_\Gamma \GG (\xx,\yy) \bmu(\yy)
+\begin{equation} \label{eq:singlelayer}
+  \bS [\bmu] (\xx) = \int_\Gamma \GG (\xx,\yy) \bmu(\yy)
   \, dS(\yy) \; .
 \end{equation}
-The double layer potential is defined to be
+We use the notation $\bsigma_\bS[\bmu]$ to denote the
+stress tensor of the single layer at any given point
+$\xx \in \R^2 \setminus \Gamma$.
+
+For $\xx \in \R^2 \setminus \Gamma$, the double layer
+potential is defined to be
 
 \begin{equation} \label{eq:doublelayer}
-  \DD \bmu (\xx) = \int_\Gamma \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy)
-  \right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
+  \bD [\bmu] (\xx) = \int_\Gamma \left ( \TT_{\cdot,\cdot,k}(\xx,\yy)
+  \nu_k(\yy)\right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
 \end{equation}
 where $\bnu$ denotes the outward unit normal to the boundary.
+Note that when $\xx \in \Gamma$ we obtain the same formula
+for the double layer potential except that the integral should be
+interpreted in the principal value sense. 
 If we write $\bmu = \bnu \mu_\nu + \btau \mu_\tau$,
@@
 \begin{align} \label{eq:stokesdlkernel}
-  \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy) \right )^\intercal
+  \left ( \TT_{\cdot,\cdot,k}(\xx,\yy)\nu_k(\yy) \right )^\intercal
   \bmu(\yy) &= \left ( - \nabla \Glap(\xx,\yy) + 2 \nabla^\bot
@@
 \end{align}
+
+When we view the layer potentials as
+operators which map densities on the boundary to functions
+on the boundary, we use special notation. Let
+
+\begin{equation}
+  \cS [\bmu] (\xx) = \int_\Gamma \GG (\xx,\yy) \bmu(\yy)
+  \, dS(\yy)
+\end{equation}
+and
+\begin{equation}
+  \cD [\bmu] (\xx) = \oint_\Gamma \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy)
+  \right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
+\end{equation}
+where the $\oint$ symbol means that the integral is to be
+evaluated in the principal value sense. For two vector valued
+functions $\ff$ and $\bg$ defined on $\Gamma$, consider the bilinear
+form
+
+\begin{equation}
+  \langle \ff , \bg \rangle = \int_\Gamma \ff \cdot \bg dS \; .
+\end{equation}
+The adjoint of $\cD$ with respect to this bilinear form
+is of particular interest; we have $\cD^\intercal = \cN$, where
+
+\begin{equation}
+  \cN [\bmu] = \oint_\Gamma \left ( \TT_{\cdot,\cdot,k}\nu_k(\xx)
+  \right ) \bmu(\yy) \, dS(\yy) \; .
+\end{equation}
+
+\subsubsection{Jump conditions for the layer potentials}
+
+In formulating an integral equation, it is important
+to understand the behavior of the layer potentials
+defined in the previous section for points near and on the
+boundary. The so-called jump conditions for the layer
+potentials are summarized in the following theorem.
+
+\begin{lemma}[Jump conditions]
+  \label{lemma:jump-conds}
+  Let $\bS$, $\bsigma_\bS$, $\bD$, $\cD$, and $\cN$ be
+  the layer potentials and operators defined above and
+  let $\Gamma$ be a sufficiently smooth domain boundary
+  with outward pointing normal $\bnu$. Then, for
+  a given density $\bmu$ defined on $\Gamma$,
+  we have that $\bS \bmu$
+  is continuous across $\Gamma$, the exterior and interior
+  limits of the surface traction of $\bD \bmu$ are equal,
+  and for each $\xx_0 \in \Gamma$,
+
+  \begin{align}
+    \lim_{h \downarrow 0} \bsigma_\bS[\bmu](\xx_0 \pm h\bnu(\xx_0)) \cdot \bnu(\xx_0)
+    &= \mp \frac{1}{2} \bmu(\xx_0) + \cN[\bmu](\xx_0) \\
+    \lim_{h \downarrow 0} \bD[\bmu](\xx_0 \pm h\bnu(\xx_0)) 
+    &= \pm \frac{1}{2} \bmu(\xx_0) + \cD[\bmu](\xx_0)    \; .
+  \end{align}
+\end{lemma}
+
+The above expressions are derived by noting that the
+leading order singularity of these integral kernels
+is the same as for the original Stokes case, so that
+the standard jump conditions for Stokes
+\cite{KimSangtae1991M:pa,Pozrikidis1992}
+apply.

### 2019-02-08 doc/draft-01-stokes/03analysis.tex
clean up stokes manuscript, update matlab routines

--- 2018-08-22 doc/draft-01/08append.tex
@@
-\appendix
-
-\section{Proof of the invertibility of the Farkas representation}
-In this appendix, we prove~\cref{lem:farkinv} which is restated here
-as~\cref{lem:farkinv_app}.
-
-In the following lemma, we present an integral indentity involving the
-Green's function of the Helmholtz-biharmonic equation.
-\begin{lem}
-Suppose that $\Gbh$ is the Green's function of the Helmholtz-biharmonic equation 
-with Helmholtz parameter $k$. Suppose that $v:\R^{2} \to \R$ is a compactly supported smooth
-function. Then
-\begin{equation}
-\int_{\R^{2}} \Gbh(\xx,\yy) \Delta (\Delta + k^2) v(\yy) d\yy = v(\xx)
-\end{equation}
-\end{lem}
-\begin{proof}
-Suppose that $r>0$. 
-Let $B_{r}(\xx)$ denote the ball of radius $r$ centered at the origin
-and let $\partial B_{r}(\xx)$ denote its boundary.
-Then applying Green's second identity twice, we get 
-\begin{align}
-\int_{\R^{2} \setminus B_{r}(\xx)} \Gbh(\xx,\yy) \Delta (\Delta +k^{2}) v(\yy)
-&=
-\int_{\R^{2} \setminus B_{r}(\xx)} \Delta \Gbh (\xx,\yy) (\Delta + k^2) 
-v(\yy) + \\
-& \hspace{5ex}\int_{\partial B_{r}(\xx)} \Gbh(\xx,\yy) (\Delta + k^{2})
-\frac{\partial}{\partial n}v(\yy) \, dS - \\
-& \hspace{5ex}\int_{\partial B_{r}(\xx)} \frac{\partial }{\partial n} \Gbh(\xx,\yy) 
-(\Delta + k^2) v \, dS \\
-&= \int_{\R^{2} \setminus B_{r}(\xx)} \Delta (\Delta + k^2)G(\xx,\yy) v(\yy)
-d\yy  - \nonumber \\
-& \hspace{5ex}\int_{\partial B_{r}(\xx)} (\Delta + k^2) 
-\frac{\partial }{\partial n} \Gbh(\xx,\yy) v \, dS + \nonumber\\
-& \hspace{5ex}\int_{\partial B_{r}(\xx)} (\Delta + k^2) 
-\Gbh(\xx,\yy) \frac{\partial}{\partial n}v \, dS - \nonumber \\
-& \hspace{5ex}\int_{\partial B_{r}(\xx)}  
-\frac{\partial }{\partial n} \Gbh(\xx,\yy) \Delta v\, dS + \\
-& \hspace{5ex}
-\int_{\partial B_{r}(\xx)} \Gbh(\xx,\yy) \Delta \frac{\partial v}{\partial n}
-\, dS \nonumber
-\end{align}
-For all $\yy \in \partial B_{r}(x)$, there exists a constant $C$ such that
-$\Gbh$ satisfies the following equations
-\begin{align}
-(\Delta + k^2) \frac{\partial }{\partial n} G(\xx,\yy) &= 
--\frac{1}{2\pi r} \label{eq:estapp1}\\
-\left|(\Delta + k^2) G(\xx,\yy) \right| &\leq C \log{(r)} \label{eq:estapp2}\\
-\left|\frac{\partial }{\partial n} G(\xx,\yy) \right| &\leq C r\log{(r)} 
-\label{eq:estapp3}\\
-\left| G(\xx,\yy) \right| &\leq C r^{2} \log{(r)} \label{eq:estapp4}\, .
-\end{align}
-Furthermore, $\Gbh$ satisfies $\Delta (\Delta + k^2) \Gbh(\xx,\yy) = 0$
-for all $\yy \in \R^{2} \setminus B_{r}(\xx)$.
-Using the estimates in~\cref{eq:estapp1,eq:estapp2,eq:estapp3,eq:estapp4}, 
-and the smoothness of $v$, we get
-\begin{equation}
-\int_{\R^{2} \setminus B_{r}(\xx)} \Gbh(\xx,\yy) \Delta (\Delta + k^2) v(\yy) 
-d \yy = \frac{1}{2\pi r} \int_{\partial B_{r}(\xx)} v(\yy) dS + 
-O(r \log(r)) \, \label{eq:estapp5}.
-\end{equation}
-The result then follows by taking the limit $r\to 0$ in~\cref{eq:estapp5}. 
-\end{proof}
-\label{sec:farkproof}
-
-\section{Existence and uniqueness results for the Helmholtz-Stokes PDE}
+\section{Fredholm analysis of the integral representations}
 
 In this section, we develop some existence and uniqueness
-results for the Helmholtz-Stokes PDE.
+results for the oscillatory Stokes PDE.
 %
@@
 %
+We first define a radiation condition for the oscillatory
+Stokes equations and prove that, under certain assumptions, the
+layer potentials satisfy the radiation condition.
+%
+The radiation condition is then key to proving uniqueness
+results for some common boundary value problems on exterior
+domains.
+%
+With the Fredholm alternative, these uniqueness results
+are sufficient to derive the invertibility of appropriate
+integral equations for a number of boundary value problems
+on simply and multiply connected domains.
+
+\subsection{A radiation condition for the oscillatory Stokes
+  equation}
+
 Let $\Omega$ be a bounded simply connected
@@
 find a pair $(\bu,p)$ which satisfies:
-\begin{align}
-\Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\label{eq:helmstokes_ext}\\
-\nabla \cdot \bu &= 0 \quad \bx \in E \, , \\
-\bu &= \bh \quad \bx \in \Gamma \, .
-\end{align}
+\begin{align*}
+\Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
+\nabla \cdot \bu &= 0 \quad \bx \in E \, , \nonumber \\
+\bu &= \bh \quad \bx \in \Gamma \, .\nonumber
+\end{align*}
 In addition to the boundary condition on
@@
 Let $\bsigma$ denote the stress tensor associated with the velocity
-field $\bu$, i.e.
+field $\bu$. The normal component of the stress,
 \begin{equation}
-\bsigma = -p \II + 2 \be(\bu) \, ,
-\end{equation}
-where $\be(\bu)$ is the strain tensor given by
-\begin{equation}
-e_{ij}(\bu) = \frac{1}{2} \left( \partial_{x_j} u_i + \partial_{x_i} u_j \right) \; .
-\end{equation}
-%
-The normal component of the stress,
-\begin{equation}
-\ff = \bsigma \cdot \bnu \; ,
+\bt = \bsigma \cdot \bnu \; , \nonumber
 \end{equation}
@@
 \begin{equation}
-\lim_{r\to \infty} \sqrt{r} \left| \ff - i k \bu \right| \to 0 \, ,
+\lim_{r\to \infty} \sqrt{r} \left| \bt - i k \bu \right| \to 0 \, ,
 \label{eq:radcond}
 \end{equation}
-uniformly in direction where $\ff = \bsigma \cdot \bnu$
-with $\bnu = \xx/|\xx|$, i.e. $\ff$ is the surface
+uniformly in direction where $\bt = \bsigma \cdot \bnu$
+with $\bnu = \xx/|\xx|$, i.e. $\bt$ is the surface
 traction on $\partial B_r(0)$.     
@@
 \begin{proposition}
-The Helmholtz-Stokeslet, as in \eqref{eq:stokeslet}, satisfies
+The oscillatory Stokeslet, as in \eqref{eq:ostokeslet}, satisfies
 the radiation condition in Definition \ref{def:radcond}.
@@
 $\int_\Gamma \bmu\cdot \bnu dS = 0$, where $\bnu$ denotes the
-outward normal to the curve $\Gamma$, the Helmholtz-Stokes
-double layer potential $\DD\bmu$, as in \eqref{eq:doublelayer},
+outward normal to the curve $\Gamma$, the oscillatory Stokes
+double layer potential $\bD\bmu$, as in \eqref{eq:doublelayer},
 also satisfies the radiation condition.
@@
 
-\begin{align}
+\begin{align*}
 \bu (\xx) &= k^2 \GG(\xx,0) \bpsi \\
@@
 \log r + \frac{i}{4} H_0^{(1)} (kr) \right ) \right)\bpsi \; .
-\end{align}
+\end{align*}
 Note that derivatives of $\log r$ are $\littleo (1/\sqrt{r})$
@@
 
-\begin{align}
+\begin{align*}
 \left | \sigma \cdot \bnu(\xx) - i k \bu \right | &=
@@
 \right) \right | + \littleo (1/\sqrt{r}) \; .
-\end{align}
+\end{align*}
 Because $H_0^{(1)}(kr)$ has the asymptotic expansion
@@
 H_0^{(1)}(kr) = \sqrt{\frac{2}{\pi k r}} e^{i(rk-\pi/4)} \left ( 1 + O\left (
-\frac{1}{r} \right ) \right ) \;
+\frac{1}{r} \right ) \right ) \; \nonumber
 \end{equation}
@@
 \left (H_0^{(1)} (kr) \right ) \right)\bpsi \right | =
-o ( 1/\sqrt{r} ) \; .
+o ( 1/\sqrt{r} ) \; . \nonumber
 \end{equation}
@@
 \nabla^\perp \left (H_0^{(1)} (kr) \right ) \cdot \bpsi  \right )
-\right) \right | = 0 \; ,
+\right) \right | = 0 \; , \nonumber
 \end{equation}
@@
 For the double layer potential, we only establish the
-decay of the pressure $p$; the rest of the terms
-in \eqref{eq:radcond} can be bounded using an argument
-like that for the Stokeslet above.
-Because $p$ is harmonic in the exterior of any disc
+decay of the pressure, which we will denote by $p^\bD$;
+the rest of the terms in \eqref{eq:radcond} can be bounded
+using an argument like that for the Stokeslet above.
+Because $p^\bD$ is harmonic in the exterior of any disc
 containing $\Gamma$, it is sufficient to show that
-$|\nabla p| = \bigo (1/r^2)$. Let $\btau$ denote the
+$|\nabla p^\bD| = \bigo (1/r^2)$. Let $\btau$ denote the
 positively oriented tangent to the curve $\Gamma$ and
@@
 $\bmu(\yy) \cdot \btau(\yy)$, respectively. Substituting
-$\DD \bmu$ into \eqref{eq:helmstokes_ext}, we obtain
+$\bD \bmu$ into \eqref{eq:ostokes}, we obtain
 
-\begin{align}
-\nabla p^\DD(\xx) &= (\Delta + k^2) \DD \bmu(\xx) \\
+\begin{align*}
+\nabla p^\bD(\xx) &= (\Delta + k^2) \bD \bmu(\xx) \\
 &= \int_\Gamma \left (-k^2 \nabla \Glap (\xx,\yy) +
@@
 \, dS(\yy) \; .
-\end{align}
+\end{align*}
 The other terms are higher-order derivatives
@@
 
-\begin{align}
+\begin{align*}
 |\nabla p_1(\xx)| &:= \left |-k^2 \nabla \int_\Gamma \Glap(\xx,\yy)
 \mu_\nu(\yy) \, dS(\yy) \right |
-\end{align}
+\end{align*}
 is $\bigo (1/r^2)$. In the following, let $z = x_1 + i x_2$ be the
@@
 be the radius of some disc containing $\Gamma$. If $|\xx| > 2R$,
-we can use a standard multipole expansion of $\log(z-(y_1+iy_2))$
+we can use the standard multipole expansion of $\log(z-(y_1+iy_2))$
 and the assumption that $\int_\Gamma \bmu \cdot \bnu = 0$
 to obtain
-\begin{align}
+\begin{align*}
 |\nabla p_1(\xx)| &= \frac{k^2}{2\pi} \left |  \partial_z \int_\Gamma \log(z-(y_1+iy_2))
@@
 &= \bigo (1/r^2) \; .
-\end{align}
+\end{align*}
 \end{proof}
@@
 Then 
-\begin{equation}
+\begin{multline}
 \label{eq:repinfest}  
 \lim_{r\to\infty}
-\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) dS +
+\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
 2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
-dV = 2 \Im \left( k \int_{\Gamma} \bu \cdot \overline{\ff} dS  \right)
-\end{equation}
+dV \\
+= 2 \Im \left( k \int_{\Gamma} \bu \cdot
+\overline{\bt} dS  \right) 
+\end{multline}
+
 \end{lem}
@@
 \begin{equation}
-\lim_{r\to\infty} \int_{|\by|=r} | \ff - i k \bu|^2 dS = 
-\lim_{r\to\infty} \int_{|\by| =r} \left( |\ff|^2 + |k|^2|\bu|^2 + 2 \Im 
-\left( k \bu\cdot \overline{\ff} \right) dS \label{eq:raddecayproof1}
+\lim_{r\to\infty} \int_{|\by|=r} | \bt - i k \bu|^2 dS = 
+\lim_{r\to\infty} \int_{|\by| =r} \left( |\bt|^2 + |k|^2|\bu|^2 + 2 \Im 
+\left( k \bu\cdot \overline{\bt} \right) dS \label{eq:raddecayproof1}
 \right) = 0 \, . 
 \end{equation}
-Since $\bu$ satisfies the Helmholtz-Stokes equation $E \cap B_{r}(0)$,
+Since $\bu$ satisfies the oscillatory Stokes equation $E \cap B_{r}(0)$,
 using a couple of applications of the divergence theorem, we have that
@@
 \int_{E\cap B_{r}(0)} |2 \be(\bu)|^2 dV =
-\int_{\Gamma} \bu \cdot \overline{\ff} dS
-+ \int_{|\by|=r} \bu \cdot \overline{\ff} dS + \overline{k}^2 
+\int_{\Gamma} \bu \cdot \overline{\bt} dS
++ \int_{|\by|=r} \bu \cdot \overline{\bt} dS + \overline{k}^2 
 \int_{E \cap B_{r}(0)} |\bu|^2 dV \,. \label{eq:raddecayproof2}
@@
 Combining~\cref{eq:raddecayproof1,eq:raddecayproof2}, we get
-\begin{equation}
-\lim_{r\to\infty} \int_{|\by|=r}\left(|\ff|^2 + |k|^2 |\bu|^2 \right) dS 
+\begin{multline*}
+\lim_{r\to\infty} \int_{|\by|=r}\left(|\bt|^2 + |k|^2 |\bu|^2 \right) dS 
 + 2 \Im(k)\int_{E \cap B_{r}(0)} \left(|2\be(\bu)|^2 + |k|^2 |\bu|^2 
-\right) dV = 2\Im \left ( k \int_{\Gamma} \bu \cdot \overline{\ff} dS \right) \, .
-\end{equation}
+\right) dV \\
+= 2\Im \left ( k \int_{\Gamma} \bu \cdot \overline{\bt} dS \right) \, .
+\end{multline*}
 \end{proof}
@@
 We first note that each component of $\bu= (u_{1},u_{2})$ satisfies the 
-Helmholtz-Biharmonic equation in $E$, i.e.
+oscillatory biharmonic equation in $E$, i.e.
 \begin{equation}
-\Delta (\Delta + k^2) u_{j} = 0 \quad j=1,2 \,. 
+\Delta (\Delta + k^2) u_{j} = 0 \quad j=1,2 \,. \nonumber
 \end{equation}
@@
 u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} a_{j,n}(r) e^{i n \theta}  \quad 
-j=1,2 \, .
+j=1,2 \, . \nonumber
 \end{equation}
@@
 \int_{|\by|=r} |\bu|^2 dS = r\sum_{n=-\infty}^{\infty} |a_{1,n}(r)|^2  +
-|a_{2,n}(r)|^2 \, .
+|a_{2,n}(r)|^2 \, . \nonumber
 \end{equation}
@@
 r^{|n|}, r^{-|n|}, H^{1}_{n}(k r), H^{2}_{n}(k r) \, , \quad
-n\neq 0 \, ,
+n\neq 0 \, , \nonumber
 \end{equation}
@@
 \begin{equation}
-1, \log{(r)}, H^{1}_{0}(k r), H^{2}_{0}(k r) \quad n=0 \, , 
+1, \log{(r)}, H^{1}_{0}(k r), H^{2}_{0}(k r) \quad n=0 \, ,  \nonumber
 \end{equation} 
@@
 u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} \frac{a_{j,n} e^{i n \theta}}{r^{|n|}} 
-\, .
+\, . \nonumber
 \end{equation}
@@
 \begin{remark} \label{rmk:harmu}
-Note that each component of $\bu$ is harmonic and thus $\bu$ then satisfies
+  Note that if $\bu$ satisfies the assumptions
+  of~\cref{lem:rellich}, then each component is harmonic
+  and thus $\bu$ satisfies
 \begin{align}
 k^2 \bu &= \nabla p  \quad \label{eq:massconsred} \\
-\nabla \cdot \bu &= 0 \, .
+\nabla \cdot \bu &= 0 \, . \nonumber
 \end{align}
-Taking the inner product with $\nabla^{\perp}$ in~\cref{eq:massconsred}, 
+Taking the inner product of~\cref{eq:massconsred} with $\nabla^{\perp}$,
 we note that $\bu$ satisfies both $\nabla^{\perp} \cdot \bu = 0$ 
-and $\nabla \cdot \bu = 0$.
+and $\nabla \cdot \bu = 0$, i.e. $u_1 - i u_2$ is analytic.
 \end{remark}
@@
 Note that in Rellich's lemma $\bu$ need not be a radiating solution. 
-All we know of $\bu$ is that it satifies the PDE in $E$.
+All that is assumed of $\bu$ is that it satifies the PDE in $E$.
 \end{remark}
@@
 \lim_{r\to\infty}
-\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) dS +
+\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
 2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |\be(\bu)|^2 \right)
-dV = 0
+dV = 0 \nonumber
 \end{equation} 
@@
 \begin{equation}
-\lim_{r\to\infty} \int_{|\by|=r} |\bu|^2 dS = 0 \, .
+\lim_{r\to\infty} \int_{|\by|=r} |\bu|^2 dS = 0 \, . \nonumber
 \end{equation}
@@
 with $\bu \to 0$ as $r \to \infty$. Furthermore, since $\bu=0$ on
-$\Gamma$, from uniqueness of solutions to the
+$\Gamma$, by the uniqueness of solutions to the
 Dirichlet problem for Laplace's equation
@@
 Suppose that $\Im(k)\geq 0$ and 
-that $(\bu,p)$ is a radiating solution to the Helmholtz-Stokes
-equation in $E$ with $\ff = 0$ on the boundary $\Gamma$, then
+that $(\bu,p)$ is a radiating solution to the oscillatory Stokes
+equation in $E$ with $\bt = 0$ on the boundary $\Gamma$, then
 $\bu \equiv 0$ in $E$.
@@
 \begin{proof}
-Since $\ff = 0$ on $\Gamma$, it follows
+Since $\bt = 0$ on $\Gamma$, it follows
 from~\cref{eq:repinfest} that
@@
 \lim_{r\to\infty}
-\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) dS +
+\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
 2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |\be(\bu)|^2 \right)
-dV = 0
+dV = 0 \; . \nonumber
 \end{equation} 
@@
 in \cref{rmk:harmu}, $k^2 \bu = \nabla p$. Then, the boundary
-condition becomes $0 = \ff = -p \bnu + 2 \nabla \partial_\nu p/k^2$.
-Because $0 = \btau \cdot \ff = 2\partial_{\tau\nu} p/k^2$,
+condition becomes $0 = \bt = -p \bnu + 2 \nabla \partial_\nu p/k^2$.
+Because $0 = \btau \cdot \bt = 2\partial_{\tau\nu} p/k^2$,
 $\partial_\nu p $ is a constant on $\Gamma$. Using the
@@
 the divergence theorem implies that $\partial_\nu p=0$ on $\Gamma$.
-Thus, $\ff = -p\bnu$ so that $p = 0$ on $\Gamma$. By the uniqueness
+Thus, $\bt = -p\bnu$ so that $p = 0$ on $\Gamma$. By the uniqueness
 of solutions to the Dirichlet problem for Laplace's equation,
 we have that $p=0$ so that $\uu \equiv 0$.
-
 \end{proof}
@@
 $(\bu,p)$ is a radiating solution of the
-Helmholtz-Stokes equation in $E$ which satisfies
-the homogeneous impednace boundary condition
+oscillatory Stokes equation in $E$ which satisfies
+the homogeneous impedance boundary condition
 \begin{equation}
-\ff - i k \bu = 0 \quad \xx \in \Gamma \, .
+\bt - i k \bu = 0 \quad \xx \in \Gamma \, . \nonumber
 \end{equation}
@@
 \begin{proof}
-Since $\bu$ satisfies the radiation condition at $\infty$ and $\ff = ik \bu$
+Since $\bu$ satisfies the radiation condition at $\infty$ and $\bt = ik \bu$
 on $\Gamma$, it follows from~\cref{eq:repinfest} that
-\begin{align}
+\begin{align*}
 0 &=
-\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) dS +
+\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
 2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
 dV \nonumber \\
-& \qquad - 2 \text{Im} \left( k \int_{\Gamma} \bu \cdot \overline{\ff} dS  \right) \\
+& \qquad - 2 \text{Im} \left( k \int_{\Gamma} \bu \cdot \overline{\bt} dS  \right) \\
 &= 
-\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) dS +
+\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
 2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
@@
 \, .
-\end{align}
+\end{align*}
 Because all of the quantities in the last expression above are
@@
   \int_{\Gamma} |\bu|^{2} = 0 \implies \bu = 0  \quad \xx \in \Gamma \,
+  \nonumber
 \end{equation}
@@
 \begin{equation}
-\lim_{r\to\infty} \int_{|\yy|=r} |\bu|^{2} dS \to 0 \, .
+\lim_{r\to\infty} \int_{|\yy|=r} |\bu|^{2} dS \to 0 \, . \nonumber
 \end{equation}
@@
 \Delta u_{j}=  0 \quad \xx \in E \quad \text{and} \quad
-u_{j} = 0 \quad \xx \in \Gamma \, ,
+u_{j} = 0 \quad \xx \in \Gamma \, , \nonumber
 \end{equation}

### 2019-02-08 doc/draft-01-stokes/old-writing.tex
clean up stokes manuscript, update matlab routines

--- 2018-07-12 doc/draft-01/01intro.tex
@@
-\section{Introduction}
+\section{01intro}
 
-Consider the pure bending of an isotropic and homogeneous thin clamped
-plate. 
-Let $\Omega$ denote the midline of the plate, $\Gamma$ denote the 
-boundary of $\Omega$ and $w$ denote the vertical displacement.
-The buckling problem consists of finding 
-values $k^{2}$ such that the boundary value problem
-
-\begin{align}
-\Delta (\Delta + k^2) w &= 0 \quad \textrm{in} \quad \Omega \label{eq:buck1} \; , \\
-w &= 0 \quad \textrm{on} \quad \Gamma \label{eq:buck2} \; ,\\
-\dwdn &=0 \quad \textrm{on} \quad \Gamma \label{eq:buck3} 
-\end{align}
-has a non-trivial solution. In a slight abuse of notation,
-these values and the corresponding solutions are often
-referred to as ``eigenvalues'' and ``eigenfunctions'',
-respectively. 
-It is well known that the buckling problem has a
-countable collection of such values
-$0 < k_{1}^{2} \leq k_{2}^2 \leq \ldots \uparrow \infty$,
-counting multiplicites.
-
-\begin{remark}
-  When $k = i\alpha$, the differential equation
-  \cref{eq:buck1} is known as the modified biharmonic
-  equation. As there appears to be no preferred
-  name for the equation with real-valued $k$,
-  we will refer to \cref{eq:buck1} as the
-  Helmholtz-biharmonic equation.
-\end{remark}
-
-The eigenvalues (and eigenfunctions)
+The eigenvalues of a system describe the behavior
 of the boundary value problem \cref{eq:buck1,eq:buck2,eq:buck3}

### 2019-02-08 matlab/src/hbhdirmat_pre.m

@@ -1,11 +1,37 @@
 
-function [stokestd,stokesinds,sysmatbl,sysmatbr,sysmattr] = hbhdirmat_pre(chunker,nchs,ccs,zk,cs,cd,intparams,varargin)
+function [stokestd,stokesinds,sysmatbl,sysmatbr,sysmattr] = ...
+    hbhdirmat_pre(chunker,nchs,ccs,zk,cs,cd,intparams,yy,opts)
 %HBHDIRMAT
 %
 % This function builds the system matrix for the Helmholtz biharmonic
-% Dirichlet problem on the given domain. This is the 'slow' version...
+% Dirichlet problem on the given domain.
 %
+% opts.fast = 1 use fast version, 0 use slow builders (1)
+% 
 
+if nargin < 8
+    yy = [];
+end
+
+if nargin < 9
+    opts = [];
+end
+
+if ~isfield(opts,'fast')
+    opts.fast = 1;
+end
+if ~isfield(opts,'fstream_tol')
+    opts.fstream_tol = 1.0e-14;
+end
+if ~isfield(opts,'fstream_np')
+    opts.fstream_np = 64;
+end
+if ~isfield(opts,'fstream_occ')
+    opts.fstream_occ = 200;
+end
+if ~isfield(opts,'verb')
+    opts.verb = 0;
+end
 
 
 % geometry stuff
@@ -28,9 +54,6 @@ end
 
 ngeo = 2*k*nch;
 nsys = 2*k*nch+ncomp;
-
-%sysmat = zeros(nsys,nsys) + 1i*zeros(nsys,nsys);
-
 
 %% effect of sources in holes
 
@@ -68,8 +91,9 @@ fkern = @(s,t,sn,tn) helmstokessubmat(zk,s,t,sn,cs,cd);
 ndims(1) = 2; ndims(2) = 2;
 [stokestd,stokesinds] = chunkskernelmattd(chunker,fkern,ndims,intparams);
 
-stokestd(:,1+ndims(2)*k:ndims(2)*2*k) = stokestd(:,1+ndims(2)*k:ndims(2)*2*k) ...
--0.5*cd*kron(ones(nch,1),eye(ndims(2)*k,ndims(2)*k));
+stokestd(:,1+ndims(2)*k:ndims(2)*2*k) = ...
+    stokestd(:,1+ndims(2)*k:ndims(2)*2*k) ...
+    - 0.5*cd*kron(ones(nch,1),eye(ndims(2)*k,ndims(2)*k));
 
[…]

### 2019-02-08 matlab/src/helmstokesstreamsubmat_wpre.m

@@ -1,17 +1,0 @@
-function mat = helmstokesstreamsubmat_wpre(zk,src,targ,src_norm,cs,cd,streammattd,streammatinds)
-
-[~,ns] = size(src);
-[~,nt] = size(targ);
-mat2 = zeros(1,2,nt,ns);
-
-mex_id_ = 'zhelmstokesallstreammatmany(i dcomplex[x], i int[x], i double[], i int[x], i double[], i dcomplex[], i dcomplex[x], i dcomplex[x], io dcomplex[])';
-[mat2] = bhdeiggateway(mex_id_, zk, ns, src, nt, targ, src_norm, cs, cd, mat2, 1, 1, 1, 1, 1);
-
-mat2 = reshape(mat2,1,2,nt,ns);
-
-mat = zeros(1*nt,2*ns);
-mat(:,1:2:2*ns) = reshape(mat2(:,1,:,:),nt,ns);
-mat(:,2:2:2*ns) = reshape(mat2(:,2,:,:),nt,ns);
-
-end
-

### 2019-02-08 matlab/src/pxyfun_sq.m

@@ -23,7 +23,7 @@ function [Kpxy,nbr] = pxyfun_sq(kern,proxy,pnorm,x,xnorm,slf,nbr,l,ctr)
 
   pxy = bsxfun(@plus,proxy*l,ctr(:));
   N = size(x,2);
-  Kpxy = kern(x,pxy,xnorm,pnorm,slf)*1.0/N;
+  Kpxy = kern(x,pxy,xnorm,pnorm,slf);
   dx = x(1,nbr) - ctr(1);
   dy = x(2,nbr) - ctr(2);
   dist = max(abs([dx; dy]),[],1);

### 2019-02-08 matlab/test/testchunkskernmat.m

@@ -6,39 +6,46 @@
 
 cparams.eps = 1.0e-6;
 cparams.nchmax = 100000;
-cparams.nover = 2;
+cparams.nover = 3;
 narms = 5;
 amp = 0.5;
-tic; chunker = chunkfunc(@(t) starfish(t,narms,amp),cparams); toc
+start = tic; chunker = chunkfunc(@(t) starfish(t,narms,amp),cparams); 
+time1 = toc(start);
 
-chunker.nch
+fprintf('%5.2e s : time to build geo\n',time1)
 
 xs = chunker.chunks(1,:,:); xs = xs(:);
 ys = chunker.chunks(2,:,:); ys = ys(:);
 
-figure(1)
-clf
-scatter(xs,ys)
-axis equal
+% build laplace dirichlet matrix
 
 fkern = @(s,t,sn,tn) glapkern(s,t,sn,tn,'D');
 ndims(1) = 1; ndims(2) = 1;
 intparams.intorder = chunker.k;
-tic; D = chunkskernelmat(chunker,fkern,ndims,intparams); toc
+start = tic; D = chunkskernelmat(chunker,fkern,ndims,intparams);
+time1 = toc(start);
+
+fprintf('%5.2e s : time to assemble matrix\n',time1)
 
 %
+
 sysmat = eye(size(D))-2*D;
 
-tic; d1 = det(sysmat); toc
+% built-in determinant computation
 
-% hifie
+start = tic; d1 = det(sysmat); time1 = toc(start);
+
+fprintf('%5.2e s : time for built in determinant routine\n',time1)
+
+% using FLAM
 npts = length(xs);
 xhifie = chunker.chunks(1:2,:);
 
 %
-start = tic; F = rskelf(sysmat,xhifie,80,1e-10); toc(start)
-start = tic; d2 = exp(rskelf_logdet(F)); toc(start)
+start = tic; F = rskelf(sysmat,xhifie,80,1e-10); time1 = toc(start);
+fprintf('%5.2e s : time for FLAM rskelf\n',time1)
+start = tic; d2 = exp(rskelf_logdet(F)); time1 = toc(start);
+fprintf('%5.2e s : time for FLAM determinant\n',time1)
+fprintf('\n')
+fprintf('ratio of determinants : %9.6e\n',d1/d2)
 
-d1-d2
-
-%scatter(real(e),imag(e))

### 2019-02-08 matlab/test/testchunkskernmat2.m

@@ -1,54 +1,0 @@
-
-%TESTCHUNKSKERNMAT2
-%
-% This file tests whether or not chunks 
-% lib is wrapped properly
-
-cparams.eps = 1.0e-6;
-cparams.nchmax = 100000;
-cparams.nover = 0;
-narms = 5;
-amp = 0.5;
-tic; chunker = chunkfunc(@(t) starfish(t,narms,amp),cparams); toc
-
-chunker.nch
-chunker.k*chunker.nch
-
-xs = chunker.chunks(1,:,:); xs = xs(:);
-ys = chunker.chunks(2,:,:); ys = ys(:);
-
-tic; mat1 = chunknormonesmat(chunker); toc
-tic; mat2 = normalonesmatwrap(chunker); toc
-
-rnorms = chunknormals(chunker);
-rnx = rnorms(1,:,:); rnx = rnx(:);
-rny = rnorms(2,:,:); rny = rny(:);
-
-figure(1)
-clf
-scatter(xs,ys)
-axis equal
-hold on
-quiver(xs,ys,rnx,rny)
-
-%%
-
-zk = 1.0;
-cd = -2.0 + 1i*0.0;
-cs = 0.0 + 1i*0.0;
-fkern = @(s,t,sn,tn) helmstokessubmat(zk,s,t,sn,cs,cd);
-ndims(1) = 2; ndims(2) = 2;
-intparams.intorder = chunker.k;
-start = tic; matul = chunkskernelmat(chunker,fkern,ndims,intparams); toc(start)
-
-normonesmat = chunknormonesmat(chunker);
-matul = eye(size(matul)) + matul + normonesmat;
-
-%%
-
-d1 = det(matul);
-
-start = tic; F = rskelf(matul,xhifie,80,1e-10); toc(start)
-start = tic; d2 = exp(rskelf_logdet(F)); toc(start)
-
-d1-d2

### 2019-02-08 matlab/test/testchunkslib.m

@@ -8,7 +8,7 @@ cparams.eps = 1.0e-6;
 cparams.nchmax = 100000;
 narms = 10;
 amp = 0.5;
-tic; chunker = chunkfunc(@(t) starfish(t,narms,amp),cparams); toc
+start = tic; chunker = chunkfunc(@(t) starfish(t,narms,amp),cparams); toc(start)
 
 chunker.nch
 

### 2019-02-08 matlab/test/testmultichunkfunc.m

@@ -87,39 +87,3 @@ ys = chunker.chunks(2,:,:); ys = ys(:);
 figure(1)
 clf
 scatter(xs,ys)
-
-%% system matrix stuff
-q1 = 0.0 + 1i*0.0; q2 = -2.0 + 1i*0.0;
-zk = 1.0i;
-tic; sysmat = zhbhstokesmatbuild(zk,wgeo,nchs,ccs,q1,q2); toc
-
-%% hifie
-[ntot,~] = size(sysmat);
-npts = length(xs);
-xhifie = zeros(2,ntot);
-xhifie(:,1:2:1+2*(npts-1)) = chunker.chunks(1:2,:);
-xhifie(:,2:2:2+2*(npts-1)) = chunker.chunks(1:2,:);
-xhifie(:,2*npts+1:ntot) = ccs;
-
-%%
-tic; F = hifie2(sysmat,xhifie,10,1e-10); toc
-
-%% 
-ntest=1000;
-tic;
-x = randn(ntot,ntest);
-y = sysmat*x;
-toc
-tic;
-x = randn(ntot,ntest);
-y = hifie_mv(F,x,'n');
-toc
-
-%%
-tic;
-det1 = det(sysmat);
-toc
-
-tic;
-det2 = exp(hifie_logdet(F));
-toc

### 2019-02-08 matlab/test/testsubmateval.m

@@ -1,8 +1,8 @@
 %TESTSUBMATEVAL
 
 
-ns = 16;
-nt = 16;
+ns = 560;
+nt = 560;
 
 src = randn(2,ns);
 targ = randn(2,nt);

### 2019-02-08 matlab/test/testwithflam.m

@@ -4,6 +4,11 @@
 % This file tests using the matrix routines with
 % FLAM (slow version of matrix build for now).
 
+seed = 8675309;
+rng(seed);
+addpath('../src')
+addpath('../../mwrap')
+
 cparams.eps = 1.0e-6;
 cparams.nchmax = 100000;
 cparams.nover = 2;
@@ -11,33 +16,19 @@ narms = 5;
 amp = 0.5;
 tic; chunker = chunkfunc(@(t) starfish(t,narms,amp),cparams); toc
 
-chunker.nch
-chunker.k*chunker.nch
-
 xs = chunker.chunks(1,:,:); xs = xs(:);
 ys = chunker.chunks(2,:,:); ys = ys(:);
 
-%tic; mat1 = chunknormonesmat(chunker); toc
-%tic; mat2 = normalonesmatwrap(chunker); toc
-
 rnorms = chunknormals(chunker);
-rnx = rnorms(1,:,:); rnx = rnx(:);
-rny = rnorms(2,:,:); rny = rny(:);
-
-%figure(1)
-%clf
-%scatter(xs,ys)
-%axis equal
-%hold on
-%quiver(xs,ys,rnx,rny)
 
 % build matrix
 
-zk = 0.1;
+zk = 1;
 cd = -2.0 + 1i*0.0;
 cs = 0.0 + 1i*0.0;
 nchs = ones(1,1);
 nchs(1) = chunker.nch;
+ncomp = length(nchs);
 ccs = zeros(2,1);
 
 intparams.intorder = chunker.k;
@@ -46,78 +37,246 @@ intparams.intorder = chunker.k;
 
 start = tic; sysmat1 = hbhdirmat(chunker,nchs,ccs,zk,cs,cd,intparams); toc(start)
 
-%%
-
-%fkern = @(s,t,sn,tn) helmstokessubmat(zk,s,t,sn,cs,cd);
-%ndims(1) = 2; ndims(2) = 2;
-%tic; [stokestd,inds] = chunkskernelmattd(chunker,fkern,ndims,intparams); toc
-
-%%
+%
 
 start = tic; yylap = hbhdirmat_lap_pre(chunker,nchs,intparams); toc(start)
 
-%% 
+% 
 
[…]

### 2019-02-08 src/helmbhrouts.f

@@ -66,6 +66,8 @@ c     local variables
       complex *16 zkh, ztemp, zkr
       data eye /(0.0d0,1.0d0)/
       data eyeo4 /(0.0d0,0.25d0)/
+      real *8 tiny
+      data tiny / 1.0d-50 /
 
       dx = zx(1) - zy(1)
       dy = zx(2) - zy(2)
@@ -80,6 +82,42 @@ c     local variables
       dy5 = dy4*dy
 
       r2 = dx2 + dy2
+
+      if (r2 .lt. tiny) then
+         if (ifpot .eq. 1) pot = 0.0d0
+         if (ifgrad .eq. 1) then
+            grad(1) =0.0d0
+            grad(2) =0.0d0
+         endif
+         if (ifhess .eq. 1) then
+            hess(1) =0.0d0
+            hess(2) =0.0d0
+            hess(3) =0.0d0            
+         endif
+         if (ifder3 .eq. 1) then
+            der3(1) =0.0d0
+            der3(2) =0.0d0
+            der3(3) =0.0d0
+            der3(4) =0.0d0                        
+         endif
+         if (ifder4 .eq. 1) then
+            der4(1) =0.0d0
+            der4(2) =0.0d0
+            der4(3) =0.0d0
+            der4(4) =0.0d0
+            der4(5) =0.0d0                                    
+         endif
+         if (ifder5 .eq. 1) then
+            der5(1) =0.0d0
+            der5(2) =0.0d0
+            der5(3) =0.0d0
+            der5(4) =0.0d0
+            der5(5) =0.0d0
+            der5(6) =0.0d0                                                
+         endif
+         return
+      endif
+      
       r = dsqrt(r2)
       r3 = r2*r
       r4 = r3*r

### 2019-02-12 doc/draft-01-stokes/02prelim.tex
updates to paper and cleaning up arguments

@@
 
-\begin{equation}
+\begin{equation} \label{eq:bi_form}
   \langle \ff , \bg \rangle = \int_\Gamma \ff \cdot \bg dS \; .
 \end{equation}
-The adjoint of $\cD$ with respect to this bilinear form
-is of particular interest; we have $\cD^\intercal = \cN$, where
+The definition of the adjoint used throughout the paper will be
+the one induced by this form.
+The adjoint of $\cD$ is of particular interest; we have
+$\cD^\intercal = \cN$, where
 
@@
 
-\begin{lemma}[Jump conditions]
-  \label{lemma:jump-conds}
+\begin{lem}[Jump conditions] \label{lem:jump-conds}
   Let $\bS$, $\bsigma_\bS$, $\bD$, $\cD$, and $\cN$ be
@@
   \end{align}
-\end{lemma}
+\end{lem}
 
@@
 apply.
+
+\subsubsection{Null-space correction}
+
+Without modification, the standard layer potentials
+can result in rank-deficient representations for
+the boundary value problems. The nature of this deficiency
+is treated below but for now we introduce a standard
+operator used to correct this. For any integrable density
+$\bmu$, let $\cW[\bmu]$ be defined by
+
+\begin{equation} \label{eq:ones_operator}
+  \cW[\bmu](\xx) = \int_\Gamma \bnu(\xx)
+  \left ( \bnu(\yy) \cdot \bmu(\yy) \right )
+  \, dS(\yy) \; ,
+\end{equation}
+for any $\xx \in \Gamma$. We have
+
+\begin{lem}
+  Let $\Omega$ be a domain with $C^2$ boundary and $\bmu$ be
+  an integrable function defined on $\Gamma$. Then
+  \begin{itemize}
+  \item $\cW[\cW[\bmu]] = \cW[\bmu]$,
+  \item $\cW^\intercal = \cW$,
+  \item $\cW[\bmu \pm 2 \cD[\bmu]] = 0$,
+  \item $\cW[\cS[\bmu]] = 0$,
+  \end{itemize}
+  where the transpose is induced by the bilinear
+  form \cref{eq:bi_form}.
+\end{lem}
+
+\begin{proof}
+  The first two results follow from the definitions of $\cW$ and
+  the normal vector. The other two follow from the fact that
+  $\bS[\bmu]$ and $\bD[\bmu]$ are divergence-free and
+  an application of \cref{lem:jump-conds}.
+\end{proof}

### 2019-02-12 doc/draft-01-stokes/03analysis.tex
updates to paper and cleaning up arguments

@@
 %
+We seek solutions in the space
+
+\begin{equation}
+  A(\Omega) = \{ (\bu,p) \textrm{ s.t. } \bu \in
+  \left ( C^2(\Omega)\times C^2(\Omega) \right ) \cap
+  \left ( C(\bar{\Omega}) \times C(\bar{\Omega}) \right ) \, , \,
+  p \in C^1(\Omega) \times C(\bar{\Omega})\} \; ,
+\end{equation}
+where $\Omega$ is an open domain and $\bar{\Omega}$ denotes
+its closure.
+%
+As above, we will assume that all domains have $C^2$ boundaries.
+%
+Most of the results will apply to multiply connected domains
+but we will identify the results which do not.
+%
+
 The structure of this section follows that used
@@
 %
-We first define a radiation condition for the oscillatory
-Stokes equations and prove that, under certain assumptions, the
-layer potentials satisfy the radiation condition.
+First, we define the interior boundary value problems
+of interest, which is straightforward.
 %
-The radiation condition is then key to proving uniqueness
-results for some common boundary value problems on exterior
-domains.
+For the exterior problems, we introduce a radiation condition
+for the equations and establish that, under certain assumptions,
+the standard layer potentials satisfy the radiation condition.
 %
-With the Fredholm alternative, these uniqueness results
-are sufficient to derive the invertibility of appropriate
+We then define well-posed versions of the
+exterior boundary value problems which incorporate the
+radiation condition.
+%
+Then we derive a number of uniqueness
+results for the boundary value problems.
+%
+Finally, along with the Fredholm alternative, these uniqueness
+results are sufficient to derive the invertibility of appropriate
 integral equations for a number of boundary value problems
 on simply and multiply connected domains.
+
+\subsection{Boundary value problems --- interior}
+
+Let $\Omega$ be a bounded domain with $C^2$ boundary
+denoted by $\Gamma$.
+The standard Dirichlet boundary problem specifies the
+velocity of the fluid on the boundary, i.e.
+
+\begin{definition}[Interior Dirichlet problem]
+  Let $\ff \in C(\Omega)$ be given. Find $(\bu,p) \in A(\Omega)$
+  such that
+  \begin{equation}
+  \begin{aligned} \label{eq:dir_interior}
+    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in \Omega \, ,\\
+    \nabla \cdot \bu &= 0 \quad \bx \in \Omega \, ,  \\
+    \bu &= \bh \quad \bx \in \Gamma \, .
+  \end{aligned}
+  \end{equation}
+\end{definition}
+Note that the divergence-free constraint for the oscillatory
+Stokes equations implies a compatibility condition on the
+Dirichlet data $\ff$, namely that
+\begin{equation} \label{eq:dir_compat}
+  \int_\Gamma \ff \cdot \nu \, dS = 0 \; .
+\end{equation}
+
+Let $\bsigma$ denote the stress tensor associated with
+field $(\bu,p)$. 
+Specifying the surface traction, $\bt = \bsigma \cdot \bnu$,
+on the boundary gives the standard Neumann boundary value
+problem, i.e.
+
+\begin{definition}[Interior Neumann problem]
+  Let $\bg \in C(\Omega)$ be given. Find $(\bu,p) \in A(\Omega)$
+  such that
+  \begin{equation}
+  \begin{aligned} \label{eq:neu_interior}
+    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in \Omega \, ,\\
+    \nabla \cdot \bu &= 0 \quad \bx \in \Omega \, ,  \\
+    \bt &= \bg \quad \bx \in \Gamma \, .
+  \end{aligned}
+  \end{equation}
+\end{definition}
 
@@
 
-Let $\Omega$ be a bounded simply connected
-domain and $E = \R^{2} \setminus \bar{\Omega}$ denote its
+Let $\Omega$ be the union of a finite collection of
+simply connected domains, i.e. $\Omega = \bigcup_{i=1}^m \Omega_i$
+for some $m \in \N$,
+and let $E = \R^{2} \setminus \bar{\Omega}$ denote its
 exterior.
@@
 find a pair $(\bu,p)$ which satisfies:
-\begin{align*}
+\begin{equation}
+\begin{aligned}
 \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
-\nabla \cdot \bu &= 0 \quad \bx \in E \, , \nonumber \\
-\bu &= \bh \quad \bx \in \Gamma \, .\nonumber
-\end{align*}
+\nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
+\bu &= \bh \quad \bx \in \Gamma \, . \nonumber
+\end{aligned}
+\end{equation}
 In addition to the boundary condition on
@@
 
-Let $\bsigma$ denote the stress tensor associated with the velocity
-field $\bu$. The normal component of the stress,
-\begin{equation}
-\bt = \bsigma \cdot \bnu \; , \nonumber
-\end{equation}
-gives the surface traction, which is the analogue of
-the normal derivative for the scalar Helmholtz equation,
-i.e. specifying the surface traction on a boundary is
-the Neumann problem for the oscillatory Stokes PDE.
-
-%
 Let $B_r(0)$ denote the disc of radius $r$ centered
@@
 
+\subsection{Boundary value problems --- exterior}
+
+Let $E$ and $\Gamma$ be as in the previous subsection.
+The radiation condition allows for a well-posed formulation
+of the exterior boundary value problems, i.e.
+\cref{def:dir_exterior,def:neu_exterior} below.
+
+\begin{definition}[Exterior Dirichlet problem]
+  \label{def:dir_exterior}
+  Let $\ff \in C(\Gamma)$ be given. Find $(\bu,p) \in A(E)$
+  such that
+  \begin{equation}
+  \begin{aligned} \label{eq:dir_exterior}
+    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
+    \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
+    \bu &= \bh \quad \bx \in \Gamma \, 
+  \end{aligned}
+  \end{equation}
+  and $(\bu,p)$ satisfies the radiation condition in
+  \cref{def:radcond}.
+\end{definition}
+\begin{definition}[Exterior Neumann problem]
+  \label{def:neu_exterior}  
+  Let $\bg \in C(\Gamma)$ be given. Find $(\bu,p) \in A(E)$
+  such that
+  \begin{equation}
+  \begin{aligned} \label{eq:neu_exterior}
+    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
+    \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
+    \bt &= \bg \quad \bx \in \Gamma \,
+  \end{aligned}
+  \end{equation}
+  and $(\bu,p)$ satisfies the radiation condition in
+  \cref{def:radcond}.
+\end{definition}
+
 \subsection{Uniqueness results}
+
+Before moving on to the exterior uniqueness theorems,
+we establish the well-known result that
+the interior eigenvalues are real-valued.
+
+\begin{thrm}
+  Let $\Omega$ be a bounded domain and suppose that
+  $\Im (k) > 0$. Then both the interior
+  Dirichlet and Neumann boundary value problems have
+  unique solutions.
+\end{thrm}
+\begin{proof}
+  A couple applications of the divergence theorem establish
+  that
+  \begin{equation} \label{eq:greenlike}
+    \int_\Omega |2\be(\bu)|^2 - \overline{k}^2 \, dV
+    = \int_\Gamma \bu \cdot \overline{\bt} \, dS \; . 
+  \end{equation}
+  Suppose that either $\bu = 0$ or $\bt = 0$ on $\Gamma$.
+  Then, the right hand side of \cref{eq:greenlike} is
+  zero. Taking the real and imaginary parts of \cref{eq:greenlike},
+  it is clear that $\bu \equiv 0$.
+\end{proof}
+
+The following lemmas are useful in establishing the uniqueness
+of oscillatory Stokes boundary value problems.
 
@@
   \label{lem:rep}
+  Let the unbounded region $E$ be given as the exterior
+  of a finite collection of bounded domains.
   Suppose that $(\bu,p)$ satisfies the oscillatory Stokes equation in 
-an unbounded region $E$ along with the radiation 
-condition~\cref{eq:radcond}. 
+  $E$ as well as the radiation condition~\cref{eq:radcond}. 
 Then 
@@
   \label{lem:rellich}
-Suppose that $\bu$ satisfies the oscillatory Stokes equation in an unbounded
-region $E$.  
-Suppose further that 
+    Let the unbounded region $E$ be given as the exterior
+  of a finite collection of bounded domains.
+  Suppose that $\bu$ satisfies the oscillatory Stokes equation in
+  $E$ and that 
 \begin{equation}
@@
 
-\begin{thrm}[Uniqueness of the Dirichlet Problem]
+\begin{thrm}[Uniqueness of the Exterior Dirichlet Problem]
+  Let the unbounded region $E$ be given as the exterior
+  of a finite collection of bounded domains.
   Suppose that $\Im(k)\geq 0$ and 
@@
 
-\begin{thrm}[Uniqueness of the Neumann Problem]
+\begin{thrm}[Uniqueness of the Exterior Neumann Problem]
+  Let the unbounded region $E$ be given as the exterior
+  of one simply connected domain.
   Suppose that $\Im(k)\geq 0$ and 
@@
 
-\begin{thrm}[Uniqueness of the Impedance Problem]
+\begin{thrm}[Uniqueness of the Exterior Impedance Problem]
+  Let the unbounded region $E$ be given as the exterior
+  of a finite collection of bounded domains.
   Suppose that $\Im(k) \geq 0$ and that

### 2019-02-12 doc/draft-01-stokes/02prelim.tex
add sketch of representation proof

@@
 $\bsigma$ on $\bu$ and $p$.
+
+We seek solutions of \cref{eq:ostokes} in the space
+
+\begin{equation}
+  A(\Omega) = \{ (\bu,p) \textrm{ s.t. } \bu \in
+  \left ( C^2(\Omega)\times C^2(\Omega) \right ) \cap
+  \left ( C(\bar{\Omega}) \times C(\bar{\Omega}) \right ) \, , \,
+  p \in C^1(\Omega) \times C(\bar{\Omega})\} \; ,
+\end{equation}
+where $\Omega$ is an open domain and $\bar{\Omega}$ denotes
+its closure.
 
@@
 In the case that $k=i\alpha$ for some real-valued $\alpha$,
-the equations \cref{eq:ostokes,eq:ostokescty}
+the oscillatory Stokes equations \cref{eq:ostokes}
 are known as the modified Stokes equations and are of particular
@@
  Consider the solution of
-\cref{eq:ostokes,eq:ostokescty} where a $\delta$-mass
+\cref{eq:ostokes} where a $\delta$-mass
 centered at $\yy$ with strength $\ff$
@@
 
+\subsubsection{Representation Theorem}
+
+Here we sketch the proof of the equivalent of the
+Green's identity for oscillatory Stokes, which is well-known
+in the Stokes and modified Stokes settings
+\cite{Pozrikidis1992,biros2002embedded,ladyzhenskaya1969mathematical}.
+
+\begin{thrm} \label{thrm:rep-theorem}
+  Let $\Omega$ be a bounded domain with $C^2$ boundary and let
+  the pair $(\bu,p)$ satisfy the oscillatory stokes equations
+  \cref{eq:ostokes} in $\Omega$. Then
+
+  \begin{equation} \label{eq:rep-theorem}
+    \bu(\xx) = \bS [\bsigma(\bu,p)](\xx) - \bD[\bu](\xx) \; .
+  \end{equation}
+\end{thrm}
+
+\begin{proof}
+  By the definitions of $\GG$ and $\Glap$, we have
+  \begin{equation*}
+    \bu(\xx) = \int_\Omega -(\Delta_x + k^2) \GG(\xx,\yy) \bu(\yy)
+    + \nabla \otimes \nabla \Glap(\xx,\yy) \bu(\yy) \, dV(\yy) \; .
+  \end{equation*}
+  Applying Green's identity and the divergence theorem, we
+  obtain
+  \begin{equation}
+    \bu(\xx) = \int_\Gamma \GG(\xx,\yy) \partial_\nu \bu
+    - \partial_\nu \GG(\xx,\yy) \bu
+    - \nabla \Glap(\xx,\yy) (\bnu \cdot \bu) \, dS 
+    - \int_\Omega \GG(\xx,\yy) (\Delta + k^2) u \, dV \; .
+    \nonumber
+  \end{equation}
+  Substituting the definition of the PDE and applying the divergence
+  theorem again, we obtain
+  \begin{equation}
+    \bu(\xx) = \int_\Gamma \GG \partial_\nu \bu - p \GG \bnu - \partial_\nu \GG \bu
+    - \nabla \Glap (\bnu \cdot \bu) \, dS  \; . \label{eq:rep_proof_1}
+  \end{equation}
+  From the divergence theorem and the divergence-free properties of
+  $\uu$ and $\GG$, we can obtain
+
+  \begin{equation}
+    \int_\Gamma \GG \nabla (\bu \cdot \bnu)
+    - (\nabla \GG \bnu)^\intercal \bu \, dS = 0 \; .  \label{eq:rep_proof_2}
+  \end{equation}
+  Adding \cref{eq:rep_proof_1,eq:rep_proof_2}, we get the desired
+  result.
+\end{proof}
+
 \subsubsection{Jump conditions for the layer potentials}

### 2019-02-12 doc/draft-01-stokes/02prelim.tex
update proof or rellich's lemma

@@
 
+By the analyticity of $\Gbh$, a consequence of \cref{thrm:rep-theorem}
+is
+\begin{cor}
+\label{cor:analytic}  
+  Let $(\uu,p) \in A(\Omega)$ be a solution of \cref{eq:ostokes}.
+  Then each component of $\uu(\xx)$ is an analytic function
+  of the coordinates $\xx$.
+\end{cor}
+
+The proof of \cref{cor:analytic} follows the same reasoning as
+that for the Helmholtz case; see \cite[Theorem 3.5]{colton1983integral}.
+
 \subsubsection{Jump conditions for the layer potentials}

### 2019-02-13 doc/draft-01-stokes/02prelim.tex
add latest updates, restructure a little

@@
 
-\subsection{An integral representation for the Stokes eigenvalue
-  problem}
+\subsection{Properties of the oscillatory Stokes layer
+  potentials}
 
@@
 
-By the analyticity of $\Gbh$, a consequence of \cref{thrm:rep-theorem}
-is
+A consequence of \cref{thrm:rep-theorem} and the analyticity
+of $\Gbh$ is 
 \begin{cor}
@@
 to understand the behavior of the layer potentials
-defined in the previous section for points near and on the
-boundary. The so-called jump conditions for the layer
-potentials are summarized in the following theorem.
+for points near and on the boundary. The so-called jump
+conditions for the layer potentials are summarized in the
+following theorem.
 
@@
 \begin{equation} \label{eq:ones_operator}
-  \cW[\bmu](\xx) = \int_\Gamma \bnu(\xx)
+  \cW[\bmu](\xx) = \frac{1}{|\Gamma|} \int_\Gamma \bnu(\xx)
   \left ( \bnu(\yy) \cdot \bmu(\yy) \right )

### 2019-02-13 doc/draft-01-stokes/03analysis.tex
update proof or rellich's lemma
add latest updates, restructure a little

@@
 
-In this section, we develop some existence and uniqueness
-results for the oscillatory Stokes PDE.
+In this section, we develop some uniqueness
+results for the oscillatory Stokes PDE and describe
+the use of the layer potentials in discovering Stokes
+eigenvalues.
 %
@@
 %
-Finally, along with the Fredholm alternative, these uniqueness
+Along with the Fredholm alternative, these uniqueness
 results are sufficient to derive the invertibility of appropriate
@@
 on simply and multiply connected domains.
+%
+Finally, we briefly describe how the approach of Zhao
+and Barnett translates to the present setting, giving
+a robust numerical method for computing Stokes
+eigenvalues.
 
@@
     \nabla \cdot \bu &= 0 \quad \bx \in \Omega \, ,  \\
-    \bu &= \bh \quad \bx \in \Gamma \, .
+    \bu &= \ff \quad \bx \in \Gamma \, .
   \end{aligned}
@@
 \begin{equation} \label{eq:dir_compat}
-  \int_\Gamma \ff \cdot \nu \, dS = 0 \; .
+  \int_\Gamma \ff \cdot \bnu \, dS = 0 \; .
 \end{equation}
@@
 %
-For a given function $\bh$ defined on $\Gamma$,
+For a given function $\ff$ defined on $\Gamma$,
 the exterior Dirichlet boundary value problem is to
@@
 \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
-\bu &= \bh \quad \bx \in \Gamma \, . \nonumber
+\bu &= \ff \quad \bx \in \Gamma \, . \nonumber
 \end{aligned}
@@
     \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
-    \bu &= \bh \quad \bx \in \Gamma \, 
+    \bu &= \ff \quad \bx \in \Gamma \, 
   \end{aligned}
@@
 \end{equation}
-Then each component of $\bu$ is harmonic and has a convergent Laurent
-expansion in $E$.
+Then each component of $\bu$ is harmonic in $E$.
 \end{lem}
@@
 u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} \frac{a_{j,n} e^{i n \theta}}{r^{|n|}} 
-\, . \nonumber
+\, , \nonumber
 \end{equation}
+for sufficiently large $r$.
+Finally, by \cref{cor:analytic}, $\bu$ is
+analytic in $E$. Therefore, each $u_j$ is harmonic
+throughout $E$.
 \end{proof}
@@
 
-\subsection{Existence results}
+\subsection{The integral equations and their nullspaces}
+
+In this section, we establish the correspondence between the
+integral equations arising from layer potential representations
+of solutions to the oscillatory Stokes equation and
+Stokes eigenvalues.
+
+Let $\Omega$ be a bounded domain given as
+the intersection of a simply connected domain $\Omega_0$ and
+the exteriors of a finite collection of bounded,
+simply connected domains $\{ \Omega_i \}_{i=1}^m$
+whose closures are contained in $\Omega_0$. Note that the
+exterior of $\Omega$, which we denote by $E$, is the
+disjoint union of the exterior of $\Omega_0$, which we
+denote $E_0$, with the sets $\{ \Omega_i \}_{i=1}^m$.
+Let $\Gamma$ denote the boundary of $\Omega$ with the normal
+$\bnu$ pointing out of $\Omega$.
+
+We represent
+the solution to the Dirichlet problem using
+a double layer potential defined on $\Gamma$, i.e.
+setting $\bu = \bD \bmu$ for
+an unknown density $\bmu$. Substituting this representation
+into the Dirichlet boundary condition and applying
+\cref{lem:jump-conds}, we obtain
+
+\begin{equation}
+  (\cI - 2\cD) \bmu = 2\ff \; , \label{eq:inteq_dir_int}
+\end{equation}
+for the interior problem, and
+
+\begin{equation}
+  (\cI + 2\cD) \bmu = 2\ff \; , \label{eq:inteq_dir_ext}
+\end{equation}
+for the exterior problem.
+
+Similarly, we represent
+the solution to the Neumann problems using
+a single layer potential defined on $\Gamma$, i.e.
+setting $\bu = \bS \brho$ for
+an unknown density $\brho$. Substituting this representation
+into the Neumann boundary condition and applying
+\cref{lem:jump-conds}, we obtain
+
+\begin{equation}
+  (\cI + 2\cN) \brho = 2\bg \; , \label{eq:inteq_neu_int}
+\end{equation}
+for the interior problem, and
+
+\begin{equation}
+  (\cI - 2\cN) \brho = 2\bg \; , \label{eq:inteq_neu_ext}
+\end{equation}
+for the exterior problem.
+
+\subsection{Computational Fredholm determinants}

### 2019-02-18 doc/draft-01-stokes/02prelim.tex
Updating analysis section

@@
 \begin{align}
-  T_{ijk} &= - \partial_{x_j} \Glap \delta_{ik}
-  + \partial_{x_k} \left ( -\Delta \Gbh \delta_{ij} +
+  T_{ij\ell} &= - \partial_{x_j} \Glap \delta_{i\ell}
+  + \partial_{x_\ell} \left ( -\Delta \Gbh \delta_{ij} +
   \partial_{x_i} \left(\partial_{x_j} \Gbh \right) \right)
   \nonumber \\
-  & \qquad+ \partial_{x_i} \left ( -\Delta \Gbh \delta_{kj} +
-  \partial_{x_k} \left(\partial_{x_j} \Gbh \right) \right)
+  & \qquad+ \partial_{x_i} \left ( -\Delta \Gbh \delta_{\ell j} +
+  \partial_{x_\ell} \left(\partial_{x_j} \Gbh \right) \right)
   \; . \label{eq:ostress} \nonumber
@@
 \begin{equation}
-  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla \Glap
+  \TT_{\cdot,\cdot,\ell} \nu_\ell = -\bnu \otimes \nabla \Glap
   + \partial_\nu \left ( -\Delta \Gbh \II
@@
 \begin{equation} \label{eq:doublelayer}
-  \bD [\bmu] (\xx) = \int_\Gamma \left ( \TT_{\cdot,\cdot,k}(\xx,\yy)
-  \nu_k(\yy)\right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
+  \bD [\bmu] (\xx) = \int_\Gamma \left ( \TT_{\cdot,\cdot,\ell}(\xx,\yy)
+  \nu_ell(\yy)\right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
 \end{equation}
@@
 \begin{align} \label{eq:stokesdlkernel}
-  \left ( \TT_{\cdot,\cdot,k}(\xx,\yy)\nu_k(\yy) \right )^\intercal
+  \left ( \TT_{\cdot,\cdot,\ell}(\xx,\yy)\nu_\ell(\yy) \right )^\intercal
   \bmu(\yy) &= \left ( - \nabla \Glap(\xx,\yy) + 2 \nabla^\bot
@@
 \begin{equation}
-  \cD [\bmu] (\xx) = \oint_\Gamma \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy)
+  \cD [\bmu] (\xx) = \oint_\Gamma \left ( \TT_{\cdot,\cdot,\ell}\nu_\ell(\yy)
   \right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
@@
 \begin{equation}
-  \cN [\bmu] = \oint_\Gamma \left ( \TT_{\cdot,\cdot,k}\nu_k(\xx)
+  \cN [\bmu] = \oint_\Gamma \left ( \TT_{\cdot,\cdot,\ell}\nu_\ell(\xx)
   \right ) \bmu(\yy) \, dS(\yy) \; .
 \end{equation}
+
+\begin{remark}
+The operators $\cD$ and $\cN$
+depend on the Helmholtz parameter $k$ of the oscillatory Stokes equation.
+In places where it is essential to highlight this dependence, in a slight
+abuse of notation, we will use the symbols $\cD(k)$ and $\cN(k)$ to 
+denote this dependence. 
+\end{remark}
 
@@
   \begin{equation} \label{eq:rep-theorem}
-    \bu(\xx) = \bS [\bsigma(\bu,p)](\xx) - \bD[\bu](\xx) \; .
+    \bS [\bsigma(\bu,p)](\xx) - \bD[\bu](\xx) = \begin{cases} 
+    \bu(\xx) &\quad \xx \in \Omega \, , \\
+    0 &\quad \xx \in \Omega^{C} \; .
+    \end{cases}
   \end{equation}
@@
 
-\subsubsection{Null-space correction}
+\subsubsection{Null-space correction \label{subsubsec:nullspacecorr}}
 
@@
 \begin{lem}
+  \label{lem:propnullspacecorr}
+
   Let $\Omega$ be a domain with $C^2$ boundary and $\bmu$ be
@@
   \item $\cW[\bmu \pm 2 \cD[\bmu]] = 0$,
+  \item If $\int_{\Gamma} p = 0 dS$, then
+  $\cW[\bmu \pm 2 \cD^{T}[\bmu]] = 0$,
   \item $\cW[\cS[\bmu]] = 0$,
@@
   an application of \cref{lem:jump-conds}.
+
 \end{proof}
+
+\begin{remark}
+Since the pressure for the oscillatory Stokes equation is only 
+well-defined up to a constant in either region, we always choose
+a normalization for the pressure which satisfies the conditon
+$\int_{\Gamma} p dS = 0$.
+\end{remark}

### 2019-02-18 doc/draft-01-stokes/03analysis.tex
Updating analysis section

@@
 
-\subsection{The integral equations and their nullspaces}
+\subsection{The integral equations and its null-spaces}
 
@@
 integral equations arising from layer potential representations
-of solutions to the oscillatory Stokes equation and
-Stokes eigenvalues.
+of solutions to the oscillatory Stokes equation with Dirichlet 
+boundary conditions and the associated Stokes eigenvalues.
 
@@
 
-We represent
-the solution to the Dirichlet problem using
+We analyze two different representations for the Dirichlet problem---
+when the velocity is represented using a double layer potential,
+i.e. setting $u=\bD \bmu$, and when the velocity
+is represented using a mixed layer potential,
+i.e. setting $u=(\bS + \bD)\bmu$, where in both cases $\bmu$ 
+is the unknown density to be solved for. 
+Eventhough both reprensentations result in a second kind
+Fredholm integral equation for the Dirichlet problem,
+the spectral properties of these representations are very
+different based on the genus of the domain.
+We analyze the double layer potential representation 
+in~\cref{subsec:dlanalysis}
+and the mixed layer potential representation in~\cref{subsec:mixedanalysis}.
+
+\begin{remark}
+The analysis of integral equations for the oscillatory Stokes
+equation and the correspondance betweeen its null spaces and the eigenvalues
+of Stokes equation is analogous to a similar analysis carried out
+for integral equations for Helmholtz equation and the eigenvalues
+for the Laplace equation in~\cref{linzhao}.
+$\bu$ plays the role of the Dirichlet data, and $\bt$ plays the role
+of the Neumann data. 
+Once the Green's representation and uniqueness results for the 
+the oscillatory Stokes equation have been established,
+the remainder of the analysis of the integral equations
+is in spirit identical to the analysis presented in~\cref{linzhao}.
+\end{remark}
+
+\subsubsection{Double layer reprensentation}
+Suppose that the solution to the Dirichlet problem using
 a double layer potential defined on $\Gamma$, i.e.
 setting $\bu = \bD \bmu$ for
-an unknown density $\bmu$. Substituting this representation
+an unknown density $\bmu$. 
+Substituting this representation
 into the Dirichlet boundary condition and applying
@@
 \begin{equation}
-  (\cI - 2\cD) \bmu = 2\ff \; , \label{eq:inteq_dir_int}
+  (\cI - 2\cD(k)) \bmu = -2\ff \; , \label{eq:inteq_dir_int}
 \end{equation}
-for the interior problem, and
+for the interior problem.
+As noted in~\cref{subsubsec:nullspacecorr}, the standard layer potentials
+result in rank-deficient representations for the boundary value problem.
+It is well-known that~\cref{eq:inteq_dir_int} has a two dimensional
+null-space due to this issue. Thus, proceeding as discussed earlier,
+we instead analyze the equation
+\begin{equation}
+(\cI - 2\cD(k) + -2\cW) \bmu = 2\ff \; \, . \label{eq:inteq_dir_int_mod}
+\end{equation}
 
+On simply connected domains, there is a one-to-one correspondance between
+the eigenvalues of the Dirichlet problem for Stokes equation
+and the values of $k$ for which the operator $(\cI - 2\cD(k) - 2\cW)$
+is not invertible. 
+The following theorem proves this result.
+
+\begin{thm}
+Suppose that $\Omega$ is a simply connected domain, then the operator
+$(\cI - 2\cD(k) - 2 \cW)$ is not invertible if and only if $k$ is 
+Dirichlet eigenvalue for Stokes equation on $\Omega$.
+\end{thm}
+\begin{proof}
+Suppose that $k$ is not a Dirichlet eigenvalue for Stokes equation on
+$\Omega$. 
+Suppose further that $\bmu$ satisfies
 \begin{equation}
-  (\cI + 2\cD) \bmu = 2\ff \; , \label{eq:inteq_dir_ext}
+(\cI - 2\cD(k) - 2\cW) \bmu = 0 \, , \label{eq:dlproofrep}
 \end{equation}
-for the exterior problem.
+i.e. $\bmu$ is in the null-space
+of $(\cI - 2 \cD_{k} - 2 \cW)$. 
+Applying the operator $\cW$ to~\cref{eq:dlproofrep} and 
+using~\cref{lem:propnullspacecorr}, we get
+\begin{equation}
+0 = \cW [(\cI - 2\cD_{k} - 2\cW)[\bmu]] = \cW [\bmu] \, .
+\end{equation}
+Thus~\cref{eq:dlproofrep} reduces to
+\begin{equation}
+(\cI - 2 \cD_{k})\bmu = 0\, .
+\end{equation}
+Suppose now $\bu = -2\cD[\bmu]$ in $\Omega$.
+Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
+and applying~\cref{lem:jump-conds}, we get that the interior
+limit of the velocity $\bu^{-} = (\cI - 2\cD) \bmu = 0$ on $\Gamma$. 
+Since $k$ is not a Dirichlet eigenvalue for the Stokes equation on 
+$\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
+This in particular implies that the interior limit of the surface traction
+denoted by $\bt^{-} = 0$ on $\Gamma$. 
+Using~\cref{lem:jump-conds} again for the jump in surface traction
+for the double layer potential, we conclude that the exterior limit
+of the surface traction $\bt^{+} = 0$ on $\Gamma$. 
+Note that $\bu$ is a radiating solution of the oscillatory
+Sotkes equation in the exterior $E$.
+From uniqueness of the Neumann problem in the exterior $E$, we conclude
+that $\bu \equiv 0$ in $E$ as well, which in particular implies that
+the exterior limit of the velocity $\bu^{+}=0$ on $\Gamma$.   
+Using the jump conditions in~\cref{lem:jump-conds} again, we
+get that $\bmu = \frac{1}{2}(\bu^{+} - \bu^{-}) = 0$ \, .
+Thus $(\cI - 2\cD(k) - 2\cW)$ is invertible is $k$ is not a Dirichlet
+eigenvalue for the Stokes equation on $\Omega$.
 
-Similarly, we represent
-the solution to the Neumann problems using
-a single layer potential defined on $\Gamma$, i.e.
-setting $\bu = \bS \brho$ for
-an unknown density $\brho$. Substituting this representation
-into the Neumann boundary condition and applying
-\cref{lem:jump-conds}, we obtain
+From Green's representation for the oscillatory Stokes qeuation, 
+we know that 
+  \begin{equation} \label{eq:rep-theorem}
+    \bS [\bt](\xx) - \bD[\bu](\xx) = \begin{cases} 
+    \bu(\xx) &\quad \xx \in \Omega \, , \\
+    0 &\quad \xx \in \Omega^{C} \; .
+    \end{cases}
+  \end{equation}
+Suppose thatw $k$ is Dirichlet eigenvalue for the Stokes equation on $\Omega$
+and let $\bu$ denote the corresponding eigenfunction and let $\bt$ denote
+the surface traction associated with the eigenfunction. 
+Applying the Green's theorem to the pair $\bt^{-}, \bu^{-}$ and taking 
+its derivative on $\Gamma$ using~\cref{lem:jump-conds}, we get
+\begin{equation}
+\bt^{-} = (\cD^{T} + \frac{1}{2} \cI) \bt^{-} \, . 
+\end{equation}
+Applying $\cW$ to the above equation and using~\cref{lem:propnullspacecorr},
+we get that $\cW[\bt^{-}] = 0$. 
+Thus,
+\begin{equation}
+(\cI - 2\cD^{T} - 2\cW)\bt^{-} = 0 \, .
+\end{equation}
+Since $\bt^{-}$ is non-trivial, and $\cW$ is self-adjoint, 
+it follows from the Fredholm alternative
+that the operator $\cI - 2\cD(k) - 2\cW$ is also not invertible.
+\end{proof}
 
+On simply connected domains, thus there is a one-to-one correspondance
+between the invertibility of the operator $\cI - 2\cD(k) - 2\cW$ 
+and the eigenvalues of the Dircihlet problem for Stokes equations. 
+However, on multiply connected domains, this is not the case.
+Whilst, it is true that the operator $\cI -2\cD(k) -2\cW$ 
+is not invertible when $k$ is the Dircihlet eigenvalue, it turns
+out that the operator is also not invertible when $k$ is 
+an interior Neumann eigenvalue corresponding to one of the obstacle
+regions $\Omega_{i}$, $i\neq 0$.
+The following lemma proves this result for a region with one obstacle
+boundary, the extension to the general case is a straightforward.
+
+\begin{lemma}
+Suppose that $\Omega$ is a multiply connected domain given by the 
+intersection of $\Omega_{0}$ and the exterior of $\Omega_{1}$
+(see~\cref{fig:1ply}). 
+Then the operator $\cI - 2\cD(k) - 2\cW$ has a non-trivial
+null space if $k$ is a Neumann eigenvalue of $\Omega_{1}$.
+\end{lemma}
+
+\begin{proof}
+Suppose that $k$ is a Neumann eigenvalue of $\Omega_{1}$. 
+$\tilde{\bu}$ be the eigenmode corresponding to this eigenvalue. 
+Note that $\tilde{\bu}$ is not identically $0$ on the boundary $\Gamma_{1}$
+of $\Omega_{1}$.
+Since $\tilde{\bu}$ is an interior Neumann eigenfunction, we note that
+the surface traction corresponding to the solution $\bt^{-} = 0$
+on the boundary.
+Applying Green's identity~\cref{thrm:rep-theorem}, to the solution 
+$\tilde{bu}$ in the interior and taking the interior limit we get
 \begin{equation}
-  (\cI + 2\cN) \brho = 2\bg \; , \label{eq:inteq_neu_int}
+\tilde{\bu} = \frac{1}{2}\tilde{\bu} + \bD_{\Gamma_{1}}[\tilde{\bu}] +
+\bS [\bt^{-}] \implies \frac{1}{2} \tilde{\bu} - \bD_{\Gamma_{1}}[\tilde{\bu}]
+= 0\, .
 \end{equation}
-for the interior problem, and
+Note that the sign of the $\bD$ in the representation theorem is fixed
+since the normal is pointing inwards for the boundary $\Omega_{1}$.
+Thus, $\tilde{\bu}$ is a non-trivial null vector of the operator 
+$\frac{1}{2}\cI - \bD_{\Gamma_{1}}$. 
+Furthermore since $\tilde{\bu}$ is the boundary data of 
+the solution of the oscillatory Stokes equation in $\Omega_{1}$, we
+get that $\cW_{\Gamma_{1}}[\tilde{\bu}] = 0$.
+Setting $\bmu = \tilde{\bu}$ on $\Gamma_{1}$, and $\bmu = 0$ on $\Gamma_{0}$,
+we obtain a non-trivial null vector for the operator $\cI - 2\cD(k) -2\cW$
+on the boundary $\Gamma_{0} \cup \Gamma_{1}$.
+\end{proof}
 
+As noted in~\cref{linzhao}, this lack of one-to-one correspondance between
+the invertibility of the integral operator $\cI - 2\cD(k) - 2\cW$
+and the Dirichlet eigenvalues of the Stokes operator on multiply
+connected domains causes non-robustness and introduces near 
+resonanaces for simply connected domains
+which are almost multiply connected. 
+This issues is discussed in detail
+in example~\cref{sec:numanalysis-nearly-mult-con}.
+
+\subsubsection{Mixed layer potential representation}
+The non-robustness of the double layer potential representation
+for computing the Dirichlet eigenvalues of Stokes equation can be remdied
+by the standard approach of using the mixed layer potential representation,
+i.e. setting
+$\bu = (\bD + ik \bS)
+\bmu$, 
+where $\bmu$ is the unknown density to be solved for. 
+On imposing the boundary conditions and using~\cref{lem:jump-conds}, 
+we obtain the following integral equation on the boundary 
 \begin{equation}
-  (\cI - 2\cN) \brho = 2\bg \; , \label{eq:inteq_neu_ext}
+(\cI - 2\cD(k) - 2ik \cS(k)) \bmu = -2 \bf \, . 
 \end{equation}
-for the exterior problem.
+As noted in~\cref{subsubsec:nullspacecorr}, this integral equation 
+is also rank-deficient, and we instead use the following 
+equivalent integral equation for $\bmu$,
+\begin{equation}
+(\cI - 2\cD(k) -2ik \cS(k)  -2\cW)\bmu = -2 \bf \, .
+\end{equation}
+
+We now prove that for any bounded region $\Omega$ (simply or multiply
+connected) with $C^{2}$ boundaries, there exists a one-to-one correspondance
+between the invertibility of the operator
+$\cI - 2\cD(k) - 2ik \cS(k) - 2\cW)$ and the Dirichlet eigenvalues
+of the Stokes operator on $Omega$. 
+The following theorem proves this result.
+
+\begin{thm}
+Suppose $\Omega$ is a bounded region defined by the intersection of a 
+simply connected domain $\Omega_{0}$ and the exteriors of a finite collection
+of bounded simply connected domains $\{ \Omega_{i} \}_{i=1}^{m}$.
+As before let $\Gamma_{i}$ denote the boundary of $\Omega_{i}$ and let
+$\Gamma = \cup_{i=0}^{m} \Gamma_{i}$ denote the boundary of $\Omega$.
+Then the operator $\cI - 2\cD(k) - 2ik \cS(k) - 2\cW$.
+is invertible if and only if $k$ is not a Dirichlet eigenvalue
+for the Stokes operator on $\Omega$.
+\end{thm}
+
+\begin{proof}
+Suppose that $k$ is not a Dirichlet eigenvalue for Stokes equation on
+$\Omega$. 
+Suppose further that $\bmu$ satisfies
+\begin{equation}
+(\cI - 2\cD(k) -2ik\cS(k) - 2\cW) \bmu = 0 \, , \label{eq:mlproofrep}
+\end{equation}
+i.e. $\bmu$ is in the null-space
+of $(\cI - 2 \cD_{k} - 2ik \cS(k) - 2 \cW)$. 
+Applying the operator $\cW$ to~\cref{eq:mlproofrep} and 
+using~\cref{lem:propnullspacecorr}, we get
+\begin{equation}
+0 = \cW [(\cI - 2\cD(k) - 2ik\cS(k) - 2\cW)[\bmu]] = \cW [\bmu] \, .
+\end{equation}
+Thus~\cref{eq:mlproofrep} reduces to
+\begin{equation}
+(\cI - 2 \cD(k) - 2ik \cS(k))\bmu = 0\, .
+\end{equation}
+Suppose now $\bu = -2\cD[\bmu] -2ik\cS[\bmu]$ in $\Omega$.
+Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
+and applying~\cref{lem:jump-conds}, we get that the interior
+limit of the velocity $\bu^{-} = (\cI - 2\cD -2ik\cS) \bmu = 0$ on $\Gamma$. 
+Since $k$ is not a Dirichlet eigenvalue for the Stokes equation on 
+$\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
+This in particular implies that the interior limit of the surface traction
+denoted by $\bt^{-} = 0$ on $\Gamma$.
+Using~\cref{lem:jump-conds}  
+we observe that the exterior limit 
+of the surface traction is $\bt^{+} = ik \bmu(\xx)$
+and the exterior limit of the velocity is 
+$\bu^{+} = \bmu(\xx)$ on $\Gamma$.
+\begin{remark}
+Note that there is a slight abuse of notation here for the obstacle
+boundaries, since the exterior limit with respect to $\Omega$ 
+for the boundary $\Gamma_{j}$ is the traditional interior 
+limit with respect to the obstacle region $\Omega_{j}$.
+\end{remark}
+We first show that $\bmu=0$ on $\Gamma_{0}$. 
+To this end, note that $\bu$ is a radiating solution of the oscillatory
+Sotkes equation in the exterior $E$.
+From uniqueness of the impedance problem in the exterior $E$, we conclude
+that $\bu \equiv 0$ in $E$ as well, which in particular implies that
+the exterior limit of the velocity $\bu^{+}=0$ on $\Gamma_{0}$.   
+Using the jump conditions in~\cref{lem:jump-conds} again, we
+get that $\bmu = \frac{1}{2}(\bu^{+} - \bu^{-}) = 0$ \, on
+$\Gamma_{0}$. 
+To show that $\bmu=0$ on $\Gamma_{j}$, we observe that
+$\bmu$ is also a solution to the oscillatory Stokes equation
+in each of the obstacles $\Omega_{j}$ as well.
+Applying Green's identity and using the fact that 
+the interior limits with respect to $\Omega_{j}$ (see remark)
+of the surface traction and the velocity
+are $ik \bmu$ and $\bmu$ respectively, we get
+\begin{equation}
+\int_{\Omega_{j}} (|e(\bu)|^{2} - \overline{k}^{2} |\bu|^2) dV 
+= \int_{\Gamma_{j}} \bu \cdot \overline{\bt} dS = 
+i\overline{k}\int_{\Gamma_{j}} |\bmu|^2 dS \, .
+\end{equation}
+Taking the imaginary part of the above equation, we get
+\begin{equation}
+2 \text{Re}(k) \text{Im}(k) \int_{\Omega_{j}} |\bu|^2 + \text{Re}(k)
+\int_{\Gamma_{j}} |\bmu|^2 dS = 0 \, .
+\end{equation}
+This implies that $\bmu=0$ for $\xx \in \Gamma_{j}$, $j=1,2,\ldots m$. 
+Thus $\cI - 2\cD(k) -2\cS(k) -2\cW$ is invertible when $k$ 
+is not a Dirichlet eigenvalue for the Stokes equation on $\Omega$.
+
+From Green's representation for the oscillatory Stokes equation, 
+we know that 
+  \begin{equation} \label{eq:rep-theorem}
+    \bS [\bt](\xx) - \bD[\bu](\xx) = \begin{cases} 
+    \bu(\xx) &\quad \xx \in \Omega \, , \\
+    0 &\quad \xx \in \Omega^{C} \; .
+    \end{cases}
+  \end{equation}
+Suppose thatw $k$ is Dirichlet eigenvalue for the Stokes equation on $\Omega$
+and let $\bu$ denote the corresponding eigenfunction and let $\bt$ denote
+the surface traction associated with the eigenfunction.
+Note that the Green's representation theorem implies that 
+$\bS[\bt^{-}] = 0$, since $\bu^{-}=0$ on $\Gamma$. 
+Applying the Green's theorem to the pair $\bt^{-}, \bu^{-}$ and taking 
+its derivative on $\Gamma$ using~\cref{lem:jump-conds}, we get
+\begin{equation}
+\bt^{-} = (\cD^{T} + \frac{1}{2} \cI) \bt^{-} \, . 
+\end{equation}
+Applying $\cW$ to the above equation and using~\cref{lem:propnullspacecorr},
+we get that $\cW[\bt^{-}] = 0$. 
+Thus, combining all three identities
+\begin{equation}
+(\cI - 2\cD^{T} -2ik \cS - 2\cW)\bt^{-} = 0 \, .
+\end{equation}
+Since $\bt^{-}$ is non-trivial, and $ik \cS, \cW$ are self-adjoint, 
+it follows from the Fredholm alternative
+that the operator $\cI - 2\cD(k) -2ik \cS - 2\cW$ is also not invertible.
+\end{proof}
 

### 2019-03-07 doc/draft-01-stokes/helm-note-dpc.tex
Adding note for helmholtz d + point charge representation

\documentclass[preprint,12pt]{article} 
\usepackage{b}
\usepackage[a4paper]{geometry}
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}
\usepackage[small,it]{caption}
\usepackage{empheq}

\usepackage{subcaption}
\usepackage{amsmath}

\usepackage{cleveref}
\crefname{equation}{}{}
\Crefname{equation}{}{}
\crefname{eqnarray}{}{}
\Crefname{eqnarray}{}{}
\crefname{lemma}{lemma}{lemma}
\crefname{cor}{corollary}{corollary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\bz{{\boldsymbol 0}}
\def\br{{\boldsymbol r}}
\def\bc{{\boldsymbol c}}
\def\bh{{\boldsymbol h}}
\def\bn{{\boldsymbol n}}
\def\bT{{\boldsymbol T}}
\def\bt{{\boldsymbol t}}
\def\xx{{\boldsymbol x}}
\def\bx{{\boldsymbol x}}
\def\yy{{\boldsymbol y}}
\def\by{{\boldsymbol y}}
\def\ss{{\boldsymbol s}}
\def\tt{{\boldsymbol t}}
\def\uu{{\boldsymbol u}}
\def\bu{{\boldsymbol u}}
\def\be{{\boldsymbol e}}
\def\bl{{\boldsymbol \ell}}
\def\ff{{\boldsymbol f}}
\def\bg{{\boldsymbol g}}
\def\GG{{\bf G}}
\def\Gbh{G^{\textrm{BH}}}
\def\Glap{G^{\textrm{L}}}
\def\Ghelm{G^{\textrm{H}}}
\def\Kfark{K^{\textrm{F}}}
\def\II{{\bf I}}
\def\TT{{\bf T}}
\def\bS{{\bf S}}
\def\bD{{\bf D}}
\def\cN{{\mathcal N}}
\def\cS{{\mathcal S}}
\def\cD{{\mathcal D}}
\def\cW{{\mathcal W}}

\def\bsigma{{\boldsymbol \sigma}}
\def\bpsi{{\boldsymbol \psi}}
\def\bmu{{\boldsymbol \mu}}
\def\bnu{{\boldsymbol \nu}}
\def\brho{{\boldsymbol \rho}}
\def\btau{{\boldsymbol \tau}}
\def\bigo{\mathcal{O}}
\def\littleo{o}

\def\Im{{\textrm{\textup{Im}}}}

\newcommand\dwdn{\frac{\partial w}{\partial n}}
\newcommand{\cI}{\mathcal I}
\newcommand{\cC}{\mathcal C}
\newcommand{\bbmat}{\begin{bmatrix}}
\newcommand{\ebmat}{\end{bmatrix}}

\newtheorem{remark}{Remark}
\newtheorem{proposition}{Proposition}
\newtheorem{lem}{Lemma}
\newtheorem{cor}{Corollary}
\newtheorem{thrm}{Theorem}
\newtheorem{definition}{Definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{A note on representation for Helmholtz equations 
on multiply connected domains}
\author{Travis Askham and Manas Rachh}
\date{\today}

\begin{document}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Suppose that $\Omega$ is a multiply connected domain.
The theorem extends for general regions, but for convenience let us assume
that the domain has one hole. Let $\Gamma_{0}$ denote the outer boundary
and let $\Gamma_{1}$ denote the obstacle boundary. 
Let $E$ denote the exterior of $\Gamma_{0}$ and let $D_{1}$ denote the 
interior of $\Gamma_{1}$ (see~\cref{fig:1}). 
Suppose that $x_{1}$ is in the interior of $D_{1}$.

Suppose that we are solving 
\begin{align} 
(\Delta + k^2) u &= 0\quad x \in \Omega \, ,\label{eq:pde} \\
u &= g \quad x \in \Gamma \, , \label{eq:bc}
\end{align}
using the following representation
\begin{equation}
u(x) = \int_{\Gamma} \frac{\partial G_{k}}{\partial n}(x,y) \sigma(y) dS_{y} + \left(\int_{\Gamma_{1}} \sigma(y) dS_{y}\right)
H_{0} (k |x-x_{1}|) \, .
= D_{k}[\sigma](x) + L[\sigma](x) \, .
\end{equation}

On imposing the boundary conditions, we obtain the following integral equation for $\sigma$
\begin{equation}
-\frac{1}{2}\sigma + D_{k} [\sigma] + L [\sigma] = A[\sigma] =  g \, ,
\end{equation}
where
\begin{equation}
A = -\frac{1}{2}I + D_{k} + L
\end{equation}

\begin{thrm}
Suppose that $k$ is not a Dirichlet eigenvalue of $\Omega$ but is a Neumann eigenvalue of $\Omega_{1}$, 
and suppose that $x_{1}$ is not on the nodal set for the correspdonding eigenfunction.
Then $\cN(A) \subset \cN(-\frac{1}{2}I + D_{k})$.
\end{thrm}

\begin{proof}
Suppose that $\sigma \in \cN(A)$. Then setting $u = D_{k} \sigma + L[\sigma]$ and imposing the boundary conditions, 
we note that $u$ satisfies the homogeneous Dirichlet boundary value problem for Helmholtz's equations. 
Since have assumed that $k$ is not a Dirichlet eigenvalue of $\Omega_{1}$, we conclude that
$u\equiv = 0$ on $\Omega$. 
Thus $\frac{\partial u}{\partial n} = 0$ when approached from the interior of $\Omega$. 
Standard arguments show that $\sigma =0$ on $\Gamma_{0}$ which follows from the uniqueness of solutions
to the exterior Neumann problem for Helmholtz equation with radiating boundary conditions.

Since the normal derivative of the double layer is continuous across the boundary and since L[$\sigma$] 
is smooth across the boundary as well, we conclude that $\frac{\partial u}{\partial n} = 0$ 
when viewed as the interior limit from $D_{1}$.

Suppose that $v$ is the interior Neumann eigenfunction associated with eigenvalue $k$. 
Then applying Green's identity on $D_{1}$, we get
\begin{equation}
\int_{D_{1}} v (\Delta + k^2) u - u (\Delta+k^2) v =
\int_{\Gamma_{1}} v \frac{\partial u}{\partial n} - u \frac{\partial v}{\partial n} dS \, .
\end{equation}
$(\Delta + k^2)v = 0$ for $x\in D_{1}$ since $v$ is an interior Neumann eigenfunction.
$\frac{\partial v}{\partial n} = 0$ for $x\in \Gamma_{1}$ since $v$ is an interior Neumann eigenfunction.
$\frac{\partial u}{\partial n} = 0$ from above. 
$(\Delta+k^2)u =\int_{\Gamma_{1}} \sigma \delta_{x_{1}}$ due to the $H_{0}$ term, the double layer satisfies Helmholtz equation
in the interior as well, combining all of this, we get
\begin{equation}
\int_{\Gamma_{1}} \sigma v(x_{1}) = 0 \, ,
\end{equation}
since we have assumed that $x_{1}$ is not on the nodal set of an interior Neumann eigenfunction, we conclude that
$\int_{\Gamma_{1}} \sigma = 0$ which implies that $L\sigma = 0$.
This further implies that $\sigma \in \cN( -\frac{1}{2} I + D_{k})$ and proves the result. 
\end{proof}

This result means that if we can find a null vector of $-\frac{1}{2} I + D_{k}$ which satisfies
$\int_{\Gamma_{1}} \sigma = 0$, then that by tautology must've been a null-vector for our operator $A$.
Thus, if the dimension of the null-space is more than one-dimensional, then all hope is lost, as we can
always find a null-vector which integrates to $0$. So there is no hope on domains like squares or rectangles.
But if the null-space is one-dimensional, then there might be some hope by showing that 
the integral of the null vector must not equal to $0$. All in all it seems pretty grim that this theorem might
be true in general. 
\end{document}

### 2019-03-08 doc/draft-01-stokes/02prelim.tex
cleaning up section 2,3 (done till 3.5 except last theorem)

@@
 $\bsigma$ on $\bu$ and $p$.
+If $\Gamma$ is the boundary of a region $\Omega$ and $\bnu$ is the outward
+normal to $\Gamma$, the surface traction $\bt$ on $\Gamma$ 
+is the Neumann data, i.e. 
+\begin{equation}
+\bt = \bsigma \cdot \bnu \, .
+\end{equation}
 
 We seek solutions of \cref{eq:ostokes} in the space
-
 \begin{equation}
@@
   \bD [\bmu] (\xx) = \int_\Gamma \left ( \TT_{\cdot,\cdot,\ell}(\xx,\yy)
-  \nu_ell(\yy)\right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
+  \nu_\ell(\yy)\right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
 \end{equation}
@@
 If we write $\bmu = \bnu \mu_\nu + \btau \mu_\tau$,
-where $\btau = \bmu^\bot$ is the positively oriented unit
+where $\btau = \bnu^\bot$ is the positively oriented unit
 tangent to the curve, then we have
@@
 The adjoint of $\cD$ is of particular interest; we have
-$\cD^\intercal = \cN$, where
-
 \begin{equation}
-  \cN [\bmu] = \oint_\Gamma \left ( \TT_{\cdot,\cdot,\ell}\nu_\ell(\xx)
+  \cD^{\intercal} [\bmu] = \oint_\Gamma \left ( \TT_{\cdot,\cdot,\ell}\nu_\ell(\xx)
   \right ) \bmu(\yy) \, dS(\yy) \; .
@@
 \begin{remark}
-The operators $\cD$ and $\cN$
+The operators $\cD$ and $\cD^{\intercal}$
 depend on the Helmholtz parameter $k$ of the oscillatory Stokes equation.
 In places where it is essential to highlight this dependence, in a slight
-abuse of notation, we will use the symbols $\cD(k)$ and $\cN(k)$ to 
+abuse of notation, we will use the symbols $\cD_{k}$ and $\cDt_{k}$ to 
 denote this dependence. 
@@
   the pair $(\bu,p)$ satisfy the oscillatory stokes equations
-  \cref{eq:ostokes} in $\Omega$. Then
+  \cref{eq:ostokes} in $\Omega$. Let $\bt$ denote the surface
+  traction associated with the velocity $\bu$. Then
 
   \begin{equation} \label{eq:rep-theorem}
-    \bS [\bsigma(\bu,p)](\xx) - \bD[\bu](\xx) = \begin{cases} 
+    \bS [\bt](\xx) - \bD[\bu](\xx) = \begin{cases} 
     \bu(\xx) &\quad \xx \in \Omega \, , \\
@@
 \begin{lem}[Jump conditions] \label{lem:jump-conds}
-  Let $\bS$, $\bsigma_\bS$, $\bD$, $\cD$, and $\cN$ be
+  Let $\bS$, $\bsigma_\bS$, $\bD$, $\cD$, and $\cDt$ be
   the layer potentials and operators defined above and
@@
     \lim_{h \downarrow 0} \bsigma_\bS[\bmu](\xx_0 \pm h\bnu(\xx_0)) \cdot \bnu(\xx_0)
-    &= \mp \frac{1}{2} \bmu(\xx_0) + \cN[\bmu](\xx_0) \\
+    &= \mp \frac{1}{2} \bmu(\xx_0) + \cDt[\bmu](\xx_0) \\
     \lim_{h \downarrow 0} \bD[\bmu](\xx_0 \pm h\bnu(\xx_0)) 
@@
   \item $\cW^\intercal = \cW$,
-  \item $\cW[\bmu \pm 2 \cD[\bmu]] = 0$,
-  \item If $\int_{\Gamma} p = 0 dS$, then
-  $\cW[\bmu \pm 2 \cD^{T}[\bmu]] = 0$,
+  \item $\cW[\bmu - 2 \cD[\bmu]] = 0$,
   \item $\cW[\cS[\bmu]] = 0$,
@@
 \end{proof}
-
-\begin{remark}
-Since the pressure for the oscillatory Stokes equation is only 
-well-defined up to a constant in either region, we always choose
-a normalization for the pressure which satisfies the conditon
-$\int_{\Gamma} p dS = 0$.
-\end{remark}

### 2019-03-08 doc/draft-01-stokes/03analysis.tex
cleaning up section 2,3 (done till 3.5 except last theorem)

@@
 
-In this section, we develop some uniqueness
-results for the oscillatory Stokes PDE and describe
-the use of the layer potentials in discovering Stokes
-eigenvalues.
+In this section, we discuss how integral equations.
+can be used to compute to the Stokes eigenvalues.
 %
-We seek solutions in the space
+We closely follow the approach developed by Zhao and Barnett
+for computing the Laplace eigenvalues.
+%
+Their work computes the Laplace eigenvalues using the following
+steps: 1) represent the solution 
+as a layer potential with 
+an unknown density, and choose the representation such that
+you get a second kind integral equation for the unknown density;
+2) establish that the intergral equation is not invertible 
+exactly for the Dirichlet eigenvalues for Laplace's equation;
+3) prove that the zeros of the Fredholm determinant 
+(when the compact operator is in trace class) 
+line up with the Dirichlet eigenvalues; 
+4) and finally, show that when the integral equation
+is discretized using a Nystr\"{o}m method, the zeros of 
+the determinant 
+of the discrete linear system 
+converge exponentially
+to the zeros of the Fredholm determinant.
 
-\begin{equation}
-  A(\Omega) = \{ (\bu,p) \textrm{ s.t. } \bu \in
-  \left ( C^2(\Omega)\times C^2(\Omega) \right ) \cap
-  \left ( C(\bar{\Omega}) \times C(\bar{\Omega}) \right ) \, , \,
-  p \in C^1(\Omega) \times C(\bar{\Omega})\} \; ,
-\end{equation}
-where $\Omega$ is an open domain and $\bar{\Omega}$ denotes
-its closure.
+In this section, we adapt their approach for computing the 
+Dirichlet eigenvalues for Stokes equation. 
 %
-As above, we will assume that all domains have $C^2$ boundaries.
-%
-Most of the results will apply to multiply connected domains
-but we will identify the results which do not.
-%
+We first develop some uniqueness
+results for the osciallatory Stokes PDE which are essential
+for establishing step 2 of the Zhao-Barnett approach.
+To the best of our knowledge, the uniqueness results, particularly
+for exterior domains are new results.
 
-The structure of this section follows that used
-by Colton and Kress \cite[Ch. 3]{colton1983integral}
+In order to prove the uniqueness results, we follow the 
+structure presented in Colton and Kress~\cite[Ch. 3]{colton1983integral}
 for the scalar Helmholtz equation.
@@
 on simply and multiply connected domains.
-%
-Finally, we briefly describe how the approach of Zhao
-and Barnett translates to the present setting, giving
-a robust numerical method for computing Stokes
-eigenvalues.
+
+Once the equivalence between the non-invertibility
+of the second kind integral equation and Dirichlet eigenvalues
+for Stokes equations is established,
+the details of how the Fredholm determinant can be used as a
+numerical tool for computing the Stokes eigenvalues
+follows in a straightforward manner from the results 
+in Zhao and Barnett~\cite{zhao2015robust}. 
+We reproduce the relevant results from their work applied 
+in this context for completeness.
 
@@
   \begin{equation} \label{eq:greenlike}
-    \int_\Omega |2\be(\bu)|^2 - \overline{k}^2 \, dV
+    \int_\Omega |2\be(\bu)|^2 - \overline{k}^2 |\bu|^2 \, dV
     = \int_\Gamma \bu \cdot \overline{\bt} \, dS \; . 
@@
 expansion of $H_{n}^{1,2}(r)$, we note that the projection of 
-$a_{j,n}$ on $r^{|n|}$, and $H_{n}^{j}(k r)$ must be zero. 
+$a_{j,n}$ on $r^{|n|}$, and $H_{n}^{1,2}(k r)$ must be zero. 
 Thus, 
@@
 \end{equation}
-Thus, the conditions for $\bu$ in Rellich's lemma (~\cref{lem:rellich})
+Thus, the conditions for $\bu$ in Rellich's lemma (\cref{lem:rellich})
 are satisfied, and each component of $\bu$ is a harmonic function
@@
 
+\begin{remark}
+For proving the equivalence between Stokes eigenvalues
+of bounded regions $\Omega$ and the non-invertibility
+of corresponding second kind integral equations, we only
+need the uniqueness result for the Neumann problem in the 
+exterior of a simply connected domain. 
+The proof of the exterior Neumann problem in the exterior of several
+obstacles is more involved and presented in the appendix~\cite{app:neuuniqueness}
+\end{remark}
+
 \begin{thrm}[Uniqueness of the Exterior Impedance Problem]
@@
   of a finite collection of bounded domains.
-  Suppose that $\Im(k) \geq 0$ and that
+  Suppose that $\Re(\eta),\Im(\eta),\Re(k),\Im(k) \geq 0$, and that
   $(\bu,p)$ is a radiating solution of the
@@
   \begin{equation}
-\bt - i k \bu = 0 \quad \xx \in \Gamma \, . \nonumber
+\bt - i \eta \bu = 0 \quad \xx \in \Gamma \, . \nonumber
 \end{equation}
@@
 \begin{proof}
-Since $\bu$ satisfies the radiation condition at $\infty$ and $\bt = ik \bu$
+Since $\bu$ satisfies the radiation condition at $\infty$ and $\bt = i\eta \bu$
 on $\Gamma$, it follows from~\cref{eq:repinfest} that
@@
 dV \nonumber \\
-& \qquad + 2 \left( |k|^{2} \int_{\Gamma} |\bu|^{2} dS  \right)
+& \qquad + 2 \left( (k_{1}\eta_{1} + k_{2}\eta_{2}) \int_{\Gamma} |\bu|^{2} dS  \right)
 \, .
@@
 \begin{equation}
-  \int_{\Gamma} |\bu|^{2} = 0 \implies \bu = 0  \quad \xx \in \Gamma \,
+  \int_{\Gamma} |\bu|^{2} = 0 \implies \bu = 0  \quad \xx \in \Gamma \, ,
   \nonumber
@@
 is represented using a mixed layer potential,
-i.e. setting $u=(\bS + \bD)\bmu$, where in both cases $\bmu$ 
+i.e. setting $u=(i\eta \bS + \bD)\bmu$, where in both cases $\bmu$ 
 is the unknown density to be solved for. 
-Eventhough both reprensentations result in a second kind
+Even though both reprensentations result in a second kind
 Fredholm integral equation for the Dirichlet problem,
@@
 for integral equations for Helmholtz equation and the eigenvalues
-for the Laplace equation in~\cref{linzhao}.
+for the Laplace equation in~\cite{zhao2015robust}.
 $\bu$ plays the role of the Dirichlet data, and $\bt$ plays the role
@@
 the remainder of the analysis of the integral equations
-is in spirit identical to the analysis presented in~\cref{linzhao}.
+is in spirit identical to the analysis presented in~\cite{zhao2015robust}.
 \end{remark}
@@
 \subsubsection{Double layer reprensentation}
+\label{subsec:dlanalysis}
 Suppose that the solution to the Dirichlet problem using
@@
 \begin{equation}
-  (\cI - 2\cD(k)) \bmu = -2\ff \; , \label{eq:inteq_dir_int}
+  (\cI - 2\cD_{k}) \bmu = -2\ff \; , \label{eq:inteq_dir_int}
 \end{equation}
@@
 \begin{equation}
-(\cI - 2\cD(k) + -2\cW) \bmu = 2\ff \; \, . \label{eq:inteq_dir_int_mod}
+(\cI - 2\cD_{k}  -2\cW) \bmu = -2\ff \; \, . \label{eq:inteq_dir_int_mod}
 \end{equation}
@@
 the eigenvalues of the Dirichlet problem for Stokes equation
-and the values of $k$ for which the operator $(\cI - 2\cD(k) - 2\cW)$
+and the values of $k$ for which the operator $(\cI - 2\cD_{k} - 2\cW)$
 is not invertible. 
@@
 Suppose that $\Omega$ is a simply connected domain, then the operator
-$(\cI - 2\cD(k) - 2 \cW)$ is not invertible if and only if $k$ is 
+$(\cI - 2\cD_{k} - 2 \cW)$ is not invertible if and only if $k$ is 
 Dirichlet eigenvalue for Stokes equation on $\Omega$.
@@
 \begin{equation}
-(\cI - 2\cD(k) - 2\cW) \bmu = 0 \, , \label{eq:dlproofrep}
+(\cI - 2\cD_{k} - 2\cW) \bmu = 0 \, , \label{eq:dlproofrep}
 \end{equation}
@@
 \begin{equation}
-0 = \cW [(\cI - 2\cD_{k} - 2\cW)[\bmu]] = \cW [\bmu] \, .
+0 = \cW [(\cI - 2\cD_{k} - 2\cW)\bmu] = \cW [\bmu] \, .
 \end{equation}
@@
 \end{equation}
-Suppose now $\bu = -2\cD[\bmu]$ in $\Omega$.
+Suppose now $\bu = -2\bD_{k}[\bmu]$ in $\Omega$.
 Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
 and applying~\cref{lem:jump-conds}, we get that the interior
-limit of the velocity $\bu^{-} = (\cI - 2\cD) \bmu = 0$ on $\Gamma$. 
+limit of the velocity $\bu^{-} = (\cI - 2\cD_{k}) \bmu = 0$ on $\Gamma$. 
 Since $k$ is not a Dirichlet eigenvalue for the Stokes equation on 
@@
 Using the jump conditions in~\cref{lem:jump-conds} again, we
-get that $\bmu = \frac{1}{2}(\bu^{+} - \bu^{-}) = 0$ \, .
-Thus $(\cI - 2\cD(k) - 2\cW)$ is invertible is $k$ is not a Dirichlet
+get that $\bmu = \frac{1}{2}(\bu^{+} - \bu^{-}) = 0$.
+Thus $(\cI - 2\cD_{k} - 2\cW)$ is invertible if $k$ is not a Dirichlet
 eigenvalue for the Stokes equation on $\Omega$.
@@
   \begin{equation} \label{eq:rep-theorem}
-    \bS [\bt](\xx) - \bD[\bu](\xx) = \begin{cases} 
+    \bS_{k} [\bt](\xx) - \bD_{k}[\bu](\xx) = \begin{cases} 
     \bu(\xx) &\quad \xx \in \Omega \, , \\
@@
 Suppose thatw $k$ is Dirichlet eigenvalue for the Stokes equation on $\Omega$
-and let $\bu$ denote the corresponding eigenfunction and let $\bt$ denote
-the surface traction associated with the eigenfunction. 
+and let $\bu$ denote the corresponding eigenfunction, and let $\bt^{-}$ denote
+the surface traction associated with the eigenfunction on the boundary $\Gamma$.
+Since $\bu$ is a Dirichlet eigenfunction, the velocity restricted to the boundary
+$\bu^{-} = 0$. 
 Applying the Green's theorem to the pair $\bt^{-}, \bu^{-}$ and taking 
@@
 \begin{equation}
-\bt^{-} = (\cD^{T} + \frac{1}{2} \cI) \bt^{-} \, . 
+\bt^{-} = (\cDt_{k} + \frac{1}{2} \cI) \bt^{-} \, ,\implies \left(\cI - 2\cDt_{k} \right) 
+\bt^{-} = 0 \, .
 \end{equation}
-Applying $\cW$ to the above equation and using~\cref{lem:propnullspacecorr},
-we get that $\cW[\bt^{-}] = 0$. 
-Thus,
-\begin{equation}
-(\cI - 2\cD^{T} - 2\cW)\bt^{-} = 0 \, .
-\end{equation}
-Since $\bt^{-}$ is non-trivial, and $\cW$ is self-adjoint, 
+From the Fredholm alternative, it then follows that $(\cI - 2\cD)$ has a non-trivial 
+null-space.
+However, we need to prove that $(\cI -2\cD - 2\cW)$ has a non-trivial null-space
+for which we need the following two lemmas.
+
+\begin{lemma}
+$\bnu \in \cN(\cI - 2\cDt_{k})$
+\end{lemma}
+\begin{proof}
+From~\cref{lem:propnullspacecorr}, we note that
+$W[(\cI - 2\cD_{k})\bmu] =0$ implies that $\left<(\cI -2\cD_{k})\bmu ,\bnu \right>$ for
+all $\bmu$, i.e. $\bnu \in R(\cI - 2\cD_{k})^{\perp}$, where
+$R(A)$ denotes the range of the operator $A$. 
+By the Fredholm alternative, the result then follows.
+\end{proof}
+
+\begin{lemma}
+If $\bt^{-}$ is the surface traction associated with an interior Dirichlet
+Stokes eigenfunction $\bu$, then $\bt^{-}$ and $\bnu$ are linearly independent.
+\end{lemma}
+\begin{proof}
+We first note that $\bS_{k}[\bnu](\bx) = 0$ for all $\bx \in \Omega$.
+This follows from the application of the divergence theorem and the fact that
+oscillatory Stokeslet is divergence free in $\Omega$. 
+If $\bt^{-}$ is a surface traction associated with a Stokes eigenvalue, then
+using Green's theorem, it follows that
+$\bS_{k}[\bt^{-}](\bx) = u(\bx) \neq 0$ for $\bx \in \Omega$ and
+thus $\bt^{-}$ and $\bnu$ are linearly independent.
+\end{proof}
+
+We now turn to the proof of the main result of the section.
+We know that $\bt^{-}, \bnu \in \cN(\cI - 2\cDt)$ are two linearly independent
+vectors in the null space.
+Let $c = \left< \bt^{-},\bnu \right>$. Then, it follows that 
+$\left<\bt^{-} -c \bnu, \bnu \right> = 0$ and thus
+$\cW[\bt^{-} - c\bnu] = 0$. 
+Since $\bt^{-}$ and $\bnu$ are linearly independent, we note that
+$\bt^{-} -c\bnu \neq 0$.
+Combining these results, we get that
+$(\cI - 2\cDt_{k} - 2\cW) (\bt^{-} - c\bnu) = 0$. 
+Since $\bt^{-}-c\bnu$ is non-trivial, and $\cW$ is self-adjoint, 
 it follows from the Fredholm alternative
-that the operator $\cI - 2\cD(k) - 2\cW$ is also not invertible.
+that the operator $\cI - 2\cD_{k} - 2\cW$ is also not invertible.
 \end{proof}
@@
 On simply connected domains, thus there is a one-to-one correspondance
-between the invertibility of the operator $\cI - 2\cD(k) - 2\cW$ 
+between the invertibility of the operator $\cI - 2\cD_{k} - 2\cW$ 
 and the eigenvalues of the Dircihlet problem for Stokes equations. 
 However, on multiply connected domains, this is not the case.
-Whilst, it is true that the operator $\cI -2\cD(k) -2\cW$ 
+Whilst, it is true that the operator $\cI -2\cD_{k} -2\cW$ 
 is not invertible when $k$ is the Dircihlet eigenvalue, it turns
@@
 The following lemma proves this result for a region with one obstacle
-boundary, the extension to the general case is a straightforward.
+boundary (the extension to the general case is a straightforward).
 
@@
 (see~\cref{fig:1ply}). 
-Then the operator $\cI - 2\cD(k) - 2\cW$ has a non-trivial
+Then the operator $\cI - 2\cD_{k} - 2\cW$ has a non-trivial
 null space if $k$ is a Neumann eigenvalue of $\Omega_{1}$.
@@
 Applying Green's identity~\cref{thrm:rep-theorem}, to the solution 
-$\tilde{bu}$ in the interior and taking the interior limit we get
+$\tilde{\bu}$ in the interior and taking the interior limit we get
 \begin{equation}
-\tilde{\bu} = \frac{1}{2}\tilde{\bu} + \bD_{\Gamma_{1}}[\tilde{\bu}] +
-\bS [\bt^{-}] \implies \frac{1}{2} \tilde{\bu} - \bD_{\Gamma_{1}}[\tilde{\bu}]
+\tilde{\bu} = \frac{1}{2}\tilde{\bu} + \cD^{\Gamma_{1}}_{k}[\tilde{\bu}] +
+\cS^{\Gamma_{1}} [\bt^{-}] \implies \frac{1}{2} \tilde{\bu} - \cD^{\Gamma_{1}}_{k}[\tilde{\bu}]
 = 0\, .
 \end{equation}
-Note that the sign of the $\bD$ in the representation theorem is fixed
+Note that the sign of the $\bD$ in the representation theorem is switched
 since the normal is pointing inwards for the boundary $\Omega_{1}$.
 Thus, $\tilde{\bu}$ is a non-trivial null vector of the operator 
-$\frac{1}{2}\cI - \bD_{\Gamma_{1}}$. 
+$\frac{1}{2}\cI - \cD^{\Gamma_{1}}_{k}$. 
 Furthermore since $\tilde{\bu}$ is the boundary data of 
 the solution of the oscillatory Stokes equation in $\Omega_{1}$, we
-get that $\cW_{\Gamma_{1}}[\tilde{\bu}] = 0$.
+get that $\cW^{\Gamma_{1}}[\tilde{\bu}] = 0$.
 Setting $\bmu = \tilde{\bu}$ on $\Gamma_{1}$, and $\bmu = 0$ on $\Gamma_{0}$,
-we obtain a non-trivial null vector for the operator $\cI - 2\cD(k) -2\cW$
-on the boundary $\Gamma_{0} \cup \Gamma_{1}$.
+we obtain a non-trivial null vector for the operator $\cI - 2\cD^{\Gamma}_{k} -2\cW^{\Gamma}$
+on the boundary $\Gamma = \Gamma_{0} \cup \Gamma_{1}$.
 \end{proof}
 
-As noted in~\cref{linzhao}, this lack of one-to-one correspondance between
-the invertibility of the integral operator $\cI - 2\cD(k) - 2\cW$
+As noted in~\cite{zhao2015robust}, this lack of one-to-one correspondance between
+the invertibility of the integral operator $\cI - 2\cD_{k} - 2\cW$
 and the Dirichlet eigenvalues of the Stokes operator on multiply
@@
 \subsubsection{Mixed layer potential representation}
+\label{subsec:mixedanalysis}
 The non-robustness of the double layer potential representation

### 2019-03-08 doc/draft-01-stokes/02prelim.tex
more cleaning section 3.5

@@
 simulation of unsteady flow
-\cite{pozrikidis1992boundary,biros2002embedded,
+\cite{Pozrikidis1992,biros2002embedded,
   jiang2013second,ladyzhenskaya1969mathematical}.
@@
 
-\begin{remark}
-The operators $\cD$ and $\cD^{\intercal}$
-depend on the Helmholtz parameter $k$ of the oscillatory Stokes equation.
-In places where it is essential to highlight this dependence, in a slight
-abuse of notation, we will use the symbols $\cD_{k}$ and $\cDt_{k}$ to 
-denote this dependence. 
-\end{remark}
-
 \subsubsection{Representation Theorem}
@@
   an application of \cref{lem:jump-conds}.
+\end{proof}
 
-\end{proof}
+\begin{remark}
+The operators $\bS,\bD,\cD$ and $\cD^{\intercal}$
+depend on the Helmholtz parameter $k$ of the oscillatory Stokes equation.
+In places where it is essential to highlight this dependence, in a slight
+abuse of notation, we will use the symbols $\bS_{k}, \bD_{k},\cD_{k}$ and $\cDt_{k}$ to 
+denote this dependence.
+Similarly, all the above operators and $\cW$ also depend on the boundary of the
+region $\Gamma$. In place where it is necessary to highlight this dependence
+we will use $A^{\Gamma}$ instead of the operator $A$.
+\end{remark}

### 2019-03-08 doc/draft-01-stokes/03analysis.tex
more cleaning section 3.5

@@
 \begin{thm}
+\label{thm:dlmain}
 Suppose that $\Omega$ is a simply connected domain, then the operator
@@
 \begin{equation}
-0 = \cW [(\cI - 2\cD_{k} - 2\cW)\bmu] = \cW [\bmu] \, .
+0 = \cW [(\cI - 2\cD_{k} - 2\cW)\bmu] = -2\cW [\bmu] \, .
 \end{equation}
@@
 i.e. setting
-$\bu = (\bD + ik \bS)
+$\bu = (\bD + i\eta \bS)
 \bmu$, 
-where $\bmu$ is the unknown density to be solved for. 
+where $\bmu$ is the unknown density to be solved for, and $\eta \in \mathbb{R}^{+}$ 
 On imposing the boundary conditions and using~\cref{lem:jump-conds}, 
@@
 \begin{equation}
-(\cI - 2\cD(k) - 2ik \cS(k)) \bmu = -2 \bf \, . 
+(\cI - 2\cD_{k} - 2i\eta \cS_{k}) \bmu = -2 \ff \, . 
 \end{equation}
@@
 \begin{equation}
-(\cI - 2\cD(k) -2ik \cS(k)  -2\cW)\bmu = -2 \bf \, .
+(\cI - 2\cD_{k} -2i\eta \cS_{k}  -2\cW)\bmu = -2 \ff \, .
 \end{equation}
@@
 between the invertibility of the operator
-$\cI - 2\cD(k) - 2ik \cS(k) - 2\cW)$ and the Dirichlet eigenvalues
+$\cI - 2\cD_{k} - 2i\eta \cS_{k} - 2\cW$ and the Dirichlet eigenvalues
 of the Stokes operator on $Omega$. 
@@
 $\Gamma = \cup_{i=0}^{m} \Gamma_{i}$ denote the boundary of $\Omega$.
-Then the operator $\cI - 2\cD(k) - 2ik \cS(k) - 2\cW$.
+Then the operator $\cI - 2\cD_{k} - 2i\eta \cS_{k} - 2\cW$
 is invertible if and only if $k$ is not a Dirichlet eigenvalue
@@
 \begin{equation}
-(\cI - 2\cD(k) -2ik\cS(k) - 2\cW) \bmu = 0 \, , \label{eq:mlproofrep}
+(\cI - 2\cD_{k} -2i\eta\cS_{k} - 2\cW) \bmu = 0 \, , \label{eq:mlproofrep}
 \end{equation}
 i.e. $\bmu$ is in the null-space
-of $(\cI - 2 \cD_{k} - 2ik \cS(k) - 2 \cW)$. 
+of $(\cI - 2 \cD_{k} - 2i\eta \cS_{k} - 2 \cW)$. 
 Applying the operator $\cW$ to~\cref{eq:mlproofrep} and 
@@
 \begin{equation}
-0 = \cW [(\cI - 2\cD(k) - 2ik\cS(k) - 2\cW)[\bmu]] = \cW [\bmu] \, .
+0 = \cW [(\cI - 2\cD_{k} - 2i\eta\cS_{k} - 2\cW)\bmu] = -2\cW [\bmu] \, .
 \end{equation}
@@
 \begin{equation}
-(\cI - 2 \cD(k) - 2ik \cS(k))\bmu = 0\, .
+(\cI - 2 \cD_{k} - 2i\eta \cS_{k})\bmu = 0\, .
 \end{equation}
-Suppose now $\bu = -2\cD[\bmu] -2ik\cS[\bmu]$ in $\Omega$.
+Suppose now $\bu = -2\bD[\bmu] -2i\eta\bS[\bmu]$ in $\Omega$.
 Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
@@
 we observe that the exterior limit 
-of the surface traction is $\bt^{+} = ik \bmu(\xx)$
+of the surface traction is $\bt^{+} = i\eta \bmu(\xx)$
 and the exterior limit of the velocity is 
@@
 of the surface traction and the velocity
-are $ik \bmu$ and $\bmu$ respectively, we get
+are $i\eta \bmu$ and $\bmu$ respectively, we get
 \begin{equation}
@@
 = \int_{\Gamma_{j}} \bu \cdot \overline{\bt} dS = 
-i\overline{k}\int_{\Gamma_{j}} |\bmu|^2 dS \, .
+i\overline{\eta}\int_{\Gamma_{j}} |\bmu|^2 dS \, .
 \end{equation}
@@
 \begin{equation}
-2 \text{Re}(k) \text{Im}(k) \int_{\Omega_{j}} |\bu|^2 + \text{Re}(k)
+2 \text{Re}(k) \text{Im}(k) \int_{\Omega_{j}} |\bu|^2 + \text{Re}(\eta)
 \int_{\Gamma_{j}} |\bmu|^2 dS = 0 \, .
@@
 This implies that $\bmu=0$ for $\xx \in \Gamma_{j}$, $j=1,2,\ldots m$. 
-Thus $\cI - 2\cD(k) -2\cS(k) -2\cW$ is invertible when $k$ 
+Thus $\cI - 2\cD_{k} -2i\eta\cS_{k} -2\cW$ is invertible when $k$ 
 is not a Dirichlet eigenvalue for the Stokes equation on $\Omega$.
@@
 Note that the Green's representation theorem implies that 
-$\bS[\bt^{-}] = 0$, since $\bu^{-}=0$ on $\Gamma$. 
+$\cS_{k}[\bt^{-}] = 0$, since $\bu^{-}=0$ on $\Gamma$. 
 Applying the Green's theorem to the pair $\bt^{-}, \bu^{-}$ and taking 
@@
 \begin{equation}
-\bt^{-} = (\cD^{T} + \frac{1}{2} \cI) \bt^{-} \, . 
+\bt^{-} = (\cDt_{k} + \frac{1}{2} \cI) \bt^{-} \, . 
 \end{equation}
-Applying $\cW$ to the above equation and using~\cref{lem:propnullspacecorr},
-we get that $\cW[\bt^{-}] = 0$. 
-Thus, combining all three identities
+Combining these two identities, we get
+that
 \begin{equation}
-(\cI - 2\cD^{T} -2ik \cS - 2\cW)\bt^{-} = 0 \, .
+(-\cI - 2\cD_{k} -2i\eta \cS_{k}) \bt^{-} = 0 \, .
 \end{equation}
-Since $\bt^{-}$ is non-trivial, and $ik \cS, \cW$ are self-adjoint, 
+As in the proof of~\cref{thm:dlmain}, letting $c = \left< \bt^{-} ,\bnu \right>$, 
+it follows that
+\begin{equation}
+(-\cI - 2\cD_{k} - 2i \eta \cS_{k} - 2\cW) (\bt^{-} - c\bnu) = 0 \, ,
+\end{equation}
+where $\bt^{-} - c\bnu \neq 0$.
+Since $\bt^{-} - c\bnu$ is non-trivial, and $i\eta \cS_{k}, \cW$ are self-adjoint ($i\eta \cS_{k}$ 
+is self-adjoint since we consider inner products without conjugation), 
 it follows from the Fredholm alternative 

### 2019-03-11 doc/draft-01-stokes/03analysis.tex
adding section 3.6

@@
 
-\begin{thm}
+\begin{thrm}
 \label{thm:dlmain}
@@
 Dirichlet eigenvalue for Stokes equation on $\Omega$.
-\end{thm}
+\end{thrm}
 \begin{proof}
@@
 it follows from the Fredholm alternative 
-that the operator $\cI - 2\cD(k) -2ik \cS - 2\cW$ is also not invertible.
+that the operator $\cI - 2\cD(k) -2i\eta \cS - 2\cW$ is also not invertible.
 \end{proof}
@@
 \subsection{Computational Fredholm determinants}
+Having established the equivalence between the Dirichlet eigenvalues
+for Stokes equation and the invertibility of
+the operator $\cI - 2\cD_{k} - 2\cW$ on simply connected domains, we show how 
+the Fredholm determinant can be as a computational tool for detecting
+the non-invertibility of $\cI - 2\cD_{k} - 2\cW$.
+
+First, we briefly review Nystr\"{o}m discretizations for integral operators
+with weakly singular kernels.
+Suppose that $\gamma(t):[0,L] \to \Gamma$ is an arc-length
+paramterization of $\Gamma$, where $L$ is the length of the
+curve $\Gamma$.
+Using this parametrization, the integral equation
+$(\cI - 2\cD_{k} - 2\cW)\bmu = \ff$, 
+can be reformulated as a system of integral equations on 
+$\bL^{2}[0,L]$ of the form 
+\begin{equation}
+\bmu(x) + \int_{0}^{L} \bK(x,y) \bmu(y) dy = \ff(x) \, , 
+\end{equation}
+where $\bK(x,y)$ is $O(|x-y|^2 \log{|x-y|})$ as $x\to y$, and
+is analytic away from $x\neq y$.
+
+Let $K$ denote the integral operator with kernel $\bK$, i.e.
+\begin{equation}
+K[\mu](\bx) = \int_{0}^{L} \bK(x,y) \bmu(y) dy \, .
+\end{equation}
+
+Suppose that $[0,L]$ is discretized using $N$ discretization
+nodes $x_{j}$, $j=1,2,\ldots N$, along with an
+the quadrature rule, $Q_{N}(x,x_{j,N})$, $j=1,2,\ldots N$.
+
+Let $K_{N}$ be the finite dimensional Nystr\"{o}m approximation of
+the integral operator whose kernel is $\bK(x,y)$ defined for all
+continuous functions $\phi$ via the formula:
+\begin{equation}
+K^{N}[\phi](\bx) = \sum_{j=1}^{N} Q^{N}(x,x^{N}_{j})  
+\bK(x,x_{j}^{N}) \phi(x,x_{j}^{N}) \, .
+\end{equation}
+
+The linear system corresponding to the Nystr\"{o}m discretization
+of $\bK$ denoted by $\tilde{K}^{N}$ is then given by
+\begin{equation}
+\tilde{K}^{N}_{i,j} = Q^{N}(x_{i}^{N}, x_{j}^{N}) \bK(x_{i}^{N}, x_{j}^{N})
+\quad i,j=1,2\ldots N \, .
+\end{equation}
+
+\begin{definition}
+The quadrature rule $Q_{N}$ is considered
+to be $p$th order accurate if there exists a $C$ independent of $N$
+such that for all $\bmu \in C^{p}$, 
+\begin{equation}
+\lim_{N\to \infty} |(K_{N} - K)\bmu|_{\bL^{2}([0,L])} \leq C_{\bmu} N^{-p} \, .
+\end{equation}
+\end{definition}
+
+\begin{remark}
+There are many sufficient conditions on
+the choice of $x_{j,N}, $Q_{N}(x,x_{j,N})$ $j=1,2\ldots,N$, $N \in mathbb{N}$
+for which the corresponding Nystr\"{o}m 
+\end{remark}
+
+given byi
+be the finite rank operator 
+The Nystr\"{o}m discretized linear system corresponding to the operator
+$\bK$ is the matrix whose entries are given by
+\begin{equation}
+K_{N} = Q_{N}(x_{i,N},x_{j,N}) \bK(x_{i,N},x_{j,N}) \, .
+\end{equation}
+
+The standard Nystr\"{o}m procedure is to solve the integral equation
+\begin{equation}
+\bmu_{i,N} + \sum_{j=1}^{N} Q_N(x_{i,N},x_{j,N} \bK(x_{i,N},x_{j,N})
+\bmu_{j,N} = \ff(\bx_{i,N}) \, ,
+\end{equation}
+for the unknowns $\bmu_{i,N}$, along with the natural interpolant
+\begin{equation}
+\bmu(\bx) = \ff(\bx) - \sum_{j=1}^{N} Q_N(x,x_{j,N}) \mu_{j,N} \, .
+\end{equation}
+
+\begin{equation}
+\end{equation}
+%Suppose that the quadrature rule $Q_{N}$ satisfies
+%the following two additional constraints:
+%a) 
+%\begin{equation}
+%\sum_{j=1}^{N} |Q_{N}(x,x_{j,N})| \leq C \, ,
+%\end{equation}
+%where $C$ is a constant independent of $x$ and $N$, and b) that
+%\begin{equation}
+%\lim_{x\to y} \sup_{n \in \mathbb{N}} \sum_{j=1}^{N} 
+%|Q_{N}(x,x_{j,N}) - Q_{N}(y,x_{j,N})| \to 0 \, .
+%\end{equation}
+
+Suppose that the domain $[0,L]$, is partitioned into $N$ 
+panels of equal length, where each panel is discretized 
+using order $p$ discretization nodes (e.g.
+
+Let $\cL = -2\cD_{k} - 2\cW$, and let $\cJ_{1}(X)$ denote the 
+space of trace class operators on the Hilbert Space $X$.
+Suppose the boundary $\Gamma$ is parametrized into $N$ panels
+of equal length.
+
+\begin{definition}
+\end{definition}
+
+The following theorem describes how 
+the determinant of a Nystr\"{o}m
+discretized second kind Fredholm equation where the integral
+kernel is weakly-singular converges to $0$ if and only if
+the operator is not invertible.
+
+\begin{thrm}
+\label{thm:mainconvfreddet}
+Suppose that $A:X \to X$ is a compact operator, and that $X$ is a
+Hilbert space
+\end{thrm}
+
+\begin{proof}
+See~\cite{zhao2015robust}, theorem 4.3 for a detailed discussion. 
+\end{proof}
+
+\begin{remark}
+The same analysis does not carry through for the operator
+$\cI - 2 \cD_{k} - 2i\eta \cS_{k} - 2\cW$, 
+since it is not a trace class operator.
+For brevity, let $\cM_{k} = -2\cD_{k} - 2i\eta \cS_{k} - 2\cW$.
+The operator $\cM$ is in $\cJ_{2}(\bL^{2}(\Gamma))$ where
+$\cJ_{2}(\bL^{2}(\Gamma))$ is the space of Hilbert-Schmidt operators
+on $\bL^{2}(\Gamma)$ (the singular values of the operator are square
+summable, as opposed to being summable).
+Thus the Fredholm determinant of $\cI + \cM$
+is not necessarily convergent. 
+However, as noted in~\cite{zhao2015robust}, the convergence i
+result~\cref{thm:mainconvfreddet}
+should be true up to a logarithmic factor in the rate
+of convergence, since the singular values of the operator
+$\cM_{k}$ decay like $\frac{1}{n}$, and the
+Fredholm determinant divergers logarithmically. 
+Let $M_{N,k}$ denote the Nystr\"{o}m discretized operator 
+corresponding to $M$, where $N$ is the number of discretization points
+on the boundary $\Gamma$.
+One way of proving such a result would be to construct a definition 
+of a determinant for Hilbert-Schmidt operators based on the 
+Diximer trace of operators as opposed to the Fredholm determinant
+and prove analogous results for this case.
+Instead, in~\cref{subsec:convannulus}, we demonstrate that
+that $\text{det} (I - M^{N,k}) \to 0$ as $N \to \infty$ if and only 
+if $k$ is a Dirichlet eigenvalue for the Stokes operator, and that
+the convergence to $0$ is exponential at the eigenvalues even in 
+this case.
+\end{remark}

### 2019-03-11 doc/draft-01-stokes/03analysis.tex
Updating small changes in 3.6

--- 2019-03-08 doc/draft-01-stokes/03analysis.tex
@@
 \subsection{Computational Fredholm determinants}
+Having established the equivalence between the Dirichlet eigenvalues
+for Stokes equation and the invertibility of
+the operator $\cI - 2\cD_{k} - 2\cW$ on simply connected domains, we show how 
+the Fredholm determinant can be as a computational tool for detecting
+the non-invertibility of $\cI - 2\cD_{k} - 2\cW$.
+
+First, we briefly review Nystr\"{o}m discretizations for integral operators.
+Suppose that $\gamma(t):[0,L] \to \Gamma$ is an arc-length
+paramterization of $\Gamma$, where $L$ is the length of the
+curve $\Gamma$.
+Using this parametrization, the integral equation
+$(\cI - 2\cD_{k} - 2\cW)\bmu = \ff$, 
+can be reformulated as a system of integral equations on 
+$C[0,L]$ of the form 
+\begin{equation}
+\bmu(x) + \int_{0}^{L} \bK(x,y) \bmu(y) dy = \ff(x) \, ,  \label{inteqfreddet}
+\end{equation}
+where $\bK(x,y)$ is $O(|x-y|^2 \log{|x-y|})$ as $x\to y$, and
+is analytic away from $x\neq y$.
+Let $K$ denote the integral operator with kernel $\bK$, i.e.
+\begin{equation}
+K[\mu](\bx) = \int_{0}^{L} \bK(x,y) \bmu(y) dy \, .
+\end{equation}
+
+Suppose that $[0,L]$ is discretized using $N$ discretization
+nodes $x_{j}^{N}$, $j=1,2,\ldots N$, along with an
+the quadrature rule, $Q_{N}(x,x_{j,N})$, $j=1,2,\ldots N$, $x\in[0,L]$.
+Let $K^{N}$ be the finite dimensional approximations of $K$ 
+given by:
+\begin{equation}
+K^{N}[\phi](\bx) = \sum_{j=1}^{N} Q^{N}(x,x^{N}_{j})  
+\bK(x,x_{j}^{N}) \phi(x,x_{j}^{N}) \, .
+\end{equation}
+We will refer to $K^{N}$ is the Nystr\"{o}m approximation of $K$ 
+with quadrature rule $Q^{N}$
+
+\begin{definition}
+The Nystr\"{o}m approximation of $K$ with quadrature rule $Q^{N}$ 
+is considered to be $p$th order accurate 
+if there exists a $C$ independent of $N$
+such that for all $\bmu \in C^{p}$, 
+\begin{equation}
+\lim_{N\to \infty} |(K^{N} - K)\bmu| \leq C_{\bmu} N^{-p} \, .
+\end{equation}
+\end{definition}
+
+\begin{remark}
+There are many sufficient conditions on
+the choice of $x_{j,N}, Q_{N}(x,x_{j,N})$ $j=1,2\ldots,N$, $N \in \mathbb{N}$
+for which the corresponding Nystr\"{o}m discretizations are $p$th order accurate.
+A few such sets of sufficient conditions are discussed in~\cite{kress1989linear}.
+While only the Kress quadrature~\cite{kress1991boundary} have been proven to be 
+spectrally 
+accurate, i.e.
+\begin{equation}
+\lim_{N\to\infty} |(K^{N}-K)\bmu| \leq C_{\bmu} e^{-\alpha N} \quad \text{for some} \, \alpha>0 \, ,
+\end{equation}
+several standard quadrature methods such as 
+Alpert quadrature~\cite{alpert1999}, quadrature by expansion~\cite{qbxquadrature}, 
+generalized Gaussian quadratures~\cite{bremer2010}
+to name a few demonstrate $p$th order convergence numerically. 
+See~\cite{hao2014high} for a detailed discussion. 
+\end{remark}
+
+Let $\tilde{K}^{N}$ denote the matrix  
+corresponding to $K^{N}$, which is given by
+\begin{equation}
+\tilde{K}^{N}_{i,j} = Q^{N}(x_{i}^{N}, x_{j}^{N}) \bK(x_{i}^{N}, x_{j}^{N})
+\quad i,j=1,2\ldots N \, .
+\end{equation}
+
+\begin{remark}
+When solving the second kind integral equation~\cref{inteqfreddet} using the Nystr\"{o}m 
+method, one solves the linear system $(I + \tilde{K}^{N})\tilde{\bmu} = \ff(x_{j}^{N})$,
+for the unknown density $\tilde{\bmu} = \{ \bmu_{j} \}_{j=1}^{N}$ 
+and then using the natural interpolation
+\begin{equation}
+\bmu(x) = \ff(x) - \sum_{j=1}^{N} Q^{N}(x,x_{j}^{N}) \bK(x,x_{j}^{N}) \bmu_{j}^{N} \, .
+\end{equation}
+\end{remark}
+
+%The standard Nystr\"{o}m procedure is to solve the integral equation
+%\begin{equation}
+%\bmu_{i,N} + \sum_{j=1}^{N} Q_N(x_{i,N},x_{j,N} \bK(x_{i,N},x_{j,N})
+%\bmu_{j,N} = \ff(\bx_{i,N}) \, ,
+%\end{equation}
+%for the unknowns $\bmu_{i,N}$, along with the natural interpolant
+%\begin{equation}
+%\bmu(\bx) = \ff(\bx) - \sum_{j=1}^{N} Q_N(x,x_{j,N}) \mu_{j,N} \, .
+%\end{equation}
+
+%\begin{equation}
+%\end{equation}
+%Suppose that the quadrature rule $Q_{N}$ satisfies
+%the following two additional constraints:
+%a) 
+%\begin{equation}
+%\sum_{j=1}^{N} |Q_{N}(x,x_{j,N})| \leq C \, ,
+%\end{equation}
+%where $C$ is a constant independent of $x$ and $N$, and b) that
+%\begin{equation}
+%\lim_{x\to y} \sup_{n \in \mathbb{N}} \sum_{j=1}^{N} 
+%|Q_{N}(x,x_{j,N}) - Q_{N}(y,x_{j,N})| \to 0 \, .
+%\end{equation}
+
+%Suppose that the domain $[0,L]$, is partitioned into $N$ 
+%panels of equal length, where each panel is discretized 
+%using order $p$ discretization nodes (e.g.
+%Let $\cL = -2\cD_{k} - 2\cW$, and let $\cJ_{1}(X)$ denote the 
+%space of trace class operators on the Hilbert Space $X$.
+%Suppose the boundary $\Gamma$ is parametrized into $N$ panels
+%of equal length.
+
+The following theorem is the main result of the section
+and shows that the determinant of the
+linear system corresponding to the Nystr\"{o}m 
+discretization of $\cI - 2\cD_{k} - 2\cW$ 
+converges to $0$ precisely at the eigenvalues of the Dirichlet
+problem for Stokes equation on
+with error proportional to the quadrature 
+method used in the Nystr\"{o}m discretization.
+
+\begin{thrm}
+\label{thm:mainconvfreddet}
+Suppose that $\Omega$ is a simply connected domain with an analytic boundary 
+$\Gamma$. 
+Suppose the Nystr\"{o}m method with quadrautre rule $Q^{N}$ 
+is $p$th order accurate. 
+Let $\tilde{L}^{N}_{k}$ denote the finite dimensional linear system corresponding
+to $-2\cD_{k} -2\cW$.
+Let $f(k) = \text{det}(I + \tilde{L}^{N}_{k})$. 
+Then $f:[0,R] \to \mathbb{C}$  is an analytic function of $k$ 
+for any $R<\infty$. 
+Suppose further that $\tilde{k}$ is an Dirichlet eigenvalue for the Stokes 
+equation on $\Omega$, then
+\begin{equation}
+f(\tilde{k}) \leq C N^{-p} \, . 
+\end{equation}
+\end{thrm}
+\begin{proof}
+The proof is rather tedious and technical and
+follows essentially from combining the theorem 4.3 in~\cite{zhao2015robust}, 
+and theorem 8.1 in~\cite{bornemann2010numerical}.
+\end{proof}
+The theorem above relies on the observation that
+the determinant of a Nystr\"{o}m discretized linear system
+is a good approximation of the Fredholm determinant of trace-class
+operators, and is an especially good approximation
+when the Fredholm determinant is $0$.
+
+\begin{remark}
+The same analysis does not carry through for the operator
+$\cI - 2 \cD_{k} - 2i\eta \cS_{k} - 2\cW$, 
+since it is not a trace class operator.
+For brevity, let $\cM_{k} = -2\cD_{k} - 2i\eta \cS_{k} - 2\cW$.
+The operator $\cM$ is in $\cJ_{2}(\bL^{2}(\Gamma))$ where
+$\cJ_{2}(\bL^{2}(\Gamma))$ is the space of Hilbert-Schmidt operators
+on $\bL^{2}(\Gamma)$ (the singular values of the operator are square
+summable, as opposed to being summable).
+Thus the Fredholm determinant of $\cI + \cM$
+is not necessarily convergent. 
+However, as noted in~\cite{zhao2015robust}, the convergence
+result~\cref{thm:mainconvfreddet}
+should be true up to a logarithmic factor in the rate
+of convergence, since the singular values of the operator
+$\cM_{k}$ decay like $\frac{1}{n}$, and the
+Fredholm determinant divergers logarithmically. 
+Let $M_{N,k}$ denote the Nystr\"{o}m discretized operator 
+corresponding to $M$, where $N$ is the number of discretization points
+on the boundary $\Gamma$.
+One way of proving such a result would be to construct a definition 
+of a determinant for Hilbert-Schmidt operators defined by 
+Hilbert~\cite{hilbertbook} and Carleman~\cite{carlemanbook}
+as opposed to the Fredholm determinant
+and prove analogous results for this case.
+Instead, in~\cref{subsec:convannulus}, we demonstrate that
+that $\text{det} (I - M^{N,k}) \to 0$ as $N \to \infty$ if and only 
+if $k$ is a Dirichlet eigenvalue for the Stokes operator, and that
+the convergence to $0$ is exponential at the eigenvalues even in 
+this case.
+\end{remark}

### 2019-03-12 doc/draft-01-stokes/03analysis2.tex
Second pass at section 3.6

--- 2019-03-08 doc/draft-01-stokes/03analysis.tex
@@
 \subsection{Computational Fredholm determinants}
+Having established the equivalence between the Dirichlet eigenvalues
+for Stokes equation and the invertibility of
+the operator $\cI - 2\cD_{k} - 2\cW$ on simply connected domains, we show how 
+the Fredholm determinant can be as a computational tool for detecting
+the non-invertibility of $\cI - 2\cD_{k} - 2\cW$.
+
+Let $\cJ_{1}(X)$ denote the space of trace class operators 
+on $X$, where $X$ is a Hilbert space.
+$\cJ_{1}$ is a subspace of compact operators on $X$.
+Suppose that $A$ is a compact operator, with eigenvalues
+$\lambda_{i}, i=1,2,\ldots$.
+Then the operator $A \in \cJ_{1}(X)$ if
+$\sum_{i} |\lambda_{i}| < \infty$.
+If $A$, is a trace class operator, then we can define 
+the Fredholm determinant of the operator $\cI + A$ as
+\begin{equation}
+\text{det}(\cI +A) = \prod_{i=1}^{\infty} (1+\lambda_{i}) \, .
+\end{equation}
+It follows from standard results in complex analysis, 
+that the Fredholm determinant is well-defined if 
+$\text{det}(\cI+A) < \infty$ if $\sum_{i} |\lambda_{i}| < \infty$,
+i.e. if $A$ is in trace class.
+
+The following lemma shows that the operator 
+$-2\cD_{k} - 2\cW$ is a trace class operator.
+\begin{lemma} 
+$-2\cD_{k} - 2\cW$ is a trace class operator for all $k$ 
+\end{lemma}
+The Fredholm determinant of a second-kind Fredholm operator
+is another way of detecting when the operator is not invertible. 
+The following result summarizes the result. 
+\begin{lemma}
+If $A$ is a trace-class operator, then
+\end{lemma}

### 2019-03-12 doc/draft-01-stokes/03analysis2.tex
updating fredholm determinant section

@@
 
-\subsection{Computational Fredholm determinants}
+\subsection{Fredholm determinants}
 Having established the equivalence between the Dirichlet eigenvalues
 for Stokes equation and the invertibility of
-the operator $\cI - 2\cD_{k} - 2\cW$ on simply connected domains, we show how 
-the Fredholm determinant can be as a computational tool for detecting
+the operator $\cI - 2\cD_{k} - 2\cW$ on simply connected domains, in this section
+we show how the Fredholm determinant can be as a computational tool for detecting
 the non-invertibility of $\cI - 2\cD_{k} - 2\cW$.
@@
 \end{lemma}
+\begom{proof}
+Using Bessel function asymptotics, we note that the
+kernel of $\cD_{k}$ given by
+$\TT_{\cdot,\cdot,\ell}\nu_{\ell}(\bx,\by)$
+has a leading order singularity of $|\bx-\by|^2 \log{|\bx-\by|^2}$ as $\bx\to \by$.
+It follows from~\cite{bornemann2010} numerical that $\cD_{k}$
+is a trace-class operator for all $k$.
+Since $\cW$ is a rank-one perturbation independent of $k$, and trace-class
+operators are a vector space, we conclude that
+$-2\cD_{k} - 2\cW$ is also a trace-class operator for all $k$.
+\end{proof}
+
+Let $f(k) = \text{det}(\cI - 2\cD_{k} - 2\cW)$.
+We first note that $f(k)$ is an analytic function of $k$
+for $k \in \mathbb{C} \setminus 0$
+since the kernel of $\cD_{k}$ is an 
+analytic function of $k$ on that domain, 
+and the Fredholm determinant is an analytic operator.
+
 The Fredholm determinant of a second-kind Fredholm operator
@@
 \begin{lemma}
-If $A$ is a trace-class operator, then
+$f(k) = 0$ if and only if $\cI - 2\cD_{k} -2\cW$ 
+is not invertible.
 \end{lemma}
+When $\Omega$ is simply connected, the above lemma combined 
+with~\cref{thm:dlmain} implies $f(k) = 0$ if and only if $k$ 
+is a Dirichlet eigenvalue for Stokes equation.

### 2019-03-12 doc/draft-01-stokes/03analysis2.tex
updating fredholm determinant section

@@
 is a Dirichlet eigenvalue for Stokes equation.
+
+We now show how this fact can be used numerically
+to estimate the Dirichlet eigenvalues.
+Suppose that $M_{k}^{N}$ is a Nystr\"{o}m discretization 
+of the operator $-2\cD_{k} - 2\cW$ when the boundary 
+$\Gamma$ is discretized with $N$ points. 
+Let $f^{N}(k) = \text{det}(I + M_{k}^{N})$
+where here $\text{det}$ is the standard matrix determinant.
+Note that the discretized matrix also depends on the choice
+of quadrature rule used in the Nystr\"{o}m discretization
+of the operator.
+In~\cite{zhao2015robust}, the authors prove that
+for computing the Laplace eigenvalues on regions with 
+analytic boundaries, when the integral
+operators are discretized using Kress-quadratures,
+the determinant of the Nystr\"{o}m discretized operators
+at the true eigenvalues converge to $0$ exponentially in $N$.
+This combined with the analyticity of $f^{N}(k)$ as a function
+of $k$ for fixed $N$ proves that

### 2019-03-12 doc/draft-01-stokes/03analysis2.tex
Updating fredholm determinant section

@@
 which are almost multiply connected. 
-This issues is discussed in detail
+This issue is discussed in detail
 in example~\cref{sec:numanalysis-nearly-mult-con}.
@@
 \end{lemma}
-\begom{proof}
+\begin{proof}
 Using Bessel function asymptotics, we note that the
@@
 of the operator.
+
 In~\cite{zhao2015robust}, the authors prove that
@@
 at the true eigenvalues converge to $0$ exponentially in $N$.
-This combined with the analyticity of $f^{N}(k)$ as a function
-of $k$ for fixed $N$ proves that
+Thus, is the eigenvalues have multiplicity $1$, i.e. the
+derivative of the determinant is non-zero at the true-eigenvalues,
+then the analyticity of the discretized determinant implies
+that the zeros of the determinant of the Nystr\"{o}m 
+discretization of the linear operator converges
+exponentially to the true Dirichlet eigenvalues for Laplace's equation.
+
+The proof presented in~\cite{zhao2015robust} carries forward
+for computing the Dirichlet eigenvalues of Stokes equation as well.
+We summarize the result in the following theorem.
+\begin{thrm}
+Suppose that $\Omega$ is a simply connected domain with an analytic boundary.
+Let $k_{j}$, $j=1,2,\ldots M$ denote all the Dirichlet eigenvalues of Stokes
+equation on $\Omega$ contained in the interval $[a,b]$. 
+Suppose further that all the eigenvalues have multiplicity $1$.
+Let $f^{N}(k) = \text{det}(I+M^{N}_{k})$, where $M^{N}_{k}$ 
+is the Nystr\"{o}m discretzation of $-2\cD_{k} - 2\cW$ with Kress
+quadratures.
+Then $f^{N}(k)$ has exactly $M$ zeros on the interval $[a,b]$. 
+Let $\omega_{j}$, $j=1,2\ldots M$ denote the zeros of $f^{N}$.
+Furthermore, there exist constants $a>0$ and $C$, 
+such that $\sup_{j=1}^{M} |\omega_{j} - k_{j}| < C e^{-aN}$.
+\end{thrm}
+
+\begin{proof}
+The proof follows from small modificiations of the proofs contained in~\cite{zhao2015robust}. 
+\end{proof}

### 2019-03-13 matlab/src/chunkerint.m
updates for plotting and such

@@ -28,6 +28,7 @@ if ~isfield(opts,'quadgkparams'); opts.quadgkparams = {}; end
 
 k = chunker.k;
 nch = chunker.nch;
+hs =chunker.hs;
 
 iffun = false;
 if isa(f,'function_handle')

### 2019-03-13 matlab/src/ostokes_determinant.m

@@ -129,6 +129,8 @@ if opts.FLAM == 1
     cfprintf('time %5.2e\n',t5)
 
     cfprintf('total time %6.3e\n',t3+t4+t5)
+    
+    varargout{1} = F_wpre;
 
 
 else
@@ -145,6 +147,7 @@ else
 
     cfprintf('total time %6.3e\n',t1+t2)
     
+    varargout{1} = sysmat2;
 end
 
 

### 2019-03-13 matlab/src/ostokesvortkern.m

@@ -14,8 +14,8 @@ srcnymat = repmat(srcn(2,:),nt,1);
 srctxmat = repmat(srct(1,:),nt,1);
 srctymat = repmat(srct(2,:),nt,1);
 
-g2 = g(:,:,2); g2 = g2(:); g1 = g(:,:,1); g1 = g1(:);
-spart = [g2.'; -g1.'];
+g2 = g(:,:,2); g1 = g(:,:,1);
+spart = [g2; -g1];
 
 spart = reshape(spart,nt,2*ns);
 

### 2019-03-13 matlab/test/test_helmfun.m

@@ -5,6 +5,7 @@
 
 
 zk = randn() + 1i*randn();
+zk = real(zk)
 start_eps = 1.0;
 src = randn(2,1); trg = randn(2,1); mu = randn(2,1); 
 srcn = randn(2,1); srcn = srcn/(norm(srcn));

### 2019-03-13 matlab/test/testsubmateval.m

@@ -1,8 +1,9 @@
 %TESTSUBMATEVAL
 
+addpath('../../mwrap')
 
-ns = 560;
-nt = 560;
+ns = 5600;
+nt = 5600;
 
 src = randn(2,ns);
 targ = randn(2,nt);

### 2019-03-13 src/chunks_helmstokes_kerndefs.f90

@@ -575,12 +575,14 @@ subroutine zhelmstokesallmatmany(zk,ns,src,nt,targ,nu,cs,cd, &
   ! local
   integer :: i, j
 
+  !$OMP PARALLEL DO DEFAULT(SHARED) PRIVATE(i,j)
   do j = 1,ns
      do i = 1,nt
         call zhelmstokesallmat(zk,src(1,j),targ(1,i),nu(1,j),cs,cd, &
              mat(1,1,i,j))
      enddo
   enddo
+  !$OMP END PARALLEL DO
 
   return
 end subroutine zhelmstokesallmatmany

### 2019-03-13 doc/draft-01-stokes/03analysis2.tex

@@
 \end{proof}
+
+In practice, using the Kress-quadrature for large problems is problematic owing to the global
+nature of the quadrature rule. 
+The coupling with fast direct solvers for computing determinants also results in $O(N^2 \log{N})$ 
+determinant evaluation since evaluating each matrix entry costs $O(N)$, where 
+$N$ is the number of discretization points on the boundary.
+Over the last two decades, many high-order quadrature methods which are compatible with
+fast algorithms like the fast multipole method (and fast direct solvers as well, 
+since each matrix entry requires O(1) work) have been developed for solving
+integral equations.
+Extensive numerical evidence suggests that the zeros of the 
+determinants of linear systems discretized using 
+these quadrature methods are also high order approximations of Dirichlet eigenvalues
+for the Stokes PDE--- the error is observed to be proportional to the quadrature error
+for the eigenfunction $\bt^{-}$ associated with the eigenvalue.
+We leave a proof of this to future work.

### 2019-03-13 doc/draft-01-stokes/03analysis2.tex
updating section 3.6

@@
 analytic boundaries, when the integral
-operators are discretized using Kress-quadratures,
+operators are discretized using Kress-quadratures~\cite{kress1991boundary},
 the determinant of the Nystr\"{o}m discretized operators
@@
 \begin{thrm}
+\label{thm:mainconvfreddet}
 Suppose that $\Omega$ is a simply connected domain with an analytic boundary.
@@
 We leave a proof of this to future work.
+
+\begin{remark}
+The same analysis does not carry through for the operator
+$\cI - 2 \cD_{k} - 2i\eta \cS_{k} - 2\cW$, 
+since $\cS_{k}$ is not a trace class operator.
+For brevity, let $\cM_{k} = -2\cD_{k} - 2i\eta \cS_{k} - 2\cW$.
+The operator $\cM_{k}$ is 
+in $\cJ_{2}(\bL^{2}(\Gamma))$ where
+$\cJ_{2}(\bL^{2}(\Gamma))$ is the space of Hilbert-Schmidt operators
+on $\bL^{2}(\Gamma)$ (the singular values of the operator are square
+summable, as opposed to being summable).
+Thus the Fredholm determinant of $\cI + \cM_{k}$
+is not necessarily convergent. 
+However, as noted in~\cite{zhao2015robust}, the convergence
+result~\cref{thm:mainconvfreddet}
+should be true up to a logarithmic factor in the rate
+of convergence, since the singular values of the operator
+$\cM_{k}$ decay like $\frac{1}{n}$, and the
+Fredholm determinant divergers logarithmically. 
+Instead, in~\cref{subsec:convannulus}, we demonstrate that this fact
+numerically on the annulus, where the eigenvalues are analytically known. 
+\end{remark}

### 2019-03-15 doc/draft-01-stokes/01intro.tex
add sketch of representation proof
Updating section 1,2

@@
 The planar incompressible Stokes equations describe
-creeping flow in two dimensions. Let $\Omega \subset \R^2$
-be a domain with $C^2$ boundary. The eigenvalue problem seeks
+creeping flows in two dimensions. Let $\Omega \subset \R^2$
+be a bounded domain with $C^2$ boundary. The eigenvalue problem seeks
 values $k^2$ such that
 
-\begin{align}
+\begin{equation}
+\begin{aligned}
   -\Delta \uu + \nabla p &= k^2 \uu \quad \textrm{in} \quad
   \Omega \label{eq:ostokes} \; , \\
-  \nabla \cdot \uu &= 0 \; , \label{eq:ostokescty}
-\end{align}
-subject to certain boundary conditions, has a non-trivial solution.
-Let $\bsigma(\uu,p)$ denote the Cauchy stress tensor
-associated with the flow (defined below) and let $\bnu$ denote
-the outward normal along the boundary.
-In this work, we consider both the Dirichlet boundary condition,
+  \nabla \cdot \uu &= 0 \; ,
+\end{aligned}
+\end{equation}
+subject to boundary conditions, has a non-trivial solution $(\uu,p)$.
+In this work, we consider the eigenvalue problem subject to 
+the Dirichlet boundary condition,
 \begin{equation}
-  \uu = \bz \quad \textrm{on} \quad \Gamma \label{eq:ostokes_dir} \; ,
-\end{equation}
-and the Neumann boundary condition,
-\begin{equation}
-  \bsigma( \uu, p ) \cdot \bnu  = \bz \; . \label{eq:ostokes_neu}
+  \uu = \bz \quad \textrm{on} \quad \Gamma \label{eq:ostokes_dir} \; .
 \end{equation}

### 2019-03-15 doc/draft-01-stokes/02prelim.tex
updating section 3.6
Updating section 1,2

@@
 ``free-space'' Green's functions, i.e. fundamental solutions which satisfy
-some natural growth or decay conditions as $|\xx-\yy| \to \infty$.
+radiation conditions as $|\xx-\yy| \to \infty$.
 The Green's function of the oscillatory biharmonic equation,
@@
 
-In the case that $k=i\alpha$ for some real-valued $\alpha$,
+Recall that, in the case that $k=i\alpha$ for some real-valued $\alpha$,
 the oscillatory Stokes equations \cref{eq:ostokes}
@@
 In this section, we review the derivation of the
-modified Stokeslet, but for the imaginary parameter
-regime, which is the appropriate setting for the Stokes
+oscillatory Stokeslet, which is the appropriate setting for the Stokes
 eigenvalue problem.
-The original modified Stokeslet is more well known,
-and is of particular interest for its application to
-numerical simulations of the unsteady Stokes equations
-\cite{pozrikidis1992boundary,biros2002embedded}.
-
  Consider the solution of
@@
 \end{equation}
-is then the equivalent of a Stokeslet
-\cite{pozrikidis1992boundary} for the problem
+is then the analog of a Stokeslet
+\cite{Pozrikidis1992} for the problem
 \eqref{eq:ostokes}.
@@
 Then the corresponding stress tensor is given by
-$\sigma_{ik} = T_{ijk} f_j$.
+$\sigma_{i\ell} = T_{ij\ell} f_j$.
 
-For the layer potentials of the next section, the following
-formulas are useful. Let $\bnu$ be a given vector. When
-summing over the third index, we obtain
-
-\begin{equation}
-  \TT_{\cdot,\cdot,\ell} \nu_\ell = -\bnu \otimes \nabla \Glap
-  + \partial_\nu \left ( -\Delta \Gbh \II
-  + \nabla \otimes \nabla \Gbh \right)
-  + \nabla \otimes \left ( -\Delta \Gbh \bnu
-  + \partial_{\nu} \nabla \Gbh \right) \; . \nonumber
-\end{equation}
-Let $\btau = \bnu^\bot$. Then
-
-\begin{equation}
-  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla \Glap
-  - \nabla^\bot \otimes \nabla^\bot \partial_\nu \Gbh
-  +\nabla \otimes \nabla^\bot \partial_\tau \Gbh \; .
-  \nonumber
-\end{equation}
+%For the layer potentials of the next section, the following
+%formulas are useful. Let $\bnu$ be a given vector. When
+%summing over the third index, we obtain
+%
+%\begin{equation}
+%  \TT_{\cdot,\cdot,\ell} \nu_\ell = -\bnu \otimes \nabla \Glap
+%  + \partial_\nu \left ( -\Delta \Gbh \II
+%  + \nabla \otimes \nabla \Gbh \right)
+%  + \nabla \otimes \left ( -\Delta \Gbh \bnu
+%  + \partial_{\nu} \nabla \Gbh \right) \; . \nonumber
+%\end{equation}
+%Let $\btau = \bnu^\bot$. Then
+%
+%\begin{equation}
+%  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla \Glap
+%  - \nabla^\bot \otimes \nabla^\bot \partial_\nu \Gbh
+%  +\nabla \otimes \nabla^\bot \partial_\tau \Gbh \; .
+%  \nonumber
+%\end{equation}
 
@@
 
-We now use the Stokeslet and stresslet definitions
-of the previous section to define the standard single
-and double layer potentials of the Stokes eigenvalue
-problem. For $\xx \in \R^2$, the single layer potential
+We now use the Stokeslet and stresslet 
+to define the single
+and double layer potentials for the oscillatory Stokes problem.
+For $\xx \in \R^2$, the single layer potential with density $\bmu$
 is defined to be
@@
 For $\xx \in \R^2 \setminus \Gamma$, the double layer
-potential is defined to be
+potential with density $\bmu$ is defined to be
 
@@
 where $\bnu$ denotes the outward unit normal to the boundary.
-Note that when $\xx \in \Gamma$ we obtain the same formula
-for the double layer potential except that the integral should be
-interpreted in the principal value sense. 
 If we write $\bmu = \bnu \mu_\nu + \btau \mu_\tau$,
@@
 
-When we view the layer potentials as
-operators which map densities on the boundary to functions
-on the boundary, we use special notation. Let
+Let $\cS[\bmu]: C(\Gamma) \to C(\Gamma)$, and
+$\cD[\bmu]: C(\Gamma) \to C(\Gamma)$ 
+denote the restrictions of the layer potentials 
+$\bS[\bmu]$ and $\bD[\bmu]$ on the boundary $\Gamma$, i.e.
+for $\bx \in \Gamma$,
 
@@
 \begin{equation}
-  \cD [\bmu] (\xx) = \oint_\Gamma \left ( \TT_{\cdot,\cdot,\ell}\nu_\ell(\yy)
+\label{eq:dlformula}
+  \cD [\bmu] (\xx) = \oint_\Gamma \left ( \TT_{\cdot,\cdot,\ell}(\bx,\by)
+  \nu_\ell(\yy)
   \right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
@@
 where the $\oint$ symbol means that the integral is to be
-evaluated in the principal value sense. For two vector valued
+evaluated in the principal value sense. 
+For two vector valued
 functions $\ff$ and $\bg$ defined on $\Gamma$, consider the bilinear
@@
 \begin{equation}
-  \cD^{\intercal} [\bmu] = \oint_\Gamma \left ( \TT_{\cdot,\cdot,\ell}\nu_\ell(\xx)
+  \cD^{\intercal} [\bmu](\bx) = 
+  \oint_\Gamma \left ( \TT_{\cdot,\cdot,\ell}(\bx,\by)\nu_\ell(\xx)
   \right ) \bmu(\yy) \, dS(\yy) \; .
@@
 
+\begin{remark}
+The operators $\bS,\bD,\cD$ and $\cD^{\intercal}$
+depend on the Helmholtz parameter $k$ of the oscillatory Stokes equation.
+In places where it is essential to highlight this dependence, in a slight
+abuse of notation, we will use the symbols $\bS_{k}, \bD_{k},\cD_{k}$ and $\cDt_{k}$ to 
+denote this dependence.
+\end{remark}
+
+In the following lemma, we review the limiting values of layer 
+potentials $\bS$ and $\bD$ on the boundary $\Gamma$.
+
+\begin{lem}[Jump conditions] \label{lem:jump-conds}
+  Suppose that $\Omega$ is a bounded region with a $C^{2}$ boundary
+  $\Gamma$.
+  Let $\bnu(\bx)$ denote the outward pointing normal at $\bx \in \Gamma$.
+  Suppose that $\bmu \in C(\Gamma)$.
+  Then $\bS[\bmu]$
+  is continuous across $\Gamma$, and the exterior and interior
+  limits of the surface traction of $\bD[\bmu]$ are equal.
+  Furthermore, for $\bx_{0} \in \Gamma$,
+
+  \begin{align}
+    \lim_{h \downarrow 0} \bsigma_\bS[\bmu](\xx_0 \pm h\bnu(\xx_0)) \cdot \bnu(\xx_0)
+    &= \mp \frac{1}{2} \bmu(\xx_0) + \cDt[\bmu](\xx_0) \\
+    \lim_{h \downarrow 0} \bD[\bmu](\xx_0 \pm h\bnu(\xx_0)) 
+    &= \pm \frac{1}{2} \bmu(\xx_0) + \cD[\bmu](\xx_0)    \; .
+  \end{align}
+\end{lem}
+
+The above expressions are derived by noting that the
+leading order singularity of these integral kernels
+is the same as for the original Stokes case, so that
+the standard jump conditions for Stokes
+\cite{KimSangtae1991,Pozrikidis1992}
+apply.
+
 \subsubsection{Representation Theorem}
 
-Here we sketch the proof of the equivalent of the
+In the following theorem, we sketch the proof of the equivalent of the
 Green's identity for oscillatory Stokes, which is well-known
@@
   From the divergence theorem and the divergence-free properties of
-  $\uu$ and $\GG$, we can obtain
+  $\uu$ and $\GG$, we then get
 
@@
 that for the Helmholtz case; see \cite[Theorem 3.5]{colton1983integral}.
-
-\subsubsection{Jump conditions for the layer potentials}
-
-In formulating an integral equation, it is important
-to understand the behavior of the layer potentials
-for points near and on the boundary. The so-called jump
-conditions for the layer potentials are summarized in the
-following theorem.
-
-\begin{lem}[Jump conditions] \label{lem:jump-conds}
-  Let $\bS$, $\bsigma_\bS$, $\bD$, $\cD$, and $\cDt$ be
-  the layer potentials and operators defined above and
-  let $\Gamma$ be a sufficiently smooth domain boundary
-  with outward pointing normal $\bnu$. Then, for
-  a given density $\bmu$ defined on $\Gamma$,
-  we have that $\bS \bmu$
-  is continuous across $\Gamma$, the exterior and interior
-  limits of the surface traction of $\bD \bmu$ are equal,
-  and for each $\xx_0 \in \Gamma$,
-
-  \begin{align}
-    \lim_{h \downarrow 0} \bsigma_\bS[\bmu](\xx_0 \pm h\bnu(\xx_0)) \cdot \bnu(\xx_0)
-    &= \mp \frac{1}{2} \bmu(\xx_0) + \cDt[\bmu](\xx_0) \\
-    \lim_{h \downarrow 0} \bD[\bmu](\xx_0 \pm h\bnu(\xx_0)) 
-    &= \pm \frac{1}{2} \bmu(\xx_0) + \cD[\bmu](\xx_0)    \; .
-  \end{align}
-\end{lem}
-
-The above expressions are derived by noting that the
-leading order singularity of these integral kernels
-is the same as for the original Stokes case, so that
-the standard jump conditions for Stokes
-\cite{KimSangtae1991M:pa,Pozrikidis1992}
-apply.
 
@@
 \begin{remark}
-The operators $\bS,\bD,\cD$ and $\cD^{\intercal}$
-depend on the Helmholtz parameter $k$ of the oscillatory Stokes equation.
-In places where it is essential to highlight this dependence, in a slight
-abuse of notation, we will use the symbols $\bS_{k}, \bD_{k},\cD_{k}$ and $\cDt_{k}$ to 
-denote this dependence.
-Similarly, all the above operators and $\cW$ also depend on the boundary of the
-region $\Gamma$. In place where it is necessary to highlight this dependence
+The operators $\bS,\bD, \cS, \cD$, and $\cW$  depend on the boundary 
+of the region $\Gamma$. In places where it is necessary to highlight this dependence
 we will use $A^{\Gamma}$ instead of the operator $A$.

### 2019-03-15 doc/draft-01-stokes/03analysis2.tex
Updating section 3

@@
 
-In this section, we discuss how integral equations.
+In this section, we discuss how integral equations
 can be used to compute to the Stokes eigenvalues.
@@
 We closely follow the approach developed by Zhao and Barnett
-for computing the Laplace eigenvalues.
+for computing the Laplace eigenvalues~\cite{zhao2015robust}.
 %
-Their work computes the Laplace eigenvalues using the following
+They compute the Laplace eigenvalues using the following
 steps: 1) represent the solution 
@@
 2) establish that the intergral equation is not invertible 
-exactly for the Dirichlet eigenvalues for Laplace's equation;
+only at the Dirichlet eigenvalues for Laplace's equation;
 3) prove that the zeros of the Fredholm determinant 
@@
 
-In this section, we adapt their approach for computing the 
+We adapt their approach for computing the 
 Dirichlet eigenvalues for Stokes equation. 
-%
-We first develop some uniqueness
-results for the osciallatory Stokes PDE which are essential
-for establishing step 2 of the Zhao-Barnett approach.
+In the context of oscialltory Stokes equation,
+while integral representations for the modified
+Stokes equation are directly applicable, 
+proving invertibility of the associated operators
+away from the eigenvalues is a more involved task.
+This in turn requires proving uniqueness results
+for various interior and exterior boundary value problems
+for the oscillatory Stokes equations.
+These results play a crucial role in estabilishing step
+2 of the Zhao-Barnett approach listed above.
 To the best of our knowledge, the uniqueness results, particularly
@@
 the standard layer potentials satisfy the radiation condition.
-%
-We then define well-posed versions of the
+and define well-posed versions of the
 exterior boundary value problems which incorporate the
@@
 Then we derive a number of uniqueness
-results for the boundary value problems.
+results for many standard boundary value problems.
 %
@@
 follows in a straightforward manner from the results 
-in Zhao and Barnett~\cite{zhao2015robust}. 
+in~\cite{zhao2015robust}. 
 We reproduce the relevant results from their work applied 
@@
 denoted by $\Gamma$.
-The standard Dirichlet boundary problem specifies the
+The Dirichlet boundary problem specifies the
 velocity of the fluid on the boundary, i.e.
@@
 Specifying the surface traction, $\bt = \bsigma \cdot \bnu$,
-on the boundary gives the standard Neumann boundary value
+on the boundary gives the Neumann boundary value
 problem, i.e.
@@
 
-\begin{proposition}
-The oscillatory Stokeslet, as in \eqref{eq:ostokeslet}, satisfies
-the radiation condition in Definition \ref{def:radcond}.
-Assuming that a density $\bmu$ is integrable and satisfies
-$\int_\Gamma \bmu\cdot \bnu dS = 0$, where $\bnu$ denotes the
-outward normal to the curve $\Gamma$, the oscillatory Stokes
-double layer potential $\bD\bmu$, as in \eqref{eq:doublelayer},
+\begin{thrm}
+The oscillatory Stokeslet, as defined in \eqref{eq:ostokeslet}, 
+satisfies the radiation condition in Definition \ref{def:radcond}.
+Suppose that $\Gamma$ is the boundary of a region $\Omega$
+and is $C^{2}$. 
+Suppose that $\bmu \in C(\Gamma)$ and satsifies
+$\int_{\Gamma} \bmu \cdot \bnu dS = 0$, where
+$\bnu$ dentoes the outward normal to the curve $\Gamma$.
+Then, the oscillatory Stokes 
+double layer potential $\bD[\bmu]$, as defined in \eqref{eq:doublelayer},
 also satisfies the radiation condition.
-\end{proposition}
+\end{thrm}
 
@@
 Consider the Stokeslet induced by an arbitrary charge
-$k^2 \bpsi$ at the origin. Let $r = |\xx|$,
+$k^2 \bpsi$ at the origin where $\psi \in \mathbb{C}^2$ 
+is a constant. Let $r = |\xx|$,
 $\bnu(\xx) = \xx/|\xx|$, and $\btau(\xx) = \bnu(\xx)^\perp$. We have
@@
     \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
-    \bu &= \ff \quad \bx \in \Gamma \, 
+    \bu &= \ff \quad \bx \in \Gamma \, , 
   \end{aligned}
@@
     \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
-    \bt &= \bg \quad \bx \in \Gamma \,
+    \bt &= \bg \quad \bx \in \Gamma \, ,
   \end{aligned}
@@
   Let $\Omega$ be a bounded domain and suppose that
-  $\Im (k) > 0$. Then both the interior
+  $\Im (k) \neq 0$. Then both the interior
   Dirichlet and Neumann boundary value problems have
@@
   Then, the right hand side of \cref{eq:greenlike} is
-  zero. Taking the real and imaginary parts of \cref{eq:greenlike},
-  it is clear that $\bu \equiv 0$.
+  zero. 
+  Taking the real and imaginary parts of \cref{eq:greenlike},
+  it is clear that $\bu \equiv 0$, if $\text{Im}(k) \neq 0$.
 \end{proof}
@@
 \begin{remark}
-Note that in Rellich's lemma $\bu$ need not be a radiating solution. 
+Note that in~\cref{lem:rellich}, $\bu$ need not be a radiating solution. 
 All that is assumed of $\bu$ is that it satifies the PDE in $E$.
@@
 \end{equation}
-Thus, the conditions for $\bu$ in Rellich's lemma (~\cref{lem:rellich})
+Thus, the conditions for $\bu$ in~\cref{lem:rellich}
 are satisfied, and each component of $\bu$ is a harmonic function
@@
 The proof of the exterior Neumann problem in the exterior of several
-obstacles is more involved and presented in the appendix~\cite{app:neuuniqueness}
+obstacles is more involved and presented in the 
+appendix~\cite{app:neuuniqueness}
 \end{remark}
@@
 \begin{equation}
-  \int_{\Gamma} |\bu|^{2} = 0 \implies \bu = 0  \quad \xx \in \Gamma \, ,
+  \int_{\Gamma} |\bu|^{2} = 0 \implies \bu = 0  \quad \xx \in \Gamma \, .
   \nonumber
 \end{equation}
-and the estimate
-\begin{equation}
-\lim_{r\to\infty} \int_{|\yy|=r} |\bu|^{2} dS \to 0 \, . \nonumber
-\end{equation}
-The last equation implies the conditions for~\cref{lem:rellich}
-are satisfied, from which we conclude that the components
-of $\bu$ are harmonic in $E$. 
-Thus, the components of $\bu$ satisfy
-\begin{equation}
-\Delta u_{j}=  0 \quad \xx \in E \quad \text{and} \quad
-u_{j} = 0 \quad \xx \in \Gamma \, , \nonumber
-\end{equation}
-for $j=1,2$.
-Then $\bu \equiv 0$ follows from the uniqueness of solutions to the 
-Dirichlet problem for Laplace's equation.
+The result then follows from the uniqueness of solutions to the exterior
+Dirichlet problem.
 \end{proof}
@@
 when the velocity is represented using a double layer potential,
-i.e. setting $u=\bD \bmu$, and when the velocity
+i.e. setting $\bu=\bD_{k} \bmu$, and when the velocity
 is represented using a mixed layer potential,
-i.e. setting $u=(i\eta \bS + \bD)\bmu$, where in both cases $\bmu$ 
+i.e. setting $\bu=(i\eta \bS_{k} + \bD_{k})\bmu$, where in both cases $\bmu$ 
 is the unknown density to be solved for. 
@@
 equation and the correspondance betweeen its null spaces and the eigenvalues
-of Stokes equation is analogous to a similar analysis carried out
+of Stokes equation is analogous to the analysis carried out
 for integral equations for Helmholtz equation and the eigenvalues
@@
 a double layer potential defined on $\Gamma$, i.e.
-setting $\bu = \bD \bmu$ for
+setting $\bu = \bD_{k} \bmu$ for
 an unknown density $\bmu$. 
@@
 result in rank-deficient representations for the boundary value problem.
-It is well-known that~\cref{eq:inteq_dir_int} has a two dimensional
+It is well-known that~\cref{eq:inteq_dir_int} has a one dimensional
 null-space due to this issue. Thus, proceeding as discussed earlier,
@@
 Note that $\bu$ is a radiating solution of the oscillatory
-Sotkes equation in the exterior $E$.
+Sotkes equation in the exterior $E$, since
+$\cW[\mu] = 0$ implies $\int_{\Gamma} \mu \cdot \bnu = 0$.
 From uniqueness of the Neumann problem in the exterior $E$, we conclude
@@
   \end{equation}
-Suppose thatw $k$ is Dirichlet eigenvalue for the Stokes equation on $\Omega$
+Suppose that $k$ is Dirichlet eigenvalue for the Stokes equation on $\Omega$
 and let $\bu$ denote the corresponding eigenfunction, and let $\bt^{-}$ denote
@@
 \end{equation}
-From the Fredholm alternative, it then follows that $(\cI - 2\cD)$ has a non-trivial 
+From the Fredholm alternative, it then follows that $(\cI - 2\cD_{k})$ has a non-trivial 
 null-space.
-However, we need to prove that $(\cI -2\cD - 2\cW)$ has a non-trivial null-space
+However, we need to prove that $(\cI -2\cD_{k} - 2\cW)$ has a non-trivial null-space
 for which we need the following two lemmas.
@@
 using Green's theorem, it follows that
-$\bS_{k}[\bt^{-}](\bx) = u(\bx) \neq 0$ for $\bx \in \Omega$ and
+$\bS_{k}[\bt^{-}](\bx) = \bu(\bx) \neq 0$ for $\bx \in \Omega$ and
 thus $\bt^{-}$ and $\bnu$ are linearly independent.
@@
 
-We now turn to the proof of the main result of the section.
-We know that $\bt^{-}, \bnu \in \cN(\cI - 2\cDt)$ are two linearly independent
+We now return to the proof of~\cref{thm:dlmain}. 
+We know that $\bt^{-}, \bnu \in \cN(\cI - 2\cDt_{k})$ are two linearly independent
 vectors in the null space.
@@
 which are almost multiply connected.
-This issue is discussed in detail
-in example~\cref{sec:numanalysis-nearly-mult-con}.
+We demonstrate this issue numerically in~\cref{sec:numanalysis-nearly-mult-con}.
 
@@
 i.e. setting
-$\bu = (\bD + i\eta \bS)
+$\bu = (\bD_{k} + i\eta \bS_{k})
 \bmu$, 
@@
 $\cI - 2\cD_{k} - 2i\eta \cS_{k} - 2\cW$ and the Dirichlet eigenvalues
-of the Stokes operator on $Omega$. 
-The following theorem proves this result.
-
-\begin{thm}
+of the Stokes operator on $\Omega$.
+
+\begin{thrm}
 Suppose $\Omega$ is a bounded region defined by the intersection of a 
@@
 for the Stokes operator on $\Omega$.
-\end{thm}
+\end{thrm}
 
@@
 \end{equation}
-Suppose now $\bu = -2\bD[\bmu] -2i\eta\bS[\bmu]$ in $\Omega$.
+Suppose now $\bu = -2\bD_{k}[\bmu] -2i\eta\bS_{k}[\bmu]$ in $\Omega$.
 Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
 and applying~\cref{lem:jump-conds}, we get that the interior
-limit of the velocity $\bu^{-} = (\cI - 2\cD -2ik\cS) \bmu = 0$ on $\Gamma$. 
+limit of the velocity $\bu^{-} = (\cI - 2\cD_{k} -2i\eta\cS_{k}) \bmu = 0$ on $\Gamma$. 
 Since $k$ is not a Dirichlet eigenvalue for the Stokes equation on 
@@
 To this end, note that $\bu$ is a radiating solution of the oscillatory
-Sotkes equation in the exterior $E$.
+Stokes equation in the exterior $E$,
+since $\cW[\bmu] = 0$ implies that $\int_{\Gamma} \bmu \cdot \bnu = 0$. 
 From uniqueness of the impedance problem in the exterior $E$, we conclude
@@
 \end{equation}
-This implies that $\bmu=0$ for $\xx \in \Gamma_{j}$, $j=1,2,\ldots m$. 
+Since $\text{Re}(\eta)>0$, this implies that $\bmu=0$ for $\xx \in \Gamma_{j}$, $j=1,2,\ldots m$. 
 Thus $\cI - 2\cD_{k} -2i\eta\cS_{k} -2\cW$ is invertible when $k$ 
@@
   \end{equation}
-Suppose thatw $k$ is Dirichlet eigenvalue for the Stokes equation on $\Omega$
+Suppose that $k$ is Dirichlet eigenvalue for the Stokes equation on $\Omega$
 and let $\bu$ denote the corresponding eigenfunction and let $\bt$ denote
@@
 Suppose that $A$ is a compact operator, with eigenvalues
-$\lambda_{i}, i=1,2,\ldots$.
+$\lambda_{i}, i\in \mathbb{N}$.
 Then the operator $A \in \cJ_{1}(X)$ if
 $\sum_{i} |\lambda_{i}| < \infty$.
-If $A$, is a trace class operator, then we can define 
-the Fredholm determinant of the operator $\cI + A$ as
+If $A$, is a trace class operator, then  
+the Fredholm determinant of the operator $\cI + A$ is defined as
 \begin{equation}
@@
 It follows from standard results in complex analysis, 
-that the Fredholm determinant is well-defined if 
+that the Fredholm determinant is finite and well-defined if 
 $\text{det}(\cI+A) < \infty$ if $\sum_{i} |\lambda_{i}| < \infty$,
@@
 has a leading order singularity of $|\bx-\by|^2 \log{|\bx-\by|^2}$ as $\bx\to \by$.
-It follows from~\cite{bornemann2010} numerical that $\cD_{k}$
+It follows from~\cite{bornemann2010numerical} numerical that $\cD_{k}$
 is a trace-class operator for all $k$.
@@
 \end{lemma}
+\begin{proof}
+The proof is standard and see for example~\cite{simon2005trace}, page 34.
+\end{proof}
+
 When $\Omega$ is simply connected, the above lemma combined 
@@
 analytic boundaries, when the integral
-operators are discretized using Kress-quadratures~\cite{kress1991boundary},
+operators are discretized using Kress-quadrature~\cite{kress1991boundary},
 the determinant of the Nystr\"{o}m discretized operators
 at the true eigenvalues converge to $0$ exponentially in $N$.
-Thus, is the eigenvalues have multiplicity $1$, i.e. the
+Thus, if the eigenvalues have multiplicity $1$, i.e. the
 derivative of the determinant is non-zero at the true-eigenvalues,
@@
 that the zeros of the determinant of the Nystr\"{o}m 
-discretization of the linear operator converges
+discretization of the linear operator converge
 exponentially to the true Dirichlet eigenvalues for Laplace's equation.
@@
 is the Nystr\"{o}m discretzation of $-2\cD_{k} - 2\cW$ with Kress
-quadratures.
+quadrature.
 Then $f^{N}(k)$ has exactly $M$ zeros on the interval $[a,b]$. 
@@
 
-In practice, using the Kress-quadrature for large problems is problematic owing to the global
+In practice, using Kress-quadrature for large problems is problematic owing to the global
 nature of the quadrature rule. 
@@
 Thus the Fredholm determinant of $\cI + \cM_{k}$
-is not necessarily convergent. 
+is not necessarily finite. 
 However, as noted in~\cite{zhao2015robust}, the convergence
@@
 Fredholm determinant divergers logarithmically. 
-Instead, in~\cref{subsec:convannulus}, we demonstrate that this fact
+In~\cref{subsec:convannulus}, we demonstrate that this fact
 numerically on the annulus, where the eigenvalues are analytically known. 

### 2019-03-18 doc/draft-01-stokes/03analysis.tex
update lemma and radiation condition
rename files

--- 2019-03-08 doc/draft-01-stokes/03analysis.tex
@@
 the pair $(\bu,p)$ is {\em radiating} if
-$p$ is bounded, $p \to 0$ as $r = |\xx| \to \infty$, and 
 \begin{equation}
@@
 
+\begin{cor}
+  If $(\bu,p)$ is a radiating solution of
+  the oscillatory Stokes equations, then
+  $p$ is bounded and $p\to 0$ as $r\to\infty$.
+\end{cor}
+
 In the next lemma, we prove the analogue of Rellich's lemma for the
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.3\linewidth]{media/multiply_final}
+\end{center}
+\caption{Example of a multiply connected domain with one obstacle.}
+\label{fig:1ply}
+\end{figure}
+
 \begin{proof}
@@
 which are almost multiply connected.
-This issues is discussed in detail
-in example~\cref{sec:numanalysis-nearly-mult-con}.
+We demonstrate this issue numerically in~\cref{sec:numanalysis-nearly-mult-con}.
 
@@
 it follows from the Fredholm alternative 
-that the operator $\cI - 2\cD(k) -2ik \cS - 2\cW$ is also not invertible.
-\end{proof}
-
-\subsection{Computational Fredholm determinants}
+that the operator $\cI - 2\cD(k) -2i\eta \cS - 2\cW$ is also not invertible.
+\end{proof}
+
+\subsection{Fredholm determinants}
+Having established the equivalence between the Dirichlet eigenvalues
+for Stokes equation and the invertibility of
+the operator $\cI - 2\cD_{k} - 2\cW$ on simply connected domains, in this section
+we show how the Fredholm determinant can be as a computational tool for detecting
+the non-invertibility of $\cI - 2\cD_{k} - 2\cW$.
+
+Let $\cJ_{1}(X)$ denote the space of trace class operators 
+on $X$, where $X$ is a Hilbert space.
+$\cJ_{1}$ is a subspace of compact operators on $X$.
+Suppose that $A$ is a compact operator, with eigenvalues
+$\lambda_{i}, i\in \mathbb{N}$.
+Then the operator $A \in \cJ_{1}(X)$ if
+$\sum_{i} |\lambda_{i}| < \infty$.
+If $A$, is a trace class operator, then  
+the Fredholm determinant of the operator $\cI + A$ is defined as
+\begin{equation}
+\text{det}(\cI +A) = \prod_{i=1}^{\infty} (1+\lambda_{i}) \, .
+\end{equation}
+It follows from standard results in complex analysis, 
+that the Fredholm determinant is finite and well-defined if 
+$\text{det}(\cI+A) < \infty$ if $\sum_{i} |\lambda_{i}| < \infty$,
+i.e. if $A$ is in trace class.
+
+The following lemma shows that the operator 
+$-2\cD_{k} - 2\cW$ is a trace class operator.
+\begin{lemma} 
+$-2\cD_{k} - 2\cW$ is a trace class operator for all $k$ 
+\end{lemma}
+\begin{proof}
+Using Bessel function asymptotics, we note that the
+kernel of $\cD_{k}$ given by
+$\TT_{\cdot,\cdot,\ell}\nu_{\ell}(\bx,\by)$
+has a leading order singularity of $|\bx-\by|^2 \log{|\bx-\by|^2}$ as $\bx\to \by$.
+It follows from~\cite{bornemann2010numerical} numerical that $\cD_{k}$
+is a trace-class operator for all $k$.
+Since $\cW$ is a rank-one perturbation independent of $k$, and trace-class
+operators are a vector space, we conclude that
+$-2\cD_{k} - 2\cW$ is also a trace-class operator for all $k$.
+\end{proof}
+
+Let $f(k) = \text{det}(\cI - 2\cD_{k} - 2\cW)$.
+We first note that $f(k)$ is an analytic function of $k$
+for $k \in \mathbb{C} \setminus 0$
+since the kernel of $\cD_{k}$ is an 
+analytic function of $k$ on that domain, 
+and the Fredholm determinant is an analytic operator.
+
+The Fredholm determinant of a second-kind Fredholm operator
+is another way of detecting when the operator is not invertible. 
+The following result summarizes the result. 
+\begin{lemma}
+$f(k) = 0$ if and only if $\cI - 2\cD_{k} -2\cW$ 
+is not invertible.
+\end{lemma}
+\begin{proof}
+The proof is standard and see for example~\cite{simon2005trace}, page 34.
+\end{proof}
+
+When $\Omega$ is simply connected, the above lemma combined 
+with~\cref{thm:dlmain} implies $f(k) = 0$ if and only if $k$ 
+is a Dirichlet eigenvalue for Stokes equation.
+
+We now show how this fact can be used numerically
+to estimate the Dirichlet eigenvalues.
+Suppose that $M_{k}^{N}$ is a Nystr\"{o}m discretization 
+of the operator $-2\cD_{k} - 2\cW$ when the boundary 
+$\Gamma$ is discretized with $N$ points. 
+Let $f^{N}(k) = \text{det}(I + M_{k}^{N})$
+where here $\text{det}$ is the standard matrix determinant.
+Note that the discretized matrix also depends on the choice
+of quadrature rule used in the Nystr\"{o}m discretization
+of the operator.
+
+In~\cite{zhao2015robust}, the authors prove that
+for computing the Laplace eigenvalues on regions with 
+analytic boundaries, when the integral
+operators are discretized using Kress-quadrature~\cite{kress1991boundary},
+the determinant of the Nystr\"{o}m discretized operators
+at the true eigenvalues converge to $0$ exponentially in $N$.
+Thus, if the eigenvalues have multiplicity $1$, i.e. the
+derivative of the determinant is non-zero at the true-eigenvalues,
+then the analyticity of the discretized determinant implies
+that the zeros of the determinant of the Nystr\"{o}m 
+discretization of the linear operator converge
+exponentially to the true Dirichlet eigenvalues for Laplace's equation.
+
+The proof presented in~\cite{zhao2015robust} carries forward
+for computing the Dirichlet eigenvalues of Stokes equation as well.
+We summarize the result in the following theorem.
+\begin{thrm}
+\label{thm:mainconvfreddet}
+Suppose that $\Omega$ is a simply connected domain with an analytic boundary.
+Let $k_{j}$, $j=1,2,\ldots M$ denote all the Dirichlet eigenvalues of Stokes
+equation on $\Omega$ contained in the interval $[a,b]$. 
+Suppose further that all the eigenvalues have multiplicity $1$.
+Let $f^{N}(k) = \text{det}(I+M^{N}_{k})$, where $M^{N}_{k}$ 
+is the Nystr\"{o}m discretzation of $-2\cD_{k} - 2\cW$ with Kress
+quadrature.
+Then $f^{N}(k)$ has exactly $M$ zeros on the interval $[a,b]$. 
+Let $\omega_{j}$, $j=1,2\ldots M$ denote the zeros of $f^{N}$.
+Furthermore, there exist constants $a>0$ and $C$, 
+such that $\sup_{j=1}^{M} |\omega_{j} - k_{j}| < C e^{-aN}$.
+\end{thrm}
+
+\begin{proof}
+The proof follows from small modificiations of the proofs contained in~\cite{zhao2015robust}. 
+\end{proof}
+
+In practice, using Kress-quadrature for large problems is problematic owing to the global
+nature of the quadrature rule. 
+The coupling with fast direct solvers for computing determinants also results in $O(N^2 \log{N})$ 
+determinant evaluation since evaluating each matrix entry costs $O(N)$, where 
+$N$ is the number of discretization points on the boundary.
+Over the last two decades, many high-order quadrature methods which are compatible with
+fast algorithms like the fast multipole method (and fast direct solvers as well, 
+since each matrix entry requires O(1) work) have been developed for solving
+integral equations.
+Extensive numerical evidence suggests that the zeros of the 
+determinants of linear systems discretized using 
+these quadrature methods are also high order approximations of Dirichlet eigenvalues
+for the Stokes PDE--- the error is observed to be proportional to the quadrature error
+for the eigenfunction $\bt^{-}$ associated with the eigenvalue.
+We leave a proof of this to future work.
+
+\begin{remark}
+The same analysis does not carry through for the operator
+$\cI - 2 \cD_{k} - 2i\eta \cS_{k} - 2\cW$, 
+since $\cS_{k}$ is not a trace class operator.
+For brevity, let $\cM_{k} = -2\cD_{k} - 2i\eta \cS_{k} - 2\cW$.
+The operator $\cM_{k}$ is 
+in $\cJ_{2}(\bL^{2}(\Gamma))$ where
+$\cJ_{2}(\bL^{2}(\Gamma))$ is the space of Hilbert-Schmidt operators
+on $\bL^{2}(\Gamma)$ (the singular values of the operator are square
+summable, as opposed to being summable).
+Thus the Fredholm determinant of $\cI + \cM_{k}$
+is not necessarily finite. 
+However, as noted in~\cite{zhao2015robust}, the convergence
+result~\cref{thm:mainconvfreddet}
+should be true up to a logarithmic factor in the rate
+of convergence, since the singular values of the operator
+$\cM_{k}$ decay like $\frac{1}{n}$, and the
+Fredholm determinant divergers logarithmically. 
+In~\cref{subsec:convannulus}, we demonstrate that this fact
+numerically on the annulus, where the eigenvalues are analytically known. 
+\end{remark}

### 2019-03-19 doc/draft-01-stokes/appendix.tex
Adding appendix for neumann eigenvalues on the unit disk

\section{Neumann eigenvalues and eigenfunctions on the unit disk}
In this section, we analytically compute some of the Neumann eigenvalues
on the unit disk for the Stokes operator.

Suppose that $\bu$ is of the form
\begin{equation}
\bu = \nabla (\alpha r^{n} \sint - \beta r^{n} \cost) + \nabla^{\perp}(\gamma \jnkr \sint + \delta \jnkr \cost) \, ,
\end{equation}
and the pressure is given by
\begin{equation}
p = k^2 (\alpha r^{n} \sint - \beta r^{n} \cost) \, ,
\end{equation}
where $\alpha,\beta,\gamma,\delta$ are constants.

We first show that this pair satisfies the oscillatory stokes equation
in the unit disk.
\begin{lemma}
$(\bu,p)$ satisfy the oscillatory Stokes equation.
\end{lemma}
\begin{proof}
$\bu$ is divergence free since
\begin{equation}
\nabla \cdot \bu  = \Delta (\alpha r^{n} \sint - \beta r^{n} \cost) = 0 \, ,
\end{equation}
as $r^{n} \cost$,  $r^{n} \sint$ are harmonic functions. 
To show that $(\bu,p)$ satisfies the PDE, observe that
\begin{equation}
\begin{aligned}
(\Delta + k^2) \bu &= (\Delta + k^2) \nabla (\alpha r^{n} \sint - \beta r^{n} \cost) \, + \\
\quad & \hspace*{15ex} (\Delta + k^2) \nabla^{\perp} (\gamma \jnkr \sint + \delta \jnkr \cost) \, , \\
&= k^2 \nabla (\alpha r^{n} \sint - \beta r^{n} \cost) \quad \bigg(\text{Since} \Delta (r^{n}\cost, r^{n}\sint) = 0 \quad
\text{and} \, ,\\
& \hspace*{25ex} (\Delta + k^2) (\jnkr \cost, \jnkr \sint) = 0 \bigg) \\
&= \nabla p
\end{aligned}
\end{equation}
\end{proof}

Let $\hat{r}, \hat{\theta}$ denote the unit vectors in polar coordinates.
Then  $\hat{r}$ is the unit normal on the boundary of the unit disk.
The surface traction on the boundary of the unit disk is then given by 
\begin{equation}
\bt = -p \hat{r} + \nabla (\bu \cdot \hat{r}) + \partial_{r} \bu \, .
\end{equation}
In particular
\begin{equation}
\begin{aligned}
t_{r} = \bt \cdot \hat{r} &= -p + 2\partial_{r} (\bu \cdot \hat{r}) \, , \\
t_{\theta} = \bt \cdot \hat{\theta} &= \frac{1}{r}\partial_{\theta}(\bu \cdot \hat{r}) + \partial_{r} (\bu \cdot \hat{\theta}) \, .
\end{aligned}
\end{equation}

The $\hat{r},\hat{\theta}$ components of $\bu$ are given by
\begin{equation}
\begin{aligned}
u_{r} = \bu \cdot \hat{r} &= \partial_{r} (\alpha r^{n} \sint - \beta r^{n} \cost) 
- \frac{1}{r}\partial_{\theta}(\gamma \jnkr \sint + \delta \jnkr \cost) \\
&= \sint \left(\alpha n r^{n-1} + \delta n \frac{\jnkr}{r} \right) 
  - \cost \left(\beta n r^{n-1} + \gamma n \frac{\jnkr}{r} \right) \, , \\
u_{\theta} = \bu \cdot \hat{\theta} &= \frac{1}{r} \partial_{\theta} (\alpha r^{n} \sint - \beta r^{n} \cost)
+ \partial_{r} (\gamma \jnkr \sint + \delta \jnkr \cost) \\ 
&= \cost \left( \alpha n r^{n-1} + \delta k \jnpkr \right) + \sint \left( \beta n r^{n-1} + \gamma k \jnpkr \right)
\end{aligned}
\end{equation}

The relevant derivatives are given by
\begin{equation}
\begin{aligned}
\partial_{r} u_{r} &= \sint \left( \alpha n (n-1) r^{n-2} + \delta n \ddr \left(\frac{\jnkr}{r}\right) \right)
- \cost \left( \beta n (n-1) r^{n-2} + \gamma n \ddr \left( \frac{\jnkr}{r} \right) \right) \, , \\
\frac{1}{r} \partial_{\theta} u_{r} &= n \cost \left(\alpha n r^{n-2} + \delta n \frac{\jnkr}{r^2} \right) + 
n \sint \left(\beta n r^{n-2} + \gamma n\frac{\jnkr}{r^2} \right) \, , \\
\partial_{r} u_{\theta} &= \cost(\alpha n(n-1) r^{n-2} + \delta k^2 \jnppkr) + 
\sint (\beta n(n-1)r^{n-2} + \gamma k^2 \jnppkr) \, .
\end{aligned}
\end{equation}

Now we finally get to the expressions for $t_{r},t_{\theta}$ 
\begin{equation}
\begin{aligned}
t_{r} &= \cost \left( \beta k^2 r^{n} -2\beta n(n-1)r^{n-2} - 2\gamma n \ddr \frac{\jnkr}{r}  \right) \, + \\
& \hspace*{15ex} \sint \left(-\alpha k^2 r^{n} + 2 \alpha n(n-1)r^{n-2} + 2 \delta n \ddr \frac{\jnkr}{r} \right) \, , \\
t_{\theta} &= \cost \left( \alpha r^{n-2} (n^2 + n(n-1)) + \delta \left( \frac{n^2}{r^2} + k^2 \jnppkr \right)  \right) + \\
& \hspace*{15ex} \sint \left( \beta r^{n-2} (n^2 + n(n-1)) + \gamma \left( \frac{n^2}{r^2} + k^2 \jnppkr \right) \right) \, .
\end{aligned}
\end{equation}
Let $h_{k} = \ddr (\jnkr/r)|_{r=1}$.
The values of $k$ for which there exists a non-zero solution $\alpha,\beta,\gamma,\delta$ 
to the following system of equations
\begin{equation}
\begin{bmatrix}
0 & 0 & k^2 - 2n(n-1) & -2nh_{k} \\
0 & 0 & 2n^2 -n & n^2 + k^2 \jnppk \\
-k^2 + 2n(n-1) & 2nh_{k} & 0 & 0 \\
2n^2 -n & n^2 + k^2 \jnppk & 0 & 0
\end{bmatrix}
\begin{bmatrix}
\alpha \\ \delta \\ \beta \\ \gamma
\end{bmatrix}
=
\begin{bmatrix}
0 \\ 0 \\ 0 \\ 0
\end{bmatrix}
\, ,
\end{equation}
are the Neumann eigenvalues of the unit disk.

A collorary of the above statement and the structure of the matrix is that
the interior Neumann eigenvalues of the unit disk satisfy
\begin{equation}
2n^2(2n-1)h_{k} - (n^2 + k^2 \jnppk)(-k^2 + 2n(n-1)) = 0 \, .
\end{equation}
A simple calculation shows that the zeros correpsonding to
$n=0$ are the zeros of $\jnppk$, the first few of which are
\begin{itemize}
\item $k = 1.74118378134066$
\item $k = 5.33144277352503$
\item $k = 11.7060049025921$
\end{itemize}

### 2019-03-19 doc/draft-01-stokes/01intro.tex
adding annulus example drivers

@@
 \end{remark}
+
+We closely follow the approach of Zhao and Barnett
+for computing the Laplace eigenvalues~\cite{zhao2015robust}.
+%
+The fact that layer potentials can be used to compute
+eigenvalues is based on the following sequence of
+facts: 1) represent the solution 
+as a layer potential with 
+an unknown density, and choose the representation such that
+you get a second kind integral equation for the unknown density;
+2) establish that the intergral equation is not invertible 
+only at the Dirichlet eigenvalues for Laplace's equation;
+3) prove that the zeros of the Fredholm determinant 
+(when the compact operator is in trace class) 
+line up with the Dirichlet eigenvalues; 
+4) and finally, show that when the integral equation
+is discretized using a Nystr\"{o}m method, the zeros of 
+the determinant 
+of the discrete linear system 
+converge exponentially
+to the zeros of the Fredholm determinant.
+
+%
+While the integral representations for the modified
+Stokes equation are directly applicable to the oscillatory
+Stokes equations, 
+proving invertibility of the associated operators
+away from the eigenvalues is a more involved task
+and forms the bulk of this section.
+%
+This in turn requires proving uniqueness results
+for various interior and exterior boundary value problems
+for the oscillatory Stokes equations.
+%
+To the best of our knowledge, the uniqueness results,
+particularly
+for exterior domains are new to the literature.

### 2019-03-19 doc/draft-01-stokes/02prelim.tex
adding annulus example drivers

@@
 We seek solutions of \cref{eq:ostokes} in the space
+\note{make sure this is the correct space}
 \begin{equation}
@@
 is then the analog of a Stokeslet
-\cite{Pozrikidis1992} for the problem
-\eqref{eq:ostokes}.
+\cite{Pozrikidis1992} for \eqref{eq:ostokes}.
 
@@
 \label{eq:dlformula}
-  \cD [\bmu] (\xx) = \oint_\Gamma \left ( \TT_{\cdot,\cdot,\ell}(\bx,\by)
+  \cD [\bmu] (\xx) = \pv \int_\Gamma \left ( \TT_{\cdot,\cdot,\ell}(\bx,\by)
   \nu_\ell(\yy)
@@
 \end{equation}
-where the $\oint$ symbol means that the integral is to be
+where the \pv indicates that the integral is to be
 evaluated in the principal value sense. 
@@
   \cD^{\intercal} [\bmu](\bx) = 
-  \oint_\Gamma \left ( \TT_{\cdot,\cdot,\ell}(\bx,\by)\nu_\ell(\xx)
+  \pv \int_\Gamma \left ( \TT_{\cdot,\cdot,\ell}(\bx,\by)\nu_\ell(\xx)
   \right ) \bmu(\yy) \, dS(\yy) \; .
@@
 
-In the following lemma, we review the limiting values of layer 
-potentials $\bS$ and $\bD$ on the boundary $\Gamma$.
+In the following lemma, we review the limiting values of
+the layer potentials $\bS$ and $\bD$ on the boundary $\Gamma$.
 
@@
   Let $\Omega$ be a bounded domain with $C^2$ boundary and let
-  the pair $(\bu,p)$ satisfy the oscillatory stokes equations
+  the pair $(\bu,p)$ satisfy the oscillatory Stokes equations
   \cref{eq:ostokes} in $\Omega$. Let $\bt$ denote the surface
-  traction associated with the velocity $\bu$. Then
+  traction associated with $(\bu,p)$. Then
 
@@
     \bS [\bt](\xx) - \bD[\bu](\xx) = \begin{cases} 
-    \bu(\xx) &\quad \xx \in \Omega \, , \\
-    0 &\quad \xx \in \Omega^{C} \; .
-    \end{cases}
+    \bu(\xx) &\quad \xx \in \Omega \,  \\
+    0 &\quad \xx \in E 
+    \end{cases} \; ,
   \end{equation}
+  where $E=\R^2\setminus\bar\Omega$ is the
+  exterior of the domain.
 \end{thrm}
@@
 \begin{proof}
+  Suppose that $\xx \in \Omega$.
   By the definitions of $\GG$ and $\Glap$, we have
@@
   Adding \cref{eq:rep_proof_1,eq:rep_proof_2}, we get the desired
-  result.
+  result. The argument for the case $\xx \in E$ is similar.
 \end{proof}
@@
   Then each component of $\uu(\xx)$ is an analytic function
-  of the coordinates $\xx$.
+  of the coordinates $\xx$ in $\Omega$.
 \end{cor}

### 2019-03-19 doc/draft-01-stokes/03analysis.tex
adding annulus example drivers

@@
 
-In this section, we discuss how integral equations
-can be used to compute to the Stokes eigenvalues.
-%
-We closely follow the approach developed by Zhao and Barnett
-for computing the Laplace eigenvalues~\cite{zhao2015robust}.
-%
-They compute the Laplace eigenvalues using the following
-steps: 1) represent the solution 
-as a layer potential with 
-an unknown density, and choose the representation such that
-you get a second kind integral equation for the unknown density;
-2) establish that the intergral equation is not invertible 
-only at the Dirichlet eigenvalues for Laplace's equation;
-3) prove that the zeros of the Fredholm determinant 
-(when the compact operator is in trace class) 
-line up with the Dirichlet eigenvalues; 
-4) and finally, show that when the integral equation
-is discretized using a Nystr\"{o}m method, the zeros of 
-the determinant 
-of the discrete linear system 
-converge exponentially
-to the zeros of the Fredholm determinant.
-
-We adapt their approach for computing the 
-Dirichlet eigenvalues for Stokes equation. 
-In the context of oscialltory Stokes equation,
-while integral representations for the modified
-Stokes equation are directly applicable, 
-proving invertibility of the associated operators
-away from the eigenvalues is a more involved task.
-This in turn requires proving uniqueness results
-for various interior and exterior boundary value problems
-for the oscillatory Stokes equations.
-These results play a crucial role in estabilishing step
-2 of the Zhao-Barnett approach listed above.
-To the best of our knowledge, the uniqueness results, particularly
-for exterior domains are new results.
-
-In order to prove the uniqueness results, we follow the 
+In this section, we establish how layer potential
+representations of oscillatory Stokes velocity fields
+can be used to compute Stokes eigenvalues.
+%
+The main results show that for certain representations
+the resulting integral equation is not invertible precisely
+when $k^2$ is an eigenvalue.
+%
+For the interior Neumann eigenvalue problem, this is proved
+for a single layer representation in \cref{thm:slmain}.
+%
+For the interior Dirichlet eigenvalue problem, this is
+proved separately for a double layer representation on
+simply connected domains in \cref{thm:dlmain} and
+for a combined-field representation on multiply connected
+domains in \cref{thm:cfmain}.
+%
+
+Before proving the main theorems, we require a number
+of uniqueness results for oscillatory Stokes boundary
+value problems.
+%
+To prove the uniqueness results, we follow the 
 structure presented in Colton and Kress~\cite[Ch. 3]{colton1983integral}
@@
 the standard layer potentials satisfy the radiation condition.
-and define well-posed versions of the
-exterior boundary value problems which incorporate the
-radiation condition.
+%
+By including the radiation condition, it is then
+possible to define well-posed versions of the
+exterior boundary value problems.
 %
 Then we derive a number of uniqueness
-results for many standard boundary value problems.
-%
+results for some standard boundary value problems
+on exterior domains.
+
 Along with the Fredholm alternative, these uniqueness
-results are sufficient to derive the invertibility of appropriate
-integral equations for a number of boundary value problems
-on simply and multiply connected domains.
-
-Once the equivalence between the non-invertibility
-of the second kind integral equation and Dirichlet eigenvalues
-for Stokes equations is established,
-the details of how the Fredholm determinant can be used as a
-numerical tool for computing the Stokes eigenvalues
-follows in a straightforward manner from the results 
+results are sufficient to prove
+\cref{thm:slmain,thm:dlmain,thm:cfmain}.
+%
+Once the main theorems are established,
+the details of how to use the Fredholm determinant
+as a numerical tool for computing the Stokes eigenvalues
+follows in a straightforward from the results
 in~\cite{zhao2015robust}.
-We reproduce the relevant results from their work applied 
-in this context for completeness.
+%
+We reproduce these results in the present
+context for completeness.
 
@@
 
-\begin{cor}
-  If $(\bu,p)$ is a radiating solution of
-  the oscillatory Stokes equations, then
-  $p$ is bounded and $p\to 0$ as $r\to\infty$.
-\end{cor}
-
 In the next lemma, we prove the analogue of Rellich's lemma for the
@@
   of a finite collection of bounded domains.
-  Suppose that $\bu$ satisfies the oscillatory Stokes equation in
-  $E$ and that 
+  Suppose $k$ is real, $\bu$ satisfies the oscillatory
+  Stokes equation in $E$, and that 
 \begin{equation}
@@
 \begin{equation}
-r^{|n|}, r^{-|n|}, H^{1}_{n}(k r), H^{2}_{n}(k r) \, , \quad
+r^{|n|}, r^{-|n|}, H^{(1)}_{n}(k r), H^{(2)}_{n}(k r) \, , \quad
 n\neq 0 \, , \nonumber
@@
 \begin{equation}
-1, \log{(r)}, H^{1}_{0}(k r), H^{2}_{0}(k r) \quad n=0 \, ,  \nonumber
-\end{equation} 
-where $H_{n}^{1,2}(\cdot)$ are the Hankel functions of the first and
+1, \log{(r)}, H^{(1)}_{0}(k r), H^{(2)}_{0}(k r) \quad n=0 \, ,  \nonumber
+\end{equation} 
+where $H_{n}^{(1),(2)}(\cdot)$ are the Hankel functions of the first and
 second kind of order $n$.
 Since $a_{j,n}(r)$ satisfy~\cref{eq:adecay}, and using the asymptotic 
-expansion of $H_{n}^{1,2}(r)$, we note that the projection of 
-$a_{j,n}$ on $r^{|n|}$, and $H_{n}^{1,2}(k r)$ must be zero. 
-Thus, 
+expansion of $H_{n}^{(1),(2)}(kr)$ when $k$ and $r$ are real-valued, we note
+that the projection of $a_{j,n}$ on $r^{|n|}$, and $H_{n}^{1,2}(k r)$
+must be zero. Thus, 
 \begin{equation}
@@
 \end{proof}
+
 \begin{remark} \label{rmk:harmu}
@@
 \begin{align}
-k^2 \bu &= \nabla p  \quad \label{eq:massconsred} \\
-\nabla \cdot \bu &= 0 \, . \nonumber
+k^2 \bu &= \nabla p \label{eq:massconsred} \; .
 \end{align}
-Taking the inner product of~\cref{eq:massconsred} with $\nabla^{\perp}$,
-we note that $\bu$ satisfies both $\nabla^{\perp} \cdot \bu = 0$ 
-and $\nabla \cdot \bu = 0$, i.e. $u_1 - i u_2$ is analytic.
 \end{remark}
+
+\note{PROVE COROLLARY}
+\begin{cor}
+  If $(\bu,p)$ is a radiating solution of
+  the oscillatory Stokes equations, then
+  $p$ is bounded and $p\to 0$ as $r\to\infty$.
+\end{cor}
+
 \begin{remark}
-Note that in~\cref{lem:rellich}, $\bu$ need not be a radiating solution. 
-All that is assumed of $\bu$ is that it satifies the PDE in $E$.
+  It should be noted that in~\cref{lem:rellich}, $\bu$ need
+  not be a radiating solution. All that is assumed of $\bu$
+  is that it satifies the PDE in $E$.
 \end{remark}
+
+We now have the results needed to establish the
+uniqueness of exterior boundary value problems.
 
@@
 \begin{proof}
-Since $\bu = 0$ on $\Gamma$, it follows from~\cref{eq:repinfest} that
+Since $\bu = 0$ on $\Gamma$, it follows from~\cref{lem:rep} that
 \begin{equation}
@@
 \end{equation}
-In particular, this implies that
+
+Suppose that $\Im(k) > 0$. Then, it is immediate that
+$\bu \equiv 0$ in $E$.
+
+Suppose that $k$ is real valued. It is clear that
 \begin{equation}
@@
 \end{equation}
-Thus, the conditions for $\bu$ in~\cref{lem:rellich}
+Thus, the conditions on $\bu$ and $k$ in~\cref{lem:rellich}
 are satisfied, and each component of $\bu$ is a harmonic function
@@
 Dirichlet problem for Laplace's equation
-on exterior domains, we conclude that $\bu \equiv 0$ in $E$.
+on exterior domains, we conclude that $\bu \equiv 0$
+in $E$.
 \end{proof}
@@
 \begin{thrm}
+  \label{thm:cfmain}
 Suppose $\Omega$ is a bounded region defined by the intersection of a 

### 2019-03-19 matlab/example/example_annulus_001.m

@@ -1,0 +1,99 @@
+
+%EXAMPLE_ANNULUS_001
+%
+% compute a chebfun representation of the fredholm determinant 
+% of the system I-2D-2iS for a domain on the intervals [j,j+1] j=1,...,8
+% save chebfun, domain, and some settings to a file
+
+filebase = 'example_annulus_001'; 
+timeref = datestr(now,'_yyyymmdd_HHMMSS');
+fileout = [filebase, timeref, '.mat'];
+
+% annulus params
+
+r1 = 1.0;
+r2 = 1.7;
+
+
+chebabs = cell(16,1);
+for j = 1:length(chebabs)
+    chebabs{j} = [1.0*j 1.0*(j+1)];
+end
+
+max_rzk = chebabs{end}(end); lam = 2*pi/max_rzk;
+
+seed = 8675309;
+rng(seed);
+addpath('../src')
+addpath('../example')
+addpath('../../mwrap')
+
+cparams.eps = 1.0e-3;
+cparams.nchmax = 100000;
+cparams.maxchunklen = lam;
+cparams.nover = 2;
+narms = 3;
+amp = 0.25;
+W = 3.0; H = 2.0; p = 4.0;
+
+chunkers = {};
+chunkert = chunkfunc(@(t) circle(t,r2),cparams);
+chunkert = chunksort(chunkert);
+chunkers{1} = chunkert;
+
+nw = 1;
+nh = 1;
+
+ind = 2;
+chunkert = chunkfunc(@(t) circle(t,r1),cparams);
+chunkert = chunkreverse(chunkert);
+chunkert = chunksort(chunkert);
+chunkers{ind} = chunkert;
+        
+[chunker,nchs] = chunkermerge(chunkers);
+
+%
+
+xs = chunker.chunks(1,:,:); xs = xs(:);
+ys = chunker.chunks(2,:,:); ys = ys(:);
+
+rnorms = chunknormals(chunker);
+
+intparams.intorder = chunker.k;
+
+hold off
+quiver(xs,ys,rnorms(1,:).',rnorms(2,:).')
+hold on
+scatter(xs,ys)
+
+%%
+
+% build matrix
+
+cd = -2.0 + 1i*0.0;
+cs = 0.0 - 1i*2.0;
+ncomp = length(nchs);
+
+%
+
+opts = []; opts.FLAM = 1; opts.verb = true;
+detfun = @(zk) ostokes_determinant(zk,chunker,nchs,cs, ...
+    cd,opts);   
+
[…]

### 2019-03-19 matlab/example/example_annulus_002.m

@@ -1,0 +1,99 @@
+
+%EXAMPLE_ANNULUS_002
+%
+% compute a chebfun representation of the fredholm determinant 
+% of the system I-2D for a domain on the intervals [j,j+1] j=1,...,8
+% save chebfun, domain, and some settings to a file
+
+filebase = 'example_annulus_002'; 
+timeref = datestr(now,'_yyyymmdd_HHMMSS');
+fileout = [filebase, timeref, '.mat'];
+
+% annulus params
+
+r1 = 1.0;
+r2 = 1.7;
+
+
+chebabs = cell(16,1);
+for j = 1:length(chebabs)
+    chebabs{j} = [1.0*j 1.0*(j+1)];
+end
+
+max_rzk = chebabs{end}(end); lam = 2*pi/max_rzk;
+
+seed = 8675309;
+rng(seed);
+addpath('../src')
+addpath('../example')
+addpath('../../mwrap')
+
+cparams.eps = 1.0e-3;
+cparams.nchmax = 100000;
+cparams.maxchunklen = lam;
+cparams.nover = 2;
+narms = 3;
+amp = 0.25;
+W = 3.0; H = 2.0; p = 4.0;
+
+chunkers = {};
+chunkert = chunkfunc(@(t) circle(t,r2),cparams);
+chunkert = chunksort(chunkert);
+chunkers{1} = chunkert;
+
+nw = 1;
+nh = 1;
+
+ind = 2;
+chunkert = chunkfunc(@(t) circle(t,r1),cparams);
+chunkert = chunkreverse(chunkert);
+chunkert = chunksort(chunkert);
+chunkers{ind} = chunkert;
+        
+[chunker,nchs] = chunkermerge(chunkers);
+
+%
+
+xs = chunker.chunks(1,:,:); xs = xs(:);
+ys = chunker.chunks(2,:,:); ys = ys(:);
+
+rnorms = chunknormals(chunker);
+
+intparams.intorder = chunker.k;
+
+hold off
+quiver(xs,ys,rnorms(1,:).',rnorms(2,:).')
+hold on
+scatter(xs,ys)
+
+%%
+
+% build matrix
+
+cd = -2.0 + 1i*0.0;
+cs = 0.0;
+ncomp = length(nchs);
+
+%
+
+opts = []; opts.FLAM = 1; opts.verb = true;
+detfun = @(zk) ostokes_determinant(zk,chunker,nchs,cs, ...
+    cd,opts);   
+
[…]

### 2019-03-20 doc/draft-01-stokes/01intro.tex
update paper, add to intro, clean up theory section

--- 2019-03-15 doc/draft-01-stokes/01intro.tex
@@
 The planar incompressible Stokes equations describe
-creeping flows in two dimensions. Let $\Omega \subset \R^2$
-be a bounded domain with $C^2$ boundary. The eigenvalue problem seeks
+creeping flows in two dimensions.
+%
+Let $\Omega \subset \R^2$
+be a bounded domain with $C^2$ boundary.
+%
+The Stokes eigenvalue problem seeks
 values $k^2$ such that
@@
 subject to boundary conditions, has a non-trivial solution $(\uu,p)$.
+%
 In this work, we consider the eigenvalue problem subject to 
@@
 \end{equation}
-It is well known that there is a countable collection of such
+It is well known that the values $k^2$ are necessarily
+real and positive and that there is a countable collection of such
 values $0 < k_{1}^{2} \leq k_{2}^2 \leq \ldots \uparrow \infty$,
@@
 \end{remark}
+
+The eigenvalues (and eigenfunctions)
+of the Stokes operator have applications in the
+stability analysis of stationary solutions of the
+Navier--Stokes equations \cite{osborn1976approximation}
+and in the study of decaying two dimensional turbulence
+\cite{schneider2008final}.
+%
+The eigenvalues and eigenfunctions of the Stokes
+operator are the subject of intense analytical
+investigation
+\cite{taylor1933buckling,szego1950membranes,
+  polya1951isoperimetric,bramble1963pointwise,
+  ashbaugh1996fundamental,leriche2004stokes,
+  kelliher2009eigenvalues,antunes2011buckling},
+particularly as they relate to the eigenvalues and
+eigenfunctions of the drum.
+
+Historically, the Stokes eigenvalue problem serves as a
+common model problem for numerical eigenvalue analysis
+with a fourth order operator (here, the bi-Laplacian).
+%
+Further, numerical simulation has long played an
+important role in the analyses described above --- both for
+estimating the eigenvalues on domains of practical
+interest and for exploring open conjectures
+and generating new conjectures.
+
+Borrowing the language of~\cite{zhao2015robust},
+which concerns the Laplace or ``drum'' eigenvalue
+problem,
+the numerical treatment of the Stokes eigenvalue
+problem can be divided into two basic approaches.
+%
+Type A
+methods perform a direct discretization of the
+Stokes operator, typically with a
+finite element basis, and the eigenvalues are found
+as the eigenvalues of the discrete system.
+%
+Type B
+methods utilize a boundary integral equation
+(BIE) re-formulation of the oscillatory Stokes
+equation which is then discretized, so that
+the eigenvalues are found by a nonlinear search
+for the values of $k$ where the BIE is not invertible.
+%
+
+There is a large body of research on type A methods
+for the Stokes eigenvalue problem.
+%
+We do not seek to review this literature here,
+but point to \cite{johnson1974beam,
+  rannacher1979nonconforming,
+  mercier1981eigenvalue,bjorstad1999high,
+  jia2009approximation,chen2006approximation,
+  lovadina2009posteriori,huang2011numerical,
+  carstensen2014guaranteed}
+for some representative examples.
+
+As noted in~\cite{zhao2015robust}, the type B
+methods provide some advantages.
+%
+Because the BIE is defined on the
+boundary alone, there is a reduction in the
+dimension of the domain to be discretized.
+%
+This reduces the number of unknowns over finite
+element discretizations, particularly given
+that finite element methods suffer from
+high-frequency ``pollution'' when $k$ is large
+\cite{babuska1997pollution}.
+
+Further, Zhao and Barnett~\cite{zhao2015robust}
+show how to alleviate some of the costliness of the
+nonlinear optimization introduced by a type B method.
+%
+The standard approach searches for ``V''-shaped minima
+of the singular values of the BIE; see, for
+instance, \cite{trefethen2006computed}.
+%
+Instead, Zhao and Barnett utilize the Fredholm
+determinant (see \cref{sec:dets}) which, for certain
+BIEs, is an analytic function of $k$ with roots
+precisely when $k^2$ is an eigenvalue.
+%
+The Fredholm determinant can be estimated using
+a Nystr\"{o}m discretization of the BIE
+\cite{bornemann2010numerical,zhao2015robust}.
+%
+Then, the eigenvalues can be estimated efficiently
+by using high order root finding methods applied
+to the discretized determinant.
+
+With the efficiency of the approach of
+\cite{zhao2015robust} for the drum problem in mind,
+we develop a type B method for the Stokes eigenvalue
+problem.
+%
+This requires that a layer
+potential representation of the solution
+of \cref{eq:ostokes} be given and that the resulting BIE
+is not invertible precisely when $k^2$ is an eigenvalue.
+%
+The first requirement is straightforward to
+satisfy because the
+well-known layer potential representations for the
+modified Stokes equation~\cite{Pozrikidis1992,biros2002embedded,
+  jiang2013second,ladyzhenskaya1969mathematical}
+are directly applicable.
+%
+Proving the invertibility of the associated operators
+away from the eigenvalues is a more involved task
+and forms the bulk of the theoretical component
+of this paper.
+
+\subsection{Relation to other work}
+
+While type B methods for the
+related ``buckling'' eigenvalue problem
+have been considered previously,
+these typically relied on first-kind integral
+equation formulations of the underlying PDE,
+i.e. formulations in which the BIE operator is
+compact \cite{kitahara2014boundary,antunes2011buckling}.
+%
+This is unsatisfying from a theoretical
+perspective, because such operators are never invertible
+(though, they are injective precisely when $k^2$ is an
+eigenvalue \cite{kitahara2014boundary,antunes2011buckling})
+so that the relation between the non-invertibility of the
+discrete system and the eigenvalues is obscured.
+%
+Further,
+such representations create numerical challenges because
+common measures of the ``non-invertibility'' of a matrix,
+like the smallest singular value or the determinant, converge
+rapidly to zero for all values of $k^2$ as the boundary is
+refined. Therefore, the measure of whether $k^2$ is an
+approximate eigenvalue is {\em relative to the current grid}
+for first kind equations.
+
+The classical single and double layer representations
+for oscillatory Stokes considered in this paper
+result in second kind equations, i.e. integral equations
+of the form $\mathcal{I} - \mathcal{K}_k$ where
+$\mathcal{K}_k$ is compact.
+%
+Such equations have a more satisfying theory
+\cite{reed1972methods,colton1983integral,kress1989linear},
+which translates well to numerical implementation
+\cite{atkinson2009numerical,bornemann2010numerical,
+  hackbusch2012integral,zhao2015robust}.
+%
+The use of a second kind representation is standard
+for the drum problem \cite{backer2003numerical,zhao2015robust}
+and was used recently to compute the vibrating
+modes of thin, clamped plates~\cite{lindsay2018boundary}.
+
+\subsection{Paper outline and contributions}
+
+The rest of this paper proceeds as follows.
+%
+In \cref{sec:prelim}, we set the notation, provide some
+mathematical preliminaries, and review the
+properties of single and double layer potentials
+for the oscillatory Stokes equations.
+%
+Then, in \cref{sec:analysis}, we develop the necessary
+theory for proving \cref{thm:dlmain,thm:cfmain},
+which show that the BIEs resulting from these
+layer potential representations are not invertible
+precisely when $k^2$ is an eigenvalue.
+%
+These theoretical developments include a detailed
+discussion of the uniqueness of oscillatory Stokes
+boundary value problems in exterior domains.
+%
+To the best of our knowledge, the invertibility
+and uniqueness results are new to the literature.
+%
+\Cref{sec:dets} then outlines how the Fredholm determinant
+can be used in the oscillatory Stokes context.
+%
+In \cref{sec:numerical}, we describe the numerical
+methods we use to discretize the BIEs and to perform
+fast determinant calculations.
+%
+That section also includes numerical experiments
+which demonstrate some of the paper's analytical
+claims as well as the effectiveness of the overall
+framework.
+%
+Finally, we provide some concluding thoughts,
+describe plans for future research,
+and outline some open questions in
+\cref{sec:conclusion}.

### 2019-03-20 doc/draft-01-stokes/02prelim.tex
update paper, add to intro, clean up theory section

@@
 \section{Mathematical Preliminaries}
-
+\label{sec:prelim}
 In this paper, vector-valued
@@
 \end{equation}
+
+\subsection{The Fredholm Alternative}
+
+We require some standard results from the theory of
+Fredholm integral equations. Interested readers may
+consult \cite{reed1972methods,colton1983integral,kress1989linear},
+among others, for the relevant background.
+
+Let $X$ be a Banach space equipped with a bilinear form ...
+
+\note{Travis: put Fredholm alternative here}
 

### 2019-03-20 doc/draft-01-stokes/03analysis.tex
update paper, add to intro, clean up theory section

@@
 \section{Fredholm analysis of the integral representations}
-
+\label{sec:analysis}
 In this section, we establish how layer potential
@@
 when $k^2$ is an eigenvalue.
-%
-For the interior Neumann eigenvalue problem, this is proved
-for a single layer representation in \cref{thm:slmain}.
 %
@@
 results are sufficient to prove
-\cref{thm:slmain,thm:dlmain,thm:cfmain}.
+\cref{thm:dlmain,thm:cfmain}.
 %
@@
 as a numerical tool for computing the Stokes eigenvalues
-follows in a straightforward from the results
+follows in a straightforward manner from the results
 in~\cite{zhao2015robust}.
@@
 The radiation condition allows for a well-posed formulation
-of the exterior boundary value problems, i.e.
+of the exterior boundary value problems, which we
+summarize in
 \cref{def:dir_exterior,def:neu_exterior} below.
@@
 we establish the well-known result that
-the interior eigenvalues are real-valued.
+the $k$ corresponding to interior eigenvalues, $k^2$,
+are real-valued.
 
@@
 
-\note{PROVE COROLLARY}
-\begin{cor}
-  If $(\bu,p)$ is a radiating solution of
-  the oscillatory Stokes equations, then
-  $p$ is bounded and $p\to 0$ as $r\to\infty$.
-\end{cor}
-
 \begin{remark}
@@
 \begin{thrm}[Uniqueness of the Exterior Dirichlet Problem]
+  \label{thrm:unique_dir_ext}
   Let the unbounded region $E$ be given as the exterior
@@
 
+\note{Manas: check out new argument below.}
+
 \begin{proof}
@@
 \end{equation}
-In particular, this implies that
+
+Suppose that $\Im(k) > 0$. It is then immediate
+that $\bu \equiv 0$ in $E$.
+
+Suppose that $k$ is real. It is clear that
 \begin{equation}
@@
 \end{equation}
-Thus, the conditions for $\bu$ in Rellich's lemma (\cref{lem:rellich})
+Thus, the conditions on $\bu$ and $k$ in \cref{lem:rellich}
 are satisfied, and each component of $\bu$ is a harmonic function
@@
 Because $0 = \btau \cdot \bt = 2\partial_{\tau\nu} p/k^2$,
-$\partial_\nu p $ is a constant on $\Gamma$. Using the
-fact that $(\bu,p)$ is radiating and the fact that $p$ is harmonic,
+$\partial_\nu p $ is a constant on $\Gamma$.
+Observe that $|\bu|$ and $|\be(\bu)|$ must be $O(1/r)$ as
+$r\to\infty$. Thus,
+for a radiating pair $(\bu,p)$ with $p$ harmonic,
+we have that $|p| = O(1/r)$ and $|\nabla p| = O(1/r^2)$
+as $r\to\infty$.
+Using this bound and that $p$ is harmonic,
 the divergence theorem implies that $\partial_\nu p=0$ on $\Gamma$.
@@
 \begin{remark}
-For proving the equivalence between Stokes eigenvalues
-of bounded regions $\Omega$ and the non-invertibility
-of corresponding second kind integral equations, we only
-need the uniqueness result for the Neumann problem in the 
-exterior of a simply connected domain. 
-The proof of the exterior Neumann problem in the exterior of several
-obstacles is more involved and presented in the 
-appendix~\cite{app:neuuniqueness}
+For proving the correspondence between Stokes eigenvalues
+for bounded regions, $\Omega$, and the non-invertibility
+of corresponding second kind integral equations defined on
+the boundary, $\Gamma$, we only need the uniqueness result
+for the Neumann problem in the exterior of a single
+simply connected domain. The proof of the exterior
+Neumann problem in the exterior of several
+obstacles is more involved and presented
+in~\cref{app:neuuniqueness}.
 \end{remark}
@@
   of a finite collection of bounded domains.
-  Suppose that $\Re(\eta),\Im(\eta),\Re(k),\Im(k) \geq 0$, and that
+  Suppose that the complex numbers $\eta$ and $k$ satisfy that
+  $\Re(\eta), \Re(k) > 0$ and $\Im(\eta),\Im(k) \geq 0$.
+  Suppose further that
   $(\bu,p)$ is a radiating solution of the
@@
 dV \nonumber \\
-& \qquad + 2 \left( (k_{1}\eta_{1} + k_{2}\eta_{2}) \int_{\Gamma} |\bu|^{2} dS  \right)
+& \qquad + 2 \left( \left (\Re(k)\Re(\eta) + \Re(k)\Re(\eta)
+\right ) \int_{\Gamma} |\bu|^{2} dS  \right)
 \, .
@@
 
-\subsection{The integral equations and its null-spaces}
-
-In this section, we establish the correspondence between the
-integral equations arising from layer potential representations
-of solutions to the oscillatory Stokes equation with Dirichlet 
-boundary conditions and the associated Stokes eigenvalues.
+\subsection{The integral equations and their null-spaces}
+
+In this section, we establish the correspondence between
+Stokes eigenvalues and the invertibility of certain integral
+equations arising from layer potential representations
+of solutions to the oscillatory Stokes equation.
 
@@
 $\bnu$ pointing out of $\Omega$.
-
-We analyze two different representations for the Dirichlet problem---
-when the velocity is represented using a double layer potential,
-i.e. setting $\bu=\bD_{k} \bmu$, and when the velocity
-is represented using a mixed layer potential,
-i.e. setting $\bu=(i\eta \bS_{k} + \bD_{k})\bmu$, where in both cases $\bmu$ 
-is the unknown density to be solved for. 
-Even though both reprensentations result in a second kind
-Fredholm integral equation for the Dirichlet problem,
-the spectral properties of these representations are very
-different based on the genus of the domain.
-We analyze the double layer potential representation 
-in~\cref{subsec:dlanalysis}
-and the mixed layer potential representation in~\cref{subsec:mixedanalysis}.
+We will use superscript $+$ and $-$ signs
+to indicate the limit values of a function on $\Gamma$
+as approached from the exterior and interior, respectively.
+
+For the sake of brevity, we consider only the
+Dirichlet eigenvalue problem but a similar analysis
+could be applied to the Neumann eigenvale problem.
+We analyze two different representations for the
+Dirichlet problem: a double layer potential,
+i.e. setting $\bu=\bD_{k} \bmu$, and a combined-field
+layer potential, i.e. setting
+$\bu=(i\eta \bS_{k} + \bD_{k})\bmu$. 
+While both representations result in a second kind
+integral equation for the oscillatory Stokes Dirichlet
+problem, the double layer potential has spurious non-trivial
+nullspaces on domains with positive genus, as
+explained below.
 
 \begin{remark}
-The analysis of integral equations for the oscillatory Stokes
-equation and the correspondance betweeen its null spaces and the eigenvalues
-of Stokes equation is analogous to the analysis carried out
-for integral equations for Helmholtz equation and the eigenvalues
-for the Laplace equation in~\cite{zhao2015robust}.
-$\bu$ plays the role of the Dirichlet data, and $\bt$ plays the role
-of the Neumann data. 
-Once the Green's representation and uniqueness results for the 
-the oscillatory Stokes equation have been established,
-the remainder of the analysis of the integral equations
-is in spirit identical to the analysis presented in~\cite{zhao2015robust}.
+  The application of the Fredholm alternative here
+  again follows the structure used for the Laplace
+  eigenvalue problem in~\cite[Ch. 3]{colton1983integral}.
 \end{remark}
 
-\subsubsection{Double layer reprensentation}
+\subsubsection{Dirichlet eigenvalues --- double layer
+  representation}
 \label{subsec:dlanalysis}
-Suppose that the solution to the Dirichlet problem using
-a double layer potential defined on $\Gamma$, i.e.
-setting $\bu = \bD_{k} \bmu$ for
+Suppose that the solution to the oscillatory
+Stokes Dirichlet problem, \cref{eq:dir_interior},
+is represented using a double layer potential defined
+on $\Gamma$, i.e. setting $\bu = \bD_{k} \bmu$ for
 an unknown density $\bmu$. 
-Substituting this representation
-into the Dirichlet boundary condition and applying
+Substituting this expression
+into the boundary condition and applying
 \cref{lem:jump-conds}, we obtain
@@
 \begin{equation}
-  (\cI - 2\cD_{k}) \bmu = -2\ff \; , \label{eq:inteq_dir_int}
-\end{equation}
-for the interior problem.
-As noted in~\cref{subsubsec:nullspacecorr}, the standard layer potentials
-result in rank-deficient representations for the boundary value problem.
-It is well-known that~\cref{eq:inteq_dir_int} has a one dimensional
-null-space due to this issue. Thus, proceeding as discussed earlier,
-we instead analyze the equation
-\begin{equation}
-(\cI - 2\cD_{k}  -2\cW) \bmu = -2\ff \; \, . \label{eq:inteq_dir_int_mod}
-\end{equation}
-
-On simply connected domains, there is a one-to-one correspondance between
-the eigenvalues of the Dirichlet problem for Stokes equation
-and the values of $k$ for which the operator $(\cI - 2\cD_{k} - 2\cW)$
-is not invertible. 
-The following theorem proves this result.
-
-\begin{thrm}
-\label{thm:dlmain}
-Suppose that $\Omega$ is a simply connected domain, then the operator
-$(\cI - 2\cD_{k} - 2 \cW)$ is not invertible if and only if $k$ is 
-Dirichlet eigenvalue for Stokes equation on $\Omega$.
-\end{thrm}
-\begin{proof}
-Suppose that $k$ is not a Dirichlet eigenvalue for Stokes equation on
-$\Omega$. 
-Suppose further that $\bmu$ satisfies
-\begin{equation}
-(\cI - 2\cD_{k} - 2\cW) \bmu = 0 \, , \label{eq:dlproofrep}
-\end{equation}
-i.e. $\bmu$ is in the null-space
-of $(\cI - 2 \cD_{k} - 2 \cW)$. 
-Applying the operator $\cW$ to~\cref{eq:dlproofrep} and 
-using~\cref{lem:propnullspacecorr}, we get
-\begin{equation}
-0 = \cW [(\cI - 2\cD_{k} - 2\cW)\bmu] = -2\cW [\bmu] \, .
-\end{equation}
-Thus~\cref{eq:dlproofrep} reduces to
-\begin{equation}
-(\cI - 2 \cD_{k})\bmu = 0\, .
-\end{equation}
-Suppose now $\bu = -2\bD_{k}[\bmu]$ in $\Omega$.
-Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
-and applying~\cref{lem:jump-conds}, we get that the interior
-limit of the velocity $\bu^{-} = (\cI - 2\cD_{k}) \bmu = 0$ on $\Gamma$. 
-Since $k$ is not a Dirichlet eigenvalue for the Stokes equation on 
-$\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
-This in particular implies that the interior limit of the surface traction
-denoted by $\bt^{-} = 0$ on $\Gamma$. 
-Using~\cref{lem:jump-conds} again for the jump in surface traction
-for the double layer potential, we conclude that the exterior limit
-of the surface traction $\bt^{+} = 0$ on $\Gamma$. 
-Note that $\bu$ is a radiating solution of the oscillatory
-Sotkes equation in the exterior $E$, since
-$\cW[\mu] = 0$ implies $\int_{\Gamma} \mu \cdot \bnu = 0$.
-From uniqueness of the Neumann problem in the exterior $E$, we conclude
-that $\bu \equiv 0$ in $E$ as well, which in particular implies that
-the exterior limit of the velocity $\bu^{+}=0$ on $\Gamma$.   
-Using the jump conditions in~\cref{lem:jump-conds} again, we
-get that $\bmu = \frac{1}{2}(\bu^{+} - \bu^{-}) = 0$.
-Thus $(\cI - 2\cD_{k} - 2\cW)$ is invertible if $k$ is not a Dirichlet
-eigenvalue for the Stokes equation on $\Omega$.
-
-From Green's representation for the oscillatory Stokes qeuation, 
-we know that 
-  \begin{equation} \label{eq:rep-theorem}
-    \bS_{k} [\bt](\xx) - \bD_{k}[\bu](\xx) = \begin{cases} 
-    \bu(\xx) &\quad \xx \in \Omega \, , \\
-    0 &\quad \xx \in \Omega^{C} \; .
-    \end{cases}
-  \end{equation}
-Suppose that $k$ is Dirichlet eigenvalue for the Stokes equation on $\Omega$
-and let $\bu$ denote the corresponding eigenfunction, and let $\bt^{-}$ denote
-the surface traction associated with the eigenfunction on the boundary $\Gamma$.
-Since $\bu$ is a Dirichlet eigenfunction, the velocity restricted to the boundary
-$\bu^{-} = 0$. 
-Applying the Green's theorem to the pair $\bt^{-}, \bu^{-}$ and taking 
-its derivative on $\Gamma$ using~\cref{lem:jump-conds}, we get
-\begin{equation}
-\bt^{-} = (\cDt_{k} + \frac{1}{2} \cI) \bt^{-} \, ,\implies \left(\cI - 2\cDt_{k} \right) 
-\bt^{-} = 0 \, .
-\end{equation}
-From the Fredholm alternative, it then follows that $(\cI - 2\cD_{k})$ has a non-trivial 
-null-space.
-However, we need to prove that $(\cI -2\cD_{k} - 2\cW)$ has a non-trivial null-space
-for which we need the following two lemmas.
-
-\begin{lemma}
-$\bnu \in \cN(\cI - 2\cDt_{k})$
-\end{lemma}
+  (\cI - 2\cD_{k}) \bmu = -2\ff \; . \label{eq:inteq_dir_int}
+\end{equation}
+
+The rank deficiency of $\cI-2\cDk$ is
+well-known~\cite{biros2002embedded} and we summarize it
+in
+
+\begin{lem}[\cite{biros2002embedded}]
+  \label{lem:nunull} In the notation above,
+  $\bnu \in \cN(\cI - 2\cDkt)$.
+\end{lem}
 \begin{proof}
 From~\cref{lem:propnullspacecorr}, we note that
-$W[(\cI - 2\cD_{k})\bmu] =0$ implies that $\left<(\cI -2\cD_{k})\bmu ,\bnu \right>$ for
+$W[(\cI - 2\cD_{k})\bmu] =0$ implies that
+$\left<(\cI -2\cD_{k})\bmu ,\bnu \right> = 0$ for
 all $\bmu$, i.e. $\bnu \in R(\cI - 2\cD_{k})^{\perp}$, where
@@
 \end{proof}
-
-\begin{lemma}
-If $\bt^{-}$ is the surface traction associated with an interior Dirichlet
-Stokes eigenfunction $\bu$, then $\bt^{-}$ and $\bnu$ are linearly independent.
-\end{lemma}
+Thus, we instead analyze the equation
+\begin{equation}
+(\cI - 2\cD_{k}  -2\cW) \bmu = -2\ff \; \, . \label{eq:inteq_dir_int_mod}
+\end{equation}
+Note that if $\ff$ satisfies the compatibility
+condition $\int_\Gamma \ff \cdot \bnu \, dS =0$, then
+\cref{eq:inteq_dir_int_mod} implies \cref{eq:inteq_dir_int}.
+
+On simply connected domains, there is a one-to-one correspondance between
+the eigenvalues of the Dirichlet problem for
+the Stokes equation
+and the values of $k$ for which the operator $(\cI - 2\cD_{k} - 2\cW)$
+is not invertible. To prove this, we require the results
+above and the following lemma:
+\begin{lem}
+  \label{lem:nutracli}
+  If $\bt^{-}$ is the surface traction associated
+  with an interior Dirichlet Stokes eigenfunction $\bu$,
+  then $\bt^{-}$ and $\bnu$ are linearly independent.
+\end{lem}
 \begin{proof}
@@
 
-We now return to the proof of~\cref{thm:dlmain}. 
-We know that $\bt^{-}, \bnu \in \cN(\cI - 2\cDt_{k})$ are two linearly independent
-vectors in the null space.
-Let $c = \left< \bt^{-},\bnu \right>$. Then, it follows that 
-$\left<\bt^{-} -c \bnu, \bnu \right> = 0$ and thus
-$\cW[\bt^{-} - c\bnu] = 0$. 
+We now have
+
+\begin{thrm}
+\label{thm:dlmain}
+Suppose that $\Omega$ is a bounded, simply connected domain. Then, the operator
+$(\cI - 2\cD_{k} - 2 \cW)$ is not invertible if and only if $k^2$ is a
+Dirichlet eigenvalue for the Stokes equation on $\Omega$.
+\end{thrm}
+\begin{proof}
+  Suppose that $k^2$ is not a Dirichlet eigenvalue for
+  the Stokes equation on
+$\Omega$. 
+Suppose further that $\bmu$ satisfies
+\begin{equation}
+(\cI - 2\cD_{k} - 2\cW) \bmu = 0 \, , \label{eq:dlproofrep}
+\end{equation}
+i.e. $\bmu$ is in the null-space
+of $(\cI - 2 \cD_{k} - 2 \cW)$. 
+Applying the operator $\cW$ to~\cref{eq:dlproofrep} and 
+using~\cref{lem:propnullspacecorr}, we get
+\begin{equation}
+0 = \cW [(\cI - 2\cD_{k} - 2\cW)\bmu] = -2\cW [\bmu] \, .
+\end{equation}
+Thus~\cref{eq:dlproofrep} reduces to
+\begin{equation}
+(\cI - 2 \cD_{k})\bmu = 0\, .
+\end{equation}
+Suppose now $\bu = -2\bD_{k}[\bmu]$ in $\Omega$.
+Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
+and applying~\cref{lem:jump-conds}, we get that the interior
+limit of the velocity $\bu^{-}$, is given by $(\cI - 2\cD_{k}) \bmu = 0$
+on $\Gamma$. Since $k^2$ is not a Dirichlet eigenvalue for the Stokes
+equation on $\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
+In particular, this implies that the interior limit of the surface traction
+denoted by $\bt^{-} = 0$ on $\Gamma$. 
+Using~\cref{lem:jump-conds} again, we conclude that the exterior limit
+of the surface traction, $\bt^{+}$, is $0$ on $\Gamma$. 
+Note that $\bu$ is a radiating solution of the oscillatory
+Stokes equation in the exterior $E$, as $\cW[\mu] = 0$ implies
+$\int_{\Gamma} \bmu \cdot \bnu = 0$.
+From the uniqueness of the Neumann problem in the
+exterior $E$, we conclude that $\bu \equiv 0$ in $E$ as well,
+which in particular implies that
+the exterior limit of the velocity, $\bu^{+}$, is $0$ on $\Gamma$.   
+Using the jump conditions in~\cref{lem:jump-conds} again, we
+get that $\bmu = \frac{1}{2}(\bu^{+} - \bu^{-}) = 0$.
+Thus $(\cI - 2\cD_{k} - 2\cW)$ is invertible if $k^2$
+is not a Dirichlet eigenvalue for the Stokes equation on $\Omega$.
+
+From \cref{thrm:rep-theorem} we have 
+  \begin{equation} \label{eq:rep-theorem}
+    \bS_{k} [\bt](\xx) - \bD_{k}[\bu](\xx) = \begin{cases} 
+    \bu(\xx) &\quad \xx \in \Omega \, , \\
+    0 &\quad \xx \in E \; .
+    \end{cases}
+  \end{equation}
+  Suppose that $k^2$ is a Dirichlet eigenvalue for the Stokes equation
+  on $\Omega$ and let $\bu$ denote the corresponding eigenfunction
+  with $\bt^{-}$ the corresponding surface traction on the
+  boundary $\Gamma$.
+  Since $\bu$ is a Dirichlet eigenfunction, the velocity restricted
+  to the boundary, $\bu^{-}$, is $0$. 
+  Using the Green's theorem representation for the pair
+  $(\bu,\bt^{-})$ and evaluating the surface traction
+  using~\cref{lem:jump-conds}, we get
+  \begin{equation}
+    \bt^{-} = (\cDt_{k} + \frac{1}{2} \cI) \bt^{-} \,
+    \implies \left(\cI - 2\cDt_{k} \right) 
+    \bt^{-} = 0 \, .
+  \end{equation}
+  From the above and \cref{lem:nunull,lem:nutracli},
+  we know that $\bt^{-}, \bnu \in \cN(\cI - 2\cDt_{k})$
+  are two linearly independent vectors in the null space.
+  Let $c = \left< \bt^{-},\bnu \right>$. Then, it
+  follows that $\left<\bt^{-} -c \bnu, \bnu \right> = 0$
+  and thus $\cW[\bt^{-} - c\bnu] = 0$. 
   Since $\bt^{-}$ and $\bnu$ are linearly independent, we note that
-$\bt^{-} -c\bnu \neq 0$.
-Combining these results, we get that
+  $\bt^{-} -c\bnu \neq 0$. Combining these results, we get that
   $(\cI - 2\cDt_{k} - 2\cW) (\bt^{-} - c\bnu) = 0$. 
-Since $\bt^{-}-c\bnu$ is non-trivial, and $\cW$ is self-adjoint, 
-it follows from the Fredholm alternative
-that the operator $\cI - 2\cD_{k} - 2\cW$ is also not invertible.
-\end{proof}
-
-On simply connected domains, thus there is a one-to-one correspondance
-between the invertibility of the operator $\cI - 2\cD_{k} - 2\cW$ 
-and the eigenvalues of the Dircihlet problem for Stokes equations. 
-However, on multiply connected domains, this is not the case.
-Whilst, it is true that the operator $\cI -2\cD_{k} -2\cW$ 
-is not invertible when $k$ is the Dircihlet eigenvalue, it turns
-out that the operator is also not invertible when $k$ is 
-an interior Neumann eigenvalue corresponding to one of the obstacle
-regions $\Omega_{i}$, $i\neq 0$.
-The following lemma proves this result for a region with one obstacle
-boundary (the extension to the general case is a straightforward).
-
-\begin{lemma}
-Suppose that $\Omega$ is a multiply connected domain given by the 
-intersection of $\Omega_{0}$ and the exterior of $\Omega_{1}$
+  Since $\bt^{-}-c\bnu$ is non-trivial, and $\cW$ is
+  self-adjoint, it follows from the Fredholm alternative
+  that the operator $\cI - 2\cD_{k} - 2\cW$ is also not
+  invertible.
+\end{proof}
+
+The correspondence result above does not hold on multiply
+connected domains.
+In particular, while the operator $\cI -2\cD_{k} -2\cW$ 
+is indeed not invertible when $k^2$ is a Dirichlet eigenvalue,
+it turns out that the operator is also not
+invertible when $k^2$ is a Neumann eigenvalue
+corresponding to the interior of one of the obstacle regions,
+i.e. one of the $\Omega_{i}$ with $i > 0$. The following theorem
+proves this result for a region with one obstacle;
+the extension to the general case is straightforward.
+
+\begin{thrm}
+  Suppose that $\Omega$ is a multiply connected domain
+  given by the intersection of a domain $\Omega_{0}$
+  and the exterior of a domain $\Omega_{1}$ with
+  $ \bar\Omega_1 \subset \Omega_0$
   (see~\cref{fig:1ply}). 
-Then the operator $\cI - 2\cD_{k} - 2\cW$ has a non-trivial
-null space if $k$ is a Neumann eigenvalue of $\Omega_{1}$.
-\end{lemma}
+  Then, the operator $\cI - 2\cD_{k} - 2\cW$ has a non-trivial
+  null space if $k^2$ is a Neumann eigenvalue of $\Omega_{1}$.
+\end{thrm}
 
@@
 \begin{proof}
-Suppose that $k$ is a Neumann eigenvalue of $\Omega_{1}$. 
-$\tilde{\bu}$ be the eigenmode corresponding to this eigenvalue. 
-Note that $\tilde{\bu}$ is not identically $0$ on the boundary $\Gamma_{1}$
-of $\Omega_{1}$.
+  Suppose that $k^2$ is a Neumann eigenvalue of $\Omega_{1}$.
+  Let $\tilde{\bu}$ be the eigenmode corresponding to $k^2$. 
+  Note that $\tilde{\bu}$ is not identically $0$ on the boundary
+  of $\Omega_{1}$, which we denote by $\Gamma_1$.
   Since $\tilde{\bu}$ is an interior Neumann eigenfunction, we note that
-the surface traction corresponding to the solution $\bt^{-} = 0$
+  the surface traction corresponding to the solution, $\bt^{-}$, is $0$
   on the boundary.
-Applying Green's identity~\cref{thrm:rep-theorem}, to the solution 
-$\tilde{\bu}$ in the interior and taking the interior limit we get
+  Applying \cref{thrm:rep-theorem} to the
+  solution $\tilde{\bu}$ in the interior
+  and taking the interior limit we get
 \begin{equation}
@@
 \end{equation}
-Note that the sign of the $\bD$ in the representation theorem is switched
-since the normal is pointing inwards for the boundary $\Omega_{1}$.
+Note that the sign of the $\bD$ operator in the
+representation theorem is switched since the normal
+is pointing inwards for the boundary $\Omega_{1}$.
 Thus, $\tilde{\bu}$ is a non-trivial null vector of the operator 
@@
 Furthermore since $\tilde{\bu}$ is the boundary data of 
-the solution of the oscillatory Stokes equation in $\Omega_{1}$, we
-get that $\cW^{\Gamma_{1}}[\tilde{\bu}] = 0$.
-Setting $\bmu = \tilde{\bu}$ on $\Gamma_{1}$, and $\bmu = 0$ on $\Gamma_{0}$,
-we obtain a non-trivial null vector for the operator $\cI - 2\cD^{\Gamma}_{k} -2\cW^{\Gamma}$
+the solution of the oscillatory Stokes equation
+in $\Omega_{1}$, we get that $\cW^{\Gamma_{1}}[\tilde{\bu}] = 0$.
+Setting $\bmu = \tilde{\bu}$ on $\Gamma_{1}$, and
+$\bmu = 0$ on $\Gamma_{0}$, we obtain a non-trivial null
+vector for the operator $\cI - 2\cD^{\Gamma}_{k} -2\cW^{\Gamma}$
 on the boundary $\Gamma = \Gamma_{0} \cup \Gamma_{1}$.
@@
 
-As noted in~\cite{zhao2015robust}, this lack of one-to-one correspondance between
+Analogous with the observation in~\cite{zhao2015robust},
+this lack of one-to-one correspondance between
 the invertibility of the integral operator $\cI - 2\cD_{k} - 2\cW$
@@
 which are almost multiply connected.
-We demonstrate this issue numerically in~\cref{sec:numanalysis-nearly-mult-con}.
-
-\subsubsection{Mixed layer potential representation}
+We demonstrate this issue numerically
+in~\cref{sec:numanalysis-nearly-mult-con}.
+
+\subsubsection{Dirichlet eigenvalues --- combined-field representation}
 \label{subsec:mixedanalysis}
-The non-robustness of the double layer potential representation
-for computing the Dirichlet eigenvalues of Stokes equation can be remdied
-by the standard approach of using the mixed layer potential representation,
-i.e. setting
-$\bu = (\bD_{k} + i\eta \bS_{k})
-\bmu$, 
-where $\bmu$ is the unknown density to be solved for, and $\eta \in \mathbb{R}^{+}$ 
-On imposing the boundary conditions and using~\cref{lem:jump-conds}, 
-we obtain the following integral equation on the boundary 
-\begin{equation}
-(\cI - 2\cD_{k} - 2i\eta \cS_{k}) \bmu = -2 \ff \, . 
-\end{equation}
-As noted in~\cref{subsubsec:nullspacecorr}, this integral equation 
-is also rank-deficient, and we instead use the following 
-equivalent integral equation for $\bmu$,
+
+The non-robustness in using the double layer
+potential representation observed above can be
+remedied by using a combined-field, or mixed layer potential,
+representation, i.e. setting $\bu = (\bD_{k} + i\eta \bS_{k})
+\bmu$, with $\eta$ real and positive.
+Imposing the Dirichlet boundary condition
+and using~\cref{lem:jump-conds}, we obtain 
+\begin{equation}
+  (\cI - 2\cD_{k} - 2i\eta \cS_{k}) \bmu = -2 \ff \,
+  \textrm{ on } \Gamma. 
+\end{equation}
+As with the double layer representation, this
+integral equation is rank deficient for any $k$.
+Instead, we consider
 \begin{equation}
@@
 
-We now prove that for any bounded region $\Omega$ (simply or multiply
-connected) with $C^{2}$ boundaries, there exists a one-to-one correspondance
-between the invertibility of the operator
-$\cI - 2\cD_{k} - 2i\eta \cS_{k} - 2\cW$ and the Dirichlet eigenvalues
-of the Stokes operator on $\Omega$.
+We now prove that for any bounded region $\Omega$
+(simply or multiply connected) with $C^{2}$ boundaries,
+there exists a one-to-one correspondence between the
+invertibility of the operator $\cI - 2\cD_{k}
+- 2i\eta \cS_{k} - 2\cW$ and the Dirichlet eigenvalues.
 
@@
   \label{thm:cfmain}
-Suppose $\Omega$ is a bounded region defined by the intersection of a 
-simply connected domain $\Omega_{0}$ and the exteriors of a finite collection
-of bounded simply connected domains $\{ \Omega_{i} \}_{i=1}^{m}$.
-As before let $\Gamma_{i}$ denote the boundary of $\Omega_{i}$ and let
-$\Gamma = \cup_{i=0}^{m} \Gamma_{i}$ denote the boundary of $\Omega$.
-Then the operator $\cI - 2\cD_{k} - 2i\eta \cS_{k} - 2\cW$
-is invertible if and only if $k$ is not a Dirichlet eigenvalue
-for the Stokes operator on $\Omega$.
+  Suppose $\Omega$ is a bounded region defined
+  by the intersection of a simply connected domain $\Omega_{0}$
+  and the exteriors of a finite collection bounded simply
+  connected domains $\{ \Omega_{i} \}_{i=1}^{m}$. As above,
+  let $\Gamma_{i}$ denote the boundary of $\Omega_{i}$ and let
+  $\Gamma = \cup_{i=0}^{m} \Gamma_{i}$ denote the boundary of
+  $\Omega$. Then, the operator $\cI - 2\cD_{k} - 2i\eta \cS_{k}
+  - 2\cW$ is invertible if and only if $k^2$ is not a Dirichlet
+  eigenvalue for the Stokes operator on $\Omega$.
 \end{thrm}
@@
 \begin{proof}
-Suppose that $k$ is not a Dirichlet eigenvalue for Stokes equation on
-$\Omega$. 
-Suppose further that $\bmu$ satisfies
-\begin{equation}
-(\cI - 2\cD_{k} -2i\eta\cS_{k} - 2\cW) \bmu = 0 \, , \label{eq:mlproofrep}
+  Suppose that $k^2$ is not a Dirichlet eigenvalue for the
+  Stokes equation on $\Omega$. Suppose further that $\bmu$ satisfies
+  \begin{equation}
+    (\cI - 2\cD_{k} -2i\eta\cS_{k} - 2\cW) \bmu = 0 \, ,
+    \label{eq:mlproofrep}
   \end{equation}
@@
 \end{equation}
-Suppose now $\bu = -2\bD_{k}[\bmu] -2i\eta\bS_{k}[\bmu]$ in $\Omega$.
-Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
-and applying~\cref{lem:jump-conds}, we get that the interior
-limit of the velocity $\bu^{-} = (\cI - 2\cD_{k} -2i\eta\cS_{k}) \bmu = 0$ on $\Gamma$. 
-Since $k$ is not a Dirichlet eigenvalue for the Stokes equation on 
-$\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
-This in particular implies that the interior limit of the surface traction
-denoted by $\bt^{-} = 0$ on $\Gamma$.
-Using~\cref{lem:jump-conds}  
-we observe that the exterior limit 
-of the surface traction is $\bt^{+} = i\eta \bmu(\xx)$
-and the exterior limit of the velocity is 
-$\bu^{+} = \bmu(\xx)$ on $\Gamma$.
+Suppose now $\bu = -2\bD_{k}[\bmu] -2i\eta\bS_{k}[\bmu]$
+in $\Omega$. Then $\bu$ is a solution to the oscillatory
+Stokes equation in $\Omega$, and applying~\cref{lem:jump-conds},
+we get that the interior limit of the velocity
+$\bu^{-} = (\cI - 2\cD_{k} -2i\eta\cS_{k}) \bmu = 0$ on $\Gamma$.
+Since $k^2$ is not a Dirichlet eigenvalue for the Stokes equation
+on $\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
+This in particular implies that the interior limit of the
+surface traction, denoted by $\bt^{-}$, is $0$ on $\Gamma$.
+Using~\cref{lem:jump-conds} we observe that $\bt^{+}
+= i\eta \bmu(\xx)$ and $\bu^{+} = \bmu(\xx)$ on $\Gamma$.
 \begin{remark}
-Note that there is a slight abuse of notation here for the obstacle
-boundaries, since the exterior limit with respect to $\Omega$ 
+  Note that there is potential for confusion here
+  in that the exterior limit with respect to $\Omega$ 
   for the boundary $\Gamma_{j}$ is the traditional interior 
@@
 We first show that $\bmu=0$ on $\Gamma_{0}$. 
-To this end, note that $\bu$ is a radiating solution of the oscillatory
-Stokes equation in the exterior $E$,
-since $\cW[\bmu] = 0$ implies that $\int_{\Gamma} \bmu \cdot \bnu = 0$. 
-From uniqueness of the impedance problem in the exterior $E$, we conclude
-that $\bu \equiv 0$ in $E$ as well, which in particular implies that
-the exterior limit of the velocity $\bu^{+}=0$ on $\Gamma_{0}$.   
-Using the jump conditions in~\cref{lem:jump-conds} again, we
-get that $\bmu = \frac{1}{2}(\bu^{+} - \bu^{-}) = 0$ \, on
-$\Gamma_{0}$. 
-To show that $\bmu=0$ on $\Gamma_{j}$, we observe that
-$\bmu$ is also a solution to the oscillatory Stokes equation
-in each of the obstacles $\Omega_{j}$ as well.
-Applying Green's identity and using the fact that 
-the interior limits with respect to $\Omega_{j}$ (see remark)
+To this end, note that $\bu$ is a radiating solution
+of the oscillatory Stokes equation in the exterior $E$,
+since $\cW[\bmu] = 0$ implies that $\int_{\Gamma} \bmu
+\cdot \bnu = 0$. From the uniqueness of the impedance problem
+in the exterior $E_0$ of $\Omega_0$, we conclude that
+$\bu \equiv 0$ in $E_0$ as well, which in particular
+implies that $\bu^{+}=0$ on $\Gamma_{0}$.   
+Using the jump conditions in~\cref{lem:jump-conds}
+again, we get that
+$\bmu = \frac{1}{2}(\bu^{+} - \bu^{-}) = 0$ on
+$\Gamma_{0}$. To show that $\bmu=0$ on
+$\Gamma_{j}$, we observe that $\bu$ is also a
+solution to the oscillatory Stokes equation in each
+of the obstacles $\Omega_{j}$.
+Applying the energy-type identity \cref{eq:greenlike}
+and using the fact that 
+the interior limits with respect to $\Omega_{j}$
 of the surface traction and the velocity
@@
 \end{equation}
-Taking the imaginary part of the above equation, we get
+Taking the imaginary part of the above equation,
+we get
 \begin{equation}
@@
 \end{equation}
-Since $\text{Re}(\eta)>0$, this implies that $\bmu=0$ for $\xx \in \Gamma_{j}$, $j=1,2,\ldots m$. 
-Thus $\cI - 2\cD_{k} -2i\eta\cS_{k} -2\cW$ is invertible when $k$ 
-is not a Dirichlet eigenvalue for the Stokes equation on $\Omega$.
-
-From Green's representation for the oscillatory Stokes equation, 
-we know that 
+Since $\text{Re}(\eta)>0$, this implies that
+$\bmu=0$ for $\xx \in \Gamma_{j}$, $j=1,2,\ldots m$. 
+Thus, $\cI - 2\cD_{k} -2i\eta\cS_{k} -2\cW$ is
+invertible when $k^2$ is not a Dirichlet eigenvalue
+for the Stokes equation on $\Omega$.
+
+From \cref{thrm:rep-theorem}, we have 
 \begin{equation} \label{eq:rep-theorem}
@@
   \end{equation}
-Suppose that $k$ is Dirichlet eigenvalue for the Stokes equation on $\Omega$
-and let $\bu$ denote the corresponding eigenfunction and let $\bt$ denote
-the surface traction associated with the eigenfunction.
-Note that the Green's representation theorem implies that 
-$\cS_{k}[\bt^{-}] = 0$, since $\bu^{-}=0$ on $\Gamma$. 
-Applying the Green's theorem to the pair $\bt^{-}, \bu^{-}$ and taking 
-its derivative on $\Gamma$ using~\cref{lem:jump-conds}, we get
+Suppose that $k^2$ is Dirichlet eigenvalue for
+the Stokes equation on $\Omega$ and let $\bu$
+denote the corresponding eigenfunction and $\bt$ denote
+its surface traction. Note that \cref{thrm:rep-theorem}
+implies that $\cS_{k}[\bt^{-}] = 0$, since
+$\bu^{-}=0$ on $\Gamma$. Applying \cref{thrm:rep-theorem}
+to the pair $\bt^{-}, \bu^{-}$ and evaluating the
+traction on $\Gamma$ using~\cref{lem:jump-conds},
+we get
 \begin{equation}
@@
 \end{equation}
-As in the proof of~\cref{thm:dlmain}, letting $c = \left< \bt^{-} ,\bnu \right>$, 
-it follows that
-\begin{equation}
-(-\cI - 2\cD_{k} - 2i \eta \cS_{k} - 2\cW) (\bt^{-} - c\bnu) = 0 \, ,
+As in the proof of~\cref{thm:dlmain}, letting
+$c = \left< \bt^{-} ,\bnu \right>$, it follows that
+\begin{equation}
+  (-\cI - 2\cD_{k} - 2i \eta \cS_{k} - 2\cW)
+  (\bt^{-} - c\bnu) = 0 \, ,
 \end{equation}
 where $\bt^{-} - c\bnu \neq 0$.
-Since $\bt^{-} - c\bnu$ is non-trivial, and $i\eta \cS_{k}, \cW$ are self-adjoint ($i\eta \cS_{k}$ 
-is self-adjoint since we consider inner products without conjugation), 
+Since $\bt^{-} - c\bnu$ is non-trivial and both
+$i\eta \cS_{k}$ and $\cW$ are self-adjoint with respect
+to the bilinear form \cref{eq:bi_form},
 it follows from the Fredholm alternative
-that the operator $\cI - 2\cD(k) -2i\eta \cS - 2\cW$ is also not invertible.
+that the operator $\cI - 2\cDk -2i\eta \cSk - 2\cW$
+is also not invertible.
 \end{proof}
@@
 \subsection{Fredholm determinants}
-Having established the equivalence between the Dirichlet eigenvalues
-for Stokes equation and the invertibility of
-the operator $\cI - 2\cD_{k} - 2\cW$ on simply connected domains, in this section
-we show how the Fredholm determinant can be as a computational tool for detecting
-the non-invertibility of $\cI - 2\cD_{k} - 2\cW$.
+\label{sec:dets}
+Above, we established the correspondence between
+the non-invertibility of certain integral equations
+and Stokes eigenvalues. In this section, we show
+how the Fredholm determinant can be used
+as a computational tool for detecting the
+non-invertibility of $\cI - 2\cD_{k} - 2\cW$.
+The arguments here follow the structure of the
+analogous arguments in~\cite{zhao2015robust}
+for Laplace eigenvalues.
 
 Let $\cJ_{1}(X)$ denote the space of trace class operators 
-on $X$, where $X$ is a Hilbert space.
-$\cJ_{1}$ is a subspace of compact operators on $X$.
-Suppose that $A$ is a compact operator, with eigenvalues
-$\lambda_{i}, i\in \mathbb{N}$.
-Then the operator $A \in \cJ_{1}(X)$ if
+on $X$, where $X$ is a Hilbert space, which is a
+subspace of the space of compact operators on $X$.
+A compact operator $\cA$ with eigenvalues
+$\lambda_{i}, i\in \mathbb{N}$ is in $\cJ_{1}(X)$ if
 $\sum_{i} |\lambda_{i}| < \infty$.
-If $A$, is a trace class operator, then  
-the Fredholm determinant of the operator $\cI + A$ is defined as
-\begin{equation}
-\text{det}(\cI +A) = \prod_{i=1}^{\infty} (1+\lambda_{i}) \, .
-\end{equation}
-It follows from standard results in complex analysis, 
-that the Fredholm determinant is finite and well-defined if 
-$\text{det}(\cI+A) < \infty$ if $\sum_{i} |\lambda_{i}| < \infty$,
-i.e. if $A$ is in trace class.
-
-The following lemma shows that the operator 
-$-2\cD_{k} - 2\cW$ is a trace class operator.
+If $\cA$, is a trace class operator, then  
+the Fredholm determinant of the operator $\cI + \cA$
+is defined by
+\begin{equation}
+\text{det}(\cI +\cA) = \prod_{i=1}^{\infty} (1+\lambda_{i}) \, .
+\end{equation}
+%It follows from standard results in complex
+%analysis, that the Fredholm determinant is finite and well-defined if 
+%$\text{det}(\cI+A) < \infty$ if $\sum_{i} |\lambda_{i}| < \infty$,
+%i.e. if $A$ is in trace class.
+
+The operator $-2\cD_{k} - 2\cW$ is trace class:
 \begin{lemma}
-$-2\cD_{k} - 2\cW$ is a trace class operator for all $k$ 
+  Suppose that $\Gamma$ is a $C^2$ curve.
+  Then, $-2\cD_{k} - 2\cW \in \cJ_1(L_2(\Gamma)\otimes L_2(\Gamma))$
+  for all $k$ 
 \end{lemma}
@@
 Using Bessel function asymptotics, we note that the
-kernel of $\cD_{k}$ given by
-$\TT_{\cdot,\cdot,\ell}\nu_{\ell}(\bx,\by)$
-has a leading order singularity of $|\bx-\by|^2 \log{|\bx-\by|^2}$ as $\bx\to \by$.
-It follows from~\cite{bornemann2010numerical} numerical that $\cD_{k}$
+kernel of $\cD_{k}$ given by $\TT_{\cdot,\cdot,\ell}\nu_{\ell}(\bx,\by)$
+has a leading order singularity of
+$|\bx-\by|^2 \log{|\bx-\by|^2}$ as $\bx\to \by$.
+It follows from the criteria listed
+in~\cite[Sec. 2]{bornemann2010numerical} that $\cD_{k}$
 is a trace-class operator for all $k$.
-Since $\cW$ is a rank-one perturbation independent of $k$, and trace-class
-operators are a vector space, we conclude that
-$-2\cD_{k} - 2\cW$ is also a trace-class operator for all $k$.
+Since $\cW$ is a rank-one perturbation independent of $k$,
+and trace-class operators are a vector space, we conclude
+that $-2\cD_{k} - 2\cW$ is also a trace-class operator for
+all $k$.
 \end{proof}
@@
 Let $f(k) = \text{det}(\cI - 2\cD_{k} - 2\cW)$.
-We first note that $f(k)$ is an analytic function of $k$
-for $k \in \mathbb{C} \setminus 0$
-since the kernel of $\cD_{k}$ is an 
-analytic function of $k$ on that domain, 
+First, note that $f(k)$ is an analytic function of $k$
+for $k \in \mathbb{C} \setminus 0$, since the kernel
+of $\cD_{k}$ is an analytic function of $k$ on that domain, 
 and the Fredholm determinant is an analytic operator.
 
-The Fredholm determinant of a second-kind Fredholm operator
-is another way of detecting when the operator is not invertible. 
-The following result summarizes the result. 
-\begin{lemma}
-$f(k) = 0$ if and only if $\cI - 2\cD_{k} -2\cW$ 
-is not invertible.
-\end{lemma}
-\begin{proof}
-The proof is standard and see for example~\cite{simon2005trace}, page 34.
-\end{proof}
-
-When $\Omega$ is simply connected, the above lemma combined 
-with~\cref{thm:dlmain} implies $f(k) = 0$ if and only if $k$ 
-is a Dirichlet eigenvalue for Stokes equation.
-
-We now show how this fact can be used numerically
-to estimate the Dirichlet eigenvalues.
+The zeros of the Fredholm determinant indicate when the
+operator is not invertible. 
+This is summarized as 
+\begin{lem} \label{lem:detzeros}
+  With $f(k)$ defined as above, $f(k) = 0$ if and only if
+  $\cI - 2\cD_{k} -2\cW$ is not invertible.
+\end{lem}
+\begin{proof}
+  The proof is standard; see, for example,
+  \cite[p. 34]{simon2005trace}.
+\end{proof}
+
+When $\Omega$ is simply connected, \cref{lem:detzeros} and 
+\cref{thm:dlmain} together imply that $f(k) = 0$
+if and only if $k^2$ 
+is a Dirichlet eigenvalue of the Stokes equation.
+This reduces the problem of finding eigenvalues to
+finding the roots of an analytic function.
+
+We now show how this fact can be used to numerically
+estimate the Dirichlet eigenvalues.
 Suppose that $M_{k}^{N}$ is a Nystr\"{o}m discretization 
@@
 for computing the Laplace eigenvalues on regions with 
-analytic boundaries, when the integral
-operators are discretized using Kress-quadrature~\cite{kress1991boundary},
+analytic boundaries, when the integral operators are
+discretized using Kress quadrature, see~\cite{kress1991boundary},
 the determinant of the Nystr\"{o}m discretized operators
-at the true eigenvalues converge to $0$ exponentially in $N$.
-Thus, if the eigenvalues have multiplicity $1$, i.e. the
-derivative of the determinant is non-zero at the true-eigenvalues,
-then the analyticity of the discretized determinant implies
-that the zeros of the determinant of the Nystr\"{o}m 
-discretization of the linear operator converge
-exponentially to the true Dirichlet eigenvalues for Laplace's equation.
-
-The proof presented in~\cite{zhao2015robust} carries forward
-for computing the Dirichlet eigenvalues of Stokes equation as well.
-We summarize the result in the following theorem.
+at the true eigenvalues converge to $0$ exponentially
+in $N$.
+Thus, if the eigenvalues have multiplicity $1$,
+i.e. the derivative of the determinant is non-zero
+at the true-eigenvalues, then the analyticity of the
+discretized determinant implies that the zeros
+of the determinant of the Nystr\"{o}m discretization
+of the linear operator converge exponentially to
+the true Dirichlet eigenvalues for Laplace's equation.
+
+The proof presented in~\cite{zhao2015robust} carries
+forward for computing the Dirichlet eigenvalues of
+Stokes equation as well.
+We summarize the result as
 \begin{thrm}
 \label{thm:mainconvfreddet}
-Suppose that $\Omega$ is a simply connected domain with an analytic boundary.
-Let $k_{j}$, $j=1,2,\ldots M$ denote all the Dirichlet eigenvalues of Stokes
-equation on $\Omega$ contained in the interval $[a,b]$. 
+Suppose that $\Omega$ is a simply connected
+domain with an analytic boundary. Let $k_{j}^2$, $j=1,2,\ldots M$
+denote all the Dirichlet eigenvalues of Stokes equation
+on $\Omega$ contained in the interval $[a,b]$. 
 Suppose further that all the eigenvalues have multiplicity $1$.
@@
 quadrature.
-Then $f^{N}(k)$ has exactly $M$ zeros on the interval $[a,b]$. 
+Then $f^{N}(k)$ has exactly $M$ zeros on the interval $[a,b]$
+\note{Manas: for sufficiently large $N$?}. 
 Let $\omega_{j}$, $j=1,2\ldots M$ denote the zeros of $f^{N}$.
@@
 \begin{proof}
-The proof follows from small modificiations of the proofs contained in~\cite{zhao2015robust}. 
-\end{proof}
-
-In practice, using Kress-quadrature for large problems is problematic owing to the global
+  The proof follows from small modificiations of the
+  proofs contained in~\cite{zhao2015robust}. 
+\end{proof}
+
+\begin{remark}
+In practice, using Kress-quadrature for large
+problems is problematic owing to the global
 nature of the quadrature rule.
-The coupling with fast direct solvers for computing determinants also results in $O(N^2 \log{N})$ 
+%
+\note{Manas: I do not understand the $O(N)$ cost per matrix entry
+  described here in the fast-direct case ... does it somehow
+  screw up compression?}
+Coupling with fast direct solvers for computing determinants also results in $O(N^2 \log{N})$ 
 determinant evaluation since evaluating each matrix entry costs $O(N)$, where 
@@
 We leave a proof of this to future work.
+\end{remark}
 
@@
 Fredholm determinant divergers logarithmically. 
-In~\cref{subsec:convannulus}, we demonstrate that this fact
-numerically on the annulus, where the eigenvalues are analytically known. 
+In~\cref{subsec:convannulus}, we demonstrate this fact
+numerically on the annulus, where the eigenvalues are
+analytically known. 
 \end{remark}

### 2019-03-20 doc/draft-01-stokes/04numerical.tex
update paper, add to intro, clean up theory section

\section{Numerical Results}
\label{sec:numerical}

### 2019-03-21 doc/draft-01-stokes/01intro.tex
add files needed for latest tests

@@
 perspective, because such operators are never invertible
-(though, they are injective precisely when $k^2$ is an
+(though, they are not injective precisely when $k^2$ is an
 eigenvalue \cite{kitahara2014boundary,antunes2011buckling})

### 2019-03-21 doc/draft-01-stokes/02prelim.tex
add files needed for latest tests

@@
 
-Let $X$ be a Banach space equipped with a bilinear form ...
+We first recall some definitions.
+Let $X$ and $Y$ be Banach spaces with a non-degenerate
+bilinear form $\langle \cdot ,\cdot \rangle: X\times Y \to \C$.
+\begin{itemize}
+\item Two operators $\cA:X\to X$ and $\cB:Y\to Y$ are
+adjoint operators if
+$\langle A \phi,\psi \rangle = \langle \phi, B\psi \rangle$
+for every $\phi \in X$ and $\psi \in Y$.
+\item For an operator $\cM:X\to X$, we can define the range
+  $R(\cM)$ as the set $\{\phi \in X: \exists \phi_0 \textrm{ with }
+  \cM\phi_0 = \phi\}$ and the null space $N(\cM)$ as the
+  set $\{\phi \in X: \cM \phi = 0 \}$.
+\item An operator $\cA$ is said to be compact if
+  $\overbar{\cA V}$ is a compact set for any
 
-\note{Travis: put Fredholm alternative here}
+\item Given a subspace $V\subset X$,
+  we can define the subspace $V^\perp\subset Y$ as the
+  set $V^\perp = \{ \psi \in Y: \langle \phi,\psi \rangle = 0
+  \textrm{ for each } \phi \in V \}$, with the analogous
+  definition for subspaces of $Y$.
+\end{itemize}
+
+Operators of the form $\cI-\cA$
+have existence and uniqueness properties analogous to
+matrices. This is known as the Fredholm Alternative;
+we present the version provided in \cite{colton1983integral}.
+
+\begin{thrm}[Fredholm Alternative \cite{colton1983integral}]
+  Let $X$ and $Y$ be Banach spaces and
+  $\langle \cdot,\cdot \rangle: X\times Y \to \C$ be
+  a bilinear form. Suppose that $\cA: X\to X$ and
+  $\cB:Y \to Y$ are compact adjoint operators. Then
+  $\dim N(\cI-\cA) = \dim N(\cI-\cB) \in \N$,
+  $R(\cI-\cA) = N(\cI-\cB)^{\perp}$, and
+  $R(\cI-\cB) = N(\cI-\cA)^\perp$.
+\end{thrm}
 
@@
 
+\begin{lem} \label{lem:compact-sd}
+  Suppose that $\Omega$ is a bounded region with a $C^{2}$ boundary
+  $\Gamma$. Then the operators $\cS$ and $\cD$ defined
+  above are compact.
+\end{lem}
+
+Compactness is proved by considering the
+asymptotic expansion of each kernel about
+$\xx=\yy$ and noting that each is at most
+weakly singular.
+
 \subsubsection{Representation Theorem}

### 2019-03-21 matlab/src/circle.m

@@ -1,0 +1,34 @@
+
+function [fvals] = circle(t,varargin)
+
+r = 1.0;
+x0 = 0.0;
+y0 = 0.0;
+if nargin > 1
+    r = varargin{1};
+end
+if nargin > 2
+    ctr = varargin{2};
+    x0 = ctr(1); y0 = ctr(2);
+end
+
+
+ct = cos(t);
+st = sin(t);
+
+xs = x0+r*ct;
+ys = y0+r*st;
+dxs = -r*st;
+dys = r*ct;
+d2xs = -r*ct;
+d2ys = -r*st;
+
+fvals(:,1) = xs;
+fvals(:,2) = ys;
+fvals(:,3) = dxs;
+fvals(:,4) = dys;
+fvals(:,5) = d2xs;
+fvals(:,6) = d2ys;
+
+end
+

### 2019-03-21 matlab/src/crescent.m

@@ -1,0 +1,25 @@
+
+function [fvalsp] = crescent(t)
+%CRESCENT polar parametric description of a crescent shape
+%r(s) = 0.2/(1+exp (4(s−3π/2)(s−π/2))) + 0.4, θ(s) = −49/50 π sin s
+
+et = exp(4*(t-3*pi/2.0).*(t-pi/2.0));
+r = 0.2./(1+et) + 0.4;
+dr = 8.0*et.*(pi-t)./(5.0*(1+et).^2);
+d2r = (8*et.*( -8*t.^2 + et.*(8*t.^2 - 16*pi*t + 8*pi^2 - 1) + 16*pi*t ...
+    - 8*pi^2 - 1))./(5*(et + 1).^3);
+
+
+th = -49.0/50.0*pi*sin(t);
+dth = -49.0/50.0*pi*cos(t);
+d2th = 49.0/50.0*pi*sin(t);
+
+fvalsp(:,1) = r;
+fvalsp(:,2) = th;
+fvalsp(:,3) = dr;
+fvalsp(:,4) = dth;
+fvalsp(:,5) = d2r;
+fvalsp(:,6) = d2th;
+
+end
+

### 2019-03-21 matlab/src/find_unique_evals.m

@@ -1,0 +1,23 @@
+function iplot = find_unique_evals(rts,sings,abs_eps,imag_eps)
+%FIND_UNIQUE_EVALS returns indices corresponding to the roots 
+% which seem like they correspond to unique eigenvalues to the
+% desired precision
+%
+
+[~,isort] = sort(real(rts));
+iplot1 = isort(abs(imag(rts(isort))) < imag_eps);
+
+if length(iplot1) < 2
+    iplot = iplot1;
+else
+    diffs = diff(rts(iplot1));
+    iremove = find(abs(diffs) < abs_eps);
+    iremover = iplot1( iremove(sings(iplot1(iremove))<sings(iplot1(iremove+1))));
+    iremovel = iplot1( iremove(sings(iplot1(iremove))>= sings(iplot1(iremove+1)))+1);
+    iplot = setdiff(iplot1(:),[iremover(:);iremovel(:)]);
+    [~,isort] = sort(real(rts(iplot)));
+    iplot = iplot(isort);
+end
+
+
+

### 2019-03-21 matlab/src/polarparam.m

@@ -1,0 +1,27 @@
+
+function [fvals] = polarparam(t,polarfun)
+
+fvalspolar = polarfun(t);
+r = fvalspolar(:,1); th = fvalspolar(:,2); 
+dr = fvalspolar(:,3); dth = fvalspolar(:,4);
+d2r = fvalspolar(:,5); d2th = fvalspolar(:,6);
+
+cth = cos(th);
+sth = sin(th);
+
+xs = r.*cth;
+ys = r.*sth;
+dxs = -r.*sth.*dth+dr.*cth;
+dys = r.*cth.*dth+dr.*sth;
+d2xs = -r.*cth.*dth.^2-r.*sth.*d2th-dr.*sth.*dth-dr.*sth.*dth+d2r.*cth;
+d2ys = -r.*sth.*dth.^2+r.*cth.*d2th+dr.*cth.*dth+dr.*cth.*dth+d2r.*sth;
+
+fvals(:,1) = xs;
+fvals(:,2) = ys;
+fvals(:,3) = dxs;
+fvals(:,4) = dys;
+fvals(:,5) = d2xs;
+fvals(:,6) = d2ys;
+
+end
+

### 2019-03-21 matlab/src/rskelf_nullvec.m

@@ -1,0 +1,28 @@
+
+function xnull = rskelf_nullvec(F,nsys,restart,tol,maxit,nref)
+%RSKELF_NULLVEC find nullvec with cheap randomized method
+%
+% (F + u*v.')x = u
+%
+
+ur = randn(nsys,1);
+vr = randn(nsys,1);
+
+xnull = gmres(@(x) rskelf_plus_mv(x,F,ur,vr),ur,restart,tol,maxit);
+
+xnull = xnull/norm(xnull);
+for i = 1:nref
+   xnull = rskelf_sv(F,xnull,'T');
+   xnull = rskelf_sv(F,xnull);
+   xnull = xnull/norm(xnull);
+end
+
+end
+
+
+function y = rskelf_plus_mv(x,F,u,v)
+
+y = rskelf_mv(F,x);
+y = y+u*v.'*x;
+
+end

### 2019-03-22 doc/draft-01-stokes/03analysis.tex
update text, fix some typos
add figures

@@
 
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.4\textwidth]{media/ext_dom}
+  \caption{Example of an exterior domain with four obstacles.}
+  \label{fig:ext_dom}
+  \end{center}
+\end{figure}
+
 Let $\Omega$ be the union of a finite collection of
@@
 and let $E = \R^{2} \setminus \bar{\Omega}$ denote its
-exterior.
+exterior; see \cref{fig:ext_dom} for an example with $m=4$.
 %
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.4\textwidth]{media/mc_dom}
+\end{center}
+\caption{Example of a multiply connected domain with four obstacles.}
+\label{fig:mc_dom}
+\end{figure}
+
 In this section, we establish the correspondence between
@@
 simply connected domains $\{ \Omega_i \}_{i=1}^m$
-whose closures are contained in $\Omega_0$. Note that the
+whose closures are contained in $\Omega_0$;
+see \cref{fig:mc_dom} for an example with four inclusions.
+Note that the
 exterior of $\Omega$, which we denote by $E$, is the
@@
 From \cref{thrm:rep-theorem} we have 
-  \begin{equation} \label{eq:rep-theorem}
+  \begin{equation} 
     \bS_{k} [\bt](\xx) - \bD_{k}[\bu](\xx) = \begin{cases} 
@@
   given by the intersection of a domain $\Omega_{0}$
-  and the exterior of a domain $\Omega_{1}$ with
-  $ \bar\Omega_1 \subset \Omega_0$
-  (see~\cref{fig:1ply}). 
+  and the exterior of a single domain $\Omega_{1}$ with
+  $ \bar\Omega_1 \subset \Omega_0$.
   Then, the operator $\cI - 2\cD_{k} - 2\cW$ has a non-trivial
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.3\linewidth]{media/multiply_final}
-\end{center}
-\caption{Example of a multiply connected domain with one obstacle.}
-\label{fig:1ply}
-\end{figure}
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=0.3\linewidth]{media/multiply_final}
+%\end{center}
+%\caption{Example of a multiply connected domain with one obstacle.}
+%\label{fig:1ply}
+%\end{figure}
 
@@
 
+The spurious eigenvalues of the operator $\cI-2\cDk-2\cW$
+are demonstrated in \cref{subsec:spurannulus} on an annulus,
+where both the true and spurious eigenvalues can be
+determined semi-analytically. 
 Analogous with the observation in~\cite{zhao2015robust},
@@
 and the Dirichlet eigenvalues of the Stokes operator on multiply
-connected domains causes non-robustness and introduces near 
+connected domains also causes non-robustness and introduces near 
 resonanaces for simply connected domains
@@
 We demonstrate this issue numerically
-in~\cref{sec:numanalysis-nearly-mult-con}.
+in~\cref{subsec:crescent}.
 
@@
 From \cref{thrm:rep-theorem}, we have 
-\begin{equation} \label{eq:rep-theorem}
+\begin{equation} 
   \bS [\bt](\xx) - \bD[\bu](\xx) = \begin{cases} 
@@
 \begin{equation}
-(-\cI - 2\cD_{k} -2i\eta \cS_{k}) \bt^{-} = 0 \, .
+(\cI - 2\cDkt -2i\eta \cS_{k}) \bt^{-} = 0 \, .
 \end{equation}
@@
 \begin{equation}
-  (-\cI - 2\cD_{k} - 2i \eta \cS_{k} - 2\cW)
+  (\cI - 2\cDkt - 2i \eta \cS_{k} - 2\cW)
   (\bt^{-} - c\bnu) = 0 \, ,

### 2019-03-24 doc/draft-01-stokes/01intro.tex
Updating paper

--- 2019-03-20 doc/draft-01-stokes/01intro.tex
@@
 %
-The Stokes eigenvalue problem seeks
+The Stokes eigenvalue problem is to find
 values $k^2$ such that
@@
   kelliher2009eigenvalues,antunes2011buckling},
-particularly as they relate to the eigenvalues and
+particularly how they relate to the eigenvalues and
 eigenfunctions of the drum.
@@
 estimating the eigenvalues on domains of practical
-interest and for exploring open conjectures
-and generating new conjectures.
+interest and for exploring open conjectures.
 
@@
 %
-Type A
-methods perform a direct discretization of the
+The first class of methods
+directly discretize the
 Stokes operator, typically with a
@@
 %
-Type B
-methods utilize a boundary integral equation
-(BIE) re-formulation of the oscillatory Stokes
-equation which is then discretized, so that
-the eigenvalues are found by a nonlinear search
-for the values of $k$ where the BIE is not invertible.
+The second class of methods reformulate the 
+oscillatory Stokes equations as a boundary integral
+equations which are discretized.
+The eigenvalues are then found
+by a nonlinear search for the values of $k$ where the BIE 
+is not invertible.
 %
 
-There is a large body of research on type A methods
+There is a large body of research on the first class of methods
 for the Stokes eigenvalue problem.
@@
 
-As noted in~\cite{zhao2015robust}, the type B
-methods provide some advantages.
+As noted in~\cite{zhao2015robust}, integral equation based
+methods provide several advantages.
 %
@@
 show how to alleviate some of the costliness of the
-nonlinear optimization introduced by a type B method.
+nonlinear optimization introduced by formulating the 
+problem as an integral equation.
 %
@@
 \cite{zhao2015robust} for the drum problem in mind,
-we develop a type B method for the Stokes eigenvalue
+we develop an integral equation based method for the Stokes eigenvalue
 problem.
@@
 
-While type B methods for the
+While integral equation based methods for the
 related ``buckling'' eigenvalue problem
@@
 This is unsatisfying from a theoretical
-perspective, because such operators are never invertible
-(though, they are injective precisely when $k^2$ is an
+perspective, because such operators are never \note{Travis: why is this the case?} 
+invertible
+(though, they are not injective precisely when $k^2$ is an
 eigenvalue \cite{kitahara2014boundary,antunes2011buckling})
@@
 Then, in \cref{sec:analysis}, we develop the necessary
-theory for proving \cref{thm:dlmain,thm:cfmain},
+theory for proving the main results of this work 
+(\cref{thm:dlmain,thm:cfmain}),
 which show that the BIEs resulting from these

### 2019-03-24 doc/draft-01-stokes/02prelim.tex
Updating paper

@@
 operators on Banach spaces, with $\mathcal{I}$ denoting the
-identity.
+identity. Given a set $X$, we denote the closure of $X$
+by $\overline{X}$.
 
@@
 We seek solutions of \cref{eq:ostokes} in the space
-\note{make sure this is the correct space}
+\note{make sure this is the correct space: (MR - looks good to me)}
 \begin{equation}
@@
 \end{equation}
-where $\Omega$ is an open domain and $\bar{\Omega}$ denotes
-its closure.
+where $\Omega$ is an open domain.
 
@@
 \begin{equation}
-  \mathcal{L}_x \int_{\R^2} G(\xx,\yy) f(\yy) \, dy = f(\xx) \; .
+  \mathcal{L}_x \int_{\R^2} G(\xx,\yy) f(\yy) \, d \by = f(\xx) \; .
   \nonumber
@@
 We consider here
-``free-space'' Green's functions, i.e. fundamental solutions which satisfy
+free-space Green's functions, i.e. fundamental solutions which satisfy
 radiation conditions as $|\xx-\yy| \to \infty$.
@@
 \item An operator $\cA$ is said to be compact if
-  $\overbar{\cA V}$ is a compact set for any
-
+  $\overline{\cA V}$ is a compact set for any
+  bounded subset $V\subset X$.
 \item Given a subspace $V\subset X$,
@@
 \subsubsection{Oscillatory Stokeslets and stresslets}
-
-In this section, we review the derivation of the
-oscillatory Stokeslet, which is the appropriate setting for the Stokes
-eigenvalue problem.
 Consider the solution of
@@
   \partial_{x_\ell} \left(\partial_{x_j} \Gbh \right) \right)
-  \; . \label{eq:ostress} \nonumber
+  \; . \label{eq:ostress} 
 \end{align}
@@
   \begin{align}
-    \lim_{h \downarrow 0} \bsigma_\bS[\bmu](\xx_0 \pm h\bnu(\xx_0)) \cdot \bnu(\xx_0)
+    \lim_{h \downarrow 0^{+}} \bsigma_\bS[\bmu](\xx_0 \pm h\bnu(\xx_0)) \cdot \bnu(\xx_0)
     &= \mp \frac{1}{2} \bmu(\xx_0) + \cDt[\bmu](\xx_0) \\
-    \lim_{h \downarrow 0} \bD[\bmu](\xx_0 \pm h\bnu(\xx_0)) 
+    \lim_{h \downarrow 0^{+}} \bD[\bmu](\xx_0 \pm h\bnu(\xx_0)) 
     &= \pm \frac{1}{2} \bmu(\xx_0) + \cD[\bmu](\xx_0)    \; .
@@
 In the following theorem, we sketch the proof of the equivalent of the
-Green's identity for oscillatory Stokes, which is well-known
+Green's identity for oscillatory Stokes setting, which is well-known
 in the Stokes and modified Stokes settings

### 2019-03-24 doc/draft-01-stokes/03analysis.tex
Updating paper

--- 2019-03-20 doc/draft-01-stokes/03analysis.tex
@@
 denoted by $\Gamma$.
-The Dirichlet boundary problem specifies the
+The Dirichlet problem specifies the
 velocity of the fluid on the boundary, i.e.
@@
 
-\begin{thrm}
+In the following lemma, we show that the oscillatory
+Stokeslet satisfies the radiation condition. 
+\begin{lem}
 The oscillatory Stokeslet, as defined in \eqref{eq:ostokeslet}, 
 satisfies the radiation condition in Definition \ref{def:radcond}.
-Suppose that $\Gamma$ is the boundary of a region $\Omega$
-and is $C^{2}$. 
-Suppose that $\bmu \in C(\Gamma)$ and satsifies
-$\int_{\Gamma} \bmu \cdot \bnu dS = 0$, where
-$\bnu$ dentoes the outward normal to the curve $\Gamma$.
-Then, the oscillatory Stokes 
-double layer potential $\bD[\bmu]$, as defined in \eqref{eq:doublelayer},
-also satisfies the radiation condition.
-\end{thrm}
-
+\end{lem}
 \begin{proof}
@@
 so that the Stokeslet satisfies the radiation condition.
-
-For the double layer potential, we only establish the
+\end{proof}
+A consquence of the above lemma is that the oscillatory Stokes
+single layer potential satisfies the radiation condition.
+\begin{cor}
+Suppose that $\Gamma$ is the boundary of a region $\Omega$
+and is $C^{2}$. 
+Suppose that $\bmu \in C(\Gamma)\times C(\Gamma)$, then
+the oscillatory Stokes single layer potential $\bS[\bmu]$,
+as defined in~\cref{eq:singlelayer}, satisfies the radition condition.
+\end{cor}
+Unfortunately, the stresslet, as defined in~\cref{eq:ostress}, 
+does not necessarily satisfy the radiation condition.
+The reason for failure is the logarithmic growth of 
+the pressure at $\infty$.
+However, this turns out to be a rank-one issue and 
+the oscillatory Stokes double layer potential
+does satisfy the radiation condition 
+if the density satisfies an integral constraint.
+The following lemma proves this result.
+
+\begin{lem}
+Suppose that $\Gamma$ is the boundary of a region $\Omega$
+and is $C^{2}$. 
+Suppose that $\bmu \in C(\Gamma) \times C(\Gamma)$ and satsifies
+$\int_{\Gamma} \bmu \cdot \bnu dS = 0$, where
+$\bnu$ dentoes the outward normal to the curve $\Gamma$.
+Then, the oscillatory Stokes 
+double layer potential $\bD[\bmu]$, as defined in \eqref{eq:doublelayer},
+also satisfies the radiation condition.
+\end{lem}
+
+\begin{proof}
+We only establish the
 decay of the pressure, which we will denote by $p^\bD$;
@@
 
-\note{Manas: check out new argument below.}
-
 \begin{proof}
@@
 dV \nonumber \\
-& \qquad + 2 \left( \left (\Re(k)\Re(\eta) + \Re(k)\Re(\eta)
+& \qquad + 2 \left( \left (\Re(k)\Re(\eta) + \Im(k)\Im(\eta)
 \right ) \int_{\Gamma} |\bu|^{2} dS  \right)
@@
 is represented using a double layer potential defined
-on $\Gamma$, i.e. setting $\bu = \bD_{k} \bmu$ for
-an unknown density $\bmu$. 
+on $\Gamma$, i.e. setting $\bu = \bD_{k} \bmu$ where
+$\bmu$ is an unknown density. 
 Substituting this expression
@@
 and the values of $k$ for which the operator $(\cI - 2\cD_{k} - 2\cW)$
-is not invertible. To prove this, we require the results
-above and the following lemma:
+is not invertible. To prove this, we also need the 
+following lemma:
 \begin{lem}
@@
 \end{proof}
-
-We now have
 
@@
 Note that $\bu$ is a radiating solution of the oscillatory
-Stokes equation in the exterior $E$, as $\cW[\mu] = 0$ implies
+Stokes equation in the exterior $E$, as $\cW[\bmu] = 0$ implies
 $\int_{\Gamma} \bmu \cdot \bnu = 0$.
@@
 Using the jump conditions in~\cref{lem:jump-conds} again, we
-get that $\bmu = \frac{1}{2}(\bu^{+} - \bu^{-}) = 0$.
+get that $\bmu = \bu^{-} - \bu^{+} = 0$.
 Thus $(\cI - 2\cD_{k} - 2\cW)$ is invertible if $k^2$
@@
 Using~\cref{lem:jump-conds} we observe that $\bt^{+}
-= i\eta \bmu(\xx)$ and $\bu^{+} = \bmu(\xx)$ on $\Gamma$.
+= -i\eta \bmu(\xx)$ and $\bu^{+} = -\bmu(\xx)$ on $\Gamma$, i.e.
+$\bt^{+}=i\eta u^{+}$ and $u^{+}$ satisfies the homogeneous
+exterior impedence problem.
 \begin{remark}
@@
 again, we get that
-$\bmu = \frac{1}{2}(\bu^{+} - \bu^{-}) = 0$ on
+$\bmu = \bu^{-} - \bu^{+} = 0$ on
 $\Gamma_{0}$. To show that $\bmu=0$ on
@@
 \begin{equation}
-\int_{\Omega_{j}} (|e(\bu)|^{2} - \overline{k}^{2} |\bu|^2) dV 
+\int_{\Omega_{j}} (|\be(\bu)|^{2} - \overline{k}^{2} |\bu|^2) dV 
 = \int_{\Gamma_{j}} \bu \cdot \overline{\bt} dS = 

### 2019-03-25 doc/draft-01-stokes/03analysis.tex
Cleaning up fredholm determinant section

@@
 \end{equation}
+
+So far, we have discussed the Fredholm theory in the space
+$C(\Gamma)\times C(\Gamma)$ equipped with the bilinear form~\cref{eq:bi_form}.
+However, it is more convenient to discuss the theory of Fredholm
+determinants on Hilbert spaces. 
+We note that both the operators $\cD_{k}$ and $\cS_{k}$ 
+are also compact operators mapping $Y \to Y$
+where $Y = \mathbb{L}^{2}(\Gamma) \times \mathbb{L}^{2}(\Gamma)$.
+Furthermore, it is well-known that the spectrum of compact
+operators with weakly singular kernels coincide on 
+$C(\Gamma)\times C(\Gamma)$ and $Y$ (see~\cite{kress1989linear},
+for example).
+So for the rest of the section, we present the discussion of 
+the relevant operators on $Y$ instead of $C(\Gamma)\times C(\Gamma)$.
+
 %It follows from standard results in complex
@@
   Suppose that $\Gamma$ is a $C^2$ curve.
-  Then, $-2\cD_{k} - 2\cW \in \cJ_1(L_2(\Gamma)\otimes L_2(\Gamma))$
-  for all $k$ 
+  Then, $-2\cD_{k} - 2\cW \in \cJ_1(Y)$
+  for all $k \in \mathbb{C} \setminus \{0\}$ 
 \end{lemma}
@@
 has a leading order singularity of
-$|\bx-\by|^2 \log{|\bx-\by|^2}$ as $\bx\to \by$.
+$|\bx-\by|^2 \log{|\bx-\by|^2}$ as $\bx\to \by$ 
+for all $k \in \mathbb{C} \setminus \{ 0\}$.
 It follows from the criteria listed
 in~\cite[Sec. 2]{bornemann2010numerical} that $\cD_{k}$
-is a trace-class operator for all $k$.
+is a trace-class operator.
 Since $\cW$ is a rank-one perturbation independent of $k$,
 and trace-class operators are a vector space, we conclude
-that $-2\cD_{k} - 2\cW$ is also a trace-class operator for
-all $k$.
+that $-2\cD_{k} - 2\cW$ is also a trace-class operator.
 \end{proof}
@@
 First, note that $f(k)$ is an analytic function of $k$
-for $k \in \mathbb{C} \setminus 0$, since the kernel
+for $k \in \mathbb{C} \setminus \{0 \}$, since the kernel
 of $\cD_{k}$ is an analytic function of $k$ on that domain, 
-and the Fredholm determinant is an analytic operator.
+and the Fredholm determinant of an analytic operator 
+is analytic on the domain of analyticity
+of the operator (see~\cite{zhao2015robust}, for example).
 
@@
 operator is not invertible.
-This is summarized as 
+The following lemma summarizes this result.
 \begin{lem} \label{lem:detzeros}
@@
 Stokes equation as well.
-We summarize the result as
+The result is summarized below.
 \begin{thrm}
@@
 quadrature.
-Then $f^{N}(k)$ has exactly $M$ zeros on the interval $[a,b]$
-\note{Manas: for sufficiently large $N$?}. 
+Then there exists $N_{0} \in \mathbb{N}$ such
+that for all $N>N_{0}$, 
+$f^{N}(k)$ has exactly $M$ zeros on the interval $[a,b]$.
 Let $\omega_{j}$, $j=1,2\ldots M$ denote the zeros of $f^{N}$.
@@
 nature of the quadrature rule.
-%
-\note{Manas: I do not understand the $O(N)$ cost per matrix entry
-  described here in the fast-direct case ... does it somehow
-  screw up compression?}
-Coupling with fast direct solvers for computing determinants also results in $O(N^2 \log{N})$ 
-determinant evaluation since evaluating each matrix entry costs $O(N)$, where 
-$N$ is the number of discretization points on the boundary.
+Coupling with fast direct solvers for computing determinants also results in $O(N^2 \log{N})$.
+where $N$ is the number of discretization points on the boundary.
+Typical fast direct solvers
+query $O(N)$ matrix entries to obtain a compressed representation,
+this combined with the fact that evaluating each matrix entry
+costs $O(N)$ for Kress-quadratures results in the sub-optimal
+complexity. 
 Over the last two decades, many high-order quadrature methods which are compatible with
@@
 The operator $\cM_{k}$ is 
-in $\cJ_{2}(\bL^{2}(\Gamma))$ where
-$\cJ_{2}(\bL^{2}(\Gamma))$ is the space of Hilbert-Schmidt operators
-on $\bL^{2}(\Gamma)$ (the singular values of the operator are square
+in $\cJ_{2}(Y)$ where
+$\cJ_{2}(Y)$ is the space of Hilbert-Schmidt operators
+on $Y$ (the singular values of the operator are square
 summable, as opposed to being summable).

### 2019-03-25 doc/draft-01-stokes/01intro.tex
update paper, add references, add conclusion

@@
 While integral equation based methods for the
-related ``buckling'' eigenvalue problem
+equivalent \cite{kelliher2009eigenvalue}
+``buckling'' eigenvalue problem
 have been considered previously,
@@
 This is unsatisfying from a theoretical
-perspective, because such operators are never \note{Travis: why is this the case?} 
-invertible
-(though, they are not injective precisely when $k^2$ is an
-eigenvalue \cite{kitahara2014boundary,antunes2011buckling})
-so that the relation between the non-invertibility of the
-discrete system and the eigenvalues is obscured.
+perspective, because compact operators always
+have nontrivial nullspaces
+(though, by design, the representations in
+\cite{kitahara2014boundary,antunes2011buckling}
+are not injective precisely when
+$k^2$ is an eigenvalue).
 %
-Further,
-such representations create numerical challenges because
-common measures of the ``non-invertibility'' of a matrix,
-like the smallest singular value or the determinant, converge
-rapidly to zero for all values of $k^2$ as the boundary is
-refined. Therefore, the measure of whether $k^2$ is an
-approximate eigenvalue is {\em relative to the current grid}
-for first kind equations.
+This obscures the relation between
+the non-invertibility of the
+discrete system and the eigenvalues;
+in particular, common measures of the
+``non-invertibility'' of a matrix, like the
+smallest singular value or the determinant,
+converge rapidly to zero for all values
+of $k^2$ as the boundary is refined.
+The measure of whether $k^2$ is an
+approximate eigenvalue is then {\em relative to the
+  current grid} for first kind formulations.
 

### 2019-03-25 doc/draft-01-stokes/03analysis.tex
update paper, add references, add conclusion

@@
 \begin{remark}
-In practice, using Kress-quadrature for large
+In practice, using Kress quadrature for large
 problems is problematic owing to the global
 nature of the quadrature rule.
-Coupling with fast direct solvers for computing determinants also results in $O(N^2 \log{N})$.
-where $N$ is the number of discretization points on the boundary.
-Typical fast direct solvers
-query $O(N)$ matrix entries to obtain a compressed representation,
-this combined with the fact that evaluating each matrix entry
-costs $O(N)$ for Kress-quadratures results in the sub-optimal
-complexity. 
-Over the last two decades, many high-order quadrature methods which are compatible with
-fast algorithms like the fast multipole method (and fast direct solvers as well, 
-since each matrix entry requires O(1) work) have been developed for solving
-integral equations.
+%
+First, the use of a global rule does not allow
+for adaptive refinement at a complicated, local
+feature of the boundary.
+%
+Second, the integration weight in each entry
+of the matrix depends on both the column and the row
+in a non-separable way.
+%
+As a result, the fast multipole method is not
+directly applicable to the resulting matrix
+and many fast-direct methods for computing
+the determinant lose efficiency (for
+instance, the reasoning behind the use of a
+{\em proxy surface} \cite{cheng2005compression}
+no longer holds).
+%
+%Coupling with fast direct solvers for computing determinants also results in $O(N^2 \log{N})$.
+%where $N$ is the number of discretization points on the boundary.
+%Typical fast direct solvers
+%query $O(N)$ matrix entries to obtain a compressed representation,
+%this combined with the fact that evaluating each matrix entry
+%costs $O(N)$ for Kress quadratures results in the sub-optimal
+%complexity. 
+Over the last two decades, many high-order quadrature
+methods which are compatible with
+the fast multipole method and fast-direct solvers
+have been developed.
+%
 Extensive numerical evidence suggests that the zeros of the 
 determinants of linear systems discretized using 
-these quadrature methods are also high order approximations of Dirichlet eigenvalues
-for the Stokes PDE--- the error is observed to be proportional to the quadrature error
+these quadrature methods are also high order approximations
+of Dirichlet eigenvalues for the Stokes operator ---
+the error is observed to be proportional to the quadrature error
 for the eigenfunction $\bt^{-}$ associated with the eigenvalue.

### 2019-03-25 doc/draft-01-stokes/05conclusion.tex
update paper, add references, add conclusion

\section{Conclusion}
\label{sec:conclusion}

In the preceding, we have demonstrated a
BIE framework for computing the eigenvalues
of the Stokes operator in the plane which
is robust and scalable.
%
To justify the
approach, we developed a uniqueness theory
for the oscillatory Stokes equations in
exterior domains in analogy with the
discussion of the Helmholtz equation in
\cite{colton1983integral}.
%
This lead to the primary theoretical
results of the paper which show that the
BIEs resulting from double layer and
combined-field representations of the
velocity field are 
not invertible precisely when $k^2$ is
an eigenvalue on simply connected
and multiply connected domains, respectively.
%
As in \cite{zhao2015robust}, the costliness
of performing the nonlinear minimization
associated with computing these eigenvalues
can be alleviated by computing instead the
approximate zeros of the discrete Fredholm
determinant.

The results of this paper can be
extended in a number of ways.
%
The theory
extends directly to three dimensions, where
computational efficiency and numerical
implementation will be the primary concern.
%
In the numerical examples above, we
consider only domains with differentiable
boundaries for simplicity.
%
However, there has been recent progress
toward efficient discretization of the
layer potentials of elliptic operators
on domains with corners
\cite{helsing2008corner,serkh2016solution,rachh2017solution,helsing2018integral}
which makes such problems tractable.
%
Of course, the theoretical considerations
are a little different for such domains
--- work in this area will be reported at
a later date.

As noted in the introduction, the
eigenvalues of the Stokes operator are
equivalent to the so-called
``buckling'' eigenvalues of the
biharmonic operator \cite{kelliher2009eigenvalues}.
%
This can be seen through the stream function
formulation  of the oscillatory Stokes
equation, i.e. setting $\bu = \nabla^\perp \psi$
where $\psi$ now satisfies

\begin{equation*}
  -\Delta^2 \psi = k^2 \Delta \psi \quad \textrm{in} \quad \Omega\; .
\end{equation*}
Note that the buckling problem enforces the
clamped, or first Dirichlet, boundary
condition on $\psi$

\begin{equation*}
  \psi = \partial_\nu \psi = 0 \; \quad \textrm{on} \quad \Gamma.
\end{equation*}
Computing the stream function corresponding
to an oscillatory Stokes layer potential can be
done in a straightforward manner
by adapting the approach of \cite{rachh2017integral}.
%
This is the subject of a note which is in
preparation.

There are some interesting questions in the
use of Fredholm determinants in numerical
calculations.
%
As observed in \cite{zhao2015robust}, the
combined-field representation causes some
difficulty in that the Fredholm determinant
is not defined when the single layer, which
is not trace-class, is included.
%
Zhao and Barnett~\cite{zhao2015robust}
suggest looking into
representations of the form $\cI-2\cD
-2i\eta\cS^2-2\cW$,
which would have a well-defined Fredholm
determinant.
%
The relative performance of
such an approach should be explored.
%
Further, as discussed above, the
convergence of the determinant of
integral equations discretized with
panel-corrected schemes (as described in
\cref{sec:numerical}) is yet to be proved.
%
Finally, is there an alternative
to the Fredholm determinant which
has similar advantages?
%

### 2019-03-25 doc/draft-01-stokes/appendix.tex
Updating neumann eigenvalues
update paper, add to intro, clean up theory section
Adding neumann proof in multiply connected domains

@@
+\section{Uniqueness of the Neumann problem in the exterior
+  of several obstacles}
+\label{app:neuuniqueness}
+In this section, we prove the uniqueness result for the oscillatory
+Stokes problem with Neumann boundary conditions on the exterior
+of several simply connected obstacles. 
+\begin{thrm}[Uniqueness of the Exterior Neumann Problem]
+  Suppose that $\Omega$ is the union of a finite collection 
+  of simply connected domains, i.e. $\Omega = \bigcup_{i=1}^m \Omega_{i}$
+  for some $m \in \N$, with $C^{2}$ boundaries, 
+  and let $E = \R^{2} \setminus \bar{\Omega}$ denote its exterior;
+  see~\cref{fig:ext_dom} for an example with $m=4$.
+  Let $\Gamma_{i}$ denote the boundary of $\Omega_{i}$, 
+  and $\Gamma = \bigcup_{i=1}^{m} \Gamma_{i}$ denote the boundary
+  of $\Omega$.
+  Suppose that $\Im(k)\geq 0$ and 
+  that $(\bu,p)$ is a radiating solution to the oscillatory Stokes
+  equation in $E$ with $\bt = 0$ on the boundary $\Gamma$, then
+  $\bu \equiv 0$ in $E$.
+\end{thrm}
+
+\begin{proof}
+Since $\bt = 0$ on $\Gamma$, it follows
+from~\cref{eq:repinfest} that
+\begin{equation}
+\lim_{r\to\infty}
+\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
+2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |\be(\bu)|^2 \right)
+dV = 0 \; . \nonumber
+\end{equation}
+
+Suppose that $\Im(k) > 0$. It is then immediate
+that $\bu \equiv 0$ in $E$.
+
+Suppose that $k$ is real. It is clear that
+\begin{equation}
+\lim_{r\to\infty} \int_{|\by|=r} |\bu|^2 dS = 0 \, . \nonumber
+\end{equation}
+Thus, the conditions on $\bu$ and $k$ in \cref{lem:rellich}
+are satisfied, and each component of $\bu$ is a harmonic function
+with $\bu \to 0$ as $r \to \infty$. Furthermore, as observed
+in \cref{rmk:harmu}, $k^2 \bu = \nabla p$. Then, the boundary
+condition becomes $0 = \bt = -p \bnu + 2 \nabla \partial_\nu p/k^2$.
+Because $0 = \btau \cdot \bt = 2\partial_{\tau\nu} p/k^2$,
+$\partial_\nu p  = c_{i}$ on $\Gamma_{i}$ for each $\Gamma_{i}$,
+where $c_{i}$ is a constant. 
+Observe that $|\bu|$ and $|\be(\bu)|$ must be $O(1/r)$ as
+$r\to\infty$. Thus,
+for a radiating pair $(\bu,p)$ with $p$ harmonic,
+we have that $|p| = O(1/r)$ and $|\nabla p| = O(1/r^2)$
+as $r\to\infty$.
+Since the boundary is $C^{2}$ and the boundary data for $p$
+is analytic, we conclude that $p$ is $C^{2}$ in
+$\overline{E}$.
+Furthermore, $\bt=0$ implies $p \bnu = 2\nabla \partial_{\nu} p/k^2$, 
+and taking the dot
+product with $\bnu$, we get
+$p = 2\partial_{\nu \nu}p/k^2$. 
+It then follows that
+$p = -2\partial_{\tau \tau}p/k^2$ on $\Gamma$ since 
+$p$ is harmonic in $E$ and $C^{2}$ in $\overline{E}$. 
+Since $p$ satisfies the radiation condition at $\infty$,
+we have
+\begin{equation}
+\begin{aligned}
+\int_{E} |\nabla p|^2 dV &= 
+\sum_{i=1}^{m} \int_{\Gamma_{i}} p \partial_{\nu}p \,dS \\
+&= \sum_{i=1}^{m} c_{i} \int_{\Gamma_{i}} p \,dS \quad \text{(Since $\partial_{\nu} p = c_{i}$ on
+$\Gamma_{i}$)} \\ 
+&= -\sum_{i=1}^{m} \frac{2c_{i}}{k^2} \int_{\Gamma_{i}} \partial_{\tau \tau} p \,dS 
+\quad \text{(Since $p = -\partial_{\tau \tau}p/k^2$ on $\Gamma$)} \\
+&= 0
+\end{aligned}
+\end{equation}
+Thus, $p$ is a constant in $E$. Furthermore, since $p\to 0$ at $\infty$, 
+we conclude that $p\equiv 0$ in $E$. 
+Finally, since $k^2 \bu = \nabla p$, we conclude that $\bu\equiv 0$ in 
+$E$.
+\end{proof}
+
 \section{Neumann eigenvalues and eigenfunctions on the unit disk}
@@
 & \hspace*{15ex} \sint \left(-\alpha k^2 r^{n} + 2 \alpha n(n-1)r^{n-2} + 2 \delta n \ddr \frac{\jnkr}{r} \right) \, , \\
-t_{\theta} &= \cost \left( \alpha r^{n-2} (n^2 + n(n-1)) + \delta \left( \frac{n^2}{r^2} + k^2 \jnppkr \right)  \right) + \\
-& \hspace*{15ex} \sint \left( \beta r^{n-2} (n^2 + n(n-1)) + \gamma \left( \frac{n^2}{r^2} + k^2 \jnppkr \right) \right) \, .
+t_{\theta} &= \cost \left( \alpha r^{n-2} (n^2 + n(n-1)) + \delta \left( \frac{n^2}{r^2} \jnkr + k^2 \jnppkr \right)  \right) + \\
+& \hspace*{15ex} \sint \left( \beta r^{n-2} (n^2 + n(n-1)) + \gamma \left( \frac{n^2}{r^2} \jnkr + k^2 \jnppkr \right) \right) \, .
 \end{aligned}
@@
 0 & 0 & k^2 - 2n(n-1) & -2nh_{k} \\
-0 & 0 & 2n^2 -n & n^2 + k^2 \jnppk \\
+0 & 0 & 2n^2 -n & n^2 \jnk + k^2 \jnppk \\
 -k^2 + 2n(n-1) & 2nh_{k} & 0 & 0 \\
-2n^2 -n & n^2 + k^2 \jnppk & 0 & 0
+2n^2 -n & n^2 \jnk + k^2 \jnppk & 0 & 0
 \end{bmatrix}
@@
 \begin{equation}
-2n^2(2n-1)h_{k} - (n^2 + k^2 \jnppk)(-k^2 + 2n(n-1)) = 0 \, .
+2n^2(2n-1)h_{k} - (n^2 \jnk + k^2 \jnppk)(-k^2 + 2n(n-1)) = 0 \, .
 \end{equation}

### 2019-03-25 doc/draft-01-stokes/01intro.tex
update conclusion and intro, fixing reference to equivalence of Stokes and buckling eigenvalues

@@
 While integral equation based methods for the
-equivalent \cite{kelliher2009eigenvalue}
-``buckling'' eigenvalue problem
+related ``buckling'' eigenvalue problem
+(which is equivalent  on simply connected domains
+\cite{kelliher2009eigenvalues})
 have been considered previously,

### 2019-03-25 doc/draft-01-stokes/05conclusion.tex
update conclusion and intro, fixing reference to equivalence of Stokes and buckling eigenvalues

@@
 ``buckling'' eigenvalues of the
-biharmonic operator \cite{kelliher2009eigenvalues}.
+biharmonic operator on simply connected
+domains~\cite{kelliher2009eigenvalues}.
 %
@@
 \end{equation*}
-Computing the stream function corresponding
-to an oscillatory Stokes layer potential can be
-done in a straightforward manner
-by adapting the approach of \cite{rachh2017integral}.
+On a multiply connected domain, it is possible for
+an eigenfield to have no corresponding stream
+function which is still clamped, so that the
+buckling eigenvalues are a subset of the Stokes
+eigenvalues.
+By adapting the approach of \cite{rachh2017integral},
+a suitable layer potential representation of the
+buckling problem can be derived based on the
+oscillatory Stokes layer potentials.
 %
-This is the subject of a note which is in
+This is the subject of a follow-up paper which is in
 preparation.
 
-There are some interesting questions in the
-use of Fredholm determinants in numerical
+There are some interesting questions to answer
+on the use of Fredholm determinants in numerical
 calculations.
@@
 %
-Finally, is there an alternative
-to the Fredholm determinant which
-has similar advantages?
-%
+Finally, it is worth exploring alternatives
+to the Fredholm determinant which perform well
+for layer potentials that are not trace class
+on the boundary.

### 2019-03-25 doc/draft-01-stokes/appendix.tex

@@
 as $r^{n} \cost$,  $r^{n} \sint$ are harmonic functions. 
-To show that $(\bu,p)$ satisfies the PDE, observe that
+To show that $(\bu,p)$ satisfies the PDE, note that
+$r^{n} \cost$ and $r^{n} \sint$ are harmonic
+and $\jnkr \cost$, $\jnkr \sint$ satisfy Helmholtz's equation.
 \begin{equation}
@@
 \quad & \hspace*{15ex} (\Delta + k^2) \nabla^{\perp} (\gamma \jnkr \sint + \delta \jnkr \cost) \, , \\
-&= k^2 \nabla (\alpha r^{n} \sint - \beta r^{n} \cost) \quad \bigg(\text{Since} \Delta (r^{n}\cost, r^{n}\sint) = 0 \quad
-\text{and} \, ,\\
-& \hspace*{25ex} (\Delta + k^2) (\jnkr \cost, \jnkr \sint) = 0 \bigg) \\
+&= k^2 \nabla (\alpha r^{n} \sint - \beta r^{n} \cost) \\ 
 &= \nabla p
@@
 \end{equation}
-In particular
-\begin{equation}
-\begin{aligned}
-t_{r} = \bt \cdot \hat{r} &= -p + 2\partial_{r} (\bu \cdot \hat{r}) \, , \\
-t_{\theta} = \bt \cdot \hat{\theta} &= \frac{1}{r}\partial_{\theta}(\bu \cdot \hat{r}) + \partial_{r} (\bu \cdot \hat{\theta}) \, .
-\end{aligned}
-\end{equation}
-
-The $\hat{r},\hat{\theta}$ components of $\bu$ are given by
-\begin{equation}
-\begin{aligned}
-u_{r} = \bu \cdot \hat{r} &= \partial_{r} (\alpha r^{n} \sint - \beta r^{n} \cost) 
-- \frac{1}{r}\partial_{\theta}(\gamma \jnkr \sint + \delta \jnkr \cost) \\
-&= \sint \left(\alpha n r^{n-1} + \delta n \frac{\jnkr}{r} \right) 
-  - \cost \left(\beta n r^{n-1} + \gamma n \frac{\jnkr}{r} \right) \, , \\
-u_{\theta} = \bu \cdot \hat{\theta} &= \frac{1}{r} \partial_{\theta} (\alpha r^{n} \sint - \beta r^{n} \cost)
-+ \partial_{r} (\gamma \jnkr \sint + \delta \jnkr \cost) \\ 
-&= \cost \left( \alpha n r^{n-1} + \delta k \jnpkr \right) + \sint \left( \beta n r^{n-1} + \gamma k \jnpkr \right)
-\end{aligned}
-\end{equation}
-
-The relevant derivatives are given by
-\begin{equation}
-\begin{aligned}
-\partial_{r} u_{r} &= \sint \left( \alpha n (n-1) r^{n-2} + \delta n \ddr \left(\frac{\jnkr}{r}\right) \right)
-- \cost \left( \beta n (n-1) r^{n-2} + \gamma n \ddr \left( \frac{\jnkr}{r} \right) \right) \, , \\
-\frac{1}{r} \partial_{\theta} u_{r} &= n \cost \left(\alpha n r^{n-2} + \delta n \frac{\jnkr}{r^2} \right) + 
-n \sint \left(\beta n r^{n-2} + \gamma n\frac{\jnkr}{r^2} \right) \, , \\
-\partial_{r} u_{\theta} &= \cost(\alpha n(n-1) r^{n-2} + \delta k^2 \jnppkr) + 
-\sint (\beta n(n-1)r^{n-2} + \gamma k^2 \jnppkr) \, .
-\end{aligned}
-\end{equation}
-
-Now we finally get to the expressions for $t_{r},t_{\theta}$ 
+If $(\bu,p)$ are as defined above, then 
+a long but tedious calculation shows that
 \begin{equation}
@@
 \end{equation}
-A simple calculation shows that the zeros correpsonding to
-$n=0$ are the zeros of $\jnppk$, the first few of which are
-\begin{itemize}
-\item $k = 1.74118378134066$
-\item $k = 5.33144277352503$
-\item $k = 11.7060049025921$
-\end{itemize}

### 2019-03-26 doc/draft-01-stokes/01intro.tex
add round of spell checking

@@
 values $0 < k_{1}^{2} \leq k_{2}^2 \leq \ldots \uparrow \infty$,
-counting multiplicites.
+counting multiplicities.
 

### 2019-03-26 doc/draft-01-stokes/02prelim.tex
update paper, add references, add conclusion
add round of spell checking

--- 2019-03-24 doc/draft-01-stokes/02prelim.tex
@@
 We seek solutions of \cref{eq:ostokes} in the space
-\note{make sure this is the correct space: (MR - looks good to me)}
 \begin{equation}
@@
 \end{equation}
-where $k$ is the Helmholtz paramater in the oscillatory biharmonic equation,
+where $k$ is the Helmholtz parameter in the oscillatory biharmonic equation,
 and $H_{0}^{1}(r)$ is the Hankel function of the first kind of order zero.
@@
   $\Gamma$. Then the operators $\cS$ and $\cD$ defined
-  above are compact.
+  above are compact operators on $C(\Gamma)\times C(\Gamma)$
+  and $\mathbb{L}^2(\Gamma)\times \mathbb{L}^2(\Gamma)$.
 \end{lem}

### 2019-03-26 doc/draft-01-stokes/03analysis.tex
add round of spell checking

@@
 \end{proof}
-A consquence of the above lemma is that the oscillatory Stokes
+A consequence of the above lemma is that the oscillatory Stokes
 single layer potential satisfies the radiation condition.
@@
 the oscillatory Stokes single layer potential $\bS[\bmu]$,
-as defined in~\cref{eq:singlelayer}, satisfies the radition condition.
+as defined in~\cref{eq:singlelayer}, satisfies the radiation condition.
 \end{cor}
@@
 and is $C^{2}$. 
-Suppose that $\bmu \in C(\Gamma) \times C(\Gamma)$ and satsifies
+Suppose that $\bmu \in C(\Gamma) \times C(\Gamma)$ and satisfies
 $\int_{\Gamma} \bmu \cdot \bnu dS = 0$, where
-$\bnu$ dentoes the outward normal to the curve $\Gamma$.
+$\bnu$ denotes the outward normal to the curve $\Gamma$.
 Then, the oscillatory Stokes 
@@
   not be a radiating solution. All that is assumed of $\bu$
-  is that it satifies the PDE in $E$.
+  is that it satisfies the PDE in $E$.
 \end{remark}
@@
 Dirichlet eigenvalue problem but a similar analysis
-could be applied to the Neumann eigenvale problem.
+could be applied to the Neumann eigenvalue problem.
 We analyze two different representations for the
@@
 
-On simply connected domains, there is a one-to-one correspondance between
+On simply connected domains, there is a one-to-one correspondence between
 the eigenvalues of the Dirichlet problem for
@@
 Analogous with the observation in~\cite{zhao2015robust},
-this lack of one-to-one correspondance between
+this lack of one-to-one correspondence between
 the invertibility of the integral operator $\cI - 2\cD_{k} - 2\cW$
@@
 connected domains also causes non-robustness and introduces near 
-resonanaces for simply connected domains
+resonances for simply connected domains
 which are almost multiply connected.
@@
 $\bt^{+}=i\eta u^{+}$ and $u^{+}$ satisfies the homogeneous
-exterior impedence problem.
+exterior impedance problem.
 \begin{remark}
@@
 Let $f^{N}(k) = \text{det}(I+M^{N}_{k})$, where $M^{N}_{k}$ 
-is the Nystr\"{o}m discretzation of $-2\cD_{k} - 2\cW$ with Kress
+is the Nystr\"{o}m discretization of $-2\cD_{k} - 2\cW$ with Kress
 quadrature.
@@
 \begin{proof}
-  The proof follows from small modificiations of the
+  The proof follows from small modifications of the
   proofs contained in~\cite{zhao2015robust}. 
@@
 $\cM_{k}$ decay like $\frac{1}{n}$, and the
-Fredholm determinant divergers logarithmically. 
+Fredholm determinant diverges logarithmically. 
 In~\cref{subsec:convannulus}, we demonstrate this fact

### 2019-03-26 doc/draft-01-stokes/05conclusion.tex
add round of spell checking

@@
 Of course, the theoretical considerations
-are a little different for such domains
---- work in this area will be reported at
-a later date.
+are different for such domains.
+%
+Computing the Stokes eigenvalues of regions
+with corners is the topic of ongoing
+research.
 

### 2019-03-26 doc/draft-01-stokes/01intro.tex
add some small edits

@@
   kelliher2009eigenvalues,antunes2011buckling},
-particularly how they relate to the eigenvalues and
-eigenfunctions of the drum.
+especially as they relate to the eigenvalues and
+eigenfunctions of the Laplacian.
 
@@
 Further, numerical simulation has long played an
-important role in the analyses described above --- both for
+important role in the analyses cited above --- both for
 estimating the eigenvalues on domains of practical
-interest and for exploring open conjectures.
+interest and in forming new conjectures.
 
 Borrowing the language of~\cite{zhao2015robust},
-which concerns the Laplace or ``drum'' eigenvalue
-problem,
+which concerns the eigenvalues of the Laplacian
+(also known as the membrane or ``drum'' problem),
 the numerical treatment of the Stokes eigenvalue
@@
 %
-This is unsatisfying from a theoretical
-perspective, because compact operators always
-have nontrivial nullspaces
-(though, by design, the representations in
+This is unsatisfying from a numerical
+perspective, because the spectrum of a
+compact operator either contains zero
+or has zero as a limit point
+(by design, the representations in
 \cite{kitahara2014boundary,antunes2011buckling}
@@
 This obscures the relation between
-the non-invertibility of the
-discrete system and the eigenvalues;
+the non-invertibility of discrete approximations
+of the operator and the eigenvalues;
 in particular, common measures of the

### 2019-03-26 doc/draft-01-stokes/05conclusion.tex
add some small edits

@@
 \end{equation*}
-On a multiply connected domain, it is possible for
-an eigenfield to have no corresponding stream
-function which is still clamped, so that the
+On a multiply connected domain, there are
+Stokes eigenfunctions which do not have a corresponding
+clamped stream function, so that the
 buckling eigenvalues are a subset of the Stokes

### 2019-03-27 doc/draft-01-stokes/appendix.tex
add round of spell checking
adding dirichlet eigenvalue on annulus

@@
 
+\section{Dirichlet eigenvalues and eigenfunctions on the unit disk}
+In this section, we compute some of the Dirichlet eigenvalues
+corresponding to the a subset of radially symmetric eigenfunctions
+on the annulus. 
+In polar coordinates $(r,\theta)$, consider the annulus defined by 
+$R_{1}<r<R_{2}$. 
+Suppose that $\bu$ is of the form 
+\begin{equation}
+\bu = \nabla^{\perp}\left( \alpha H_{0}(kr) + \beta J_{0}(kr) \right) \, ,
+\label{eq:annulus_direig}
+\end{equation}
+and $p=0$.
+
+Clearly, this pair satisfies the osciallatory Stokes equation
+with parameter $k$, since $J_{0}(kr)$ and $H_{0}(kr)$ 
+satisfy the Helmholtz equation on the annulus.
+
+Let $\hat{r},\hat{\theta}$ denote the unit vectors in polar coordinates.
+A simple calculation shows that 
+\begin{equation}
+\begin{aligned}
+u_{r} &= \bu \cdot \hat{r}  = 0 \, \\
+u_{\theta} &= \bu \cdot \hat{\theta} = k(\alpha  H_{0}'(kr) + \beta J_{0}'(kr)) \, .
+\end{aligned}
+\end{equation}
+
+This in particular implies that on $r=R_{1}$,
+$u_{\theta}$ takes on the constant value,
+$k(\alpha H_{0}'(kR_{1}) + \beta J_{0}'(kR_{1}))$.
+Similarly, on $r=R_{2}$, 
+$u_{\theta}$ takes on the constant value,
+$k(\alpha H_{0}'(kR_{2}) + \beta J_{0}'(kR_{2}))$.
+
+Thus, if $k$ satisfies, 
+\begin{equation}
+H_{0}'(kR_{1}) J_{0}'(kR_{2}) - H_{0}'(kR_{2})J_{0}'(kR_{1}) = 0 \, ,
+\end{equation}
+and for those values of $k$ if 
+$\alpha,\beta$ are non-zero solutions to system of equations 
+\begin{equation}
+\begin{bmatrix}
+H_{0}'(kR_1) & J_{0}'(kR_{1}) \\
+H_{0}'(kR_{2}) & J_{0}'(kR_{2}) 
+\end{bmatrix}
+\begin{bmatrix}
+\alpha \\
+\beta
+\end{bmatrix}
+=
+\begin{bmatrix}
+0 \\
+0
+\end{bmatrix}
+\, ,
+\end{equation}
+then $k$ is a Dirichlet eigenvalue and $\bu$ 
+defined by~\cref{eq:annulus_direig}
+is the corresponding eigenfunction.
+
 \section{Neumann eigenvalues and eigenfunctions on the unit disk}
@@
 
-A collorary of the above statement and the structure of the matrix is that
+A corollary of the above statement and the structure of the matrix is that
 the interior Neumann eigenvalues of the unit disk satisfy

### 2019-03-28 doc/draft-01-stokes/01intro.tex
update small differences

@@
 stability analysis of stationary solutions of the
-Navier--Stokes equations \cite{osborn1976approximation}
-and in the study of decaying two dimensional turbulence
-\cite{schneider2008final}.
+Navier--Stokes equations \cite{osborn1976approximation},
+in the study of decaying two dimensional turbulence
+\cite{schneider2008final}, and as a trial basis for
+numerical simulations of the Navier--Stokes
+equations~\cite{batcho1994generalized}.
 %
 The eigenvalues and eigenfunctions of the Stokes
-operator are the subject of intense analytical
+operator are also the subject of intense analytical
 investigation
@@
 important role in the analyses cited above --- both for
-estimating the eigenvalues on domains of practical
-interest and in forming new conjectures.
+computing the eigenvalues and eigenfunctions
+on domains of practical interest and in forming
+new conjectures.
 
@@
 oscillatory Stokes equations as a boundary integral
-equations which are discretized.
+equation (BIE) which is discretized.
 The eigenvalues are then found
-by a nonlinear search for the values of $k$ where the BIE 
-is not invertible.
+by a nonlinear search for the values of
+$k$ where the BIE is not invertible.
 %
@@
 
-As noted in~\cite{zhao2015robust}, integral equation based
-methods provide several advantages.
+As noted in~\cite{zhao2015robust}, integral
+equation based methods provide several advantages.
 %
@@
 \cite{zhao2015robust} for the drum problem in mind,
-we develop an integral equation based method for the Stokes eigenvalue
-problem.
+we develop an integral equation based method for the
+Stokes eigenvalue problem.
 %
@@
 methods we use to discretize the BIEs and to perform
-fast determinant calculations.
+determinant calculations.
+%
+At the moderate frequencies considered in this
+paper, we find that standard fast-direct
+solvers provide a reasonably efficient determinant
+evaluation.
 %

### 2019-03-28 doc/draft-01-stokes/appendix.tex
update small differences

--- 2019-03-25 doc/draft-01-stokes/appendix.tex
@@
 
-We first show that this pair satisfies the oscillatory stokes equation
+We first show that this pair satisfies the oscillatory Stokes equation
 in the unit disk.

### 2019-03-28 doc/draft-01-stokes/stokes-eig.tex
adding stokes paper stuff
clean up stokes manuscript, update matlab routines
updates to paper and cleaning up arguments
update proof or rellich's lemma
add latest updates, restructure a little
cleaning up section 2,3 (done till 3.5 except last theorem)
Second pass at section 3.6
updating stokes-eig to 03analysis from 03anlysis2
Adding appendix for neumann eigenvalues on the unit disk
Updating neumann eigenvalues
adding annulus example drivers
update paper, add to intro, clean up theory section
add files needed for latest tests
update paper, add references, add conclusion
update small differenc

--- 2018-06-22 doc/draft-01/biharm-evals.tex
@@
 \usepackage{subcaption}
+\usepackage{amsmath}
 
@@
 \Crefname{eqnarray}{}{}
+\crefname{lemma}{lemma}{lemmas}
+\crefname{lem}{lemma}{lemmas}
+\crefname{cor}{corollary}{corollaries}
+\crefname{thrm}{theorem}{theorems}
 
@@
 
+\def\bz{{\boldsymbol 0}}
 \def\br{{\boldsymbol r}}
+\def\bc{{\boldsymbol c}}
 \def\bh{{\boldsymbol h}}
@@
 \def\bT{{\boldsymbol T}}
+\def\bt{{\boldsymbol t}}
 \def\xx{{\boldsymbol x}}
@@
 \def\bu{{\boldsymbol u}}
+\def\be{{\boldsymbol e}}
 \def\bl{{\boldsymbol \ell}}
 \def\ff{{\boldsymbol f}}
+\def\bg{{\boldsymbol g}}
 \def\GG{{\bf G}}
-\def\Gbh{{G_{BH}}}
+\def\Gbh{G^{\textrm{BH}}}
+\def\Glap{G^{\textrm{L}}}
+\def\Ghelm{G^{\textrm{H}}}
+\def\Kfark{K^{\textrm{F}}}
 \def\II{{\bf I}}
 \def\TT{{\bf T}}
-\def\SS{{\bf S}}
-\def\DD{{\bf D}}
+\def\bS{{\bf S}}
+\def\bD{{\bf D}}
+\def\cN{{\mathcal N}}
+\def\cK{{\mathcal K}}
+\def\cB{{\mathcal B}}
+\def\cA{{\mathcal A}}
+\def\cS{{\mathcal S}}
+\def\cSk{{\mathcal S}_k}
+\def\cD{{\mathcal D}}
+\def\cDt{{\mathcal D}^{\intercal}}
+\def\cDk{{\mathcal D}_{k}}
+\def\cDkt{{\mathcal D}_{k}^{\intercal}}
+\def\cW{{\mathcal W}}
+\def\cJ{{\mathcal J}}
+\def\cL{{\mathcal L}}
+\def\cA{{\mathcal A}}
+\def\cM{{\mathcal M}}
+\def\bL{{\mathbb L}}
+\def\bK{{\mathbf K}}
+\def\sint{{\sin{(n \theta)}}}
+\def\cost{{\cos{(n \theta)}}}
+\def\jnkr{J_{n}(kr)}
+\def\jnk{J_{n}(k)}
+\def\jnpkr{J_{n}'(kr)}
+\def\jnppkr{J_{n}''(kr)}
+\def\jnppk{J_{n}''(k)}
+\def\ddr{\frac{d}{dr}}
+
 \def\bsigma{{\boldsymbol \sigma}}
+\def\bpsi{{\boldsymbol \psi}}
 \def\bmu{{\boldsymbol \mu}}
 \def\bnu{{\boldsymbol \nu}}
+\def\brho{{\boldsymbol \rho}}
 \def\btau{{\boldsymbol \tau}}
@@
 \def\littleo{o}
+
+\def\Im{{\textrm{\textup{Im}}}}
+
 \newcommand\dwdn{\frac{\partial w}{\partial n}}
+\newcommand{\cI}{\mathcal I}
 \newcommand{\cC}{\mathcal C}
+\newcommand{\bbmat}{\begin{bmatrix}}
+\newcommand{\ebmat}{\end{bmatrix}}
+
+\newcommand{\note}[1]{ {\color{red} #1 }}
+
+\def\pv{\textrm{P.V.} }
 
@@
 \newtheorem{lem}{Lemma}
+\newtheorem{cor}{Corollary}
+\newtheorem{thrm}{Theorem}
+\newtheorem{definition}{Definition}
 
@@
 
-\title{A Fredholm operator approach to the plate
-buckling problem}
-\author{Askham and Rachh}
+\title{A boundary integral equation approach to
+  computing eigenvalues of the Stokes operator}
+%A Fredholm integral equation approach to
+%  computing Stokes eigenvalues in the plane
+\author{Travis Askham and Manas Rachh}
 \date{\today}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\abstract{The Stokes eigenvalue problem is a common
+  model problem in the numerical analysis of
+  the eigenvalues of higher-order partial differential
+  equations.
+  }
 
@@
 \input{02prelim}
-\input{03inteq}
-\input{04analyze}
-\input{05results}
-\input{06conclude}
+\input{03analysis}
+\input{04numerical}
+\input{05conclusion}
 
+\appendix
+
+\input{appendix}
 \bibliographystyle{plain}

### 2019-03-28 doc/draft-01-stokes/05conclusion.tex
first pass at abstract

@@
 %
+When addressing high frequency problems,
+the fast-direct solver used to evaluate
+determinants in this paper will no longer
+have near-linear scaling~\cite{ho2012fast}.
+%
+The design of fast-direct solvers in this
+regime is the subject of ongoing research, and
+to the best of our knowledge, fast determinant
+computation at high frequency is an open
+question.
+%
 Finally, it is worth exploring alternatives
@@
 for layer potentials that are not trace class
-on the boundary.
+on the boundary or for problems at higher
+frequencies.

### 2019-03-28 doc/draft-01-stokes/stokes-eig.tex
first pass at abstract

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\abstract{The Stokes eigenvalue problem is a common
-  model problem in the numerical analysis of
-  the eigenvalues of higher-order partial differential
-  equations.
+\abstract{The boundary integral equation (BIE) framework
+  provides robust and scalable eigenvalue computations, which
+  owes to the fact that only the boundary of the domain
+  must be discretized and that there is no high frequency
+  ``pollution'' when using a Green's function to analytically
+  represent the propagation of oscillatory waves.
+  %
+  In this paper, we detail the theoretical justification
+  for a BIE approach to the Stokes eigenvalue problem on
+  simply and multiply-connected planar domains, which entails
+  a treatment of the uniqueness theory for oscillatory
+  Stokes equations on exterior domains. 
+  %
+  Then, using well-established techniques for
+  discretizing BIEs and fast linear algebra,
+  we present numerical results which confirm
+  the analytical claims of the paper and demonstrate
+  the efficiency of the overall approach.
 }

### 2019-03-29 doc/draft-01-stokes/04numerical.tex
add early changes to numerical section

@@
 \label{sec:numerical}
+
+In order to turn the BIEs analyzed
+above into discrete linear systems,
+we require some standard techniques
+from the BIE literature.
+
+Let the boundary be divided into $N_p$
+panels.
+%
+We parameterize panel $j$ as
+$\bx_j(t)$, with $t$ ranging over the
+interval $[-1,1]$.
+%
+Each component of $\bx_j$ is taken to be
+a polynomial interpolant over the
+standard 16th order Legendre nodes on
+$[-1,1]$, denoted by $t_n$, so that
+the total number of discretization
+points is $N=16N_p$.
+%
+See \cref{fig:panels} for an example
+discretization.
+%
+Another important quantity below is the
+arc-length density of a panel, which
+we denote by $s_j(t) := |\bx'_j(t)|$.
+%
+Finally, we denote the set of panels
+which are adjacent to panel $i$
+by $A(i)$. On a closed curve,
+$A(i)$ contains two integers.
+
+The integral kernels of the single and
+double layer potentials have weak
+singularities of the form $r^p\log r$
+which require special quadrature rules to
+achieve high-order accuracy.
+%
+In the examples below, we use generalized
+Gaussian quadrature (GGQ)~\cite{bremer2010}.
+%
+To demonstrate the idea, we consider
+evaluating the convolution of a kernel
+$K$ with a density $\sigma$
+at the boundary node $\xx_j(t_l)$.
+%
+GGQ is a Nystr\"{o}m-type discretization ---
+the density is approximated 
+by its values at the discretization nodes,
+which we denote by
+$\sigma_{qp} \approx \sigma(\xx_q(t_p))$.
+%
+The basis of a GGQ is a set of 
+support nodes and weights for the
+contribution to the integral from the
+``self'' panel (panel $j$) and the adjacent
+panels (with index in $A(j)$).
+%
+
+For the self panel, there is a special set
+of nodes and weights for each interpolation
+point. Denote the nodes and weights
+for interpolation point $l$ by $t^{(l)}_{n}$
+and $w^{(l)}_{n}$, respectively, with
+$1\leq l \leq 16$ and $1\leq n \leq N_s$.
+%
+The adjacent panels are handled by a single
+set of over-sampled support nodes and weights.
+We denote these nodes and weights
+by $\tilde{t}_n$ and $\tilde{w}_n$, respectively,
+for $1 \leq n \leq N_a$.
+%
+For the rules we used, $N_s = 16$ and
+$N_a = 48$.
+%
+The contribution of other panels is assumed
+to be given to high accuracy by the standard
+Gauss-Legendre weights, which we denote
+by $w_n$.
+%
+Adding these contributions together, we obtain the
+quadrature
+
+\begin{multline}
+  \int_\Gamma K(\xx_i(t_l),\yy) \, \sigma(\yy)
+  \, dS(\yy) \approx \\
+  \sum_{p=1}^{16} \sum_{n=1}^{N_s}
+  w^{(l)}_{n} K(\xx_i(t_l),\xx_i({t}^{(l)}_{n}))
+  s_i({t}^{(l)}_{n}) B^{(l)}_{np} \sigma_{ip} \quad \textrm{(self)}
+  \\
+  + \sum_{q\in A(i)} \sum_{p=1}^{16} \sum_{n=1}^{N_a}
+  \tilde{w}_jK(\xx_i(t_l),\xx_q(\tilde{t}_n)) s_q(\tilde{t}_n)
+  C_{np} \sigma_{qp}
+  \quad \textrm{(adjacent)} \\
+  + \sum_{q\neq i, q\not\in A(i)} \sum_{p=1}^{16}
+  w_p K(\xx_i(t_l),\xx_q(t_p)) s_q(t_p)
+  \sigma_{qp} \quad \textrm{(far)} \nonumber \; ,
+\end{multline}
+where $\bB^{(l)}$ and $\bC$ are interpolation
+matrices from the standard Legendre nodes
+to the self and adjacent panel support nodes,
+respectively. Observe that the quadrature is
+linear in $\sigma_{qp}$. In practice, we pre-compute
+and store the self and adjacent matrix entries for each
+interpolation point, which is a parallelizable
+$O(N)$ calculation. The ``far'' interactions
+are computed on-the-fly.
+
+\subsection{Spurious eigenvalues --- annulus}
+\label{subsec:spurannulus}
+
+\subsection{Convergence study --- annulus}
+\label{subsec:convannulus}
+
+\subsection{Robustness on a nearly multiply connected domain}
+\label{subsec:crescent}
+
+\subsection{Eigenvalues of a domain with several inclusions}

### 2019-03-29 doc/draft-01-stokes/stokes-eig.tex
add early changes to numerical section

@@
 \def\bD{{\bf D}}
+\def\bC{{\bf C}}
+\def\bB{{\bf B}}
 \def\cN{{\mathcal N}}
@@
 \abstract{The boundary integral equation (BIE) framework
-  provides robust and scalable eigenvalue computations, which
-  owes to the fact that only the boundary of the domain
-  must be discretized and that there is no high frequency
-  ``pollution'' when using a Green's function to analytically
-  represent the propagation of oscillatory waves.
+  provides robust and scalable eigenvalue computations
+  due to (a) the reduction in the dimension of the problem to
+  be discretized and (b)
+  the absence of high frequency ``pollution'' when using
+  a Green's function to represent propagating waves.
   %

### 2019-03-31 doc/draft-01-stokes/04numerical.tex
update numerical section

@@
 %
-The basis of a GGQ is a set of 
+The basis of a GGQ rule is a set of 
 support nodes and weights for the
@@
 
-\subsection{Spurious eigenvalues --- annulus}
+Once the discretization is set, we can form
+a compressed representation of the system matrix
+using recursive skeletonization~\cite{ho2012fast}.
+%
+We use the recursive skeletonization algorithm
+included in the fast linear algebra in
+MATLAB (\texttt{FLAM}) package by
+Kenneth Ho~\cite{hoFLAM_1253582}.
+%
+At low-to-medium frequencies, the scaling
+of the recursive skeletonization algorithm
+is $O(N\log N)$ in operation count and
+storage and allows for a fast determinant
+calculation in $O(N\log N)$ time as a
+follow-up step, by using a generalization
+of the Sylvester determinant formula.
+%
+At higher-frequencies,
+the recursive skeletonization procedure,
+which is based on the assumption that off-diagonal
+blocks of the matrix are of low rank,
+breaks down and does not offer a speed advantage.
+%
+These algorithms take a precision parameter
+$\epsflam$ which determines the
+accuracy to which any sub-blocks of the matrix
+should be compressed. In all experiments,
+we set $\epsflam = 10^{-14}$.
+
+To estimate the eigenvalues, we fit a Chebyshev
+interpolant to the discretized determinant as a
+function of $k$ on intervals.
+%
+This is done adaptively so that the Chebyshev
+coefficients of the determinant have decayed
+to the point that the ratio of the last
+coefficient to the largest coefficient is below
+some threshold.
+%
+In all experiments, we set this threshold
+as $\epscheb = 10^{-13}$.
+%
+We perform this fit using the \texttt{chebfun}
+utility in the package of the same name
+\cite{driscoll2014chebfun}
+so that we can make use
+of the \texttt{roots} utility to approximate
+the roots of the determinant.
+
+Below, we let $D^N_k$, $S^N_k$ and $W^N$ denote
+the discretized versions of the $\cDk$,
+$\cSk$, and $\cW$ operators, respectively.
+
+\subsection{Eigenvalues of an annulus}
+
+\subsubsection{Spurious eigenvalues}
 \label{subsec:spurannulus}
 
-\subsection{Convergence study --- annulus}
+\subsubsection{Convergence study}
 \label{subsec:convannulus}
 
-\subsection{Robustness on a nearly multiply connected domain}
-\label{subsec:crescent}
+\subsection{Eigenvalues of a barbell-shaped domain}
+\label{subsec:barbell}
+
+%\subsection{Robustness on a nearly multiply connected domain}
+%\label{subsec:crescent}
 

### 2019-03-31 doc/draft-01-stokes/stokes-eig.tex
update numerical section

@@
 
+\def\epsflam{{\epsilon_{\texttt{FLAM}}}}
+\def\epscheb{{\epsilon_{\texttt{CHEB}}}}
+
 \newcommand\dwdn{\frac{\partial w}{\partial n}}
@@
   Then, using well-established techniques for
-  discretizing BIEs and fast linear algebra,
+  discretizing BIEs,
   we present numerical results which confirm

### 2019-04-03 doc/draft-01-stokes/04numerical.tex
update numerical section, add barbell driver

@@
 %
-We use the recursive skeletonization algorithm
+We use the implementation of this procedure
 included in the fast linear algebra in
-MATLAB (\texttt{FLAM}) package by
-Kenneth Ho~\cite{hoFLAM_1253582}.
+MATLAB (\texttt{FLAM}) package
+\cite{hoFLAM_1253582}.
 %
@@
 is $O(N\log N)$ in operation count and
-storage and allows for a fast determinant
+storage and, by using a generalization
+of the Sylvester determinant formula,
+allows for a fast determinant
 calculation in $O(N\log N)$ time as a
-follow-up step, by using a generalization
-of the Sylvester determinant formula.
+follow-up step.
 %

### 2019-04-03 matlab/example/example_barbell_001.m

@@ -1,0 +1,100 @@
+
+%EXAMPLE_BARBELL_001
+%
+% compute a chebfun representation of the fredholm determinant 
+% of the system I-2D for a domain on the interval [0.5,24.5]
+% save chebfun, domain, and some settings to a file
+
+filebase = 'example_barbell_001'; 
+timeref = datestr(now,'_yyyymmdd_HHMMSS');
+fileout = [filebase, timeref, '.mat'];
+
+
+chebabs = cell(12,1);
+for j = 1:length(chebabs)
+    chebabs{j} = 0.5*[1.0*j 1.0*(j+1)];
+end
+
+max_rzk = chebabs{end}(end); lam = 2*pi/max_rzk;
+
+seed = 8675309;
+rng(seed);
+addpath('../src')
+addpath('../example')
+addpath('../../mwrap')
+addpath('~/Dropbox/MATLAB/chebfun/')
+addpath(genpath('~/Dropbox/MATLAB/FLAM'))
+
+
+opts = [];
+opts.autowidths = false;
+opts.autowidthsfac = 0.1;
+
+
+verts = barbell_example_001(6,3);
+
+opts.widths = 0.1*ones(size(verts,2),1);
+opts.eps = 1e-12;
+
+chunker1 = chunkcorner(verts,opts);
+
+
+optsref = [];
+optsref.nchmax = 10000;
+optsref.maxchunklen = lam;
+
+checkadjinfo(chunker1);
+
+chunkert = chunkrefine(chunker1,optsref);
+
+checkadjinfo(chunkert);
+
+chunkers{1} = chunkert;
+
+[chunker,nchs] = chunkermerge(chunkers);
+
+%
+
+xs = chunker.chunks(1,:,:); xs = xs(:);
+ys = chunker.chunks(2,:,:); ys = ys(:);
+
+rnorms = chunknormals(chunker);
+
+intparams.intorder = chunker.k;
+
+hold off
+quiver(xs,ys,rnorms(1,:).',rnorms(2,:).')
+hold on
+scatter(xs,ys)
+
+%%
+
+% build matrix
+
+cd = -2.0 + 1i*0.0;
+cs = 0;
+ncomp = length(nchs);
+
+%
+
+opts = []; opts.FLAM = 1; opts.verb = true;
+detfun = @(zk) ostokes_determinant(zk,chunker,nchs,cs, ...
+    cd,opts);   
+
+p = chebfunpref; p.chebfuneps = 1.0e-13;
[…]

### 2019-04-03 matlab/src/find_unique_evals.m

@@ -12,8 +12,8 @@ if length(iplot1) < 2
 else
     diffs = diff(rts(iplot1));
     iremove = find(abs(diffs) < abs_eps);
-    iremover = iplot1( iremove(sings(iplot1(iremove))<sings(iplot1(iremove+1))));
-    iremovel = iplot1( iremove(sings(iplot1(iremove))>= sings(iplot1(iremove+1)))+1);
+    iremover = iplot1( iremove(sings(iplot1(iremove))<sings(iplot1(iremove+1)))+1);
+    iremovel = iplot1( iremove(sings(iplot1(iremove))>= sings(iplot1(iremove+1))));
     iplot = setdiff(iplot1(:),[iremover(:);iremovel(:)]);
     [~,isort] = sort(real(rts(iplot)));
     iplot = iplot(isort);

### 2019-04-03 matlab/src/ostokes_determinant.m

@@ -129,6 +129,7 @@ if opts.FLAM == 1
     cfprintf('time %5.2e\n',t5)
 
     cfprintf('total time %6.3e\n',t3+t4+t5)
+    cfprintf('determinant = %5.2e\n',d)
     
     varargout{1} = F_wpre;
 

### 2019-04-03 matlab/test/test_corners.m

@@ -1,0 +1,42 @@
+
+%TEST_CORNERS
+%
+% This file tests whether or not the polygon routine
+% in chunks.mw is working
+
+addpath('../src','../../mwrap')
+
+opts = [];
+opts.autowidths = false;
+opts.autowidthsfac = 0.1;
+
+opts.eps = 1e2;
+
+verts = barbell_example_001(6,3);
+
+opts.widths = 0.3*ones(size(verts,2),1);
+
+chunker = chunkcorner(verts,opts);
+
+chunker.nch
+
+%
+
+nch = chunker.nch;
+k = chunker.k;
+
+optsref = [];
+optsref.nchmax = 10000;
+optsref.maxchunklen = 0.01;
+
+chunker2 = chunkrefine(chunker,optsref);
+
+%%
+
+xs = chunker.chunks(1,:,:); xs = xs(:);
+ys = chunker.chunks(2,:,:); ys = ys(:);
+
+figure(1)
+clf
+scatter(xs,ys,'rx')
+axis equal

### 2019-04-03 doc/draft-01-stokes/03analysis.tex
add barbell plot

@@
 as a numerical tool for computing the Stokes eigenvalues
-follows in a straightforward manner from the results
+follow in a straightforward manner from the results
 in~\cite{zhao2015robust}.

### 2019-04-03 doc/draft-01-stokes/05conclusion.tex
add barbell plot

@@
 %
-However, there has been recent progress
+When using the eigenfunctions as a trial
+basis for simulating the Navier--Stokes
+equations~\cite{batcho1994generalized},
+it is necessary to handle domains
+with corners because the domains of interest
+arise from domain decomposition, e.g.
+dividing a larger domain into 
+rectangles or triangles.
+Fortunately, there has been recent progress
 toward efficient discretization of the
@@
 \cite{helsing2008corner,serkh2016solution,rachh2017solution,helsing2018integral}
-which makes such problems tractable.
+which makes the solution of such problems
+tractable.
 %

### 2019-04-03 doc/draft-01-stokes/03analysis.tex
adding impendence problems, moving neumann proof to main paper

@@
 for the scalar Helmholtz equation.
-%
-First, we define the interior boundary value problems
-of interest, which is straightforward.
-%
-For the exterior problems, we introduce a radiation condition
-for the equations and establish that, under certain assumptions,
-the standard layer potentials satisfy the radiation condition.
-%
-By including the radiation condition, it is then
-possible to define well-posed versions of the
-exterior boundary value problems.
-%
-Then we derive a number of uniqueness
-results for some standard boundary value problems
-on exterior domains.
+While uniqueness results for interior Dirchilet, Neumann, and impedance
+problems follow from energy considerations and compactness
+arguments, the proofs for uniqueness of exterior
+results are more involved. 
+In particular,
+this entails making the exterior problems
+well-posed by imposing an appropriate radiaiton condition.
+We present well-posed boundary value formulations 
+for both interior and exterior Dirichlet, Neumann and impedance
+boundary value problems, and also
+present uniqueness results for all of them.
 
@@
     \bt &= \bg \quad \bx \in \Gamma \, .
+  \end{aligned}
+  \end{equation}
+\end{definition}
+
+\begin{definition}[Interior impedance problem]
+  Let $\bh \in C(\Omega)$ be given and suppose 
+  $\eta \in \mathbb{C}$ with $\Re{(\eta)},\Im{(\eta)}>0$. 
+  Find $(\bu,p) \in A(\Omega)$  such that
+  \begin{equation}
+  \begin{aligned} \label{eq:neu_interior}
+    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in \Omega \, ,\\
+    \nabla \cdot \bu &= 0 \quad \bx \in \Omega \, ,  \\
+    \bt - i \eta \bu &= \bh \quad \bx \in \Gamma \, .
   \end{aligned}
@@
 Consider the Stokeslet induced by an arbitrary charge
-$k^2 \bpsi$ at the origin where $\psi \in \mathbb{C}^2$ 
+$k^2 \bpsi$ at the origin where $\bpsi \in \mathbb{C}^2$ 
 is a constant. Let $r = |\xx|$,
@@
 
+\begin{definition}[Exterior Impedence problem]
+  \label{def:neu_exterior}  
+  Let $\bh \in C(\Gamma)$ be given and suppose that
+  $\eta \in \mathbb{C}$ with $\Re{(\eta)},\Im{(\eta)} >0$. 
+  Find $(\bu,p) \in A(E)$
+  such that
+  \begin{equation}
+  \begin{aligned} \label{eq:neu_exterior}
+    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
+    \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
+    \bt - i\eta \bu &= \bh \quad \bx \in \Gamma \, ,
+  \end{aligned}
+  \end{equation}
+  and $(\bu,p)$ satisfies the radiation condition in
+  \cref{def:radcond}.
+\end{definition}
+
 \subsection{Uniqueness results}
@@
   it is clear that $\bu \equiv 0$, if $\text{Im}(k) \neq 0$.
+\end{proof}
+
+In the following lemma, we prove uniqueness for the
+interior impedence problem.
+
+\begin{thrm}
+  Let $\Omega$ be a bounded domain and suppose that
+  $\Re(k),\Im (k) > 0$. Then the interior
+  impendence problem has a unique solution.
+\end{thrm}
+\begin{proof}
+  Plugging in $\bt = i\eta \bu$ in~\cref{eq:greenlike}
+  and taking the imaginary part, we get
+  \begin{equation}
+   2 \Re{(k)} \Im{(k)} \int_{\Omega} |\bu|^2\, dV + 2\Re{(\eta)} \int_{\Gamma}
+   |\bu|^2 \, dS = 0 \, ,
+  \end{equation}
+  from which it is is clear that $\bu \equiv 0$, since
+  $\Re{(\eta)}, \Re{(k)}, \Im{(k)} > 0$.
 \end{proof}
@@
 \begin{thrm}[Uniqueness of the Exterior Neumann Problem]
-  Let the unbounded region $E$ be given as the exterior
-  of one simply connected domain.
+  Suppose that $\Omega$ is the union of a finite collection 
+  of simply connected domains, i.e. $\Omega = \bigcup_{i=1}^m \Omega_{i}$
+  for some $m \in \N$, with $C^{2}$ boundaries, 
+  and let $E = \R^{2} \setminus \bar{\Omega}$ denote its exterior;
+  see~\cref{fig:ext_dom} for an example with $m=4$.
+  Let $\Gamma_{i}$ denote the boundary of $\Omega_{i}$, 
+  and $\Gamma = \bigcup_{i=1}^{m} \Gamma_{i}$ denote the boundary
+  of $\Omega$.
   Suppose that $\Im(k)\geq 0$ and 
@@
 Because $0 = \btau \cdot \bt = 2\partial_{\tau\nu} p/k^2$,
-$\partial_\nu p $ is a constant on $\Gamma$.
+$\partial_\nu p  = c_{i}$ on $\Gamma_{i}$ for each $\Gamma_{i}$,
+where $c_{i}$ is a constant. 
 Observe that $|\bu|$ and $|\be(\bu)|$ must be $O(1/r)$ as
@@
 as $r\to\infty$.
-Using this bound and that $p$ is harmonic,
-the divergence theorem implies that $\partial_\nu p=0$ on $\Gamma$.
-Thus, $\bt = -p\bnu$ so that $p = 0$ on $\Gamma$. By the uniqueness
-of solutions to the Dirichlet problem for Laplace's equation,
-we have that $p=0$ so that $\uu \equiv 0$.
-\end{proof}
-
-\begin{remark}
-For proving the correspondence between Stokes eigenvalues
-for bounded regions, $\Omega$, and the non-invertibility
-of corresponding second kind integral equations defined on
-the boundary, $\Gamma$, we only need the uniqueness result
-for the Neumann problem in the exterior of a single
-simply connected domain. The proof of the exterior
-Neumann problem in the exterior of several
-obstacles is more involved and presented
-in~\cref{app:neuuniqueness}.
-\end{remark}
+Since the boundary is $C^{2}$ and the boundary data for $p$
+is analytic, we conclude that $p$ is $C^{2}$ in
+$\overline{E}$.
+Furthermore, $\bt=0$ implies $p \bnu = 2\nabla \partial_{\nu} p/k^2$, 
+and taking the dot
+product with $\bnu$, we get
+$p = 2\partial_{\nu \nu}p/k^2$. 
+It then follows that
+$p = -2\partial_{\tau \tau}p/k^2$ on $\Gamma$ since 
+$p$ is harmonic in $E$ and $C^{2}$ in $\overline{E}$. 
+Since $p$ satisfies the radiation condition at $\infty$,
+we have
+\begin{equation}
+\begin{aligned}
+\int_{E} |\nabla p|^2 dV &= 
+\sum_{i=1}^{m} \int_{\Gamma_{i}} p \partial_{\nu}p \,dS \\
+&= \sum_{i=1}^{m} c_{i} \int_{\Gamma_{i}} p \,dS \quad \text{(Since $\partial_{\nu} p = c_{i}$ on
+$\Gamma_{i}$)} \\ 
+&= -\sum_{i=1}^{m} \frac{2c_{i}}{k^2} \int_{\Gamma_{i}} \partial_{\tau \tau} p \,dS 
+\quad \text{(Since $p = -\partial_{\tau \tau}p/k^2$ on $\Gamma$)} \\
+&= 0
+\end{aligned}
+\end{equation}
+Thus, $p$ is a constant in $E$. Furthermore, since $p\to 0$ at $\infty$, 
+we conclude that $p\equiv 0$ in $E$. 
+Finally, since $k^2 \bu = \nabla p$, we conclude that $\bu\equiv 0$ in 
+$E$.
+\end{proof}
 
@@
 
-From \cref{thrm:rep-theorem} we have 
+To prove the converse, note that from \cref{thrm:rep-theorem} we have 
   \begin{equation} 
@@
   \begin{equation}
-    \bt^{-} = (\cDt_{k} + \frac{1}{2} \cI) \bt^{-} \,
+    \bt^{-} = \left(\cDt_{k} + \frac{1}{2} \cI\right) \bt^{-} \,
     \implies \left(\cI - 2\cDt_{k} \right) 
@@
   Suppose that $k^2$ is a Neumann eigenvalue of $\Omega_{1}$.
-  Let $\tilde{\bu}$ be the eigenmode corresponding to $k^2$. 
+  Let $\tilde{\bu}$ be the eigenfunction corresponding to $k^2$. 
   Note that $\tilde{\bu}$ is not identically $0$ on the boundary
@@
 of the obstacles $\Omega_{j}$.
-Applying the energy-type identity \cref{eq:greenlike}
-and using the fact that 
-the interior limits with respect to $\Omega_{j}$
-of the surface traction and the velocity
-are $i\eta \bmu$ and $\bmu$ respectively, we get
-\begin{equation}
-\int_{\Omega_{j}} (|\be(\bu)|^{2} - \overline{k}^{2} |\bu|^2) dV 
-= \int_{\Gamma_{j}} \bu \cdot \overline{\bt} dS = 
-i\overline{\eta}\int_{\Gamma_{j}} |\bmu|^2 dS \, .
-\end{equation}
-Taking the imaginary part of the above equation,
-we get
-\begin{equation}
-2 \text{Re}(k) \text{Im}(k) \int_{\Omega_{j}} |\bu|^2 + \text{Re}(\eta)
-\int_{\Gamma_{j}} |\bmu|^2 dS = 0 \, .
-\end{equation}
-Since $\text{Re}(\eta)>0$, this implies that
-$\bmu=0$ for $\xx \in \Gamma_{j}$, $j=1,2,\ldots m$. 
+Using the jump conditions in~\cref{lem:jump-conds},
+we get that $\bt^{+} = i\eta \bmu$ and $\bu^{+} = \bmu$.
+From the uniqueness of solutions to the interior 
+impedence problem, we conlcude that $\bu \equiv 0$
+in $\Omega_{j}$, which in particular implies
+that $\bmu = \bu^{+} = 0$ for $\xx \in \Gamma_{j}$,
+$j=1,2,\ldots m$.
 Thus, $\cI - 2\cD_{k} -2i\eta\cS_{k} -2\cW$ is

### 2019-04-03 doc/draft-01-stokes/appendix.tex
adding impendence problems, moving neumann proof to main paper

--- 2019-03-27 doc/draft-01-stokes/appendix.tex
@@
-\section{Uniqueness of the Neumann problem in the exterior
-  of several obstacles}
-\label{app:neuuniqueness}
-In this section, we prove the uniqueness result for the oscillatory
-Stokes problem with Neumann boundary conditions on the exterior
-of several simply connected obstacles. 
-\begin{thrm}[Uniqueness of the Exterior Neumann Problem]
-  Suppose that $\Omega$ is the union of a finite collection 
-  of simply connected domains, i.e. $\Omega = \bigcup_{i=1}^m \Omega_{i}$
-  for some $m \in \N$, with $C^{2}$ boundaries, 
-  and let $E = \R^{2} \setminus \bar{\Omega}$ denote its exterior;
-  see~\cref{fig:ext_dom} for an example with $m=4$.
-  Let $\Gamma_{i}$ denote the boundary of $\Omega_{i}$, 
-  and $\Gamma = \bigcup_{i=1}^{m} \Gamma_{i}$ denote the boundary
-  of $\Omega$.
-  Suppose that $\Im(k)\geq 0$ and 
-  that $(\bu,p)$ is a radiating solution to the oscillatory Stokes
-  equation in $E$ with $\bt = 0$ on the boundary $\Gamma$, then
-  $\bu \equiv 0$ in $E$.
-\end{thrm}
-
-\begin{proof}
-Since $\bt = 0$ on $\Gamma$, it follows
-from~\cref{eq:repinfest} that
-\begin{equation}
-\lim_{r\to\infty}
-\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
-2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |\be(\bu)|^2 \right)
-dV = 0 \; . \nonumber
-\end{equation}
-
-Suppose that $\Im(k) > 0$. It is then immediate
-that $\bu \equiv 0$ in $E$.
-
-Suppose that $k$ is real. It is clear that
-\begin{equation}
-\lim_{r\to\infty} \int_{|\by|=r} |\bu|^2 dS = 0 \, . \nonumber
-\end{equation}
-Thus, the conditions on $\bu$ and $k$ in \cref{lem:rellich}
-are satisfied, and each component of $\bu$ is a harmonic function
-with $\bu \to 0$ as $r \to \infty$. Furthermore, as observed
-in \cref{rmk:harmu}, $k^2 \bu = \nabla p$. Then, the boundary
-condition becomes $0 = \bt = -p \bnu + 2 \nabla \partial_\nu p/k^2$.
-Because $0 = \btau \cdot \bt = 2\partial_{\tau\nu} p/k^2$,
-$\partial_\nu p  = c_{i}$ on $\Gamma_{i}$ for each $\Gamma_{i}$,
-where $c_{i}$ is a constant. 
-Observe that $|\bu|$ and $|\be(\bu)|$ must be $O(1/r)$ as
-$r\to\infty$. Thus,
-for a radiating pair $(\bu,p)$ with $p$ harmonic,
-we have that $|p| = O(1/r)$ and $|\nabla p| = O(1/r^2)$
-as $r\to\infty$.
-Since the boundary is $C^{2}$ and the boundary data for $p$
-is analytic, we conclude that $p$ is $C^{2}$ in
-$\overline{E}$.
-Furthermore, $\bt=0$ implies $p \bnu = 2\nabla \partial_{\nu} p/k^2$, 
-and taking the dot
-product with $\bnu$, we get
-$p = 2\partial_{\nu \nu}p/k^2$. 
-It then follows that
-$p = -2\partial_{\tau \tau}p/k^2$ on $\Gamma$ since 
-$p$ is harmonic in $E$ and $C^{2}$ in $\overline{E}$. 
-Since $p$ satisfies the radiation condition at $\infty$,
-we have
-\begin{equation}
-\begin{aligned}
-\int_{E} |\nabla p|^2 dV &= 
-\sum_{i=1}^{m} \int_{\Gamma_{i}} p \partial_{\nu}p \,dS \\
-&= \sum_{i=1}^{m} c_{i} \int_{\Gamma_{i}} p \,dS \quad \text{(Since $\partial_{\nu} p = c_{i}$ on
-$\Gamma_{i}$)} \\ 
-&= -\sum_{i=1}^{m} \frac{2c_{i}}{k^2} \int_{\Gamma_{i}} \partial_{\tau \tau} p \,dS 
-\quad \text{(Since $p = -\partial_{\tau \tau}p/k^2$ on $\Gamma$)} \\
-&= 0
-\end{aligned}
-\end{equation}
-Thus, $p$ is a constant in $E$. Furthermore, since $p\to 0$ at $\infty$, 
-we conclude that $p\equiv 0$ in $E$. 
-Finally, since $k^2 \bu = \nabla p$, we conclude that $\bu\equiv 0$ in 
-$E$.
-\end{proof}
-
 \section{Dirichlet eigenvalues and eigenfunctions on the unit disk}

### 2019-04-03 doc/draft-01-stokes/stokes-eig.tex
adding impendence problems, moving neumann proof to main paper

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\abstract{The boundary integral equation (BIE) framework
+\abstract{
+  The eigenvalues and eigenfunctions of the Stokes 
+  operator have been the subject of intense analytical
+  investigation and also have many applications
+  in studying turbulence in numerical simulation
+  of Navier Stokes equations.
+  Since the Stokes operator is a fourth-order operator,
+  the numerical computation of these eigenvalues 
+  and the corresponding eigenfunctions 
+  is a challenging task particularly in complex
+  geometries and at high frequencies.
+  The boundary integral equation (BIE) framework
   provides robust and scalable eigenvalue computations

### 2019-04-05 doc/draft-01-stokes/03analysis.tex
Updating analysis and mathematica notebook

--- 2019-03-26 doc/draft-01-stokes/03analysis.tex
@@
 = -i\eta \bmu(\xx)$ and $\bu^{+} = -\bmu(\xx)$ on $\Gamma$, i.e.
-$\bt^{+}=i\eta u^{+}$ and $u^{+}$ satisfies the homogeneous
+$\bt^{+}=i\eta \bu^{+}$ and $\bu^{+}$ satisfies the homogeneous
 exterior impedance problem.
@@
 \label{sec:dets}
-Above, we established the correspondence between
-the non-invertibility of certain integral equations
-and Stokes eigenvalues. In this section, we show
+In this section, we show
 how the Fredholm determinant can be used

### 2019-04-05 doc/draft-01-stokes/01intro.tex

@@
 Let $\Omega \subset \R^2$
-be a bounded domain with $C^2$ boundary.
+be a bounded domain with $C^2$ boundary denoted by $\Gamma$.
 %
@@
 that finite element methods suffer from
-high-frequency ``pollution'' when $k$ is large
+high-frequency ``pollution'' due to the 
+large number of unknowns required to resolve
+the computation when $k$ is large
 \cite{babuska1997pollution}.
@@
 The first requirement is straightforward to
-satisfy because the
+satisfy because 
 well-known layer potential representations for the
@@
 %
-That section also includes numerical experiments
+We also present numerical experiments
 which demonstrate some of the paper's analytical

### 2019-04-05 doc/draft-01-stokes/02prelim.tex

@@
 and upper-case (e.g. $\mathbf{T}$). 
-Subscript indices of non-bold characters (e.g. $h_j$ or $T_{jkl}$)
+Subscript indices of non-bold characters (e.g. $h_j$ or $T_{ij\ell}$)
 are used to denote the entries within a vector ($\bh$) or tensor ($\bT$).
@@
 some of the relevant results here, translating to
-the present, oscillatory setting.
+the oscillatory setting.
 
@@
 evaluated in the principal value sense.
+
 For two vector valued
@@
 form
-
 \begin{equation} \label{eq:bi_form}
@@
 the one induced by this form.
-The adjoint of $\cD$ is of particular interest; we have
+
+The adjoint of $\cD$ with respect to the above bilinear form
+is of particular interest; and is given by
 \begin{equation}
@@
 \end{equation}
-
-\begin{remark}
-The operators $\bS,\bD,\cD$ and $\cD^{\intercal}$
-depend on the Helmholtz parameter $k$ of the oscillatory Stokes equation.
-In places where it is essential to highlight this dependence, in a slight
-abuse of notation, we will use the symbols $\bS_{k}, \bD_{k},\cD_{k}$ and $\cDt_{k}$ to 
-denote this dependence.
-\end{remark}
 
@@
 \begin{remark}
-The operators $\bS,\bD, \cS, \cD$, and $\cW$  depend on the boundary 
-of the region $\Gamma$. In places where it is necessary to highlight this dependence
-we will use $A^{\Gamma}$ instead of the operator $A$.
+The operators $\bS,\bD,\cD$ and $\cD^{\intercal}$
+depend on the Helmholtz parameter $k$ of the oscillatory Stokes equation.
+In places where it is essential to highlight this dependence, in a slight
+abuse of notation, we will use the symbols $\bS_{k}, \bD_{k},\cD_{k}$ and $\cDt_{k}$ to 
+denote this dependence.
+Similarly, we will use $A^{\Gamma}$ instead of the operator $A$ to highlight 
+the dependence of the operator $A$ on the boundary of the region $\Gamma$.
 \end{remark}

### 2019-04-05 doc/draft-01-stokes/04numerical.tex
add barbell plot
update numerical section

@@
 \label{sec:numerical}
+
+\subsection{Numerical methods}
+
+\subsubsection{Discretizing the BIE}
 
@@
 a polynomial interpolant over the
-standard 16th order Legendre nodes on
+standard 16th-order Legendre nodes on
 $[-1,1]$, denoted by $t_n$, so that
@@
 Finally, we denote the set of panels
-which are adjacent to panel $i$
-by $A(i)$. On a closed curve,
-$A(i)$ contains two integers.
+which are adjacent to panel $j$
+by $A(j)$. On a closed curve,
+$A(j)$ contains two integers.
 
@@
 which we denote by
-$\sigma_{qp} \approx \sigma(\xx_q(t_p))$.
+$\sigma_{qp} := \sigma(\xx_q(t_p))$.
 %
@@
 
+\begin{remark}
+  \label{rmk:levelrestrict}
+  We ensure that ``far'' interactions
+  are handled to high precision by requiring that
+  no two adjacent panels differ in length
+  by more than a factor of 2. On a domain which does
+  not nearly self-intersect this
+  guarantees that no ``far'' interactions occur
+  which are much closer than 1/2 of a panel away
+  (assuming panels are relatively flat).
+  Because the location of the singularity is
+  bounded away from the panel and the smooth
+  rule is of high order, we obtain a quadrature
+  rule with sufficient precision.
+\end{remark}
+
+\subsubsection{Fast determinant method}
+
 Once the discretization is set, we can form
@@
 
+The compressed representation also allows
+for fast applications of the system matrix,
+its transpose, the inverse of the system
+matrix, and the inverse transpose to
+vectors.
+%
+In particular, this allows us to estimate the
+smallest singular values by performing
+randomized subspace iteration, see
+\cite[Algorithm 4.4]{halko2011finding},
+on the inverse operator.
+%
+Below, we use the smallest singular value
+as a measure of the quality of the
+eigenvalues found by approximating the
+roots of the determinant.
+%
+We also evaluate the second smallest singular
+value if the root finding precedure suggests a
+possible double root.
+
+\subsubsection{Interpolation and root-finding}
+
 To estimate the eigenvalues, we fit a Chebyshev
@@
 
-Below, we let $D^N_k$, $S^N_k$ and $W^N$ denote
-the discretized versions of the $\cDk$,
-$\cSk$, and $\cW$ operators, respectively.
+The \texttt{roots} utility returns the roots
+of the polynomial in the complex plane, with
+some minimal internal processing to remove
+spurious roots.
+%
+Because our numerical determinant evaluation
+is somewhat noisy and we fit the function up to
+precision $\epscheb$, we perform some
+further post-processing to eliminate remaining
+spurious roots.
+%
+We ignore any of the returned roots $z$ with $\imag(z)
+> \sqrt{\epscheb}$, as these are too far from real-valued
+to be non-spurious.
+%
+For the remaining roots, we inspect any
+pairs of roots which are closer than
+$\epsclose = 10^{-5}$.
+%
+For these roots, we compare the resulting
+eigenfunctions evaluated at a large number of points
+within the domain.
+%
+If the eigenfunctions are the same to
+reasonable precision, we declare that these
+roots correspond to a single root and
+retain the root for which the operator
+has the smallest singular value.
+%
+For these near double-roots, we also check
+that there is no two dimensional null-space
+corresponding to the root by estimating the
+second smallest singular value.
 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{fig/barbell_gallery}
+  \caption{Vorticity plots of the first 119 eigenfunctions
+    of the barbell-shaped domain.}
+  \label{fig:barbell_gallery}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \begin{subfigure}[t]{0.4\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{fig/ex_barbell_001_sings_plot}
+    \caption{Smallest singular value corresponding to the
+    first 119 computed eigenfunctions of the barbell-shaped
+    domain.}
+    \label{subfig:barbell_sings}
+  \end{subfigure}
+  ~
+  \begin{subfigure}[t]{0.4\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{fig/ex_barbell_001_coeffs_plot}
+    \caption{Normalized Chebyshev coefficients of $f^N(k)$ on
+      3 different intervals in $k$.}
+    \label{subfig:barbell_coeffs}
+  \end{subfigure}
+  \caption{Diagnostics for the barbell eigenvalues.}
+  \label{fig:barbell_diagnostics}
+\end{figure}
+
+We consider the barbell-shaped domain in \cref{fig:barbell}.
+This domain is the union of a square of side-length 6,
+a square of side-length 3, and a ``bridge'' connecting
+them of height 1 and width 5/2.
+%
+For simplicity, we round the corners of the domain
+to obtain a smooth object.
+%
+Applying the approach described in~\cite{epstein2016smoothed},
+the corners of the domain are rounded using the Gaussian kernel
+\begin{equation}
+  \nonumber
+\phi(x) = \frac{1}{\sqrt{2\pi h}} e^{-x^2/(2 h^2)} \, ,
+\end{equation}
+with $h\approx 0.06$. This leaves the domain unperturbed
+outside of a radius of $0.1$ around each corner.
+%
+The eigenfunctions of such a domain display the well-known
+localization property~\cite{trefethen2006computed}:
+many of the eigenfunctions are approximately supported
+within one of the squares.
+%
+We compute these eigenfunctions corresponding to
+eigenvalues $k^2$ with $k$ in the range
+$0.5 \leq k \leq 6.5$.
+
+%
+The panels are chosen adaptively so that the coordinates,
+the first and second derivatives of the coordinates,
+and the arc-length function are resolved to a precision
+of $10^{-12}$ on each panel.
+%
+This results in $N_p = 412$ after enforcing the
+level-restriction property described in
+\cref{rmk:levelrestrict}
+and enforcing that no panel is larger than
+one wavelength for the largest $k$
+(here $\lambda=2\pi/6.5$).
+
+We compute the eigenvalues as the values of
+$k$ for which $\cI-2\cDk-2\cW$ is non-invertible.
+%
+Let $f^N(k) = \det (\cI^N-2\cDk^N-2\cW^N)$.
+To find the roots of $f^N(k)$, we fit a \texttt{chebfun}
+representation of $f^N(k)$ on each of the intervals
+$[j/2,(j+1)/2]$ for $j = 1,\ldots,12$.
+%
+We plot the absolute value of the Chebyshev coefficients
+of $f^N(k)$ on the intervals $[0.5,1.0]$, $[3.0,3.5]$,
+and $[6.0,6.5]$ in \cref{subfig:barbell_coeffs}.
+%
+As expected, the coefficients decay exponentially
+to zero, with more terms required at higher
+frequencies.
+%
+
+We compute the roots of these Chebyshev interpolants
+and apply the post-processing described above.
+%
+There were 135 total roots: 2 were removed because
+$\Im(z) > \sqrt{\epscheb}$ and 13 pairs were found
+with values within $\epsclose = 10^{-5}$ of each other.
+%
+For these 13 pairs, none corresponded to a double
+root.
+%
+This leaves 119 roots in the range $0\leq k \leq 6.5$.
+%
+We plot the smallest singular value of
+$\cI^N-\cDk^N-2\cW^N$ for each of these roots in
+\cref{subfig:barbell_sings}
+and plot the vorticity of the eigenfunctions
+in \cref{fig:barbell_gallery}.
+%
+The singular values suggest that the quality of the
+eigenvalues is good.
+From the plots, we see that localization occurs
+until about the 100th eigenvalue.
+
+%
+
 %\subsection{Robustness on a nearly multiply connected domain}

### 2019-04-05 matlab/example/example_barbell_001.m

@@ -2,7 +2,7 @@
 %EXAMPLE_BARBELL_001
 %
 % compute a chebfun representation of the fredholm determinant 
-% of the system I-2D for a domain on the interval [0.5,24.5]
+% of the system I-2D for a domain on the interval [0.5,6.5]
 % save chebfun, domain, and some settings to a file
 
 filebase = 'example_barbell_001'; 

### 2019-04-05 matlab/src/find_unique_evals.m

@@ -1,4 +1,4 @@
-function iplot = find_unique_evals(rts,sings,abs_eps,imag_eps)
+function [iplot,ichkdbl] = find_unique_evals(rts,sings,abs_eps,imag_eps)
 %FIND_UNIQUE_EVALS returns indices corresponding to the roots 
 % which seem like they correspond to unique eigenvalues to the
 % desired precision
@@ -9,14 +9,24 @@ iplot1 = isort(abs(imag(rts(isort))) < imag_eps);
 
 if length(iplot1) < 2
     iplot = iplot1;
+    ichkdbl = [];
 else
     diffs = diff(rts(iplot1));
     iremove = find(abs(diffs) < abs_eps);
+    
     iremover = iplot1( iremove(sings(iplot1(iremove))<sings(iplot1(iremove+1)))+1);
+    ichkr = iplot1( iremove(sings(iplot1(iremove))<sings(iplot1(iremove+1))));
     iremovel = iplot1( iremove(sings(iplot1(iremove))>= sings(iplot1(iremove+1))));
+    ichkl = iplot1( iremove(sings(iplot1(iremove))>= sings(iplot1(iremove+1)))+1);
+    
     iplot = setdiff(iplot1(:),[iremover(:);iremovel(:)]);
     [~,isort] = sort(real(rts(iplot)));
     iplot = iplot(isort);
+    
+    ichkdbl = [ichkr(:), iremover(:); ichkl(:), iremovel(:)];
+    [~,isort] = sort(real(rts(ichkdbl(:,1))));
+    ichkdbl = ichkdbl(isort,:);
+    
 end
 
 

### 2019-04-05 matlab/src/rskelf_nullvec.m

@@ -1,20 +1,27 @@
 
-function xnull = rskelf_nullvec(F,nsys,restart,tol,maxit,nref)
+function xnull = rskelf_nullvec(F,nsys,p,q)
 %RSKELF_NULLVEC find nullvec with cheap randomized method
 %
 % (F + u*v.')x = u
 %
 
-ur = randn(nsys,1);
-vr = randn(nsys,1);
+%ur = randn(nsys,nvec);
+%vr = randn(nsys,nvec);
 
-xnull = gmres(@(x) rskelf_plus_mv(x,F,ur,vr),ur,restart,tol,maxit);
+%xnull = zeros(nsys,nvec);
+%for i = 1:nvec
+%    xnull(:,i) = gmres(@(x) rskelf_plus_mv(x,F,ur(:,i),vr(:,i)), ...
+%        ur(:,i),restart,tol,maxit);
+%end
 
-xnull = xnull/norm(xnull);
-for i = 1:nref
+xnull = rskelf_sv(F,randn(nsys,p));
+[xnull,~,~] = qr(xnull,0);
+for i = 1:q
    xnull = rskelf_sv(F,xnull,'T');
+   [xnull,~,~] = qr(xnull,0);
    xnull = rskelf_sv(F,xnull);
-   xnull = xnull/norm(xnull);
+   [xnull,~,~] = qr(xnull,0);
+   
 end
 
 end

### 2019-04-06 doc/draft-01-stokes/04numerical.tex
update numerical section

@@
 %
-We ignore any of the returned roots $z$ with $\imag(z)
+We ignore any of the returned roots $z$ with $|\imag(z)|
 > \sqrt{\epscheb}$, as these are too far from real-valued
@@
 
-We compute the eigenvalues as the values of
+As this is a simply-connected domain,
+the eigenvalues are estimated by finding the values
 $k$ for which $\cI-2\cDk-2\cW$ is non-invertible.
@@
 There were 135 total roots: 2 were removed because
-$\Im(z) > \sqrt{\epscheb}$ and 13 pairs were found
+the imaginary part was too large and 13 pairs were found
 with values within $\epsclose = 10^{-5}$ of each other.

### 2019-04-06 doc/draft-01-stokes/stokes-eig.tex
update numerical section

@@
 \def\epscheb{{\epsilon_{\texttt{CHEB}}}}
+\def\epsclose{{\epsilon_{\textrm{close}}}}
 
@@
   operator have been the subject of intense analytical
-  investigation and also have many applications
-  in studying turbulence in numerical simulation
-  of Navier Stokes equations.
-  Since the Stokes operator is a fourth-order operator,
-  the numerical computation of these eigenvalues 
-  and the corresponding eigenfunctions 
-  is a challenging task particularly in complex
-  geometries and at high frequencies.
+  investigation and they have applications in the study
+  and simulation of the Navier--Stokes equations.
+  %
+  As the Stokes operator is inherently a fourth-order
+  operator,
+  computing these eigenvalues and the corresponding
+  eigenfunctions is a challenging task, particularly in
+  complex geometries and at high frequencies.
+  %
   The boundary integral equation (BIE) framework

### 2019-04-08 doc/draft-01-stokes/04numerical.tex

@@
 %
-We ignore any of the returned roots $z$ with $|\imag(z)|
+Let $\kcheb_l$ denote the roots of the interpolants.
+%
+We ignore any of the returned roots with $|\imag(\kcheb_l)|
 > \sqrt{\epscheb}$, as these are too far from real-valued
@@
 %
-For the remaining roots, we inspect any
-pairs of roots which are closer than
-$\epsclose = 10^{-5}$.
+For the remaining roots, we consider the
+properties of $\real(\kcheb_l)$.
 %
-For these roots, we compare the resulting
-eigenfunctions evaluated at a large number of points
-within the domain.
+We inspect any pairs of roots $(\kcheb_p,\kcheb_q)$
+for which $|\real(\kcheb_p-\kcheb_q)| < \sqrt{\epscheb}$,
+as these are possibly spurious double roots.
 %
-If the eigenfunctions are the same to
-reasonable precision, we declare that these
-roots correspond to a single root and
-retain the root for which the operator
-has the smallest singular value.
+For these pairs, we compare the right singular
+vector of the appropriate BIE operator corresponding
+to the smallest singular value for each of $k=\real(\kcheb_p)$
+and $k=\real(\kcheb_p)$, which we denote by
+$\bv_p$ and $\bv_q$.
+%
+If $\|\bv_p - \bv_q \bv_q^* \bv_p \| < 10^{-5}$, then
+we consider the pair to be spurious.
 %
@@
 corresponding to the root by estimating the
-second smallest singular value.
+second smallest singular value of the BIE operator.
+%
+If this is larger than $10^{-5}$, then we declare
+it to be a simple root.
 
@@
 with $h\approx 0.06$. This leaves the domain unperturbed
-outside of a radius of $0.1$ around each corner.
+to high precision outside of a radius of $0.1$ around
+each corner.
 %
@@
 %
-The panels are chosen adaptively so that the coordinates,
-the first and second derivatives of the coordinates,
-and the arc-length function are resolved to a precision
-of $10^{-12}$ on each panel.
+The panels are divided adaptively so that the smallest
+panels in the rounded corner are smaller than $10^{-2}$.
 %
@@
 %
-There were 135 total roots: 2 were removed because
+There were 135 total roots: 3 were removed because
 the imaginary part was too large and 13 pairs were found
@@
 %
-For these 13 pairs, none corresponded to a double
-root.
+For these 13 pairs, none represented two distinct
+eigenvalues or a double root and all were in fact
+much closer than $\epsclose$.
 %
@@
 \subsection{Eigenvalues of a domain with several inclusions}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{fig/many_inclusions_gallery}
+  \caption{Vorticity plots of...}
+  \label{fig:many_inclusions_gallery}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \begin{subfigure}[t]{0.4\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{fig/ex_many_holes_004_sings_plot}
+    \caption{Smallest singular value corresponding to the
+    first.}
+    \label{subfig:many_inclusions_sings}
+  \end{subfigure}
+  ~
+  \begin{subfigure}[t]{0.4\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{fig/ex_many_holes_004_coeffs_plot}
+    \caption{Normalized Chebyshev coefficients of $f^N(k)$ on
+      3 different intervals in $k$.}
+    \label{subfig:many_inclusions_coeffs}
+  \end{subfigure}
+  \caption{Diagnostics for the ... eigenvalues.}
+  \label{fig:many_inclusions_diagnostics}
+\end{figure}
+
+We now consider the multiply-connected domain in
+\cref{fig:many_holes}.
+% 
+The domain is defined by a smooth rectangular region
+of width 3 and height 2,
+with an array of randomly rotated ``starfish'' shapes
+removed. 
+%
+Such shapes are of interest in
+materials design and micro-fluidics \note{cite}.
+%
+We compute the eigenfunctions corresponding to
+eigenvalues $k^2$ with $k$ in the range
+$3 \leq k \leq 9$ (this range includes the smallest
+eigenvalue).
+
+%
+For this smooth shape, the panels are chosen
+adaptively so that the coordinates, the first
+and second derivatives of the coordinates, and
+the arc-length function are resolved to a precision
+of $10^{-3}$ on each panel.
+%
+This results in $N_p = 224$ after enforcing the
+level-restriction property described in
+\cref{rmk:levelrestrict}
+and enforcing that no panel is larger than
+one wavelength for the largest $k$
+(here $\lambda=2\pi/9$).
+
+As this is a multiply-connected domain,
+the eigenvalues are estimated by finding the values
+$k$ for which $\cI-2\cDk-2i\cSk-2\cW$ is non-invertible.
+%
+Let $f^N(k) = \det (\cI^N-2\cDk^N-2i\cSk^N-2\cW^N)$.
+To find the roots of $f^N(k)$, we fit a \texttt{chebfun}
+representation of $f^N(k)$ on each of the intervals
+$[j/2,(j+1)/2]$ for $j = 6,\ldots,13$ and the intervals
+$[j/4,(j+1)/4]$ for $j = 28,\ldots,35$.
+%
+It should be noted that, due to the relative sizes
+of the domains,
+this represents a lower frequency problem than
+that for the barbell when measured in the number
+of wavelengths across the object.
+%
+Thus, the use of a finer grid here results from
+the difficulty in resolving the Fredholm determinant
+when the kernel is not trace-class.
+%
+We plot the absolute value of the Chebyshev coefficients
+of $f^N(k)$ on the intervals $[3,3.5]$, $[6.5,7]$,
+and $[8.75,9]$ in \cref{subfig:barbell_coeffs}.
+%
+As expected, the coefficients decay exponentially
+to zero, with more terms required at higher
+frequencies (note that the interval $[8.75,9]$ is
+smaller than the others).
+%
+
+We compute the roots of these Chebyshev interpolants
+and apply the post-processing described above.
+%
+There were 103 total roots: 21 were removed because
+the imaginary part was too large and 6 pairs were found
+with values within $\epsclose = 10^{-5}$ of each other.
+%
+For these 6 pairs, none represented two distinct
+eigenvalues or a double root and all were in fact
+much closer than $\epsclose$.
+%
+This leaves 76 roots in the range $0\leq k \leq 9$.
+%
+We plot the smallest singular value of
+$\cI^N-\cDk^N-2i\cSk^n-2\cW^N$ for each of these roots in
+\cref{subfig:many_inclusions_sings}
+and plot the vorticity of the eigenfunctions
+in \cref{fig:many_inclusions_gallery}.
+%
+The singular values suggest that the quality of the
+eigenvalues is good, with a few outliers.
+%
+These outliers correspond to eigenvalues 9 through 12,
+which have 
+The conditioning of the eigenvalue problem depends
+on the distance to the nearest eigenvalue. For
+the 8th through 13th eigenvalues, the average
+spacing between consecutive roots is 0.0447,
+which is much smaller than the average spacing of
+the roots for the first 20 eigenvalues, given by
+0.1132.
+In the plots, we observe a different type of
+localization property, with many of the eigenfunctions
+approximately supported in a small, connected subset
+of the domain. This is consistent with other studies
+\note{cite}
+
+%

### 2019-04-09 doc/draft-01-stokes/04numerical.tex
minor updates

@@
 %
-Let $\kcheb_l$ denote the roots of the interpolants.
+Let $k^{(l)}_\cheb$ denote the roots of the interpolants.
 %
-We ignore any of the returned roots with $|\imag(\kcheb_l)|
+We ignore any of the returned roots with $|\imag(k^{(l)}_\cheb)|
 > \sqrt{\epscheb}$, as these are too far from real-valued
@@
 For the remaining roots, we consider the
-properties of $\real(\kcheb_l)$.
+properties of $\real(k^{(l)}_\cheb)$.
 %
-We inspect any pairs of roots $(\kcheb_p,\kcheb_q)$
-for which $|\real(\kcheb_p-\kcheb_q)| < \sqrt{\epscheb}$,
+We inspect any pairs of roots $(k^{(p)}_\cheb,k^{(q)}_\cheb)$
+for which $|\real(k^{(p)}_\cheb-k^{(q)}_\cheb)| < \sqrt{\epscheb}$,
 as these are possibly spurious double roots.
@@
 vector of the appropriate BIE operator corresponding
-to the smallest singular value for each of $k=\real(\kcheb_p)$
-and $k=\real(\kcheb_p)$, which we denote by
+to the smallest singular value for each of $k=\real(k^{(p)}_\cheb)$
+and $k=\real(k^{(p)}_\cheb)$, which we denote by
 $\bv_p$ and $\bv_q$.
@@
 the imaginary part was too large and 13 pairs were found
-with values within $\epsclose = 10^{-5}$ of each other.
+with values within $\sqrt{\epscheb}$ of each other.
 %
 For these 13 pairs, none represented two distinct
-eigenvalues or a double root and all were in fact
-much closer than $\epsclose$.
+eigenvalues or a double root.
 %
@@
 the imaginary part was too large and 6 pairs were found
-with values within $\epsclose = 10^{-5}$ of each other.
+with values within $\sqrt{\epscheb}$ of each other.
 %
 For these 6 pairs, none represented two distinct
-eigenvalues or a double root and all were in fact
-much closer than $\epsclose$.
+eigenvalues or a double root.
 %
@@
 We plot the smallest singular value of
-$\cI^N-\cDk^N-2i\cSk^n-2\cW^N$ for each of these roots in
+$\cI^N-\cDk^N-2i\cSk^N-2\cW^N$ for each of these roots in
 \cref{subfig:many_inclusions_sings}

### 2019-04-09 doc/draft-01-stokes/03analysis.tex

@@
     \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
-    \bt - i\eta \bu &= \bh \quad \bx \in \Gamma \, ,
+    \bt + i\eta \bu &= \bh \quad \bx \in \Gamma \, ,
   \end{aligned}
@@
     dV \\
-    = 2 \Im \left( k \int_{\Gamma} \bu \cdot
-\overline{\bt} dS  \right) 
+    + 2 \Im \left( k \int_{\Gamma} \bu \cdot 
+\overline{\bt} dS  \right) = 0
   \end{multline}
@@
 \int_{E\cap B_{r}(0)} |2 \be(\bu)|^2 dV =
-\int_{\Gamma} \bu \cdot \overline{\bt} dS
+-\int_{\Gamma} \bu \cdot \overline{\bt} dS
 + \int_{|\by|=r} \bu \cdot \overline{\bt} dS + \overline{k}^2 
@@
 \right) dV \\
-= 2\Im \left ( k \int_{\Gamma} \bu \cdot \overline{\bt} dS \right) \, .
++ 2\Im \left ( k \int_{\Gamma} \bu \cdot \overline{\bt} dS \right) = 0 \, .
 \end{multline*}
@@
   \begin{equation}
-\bt - i \eta \bu = 0 \quad \xx \in \Gamma \, . \nonumber
+\bt + i \eta \bu = 0 \quad \xx \in \Gamma \, . \nonumber
 \end{equation}
@@
 dV \nonumber \\
-& \qquad - 2 \text{Im} \left( k \int_{\Gamma} \bu \cdot \overline{\bt} dS  \right) \\
+& \qquad + 2 \text{Im} \left( k \int_{\Gamma} \bu \cdot \overline{\bt} dS  \right) \\
 &= 
@@
 Using the jump conditions in~\cref{lem:jump-conds} again, we
-get that $\bmu = \bu^{-} - \bu^{+} = 0$.
+get that $2\bmu = \bu^{-} - \bu^{+} = 0$.
 Thus $(\cI - 2\cD_{k} - 2\cW)$ is invertible if $k^2$
@@
 where both the true and spurious eigenvalues can be
-determined semi-analytically. 
+determined analytically. 
 Analogous with the observation in~\cite{zhao2015robust},
@@
 surface traction, denoted by $\bt^{-}$, is $0$ on $\Gamma$.
+
 Using~\cref{lem:jump-conds} we observe that $\bt^{+}
-= -i\eta \bmu(\xx)$ and $\bu^{+} = -\bmu(\xx)$ on $\Gamma$, i.e.
-$\bt^{+}=i\eta \bu^{+}$ and $\bu^{+}$ satisfies the homogeneous
+= 2i\eta \bmu(\xx)$ and $\bu^{+} = -2\bmu(\xx)$ on $\Gamma$, i.e.
+$\bt^{+}+i\eta \bu^{+}=0$ and $\bu^{+}$ satisfies the homogeneous
 exterior impedance problem.
-\begin{remark}
-  Note that there is potential for confusion here
-  in that the exterior limit with respect to $\Omega$ 
-  for the boundary $\Gamma_{j}$ is the traditional interior 
-  limit with respect to the obstacle region $\Omega_{j}$.
-\end{remark}
 We first show that $\bmu=0$ on $\Gamma_{0}$. 
@@
 again, we get that
-$\bmu = \bu^{-} - \bu^{+} = 0$ on
-$\Gamma_{0}$. To show that $\bmu=0$ on
+$2\bmu = \bu^{-} - \bu^{+} = 0$ on
+$\Gamma_{0}$.
+
+\begin{remark}
+  Note that there is potential for confusion here
+  in that the exterior limit with respect to $\Omega$ 
+  for the boundary $\Gamma_{j}$ is the traditional interior 
+  limit with respect to the obstacle region $\Omega_{j}$.
+\end{remark}
+
+To show that $\bmu=0$ on
 $\Gamma_{j}$, we observe that $\bu$ is also a
@@
 Using the jump conditions in~\cref{lem:jump-conds},
-we get that $\bt^{+} = i\eta \bmu$ and $\bu^{+} = \bmu$.
+we get that $\bt^{+} = 2i\eta \bmu$ and $\bu^{+} = -2\bmu$.
+However, the normal is inward pointing inside $\Omega_{j}$
+on the boundary $\Gamma_{j}$. 
+If we revert back to the normal being defined as 
+an outward normal to $\Omega_{j}$, then
+the boundary conditions on $\Gamma_{j}$ 
+is $\bt - i \eta \bu = 0$. 
 From the uniqueness of solutions to the interior 
@@
 in $\Omega_{j}$, which in particular implies
-that $\bmu = \bu^{+} = 0$ for $\xx \in \Gamma_{j}$,
+that $2\bmu = \bu^{-}-\bu^{+} = 0$ for $\xx \in \Gamma_{j}$,
 $j=1,2,\ldots m$.

### 2019-04-09 doc/draft-01-stokes/appendix.tex

@@
 \section{Neumann eigenvalues and eigenfunctions on the unit disk}
-In this section, we analytically compute some of the Neumann eigenvalues
-on the unit disk for the Stokes operator.
+In this section, we analytically compute some of the radially symmetric 
+Neumann eigenvalues on the unit disk for the Stokes operator.
 
@@
 \begin{equation}
-\bu = \nabla (\alpha r^{n} \sint - \beta r^{n} \cost) + \nabla^{\perp}(\gamma \jnkr \sint + \delta \jnkr \cost) \, ,
+\bu = \nabla^{\perp} \jkr \, ,
 \end{equation}
-and the pressure is given by
+and the pressure is given by $p=0$, since
+$\bu$ satisfies $(\Delta + k^2)\bu = 0$.
+
+Then, the surface traction $\bt$ on the disk of radius $r$ 
+is given by
 \begin{equation}
-p = k^2 (\alpha r^{n} \sint - \beta r^{n} \cost) \, ,
+\bt = 
+\left( -\frac{k}{r}\jpkr  + \frac{k^2}{r^2} \jppkr\right)
+\begin{bmatrix}
+\sint \\
+-\cost
+\end{bmatrix} \, .
 \end{equation}
-where $\alpha,\beta,\gamma,\delta$ are constants.
 
-We first show that this pair satisfies the oscillatory Stokes equation
-in the unit disk.
-\begin{lemma}
-$(\bu,p)$ satisfy the oscillatory Stokes equation.
-\end{lemma}
-\begin{proof}
-$\bu$ is divergence free since
+Thus, $k$ which satisfies
 \begin{equation}
-\nabla \cdot \bu  = \Delta (\alpha r^{n} \sint - \beta r^{n} \cost) = 0 \, ,
+-k \jpk + k^2 \jppk = 0 \, ,
 \end{equation}
-as $r^{n} \cost$,  $r^{n} \sint$ are harmonic functions. 
-To show that $(\bu,p)$ satisfies the PDE, note that
-$r^{n} \cost$ and $r^{n} \sint$ are harmonic
-and $\jnkr \cost$, $\jnkr \sint$ satisfy Helmholtz's equation.
-\begin{equation}
-\begin{aligned}
-(\Delta + k^2) \bu &= (\Delta + k^2) \nabla (\alpha r^{n} \sint - \beta r^{n} \cost) \, + \\
-\quad & \hspace*{15ex} (\Delta + k^2) \nabla^{\perp} (\gamma \jnkr \sint + \delta \jnkr \cost) \, , \\
-&= k^2 \nabla (\alpha r^{n} \sint - \beta r^{n} \cost) \\ 
-&= \nabla p
-\end{aligned}
-\end{equation}
-\end{proof}
-
-Let $\hat{r}, \hat{\theta}$ denote the unit vectors in polar coordinates.
-Then  $\hat{r}$ is the unit normal on the boundary of the unit disk.
-The surface traction on the boundary of the unit disk is then given by 
-\begin{equation}
-\bt = -p \hat{r} + \nabla (\bu \cdot \hat{r}) + \partial_{r} \bu \, .
-\end{equation}
-If $(\bu,p)$ are as defined above, then 
-a long but tedious calculation shows that
-\begin{equation}
-\begin{aligned}
-t_{r} &= \cost \left( \beta k^2 r^{n} -2\beta n(n-1)r^{n-2} - 2\gamma n \ddr \frac{\jnkr}{r}  \right) \, + \\
-& \hspace*{15ex} \sint \left(-\alpha k^2 r^{n} + 2 \alpha n(n-1)r^{n-2} + 2 \delta n \ddr \frac{\jnkr}{r} \right) \, , \\
-t_{\theta} &= \cost \left( \alpha r^{n-2} (n^2 + n(n-1)) + \delta \left( \frac{n^2}{r^2} \jnkr + k^2 \jnppkr \right)  \right) + \\
-& \hspace*{15ex} \sint \left( \beta r^{n-2} (n^2 + n(n-1)) + \gamma \left( \frac{n^2}{r^2} \jnkr + k^2 \jnppkr \right) \right) \, .
-\end{aligned}
-\end{equation}
-Let $h_{k} = \ddr (\jnkr/r)|_{r=1}$.
-The values of $k$ for which there exists a non-zero solution $\alpha,\beta,\gamma,\delta$ 
-to the following system of equations
-\begin{equation}
-\begin{bmatrix}
-0 & 0 & k^2 - 2n(n-1) & -2nh_{k} \\
-0 & 0 & 2n^2 -n & n^2 \jnk + k^2 \jnppk \\
--k^2 + 2n(n-1) & 2nh_{k} & 0 & 0 \\
-2n^2 -n & n^2 \jnk + k^2 \jnppk & 0 & 0
-\end{bmatrix}
-\begin{bmatrix}
-\alpha \\ \delta \\ \beta \\ \gamma
-\end{bmatrix}
-=
-\begin{bmatrix}
-0 \\ 0 \\ 0 \\ 0
-\end{bmatrix}
-\, ,
-\end{equation}
-are the Neumann eigenvalues of the unit disk.
-
-A corollary of the above statement and the structure of the matrix is that
-the interior Neumann eigenvalues of the unit disk satisfy
-\begin{equation}
-2n^2(2n-1)h_{k} - (n^2 \jnk + k^2 \jnppk)(-k^2 + 2n(n-1)) = 0 \, .
-\end{equation}
+are Neumann eigenvalues on the unit disk.

### 2019-04-09 doc/draft-01-stokes/04numerical.tex
minor changes

@@
 vector of the appropriate BIE operator corresponding
-to the smallest singular value for each of $k=\real(k^{(p)}_\cheb)$
-and $k=\real(k^{(p)}_\cheb)$, which we denote by
+to the smallest singular value for each of $\real(k^{(p)}_\cheb)$
+and $\real(k^{(p)}_\cheb)$, which we denote by
 $\bv_p$ and $\bv_q$.
@@
 %
-For these near double-roots, we also check
+For these near double roots, we also check
 that there is no two dimensional null-space
@@
 %
-Thus, the use of a finer grid here results from
+Thus, the use of a finer grid in frequency results from
 the difficulty in resolving the Fredholm determinant
-when the kernel is not trace-class.
+for this problem, which has a larger dynamical range
+than that for the barbell.
 %
@@
 %
-These outliers correspond to eigenvalues 9 through 12,
-which have 
-The conditioning of the eigenvalue problem depends
-on the distance to the nearest eigenvalue. For
-the 8th through 13th eigenvalues, the average
-spacing between consecutive roots is 0.0447,
-which is much smaller than the average spacing of
-the roots for the first 20 eigenvalues, given by
-0.1132.
+These outliers are from the interval $[4.5,5]$.
+%
 In the plots, we observe a different type of

### 2019-04-09 doc/draft-01-stokes/04numerical.tex
fix spelling

@@
 to the smallest singular value for each of $\real(k^{(p)}_\cheb)$
-and $\real(k^{(p)}_\cheb)$, which we denote by
+and $\real(k^{(q)}_\cheb)$, which we denote by
 $\bv_p$ and $\bv_q$.

### 2019-04-10 doc/draft-01-stokes/04numerical.tex
update manuscript

@@
 
+In this section, we demonstrate the analytical
+claims above with numerical examples and
+highlight the performance of the BIE approach
+to Stokes eigenvalues.
+
 \subsection{Numerical methods}
+
+First, we describe the numerical tools needed
+to compute Stokes eigenvalues in a BIE
+framework.
 
@@
 
+We can obtain an a posteriori estimate of the
+error in a computed root as follows.
+%
+Let $f$ denote an analytic function,
+$P$ be the polynomial interpolant
+of that function over some interval,
+$\delta f = f-P$ be the difference,
+and $k_\cheb$ denote a computed root
+of $P$.
+%
+The algorithm used by \texttt{chebfun}
+to approximate the roots of $P$ is
+backward stable~\cite{noferini2017chebyshev}.
+Therefore the error in the roots will be
+small relative to the error of the fit and
+we set $P(k_\cheb) = 0$ below.
+%
+Suppose that
+$f(k_\cheb + \delta k) = 0$ for some
+small $\delta k$. Then
+
+\begin{align*}
+  0 &= f(k_\cheb + \delta k) \\
+  0 &= P(k_\cheb + \delta k) + \delta f(k_\cheb + \delta k) \\
+  \delta k &= -\frac{\delta f(k_\cheb + \delta k)}{P'(k_\cheb)} + O(\delta k^2) .
+\end{align*}
+In practice, we can obtain an approximate upper
+bound for $|\delta f(k_\cheb+\delta k)|$
+as $\epscheb \|P\|_\infty$ so that $\epscheb \|P\|_\infty/
+|P'(k_\cheb)|$ provides an approximate upper bound
+for the error in the root.
+
 \subsection{Eigenvalues of an annulus}
@@
     \includegraphics[width=\textwidth]{fig/ex_barbell_001_sings_plot}
-    \caption{Smallest singular value corresponding to the
-    first 119 computed eigenfunctions of the barbell-shaped
-    domain.}
+    \caption{Smallest singular value of the BIE operator.}
     \label{subfig:barbell_sings}
@@
     \includegraphics[width=\textwidth]{fig/ex_barbell_001_coeffs_plot}
-    \caption{Normalized Chebyshev coefficients of $f^N(k)$ on
-      3 different intervals in $k$.}
+    \caption{Normalized Chebyshev coefficients of the
+      determinant on 3 intervals in $k$.}
     \label{subfig:barbell_coeffs}
   \end{subfigure}
-  \caption{Diagnostics for the barbell eigenvalues.}
+  \caption{Diagnostics for the first 119 barbell eigenvalues.}
   \label{fig:barbell_diagnostics}
@@
 %
-For simplicity, we round the corners of the domain
+For the sake of simplicity, we round the corners of the domain
 to obtain a smooth object.
@@
 Applying the approach described in~\cite{epstein2016smoothed},
-the corners of the domain are rounded using the Gaussian kernel
+the corners of the domain are rounded by convolving with
+the Gaussian kernel
 \begin{equation}
@@
 The panels are divided adaptively so that the smallest
-panels in the rounded corner are smaller than $10^{-2}$.
+panels in the rounded corners are smaller than $10^{-2}$,
+which keeps the panels relatively flat.
 %
@@
 We plot the absolute value of the Chebyshev coefficients
+(normalized by the absolute value of the first coefficient)
 of $f^N(k)$ on the intervals $[0.5,1.0]$, $[3.0,3.5]$,
@@
   \includegraphics[width=\textwidth]{fig/many_inclusions_gallery}
-  \caption{Vorticity plots of...}
+  \caption{Vorticity plots of the eigenfunctions corresponding
+  to the first 76 eigenvalues of a domain with several inclusions.}
   \label{fig:many_inclusions_gallery}
@@
     \includegraphics[width=\textwidth]{fig/ex_many_holes_004_sings_plot}
-    \caption{Smallest singular value corresponding to the
-    first.}
+    \caption{Smallest singular value of the BIE operator
+      corresponding to the first 76 eigenvalues of a
+      domain with several inclusions.}
     \label{subfig:many_inclusions_sings}
@@
   \end{subfigure}
-  \caption{Diagnostics for the ... eigenvalues.}
+  \caption{Diagnostics for the eigenvalues of a domain
+    with several inclusions.}
   \label{fig:many_inclusions_diagnostics}
@@
 %
-For this smooth shape, the panels are chosen
-adaptively so that the coordinates, the first
-and second derivatives of the coordinates, and
-the arc-length function are resolved to a precision
-of $10^{-3}$ on each panel.
+For this smooth shape, ensuring that no panel is
+larger than one wavelength for the largest $k$
+(here $\lambda=2\pi/9$) is sufficient to resolve
+the object to high precision.
 %
-This results in $N_p = 224$ after enforcing the
+After enforcing the
 level-restriction property described in
-\cref{rmk:levelrestrict}
-and enforcing that no panel is larger than
-one wavelength for the largest $k$
-(here $\lambda=2\pi/9$).
+\cref{rmk:levelrestrict}, we end up with
+$N_p = 224$.
 
@@
 %
-The singular values suggest that the quality of the
-eigenvalues is good, with a few outliers.
-%
-These outliers are from the interval $[4.5,5]$.
-%
-In the plots, we observe a different type of
-localization property, with many of the eigenfunctions
+In the vorticity plots, we observe a different type of
+localization property than that seen in the barbell,
+with many of the eigenfunctions
 approximately supported in a small, connected subset
@@
 %
+
+\begin{figure}
+  \centering
+  \begin{subfigure}[t]{0.4\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{fig/ex_many_holes_004_sings_plot_west}
+    \caption{Smallest singular value of the BIE operator
+      for the computed roots (original intervals)
+      along with an estimate of the error in the root (dotted).}
+    \label{subfig:many_inclusions_sings_west}
+  \end{subfigure}
+  ~
+  \begin{subfigure}[t]{0.4\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{fig/ex_many_holes_004_sings_plot_ref}
+    \caption{Smallest singular value of the BIE operator
+      for the computed roots on the original intervals (\textbullet)
+      and the values obtained on the refined interval ($\times$).}
+    \label{subfig:many_inclusions_sings_ref}
+  \end{subfigure}
+  \caption{Further diagnostics for the eigenvalues of a domain
+    with several inclusions.}
+  \label{fig:many_inclusions_diagnostics_2}
+\end{figure}
+
+The singular values suggest that the quality of the
+eigenvalues is good, with a few outliers.
+%
+To explain these outliers, we consider two quantities
+which affect the singular value at a computed root.
+%
+As described above, we can approximate the
+error in the computed root at $k_\cheb$ by
+$\epscheb \|P\|_\infty/|P'(k_\cheb)|$,
+where $P$ is the interpolating polynomial.
+%
+The singular value estimate itself is affected by
+the error incurred in applying the inverse of the
+compressed BIE matrix, which can be hard to quantify
+\cite{ho2012fast}.
+%
+We approximate this error by $O(\sqrt{N})\epsflam$
+and assume this is the order of the error in
+the singular value estimate.
+We plot the maximum of these two estimates
+along with the computed singular values in
+\cref{subfig:many_inclusions_sings_west}.
+There is a reasonably good correlation between
+the maximum of the error estimates and the
+observed smallest singular value for the BIE,
+especially for larger errors.
+
+The worst outliers are from the left half
+of the interval $[4.5,5]$.
+%
+Because the determinant is much larger on the
+right half than the left half of $[4.5,5]$,
+we can improve the estimate for the error
+in the roots by subdividing the interval. 
+We plot the smallest singular value of the
+BIE for the roots obtained by fitting a polynomial
+on $[4.5,4.75]$ in \cref{subfig:many_inclusions_sings_ref};
+the roots on the refined interval
+are of significantly higher quality.
+
+\begin{remark}
+  The above experience suggests that
+  the ratio $\|P\|_\infty/|P'(k_\cheb)|$
+  is a useful diagnostic for performing
+  automated eigenvalue estimation.
+  Note that at a multiple root, this ratio
+  will be more difficult to bound.
+\end{remark}
+%
+
+%

### 2019-04-10 doc/draft-01-stokes/02prelim.tex
minor updates

@@
 \label{sec:prelim}
-In this paper, vector-valued
-quantities are denoted by bold, lower-case letters
-(e.g. $\bh$), while tensor-valued quantities are bold
-and upper-case (e.g. $\mathbf{T}$). 
+In this paper, vector- and tensor-valued quantities
+are denoted by bold letters (e.g. $\bh$ and $\mathbf{T}$). 
 Subscript indices of non-bold characters (e.g. $h_j$ or $T_{ij\ell}$)
-are used to denote the entries within a vector ($\bh$) or tensor ($\bT$).
-We use the standard Einstein summation convention; in other words, 
+are used to denote the entries within a vector or tensor.
+We use the standard Einstein summation convention; i.e., 
 there is an implied sum taken over the repeated indices of 

### 2019-04-10 doc/draft-01-stokes/03analysis.tex
Adding result plots, updating appendix to include neumann eigenvalues, fixing sign of impendence problem in section3
update spelling

@@
 \begin{proof}
-  Plugging in $\bt = i\eta \bu$ in~\cref{eq:greenlike}
+  Plugging $\bt = i\eta \bu$ in~\cref{eq:greenlike}
   and taking the imaginary part, we get
@@
 \begin{proof}
-Since $\bu$ satisfies the radiation condition at $\infty$ and $\bt = i\eta \bu$
+Since $\bu$ satisfies the radiation condition at $\infty$ and $\bt = -i\eta \bu$
 on $\Gamma$, it follows from~\cref{eq:repinfest} that

### 2019-04-10 doc/draft-01-stokes/04numerical.tex
add figures
minor updates
update figure

@@
 and $k_\cheb$ denote a computed root
-of $P$.
+of $P$ which is simple (i.e. assume
+that $P'(k_\cheb) \ne 0$).
 %
@@
   \centering
+  \begin{subfigure}[t]{0.4\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{fig/ex_barbell_001_bdry}
+    \caption{A barbell-shaped domain.}
+    \label{subfig:barbell_bdry}
+  \end{subfigure}
+  ~
+  \begin{subfigure}[t]{0.4\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{fig/ex_many_holes_004_bdry}
+    \caption{A domain with several inclusions.}
+    \label{subfig:many_inclusions_bdry}
+  \end{subfigure}
+\end{figure}
+
+\begin{figure}
+  \centering
   \includegraphics[width=\textwidth]{fig/barbell_gallery}
@@
 
-We consider the barbell-shaped domain in \cref{fig:barbell}.
+We consider the barbell-shaped domain in \cref{subfig:barbell_bdry}.
 This domain is the union of a square of side-length 6,
@@
 We now consider the multiply-connected domain in
-\cref{fig:many_holes}.
+\cref{subfig:many_inclusions_bdry}.
 % 

### 2019-04-10 doc/draft-01-stokes/04numerical.tex
adding annulus results

@@
 \subsection{Eigenvalues of an annulus}
+We test our numerical machinery and validate our analytical 
+and numerical claims
+by comparing the results to the true eigenvalues on the annulus
+which are known analytically (see~\cref{sec:annul_dir_exact}).
+In all of the examples below, we work on the annulus $r_{1}<r<r_{2}$
+with $r_{1} = 1$ and $r_{2} = 1.7$.
+If the inner boundary is discretized using $N_{1}$ panels, 
+then the outer boundary is discretized using $N_{2} = 
+\lceil r_{2}/r_{1} N_{1} \rceil +1$ panels to ensure that the
+panels are approximately the same length on both the boundaries. 
+The total number of discretization points 
+is then given by $N = 16(N_{1} + N_{2})$.
+Let $D^{N}_{k}$ denote the linear system corresponding
+to the Nystr\"{o}m discretization of
+$-2\cD_{k} -2\cW$ using generalized Gaussian quadrature, 
+and let $C^{N}_{k}$ denote the linear system corresponding
+to the Nystr\"{o}m discretization of 
+$-2\cD_{k} - 2i\cS_{k} -2\cW$.
+Let $f_{D}^{N}(k) = \text{det}(I+D^{N}_{k})$, and 
+$f_{C}^{N}(k) = \text{det}(I+C^{N}_{k})$.
+
+\subsubsection{Convergence study}
+\label{subsec:convannulus}
+We demonstrate that 
+for sufficiently large $N$, if $k_{0}$ is a Dirichlet 
+eigenvalue of the annulus, 
+then $f_{D}^{N}(k_{D}) = 0$ and $f_{C}^{N}(k_{C}) = 0$
+where $|k_{D} - k_{0}| \lsim N^{-20}$, 
+and $|k_{C} - k_{0}| \lsim N^{-20}$.
+Note that N^{-20} is the observed order of
+convergence for Generalized Gaussiuan quadratures for weakly 
+singular integrals.
+In~\cref{fig:conv}, we show this result for $k_{0} = 13.48025717955055$
+and plot the errors $|k_{D}-k_{0}|$ and $|k_{C}-k_{0}|$ as a function
+of $N$.
 
@@
 \label{subsec:spurannulus}
+As noted in~\cref{subsec:dlanalysis},
+if $k_{0}$ is a Neumann eigenvalue corresponding to the interior
+inclusion, which in our case is the disk $r\leq r_{1}$, then
+$f_{D}(N)(k_{0}) is O(\varepsilon)$ even though $k_{0}$ 
+is not a Dirichlet eigenvalue of the annulus, i.e.
+the integral equation $-\cI - 2\cD_{k} -2\cW$ has a spurious eigenvalue.
+In~\cref{fig:spur}, we demonstrate this result and also show that 
+$f_{C}^{N}(k_{0}) \neq 0$, i.e., the combined field representation is
+robust and invertible at all values of $k$ which are not the Dirichlet
+eigenvalues of the annulus.
 
-\subsubsection{Convergence study}
-\label{subsec:convannulus}
+\subsubsection{Speed}
+\label{subsec:speed}
+In this section, we demonstrate the O(N\log{N}) scaling of evaluating
+$f^{N}_{C}(k)$ as long as $N$ is large enough to resolve the interactions
+at the Helmholtz parameter $k$. 
+When $N$ is smaller than that, we observe a worse scaling since the
+assumption that far-interactions are low-rank is no longer valid at
+the tolerance of FLAM.
+We plot the timing results corresponding to three different values of 
+$k$ in~\cref{fig:speed}.
 

### 2019-04-11 doc/draft-01-stokes/04numerical.tex
Updating numerical results

@@
 then $f_{D}^{N}(k_{D}) = 0$ and $f_{C}^{N}(k_{C}) = 0$
-where $|k_{D} - k_{0}| \lsim N^{-20}$, 
-and $|k_{C} - k_{0}| \lsim N^{-20}$.
-Note that N^{-20} is the observed order of
+where $|k_{D} - k_{0}| \lesssim N^{-20}$, 
+and $|k_{C} - k_{0}| \lesssim N^{-20}$.
+Note that $N^{-20}$ is the expected order of
 convergence for Generalized Gaussiuan quadratures for weakly 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.98\textwidth]{media/conv-studies.pdf}
+  \caption{Convergence studies for the Dirichlet eigenvalues
+  computed using the integral equations 
+  $\cI - 2\cD_{k} - 2\cW$ (left) and
+  $\cI - 2\cD_{k} - 2i \cS_{k} - 2\cW$ (right).}
+  \label{fig:conv}
+\end{figure}
+
 \subsubsection{Spurious eigenvalues}
@@
 inclusion, which in our case is the disk $r\leq r_{1}$, then
-$f_{D}(N)(k_{0}) is O(\varepsilon)$ even though $k_{0}$ 
+$f_{D}(N)(k_{D}) = 0$ with $|k_{D}-k_{0}| = O(\varepsilon)$, even though $k_{0}$ 
 is not a Dirichlet eigenvalue of the annulus, i.e.
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.98\linewidth]{media/det_spur.pdf}
+\caption{The values of the discretized determinants $f_{C}^{N}(k)$ (left)
+and $f_{D}^{N}(k)$ on the interval $k=[13,14]$ with $N=368$. The vertical
+dotted line denotes the spurious eigenvalue $k_{0} = 14.79595178235126$ 
+and $f_{D}^{N}(k_{D}) = 0$ with $|k_{D}-k_{0}|=6.8\times 10^{-12}$.
+On the other hand $|f_{C}^{N}(k_{0})|=0.42$, and thus $\cI-2\cD_{k}-2i\cS_{k} 
+-2\cW$ has no 
+spurious eigenvalue in the neighborhood of $k=k_{0}$.}
+\label{fig:spur}
+\end{figure}
+
 \subsubsection{Speed}
 \label{subsec:speed}
-In this section, we demonstrate the O(N\log{N}) scaling of evaluating
+In this section, we demonstrate the $O(N\log{N})$ scaling of evaluating
 $f^{N}_{C}(k)$ as long as $N$ is large enough to resolve the interactions
@@
 $k$ in~\cref{fig:speed}.
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{media/speed_res.pdf}
+\caption{Time taken $(t)$ in seconds to evaluate the determinant $f_{C}^{N}(k)$ as
+a function of $N$ for three different values of $k$.}
+\label{fig:speed}
+\end{figure}
 

### 2019-04-11 doc/draft-01-stokes/appendix.tex
Updating numerical results

@@
-\section{Dirichlet eigenvalues and eigenfunctions on the unit disk}
+\section{Dirichlet eigenvalues and eigenfunctions on the annulus \label{sec:annul_dir_exact}}
 In this section, we compute some of the Dirichlet eigenvalues
@@
 \bt = 
-\left( -\frac{k}{r}\jpkr  + \frac{k^2}{r^2} \jppkr\right)
+\left( -\frac{k}{r^2}\jpkr  + \frac{k^2}{r} \jppkr\right)
 \begin{bmatrix}
@@
 are Neumann eigenvalues on the unit disk.
+The first $4$ roots of the above equation are 
+\begin{equation}
+\begin{aligned}
+k &= 5.135622301840683 \\
+  &= 8.417244140399865 \\
+  &= 11.61984117214906 \\
+  &= 14.79595178235126
+\end{aligned}
+\end{equation}

### 2019-04-11 doc/draft-01-stokes/02prelim.tex
cleaning up paper and adding annulus discretization plot

@@
 
-For a given velocity field $\bu$ and pressure $p$, let $\bsigma(\bu,p)$
-denote the Cauchy stress tensor, i.e.
+For a velocity field $\bu$ and pressure $p$, let $\bsigma(\bu,p)$
+denote the Cauchy stress tensor is given by
 \begin{equation}
@@
 We consider here
-free-space Green's functions, i.e. fundamental solutions which satisfy
+free-space Green's functions, i.e. fundamental solutions which satisfy appropriate
 radiation conditions as $|\xx-\yy| \to \infty$.
@@
 
-Recall that, in the case that $k=i\alpha$ for some real-valued $\alpha$,
+Recall that, in the case $k=i\alpha$ for some real-valued $\alpha$,
 the oscillatory Stokes equations \cref{eq:ostokes}
@@
   \begin{equation*}
-    \bu(\xx) = \int_\Omega -(\Delta_x + k^2) \GG(\xx,\yy) \bu(\yy)
+    \bu(\xx) = \int_\Omega -(\Delta + k^2) \GG(\xx,\yy) \bu(\yy)
     + \nabla \otimes \nabla \Glap(\xx,\yy) \bu(\yy) \, dV(\yy) \; .
@@
 the boundary value problems. The nature of this deficiency
-is treated below but for now we introduce a standard
+is treated in~\cref{sec:analysis} but for now we introduce a standard
 operator used to correct this. For any integrable density

### 2019-04-11 doc/draft-01-stokes/03analysis.tex
cleaning up paper and adding annulus discretization plot

@@
 for the scalar Helmholtz equation.
-While uniqueness results for interior Dirchilet, Neumann, and impedance
+While uniqueness results for interior Dirichlet, Neumann, and impedance
 problems follow from energy considerations and compactness
@@
 denoted by $\Gamma$.
-The Dirichlet problem specifies the
-velocity of the fluid on the boundary, i.e.
+We summarize the interior Dirichlet, Neumann and impedance
+boundary value problems in~\cref{def:int_dir,def:int_neu,def:int_imp} below.
 
 \begin{definition}[Interior Dirichlet problem]
+  \label{def:int_dir}
   Let $\ff \in C(\Omega)$ be given. Find $(\bu,p) \in A(\Omega)$
@@
 
-Let $\bsigma$ denote the stress tensor associated with
-field $(\bu,p)$. 
-Specifying the surface traction, $\bt = \bsigma \cdot \bnu$,
-on the boundary gives the Neumann boundary value
-problem, i.e.
-
 \begin{definition}[Interior Neumann problem]
+  \label{def:int_neu}
   Let $\bg \in C(\Omega)$ be given. Find $(\bu,p) \in A(\Omega)$
@@
 \begin{definition}[Interior impedance problem]
+\label{def:int_imp}
   Let $\bh \in C(\Omega)$ be given and suppose 
@@
 \end{equation}
-Finally, because $H_0^{(1)}(kr)$ is radially symmetric,
+Finally, since $H_0^{(1)}(kr)$ is radially symmetric,
 we have
@@
 summarize in
-\cref{def:dir_exterior,def:neu_exterior} below.
+\cref{def:dir_exterior,def:neu_exterior,def:imp_exterior} below.
 
@@
 
-\begin{definition}[Exterior Impedence problem]
-  \label{def:neu_exterior}  
+\begin{definition}[Exterior impedance problem]
+  \label{def:imp_exterior}  
   Let $\bh \in C(\Gamma)$ be given and suppose that
@@
 In the following lemma, we prove uniqueness for the
-interior impedence problem.
+interior impedance problem.
 
@@
 
-The following lemmas are useful in establishing the uniqueness
-of oscillatory Stokes boundary value problems.
+We now turn our attention to the proofs of the exterior boundary value problems
+for the oscillatory Stokes equation. The following lemmas are useful for
+proving these results.
 
@@
 that the projection of $a_{j,n}$ on $r^{|n|}$, and $H_{n}^{1,2}(k r)$
-must be zero. Thus, 
+must be zero. Thus, for sufficiently large $r$,
 \begin{equation}
@@
 \end{equation}
-for sufficiently large $r$.
+i.e. $u_{j}$ is harmonic 
+in $B_{r}(0)^{c}$.
 Finally, by \cref{cor:analytic}, $\bu$ is
@@
   not be a radiating solution. All that is assumed of $\bu$
-  is that it satisfies the PDE in $E$.
+  is that it satisfies the oscillatory Stokes equations in $E$.
 \end{remark}
@@
 well-known~\cite{biros2002embedded} and we summarize it
-in
-
-\begin{lem}[\cite{biros2002embedded}]
+in the lemma below.
+
+\begin{lem}
   \label{lem:nunull} In the notation above,
@@
 and applying~\cref{lem:jump-conds}, we get that the interior
-limit of the velocity $\bu^{-}$, is given by $(\cI - 2\cD_{k}) \bmu = 0$
+limit of the velocity $\bu^{-}=(\cI - 2\cD_{k}) \bmu = 0$
 on $\Gamma$. Since $k^2$ is not a Dirichlet eigenvalue for the Stokes
@@
 $\int_{\Gamma} \bmu \cdot \bnu = 0$.
-From the uniqueness of the Neumann problem in the
-exterior $E$, we conclude that $\bu \equiv 0$ in $E$ as well,
+From the uniqueness of solutions to the exterior Neumann problem, 
+we conclude that $\bu \equiv 0$ in $E$ as well,
 which in particular implies that
@@
   $ \bar\Omega_1 \subset \Omega_0$.
-  Then, the operator $\cI - 2\cD_{k} - 2\cW$ has a non-trivial
-  null space if $k^2$ is a Neumann eigenvalue of $\Omega_{1}$.
+  Then, the operator $\cI - 2\cD_{k} - 2\cW$ is not invertible
+  if $k^2$ is a Neumann eigenvalue of $\Omega_{1}$.
 \end{thrm}
@@
 \begin{proof}
-  Suppose that $k^2$ is a Neumann eigenvalue of $\Omega_{1}$.
-  Let $\tilde{\bu}$ be the eigenfunction corresponding to $k^2$. 
+  Suppose that $k^2$ is a Neumann eigenvalue of $\Omega_{1}$, and
+  let $\tilde{\bu}$ denote the corresponding eigenfunction. 
   Note that $\tilde{\bu}$ is not identically $0$ on the boundary
@@
 which are almost multiply connected.
-We demonstrate this issue numerically
-in~\cref{subsec:crescent}.
 
@@
 The non-robustness in using the double layer
-potential representation observed above can be
+potential representation can be
 remedied by using a combined-field, or mixed layer potential,
@@
 From the uniqueness of solutions to the interior 
-impedence problem, we conlcude that $\bu \equiv 0$
+impedance problem, we conlcude that $\bu \equiv 0$
 in $\Omega_{j}$, which in particular implies
@@
 The operator $-2\cD_{k} - 2\cW$ is trace class:
-\begin{lemma}
+\begin{lem}
   Suppose that $\Gamma$ is a $C^2$ curve.
-  Then, $-2\cD_{k} - 2\cW \in \cJ_1(Y)$
+  Then $-2\cD_{k} - 2\cW \in \cJ_1(Y)$
   for all $k \in \mathbb{C} \setminus \{0\}$ 
-\end{lemma}
+\end{lem}
 \begin{proof}
@@
 estimate the Dirichlet eigenvalues.
-Suppose that $M_{k}^{N}$ is a Nystr\"{o}m discretization 
+Suppose that $D_{k}^{N}$ is a Nystr\"{o}m discretization 
 of the operator $-2\cD_{k} - 2\cW$ when the boundary 
 $\Gamma$ is discretized with $N$ points. 
-Let $f^{N}(k) = \text{det}(I + M_{k}^{N})$
+Let $f^{N}(k) = \text{det}(I + D_{k}^{N})$
 where here $\text{det}$ is the standard matrix determinant.
@@
 Suppose further that all the eigenvalues have multiplicity $1$.
-Let $f^{N}(k) = \text{det}(I+M^{N}_{k})$, where $M^{N}_{k}$ 
+Let $f^{N}(k) = \text{det}(I+D^{N}_{k})$, where $D^{N}_{k}$ 
 is the Nystr\"{o}m discretization of $-2\cD_{k} - 2\cW$ with Kress
@@
 no longer holds).
-%
-%Coupling with fast direct solvers for computing determinants also results in $O(N^2 \log{N})$.
-%where $N$ is the number of discretization points on the boundary.
-%Typical fast direct solvers
-%query $O(N)$ matrix entries to obtain a compressed representation,
-%this combined with the fact that evaluating each matrix entry
-%costs $O(N)$ for Kress quadratures results in the sub-optimal
-%complexity. 
 Over the last two decades, many high-order quadrature
 methods which are compatible with
-the fast multipole method and fast-direct solvers
+the fast multipole method and fast-direct methods
 have been developed.
@@
 since $\cS_{k}$ is not a trace class operator.
-For brevity, let $\cM_{k} = -2\cD_{k} - 2i\eta \cS_{k} - 2\cW$.
-The operator $\cM_{k}$ is 
+For brevity, let $\cC_{k} = -2\cD_{k} - 2i\eta \cS_{k} - 2\cW$.
+The operator $\cC_{k}$ is 
 in $\cJ_{2}(Y)$ where
@@
 summable, as opposed to being summable).
-Thus the Fredholm determinant of $\cI + \cM_{k}$
+Thus the Fredholm determinant of $\cI + \cC_{k}$
 is not necessarily finite. 
@@
 of convergence, since the singular values of the operator
-$\cM_{k}$ decay like $\frac{1}{n}$, and the
+$\cC_{k}$ decay like $\frac{1}{n}$, and the
 Fredholm determinant diverges logarithmically. 

### 2019-04-11 doc/draft-01-stokes/stokes-eig.tex
update numerical section
Updating stokes-eig.tex
minor updates
cleaning up paper and adding annulus discretization plot

@@
 \def\br{{\boldsymbol r}}
+\def\bv{{\boldsymbol v}}
 \def\bc{{\boldsymbol c}}
@@
 \def\bK{{\mathbf K}}
-\def\sint{{\sin{(n \theta)}}}
-\def\cost{{\cos{(n \theta)}}}
-\def\jnkr{J_{n}(kr)}
-\def\jnk{J_{n}(k)}
-\def\jnpkr{J_{n}'(kr)}
-\def\jnppkr{J_{n}''(kr)}
-\def\jnppk{J_{n}''(k)}
+\def\sint{{\sin{(\theta)}}}
+\def\cost{{\cos{(\theta)}}}
+
+\def\jkr{J_{0}(kr)}
+\def\jpkr{J_{0}'(kr)}
+\def\jpk{J_{0}'(k)}
+\def\jppkr{J_{0}''(kr)}
+\def\jppk{J_{0}''(k)}
 \def\ddr{\frac{d}{dr}}
@@
 \def\epsflam{{\epsilon_{\texttt{FLAM}}}}
-\def\epscheb{{\epsilon_{\texttt{CHEB}}}}
+\def\epscheb{{\epsilon_{\texttt{cheb}}}}
 \def\epsclose{{\epsilon_{\textrm{close}}}}
+\def\cheb{{\texttt{cheb}}}
 
@@
   %
-  As the Stokes operator is inherently a fourth-order
+  As the Stokes operator is a fourth-order
   operator,

### 2019-04-11 matlab/example/plot_annulus.m

@@ -1,0 +1,52 @@
+
+%EXAMPLE_ANNULUS_001
+%
+% compute a chebfun representation of the fredholm determinant 
+% of the system I-2D-2iS for a domain on the intervals [j,j+1] j=1,...,8
+% save chebfun, domain, and some settings to a file
+
+filebase = 'example_annulus_001'; 
+timeref = datestr(now,'_yyyymmdd_HHMMSS');
+fileout = [filebase, '_reptest.mat'];
+
+% annulus params
+
+r1 = 1.0;
+r2 = 1.7;
+
+
+chunkers = {};
+nchi = 6;
+ncho = 10;
+
+chunkert = circle_chunks(ncho,r2);
+chunkers{1} = chunkert;
+
+nw = 1;
+nh = 1;
+
+ind = 2;
+chunkert = circle_chunks(nchi,r1);
+chunkert = chunkreverse(chunkert);
+chunkert = chunksort(chunkert);
+chunkers{ind} = chunkert;
+        
+[chunker,nchs] = chunkermerge(chunkers);
+
+%
+
+nn = nchi+ncho;
+xx1 = chunker.chunks(1,:,1:2:nn); xx1 = xx1(:);
+yy1 = chunker.chunks(2,:,1:2:nn); yy1 = yy1(:);
+
+
+xx2 = chunker.chunks(1,:,2:2:nn); xx2 = xx2(:);
+yy2 = chunker.chunks(2,:,2:2:nn); yy2 = yy2(:);
+
+rnorms = chunknormals(chunker);
+
+intparams.intorder = chunker.k;
+
+plot(xx1,yy1,'r.','MarkerSize',15); hold on;
+plot(xx2,yy2,'b.','MarkerSize',15);
+saveas(gcf,'annulus_discretization.pdf')

### 2019-04-11 doc/draft-01-stokes/04numerical.tex
Adding annulus discretization to pdf
small fix to numerical

@@
 inclusion, which in our case is the disk $r\leq r_{1}$, then
-$f_{D}(N)(k_{D}) = 0$ with $|k_{D}-k_{0}| = O(\varepsilon)$, even though $k_{0}$ 
+$f_{D}^{N}(k_{D}) = 0$ with $|k_{D}-k_{0}| = O(\varepsilon)$, even though $k_{0}$ 
 is not a Dirichlet eigenvalue of the annulus, i.e.

### 2019-04-11 doc/draft-01-stokes/03analysis.tex
clean up code

--- 2019-04-10 doc/draft-01-stokes/03analysis.tex
@@
 for the scalar Helmholtz equation.
-While uniqueness results for interior Dirchilet, Neumann, and impedance
-problems follow from energy considerations and compactness
-arguments, the proofs for uniqueness of exterior
-results are more involved. 
-In particular,
-this entails making the exterior problems
-well-posed by imposing an appropriate radiaiton condition.
-We present well-posed boundary value formulations 
-for both interior and exterior Dirichlet, Neumann and impedance
-boundary value problems, and also
-present uniqueness results for all of them.
+%
+While uniqueness results for interior Dirchilet,
+Neumann, and impedance problems follow from energy
+considerations and compactness arguments, the proofs
+for the uniqueness of exterior problems are more
+involved.
+%
+In particular, the exterior problems are only 
+well-posed after imposing an appropriate radiation
+condition.
+%
+We formulate well-posed boundary value problems 
+for both interior and exterior domains with
+Dirichlet, Neumann and impedance boundary
+conditions and present uniqueness results for
+each.
 
@@
 
-Let $\Omega$ be a bounded domain with $C^2$ boundary
+Let $\Omega$ be a bounded domain with a $C^2$ boundary
 denoted by $\Gamma$.
@@
 
-Let $\bsigma$ denote the stress tensor associated with
-field $(\bu,p)$. 
+Let $\bsigma$ denote the stress tensor associated with the
+pair $(\bu,p)$. 
 Specifying the surface traction, $\bt = \bsigma \cdot \bnu$,
@@
 \begin{definition}[Exterior Impedence problem]
-  \label{def:neu_exterior}  
+  \label{def:imp_exterior}  
   Let $\bh \in C(\Gamma)$ be given and suppose that
@@
   \begin{equation}
-  \begin{aligned} \label{eq:neu_exterior}
+  \begin{aligned} \label{eq:imp_exterior}
     \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
@@
 We first note that $\bS_{k}[\bnu](\bx) = 0$ for all $\bx \in \Omega$.
-This follows from the application of the divergence theorem and the fact that
+This follows from an application of the divergence
+theorem and the fact that
 oscillatory Stokeslet is divergence free in $\Omega$. 
-If $\bt^{-}$ is a surface traction associated with a Stokes eigenvalue, then
+If $\bt^{-}$ is a surface traction associated with
+a Stokes eigenvalue, then
 using Green's theorem, it follows that
@@
 and the Dirichlet eigenvalues of the Stokes operator on multiply
-connected domains also causes non-robustness and introduces near 
-resonances for simply connected domains
-which are almost multiply connected.
-We demonstrate this issue numerically
-in~\cref{subsec:crescent}.
+connected domains also causes non-robustness and introduces
+near-resonances for simply-connected domains which are almost
+multiply-connected.
+%We demonstrate this issue numerically
+%in~\cref{subsec:crescent}.
 
@@
     \bu(\xx) &\quad \xx \in \Omega \, , \\
-    0 &\quad \xx \in \Omega^{C} \; .
+    0 &\quad \xx \in \R^2 \setminus \bar{\Omega} \; .
     \end{cases}
@@
 analytic boundaries, when the integral operators are
-discretized using Kress quadrature, see~\cite{kress1991boundary},
+discretized using Kress quadrature --- a spectrally accurate
+quadrature rule for such kernels, see~\cite{kress1991boundary} ---
 the determinant of the Nystr\"{o}m discretized operators
@@
 
-The proof presented in~\cite{zhao2015robust} carries
-forward for computing the Dirichlet eigenvalues of
-Stokes equation as well.
+The proof presented in~\cite{zhao2015robust} applies
+to the BIE approach for computing the Dirichlet eigenvalues
+of the Stokes operator as well.
 The result is summarized below.
@@
 %
-Extensive numerical evidence suggests that the zeros of the 
+Our numerical experiments, see \cref{subsec:convannulus},
+suggest that the zeros of the 
 determinants of linear systems discretized using 

### 2019-04-11 doc/draft-01-stokes/04numerical.tex
clean up code

--- 2019-04-11 doc/draft-01-stokes/04numerical.tex
@@
 highlight the performance of the BIE approach
-to Stokes eigenvalues.
+with demonstrations on domains of analytical
+and practical interest.
 

### 2019-04-11 doc/draft-01-stokes/stokes-eig.tex
clean up code

@@
   operator have been the subject of intense analytical
-  investigation and they have applications in the study
+  investigation and have applications in the study
   and simulation of the Navier--Stokes equations.
   %
-  As the Stokes operator is a fourth-order
+  As the Stokes operator is inherently a fourth-order
   operator,

### 2019-04-11 matlab/example/example_antunes_001.m

@@ -1,75 +1,0 @@
-
-%EXAMPLE_ANTUNES_001
-%
-% compute a chebfun representation of the fredholm determinant 
-% of the system I-2D for the Antunes domain on the interval [0.1,10]
-% save chebfun, domain, and some settings to a file
-
-fileout = 'example_antunes_001.mat';
-
-chebabs = cell(12,1);
-for j = 1:length(chebabs)
-    chebabs{j} = [1.0*j 1.0*(j+1)];
-end
-
-max_rzk = chebabs{end}(end); lam = 2*pi/max_rzk;
-
-seed = 8675309;
-rng(seed);
-addpath('../src')
-addpath('../example')
-addpath('../../mwrap')
-addpath('~/Dropbox/MATLAB/chebfun')
-addpath(genpath('~/Dropbox/MATLAB/FLAM'))
-cparams.eps = 1.0e-6;
-cparams.nchmax = 100000;
-cparams.maxchunklen = lam;
-cparams.nover = 2;
-narms = 5;
-amp = 0.5;
-chunker = chunkfunc(@(t) antunes(t),cparams);
-
-%%
-
-xs = chunker.chunks(1,:,:); xs = xs(:);
-ys = chunker.chunks(2,:,:); ys = ys(:);
-
-scatter(xs,ys)
-
-%%
-
-rnorms = chunknormals(chunker);
-
-intparams.intorder = chunker.k;
-
-% build matrix
-
-cd = -2.0 + 1i*0.0;
-cs = 0.0 + 1i*0.0;
-nchs = ones(1,1);
-nchs(1) = chunker.nch;
-ncomp = length(nchs);
-
-%
-
-opts = []; opts.FLAM = 1; opts.verb = true;
-detfun = @(zk) ostokes_determinant(zk,chunker,nchs,cs, ...
-    cd,opts);   
-
-p = chebfunpref; p.chebfuneps = 1.0e-13;
-p.splitting=0; p.maxLength = 257;
-
-t1s = cell(size(chebabs));
-detchebs = cell(size(chebabs));
-    
-parfor j = 1:length(chebabs)
-    fprintf('running on interval [ %5.2e %5.2e ]\n',chebabs{j}(1), ...
-        chebabs{j}(2))
-    start = tic; detchebs{j} = ...
-        chebfun(detfun,chebabs{j},p); 
-    t1s{j} = toc(start);
-    fprintf('%5.2e time for chebfun build\n',t1s{j})
-end
-
[…]

### 2019-04-11 matlab/example/example_antunes_001_post.m

@@ -1,46 +1,0 @@
-%EXAMPLE_ANTUNES_001_POST
-%
-% post-processing for example_antunes_001
-%
-% reads in chebfun and writes info for figures to 
-% various files 
-
-filein='example_antunes_001.mat';
-load(filein);
-
-rdetcheb = real(detcheb);
-idetcheb = imag(detcheb);
-detcheb_roots = roots(detcheb,'complex'); 
-detcheb_roots = detcheb_roots(:).';
-detcheb_coeffs = chebcoeffs(detcheb); 
-detcheb_coeffs = detcheb_coeffs(:).';
-
-dom = detcheb.domain;
-
-nplot = 2000;
-xx = linspace(dom(1),dom(2),nplot);
-yyr = rdetcheb(xx);
-yyi = idetcheb(xx);
-
-%%
-
-fileout = 'ex_antunes_001_plotreal.tex';
-fid = fopen(fileout,'w'); fprintf(fid,'%7.4e %7.4e\n',[xx;yyr]); 
-fclose(fid);
-
-fileout = 'ex_antunes_001_plotimag.tex';
-fid = fopen(fileout,'w'); fprintf(fid,'%7.4e %7.4e\n',[xx;yyi]); 
-fclose(fid);
-
-fileout = 'ex_antunes_001_roots.tex';
-fid = fopen(fileout,'w'); 
-fprintf(fid,'%7.4e %7.4e\n',[detcheb_roots;zeros(size(detcheb_roots))]); 
-fclose(fid);
-
-fileout = 'ex_antunes_001_coeffs.tex';
-fid = fopen(fileout,'w'); 
-fprintf(fid,'%7.4e %7.4e\n',[1.0*(1:length(detcheb_coeffs)); ...
-    abs(detcheb_coeffs)/abs(detcheb_coeffs(1))]);
-fclose(fid);
-
-

### 2019-04-11 matlab/example/example_barbell_001_big_plots.m

@@ -1,0 +1,102 @@
+%EXAMPLE_BARBELL_001_BIG_PLOTS
+%
+% batch make images of vorticity 
+
+addpath('../src','../test','../../mwrap');
+
+filein = 'example_barbell_001.mat';
+fileout = 'example_barbell_001_big_plots.mat';
+addpath('~/Dropbox/MATLAB/chebfun')
+addpath(genpath('~/Dropbox/MATLAB/FLAM'))
+
+load(filein);
+
+%% 
+
+nints = length(detchebs);
+
+rtsc = cell(nints,1);
+
+for i = 1:nints
+    rtsc{i} = roots(detchebs{i},'complex');
+end
+
+nrts = 0;
+for i = 1:nints
+    nrts = nrts + length(rtsc{i});
+end
+
+rts = zeros(nrts,1);
+ind = 1;
+for i = 1:nints
+    rts(ind:(ind+length(rtsc{i})-1)) = rtsc{i};
+    ind = ind + length(rtsc{i});
+end
+
+%%
+
+nxdir = 100;
+
+xs = chunker.chunks(1,:,:); xmin = min(xs(:)); xmax = max(xs(:));
+ys = chunker.chunks(2,:,:); ymin = min(ys(:)); ymax = max(ys(:));
+offsetx = 0.5*(xmax-xmin)/(nxdir-1);
+offsety = 0.5*(ymax-ymin)/(nxdir-1);
+xgrid = linspace(xmin+offsetx,xmax-offsetx,nxdir);
+ygrid = linspace(ymin+offsety,ymax-offsety,nxdir);
+[xx,yy] = meshgrid(xgrid,ygrid);
+nt = length(xx(:)); targs = zeros(2,nt); 
+targs(1,:) = xx(:); targs(2,:) = yy(:);
+
+%
+
+start = tic; in = chunkerin(chunker,targs); toc(start)
+
+hold off
+scatter(targs(1,in),targs(2,in),'go');
+hold on
+scatter(targs(1,~in),targs(2,~in),'rx');
+scatter(xs(:),ys(:),'bo');
+
+%%
+
+opts.usesmooth=2;
+opts.verb=false;
+opts.quadkgparams = {'RelTol',1.0e-8,'AbsTol',1.0e-8};
+opts.gausseps = 1e-7;
+targsin=targs(:,in);
+intparams = []; intparams.intorder = 16;
+ss = cell(length(rts),1);
+vorts = cell(length(rts),1);
[…]

### 2019-04-11 matlab/example/example_barbell_001_big_plots_post.m

@@ -1,0 +1,212 @@
+%EXAMPLE_BARBELL_001_BIG_PLOTS_POST
+%
+% process saved vorticity and singular value data
+
+addpath('../src','../test','../../mwrap');
+
+filein1 = 'example_barbell_001.mat';
+filein2 = 'example_barbell_001_big_plots.mat';
+
+load(filein1); load(filein2);
+
+chunkers = multichunksort(chunker,nchs,true);
+%%
+
+sings = zeros(length(ss),1);
+for i = 1:length(ss)
+    sings(i) = ss{i}(end);
+end
+
+%%
+
+indimagbig = abs(imag(rts)) > sqrt(p.chebfuneps);
+nnz(indimagbig)
+find(indimagbig)
+sings(indimagbig)
+
+%%
+%
+
+[iplot,ichkdbl] = find_unique_evals(rts,sings,1e-5,...
+    sqrt(p.chebfuneps));
+
+%% 
+
+figure(1)
+clf
+
+mrow = 12; ncol = 10;
+[ha, pos] = tight_subplot(mrow,ncol,[.01 .01],[.01 .01],[.01 .01]) ;
+
+nsamp=10;
+
+for ii = 1:min(length(iplot),mrow*ncol)
+    i = iplot(ii);
+    axes(ha(ii))
+    vort = nan(size(vorts{i}));
+    
+    vort(in) = vorts{i}(in); iin = find(in); isel = randperm(length(iin),nsamp);
+    vort = vort/(mean(vort(iin(isel))));
+    norm(imag(vort(in)),'fro')/norm(vort(in),'fro')
+    vort = real(vort);
+    vmax = max(max(abs(vort))); vort = vort/vmax;
+    hold off
+    h = pcolor(xx,yy,vort); set(h,'EdgeColor','none');
+    hold on
+    for i = 1:length(chunkers)
+        chnkr = chunkers{i};
+        plot(chnkr.chunks(1,:),chnkr.chunks(2,:),'-k')
+    end
+    
+    axis equal
+    colormap(redblue)
+    caxis([-1 1])
+
+    set(gca,'XTick',[], 'YTick', [])
+    axis equal    
+    axis tight
+    axis equal
+end
+
+%%
+
+tempi = [97, 98];
+
+mmrow = 1; nncol =2;
+
+for ii = 1:2
+    i =  tempi(ii);
+    subplot(mmrow,nncol,ii)
[…]

### 2019-04-11 matlab/example/example_many_holes_002.m

@@ -1,87 +1,0 @@
-
-%EXAMPLE_MANY_HOLES_002
-%
-% compute a chebfun representation of the fredholm determinant 
-% of the system I-2D for a domain on the interval [0.1,10]
-% save chebfun, domain, and some settings to a file
-
-filebase = 'example_many_holes_002'; 
-timeref = datestr(now,'_yyyymmdd_HHMMSS');
-fileout = [filebase, timeref, '.mat'];
-
-a = 0.1; b = 10.0; chebab = [a b];
-
-max_rzk = b; lam = 2*pi/max_rzk;
-
-seed = 8675309;
-rng(seed);
-addpath('../src')
-addpath('../example')
-addpath('../../mwrap')
-
-cparams.eps = 1.0e-3;
-cparams.nchmax = 100000;
-cparams.maxchunklen = lam;
-cparams.nover = 2;
-narms = 3;
-amp = 0.25;
-W = 3.0; H = 2.0; p = 4.0;
-chunkers = {};
-chunkert = chunkfunc(@(t) smoothbox(t,W,H,p),cparams);
-chunkers{1} = chunkert;
-
-nw = 4;
-nh = 3;
-
-ind = 1;
-for ii = 1:nw
-    for jj = 1:nh
-        phi = rand()*2*pi;
-        scale = 0.20;
-        ctr = [-(nw-1)/2.0 + ii-1; -(nh-1)/2.0 + jj-1];
-        chunkert = chunkfunc(@(t) starfish(t,narms,amp,ctr,phi,scale),cparams);
-        chunkert = chunkreverse(chunkert);
-        chunkert = chunksort(chunkert);
-        ind = ind+1;
-        chunkers{ind} = chunkert;
-        
-    end
-end
-        
-[chunker,nchs] = chunkermerge(chunkers);
-
-%
-
-xs = chunker.chunks(1,:,:); xs = xs(:);
-ys = chunker.chunks(2,:,:); ys = ys(:);
-
-rnorms = chunknormals(chunker);
-
-intparams.intorder = chunker.k;
-
-hold off
-quiver(xs,ys,rnorms(1,:).',rnorms(2,:).')
-hold on
-scatter(xs,ys)
-
-%%
-
-% build matrix
-
-cd = -2.0 + 1i*0.0;
-cs = 0.0 - 1i*2.0;
-%csfun = @(zk) -2.0*1i*zk;
-ncomp = length(nchs);
-
-%
-
[…]

### 2019-04-11 matlab/example/example_many_holes_004.m

@@ -1,0 +1,106 @@
+
+%EXAMPLE_MANY_HOLES_004
+%
+% compute a chebfun representation of the fredholm determinant 
+% of the system I-2D-2iS for a domain on finer intervals
+% save chebfun, domain, and some settings to a file
+
+filebase = 'example_many_holes_004'; 
+timeref = datestr(now,'_yyyymmdd_HHMMSS');
+fileout = [filebase, timeref, '.mat'];
+
+chebabs = cell(16,1);
+for j = 1:8
+    chebabs{j} = 3.0 + 0.5*[1.0*(j-1) 1.0*(j)];
+end
+
+for j = 9:16
+    chebabs{j} = 7 + 0.25*[1.0*(j-9) 1.0*(j-8)];
+end
+
+max_rzk = chebabs{end}(end); lam = 2*pi/max_rzk;
+
+%%
+
+seed = 8675309;
+rng(seed);
+addpath('../src')
+addpath('../example')
+addpath('../../mwrap')
+
+cparams.eps = 1.0e-3;
+cparams.nchmax = 100000;
+cparams.maxchunklen = lam;
+cparams.nover = 2;
+narms = 3;
+amp = 0.125;
+W = 3.0; H = 2.0; p = 4.0;
+chunkers = {};
+chunkert = chunkfunc(@(t) smoothbox(t,W,H,p),cparams);
+chunkers{1} = chunkert;
+
+nw = 4;
+nh = 3;
+
+ind = 1;
+for ii = 1:nw
+    for jj = 1:nh
+        phi = rand()*2*pi;
+        scale = 0.20;
+        ctr = [-(nw-1)/2.0 + ii-1; -(nh-1)/2.0 + jj-1];
+        chunkert = chunkfunc(@(t) starfish(t,narms,amp,ctr,phi,scale),cparams);
+        chunkert = chunkreverse(chunkert);
+        chunkert = chunksort(chunkert);
+        ind = ind+1;
+        chunkers{ind} = chunkert;
+        
+    end
+end
+        
+[chunker,nchs] = chunkermerge(chunkers);
+
+%
+
+xs = chunker.chunks(1,:,:); xs = xs(:);
+ys = chunker.chunks(2,:,:); ys = ys(:);
+
+rnorms = chunknormals(chunker);
+
+intparams.intorder = chunker.k;
+
+hold off
+quiver(xs,ys,rnorms(1,:).',rnorms(2,:).')
+hold on
[…]

### 2019-04-11 matlab/example/example_many_holes_004_big_plots.m

@@ -1,0 +1,99 @@
+%EXAMPLE_MANY_HOLES_004_BIG_PLOTS
+%
+% batch make images of vorticity 
+
+addpath('../src','../test','../../mwrap');
+
+filein = 'example_many_holes_004.mat';
+fileout = 'example_many_holes_004_big_plots.mat';
+addpath('~/Dropbox/MATLAB/chebfun')
+addpath(genpath('~/Dropbox/MATLAB/FLAM'))
+
+load(filein);
+
+%% 
+
+nints = length(detchebs);
+
+rtsc = cell(nints,1);
+
+for i = 1:nints
+    rtsc{i} = roots(detchebs{i},'complex');
+end
+
+nrts = 0;
+for i = 1:nints
+    nrts = nrts + length(rtsc{i});
+end
+
+rts = zeros(nrts,1);
+ind = 1;
+for i = 1:nints
+    rts(ind:(ind+length(rtsc{i})-1)) = rtsc{i};
+    ind = ind + length(rtsc{i});
+end
+
+%%
+
+nxdir = 100;
+xs = chunker.chunks(1,:,:); xmin = min(xs(:)); xmax = max(xs(:));
+ys = chunker.chunks(2,:,:); ymin = min(ys(:)); ymax = max(ys(:));
+xgrid = linspace(xmin,xmax,nxdir);
+ygrid = linspace(ymin,ymax,nxdir);
+[xx,yy] = meshgrid(xgrid,ygrid);
+nt = length(xx(:)); targs = zeros(2,nt); 
+targs(1,:) = xx(:); targs(2,:) = yy(:);
+
+%
+
+start = tic; in = chunkerin(chunker,targs); toc(start)
+
+hold off
+scatter(targs(1,in),targs(2,in),'go');
+hold on
+scatter(targs(1,~in),targs(2,~in),'rx');
+scatter(xs(:),ys(:),'bo');
+
+%%
+
+opts.usesmooth=2;
+opts.verb=false;
+opts.quadkgparams = {'RelTol',1.0e-8,'AbsTol',1.0e-8};
+opts.gausseps = 1e-7;
+targsin=targs(:,in);
+intparams = []; intparams.intorder = 16;
+ss = cell(length(rts),1);
+vorts = cell(length(rts),1);
+xnulls = cell(length(rts),1);
+
+opts.FLAM=1;
+
+parfor i = 1:length(rts)
+    fprintf('iter %d\n',i);
[…]

### 2019-04-11 matlab/example/example_many_holes_004_big_plots_post.m

@@ -1,0 +1,295 @@
+%EXAMPLE_MANY_HOLES_004_BIG_PLOTS_POST
+%
+% process saved vorticity and singular value data
+
+clear all
+
+addpath('../src','../test','../../mwrap');
+
+filein1 = 'example_many_holes_004.mat';
+filein2 = 'example_many_holes_004_big_plots.mat';
+
+filein0 = 'example_many_holes_005_big_plots.mat';
+filein00 = 'example_many_holes_005.mat';
+
+load(filein0); load(filein00);
+ss5 = ss; rts5 = rts; detchebs5 = detchebs;
+vorts5 = vorts; xnulls5 = xnulls;
+
+load(filein1); load(filein2);
+
+chunkers = multichunksort(chunker,nchs,true);
+%%
+
+sings = zeros(length(ss),1);
+for i = 1:length(ss)
+    sings(i) = ss{i}(1);
+end
+
+sings5 = zeros(length(ss5),1);
+for i = 1:length(ss5)
+    sings5(i) = ss5{i}(1);
+end
+
+%
+
+indimagbig = abs(imag(rts)) > sqrt(p.chebfuneps);
+nnz(indimagbig)
+find(indimagbig)
+sings(indimagbig)
+
+%
+
+[iplot,ichkdbl] = find_unique_evals(rts,sings,1e-5, ...
+    sqrt(p.chebfuneps));
+
+%% 
+
+figure(1)
+clf
+
+mrow = 8; ncol = 10;
+[ha, pos] = tight_subplot(mrow,ncol,[.01 .01],[.01 .01],[.01 .01]);
+
+nsamp=10;
+
+for ii = 1:mrow*ncol
+    axes(ha(ii))
+    
+    if ii > length(iplot)
+        axis off
+    else
+        i = iplot(ii);
+
+        vort = nan(size(vorts{i}));
+
+        vort(in) = vorts{i}(in); iin = find(in); isel = randperm(length(iin),nsamp);
+        vort = vort/(mean(vort(iin(isel))));
+        norm(imag(vort(in)),'fro')/norm(vort(in),'fro')
+        vort = real(vort);
+        vmax = max(max(abs(vort))); vort = vort/vmax;
+        hold off
+        h = pcolor(xx,yy,vort); set(h,'EdgeColor','none');
+        hold on
[…]

### 2019-04-11 matlab/example/example_many_holes_005.m

@@ -1,0 +1,101 @@
+
+%EXAMPLE_MANY_HOLES_005
+%
+% compute a chebfun representation of the fredholm determinant 
+% of the system I-2D-2iS for a domain on the interval [4.5,4.75]
+% save chebfun, domain, and some settings to a file
+
+filebase = 'example_many_holes_005';
+timeref = datestr(now,'_yyyymmdd_HHMMSS');
+fileout = [filebase, timeref, '.mat'];
+
+chebabs = cell(1,1);
+chebabs{1} = [4.5,4.75];
+
+max_rzk = 9.0;
+lam = 2*pi/max_rzk;
+
+%%
+
+seed = 8675309;
+rng(seed);
+addpath('../src')
+addpath('../example')
+addpath('../../mwrap')
+
+cparams.eps = 1.0e-3;
+cparams.nchmax = 100000;
+cparams.maxchunklen = lam;
+cparams.nover = 2;
+narms = 3;
+amp = 0.125;
+W = 3.0; H = 2.0; p = 4.0;
+chunkers = {};
+chunkert = chunkfunc(@(t) smoothbox(t,W,H,p),cparams);
+chunkers{1} = chunkert;
+
+nw = 4;
+nh = 3;
+
+ind = 1;
+for ii = 1:nw
+    for jj = 1:nh
+        phi = rand()*2*pi;
+        scale = 0.20;
+        ctr = [-(nw-1)/2.0 + ii-1; -(nh-1)/2.0 + jj-1];
+        chunkert = chunkfunc(@(t) starfish(t,narms,amp,ctr,phi,scale),cparams);
+        chunkert = chunkreverse(chunkert);
+        chunkert = chunksort(chunkert);
+        ind = ind+1;
+        chunkers{ind} = chunkert;
+        
+    end
+end
+        
+[chunker,nchs] = chunkermerge(chunkers);
+
+%
+
+xs = chunker.chunks(1,:,:); xs = xs(:);
+ys = chunker.chunks(2,:,:); ys = ys(:);
+
+rnorms = chunknormals(chunker);
+
+intparams.intorder = chunker.k;
+
+hold off
+quiver(xs,ys,rnorms(1,:).',rnorms(2,:).')
+hold on
+scatter(xs,ys)
+
+%%
+
+% build matrix
+
+cd = -2.0 + 1i*0.0;
+cs = 0.0 - 1i*2.0;
+ncomp = length(nchs);
+
+%
+
[…]

### 2019-04-11 matlab/example/example_many_holes_005_big_plots.m

@@ -1,0 +1,99 @@
+%EXAMPLE_MANY_HOLES_004_BIG_PLOTS
+%
+% batch make images of vorticity 
+
+addpath('../src','../test','../../mwrap');
+
+filein = 'example_many_holes_005.mat';
+fileout = 'example_many_holes_005_big_plots.mat';
+addpath('~/Dropbox/MATLAB/chebfun')
+addpath(genpath('~/Dropbox/MATLAB/FLAM'))
+
+load(filein);
+
+%% 
+
+nints = length(detchebs);
+
+rtsc = cell(nints,1);
+
+for i = 1:nints
+    rtsc{i} = roots(detchebs{i},'complex');
+end
+
+nrts = 0;
+for i = 1:nints
+    nrts = nrts + length(rtsc{i});
+end
+
+rts = zeros(nrts,1);
+ind = 1;
+for i = 1:nints
+    rts(ind:(ind+length(rtsc{i})-1)) = rtsc{i};
+    ind = ind + length(rtsc{i});
+end
+
+%%
+
+nxdir = 100;
+xs = chunker.chunks(1,:,:); xmin = min(xs(:)); xmax = max(xs(:));
+ys = chunker.chunks(2,:,:); ymin = min(ys(:)); ymax = max(ys(:));
+xgrid = linspace(xmin,xmax,nxdir);
+ygrid = linspace(ymin,ymax,nxdir);
+[xx,yy] = meshgrid(xgrid,ygrid);
+nt = length(xx(:)); targs = zeros(2,nt); 
+targs(1,:) = xx(:); targs(2,:) = yy(:);
+
+%
+
+start = tic; in = chunkerin(chunker,targs); toc(start)
+
+hold off
+scatter(targs(1,in),targs(2,in),'go');
+hold on
+scatter(targs(1,~in),targs(2,~in),'rx');
+scatter(xs(:),ys(:),'bo');
+
+%%
+
+opts.usesmooth=2;
+opts.verb=false;
+opts.quadkgparams = {'RelTol',1.0e-8,'AbsTol',1.0e-8};
+opts.gausseps = 1e-7;
+targsin=targs(:,in);
+intparams = []; intparams.intorder = 16;
+ss = cell(length(rts),1);
+vorts = cell(length(rts),1);
+xnulls = cell(length(rts),1);
+
+opts.FLAM=1;
+
+parfor i = 1:length(rts)
+    fprintf('iter %d\n',i);
[…]

### 2019-04-11 matlab/src/barbell_example_001.m

@@ -1,0 +1,30 @@
+function verts = barbell_example_001(s1,s2,hb,lb)
+%BARBELL_EXAMPLE_001 
+%
+% Input (all optional)
+%   s1 - side length of left square (4.0)
+%   s2 - side length of right square (3.0)
+%   hb - height of bridge between squares (1.0)
+%   lb - length of bridge (2.5)
+%
+
+if nargin < 1; s1 = 4.0; end
+if nargin < 2; s2 = 3.0; end
+if nargin < 3; hb = 1.0; end
+if nargin < 4; lb = 2.5; end
+
+verts_sqr1 = s1/2.0*[1, -1, -1, 1; 1, 1, -1, -1];
+verts_sqr2 = s2/2.0*[-1, 1, 1, -1; -1, -1, 1, 1];
+
+wbrdg = hb/2.0;
+
+ctr_sqr1 = [-(s1/2.0+lb/2.0); 0.0];
+ctr_sqr2 = [(s2/2.0+lb/2.0); 0.0];
+
+verts_sqr1 = verts_sqr1 + repmat(ctr_sqr1,1,size(verts_sqr1,2));
+verts_sqr2 = verts_sqr2 + repmat(ctr_sqr2,1,size(verts_sqr2,2));
+
+verts1 = [verts_sqr1(1,end), verts_sqr2(1,1); -wbrdg, -wbrdg];
+verts2 = [verts_sqr2(1,end), verts_sqr1(1,1); wbrdg, wbrdg];
+
+verts = [verts_sqr1, verts1, verts_sqr2, verts2];

### 2019-04-11 doc/draft-01-stokes/01intro.tex

@@
 directly discretize the
-Stokes operator, typically with a
+differential operator, typically with a
 finite element basis, and the eigenvalues are found
@@
 %
-This reduces the number of unknowns over finite
-element discretizations, particularly given
-that finite element methods suffer from
-high-frequency ``pollution'' due to the 
+This approach reduces the number of unknowns over finite
+element discretizations, and does not suffer
+from high-frequency ``pollution'' due to the 
 large number of unknowns required to resolve
 the computation when $k$ is large
-\cite{babuska1997pollution}.
+\cite{babuska1997pollution} (which typically affects
+finite element approaches to determining the eigenvalues).
 
@@
 In \cref{sec:prelim}, we set the notation, provide some
-mathematical preliminaries, and review the
+mathematical preliminaries, and review 
 properties of single and double layer potentials

### 2019-04-11 doc/draft-01-stokes/03analysis.tex

--- 2019-04-11 doc/draft-01-stokes/03analysis.tex
@@
 for the scalar Helmholtz equation.
-While uniqueness results for interior Dirichlet, Neumann, and impedance
-problems follow from energy considerations and compactness
-arguments, the proofs for uniqueness of exterior
-results are more involved. 
-In particular,
-this entails making the exterior problems
-well-posed by imposing an appropriate radiaiton condition.
-We present well-posed boundary value formulations 
-for both interior and exterior Dirichlet, Neumann and impedance
-boundary value problems, and also
-present uniqueness results for all of them.
+%
+While uniqueness results for interior Dirchilet,
+Neumann, and impedance problems follow from energy
+considerations and compactness arguments, the proofs
+for the uniqueness of exterior problems are more
+involved.
+%
+In particular, the exterior problems are only 
+well-posed after imposing an appropriate radiation
+condition.
+%
+We formulate well-posed boundary value problems 
+for both interior and exterior domains with
+Dirichlet, Neumann and impedance boundary
+conditions and present uniqueness results for
+each.
 
@@
 and the Dirichlet eigenvalues of the Stokes operator on multiply
-connected domains also causes non-robustness and introduces near 
-resonances for simply connected domains
-which are almost multiply connected.
+connected domains also causes non-robustness and introduces
+near-resonances for simply-connected domains which are almost
+multiply-connected.
+%We demonstrate this issue numerically
+%in~\cref{subsec:crescent}.
 

### 2019-04-11 doc/draft-01-stokes/04numerical.tex

--- 2019-04-11 doc/draft-01-stokes/04numerical.tex
@@
 discretization.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{media/annulus_discretization.pdf}
+\caption{Sample discretization of an annulus 1<r<1.7, where the inner
+circle, $r=1$ is discretized using $6$ panels and the outer circle $r=1.7$
+is discretized using $10$ panels.}
+\label{fig:panels}
+\end{figure}
 %

### 2019-04-12 doc/draft-01-stokes/04numerical.tex
minor edits

@@
 \includegraphics[width=0.5\textwidth]{media/annulus_discretization.pdf}
-\caption{Sample discretization of an annulus 1<r<1.7, where the inner
+\caption{Sample discretization of an annulus, where the inner
 circle, $r=1$ is discretized using $6$ panels and the outer circle $r=1.7$
@@
   \end{subfigure}
+  \caption{Computational domains.}
 \end{figure}
@@
     \caption{Smallest singular value of the BIE operator
-      for the computed roots (original intervals)
-      along with an estimate of the error in the root (dotted).}
+      for the computed roots on the original intervals (\textbullet)
+      and an estimate of the error (dotted).}
     \label{subfig:many_inclusions_sings_west}

### 2019-04-12 external/FLAM/hifde/hifde2x.m
unsubmodule FLAM

@@ -1,0 +1,482 @@
+% HIFDE2X  Hierarchical interpolative factorization for differential equations
+%          on general meshes in 2D.
+%
+%    F = HIFDE2X(A,X,OCC,RANK_OR_TOL) produces a factorization F of the sparse
+%    interaction matrix A on the points X using tree occupancy parameter OCC and
+%    local skeletonization precision parameter RANK_OR_TOL.
+%
+%    F = HIFDE2X(A,X,OCC,RANK_OR_TOL,OPTS) also passes various options to the
+%    algorithm. Valid options include:
+%
+%      - EXT: set the root node extent to [EXT(I,1) EXT(I,2)] along dimension I.
+%             If EXT is empty (default), then the root extent is calculated from
+%             the data.
+%
+%      - LVLMAX: maximum tree depth (default: LVLMAX = Inf).
+%
+%      - SKIP: skip the dimension reductions on the first SKIP levels (default:
+%              SKIP = 0).
+%
+%      - SYMM: assume that the matrix is unsymmetric if SYMM = 'N', (complex-)
+%              symmetric if SYMM = 'S', Hermitian if SYMM = 'H', and Hermitian
+%              positive definite if SYMM = 'P' (default: SYMM = 'N'). If
+%              SYMM = 'N' or 'S', then local factors are computed using the LU
+%              decomposition; if SYMM = 'H', the LDL decomposition; and if
+%              SYMM = 'P', the Cholesky decomposition.
+%
+%      - VERB: display status of the code if VERB = 1 (default: VERB = 0).
+%
+%    References:
+%
+%      A. Gillman, P.G. Martinsson. A direct solver with O(N) complexity for
+%        variable coefficient elliptic PDEs discretized via a high-order
+%        composite spectral collocation method. SIAM J. Sci. Comput. 36 (4):
+%        A2023-A2046, 2014.
+%
+%      A. Gillman, P.G. Martinsson. An O(N) algorithm for constructing the
+%        solution operator to 2D elliptic boundary value problems in the absence
+%        of body loads. Adv. Comput. Math. 40 (4): 773-796, 2014.
+%
[…]

### 2019-04-12 external/FLAM/hifie/test/ie_cube1.m

@@ -1,0 +1,131 @@
+% First-kind integral equation on the unit cube, Laplace single-layer.
+
+function ie_cube1(n,occ,p,rank_or_tol,skip,symm)
+
+  % set default parameters
+  if nargin < 1 || isempty(n)
+    n = 32;
+  end
+  if nargin < 2 || isempty(occ)
+    occ = 512;
+  end
+  if nargin < 3 || isempty(p)
+    p = 512;
+  end
+  if nargin < 4 || isempty(rank_or_tol)
+    rank_or_tol = 1e-3;
+  end
+  if nargin < 5 || isempty(skip)
+    skip = 0;
+  end
+  if nargin < 6 || isempty(symm)
+    symm = 'h';
+  end
+
+  % initialize
+  [x1,x2,x3] = ndgrid((1:n)/n);
+  x = [x1(:) x2(:) x3(:)]';
+  N = size(x,2);
+  proxy = randn(3,p);
+  proxy = 1.5*bsxfun(@rdivide,proxy,sqrt(sum(proxy.^2)));
+  clear x1 x2 x3
+
+  % compute diagonal quadratures
+  h = 1/n;
+  intgrl = 8*triplequad(@(x,y,z)(1/(4*pi)./sqrt(x.^2 + y.^2 + z.^2)), ...
+                        0,h/2,0,h/2,0,h/2);
+
+  % factor matrix
+  Afun = @(i,j)Afun2(i,j,x,intgrl);
+  pxyfun = @(x,slf,nbr,l,ctr)pxyfun2(x,slf,nbr,l,ctr,proxy);
+  opts = struct('skip',skip,'symm',symm,'verb',1);
+  F = hifie3(Afun,x,occ,rank_or_tol,pxyfun,opts);
+  w = whos('F');
+  fprintf([repmat('-',1,80) '\n'])
+  fprintf('mem: %6.2f (MB)\n',w.bytes/1e6)
+
+  % set up FFT multiplication
+  a = reshape(Afun(1:N,1),n,n,n);
+  B = zeros(2*n-1,2*n-1,2*n-1);
+  B(  1:n  ,  1:n  ,  1:n  ) = a;
+  B(  1:n  ,  1:n  ,n+1:end) = a(:,:,2:n);
[…]

### 2019-04-12 external/FLAM/hifie/test/ie_square3.m

@@ -1,0 +1,152 @@
+% Second-kind integral equation on the unit square, Helmholtz single-layer.
+
+function ie_square3(n,k,occ,p,rank_or_tol,skip,symm)
+
+  % set default parameters
+  if nargin < 1 || isempty(n)
+    n = 128;
+  end
+  if nargin < 2 || isempty(k)
+    k = 2*pi*4;
+  end
+  if nargin < 3 || isempty(occ)
+    occ = 64;
+  end
+  if nargin < 4 || isempty(p)
+    p = 64;
+  end
+  if nargin < 5 || isempty(rank_or_tol)
+    rank_or_tol = 1e-6;
+  end
+  if nargin < 6 || isempty(skip)
+    skip = 1;
+  end
+  if nargin < 7 || isempty(symm)
+    symm = 's';
+  end
+
+  % initialize
+  [x1,x2] = ndgrid((1:n)/n);
+  x = [x1(:) x2(:)]';
+  N = size(x,2);
+  theta = (1:p)*2*pi/p;
+  proxy = 1.5*[cos(theta); sin(theta)];
+  clear x1 x2
+
+  % set up potential
+  V = exp(-32*((x(1,:) - 0.5).^2 + (x(2,:) - 0.5).^2))';
+  sqrtb = k*sqrt(V);
+
+  % compute diagonal quadratures
+  h = 1/n;
+  intgrnd = @(x,y)(0.25i*besselh(0,1,k*sqrt(x.^2 + y.^2)));
+  if isoctave()
+    intgrl_r = 4*dblquad(@(x,y)(real(intgrnd(x,y))),0,h/2,0,h/2);
+    intgrl_i = 4*dblquad(@(x,y)(imag(intgrnd(x,y))),0,h/2,0,h/2);
+    intgrl = intgrl_r + intgrl_i*1i;
+  else
+    intgrl = 4*dblquad(intgrnd,0,h/2,0,h/2);
+  end
+
+  % factor matrix
+  Afun = @(i,j)Afun2(i,j,x,k,intgrl,sqrtb);
+  pxyfun = @(x,slf,nbr,l,ctr)pxyfun2(x,slf,nbr,l,ctr,proxy,k,sqrtb,symm);
+  opts = struct('skip',skip,'symm',symm,'verb',1);
[…]

### 2019-04-12 external/FLAM/ifmm/test/mv_circle1.m

@@ -1,0 +1,106 @@
+% Unit circle, Laplace sources.
+
+function mv_circle1(m,n,occ,p,rank_or_tol,near,store)
+
+  % set default parameters
+  if nargin < 1 || isempty(m)
+    m = 16384;
+  end
+  if nargin < 2 || isempty(n)
+    n = 8192;
+  end
+  if nargin < 3 || isempty(occ)
+    occ = 128;
+  end
+  if nargin < 4 || isempty(p)
+    p = 64;
+  end
+  if nargin < 5 || isempty(rank_or_tol)
+    rank_or_tol = 1e-12;
+  end
+  if nargin < 6 || isempty(near)
+    near = 0;
+  end
+  if nargin < 7 || isempty(store)
+    store = 'n';
+  end
+
+  % initialize
+  theta = 2*pi*rand(1,m);
+  rx = [cos(theta); sin(theta)];
+  theta = 2*pi*rand(1,n);
+  cx = [cos(theta); sin(theta)];
+  M = size(rx,2);
+  N = size(cx,2);
+  theta = (1:p)*2*pi/p;
+  proxy = 1.5*[cos(theta); sin(theta)];
+
+  % compress matrix
+  Afun = @(i,j)Afun2(i,j,rx,cx);
+  pxyfun = @(rc,rx,cx,slf,nbr,l,ctr)pxyfun2(rc,rx,cx,slf,nbr,l,ctr,proxy);
+  opts = struct('near',near,'store',store,'verb',1);
+  F = ifmm(Afun,rx,cx,occ,rank_or_tol,pxyfun,opts);
+  w = whos('F');
+  fprintf([repmat('-',1,80) '\n'])
+  fprintf('mem: %6.2f (MB)\n', w.bytes/1e6)
+
+  % test matrix apply accuracy
+  X = rand(N,1);
+  X = X/norm(X);
+  tic
+  ifmm_mv(F,X,Afun,'n');
+  t = toc;
+  X = rand(N,16);
+  X = X/norm(X);
+  r = randperm(M);
+  r = r(1:min(M,128));
+  A = Afun(r,1:N);
+  Y = ifmm_mv(F,X,Afun,'n');
+  Z = A*X;
+  e = norm(Z - Y(r,:))/norm(Z);
[…]

### 2019-04-12 doc/draft-01-stokes/appendix.tex
update numerical section and appendix

--- 2019-04-09 doc/draft-01-stokes/appendix.tex
@@
-\section{Dirichlet eigenvalues and eigenfunctions on the unit disk}
+\section{Dirichlet eigenvalues and eigenfunctions on the annulus \label{sec:annul_dir_exact}}
 In this section, we compute some of the Dirichlet eigenvalues
-corresponding to the a subset of radially symmetric eigenfunctions
+corresponding to a subset of the radially symmetric eigenfunctions
 on the annulus. 
@@
 \section{Neumann eigenvalues and eigenfunctions on the unit disk}
-In this section, we analytically compute some of the radially symmetric 
+In this section, we derive an analytical expression which
+can be used to compute some of the radially symmetric 
 Neumann eigenvalues on the unit disk for the Stokes operator.
@@
 \end{equation}
-and the pressure is given by $p=0$, since
+and the pressure is given by $p=0$, as
 $\bu$ satisfies $(\Delta + k^2)\bu = 0$.
@@
 \begin{equation}
+  \label{eq:neu_roots}
 -k \jpk + k^2 \jppk = 0 \, ,
@@
 are Neumann eigenvalues on the unit disk.
+The first $4$ roots of the \cref{eq:neu_roots} are
+in \cref{tab:neu_roots}.
+\begin{table}
+  \centering
+  \begin{tabular}{c}
+    k  \\ \hline
+    5.135622301840683 \\
+    8.417244140399865 \\
+    11.61984117214906 \\
+    14.79595178235126 
+  \end{tabular}
+  \caption{Roots of \cref{eq:neu_roots}.}
+  \label{tab:neu_roots}
+\end{table}

### 2019-04-12 matlab/example/example_barbell_001.m
update instructions

@@ -6,8 +6,9 @@
 % save chebfun, domain, and some settings to a file
 
 filebase = 'example_barbell_001'; 
-timeref = datestr(now,'_yyyymmdd_HHMMSS');
-fileout = [filebase, timeref, '.mat'];
+%timeref = datestr(now,'_yyyymmdd_HHMMSS');
+%fileout = [filebase, timeref, '.mat'];
+fileout = [filebase, '.mat'];
 
 
 chebabs = cell(12,1);

### 2019-04-12 matlab/example/example_many_holes_004.m

@@ -7,7 +7,8 @@
 
 filebase = 'example_many_holes_004'; 
 timeref = datestr(now,'_yyyymmdd_HHMMSS');
-fileout = [filebase, timeref, '.mat'];
+%fileout = [filebase, timeref, '.mat'];
+fileout = [filebase, '.mat'];
 
 chebabs = cell(16,1);
 for j = 1:8

### 2019-04-12 matlab/example/example_many_holes_005.m

@@ -7,7 +7,8 @@
 
 filebase = 'example_many_holes_005';
 timeref = datestr(now,'_yyyymmdd_HHMMSS');
-fileout = [filebase, timeref, '.mat'];
+%fileout = [filebase, timeref, '.mat'];
+fileout = [filebase, '.mat'];
 
 chebabs = cell(1,1);
 chebabs{1} = [4.5,4.75];

### 2019-04-15 doc/draft-01-stokes/03analysis.tex
update sections, minor edits

@@
   Let $\bh \in C(\Omega)$ be given and suppose 
-  $\eta \in \mathbb{C}$ with $\Re{(\eta)},\Im{(\eta)}>0$. 
+  $\eta \in \mathbb{C}$ with $\Re{(\eta)} >0$ and $\Im{(\eta)}\ge 0$. 
   Find $(\bu,p) \in A(\Omega)$  such that
@@
   Let $\bh \in C(\Gamma)$ be given and suppose that
-  $\eta \in \mathbb{C}$ with $\Re{(\eta)},\Im{(\eta)} >0$. 
+  $\eta \in \mathbb{C}$ with $\Re{(\eta)} > 0$ and $\Im{(\eta)} \ge 0$. 
   Find $(\bu,p) \in A(E)$

### 2019-04-15 doc/draft-01-stokes/04numerical.tex
update numerical section and appendix
update sections, minor edits

@@
 double layer potentials have weak
-singularities of the form $r^p\log r$
-which require special quadrature rules to
-achieve high-order accuracy.
+singularities of the form $|\xx-\yy|^p\log |\xx-\yy|$
+for some $p \in \N_0$, which require special
+quadrature rules to achieve high-order accuracy.
 %
@@
 Such shapes are of interest in
-materials design and micro-fluidics \note{cite}.
+materials design, see, for instance, \cite{overvelde2012compaction}.
 %
@@
 of the domain. This is consistent with other studies
-\note{cite}
+\cite{filoche2009strong,lindsay2018boundary}.
 

### 2019-04-15 doc/draft-01-stokes/03analysis.tex
spell check

@@
 %
-While uniqueness results for interior Dirchilet,
+While uniqueness results for interior Dirichlet,
 Neumann, and impedance problems follow from energy
@@
   $\Re(k),\Im (k) > 0$. Then the interior
-  impendence problem has a unique solution.
+  impedance problem has a unique solution.
 \end{thrm}
@@
 From the uniqueness of solutions to the interior 
-impedance problem, we conlcude that $\bu \equiv 0$
+impedance problem, we conclude that $\bu \equiv 0$
 in $\Omega_{j}$, which in particular implies

### 2019-04-15 doc/draft-01-stokes/04numerical.tex
spell check

@@
 We also evaluate the second smallest singular
-value if the root finding precedure suggests a
+value if the root finding procedure suggests a
 possible double root.
@@
 Note that $N^{-20}$ is the expected order of
-convergence for Generalized Gaussiuan quadratures for weakly 
+convergence for Generalized Gaussian quadrature for weakly 
 singular integrals.

### 2019-04-15 doc/draft-01-stokes/04numerical.tex
updating makefile, adding acks, adding affils, and cleaning figs
add info on software location and cpu used
update url
add note about order of ggq

@@
 with demonstrations on domains of analytical
-and practical interest.
+and practical interest. The software used to
+generate the figures is available online
+\footnote{\texttt{https://doi.org/10.5281/zenodo.2641296}}.
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{media/annulus_discretization.pdf}
+\includegraphics[width=0.5\textwidth]{fig/annulus_discretization.pdf}
 \caption{Sample discretization of an annulus, where the inner
@@
 %
-For the rules we used, $N_s = 16$ and
+For the 20th-order rule we used, $N_s = 16$ and
 $N_a = 48$. 
@@
   rule with sufficient precision.
+
+  The overall order of accuracy of the GGQ we use
+  is 20th-order, up to the precision of the ``far''
+  interactions.
 \end{remark}
@@
 and $|k_{C} - k_{0}| \lesssim N^{-20}$.
-Note that $N^{-20}$ is the expected order of
-convergence for Generalized Gaussian quadrature for weakly 
-singular integrals.
+Recall that the GGQ we use has an expected order
+of convergence of $N^{-20}$ for evaluating convolutions
+with such integral kernels,
+so that the error of the roots is observed to have the
+same order as the quadrature rule.
 In~\cref{fig:conv}, we show this result for $k_{0} = 13.48025717955055$
@@
   \centering
-  \includegraphics[width=0.98\textwidth]{media/conv-studies.pdf}
+  \includegraphics[width=0.98\textwidth]{fig/conv-studies.pdf}
   \caption{Convergence studies for the Dirichlet eigenvalues
@@
 \centering
-\includegraphics[width=0.98\linewidth]{media/det_spur.pdf}
+\includegraphics[width=0.98\linewidth]{fig/det_spur.pdf}
 \caption{The values of the discretized determinants $f_{C}^{N}(k)$ (left)
@@
 We plot the timing results corresponding to three different values of 
-$k$ in~\cref{fig:speed}.
+$k$ in~\cref{fig:speed}. The times are as recorded for a laptop with
+16Gb of RAM and an Intel Core i7-6600U CPU at 2.60GHz with 4 cores.
 \begin{figure}
 \centering
-\includegraphics[width=0.5\textwidth]{media/speed_res.pdf}
+\includegraphics[width=0.5\textwidth]{fig/speed_res.pdf}
 \caption{Time taken $(t)$ in seconds to evaluate the determinant $f_{C}^{N}(k)$ as

### 2019-05-07 doc/draft-01/01intro.tex
Updating buckling eigenvalues paper

--- 2018-06-24 doc/draft-01/01intro.tex
@@
 boundary of $\Omega$ and $w$ denote the vertical displacement.
-The buckling problem consists of finding 
+The buckling eigenvalue problem consists of finding 
 values $k^{2}$ such that the boundary value problem
@@
 \end{align}
-has a non-trivial solution. In a slight abuse of notation,
-these values and the corresponding solutions are often
-referred to as ``eigenvalues'' and ``eigenfunctions'',
-respectively. 
-It is well known that the buckling problem has a
-countable collection of such values
+has a non-trivial solution $w$. 
+It is well known that the values $k^2$ are necessarily real 
+and positive and there is a countable collection
+of such values 
 $0 < k_{1}^{2} \leq k_{2}^2 \leq \ldots \uparrow \infty$,
@@
 
+A related problem is that of the Stokes eigenvalue problem
+which is to find values $k^2$ such that
+\begin{align}
+\Delta (\Delta + k^2) w &= 0 \quad \textrm{in} \quad \Omega \label{eq:stokes1} \; , \\
+\nabla w &= 0 \quad \textrm{on} \quad \Gamma \label{eq:stokes2} \; ,\\
+\end{align}
+has a non-trivial solution $w$.
+While the buckling eigenvalues are identical to the Stokes
+eigenvalues on simply connected domains, on multiply
+connected domains it turns out that the buckling eigenvalues
+are a subset of the Stokes eigenvalues.
+
+In this note, we derive integral conditions on the stream function 
+associated with the Stokes eigenfunction
+to determine whether the Stokes eigenvalue is also a 
+buckling eigenvalue on multiply connected domains.
+Thus, given the Stokes eigenvalues 
+of the domain and the stream functions associated with the 
+corresponding eigenfunctions, 
+the buckling eigenvalues can be determined using a simple
+post-processing step.
+Given $k^2$ to be a Stokes eigenvalue, we also derive
+a well-conditioned second-kind integral equation for computing 
+the stream function associated with the 
+Stokes eigenfunction.
+
 Numerical simulations have long played an important
@@
   jia2009approximation,carstensen2014guaranteed}.
-Because of the fourth order term in \cref{eq:buck1},
-the system matrices resulting from a finite element
-discretization can have large condition numbers (growing
-like $1/h^4$ where $h$ is the diameter of a typical element
-in the discretization) which can cause numerical instability.
 
-Integral equation methods \cite{kress1989linear,
-  atkinson2009numerical,kitahara2014boundary} present
-a natural alternative to the finite element method
-for the buckling problem, because (a) the
-integral representation acts as an analytical preconditioner
-for the fourth order term and (b) the problem is reduced
-to one defined on the boundary of the domain alone,
-requiring fewer degrees of freedom to resolve the solution
-on a complex domain. In an integral equation method,
-the solution $w$ is represented in terms of a sum of
-two layer potentials (which a priori satisfy
-\cref{eq:buck1}) with unknown densities. Substituting this
-representation into the boundary conditions
-\cref{eq:buck2,eq:buck3} results in an integral equation
-for the unknown densities, which
-is in turn discretized using numerical quadrature.
-Unlike the original equation \cref{eq:buck1} and the weak
-formulation used in a finite element method, the integral
-equation for the unknown densities has a nonlinear dependence
-on the parameter $k^2$. In an integral equation method, then,
-the eigenvalues are found by searching for the values
-of $k^2$ where the discrete system for the unknown densities
-is no longer invertible.
-
-While integral equation methods for the buckling problem
-have been considered previously, the existing formulations
-have resulted in first kind integral equations, i.e. equations
-in which the operator is compact \cite{kitahara2014boundary,
-  antunes2011buckling}. This is unsatisfying from a theoretical
-perspective, because such operators are never invertible
-(though, they are injective precisely when $k^2$ is an
-eigenvalue \cite{kitahara2014boundary}) so that the
-relation between the non-invertibility of the discrete system
-and the eigenvalues is obscured. Further, such representations
-create numerical challenges because common measures of the
-``non-invertibility'' of a matrix, like the smallest singular
-value or the determinant, converge rapidly to zero for all
-values of $k^2$ as the boundary is refined.
-
-Second kind integral equations, i.e. integral equations
-of the form $\mathcal{I} + \mathcal{K}$ where $\mathcal{K}$
-is compact, have a more satisfying theory
-\cite{reed1972methods}, which translates
-well to numerical implementation
-\cite{bornemann2010numerical,zhao2015robust}.
-In \cite{zhao2015robust}, Zhao and Barnett demonstrated
-that the eigenvalues of the drum problem can be
-computed with such a framework, resulting in
-spectrally accurate numerical methods.
-In this paper, we develop a second kind integral
-equation for the buckling problem, based on the
-approach in \cite{rachh2017integral}. This allows
-for a robust approach to computing the eigenvalues
-of the buckling problem, model after the approach for
-the drum problem in \cite{zhao2015robust}, which we
-demonstrate with a number of examples.
+\note{needs work}
 

### 2019-05-07 doc/draft-01/02prelim.tex
Updating buckling eigenvalues paper

@@
 \section{Mathematical Preliminaries}
-
-In this paper, vector-valued
-quantities are denoted by bold, lower-case letters
-(e.g. $\bh$), while tensor-valued quantities are bold
-and upper-case (e.g. $\mathbf{T}$). 
-Subscript indices of non-bold characters (e.g. $h_j$ or $T_{jkl}$)
-are used to denote the entries within a vector ($\bh$) or tensor ($\bT$).
-We use the standard Einstein summation convention; in other words, 
+\label{sec:prelim}
+In this paper, vector- and tensor-valued quantities
+are denoted by bold letters (e.g. $\bh$ and $\mathbf{T}$). 
+Subscript indices of non-bold characters (e.g. $h_j$ or $T_{ij\ell}$)
+are used to denote the entries within a vector or tensor.
+We use the standard Einstein summation convention; i.e., 
 there is an implied sum taken over the repeated indices of 
@@
 operators on Banach spaces, with $\mathcal{I}$ denoting the
-identity.
+identity. Given a set $X$, we denote the closure of $X$
+by $\overline{X}$.
 
-\subsection{Green's functions}
+In the rest of the paper, 
+suppose that $\Omega$ is a multiply connected region defined by
+the intersection of a simply connected domain $\Omega_{0}$ 
+and the exteriors of a finite collection of bounded
+simply connected domains $\{ \Omega_{i} \}_{i=1}^{m}$. 
+Let $\Gamma_{i}$, denote the boundary of $\Omega_{i}$, and 
+let $\Gamma = \cup_{i=0}^{m} \Gamma_{i}$ denote the boundary of $\Omega$.
+Let $\bnu(\bx)$ denote the outward normal at $\bx \in \Gamma$.
 
-Let $\mathcal{L}_x$ denote a linear differential operator. A fundamental
-solution $G(\xx,\yy)$ of $\mathcal{L}_x$ satisfies the equation
-$\mathcal{L}_x G(\xx,\yy) = \delta_y(\xx)$ in the distributional sense, i.e.
-for sufficiently smooth $f$
+\section{Stokes eigenvalue problem}
+The Stokes Dirichlet eigenvalue problem is to find values $k^2$ such that
 \begin{equation}
-  \mathcal{L}_x \int_{\R^2} G(\xx,\yy) f(\yy) \, dy = f(\xx) \; .
+\begin{aligned}
+  -\Delta \uu + \nabla p &= k^2 \uu \quad \textrm{in} \quad
+  \Omega \label{eq:ostokes} \; , \\
+  \nabla \cdot \uu &= 0 \; , \\
+  \bu &=0 \quad \textrm{on} \quad \Gamma \, ,
+\end{aligned}
 \end{equation}
-We consider here
-``free-space'' Green's functions, i.e. fundamental solutions which satisfy
-some natural growth or decay conditions as $|\xx-\yy| \to \infty$.
-The Green's function of the oscillatory biharmonic equation
-\cref{eq:buck1} is given by 
+has a non-trivial solution $(\bu,p)$.
+Since the Stokes eigenfunction $\bu$ is divergence free, 
+and satisfies 
+$\int_{\Gamma_{i}} \bu \cdot \bnu \, ds = 0$ 
+for all $i=0,1,2\ldots m$, there exists a single valued
+stream function $\psi$ associated with $\bu$, i.e., 
+$\bu = \nabla^{\perp} \psi$ for all $\bx \in \Omega$.
+
+The Stokes eigenvalue problem can be reformulated as a buckling
+eigenvalue problem with gradient boundary conditions for
+the stream function $\psi$.
+Plugging in $\bu = \nabla^{\perp} \psi$ and applying $\nabla^{\perp} \cdot$
+to~\cref{eq:ostokes}, we observe that $\psi$ satisfies the following 
+differential equation.
+
+\begin{equation}
+\begin{aligned}
+\Delta (\Delta + k^2) \psi &= 0 \, \quad \textrm{in} \quad \Omega \, , \\
+\nabla \psi &=0 \, ,\quad \textrm{in} \quad \Gamma \, .
+\end{aligned}
+\end{equation}
+
+\section{Connection to buckling eigenvalues}
+It is clear that if $w$ is a buckling eigenfunction with
+eigenvalue $k^2$, then $\bu = \nabla^{\perp} w$ is a Stokes eigenfunction
+with the same eigenvalue. 
+Thus, for a given region $\Omega$,
+the buckling eigenvalues are a subset of the Stokes eigenvalue.
+
+However, the converse is not necessarily true. 
+The reason is the following.
+As before, suppose that $\bu$ is a Stokes eigenfunction
+with eigenvalue $k^2$.
+Note that a single valued stream function $\psi$ associated with
+$\bu$ always exists. 
+Moreover, on each component $\Gamma_{i}$, 
+$\psi$ satisfies $\partial_{\tau} \psi = 0$, which implies that
+$\psi$ is a constant on $\Gamma_{i}$, for each $i=0,1,2\ldots m$.
+If the domain is simply connected, then since $\psi$ is only
+well-defined upto a constant, we can adjust to constant term 
+to ensure that $\psi$ also satisfies $\psi = 0$ on $\Gamma_{0}$.
+However, on multiply connected domains, this is not always 
+the case since $\psi$ might be different constants on different
+boundary components. 
+In the following lemma, we identify necessary and sufficient 
+conditions on the stream function $\psi$ to guarantee that
+$\psi$ (upto a constant) is also a buckling eigenfunction.
+
+\begin{lem}
+\label{lem:mainlem}
+Suppose that $k^2$ is a Stokes eigenvalue for the region $\Omega$ and 
+let $\bu$ be the corresponding eigenfunction. 
+Then, the stream function associated with the velocity $\bu$ defined by
+$\psi = \left(\nabla^{\perp} \right)^{-1} \bu$ exists and is single valued. 
+Furthermore, $k^2$ is also a buckling eigenvalue if and only if
+there exists a constant $c$ such that
+\begin{equation}
+\frac{1}{\Gamma_{j}}\int_{\Gamma_{j}} \psi\, ds = c \quad \forall j=0,1,\ldots m \, .
+\end{equation}
+\end{lem}
+
+\begin{proof}
+Since $\bu$ is a Stokes eigenfunction, it satisfies
+\begin{equation}
+\int_{\Gamma_{j}} \bu \cdot \bn ds = 0 \quad j=1,2\ldots n \, .
+\end{equation}
+Thus, there exists a single valued stream function associated with the
+velocity field $\bu$ such that 
+\begin{equation}
+\nabla^{\perp} w = \bu \, .
+\end{equation}
+Furthermore, since $\bu$ satisfies the oscillatory Stokes equations, 
+$w$ satisfies
+\begin{align}
+\Delta (\Delta + k^{2} ) w &= 0 \, , \quad \bx \in \Omega \\
+\nabla^{\perp} w = \bu &=0 \, ,\quad \bx \in \Gamma \, ,
+\end{align}
+In particular $\psi= c_{j}$ for $\bx \in \Gamma_{j}$ for
+some constant $c_{j}$.
+Thus $k$ is also a buckling eigenvalue if and only if 
+\begin{equation}
+c_{j} = \frac{1}{|\Gamma_{j}|}\int_{\Gamma_{j}} w ds =  c \, .
+\end{equation}
+The buckling eigenfunction is then given by $\psi -c$. 
+\end{proof}
+
+\section{Computing the stream function}
+Given $k^2$ to be a Stokes eigenvalue, in this section, we describe
+an integral formulation for computing the eigenfunction $\bu$
+and the corresponding stream function $\psi$.
+
+Following the approach in~\cite{askhameig2019}, we
+first reformulate the oscillatory Stokes equation
+as an integral equation on the boundary using the combined
+field representation.
+
+Let $\GG(\bx,\by)$ denote the Stokeslet for the oscillatory
+Stokes equation and $T_{ij\ell}(\bx,\by)$ denote the corresponding
+Stresslet. 
+These are given by the formulae
+\begin{align} 
+  \GG &= - \II \Delta \Gbh + \nabla \otimes \nabla \Gbh 
+\label{eq:ostokeslet} \\
+  T_{ij\ell} &= - \partial_{x_j} \Glap \delta_{i\ell}
+  + \partial_{x_\ell} \left ( -\Delta \Gbh \delta_{ij} +
+  \partial_{x_i} \left(\partial_{x_j} \Gbh \right) \right)
+  \nonumber \\
+  & \qquad+ \partial_{x_i} \left ( -\Delta \Gbh \delta_{\ell j} +
+  \partial_{x_\ell} \left(\partial_{x_j} \Gbh \right) \right)
+  \; . \label{eq:ostress} 
+\end{align}
+$\Gbh$ is the Green's function for the oscillatory
+biharmonic equation given by
 \begin{equation}
@@
   \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \right ) \, ,
+  \label{eq:Gbh}
 \end{equation}
-where $k$ is the Helmholtz paramater in the oscillatory biharmonic equation,
-and $H_{0}^{1}(r)$ is the Hankel function of the first kind of order zero.
-Note that this is a scaled difference of the Green's function for
-Laplace, i.e.
+where $k$ is the Helmholtz parameter in the oscillatory biharmonic equation,
+and $H_{0}^{1}(r)$ is the Hankel function of the first kind of order zero,
+and $\Glap(\xx,\yy)$ is the Laplace Green's function given by
+\begin{equation}
+  \Glap(\xx,\yy) = \frac{1}{2\pi} \log |\xx-\yy| \; . \nonumber
+\end{equation}
+
+Given a density $\bmu$, the oscillatory Stokes single and double layer
+potentials denoted by $\bS[\bmu](\bx)$ and $\bD[\bmu](\bx)$ respectively,
+are given by
+\begin{align} \label{eq:singlelayer}
+  \bS [\bmu] (\xx) &= \int_\Gamma \GG (\xx,\yy) \bmu(\yy)
+  \, dS(\yy) \; , \\
+  \bD [\bmu] (\xx) &= \int_\Gamma \left ( \TT_{\cdot,\cdot,\ell}(\xx,\yy)
+  \nu_\ell(\yy)\right )^\intercal \bmu(\yy) \, dS(\yy) \; .
+\end{align}
+When solving the velocity boundary value problem for the oscillatory
+Stokes equation on multiply connected domains, the velocity
+is represented as a bomcinbed field layer potential, i.e.
+setting $\bu = (i\eta \bS_{k} + \bD_{k})[\bmu]$, where
+$\eta>0$ is a constant and $\bmu$ now is an unknown density.
+By construction, this velocity field satisfies the oscillatory
+Stokes equation.
+On imposing the velocity boundary condition, and using the jump
+conditions for the layer potentials (see~\cref{askhameig2019}, 
+for example)
+we obtain the following integral equation for the unknown density
+$\bmu$,
+\begin{equation}
+\label{eq:inteq0}
+(\cI - 2\cD_{k} -2i \eta \cS_{k})\bmu = 0 \, \quad \textrm{on} \quad \Gamma \,,
+\end{equation}
+where $\cS_{k}$ and $\cD_{k}$ are the restrictions of the layer potentials
+$\bS_{k}$ and $\bD_{k}$ on the boundary $\Gamma$ respectively, and are given
+by
+\begin{align}
+  \cS [\bmu] (\xx) &= \int_\Gamma \GG (\xx,\yy) \bmu(\yy)
+  \, dS(\yy) \\
+  \cD [\bmu] (\xx) &= \pv \int_\Gamma \left ( \TT_{\cdot,\cdot,\ell}(\bx,\by)
+  \nu_\ell(\yy)
+  \right )^\intercal \bmu(\yy) \, dS(\yy) \; .
+\end{align}
+Here \pv indicates that the integral is to be
+evaluated in the principal value sense.
+The integral equation~\cref{eq:inteq0} is known to be rank-deficient
+for all values of $k$ due to the divergence-free condition
+on $\bu$, and a standard approach is to use the following integral 
+equation instead
 
 \begin{equation}
-  \Glap(\xx,\yy) = \frac{1}{2\pi} \log |\xx-\yy| \; ,
+\label{eq:inteq}
+(\cI - 2\cD_{k} -2i \eta \cS_{k}-2\cW)\bmu = 0 \, \quad \textrm{on} \quad \Gamma \,,
 \end{equation}
-and the Green's function for the Helmholtz equation
-
+where $\cW$ is the operator given by
 \begin{equation}
-  \Ghelm(\xx,\yy) = -\frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \; .
+\cW[\bmu](\bx) = \frac{\bnu(x)}{|\Gamma|}\int_{\Gamma} \bmu(\by) \cdot \bnu(\by) \, ds \, .
 \end{equation}
 
-\subsection{An integral representation for the Stokes eigenvalue
-  problem}
+In~\cite{askhameig2019}, the authors show that the operator 
+$\cI -2\cD_{k} -2i \cS_{k} -2\cW$ is not invertible if and only
+if $k^2$ is a Stokes eigenvalue.
+Furthermore if $\bmu$ is a non-zero null-vector of $\cI - 2\cD_{k} -2i \cS_{k} 
+-2 \cW$, then 
+$\bu = (i \eta \bS_{k} + \bD_{k})[\bmu]$ is the Stokes eigenfunction.
 
-The Stokes eigenvalue problem (with ``no-slip'' boundary conditions)
-seeks values $k^2$ such that the equations
+In order to verify the conditions in~\cref{lem:mainlem}, we
+need to be able to compute the stream function associated with
+the velocity $\bmu$ defined above.
+If $\bmu = \mu_{\tau} \btau + \mu_{\nu} \bnu$, where $\btau=\bnu^{\perp}$
+is the positively oriented tangential vector then the
+layer potentials $\bS_{k}[\bmu]$ and $\bD_{k}[\bmu]$ can be rewritten as
 \begin{align}
-  \nabla p - \Delta \uu - k^2 \uu &= 0 \quad \textrm{in} \quad \Omega
-  \; , \label{eq:helmstokes}\\
-  \nabla \cdot \uu &= 0 \quad \textrm{in} \quad \Omega
-  \; , \label{eq:helmstokescty} \\
-  \uu &= 0 \quad \textrm{on} \quad \Gamma \; \label{eq:helmstokesnoslip}
+\bS_{k}[\bmu] &=  
+\nabla^{\perp} 
+\int_{\Gamma} (\partial_{\tau} \Gbh(\xx,\yy) \mu_{\tau}(\yy) -
+\partial_{\nu} \Gbh(\xx,\yy) \mu_{\nu}(\yy)) \, ds \\
+\bD_{k}[\bmu] &= 
+-\nabla 
+\int_{\Gamma} \Glap(\xx,\yy) \mu_{\nu}(\yy) \, ds 
++ \nabla^{\perp} 
+\int_{\Gamma} \big( 2 \partial_{\nu\tau} \Gbh(\xx,\yy) \mu_{\nu}(\yy) 
++ \\
+& \hspace*{35ex}(\partial_{\tau\tau} -\partial_{\nu\nu})\Gbh(\xx,\yy) \mu_{\tau}(\yy) 
+\big) \, ds \, .
 \end{align}
-have a non-trivial solution. In the case that $k=i\alpha$ for
-some real-valued $\alpha$, the equations \cref{eq:helmstokes,eq:helmstokescty}
-are known as the modified Stokes equations and are of particular
-interest for their application to numerical simulations of unsteady
-flow
-\cite{pozrikidis1992boundary,biros2002embedded,jiang2013second}.
-In the absence of a preferred name for the case of real-valued $k$,
-we will refer to \cref{eq:helmstokes,eq:helmstokescty} as the
-oscillatory Stokes equations.
 
-\subsubsection{Stokeslets and stresslets}
-
-In this section, we review the derivation of the
-modified Stokeslet, but for the imaginary parameter
-regime, which is the appropriate setting for the Stokes
-eigenvalue problem.
-The original modified Stokeslet is more well known,
-and is of particular interest for its application to
-numerical simulations of the unsteady Stokes equations
-\cite{pozrikidis1992boundary,biros2002embedded}.
-
- Consider the solution of
-\cref{eq:helmstokes,eq:helmstokescty} where a $\delta$-mass
-centered at $\yy$ with strength $\ff$
-has been added to the right-hand side of \cref{eq:helmstokes}, i.e.
-
-\begin{align}
-  \nabla p - \Delta \uu - k^2 \uu &= \delta_\yy \ff \; ,
-  \label{eq:helmstokes_charge} \\
-  \nabla \cdot \uu &= 0 \; .
-\end{align}
-Recall that
-
+From the expressions above, it is clear that the stream function 
+$\psi_{S}[\bmu]$ associated with the single layer potential is given
+by
 \begin{equation}
- \Delta \Glap(\xx,\yy) = \delta_\yy(\xx) \; .
-\end{equation}
-If we substitute this expression into
-\eqref{eq:helmstokes_charge} and take the divergence,
-we obtain
-
-\begin{equation}
-  p = \nabla \Glap(\xx,\yy) \cdot \ff \; .
-\end{equation}
-We then have, formally,
-
-\begin{align}
-  \uu &= - (\Delta + k^2)^{-1} ( \Delta \Glap \ff
-  - \nabla (\nabla \Glap \cdot \ff ) ) \\
-  &= \left ( -\Delta + \nabla \otimes \nabla \right )
-  \Gbh \ff \; .
-\end{align}
-The tensor
-
-\begin{equation} \label{eq:stokeslet}
-  \GG = - \II \Delta \Gbh + \nabla \otimes \nabla \Gbh
-\end{equation}
-is then the equivalent of a Stokeslet
-\cite{pozrikidis1992boundary} for the problem
-\eqref{eq:helmstokes}.
-
-A related object is the stresslet, which is defined
-in terms of the stress tensor of a velocity, pressure
-pair induced by a Stokeslet. For these tensors, we find
-that it is more convenient to express them in index notation
-with the Einstein index summing convention.
-Recall that the stress tensor $\bsigma$ is defined as
-
-\begin{equation}
-  \sigma_{ij} = -p \delta_{ij} + \left ( \partial_{x_j}u_i
-  +\partial_{x_i} u_j \right ) \; ,
-\end{equation}
-where $\delta_{ij}$ is the standard Kronecker delta notation.
-The stresslet $\TT$ is defined to be
-
-\begin{align}
-  T_{ijk} &= - \partial_{x_j} \Glap \delta_{ik}
-  + \partial_{x_k} \left ( -\Delta \Gbh \delta_{ij} +
-  \partial_{x_i} \left(\partial_{x_j} \Gbh \right) \right)
-  \nonumber \\
-  & \qquad+ \partial_{x_i} \left ( -\Delta \Gbh \delta_{kj} +
-  \partial_{x_k} \left(\partial_{x_j} \Gbh \right) \right)
-  \; .
-\end{align}
-Let $u_i = G_{ij} f_j$ and $p = \partial_{x_i} \Glap f_i$ be a
-solution of the Stokes equations induced by a Stokeslet.
-Then the corresponding stress tensor is given by
-$\sigma_{ik} = T_{ijk} f_j$.
-
-For the layer potentials of the next section, the following
-formulas are useful. Let $\bnu$ be a given vector. When
-summing over the third index, we obtain
-
-\begin{equation}
-  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla \Glap
-  + \partial_\nu \left ( -\Delta \Gbh \II
-  + \nabla \otimes \nabla \Gbh \right)
-  + \nabla \otimes \left ( -\Delta \Gbh \bnu
-  + \partial_{\nu} \nabla \Gbh \right) \; .
-\end{equation}
-%\begin{align}
-% -\Delta \Gbh \bnu
-% + \partial_{\nu} \nabla \Gbh &=
-% ( (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_1 \Gbh +
-% (\partial_{x_1x_1}\nu_1 + \partial_{x_2x_1} \nu_2 )\Gbh,
-% (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_2 \Gbh +
-% (\partial_{x_1x_2}\nu_1 + \partial_{x_2x_2} \nu_2 )\Gbh) \\
-% &= (-\partial_{x_2} \partial_\tau \Gbh,
-% \partial_{x_1} \partial_\tau \Gbh)
-%\end{align}
-%\begin{equation}
-%  \begin{pmatrix}
-%    -\partial_{x_2x_2} & \partial_{x_1x_2} \\
-%    \partial_{x_1x_2} & -\partial_{x_1x_1}
-%  \end{pmatrix} = -\nabla^\bot \otimes \nabla^\bot
-%\end{equation}
-Let $\btau = \bnu^\bot$. Then
-
-\begin{equation}
-  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla \Glap
-  - \nabla^\bot \otimes \nabla^\bot \partial_\nu \Gbh
-  +\nabla \otimes \nabla^\bot \partial_\tau \Gbh \; .
+\psi_{S}[\bmu] = 
+\int_{\Gamma} (\partial_{\tau} \Gbh(\xx,\yy) \mu_{\tau}(\yy) -
+\partial_{\nu} \Gbh(\xx,\yy) \mu_{\nu}(\yy)) \, ds \, . 
 \end{equation}
 
-\subsubsection{Layer potentials and integral representation}
+The situation with the double layer potential is a little trickier. 
+We write the double layer potential as $\bD_{k}[\bmu] = \nabla \phi_{D}[\bmu]
++ \nabla^{\perp} \xi_{D}[\bmu]$, 
+where 
+\begin{align}
+\label{eq:phiddef}
+\phi_{D}[\bmu] &= 
+-\int_{\Gamma} \Glap(\xx,\yy) \mu_{\nu}(\yy) \, ds  \, , \\
+\xi_{D}[\bmu] &= 
+\int_{\Gamma} \big( 2 \partial_{\nu\tau} \Gbh(\xx,\yy) \mu_{\nu}(\yy) 
++ (\partial_{\tau\tau} -\partial_{\nu\nu})\Gbh(\xx,\yy) \mu_{\tau}(\yy) ) \,
+ds \, . 
+\end{align}
 
-We now use the Stokeslet and stresslet definitions
-of the previous section to define the standard single
-and double layer potentials of the Stokes eigenvalue
-problem. The single layer potential is defined to
-be
+If we can find a function $\tilde{\psi}_{D}[\bmu]$ such
+that 
+\begin{equation}
+\label{eq:perptogradperp}
+\nabla^{\perp} \tilde{\psi}_{D}[\bmu] = \nabla \phi_{D} [\bmu] \, ,
+\end{equation}
+then the stream function $\psi_{D}[\bmu]$ 
+associated with the double layer potential would
+be given by $\psi_{D}[\bmu] = \tilde{\psi}_{D}[\bmu] + \xi_{D}[\bmu]$.
+However, on multiply connected domains, it is not necessarily true, 
+that given a function $\phi_{D}[\bmu]$ of the form~\cref{eq:phiddef} 
+there exists a single valued function $\tilde{\psi}_{D}[\bmu]$ 
+which satisfies the condition~\cref{eq:perptogradperp} for
+every $\bmu$.
+Turns out, in the case where $\bmu$ satisfies the conditions
+\begin{equation}
+\label{eq:inteqconst}
+\int_{\Gamma_{i}} \mu_{\nu} \, ds = 0 \, ,\quad i=0,1,2\ldots m \, ,
+\end{equation}
+then there exists a single valued function $\tilde{\psi}_{D}[\bmu]$
+which satisfies~\cref{eq:perptogradperp} (see~\cite{rachh2015integral}, 
+for example).
+In the following lemma, we show that every null-vector of 
+$\cI - 2\cD_{k} -2i \eta \cS_{k} - 2\cW$ satisfies the above integral
+constraints.
 
-\begin{equation}
-  \SS \bmu (\xx) = \int_\Gamma \GG (\xx,\yy) \bmu(\yy)
-  \, dS(\yy) \; .
-\end{equation}
-The double layer potential is defined to be
-
-\begin{equation} \label{eq:doublelayer}
-  \DD \bmu (\xx) = \int_\Gamma \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy)
-  \right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
-\end{equation}
-where $\bnu$ denotes the outward unit normal to the boundary.
-If we write $\bmu = \bnu \mu_\nu + \btau \mu_\tau$,
-where $\btau = \bmu^\bot$ is the positively oriented unit
-tangent to the curve, then we have
-
-\begin{align} \label{eq:stokesdlkernel}
-  \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy) \right )^\intercal
-  \bmu(\yy) &= \left ( - \nabla \Glap(\xx,\yy) + 2 \nabla^\bot
-  \partial_{\nu\tau} \Gbh(\xx,\yy) \right ) \mu_\nu(\yy) \nonumber \\
-  & \qquad+
-  \nabla^\bot \left (\partial_{\tau\tau}-\partial_{\nu\nu} \right )
-  \Gbh(\xx,\yy) \mu_\tau(\yy) \; .
-\end{align}
+\begin{lem}
+Suppose $\bmu$ is a null-vector of 
+$\cI - 2\cD_{k} - 2i \eta \cS_{k} -2\cW$, then
+$\bmu$ satisfies~\cref{eq:inteqconst}.
+\end{lem}
+\begin{proof}
+Insert proof here
+\end{proof}

### 2019-05-07 doc/draft-01/08append.tex
Updating buckling eigenvalues paper

--- 2018-08-22 doc/draft-01/08append.tex
@@
 
-\section{Proof of the invertibility of the Farkas representation}
-In this appendix, we prove~\cref{lem:farkinv} which is restated here
-as~\cref{lem:farkinv_app}.
-
-In the following lemma, we present an integral indentity involving the
-Green's function of the Helmholtz-biharmonic equation.
 \begin{lem}
-Suppose that $\Gbh$ is the Green's function of the Helmholtz-biharmonic equation 
-with Helmholtz parameter $k$. Suppose that $v:\R^{2} \to \R$ is a compactly supported smooth
-function. Then
+Suppose that $\Omega$ is a multiply connected domain with outer boundary
+$\Gamma_{0}$ and $n-$ obstacle boundaries $\Gamma_{j}$, $j=1,2,\ldots n$. 
+Suppose that $k$ is a Stokes eigenvalue for the region $\Omega$ and 
+let $\bu$ be the corresponding eigenfunction. 
+Then, the stream function associated with the velocity $\bu$ defined by
+$w = \left(\nabla^{\perp} \right)^{-1} \bu$ exists and is single valued. 
+Furthermore, $k$ is also a buckling eigenvalue if and only if
 \begin{equation}
-\int_{\R^{2}} \Gbh(\xx,\yy) \Delta (\Delta + k^2) v(\yy) d\yy = v(\xx)
-\end{equation}
-\end{lem}
-\begin{proof}
-Suppose that $r>0$. 
-Let $B_{r}(\xx)$ denote the ball of radius $r$ centered at the origin
-and let $\partial B_{r}(\xx)$ denote its boundary.
-Then applying Green's second identity twice, we get 
-\begin{align}
-\int_{\R^{2} \setminus B_{r}(\xx)} \Gbh(\xx,\yy) \Delta (\Delta +k^{2}) v(\yy)
-&=
-\int_{\R^{2} \setminus B_{r}(\xx)} \Delta \Gbh (\xx,\yy) (\Delta + k^2) 
-v(\yy) + \\
-& \hspace{5ex}\int_{\partial B_{r}(\xx)} \Gbh(\xx,\yy) (\Delta + k^{2})
-\frac{\partial}{\partial n}v(\yy) \, dS - \\
-& \hspace{5ex}\int_{\partial B_{r}(\xx)} \frac{\partial }{\partial n} \Gbh(\xx,\yy) 
-(\Delta + k^2) v \, dS \\
-&= \int_{\R^{2} \setminus B_{r}(\xx)} \Delta (\Delta + k^2)G(\xx,\yy) v(\yy)
-d\yy  - \nonumber \\
-& \hspace{5ex}\int_{\partial B_{r}(\xx)} (\Delta + k^2) 
-\frac{\partial }{\partial n} \Gbh(\xx,\yy) v \, dS + \nonumber\\
-& \hspace{5ex}\int_{\partial B_{r}(\xx)} (\Delta + k^2) 
-\Gbh(\xx,\yy) \frac{\partial}{\partial n}v \, dS - \nonumber \\
-& \hspace{5ex}\int_{\partial B_{r}(\xx)}  
-\frac{\partial }{\partial n} \Gbh(\xx,\yy) \Delta v\, dS + \\
-& \hspace{5ex}
-\int_{\partial B_{r}(\xx)} \Gbh(\xx,\yy) \Delta \frac{\partial v}{\partial n}
-\, dS \nonumber
-\end{align}
-For all $\yy \in \partial B_{r}(x)$, there exists a constant $C$ such that
-$\Gbh$ satisfies the following equations
-\begin{align}
-(\Delta + k^2) \frac{\partial }{\partial n} G(\xx,\yy) &= 
--\frac{1}{2\pi r} \label{eq:estapp1}\\
-\left|(\Delta + k^2) G(\xx,\yy) \right| &\leq C \log{(r)} \label{eq:estapp2}\\
-\left|\frac{\partial }{\partial n} G(\xx,\yy) \right| &\leq C r\log{(r)} 
-\label{eq:estapp3}\\
-\left| G(\xx,\yy) \right| &\leq C r^{2} \log{(r)} \label{eq:estapp4}\, .
-\end{align}
-Furthermore, $\Gbh$ satisfies $\Delta (\Delta + k^2) \Gbh(\xx,\yy) = 0$
-for all $\yy \in \R^{2} \setminus B_{r}(\xx)$.
-Using the estimates in~\cref{eq:estapp1,eq:estapp2,eq:estapp3,eq:estapp4}, 
-and the smoothness of $v$, we get
-\begin{equation}
-\int_{\R^{2} \setminus B_{r}(\xx)} \Gbh(\xx,\yy) \Delta (\Delta + k^2) v(\yy) 
-d \yy = \frac{1}{2\pi r} \int_{\partial B_{r}(\xx)} v(\yy) dS + 
-O(r \log(r)) \, \label{eq:estapp5}.
-\end{equation}
-The result then follows by taking the limit $r\to 0$ in~\cref{eq:estapp5}. 
-\end{proof}
-\label{sec:farkproof}
-
-\section{Existence and uniqueness results for the Helmholtz-Stokes PDE}
-
-In this section, we develop some existence and uniqueness
-results for the Helmholtz-Stokes PDE.
-%
-The structure of this section follows that used
-by Colton and Kress \cite[Ch. 3]{colton1983integral}
-for the scalar Helmholtz equation.
-%
-Let $\Omega$ be a bounded simply connected
-domain and $E = \R^{2} \setminus \bar{\Omega}$ denote its
-exterior.
-%
-Let $\Gamma = \partial E$ denote the boundary of $E$ and
-$\bnu(\yy)$ denote the exterior normal to the point $\yy$ on
-$\Gamma$, i.e. the normal vector pointing out of $E$ into $\Omega$.
-%
-For a given function $\bh$ defined on $\Gamma$,
-the exterior Dirichlet boundary value problem is to
-find a pair $(\bu,p)$ which satisfies:
-\begin{align}
-\Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\label{eq:helmstokes_ext}\\
-\nabla \cdot \bu &= 0 \quad \bx \in E \, , \\
-\bu &= \bh \quad \bx \in \Gamma \, .
-\end{align}
-In addition to the boundary condition on
-$\Gamma$, we must impose radiation conditions
-at $\infty$, analogous to the Helmholtz equation.
-%
-
-Let $\bsigma$ denote the stress tensor associated with the velocity
-field $\bu$, i.e.
-\begin{equation}
-\bsigma = -p \II + 2 \be(\bu) \, ,
-\end{equation}
-where $\be(\bu)$ is the strain tensor given by
-\begin{equation}
-e_{ij}(\bu) = \frac{1}{2} \left( \partial_{x_j} u_i + \partial_{x_i} u_j \right) \; .
-\end{equation}
-%
-The normal component of the stress,
-\begin{equation}
-\ff = \bsigma \cdot \bnu \; ,
-\end{equation}
-gives the surface traction, which is the analogue of
-the normal derivative for the scalar Helmholtz equation,
-i.e. specifying the surface traction on a boundary is
-the Neumann problem for the Helmholtz-Stokes PDE.
-
-%
-Let $B_r(0)$ denote the disc of radius $r$ centered
-at the origin and $\partial B_r(0)$ its boundary.
-%
-We propose the following radiation condition.
-
-\begin{definition} \label{def:radcond}
-Let $(\bu,p)$ satisfy the Helmholtz-Stokes equations in
-the exterior of a bounded domain. We say that
-the pair $(\bu,p)$ is {\em radiating} if
-$p$ is bounded, $p \to 0$ as $r = |\xx| \to \infty$, and 
-\begin{equation}
-\lim_{r\to \infty} \sqrt{r} \left| \ff - i k \bu \right| \to 0 \, ,
-\label{eq:radcond}
-\end{equation}
-uniformly in direction where $\ff = \bsigma \cdot \bnu$
-with $\bnu = \xx/|\xx|$, i.e. $\ff$ is the surface
-traction on $\partial B_r(0)$.     
-\end{definition}
-
-\begin{proposition}
-The Helmholtz-Stokeslet, as in \eqref{eq:stokeslet}, satisfies
-the radiation condition in Definition \ref{def:radcond}.
-Assuming that a density $\bmu$ is integrable and satisfies
-$\int_\Gamma \bmu\cdot \bnu dS = 0$, where $\bnu$ denotes the
-outward normal to the curve $\Gamma$, the Helmholtz-Stokes
-double layer potential $\DD\bmu$, as in \eqref{eq:doublelayer},
-also satisfies the radiation condition.
-\end{proposition}
-
-\begin{proof}
-Consider the Stokeslet induced by an arbitrary charge
-$k^2 \bpsi$ at the origin. Let $r = |\xx|$,
-$\bnu(\xx) = \xx/|\xx|$, and $\btau(\xx) = \bnu(\xx)^\perp$. We have
-
-\begin{align}
-\bu (\xx) &= k^2 \GG(\xx,0) \bpsi \\
-&= k^2 \left (-\II \Delta \Gbh(\xx,0)
-+ \nabla \otimes \nabla \Gbh(\xx,0)\right ) \bpsi \\
-&= -k^2 \left (\nabla^\perp \otimes \nabla^\perp \Gbh(\xx,0) \right) \bpsi \\
-&= \left(\nabla^\perp \otimes \nabla^\perp \left ( \frac{1}{2\pi}
-\log r + \frac{i}{4} H_0^{(1)} (kr) \right ) \right)\bpsi \; .
-\end{align}
-Note that derivatives of $\log r$ are $\littleo (1/\sqrt{r})$
-and that the pressure associated with the Stokeslet is
-$p = \nabla \Glap(\xx) \cdot \bpsi$. We then have
-
-\begin{align}
-\left | \sigma \cdot \bnu(\xx) - i k \bu \right | &=
-\left | p \bnu(\xx) + \partial_{{\nu_x}} \bu + \nabla (\bu \cdot \bnu(\xx))
-- ik \bu \right | \\
-&\leq \left | \partial_{{\nu_x}} \bu - ik\bu \right | + \left | \nabla(\bu \cdot \bnu(\xx)) \right |
-+ \littleo (1/\sqrt{r}) \\
-&\leq \frac{1}{4} \left | \partial_{{\nu_x}} \left(\nabla^\perp \otimes
-\nabla^\perp \left (H_0^{(1)} (kr) \right ) \right)\bpsi
-- i k \left(\nabla^\perp \otimes \nabla^\perp
-\left (H_0^{(1)} (kr) \right ) \right)\bpsi \right | \\
-& \quad + \left | \nabla \left( \partial_{\tau_x} \left ( 
-\nabla^\perp \left (H_0^{(1)} (kr) \right ) \cdot \bpsi  \right )
-\right) \right | + \littleo (1/\sqrt{r}) \; .
-\end{align}
-Because $H_0^{(1)}(kr)$ has the asymptotic expansion
-
-\begin{equation}
-H_0^{(1)}(kr) = \sqrt{\frac{2}{\pi k r}} e^{i(rk-\pi/4)} \left ( 1 + O\left (
-\frac{1}{r} \right ) \right ) \;
-\end{equation}
-as $r\to \infty$, we have
-
-\begin{equation}
-\left | \partial_{{\nu_x}} \left(\nabla^\perp \otimes
-\nabla^\perp \left (H_0^{(1)} (kr) \right ) \right)\bpsi
-- ik \left(\nabla^\perp \otimes \nabla^\perp
-\left (H_0^{(1)} (kr) \right ) \right)\bpsi \right | =
-o ( 1/\sqrt{r} ) \; .
-\end{equation}
-Finally, because $H_0^{(1)}(kr)$ is radially symmetric,
-we have
-
-\begin{equation}
-\left | \nabla \left( \partial_{\tau_x} \left ( 
-\nabla^\perp \left (H_0^{(1)} (kr) \right ) \cdot \bpsi  \right )
-\right) \right | = 0 \; ,
-\end{equation}
-so that the Stokeslet satisfies the radiation condition.
-
-For the double layer potential, we only establish the
-decay of the pressure $p$; the rest of the terms
-in \eqref{eq:radcond} can be bounded using an argument
-like that for the Stokeslet above.
-Because $p$ is harmonic in the exterior of any disc
-containing $\Gamma$, it is sufficient to show that
-$|\nabla p| = \bigo (1/r^2)$. Let $\btau$ denote the
-positively oriented tangent to the curve $\Gamma$ and
-$\mu_\nu(\yy)$ and $\mu_\tau(\yy)$ denote $\bmu(\yy) \cdot \bnu(\yy)$ and
-$\bmu(\yy) \cdot \btau(\yy)$, respectively. Substituting
-$\DD \bmu$ into \eqref{eq:helmstokes_ext}, we obtain
-
-\begin{align}
-\nabla p^\DD(\xx) &= (\Delta + k^2) \DD \bmu(\xx) \\
-&= \int_\Gamma \left (-k^2 \nabla \Glap (\xx,\yy) +
-2 \nabla^\perp \partial_{\nu\tau} \Glap (\xx,\yy) \right ) \mu_\nu(\yy)
-\, dS(\yy) \\
-& \qquad + \int_\Gamma \nabla^\perp (\partial_{\tau\tau}-\partial_{\nu\nu})\Glap \mu_\tau(\yy)
-\, dS(\yy) \; .
-\end{align}
-The other terms are higher-order derivatives
-of $\Glap$, so it is sufficient to show that the term
-
-\begin{align}
-|\nabla p_1(\xx)| &:= \left |-k^2 \nabla \int_\Gamma \Glap(\xx,\yy)
-\mu_\nu(\yy) \, dS(\yy) \right |
-\end{align}
-is $\bigo (1/r^2)$. In the following, let $z = x_1 + i x_2$ be the
-point corresponding to $\xx$ in the complex plane and let $R$
-be the radius of some disc containing $\Gamma$. If $|\xx| > 2R$,
-we can use a standard multipole expansion of $\log(z-(y_1+iy_2))$
-and the assumption that $\int_\Gamma \bmu \cdot \bnu = 0$
-to obtain
-\begin{align}
-|\nabla p_1(\xx)| &= \frac{k^2}{2\pi} \left |  \partial_z \int_\Gamma \log(z-(y_1+iy_2))
-\mu_\nu(\yy) dS(\yy) \right | \\
-&= \frac{k^2}{2\pi} \left |  \partial_z  \left ( \log(z) \int_\Gamma \mu_\nu(\yy) \, dS(\yy)
-+ \sum_{l=1}^\infty \frac{1}{z^l} \int_\Gamma \left( y_1+iy_2 \right)^l \mu_\nu(\yy) \, dS(\yy)
-\right ) \right | \\
-&= \frac{k^2}{2\pi} \left | \sum_{l=1}^\infty \frac{-l}{z^{l+1}}
-\int_\Gamma \left( y_1+iy_2 \right)^l \mu_\nu(\yy) \, dS(\yy) \right | \\
-&= \bigo (1/r^2) \; .
-\end{align}
-\end{proof}
-
-\subsection{Uniqueness results}
-
-\begin{lem}
-\label{lem:rep}
-Suppose that $(\bu,p)$ satisfies the Helmholtz-Stokes equation in 
-an unbounded region $E$ along with the radiation 
-condition~\cref{eq:radcond}. 
-Then 
-\begin{equation}
-\label{eq:repinfest}
-\lim_{r\to\infty}
-\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) dS +
-2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
-dV = 2 \Im \left( k \int_{\Gamma} \bu \cdot \overline{\ff} dS  \right)
+\int_{\Gamma_{j}} w\, ds = 0 \quad \forall j=1,2,\ldots n \, .
 \end{equation}
@@
 \begin{proof}
-Since $(\bu,p)$ satisfies the radiation condition, we have that
+Since $\bu$ is a Stokes eigenfunction, it satisfies
 \begin{equation}
-\lim_{r\to\infty} \int_{|\by|=r} | \ff - i k \bu|^2 dS = 
-\lim_{r\to\infty} \int_{|\by| =r} \left( |\ff|^2 + |k|^2|\bu|^2 + 2 \Im 
-\left( k \bu\cdot \overline{\ff} \right) dS \label{eq:raddecayproof1}
-\right) = 0 \, . 
+\int_{\Gamma_{j}} \bu \cdot \bn ds = 0 \quad j=0,1\ldots m \, .
 \end{equation}
-Since $\bu$ satisfies the Helmholtz-Stokes equation $E \cap B_{r}(0)$,
-using a couple of applications of the divergence theorem, we have that
+Thus, there exists a single valued stream function associated with the
+velocity field $\bu$ such that 
 \begin{equation}
-\int_{E\cap B_{r}(0)} |2 \be(\bu)|^2 dV =
-\int_{\Gamma} \bu \cdot \overline{\ff} dS
-+ \int_{|\by|=r} \bu \cdot \overline{\ff} dS + \overline{k}^2 
-\int_{E \cap B_{r}(0)} |\bu|^2 dV \,. \label{eq:raddecayproof2}
+\nabla^{\perp} w = \bu \, .
 \end{equation}
-Combining~\cref{eq:raddecayproof1,eq:raddecayproof2}, we get
+Furthermore, since $\bu$ satisfies the oscillatory Stokes equations, 
+$w$ satisfies
+\begin{align}
+\Delta (\Delta + k^{2} ) w &= 0 \, , \quad \bx \in \Omega \\
+\nabla^{\perp} w = \bu &=0 \, ,\quad \bx \in \Gamma \, .
+\end{align}
+In particular $w= c_{j}$ for $\bx \in \Gamma_{j}$ for
+some constant $c_{j}$, $j=0,1,2\ldots m$.
+Thus $k$ is also a buckling eigenvalue if and only if 
 \begin{equation}
-\lim_{r\to\infty} \int_{|\by|=r}\left(|\ff|^2 + |k|^2 |\bu|^2 \right) dS 
-+ 2 \Im(k)\int_{E \cap B_{r}(0)} \left(|2\be(\bu)|^2 + |k|^2 |\bu|^2 
-\right) dV = 2\Im \left ( k \int_{\Gamma} \bu \cdot \overline{\ff} dS \right) \, .
+c_{j} = \frac{1}{|\Gamma_{j}|}\int_{\Gamma_{j}} w ds =  0 \, .
 \end{equation}
 \end{proof}
-
-In the next lemma, we prove the analogue of Rellich's lemma for the
-Helmholtz-Stokes equation. 
-\begin{lem}
-\label{lem:rellich}
-Suppose that $\bu$ satisfies the Helmholtz-Stokes equation in an unbounded
-region $E$.  
-Suppose further that 
-\begin{equation}
-\lim_{r \to \infty} \int_{|\by|=r} |\bu|^2 dS = 0 
-\, . \label{eq:decayatinf}
-\end{equation}
-Then each component of $\bu$ is harmonic and has a convergent Laurent
-expansion in $E$.
-\end{lem}
-\begin{proof}
-We first note that each component of $\bu= (u_{1},u_{2})$ satisfies the 
-Helmholtz-Biharmonic equation in $E$, i.e.
-\begin{equation}
-\Delta (\Delta + k^2) u_{j} = 0 \quad j=1,2 \,. 
-\end{equation}
-For $r$ sufficiently large, we can express $u_{j}$ in the Fourier basis as
-\begin{equation}
-u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} a_{j,n}(r) e^{i n \theta}  \quad 
-j=1,2 \, .
-\end{equation}
-Using Parseval's identity then
-\begin{equation}
-\int_{|\by|=r} |\bu|^2 dS = r\sum_{n=-\infty}^{\infty} |a_{1,n}(r)|^2  +
-|a_{2,n}(r)|^2 \, .
-\end{equation}
-Since $\bu$ satisfies~\cref{eq:decayatinf}, we conclude that
-\begin{equation}
-\lim_{r\to\infty} r|a_{j,n}(r)|^2 = 0 \quad j=1,2 \, , \label{eq:adecay}
-\end{equation}
-Since $u_{j}$, $j=1,2$ satisfies the Helmholtz-biharmonic equation,
-the functions $a_{j,n}$ are linear combinations of 
-\begin{equation}
-r^{|n|}, r^{-|n|}, H^{1}_{n}(k r), H^{2}_{n}(k r) \, , \quad
-n\neq 0 \, ,
-\end{equation}
-and
-\begin{equation}
-1, \log{(r)}, H^{1}_{0}(k r), H^{2}_{0}(k r) \quad n=0 \, , 
-\end{equation} 
-where $H_{n}^{1,2}(\cdot)$ are the Hankel functions of the first and
-second kind of order $n$.
-Since $a_{j,n}(r)$ satisfy~\cref{eq:adecay}, and using the asymptotic 
-expansion of $H_{n}^{1,2}(r)$, we note that the projection of 
-$a_{j,n}$ on $r^{|n|}$, and $H_{n}^{j}(k r)$ must be zero. 
-Thus, 
-\begin{equation}
-u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} \frac{a_{j,n} e^{i n \theta}}{r^{|n|}} 
-\, .
-\end{equation}
-\end{proof}
-\begin{remark} \label{rmk:harmu}
-Note that each component of $\bu$ is harmonic and thus $\bu$ then satisfies
-\begin{align}
-k^2 \bu &= \nabla p  \quad \label{eq:massconsred} \\
-\nabla \cdot \bu &= 0 \, .
-\end{align}
-Taking the inner product with $\nabla^{\perp}$ in~\cref{eq:massconsred}, 
-we note that $\bu$ satisfies both $\nabla^{\perp} \cdot \bu = 0$ 
-and $\nabla \cdot \bu = 0$.
-\end{remark}
-\begin{remark}
-Note that in Rellich's lemma $\bu$ need not be a radiating solution. 
-All we know of $\bu$ is that it satifies the PDE in $E$.
-\end{remark}
-
-\begin{thrm}[Uniqueness of the Dirichlet Problem]
-Suppose that $\Im(k)\geq 0$ and 
-that $(\bu,p)$ is a radiating solution to the Helmholtz-Stokes
-equation in $E$ with $\bu =0$ on the boundary $\Gamma$, then
-$\bu \equiv 0$ in $E$.
-\end{thrm}
-
-\begin{proof}
-Since $\bu = 0$ on $\Gamma$, it follows from~\cref{eq:repinfest} that
-\begin{equation}
-\lim_{r\to\infty}
-\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) dS +
-2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |\be(\bu)|^2 \right)
-dV = 0
-\end{equation} 
-In particular, this implies that
-\begin{equation}
-\lim_{r\to\infty} \int_{|\by|=r} |\bu|^2 dS = 0 \, .
-\end{equation}
-Thus, the conditions for $\bu$ in Rellich's lemma (~\cref{lem:rellich})
-are satisfied, and each component of $\bu$ is a harmonic function
-with $\bu \to 0$ as $r \to \infty$. Furthermore, since $\bu=0$ on
-$\Gamma$, from uniqueness of solutions to the
-Dirichlet problem for Laplace's equation
-on exterior domains, we conclude that $\bu \equiv 0$ in $E$.
-\end{proof}
-
-\begin{thrm}[Uniqueness of the Neumann Problem]
-Suppose that $\Im(k)\geq 0$ and 
-that $(\bu,p)$ is a radiating solution to the Helmholtz-Stokes
-equation in $E$ with $\ff = 0$ on the boundary $\Gamma$, then
-$\bu \equiv 0$ in $E$.
-\end{thrm}
-
-\begin{proof}
-Since $\ff = 0$ on $\Gamma$, it follows
-from~\cref{eq:repinfest} that
-\begin{equation}
-\lim_{r\to\infty}
-\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) dS +
-2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |\be(\bu)|^2 \right)
-dV = 0
-\end{equation} 
-In particular, this implies that
-\begin{equation}
-\lim_{r\to\infty} \int_{|\by|=r} |\bu|^2 dS = 0 \, .
-\end{equation}
-Thus, the conditions for $\bu$ in Rellich's lemma (~\cref{lem:rellich})
-are satisfied, and each component of $\bu$ is a harmonic function
-with $\bu \to 0$ as $r \to \infty$. Furthermore, as observed
-in \cref{rmk:harmu}, $k^2 \bu = \nabla p$. Then, the boundary
-condition becomes $0 = \ff = -p \bnu + 2 \nabla \partial_\nu p/k^2$.
-Because $0 = \btau \cdot \ff = 2\partial_{\tau\nu} p/k^2$,
-$\partial_\nu p $ is a constant on $\Gamma$. Using the
-fact that $(\bu,p)$ is radiating and the fact that $p$ is harmonic,
-the divergence theorem implies that $\partial_\nu p=0$ on $\Gamma$.
-Thus, $\ff = -p\bnu$ so that $p = 0$ on $\Gamma$. By the uniqueness
-of solutions to the Dirichlet problem for Laplace's equation,
-we have that $p=0$ so that $\uu \equiv 0$.
-
-\end{proof}
-
-\begin{thrm}[Uniqueness of the Impedance Problem]
-Suppose that $\Im(k) \geq 0$ and that
-$(\bu,p)$ is a radiating solution of the
-Helmholtz-Stokes equation in $E$ which satisfies
-the homogeneous impednace boundary condition
-\begin{equation}
-\ff - i k \bu = 0 \quad \xx \in \Gamma \, .
-\end{equation}
-Then $\bu \equiv 0$ for $\xx \in E$.
-\end{thrm}
-
-\begin{proof}
-Since $\bu$ satisfies the radiation condition at $\infty$ and $\ff = ik \bu$
-on $\Gamma$, it follows from~\cref{eq:repinfest} that
-\begin{align}
-0 &=
-\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) dS +
-2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
-dV \nonumber \\
-& \qquad - 2 \text{Im} \left( k \int_{\Gamma} \bu \cdot \overline{\ff} dS  \right) \\
-&= 
-\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) dS +
-2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
-dV \nonumber \\
-& \qquad + 2 \left( |k|^{2} \int_{\Gamma} |\bu|^{2} dS  \right)
-\, .
-\end{align}
-Because all of the quantities in the last expression above are
-nonnegative, we have that
-\begin{equation}
-\int_{\Gamma} |\bu|^{2} = 0 \implies \bu = 0  \quad \xx \in \Gamma \, 
-\end{equation}
-and the estimate
-\begin{equation}
-\lim_{r\to\infty} \int_{|\yy|=r} |\bu|^{2} dS \to 0 \, .
-\end{equation}
-The last equation implies the conditions for~\cref{lem:rellich}
-are satisfied, from which we conclude that the components
-of $\bu$ are harmonic in $E$. 
-Thus, the components of $\bu$ satisfy
-\begin{equation}
-\Delta u_{j}=  0 \quad \xx \in E \quad \text{and} \quad
-u_{j} = 0 \quad \xx \in \Gamma \, ,
-\end{equation}
-for $j=1,2$.
-Then $\bu \equiv 0$ follows from the uniqueness of solutions to the 
-Dirichlet problem for Laplace's equation.
-\end{proof}
-
-\subsection{Existence results}

### 2019-05-07 doc/draft-01/biharm-evals.tex
update manuscript, reorganize intro
update paper, build out introduction
Updating biharm paper
update appendix
update proofs and notation
updating appendix
fix sign in def of bi-helmholtz green's function
Updating buckling eigenvalues paper

@@
 \usepackage{subcaption}
+\usepackage{amsmath}
+\usepackage{authblk}
+\renewcommand\Affilfont{\itshape\small}
 
@@
 
+\def\bz{{\boldsymbol 0}}
 \def\br{{\boldsymbol r}}
+\def\bv{{\boldsymbol v}}
+\def\bc{{\boldsymbol c}}
 \def\bh{{\boldsymbol h}}
@@
 \def\bu{{\boldsymbol u}}
+\def\be{{\boldsymbol e}}
 \def\bl{{\boldsymbol \ell}}
 \def\ff{{\boldsymbol f}}
+\def\bg{{\boldsymbol g}}
 \def\GG{{\bf G}}
-\def\Gbh{{G_{BH}}}
+\def\Gbh{G^{\textrm{BH}}}
+\def\Glap{G^{\textrm{L}}}
+\def\Ghelm{G^{\textrm{H}}}
+\def\Kfark{K^{\textrm{F}}}
 \def\II{{\bf I}}
 \def\TT{{\bf T}}
-\def\SS{{\bf S}}
-\def\DD{{\bf D}}
+\def\bS{{\bf S}}
+\def\bD{{\bf D}}
+\def\bC{{\bf C}}
+\def\bB{{\bf B}}
+\def\cN{{\mathcal N}}
+\def\cK{{\mathcal K}}
+\def\cB{{\mathcal B}}
+\def\cA{{\mathcal A}}
+\def\cS{{\mathcal S}}
+\def\cSk{{\mathcal S}_k}
+\def\cD{{\mathcal D}}
+\def\cDt{{\mathcal D}^{\intercal}}
+\def\cDk{{\mathcal D}_{k}}
+\def\cDkt{{\mathcal D}_{k}^{\intercal}}
+\def\cW{{\mathcal W}}
+\def\cJ{{\mathcal J}}
+\def\cL{{\mathcal L}}
+\def\cA{{\mathcal A}}
+\def\cM{{\mathcal M}}
+\def\bL{{\mathbb L}}
+\def\bK{{\mathbf K}}
+\def\sint{{\sin{(\theta)}}}
+\def\cost{{\cos{(\theta)}}}
+
+\def\jkr{J_{0}(kr)}
+\def\jpkr{J_{0}'(kr)}
+\def\jpk{J_{0}'(k)}
+\def\jppkr{J_{0}''(kr)}
+\def\jppk{J_{0}''(k)}
+\def\ddr{\frac{d}{dr}}
+
 \def\bsigma{{\boldsymbol \sigma}}
+\def\bpsi{{\boldsymbol \psi}}
 \def\bmu{{\boldsymbol \mu}}
 \def\bnu{{\boldsymbol \nu}}
+\def\brho{{\boldsymbol \rho}}
 \def\btau{{\boldsymbol \tau}}
@@
 \def\littleo{o}
+
+\def\Im{{\textrm{\textup{Im}}}}
+
+\def\epsflam{{\epsilon_{\texttt{FLAM}}}}
+\def\epscheb{{\epsilon_{\texttt{cheb}}}}
+\def\epsclose{{\epsilon_{\textrm{close}}}}
+\def\cheb{{\texttt{cheb}}}
+
 \newcommand\dwdn{\frac{\partial w}{\partial n}}
+\newcommand{\cI}{\mathcal I}
 \newcommand{\cC}{\mathcal C}
+\newcommand{\bbmat}{\begin{bmatrix}}
+\newcommand{\ebmat}{\end{bmatrix}}
+
+\newcommand{\note}[1]{ {\color{red} #1 }}
+
+\def\pv{\textrm{P.V.} }
 
@@
 \newtheorem{lem}{Lemma}
+\newtheorem{cor}{Corollary}
+\newtheorem{thrm}{Theorem}
+\newtheorem{definition}{Definition}
+
+\title{A boundary integral equation approach to
+  computing eigenvalues of the Stokes operator}
+\author{Travis Askham\thanks{
+Department of Mathematical Sciences, New Jersey Institute of
+Technology, USA.\\ 
+email: travis.l.askham@njit.edu} ,\, 
+Manas Rachh\thanks{Center for Computational Mathematics,
+Flatiron Institute, USA. \\
+email: mrachh@flatironinstitute.org}}
 
@@
 
-\title{A Fredholm operator approach to the plate
-buckling problem}
-\author{Askham and Rachh}
+\title{A Fredholm operator approach to eigenvalue problems in elasticity and planar Stokes flow}
+\author{Travis Askham and Manas Rachh}
 \date{\today}
@@
 \input{02prelim}
-\input{03inteq}
-\input{04analyze}
-\input{05results}
-\input{06conclude}
+%\input{03inteq}
+%\input{04analyze}
+%\input{05numerics}
+%\input{06results}
+%\input{07conclude}
 
@@
 
+%\input{08append}
+
 \end{document}

### 2019-12-01 doc/draft-01-stokes/appendix-b.tex
adding appendix for space estimates

\section{Proof of convergence for general case}
Let $T_{n}$ denote the space of trignometric polynomials
$\{ e^{-inx}, \ldots e^{inx} \}$. Let $K_{n}: T_{n} \to T_{n}$ 
denote a discretization of the Helmholtz double layer kernel
using kress quadrature. Let $\phi_{0}$ denote the null vector
of $I+ K$, and let $\psi_{0}$ denote the null vector
of $I+K^{\ast}$. 
Let $P_{n}$ denote the orthogonal 
projection operator from $L^{2} \to T_{n}$.
Let $P_{n,\phi_{0}^{\perp}}: T_{n} \to T_{n}$ denote the orthogonal
projection on to the orthogonal complement of $P_{n} \phi_{0}$.
Let $P_{n,\psi_{0}^{\perp}}: T_{n} \to T_{n}$ denote the
analogous operator for $\psi_{0}$.

The matrix $I+K_{n}$ can be rewritten as a map from the
following two bases for $T_{n}: \{ P_{n} \phi_{0}, \text{basis for }
P_{n}\phi_{0}^{\perp} \}$, and for the range the basis:
$\{ P_{n} \psi_{0}, \text{basis for } P_{n} \psi_{0}^{\perp} \}$.
In these bases, the linear operator $I_{n} + K_{n}$ is given by
\begin{equation}
\begin{bmatrix}
A_{n} & B_{n} \\
C_{n} & D_{n} 
\end{bmatrix} \, .
\end{equation}

The operator $A_{n}$
is the restriction of $I_{n} + K_{n}$ as a map from $P_{n} \phi_{0}$ 
to $P_{n} \psi_{0}$. Thus, it is just a number and it is given by
\begin{equation}
A_{n} = \left(P_{n} \psi_{0}, (I_{n} + K_{n}) P_{n} \phi_{0} \right) \,.
\end{equation}

The operator $D_{n}$ is the restriction of $I_{n} + K_{n}$ 
as a map from $P_{n} \phi_{0}^{\perp}$ 
to $P_{n} \psi_{0}^{\perp}$. 
As $n \to \infty$, $D_{n}$ converges pointwise to the restriction
of $I + K: \phi_{0}^{\perp} \to R(I+K)$. Moreover, the collection
of operators $K_{n}$ are collectively compact, and hence their restrictions
are also collectively compact. 
Since the operator $I+K: \phi_{0}^{\perp} \to R(I+K)$ is an invertible
operator, by standard estimates, for $n$ large enough $D_{n}$ is also 
an invertible operator.

The operator $B_{n}$ is the restriction of $I_{n} + K_{n}$ as a map from 
$P_{n} \phi_{0} ^{\perp} \to P_{n} \psi_{0}$ and is given by
\begin{equation}
B_{n} \phi = \left( P_{n} \psi_{0}, (I_{n} + K_{n}) 
(P_{n} \phi -( P_{n} \phi, P_{n} \phi_{0}) P_{n} \phi_{0}) \right) P_{n} \psi_{0}  \, .
\end{equation}

And finally the operator $C_{n}$ is the restriction of $I_{n} + K_{n}$ as a map from
$P_{n} \phi_{0} \to P_{n} \psi_{0}^{\perp}$ and is its adjoint is given by
\begin{equation}
C_{n}^{\ast}\psi = \left( (I_{n} + K_{n}^{\ast}) \left(P_{n} \psi - (P_{n} \psi, P_{n} \psi_{0}) P_{n} \psi_{0} \right), P_{n} \phi_{0} \right)
\end{equation}

In this setting, $\phi_{0}$ and $\psi_{0}$ are known to be linearly independent.
Thus for large enough $n$, 
$f_{n} = P_{n} \phi_{0} - (P_{n} \phi_{0}, P_{n} \psi_{0}) P_{n} \psi_{0} \neq 0$
and $f_{n} \in P_{n} \psi_{0}^{\perp}$.
Similarly $g_{n} = P_{n} \psi_{0} - (P_{n}\phi_{0}, P_{n} \psi_{0}) P_{n} \phi_{0} \neq 0$
and $g_{n} \in P_{n} \phi_{0}^{\perp}$.

By block linear algebra, the determinant of the matrix above is also given by
\begin{equation}
\det{
\begin{bmatrix}
A_{n} & B_{n} \\
C_{n} & D_{n} 
\end{bmatrix} 
}
= \det{D_{n}} \cdot (A_{n} - C_{n} D_{n}^{-1} B_{n}) \,.
\end{equation}
Note that $C_{n} D_{n}^{-1} B_{n}$ is a number and can be evaluated as 
\begin{equation}
\begin{aligned}
C_{n} D_{n}^{-1} B_{n} &= 
\left( f_{n} \cdot  C_{n} D_{n}^{-1} B_{n} g_{n} \right) \\
&= \left( C_{n}^{\ast} f_{n}, D_{n}^{-1} B_{n} g_{n} \right) \\
&= \left( \left((I_{n} + K_{n}^{\ast})f_{n}, P_{n} \phi_{0}\right) P_{n} \phi_{0}, D_{n}^{-1} B_{n} g_{n} \right) \\
&= \left(f_{n}, (I_{n} + K_{n})P_{n} \phi_{0} \right) \cdot (P_{n} \phi_{0}, D_{n}^{-1} B_{n} g_{n}) \\
&= \left(f_{n}, (I_{n} + K_{n})P_{n} \phi_{0} \right) \cdot (P_{n} \phi_{0}, D_{n}^{-1} P_{n} \psi_{0})  \cdot 
\left((I_{n} + K_{n}^{\ast})P_{n} \psi_{0}, g_{n}  \right) \\
\end{aligned}
\end{equation}

### 2019-12-05 doc/draft-01-stokes/04numerical.tex
updating figure 5 and 6

@@
 \caption{The values of the discretized determinants $f_{C}^{N}(k)$ (left)
-and $f_{D}^{N}(k)$ on the interval $k=[13,14]$ with $N=368$. The vertical
+and $f_{D}^{N}(k)$ on the interval $k=[14,15]$ with $N=368$ (the 
+solid lines are the real parts of the determinant and the dashed lines
+are the imaginary parts of the determinant). The vertical
 dotted line denotes the spurious eigenvalue $k_{0} = 14.79595178235126$ 

### 2019-12-06 doc/review-acom/response-to-referees.tex
add rebuttal docs

\documentclass{article}

\usepackage{amsmath,amsfonts,amssymb}
\usepackage{cleveref}

\usepackage{color}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Crefname{equation}{}{}
\crefname{equation}{}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator{\dn}{dn}
\DeclareMathOperator{\cn}{cn}
\DeclareMathOperator{\sn}{sn}

\newcommand*\C{\mathbb{C}}
\newcommand*\R{\mathbb{R}}
\def\bx{{\mathbf x}}
\def\bX{{\mathbf X}}
\def\bf{{\mathbf f}}
\def\bg{{\mathbf g}}
\def\bc{{\mathbf c}}
\def\by{{\mathbf y}}
\def\bxi{{\boldsymbol \xi}}
\def\bPhi{{\boldsymbol \Phi}}
\def\bSigma{{\boldsymbol \Sigma}}
\def\btheta{{\boldsymbol \theta}}
\def\bTheta{{\boldsymbol \Theta}}
\def\bC{{\mathbf C}}
\def\balpha{{\boldsymbol \alpha}}
\def\bB{{\mathbf B}}
\def\bigo{\mathcal{O}}

\newtheorem{remark}{Remark}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}

\title{Response to referees}
\author{Travis Askham, Manas Rachh}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

In this document, we respond to the referees' comments
for the paper ``A boundary integral equation approach to computing
eigenvalues of the Stokes operator''.
We believe that the referees' suggestions improve the
quality of the paper and that we have been able to
address their concerns. Changes made to address these concerns
are marked in {\color{red} red} in the revised manuscript.

\section{Reviewer 1}

A general concern of the first reviewer was the discussion
of what we originally called ``spurious double roots''.
We appreciate the reviewer pressing us on this issue, as it
has clarified the results of the paper.

To explain what had happened, we computed the roots using a rootfinding
utility in another software package, \texttt{chebfun}. In our
numerical experiments, we were puzzled that the output of the
utility consistently gave us pairs of roots which seemed to
be identical. Yet, they did not actually seem to correspond to
a double root of the Fredholm determinant in any meaningful sense
(indeed, the derivative of our interpolant was not particularly
close to zero for these points). We performed some other tests
(including checking whether there truly was a corresponding
two-dimensional eigenspace) and no other tests suggested a double
root existed. Thus, in the original submission, we made a note
suggesting that rounding errors may explain this strange behavior
and we described our ad hoc methods for determining true roots.
To confuse matters, we mentioned the existence of roots that
were computed and had large imaginary part as being part of
the same phenomenon (they are not).

It turns out that this behavior can be suppressed rather
simply. By default, the \texttt{roots}
utility in \texttt{chebfun} first divides the interval on
which the interpolant is defined into smaller intervals on which
the interpolant can be represented by a shorter Chebyshev series.
The roots on these subintervals can then be computed more efficiently.
However, the roots for neighboring intervals can be found twice
by this procedure and there is some internal processing to eliminate
double roots. This processing seems to fail in our case (perhaps because
we are using the complex roots mode, which is more experimental) and
we observe the fake double roots described above. Fortunately, the
subdivision procedure can be turned off. When this was done, such
roots disappeared (aside from double roots introduced by our
own splitting into subintervals). Once aware of this issue,
a much simpler procedure for identifying the roots which are actually
contained on a real subinterval can be employed.

We describe this simplified root finding procedure in the updated
manuscript. The eigenvalues/eigenvectors in the examples
did not change.

We respond to other comments from Reviewer 1 below. Original
reviewer comments in {\color{blue} blue}

\begin{itemize}
\item[1.] {\color{blue} In different parts of the paper the connection between the eigenvalue
problem of the Stokes operator and the biharmonic eigenvalue problem
1is addressed and utilized. Therefore for me it is strange that just in
the last section of the paper (“Conclusions”) this connection is elabo-
rated. It would be better that this elaboration is done somewhere at
the beginning of the paper and not in the end.}

We appreciate this suggestion and have moved this elaboration to
the introduction.

\item[2.] {\color{blue}
  In the abstract the Stokes operator is denoted as fourth-order operator.
This is unusual and in my opinion not the case (even if there is an
equivalence to a forth-order operator).}

We see how this could be confusing and have adjusted this phrasing.

\item[3.] {\color{blue} I would appreciate it if the following issue would be addressed in the
paper: under which weaker conditions (not analytic boundary, non-
simple eigenvalues) convergence of the discretization of the eigenvalues
can be proven. (Are there results concerning the convergence of the
eigenfunctions?)}

\item[4.] {\color{blue} In the paper it is not explicitly mentioned that both presented bound-
ary integral equations may have non-trivial null-spaces for certain $k$
with ${\rm Im}(k) < 0$. These $k$s correspond to the eigenvalues of some re-
lated eigenvalue problems in the exterior domain. It is possible that
these $k$s are also be detected by the root search method and that these
eigenvalues may be some of those “spurious eigenvalues too far from
real-valued” which are blamed to be caused by “noisy numerical de-
terminant evaluation” but are actually caused by the used boundary
integral formulation.}

Thank you for pointing this out. This is indeed the case, as can be seen
by the dependence of many of the results on ${\rm Im}(k) \geq 0$. We have
added a remark about this after Theorem 10 and updated the theorems and lemmas
as suggested in other comments below. These are indeed detected by the
root finding procedure, though they are easy to identify as
being distinct from the real-valued roots which correspond to
eigenvalues (the imaginary part of the real-valued roots is several
orders of magnitued smaller than the imaginary part of the
spurious roots we observed).

\item[5.] {\color{blue}
  In general it would be of interest which kind of spurious eigenvalues may
occur from a“noisy numerical determinant evaluation”. In the paper
only two kinds are specified, namely spurious eigenvalues with “large”
imaginary part (which may result also from the boundary integral for-
mulation itself as pointed out above) and spurious “double roots” on
the real line. Isn’t it possible that for example spurious single roots
occur on the real line?}

Again, thank you for pressing this point. We believe that this
is mostly resolved by the discussion above. In the case of a spurious
single root on the real line, we imagine that this could happen, though it
was not observed, i.e. one can imagine a pathological domain for which a
true spurious root exists that is within, say, $10^{-7}$ of the real line.
Such a root would be hard to distinguish from a true root.
In all cases, we also computed the smallest singular
value of the BIE corresponding to the real part of a given root.
This singular value was found to be quite small. Because we believe
that the integral equation was well-resolved
by our discretization, this is rather convincing evidence that an
eigenvalue of the PDE has been found.

\item[6.] {\color{blue}
  For me it is not clear why with the suggested procedure spurious ``double roots''
  may be detected. What is actually the argument that this
  procedure detects spurious double roots?}

The original procedure was designed to test whether a root was
an eigenvalue in a manner independent of the interpolant we had
computed for the Fredholm determinant. Thus, we checked the several smallest
singular values to see if any eigenspaces of dimension larger
than one were associated
with the weird double roots. None were found. We thus chose what
seemed to be the better root in an ad hoc way. As noted above, this
procedure is no longer necessary when calling \texttt{roots} with
the subdivision procedure suppressed.

\item[7.] {\color{blue}In the caption of figure 5 the given interval for $k$
  does not match with the plots. Moreover, in each plot of figure
  5 two functions are given but in the caption only one function is described.}

\item[8.] {\color{blue}Subsection 1.1 (”Relation to other work“) may
  lead to the false impression that boundary integral equations of the
  second kind combined with the proposed root finding method is the only
  profound and reasonable boundary integral equation approach for the Stokes
  eigenvalue problem. The authors seem not be aware of works which deal with
  boundary integral equation methods based on integral equations of the
  first kind (for several types of eigenvalue problems(Laplacian, Maxwell,
  fluid-solid interaction, plasmonics, ....)) which are well analyzed and for
  which a rigorous and comprehensive convergence theory is established.
  Such kind of an approach could be also applied to the Stokes eigen-
  value problem. Moreover, in these works instead of the root search for
  the determinant the contour integral method for nonlinear eigenvalue
  problem is used for which multiple and spurious eigenvalues seem not
  to be a problematic issue. In some way these alternatives should be
  briefly mentioned in the paper.}

  This comment is well taken.
  We did not mean to give this impression but had intended this section
  to be focused on methods specifically for the Stokes eigenvalue problem.
  We have added some references to applications treated using integral
  equation methods in the literature. 
  We note that in the original submission this subsection started with
  a paragraph that cited previous, first kind integral equation
  formulations for the buckling problem. There were also references to
  the Laplace eigenvalue problem and alternative root finding methods
  earlier in the introduction.

\item[9.] {\color{blue}
  I cannot follow the ”formal“ derivation of the fundamental solution from
  equation (8) to (10). Is it possible to describe the derivation in more
  detail? (It would be also good to mention the reference [7] between
  equation (8) and (10)).}

  We've added some more steps and added the suggested
  reference in that section.

\item[10.] {\color{blue}
  Lemma 4 only seems to hold for $k$ with ${\rm Im}(k) \geq 0$,
  see the asymptotic expansion of the Hankel function.}

  Thank you for pointing out this ommission. It's been fixed
  in the revision.

\item[11.] {\color{blue} In the proof of Theorem 3 and 4 only the
  uniqueness of the solution is shown but not the existence.
  (The existence follow for example from the Fredholm theory.)}

  Thank you for pointing this out. We adjusted the
  phrasing of these.

\item[12.] {\color{blue}
  Theorem 8, 9 and 10 only seem to be valid for $k$ with
  ${\rm Im}(k) \geq 0$.}

  Again, thank you for this. This is certainly true for theorems
  8 and 10. We think that the demonstrated null vector in
  theorem 9 works for general $k$.

\end{itemize}

We also appreciate the reviewer alerting us to some typos, which have
been fixed.

\section{Reviewer 2}

Comments by the second reviewer. Original reviewer comments
in {\color{blue} blue}.

\begin{itemize}
\item[1.] {\color{blue} In the abstract and introduction the authors talk about the so-called pollution effect
with no reference to the Helmholtz problem or what high frequency regime means for
this problem. Thus unless the reader has experience with Helmholtz problems (may
not be the case for people interested in Stokes problems), they will not understand the
associated numerical challenges. This should be clarified.}

  We appreciate this suggestion and agree it may have been confusing.
  We have added a brief description of the phenomenon to the
  introduction.

\item[2.] {\color{blue} On page 3 line 31, what is meant by “current grid?”}

  Thank you for pointing out this vagueness. The current grid referred
  to the current boundary discretization. We have reworked this section
  in response to comments by the other reviewer and have dropped this more
  philosophical point altogether.

\item[3.] {\color{blue} On page 5 line 36, should $\exists \phi_0$ read $\exists \phi_0 \in X$?}

  Thank you for pointing this out. It's been fixed.

\item[4.] {\color{blue} On page 28 line 38, is the linear system $C_k^N$
  also discretized with generalized Gaussian quadrature?}

  Yes, this has been clarified in the revision.

\item[5.] {\color{blue} In Figure 6, a plot of $O(N \log N )$
  would be more helpful than $O(N )$ since that is the expected scaling.}

  Good point. This has been adjusted.

\end{itemize}

\end{document}

### 2019-12-06 doc/review-acom/stokes-eig.tex
add rebuttal docs

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}

\newcounter{chapter} % to fix the bug in svjour3

%\usepackage{b} inserted b.sty

%Packages
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage{amsthm}
\usepackage{cancel}
\usepackage{graphicx}
\usepackage{color}

%Theorems, etc.
%\newtheorem*{thm}{Theorem}
%\newtheorem*{lemma}{Lemma}
%\newtheorem*{defn}{Definition}
%\newtheorem*{prop}{Proposition}

%Changed Notation
%\renewcommand{\phi}{\varphi} 
\renewcommand{\Re}{{\rm Re}}
\renewcommand{\Im}{{\rm Im}}
\renewcommand{\sec}{\textsection}
\renewcommand{\S}{\mathbb{S}}

%Notation
\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\D}{\mathbb{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\setdef}[2]{\left\{#1 \mid #2\right\} }
\newcommand{\fcndef}[3]{#1:#2\rightarrow#3}
\newcommand{\norm}[1]{\left\Vert#1\right\Vert}
\newcommand{\dotp}[2]{\left\langle#1,#2\right\rangle}
\newcommand{\br}[1]{\!\left\langle#1\right\rangle\!}
\newcommand{\parder}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\bd}{\partial}
\newcommand{\eps}{\varepsilon}
\newcommand{\lap}{\Delta}
\newcommand{\norder}[1]{\parder{#1}{\nu}}
\newcommand{\del}{\nabla}

%boldface
\newcommand{\bld}[1]{{\bf{#1}}}

\def\bz{{\boldsymbol 0}}
\def\br{{\boldsymbol r}}
\def\bv{{\boldsymbol v}}
\def\bc{{\boldsymbol c}}
\def\bh{{\boldsymbol h}}
\def\bn{{\boldsymbol n}}
\def\bT{{\boldsymbol T}}
\def\bt{{\boldsymbol t}}
\def\xx{{\boldsymbol x}}
\def\bx{{\boldsymbol x}}
\def\yy{{\boldsymbol y}}
\def\by{{\boldsymbol y}}
\def\ss{{\boldsymbol s}}
\def\tt{{\boldsymbol t}}
\def\uu{{\boldsymbol u}}
\def\bu{{\boldsymbol u}}
\def\be{{\boldsymbol e}}
\def\bl{{\boldsymbol \ell}}
\def\ff{{\boldsymbol f}}
\def\bg{{\boldsymbol g}}
\def\GG{{\bf G}}
\def\Gbh{G^{\textrm{BH}}}
\def\Glap{G^{\textrm{L}}}
\def\Ghelm{G^{\textrm{H}}}
\def\Kfark{K^{\textrm{F}}}
\def\II{{\bf I}}
\def\TT{{\bf T}}
\def\bS{{\bf S}}
\def\bD{{\bf D}}
\def\bC{{\bf C}}
\def\bB{{\bf B}}
\def\cN{{\mathcal N}}
\def\cK{{\mathcal K}}
\def\cB{{\mathcal B}}
\def\cA{{\mathcal A}}
\def\cS{{\mathcal S}}
\def\cSk{{\mathcal S}_k}
\def\cD{{\mathcal D}}
\def\cDt{{\mathcal D}^{\intercal}}
\def\cDk{{\mathcal D}_{k}}
\def\cDkt{{\mathcal D}_{k}^{\intercal}}
\def\cW{{\mathcal W}}
\def\cJ{{\mathcal J}}
\def\cL{{\mathcal L}}
\def\cA{{\mathcal A}}
\def\cM{{\mathcal M}}
\def\bL{{\mathbb L}}
\def\bK{{\mathbf K}}
\def\sint{{\sin{(\theta)}}}
\def\cost{{\cos{(\theta)}}}

\def\jkr{J_{0}(kr)}
\def\jpkr{J_{0}'(kr)}
\def\jpk{J_{0}'(k)}
\def\jppkr{J_{0}''(kr)}
\def\jppk{J_{0}''(k)}
\def\ddr{\frac{d}{dr}}

\def\bsigma{{\boldsymbol \sigma}}
\def\bpsi{{\boldsymbol \psi}}
\def\bmu{{\boldsymbol \mu}}
\def\bnu{{\boldsymbol \nu}}
\def\brho{{\boldsymbol \rho}}
\def\btau{{\boldsymbol \tau}}
\def\bigo{\mathcal{O}}
\def\littleo{o}

\def\Im{{\textrm{\textup{Im}}}}

\def\epsflam{{\epsilon_{\texttt{FLAM}}}}
\def\epscheb{{\epsilon_{\texttt{cheb}}}}
\def\epsclose{{\epsilon_{\textrm{close}}}}
\def\cheb{{\texttt{cheb}}}

\newcommand\dwdn{\frac{\partial w}{\partial n}}
\newcommand{\cI}{\mathcal I}
\newcommand{\cC}{\mathcal C}
\newcommand{\bbmat}{\begin{bmatrix}}
\newcommand{\ebmat}{\end{bmatrix}}

\newcommand{\real}{\textrm{Re}}
\newcommand{\imag}{\textrm{Im}}

\def\pv{\textrm{P.V.} }

\usepackage{subcaption}
\captionsetup{compatibility=false}

\usepackage{cleveref}
\crefname{equation}{}{}
\Crefname{equation}{}{}
\crefname{eqnarray}{}{}
\Crefname{eqnarray}{}{}

% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
 \journalname{Advances in Computational Mathematics}
%
\begin{document}

\title{A boundary integral equation approach to
  computing eigenvalues of the Stokes operator%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
\subtitle{}
\titlerunning{Stokes Eigenvalues}        % if too long for running head

\author{Travis Askham         \and
  Manas Rachh %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{T. Askham \at
  Department of Mathematical Sciences\\
  New Jersey Institute of Technology\\
  Newark, NJ, USA.\\
  \email{askham@njit.edu}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
  \and
  M. Rachh \at
  Center for Computational Mathematics \\
  Flatiron Institute \\
  New York, NY, USA. \\
  \email{mrachh@flatironinstitute.org}
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abstract{
  The eigenvalues and eigenfunctions of the Stokes 
  operator have been the subject of intense analytical
  investigation and have applications in the study
  and simulation of the Navier--Stokes equations.
  %
  As the Stokes operator is second-order and has
  the divergence-free constraint,
  computing these eigenvalues and the corresponding
  eigenfunctions is a challenging task, particularly in
  complex geometries and at high frequencies.
  %
  The boundary integral equation (BIE) framework
  provides robust and scalable eigenvalue computations
  due to (a) the reduction in the dimension of the problem to
  be discretized and (b)
  the absence of high frequency ``pollution'' when using
  a Green's function to represent propagating waves.
  %
  In this paper, we detail the theoretical justification
  for a BIE approach to the Stokes eigenvalue problem on
  simply and multiply-connected planar domains, which entails
  a treatment of the uniqueness theory for oscillatory
  Stokes equations on exterior domains. 
  %
  Then, using well-established techniques for
  discretizing BIEs,
  we present numerical results which confirm
  the analytical claims of the paper and demonstrate
  the efficiency of the overall approach.
}

% flatex input: [01intro.tex]
\section{Introduction}

The planar incompressible Stokes equations describe
creeping flows in two dimensions.
%
Let $\Omega \subset \R^2$
be a bounded domain with $C^2$ boundary denoted by $\Gamma$.
%
The Stokes eigenvalue problem is to find
values $k^2$ such that

\begin{equation}
\begin{aligned}
  -\Delta \uu + \nabla p &= k^2 \uu \quad \textrm{in} \quad
  \Omega \label{eq:ostokes} \; , \\
  \nabla \cdot \uu &= 0 \; ,
\end{aligned}
\end{equation}
subject to boundary conditions, has a non-trivial solution $(\uu,p)$.
%
In this work, we consider the eigenvalue problem subject to 
the Dirichlet boundary condition,
\begin{equation}
  \uu = \bz \quad \textrm{on} \quad \Gamma \label{eq:ostokes_dir} \; .
\end{equation}
It is well known that the values $k^2$ are necessarily
real and positive and that there is a countable collection of such
values $0 < k_{1}^{2} \leq k_{2}^2 \leq \ldots \uparrow \infty$,
counting multiplicities.

\begin{remark}
  When $k = i\alpha$, the differential equation
  \cref{eq:ostokes} is known as the modified Stokes
  equation. As there appears to be no preferred
  name for the equation with real-valued $k$,
  we will refer to \cref{eq:ostokes} as the
  oscillatory Stokes equation.
\end{remark}

The eigenvalues (and eigenfunctions)
of the Stokes operator have applications in the
stability analysis of stationary solutions of the
Navier--Stokes equations \cite{osborn1976approximation},
in the study of decaying two dimensional turbulence
\cite{schneider2008final}, and as a trial basis for
numerical simulations of the Navier--Stokes
equations~\cite{batcho1994generalized}.
%
The eigenvalues and eigenfunctions of the Stokes
operator are also the subject of intense analytical
investigation
\cite{taylor1933buckling,szego1950membranes,polya1951isoperimetric,bramble1963pointwise,ashbaugh1996fundamental,leriche2004stokes,kelliher2009eigenvalues,antunes2011buckling},
especially as they relate to the eigenvalues and
eigenfunctions of the Laplacian.
{\color{red} Some of these latter studies are
  formulated in terms of the ``buckling''
  eigenvalues of the biharmonic operator (so-called
  because the lowest eigenvalue represents the
  critical buckling load of an idealized
  elastic plate~\cite{taylor1933buckling,szego1950membranes,polya1951isoperimetric}),
  which are equivalent to the Stokes operator eigenvalues on simply
  connected domains~\cite{kelliher2009eigenvalues}.
%
  This can be seen through the stream function
  formulation  of the oscillatory Stokes
  equation, i.e. setting $\bu = \nabla^\perp \psi$
  where $\psi$ now satisfies

  \begin{equation*}
    -\Delta^2 \psi = k^2 \Delta \psi \quad \textrm{in} \quad \Omega\; .
  \end{equation*}
  Note that the buckling problem enforces the
  clamped, or first Dirichlet, boundary
  condition on $\psi$

  \begin{equation*}
    \psi = \partial_\nu \psi = 0 \; \quad \textrm{on} \quad \Gamma.
  \end{equation*}
  On a multiply connected domain, there are
  Stokes eigenfunctions which do not have a corresponding
  clamped stream function, so that the
  buckling eigenvalues are a subset of the Stokes
  eigenvalues.}

Historically, the Stokes eigenvalue problem serves as a
common model problem for numerical eigenvalue analysis
with a {\color{red} constrained, second-order operator (or a
fourth-order operator through the connection to buckling
above).}
%
Further, numerical simulation has long played an
important role in the analyses cited above --- both for
computing the eigenvalues and eigenfunctions
on domains of practical interest and in forming
new conjectures.

Borrowing the language of~\cite{zhao2015robust},
which concerns the eigenvalues of the Laplacian
(also known as the membrane or ``drum'' problem),
the numerical treatment of the Stokes eigenvalue
problem can be divided into two basic approaches.
%
The first class of methods
directly discretize the
differential operator, typically with a
finite element basis, and the eigenvalues are found
as the eigenvalues of the discrete system.
%
The second class of methods reformulate the 
oscillatory Stokes equations as a boundary integral
equation (BIE) which is discretized.
The eigenvalues are then found
by a nonlinear search for the values of
$k$ where the BIE is not invertible.
%

There is a large body of research on the first class of methods
for the Stokes eigenvalue problem.
%
We do not seek to review this literature here,
but point to \cite{johnson1974beam,rannacher1979nonconforming,mercier1981eigenvalue,bjorstad1999high,jia2009approximation,chen2006approximation,lovadina2009posteriori,huang2011numerical,carstensen2014guaranteed}
for some representative examples.

As noted in~\cite{zhao2015robust}, integral
equation based methods provide several advantages.
%
Because the BIE is defined on the
boundary alone, there is a reduction in the
dimension of the domain to be discretized.
%
{\color{red}This reduces the number of required unknowns over finite
element discretizations. Further, it is known
that standard finite element approaches suffer from
high-frequency ``pollution'' in two and three dimensions
for oscillatory problems and, hence, the computation
of larger eigenvalues. In the original context, 
the term pollution refers to the fact that,
when solving the Helmholtz equation in dimension
greater than one,
the accuracy of the Galerkin solution of
a problem does indeed differ by a constant factor from
the error in the best approximation of the true
solution in the finite element space but this factor
grows as a function of the frequency $k$
\cite{babuska1997pollution}.
Thus, at higher frequencies, a finite element method
requires more degrees of freedom than suggested
by the number of degrees of freedom required to
resolve the solution.
In constrast, a BIE does not suffer from this
effect.}

Further, Zhao and Barnett~\cite{zhao2015robust}
show how to alleviate some of the costliness of the
nonlinear optimization introduced by formulating the 
problem as an integral equation.
%
The standard approach searches for ``V''-shaped minima
of the singular values of the BIE; see, for
instance, \cite{trefethen2006computed}.
%
Instead, Zhao and Barnett utilize the Fredholm
determinant (see \cref{sec:dets}) which, for certain
BIEs, is an analytic function of $k$ with roots
precisely when $k^2$ is an eigenvalue.
%
The Fredholm determinant can be estimated using
a Nystr\"{o}m discretization of the BIE
\cite{bornemann2010numerical,zhao2015robust}.
%
Then, the eigenvalues can be estimated efficiently
by using high order root finding methods applied
to the discretized determinant.

With the efficiency of the approach of
\cite{zhao2015robust} for the drum problem in mind,
we develop an integral equation based method for the
Stokes eigenvalue problem.
%
This requires that a layer
potential representation of the solution
of \cref{eq:ostokes} be given and that the resulting BIE
is not invertible precisely when $k^2$ is an eigenvalue.
%
The first requirement is straightforward to
satisfy because 
well-known layer potential representations for the
modified Stokes equation~\cite{Pozrikidis1992,biros2002embedded,jiang2013second,ladyzhenskaya1969mathematical}
are directly applicable.
%
Proving the invertibility of the associated operators
away from the eigenvalues is a more involved task
and forms the bulk of the theoretical component
of this paper.

\subsection{Relation to other work}

{\color{red} BIE methods, as described above, are used
  to compute eigenvalues in a
  variety of applications. These include eigenvalue problems
  for the Laplace operator~\cite{lu1991eigenvalues,steinbach2012convergence,akhmetgaliyev2015boundary,zhao2015robust}, the buckling problem~\cite{kitahara2014boundary,antunes2011buckling},
  Maxwell's equations~\cite{kirsch2007integral}, quantum ``billiards''
  \cite{backer2003numerical,tureci2007efficient,veble2007expanded,barnett2006asymptotic}, clamped plates~\cite{lindsay2018boundary}, 
  and fluid-structure interactions~\cite{kimeswenger2014coupled},
  among others. In some applications, e.g. electrostatic plasmon
  resonances~\cite{mayergoyz2005electrostatic}, it is the eigenvalues
  of the integral operators themselves which are of interest. }

{\color{red}We note that the BIE method can generally be divided
into first-kind formulations, i.e. formulations where
the BIE operator is compact, and second-kind formulations,
i.e. formulations where the BIE operator is of the form
$\mathcal{I}-\mathcal{K}_k$ with $\mathcal{K}_k$
compact. The studies cited above contain examples of both
types of formulations and a variety of optimization techniques
for finding the eigenvalues $k^2$. The previous integral equation
studies of the ``buckling'' eigenvalue problem
(which is equivalent to the Stokes problem on simply connected
domains \cite{kelliher2009eigenvalues}) typically relied on
first-kind integral equation formulations of the underlying partial
differential equation (PDE), based on layer
potentials~\cite{kitahara2014boundary}
or the method of fundamental solutions~\cite{antunes2011buckling}.
In~\cite{kitahara2014boundary}, it is suggested that an
advantage of the layer potentials in that study is that the
corresponding integral kernels are relatively smooth and that
quadrature is straightforward. Since the publication of that
study, high-quality singular quadrature methods have become
available for a variety of singularities on curves and surfaces,
see, e.g.,~\cite{kress1991boundary,alpert1999,bruno2001fast,helsing2008evaluation,bremer2010,bremer2012nystrom,qbxquadrature}. In~\cite{antunes2011buckling},
domains with corners are considered. The method of
fundamental solutions, which does not directly discretize the
domain boundary, offers significant appeal in such a setting because
efficient singular quadrature is not as well understood for a domain
with corners (though progress is being made~\cite{helsing2008corner,serkh2016solution,rachh2017solution,helsing2018integral})
and the boundary integral operators are not as well behaved.
%

In this paper, we develop a second-kind method for the Stokes
operator because
of the aforementioned progress in the area of singular
quadrature and the necessity of a second-kind formulation
to the efficient Fredholm determinant approach advocated
in~\cite{zhao2015robust}.}

\subsection{Paper outline and contributions}

The rest of this paper proceeds as follows.
%
In \cref{sec:prelim}, we set the notation, provide some
mathematical preliminaries, and review 
properties of single and double layer potentials
for the oscillatory Stokes equations.
%
Then, in \cref{sec:analysis}, we develop the necessary
theory for proving the main results of this work 
(\cref{thm:dlmain,thm:cfmain}),
which show that the BIEs resulting from these
layer potential representations are not invertible
precisely when $k^2$ is an eigenvalue.
%
These theoretical developments include a detailed
discussion of the uniqueness of oscillatory Stokes
boundary value problems in exterior domains.
%
To the best of our knowledge, the invertibility
and uniqueness results are new to the literature.
%
\Cref{sec:dets} then outlines how the Fredholm determinant
can be used in the oscillatory Stokes context.
%
In \cref{sec:numerical}, we describe the numerical
methods we use to discretize the BIEs and to perform
determinant calculations.
%
While the underlying methods are well-established,
the combination of a high-order singular quadrature
rule and a fast-direct method for determinant evaluations
in a BIE framework is novel.
%
At the moderate frequencies considered in this
paper, we find that standard fast-direct
solvers provide a reasonably efficient determinant
evaluation.
%
We also present numerical experiments
which demonstrate some of the paper's analytical
claims as well as the effectiveness of the overall
framework.
%
Finally, we provide some concluding thoughts,
describe plans for future research,
and outline some open questions in
\cref{sec:conclusion}.

% flatex input end: [01intro.tex]

%
% flatex input: [02prelim.tex]
\section{Mathematical Preliminaries}
\label{sec:prelim}
In this paper, vector- and tensor-valued quantities
are denoted by bold letters (e.g. $\bh$ and $\mathbf{T}$). 
Subscript indices of non-bold characters (e.g. $h_j$ or $T_{ij\ell}$)
are used to denote the entries within a vector or tensor.
We use the standard Einstein summation convention; i.e., 
there is an implied sum taken over the repeated indices of 
any term (e.g. the symbol $a_{j} b_{j}$ is used to represent the sum
$\sum_{j} a_{j} b_{j}$).
If $\xx = (x_1,x_2)^\intercal$, then $\xx^\bot = (-x_2,x_1)^\intercal$.
Similarly, $\nabla^\bot = (-\partial_{x_2},\partial_{x_1})^\intercal$.
Upper-case script characters (e.g. $\mathcal{K}$) are reserved for
operators on Banach spaces, with $\mathcal{I}$ denoting the
identity. Given a set $X$, we denote the closure of $X$
by $\overline{X}$.

For a velocity field $\bu$ and pressure $p$, let $\bsigma(\bu,p)$
denote the Cauchy stress tensor is given by
\begin{equation}
\bsigma(\uu,p) = -p \II + 2 \be(\bu) \, ,
\end{equation}
where $\be(\bu)$ is the strain tensor given by
\begin{equation}
e_{ij}(\bu) = \frac{1}{2} \left( \partial_{x_j} u_i + \partial_{x_i} u_j \right) \; .
\end{equation}
When it is clear from context, we will drop the dependence of
$\bsigma$ on $\bu$ and $p$.
If $\Gamma$ is the boundary of a region $\Omega$ and $\bnu$ is the outward
normal to $\Gamma$, the surface traction $\bt$ on $\Gamma$ 
is the Neumann data, i.e. 
\begin{equation}
\bt = \bsigma \cdot \bnu \, .
\end{equation}

We seek solutions of \cref{eq:ostokes} in the space
\begin{equation}
  A(\Omega) = \{ (\bu,p) \textrm{ s.t. } \bu \in
  \left ( C^2(\Omega)\times C^2(\Omega) \right ) \cap
  \left ( C(\bar{\Omega}) \times C(\bar{\Omega}) \right ) \, , \,
  p \in C^1(\Omega) \cap C(\bar{\Omega})\} \; ,
\end{equation}
where $\Omega$ is an open domain.

\subsection{Green's functions}

Let $\mathcal{L}_x$ denote a linear differential operator. A fundamental
solution $G(\xx,\yy)$ of $\mathcal{L}_x$ satisfies the equation
$\mathcal{L}_x G(\xx,\yy) = \delta_y(\xx)$ in the distributional sense, i.e.
for sufficiently smooth $f$
\begin{equation}
  \mathcal{L}_x \int_{\R^2} G(\xx,\yy) f(\yy) \, d \by = f(\xx) \; .
  \nonumber
\end{equation}
We consider here
free-space Green's functions, i.e. fundamental solutions which satisfy appropriate
radiation conditions as $|\xx-\yy| \to \infty$.
The Green's function of the oscillatory biharmonic equation,
\begin{equation}
  \Delta ( \Delta + k^2 ) u = 0 \; , \label{eq:obiharm} \nonumber
\end{equation}
is given by 
\begin{equation}
  \Gbh(\xx,\yy) = \frac{1}{k^2}
  \left (\frac{1}{2\pi} \log |\xx-\yy| +
  \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \right ) \, ,
  \label{eq:Gbh}
\end{equation}
where $k$ is the Helmholtz parameter in the oscillatory biharmonic equation,
and $H_{0}^{1}(r)$ is the Hankel function of the first kind of order zero.
Note that this is a scaled difference of the Green's function for
Laplace, i.e.

\begin{equation}
  \Glap(\xx,\yy) = \frac{1}{2\pi} \log |\xx-\yy| \; , \nonumber
\end{equation}
and the Green's function for the Helmholtz equation

\begin{equation}
  \Ghelm(\xx,\yy) = -\frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \; . \nonumber
\end{equation}

\subsection{The Fredholm Alternative}

We require some standard results from the theory of
Fredholm integral equations. Interested readers may
consult \cite{reed1972methods,colton1983integral,kress1989linear},
among others, for the relevant background.

We first recall some definitions.
Let $X$ and $Y$ be Banach spaces with a non-degenerate
bilinear form $\langle \cdot ,\cdot \rangle: X\times Y \to \C$.
\begin{itemize}
\item Two operators $\cA:X\to X$ and $\cB:Y\to Y$ are
adjoint operators if
$\langle A \phi,\psi \rangle = \langle \phi, B\psi \rangle$
for every $\phi \in X$ and $\psi \in Y$.
\item For an operator $\cM:X\to X$, we can define the range
  $R(\cM)$ as the set {\color{red}$\{\phi \in X: \exists \phi_0 \in X
  \textrm{ with }
  \cM\phi_0 = \phi\}$} and the null space $N(\cM)$ as the
  set $\{\phi \in X: \cM \phi = 0 \}$.
\item An operator $\cA$ is said to be compact if
  $\overline{\cA V}$ is a compact set for any
  bounded subset $V\subset X$.
\item Given a subspace $V\subset X$,
  we can define the subspace $V^\perp\subset Y$ as the
  set $V^\perp = \{ \psi \in Y: \langle \phi,\psi \rangle = 0
  \textrm{ for each } \phi \in V \}$, with the analogous
  definition for subspaces of $Y$.
\end{itemize}

Operators of the form $\cI-\cA$
have existence and uniqueness properties analogous to
matrices. This is known as the Fredholm Alternative;
we present the version provided in \cite{colton1983integral}.

\begin{theorem}[Fredholm Alternative \cite{colton1983integral}]
  Let $X$ and $Y$ be Banach spaces and
  $\langle \cdot,\cdot \rangle: X\times Y \to \C$ be
  a bilinear form. Suppose that $\cA: X\to X$ and
  $\cB:Y \to Y$ are compact adjoint operators. Then
  $\dim N(\cI-\cA) = \dim N(\cI-\cB) \in \N$,
  $R(\cI-\cA) = N(\cI-\cB)^{\perp}$, and
  $R(\cI-\cB) = N(\cI-\cA)^\perp$.
\end{theorem}

\subsection{Properties of the oscillatory Stokes layer
  potentials}

Recall that, in the case $k=i\alpha$ for some real-valued $\alpha$,
the oscillatory Stokes equations \cref{eq:ostokes}
are known as the modified Stokes equations and are of particular
interest for their application to the analysis and numerical
simulation of unsteady flow
\cite{Pozrikidis1992,biros2002embedded,jiang2013second,ladyzhenskaya1969mathematical}.
The equations are well-studied in that setting and
integral representations which lead to second-kind
integral equations have been developed. We review
some of the relevant results here, translating to
the oscillatory setting.

\subsubsection{Oscillatory Stokeslets and stresslets}
Consider the solution of
\cref{eq:ostokes} where a $\delta$-mass
centered at $\yy$ with strength $\ff$
has been added to the right-hand side of \cref{eq:ostokes}, i.e.

\begin{align}
  \nabla p - \Delta \uu - k^2 \uu &= \delta_\yy \ff \; ,
  \label{eq:ostokes_charge}  \\
  \nabla \cdot \uu &= 0 \; . \nonumber
\end{align}
Recall that

\begin{equation}
 \Delta \Glap(\xx,\yy) = \delta_\yy(\xx) \; . \label{eq:lapdelta}
\end{equation}
    {\color{red}
      Proceeding as in~\cite{biros2002embedded},
      we substitute \eqref{eq:lapdelta} into
      \eqref{eq:ostokes_charge} and take the divergence,
      obtaining

\begin{equation}
  \Delta p = \Delta \left (\nabla \Glap(\xx,\yy) \cdot \ff
  \right ) \; . \nonumber
\end{equation}
Then, setting

\begin{equation}
p = \nabla \Glap(\xx,\yy) \cdot \ff \; ,\nonumber
\end{equation}
we obtain}

\begin{align}
  \uu &= - (\Delta + k^2)^{-1} ( \Delta \Glap \ff
  - \nabla (\nabla \Glap \cdot \ff ) ) \nonumber \\
  &= \left ( -\Delta + \nabla \otimes \nabla \right )
  \Gbh \ff \; . \nonumber
\end{align}
The tensor

\begin{equation} \label{eq:ostokeslet}
  \GG = - \II \Delta \Gbh + \nabla \otimes \nabla \Gbh
\end{equation}
is then the analog of a Stokeslet
\cite{Pozrikidis1992} for \eqref{eq:ostokes}.

A related object is the stresslet, which is defined
in terms of the stress tensor of the velocity, pressure
pair induced by a Stokeslet. For these tensors, we find
that it is more convenient to express them in index notation
with the Einstein index summing convention.
Recall that the stress tensor $\bsigma$ is defined as

\begin{equation}
  \sigma_{ij} = -p \delta_{ij} + \left ( \partial_{x_j}u_i
  +\partial_{x_i} u_j \right ) \; , \nonumber
\end{equation}
where $\delta_{ij}$ is the standard Kronecker delta notation.
The stresslet $\TT$ is defined to be

\begin{align}
  T_{ij\ell} &= - \partial_{x_j} \Glap \delta_{i\ell}
  + \partial_{x_\ell} \left ( -\Delta \Gbh \delta_{ij} +
  \partial_{x_i} \left(\partial_{x_j} \Gbh \right) \right)
  \nonumber \\
  & \qquad+ \partial_{x_i} \left ( -\Delta \Gbh \delta_{\ell j} +
  \partial_{x_\ell} \left(\partial_{x_j} \Gbh \right) \right)
  \; . \label{eq:ostress} 
\end{align}
Let $u_i = G_{ij} f_j$ and $p = \partial_{x_i} \Glap f_i$ be a
solution of the Stokes equations induced by a Stokeslet.
Then the corresponding stress tensor is given by
$\sigma_{i\ell} = T_{ij\ell} f_j$.

%For the layer potentials of the next section, the following
%formulas are useful. Let $\bnu$ be a given vector. When
%summing over the third index, we obtain
%
%\begin{equation}
%  \TT_{\cdot,\cdot,\ell} \nu_\ell = -\bnu \otimes \nabla \Glap
%  + \partial_\nu \left ( -\Delta \Gbh \II
%  + \nabla \otimes \nabla \Gbh \right)
%  + \nabla \otimes \left ( -\Delta \Gbh \bnu
%  + \partial_{\nu} \nabla \Gbh \right) \; . \nonumber
%\end{equation}
%Let $\btau = \bnu^\bot$. Then
%
%\begin{equation}
%  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla \Glap
%  - \nabla^\bot \otimes \nabla^\bot \partial_\nu \Gbh
%  +\nabla \otimes \nabla^\bot \partial_\tau \Gbh \; .
%  \nonumber
%\end{equation}

\subsubsection{Layer potentials}

We now use the Stokeslet and stresslet 
to define the single
and double layer potentials for the oscillatory Stokes problem.
For $\xx \in \R^2$, the single layer potential with density $\bmu$
is defined to be

\begin{equation} \label{eq:singlelayer}
  \bS [\bmu] (\xx) = \int_\Gamma \GG (\xx,\yy) \bmu(\yy)
  \, dS(\yy) \; .
\end{equation}
We use the notation $\bsigma_\bS[\bmu]$ to denote the
stress tensor of the single layer at any given point
$\xx \in \R^2 \setminus \Gamma$.

For $\xx \in \R^2 \setminus \Gamma$, the double layer
potential with density $\bmu$ is defined to be

\begin{equation} \label{eq:doublelayer}
  \bD [\bmu] (\xx) = \int_\Gamma \left ( \TT_{\cdot,\cdot,\ell}(\xx,\yy)
  \nu_\ell(\yy)\right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
\end{equation}
where $\bnu$ denotes the outward unit normal to the boundary.
If we write $\bmu = \bnu \mu_\nu + \btau \mu_\tau$,
where $\btau = \bnu^\bot$ is the positively oriented unit
tangent to the curve, then we have

\begin{align} \label{eq:stokesdlkernel}
  \left ( \TT_{\cdot,\cdot,\ell}(\xx,\yy)\nu_\ell(\yy) \right )^\intercal
  \bmu(\yy) &= \left ( - \nabla \Glap(\xx,\yy) + 2 \nabla^\bot
  \partial_{\nu\tau} \Gbh(\xx,\yy) \right ) \mu_\nu(\yy) \nonumber \\
  & \qquad+
  \nabla^\bot \left (\partial_{\tau\tau}-\partial_{\nu\nu} \right )
  \Gbh(\xx,\yy) \mu_\tau(\yy) \; .
\end{align}

Let $\cS[\bmu]: C(\Gamma) \to C(\Gamma)$, and
$\cD[\bmu]: C(\Gamma) \to C(\Gamma)$ 
denote the restrictions of the layer potentials 
$\bS[\bmu]$ and $\bD[\bmu]$ on the boundary $\Gamma$, i.e.
for $\bx \in \Gamma$,

\begin{equation}
  \cS [\bmu] (\xx) = \int_\Gamma \GG (\xx,\yy) \bmu(\yy)
  \, dS(\yy)
\end{equation}
and
\begin{equation}
\label{eq:dlformula}
  \cD [\bmu] (\xx) = \pv \int_\Gamma \left ( \TT_{\cdot,\cdot,\ell}(\bx,\by)
  \nu_\ell(\yy)
  \right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
\end{equation}
where the \pv indicates that the integral is to be
evaluated in the principal value sense.

For two vector valued
functions $\ff$ and $\bg$ defined on $\Gamma$, consider the bilinear
form
\begin{equation} \label{eq:bi_form}
  \langle \ff , \bg \rangle = \int_\Gamma \ff \cdot \bg dS \; .
\end{equation}
The definition of the adjoint used throughout the paper will be
the one induced by this form.

The adjoint of $\cD$ with respect to the above bilinear form
is of particular interest; and is given by
\begin{equation}
  \cD^{\intercal} [\bmu](\bx) = 
  \pv \int_\Gamma \left ( \TT_{\cdot,\cdot,\ell}(\bx,\by)\nu_\ell(\xx)
  \right ) \bmu(\yy) \, dS(\yy) \; .
\end{equation}

In the following lemma, we review the limiting values of
the layer potentials $\bS$ and $\bD$ on the boundary $\Gamma$.

\begin{lemma}[Jump conditions] \label{lem:jump-conds}
  Suppose that $\Omega$ is a bounded region with a $C^{2}$ boundary
  $\Gamma$.
  Let $\bnu(\bx)$ denote the outward pointing normal at $\bx \in \Gamma$.
  Suppose that $\bmu \in C(\Gamma)$.
  Then $\bS[\bmu]$
  is continuous across $\Gamma$, and the exterior and interior
  limits of the surface traction of $\bD[\bmu]$ are equal.
  Furthermore, for $\bx_{0} \in \Gamma$,

  \begin{align}
    \lim_{h \downarrow 0^{+}} \bsigma_\bS[\bmu](\xx_0 \pm h\bnu(\xx_0)) \cdot \bnu(\xx_0)
    &= \mp \frac{1}{2} \bmu(\xx_0) + \cDt[\bmu](\xx_0) \\
    \lim_{h \downarrow 0^{+}} \bD[\bmu](\xx_0 \pm h\bnu(\xx_0)) 
    &= \pm \frac{1}{2} \bmu(\xx_0) + \cD[\bmu](\xx_0)    \; .
  \end{align}
\end{lemma}

The above expressions are derived by noting that the
leading order singularity of these integral kernels
is the same as for the original Stokes case, so that
the standard jump conditions for Stokes
\cite{KimSangtae1991,Pozrikidis1992}
apply.

\begin{lemma} \label{lem:compact-sd}
  Suppose that $\Omega$ is a bounded region with a $C^{2}$ boundary
  $\Gamma$. Then the operators $\cS$ and $\cD$ defined
  above are compact operators on $C(\Gamma)\times C(\Gamma)$
  and $\mathbb{L}^2(\Gamma)\times \mathbb{L}^2(\Gamma)$.
\end{lemma}

Compactness is proved by considering the
asymptotic expansion of each kernel about
$\xx=\yy$ and noting that each is at most
weakly singular.

\subsubsection{Representation theorem}

In the following theorem, we sketch the proof of the equivalent of the
Green's identity for oscillatory Stokes setting, which is well-known
in the Stokes and modified Stokes settings
\cite{Pozrikidis1992,biros2002embedded,ladyzhenskaya1969mathematical}.

\begin{theorem} \label{thrm:rep-theorem}
  Let $\Omega$ be a bounded domain with $C^2$ boundary and let
  the pair $(\bu,p)$ satisfy the oscillatory Stokes equations
  \cref{eq:ostokes} in $\Omega$. Let $\bt$ denote the surface
  traction associated with $(\bu,p)$. Then

  \begin{equation} \label{eq:rep-theorem}
    \bS [\bt](\xx) - \bD[\bu](\xx) = \begin{cases} 
    \bu(\xx) &\quad \xx \in \Omega \,  \\
    0 &\quad \xx \in E 
    \end{cases} \; ,
  \end{equation}
  where $E=\R^2\setminus\bar\Omega$ is the
  exterior of the domain.
\end{theorem}

\begin{proof}
  Suppose that $\xx \in \Omega$.
  By the definitions of $\GG$ and $\Glap$, we have
  \begin{equation*}
    \bu(\xx) = \int_\Omega -(\Delta + k^2) \GG(\xx,\yy) \bu(\yy)
    + \nabla \otimes \nabla \Glap(\xx,\yy) \bu(\yy) \, dV(\yy) \; .
  \end{equation*}
  Applying Green's identity and the divergence theorem, we
  obtain
  \begin{equation}
    \bu(\xx) = \int_\Gamma \GG(\xx,\yy) \partial_\nu \bu
    - \partial_\nu \GG(\xx,\yy) \bu
    - \nabla \Glap(\xx,\yy) (\bnu \cdot \bu) \, dS 
    - \int_\Omega \GG(\xx,\yy) (\Delta + k^2) u \, dV \; .
    \nonumber
  \end{equation}
  Substituting the definition of the PDE and applying the divergence
  theorem again, we obtain
  \begin{equation}
    \bu(\xx) = \int_\Gamma \GG \partial_\nu \bu - p \GG \bnu - \partial_\nu \GG \bu
    - \nabla \Glap (\bnu \cdot \bu) \, dS  \; . \label{eq:rep_proof_1}
  \end{equation}
  From the divergence theorem and the divergence-free properties of
  $\uu$ and $\GG$, we then get

  \begin{equation}
    \int_\Gamma \GG \nabla (\bu \cdot \bnu)
    - (\nabla \GG \bnu)^\intercal \bu \, dS = 0 \; .  \label{eq:rep_proof_2}
  \end{equation}
  Adding \cref{eq:rep_proof_1,eq:rep_proof_2}, we get the desired
  result. The argument for the case $\xx \in E$ is similar.
\qed
\end{proof}

A consequence of \cref{thrm:rep-theorem} and the analyticity
of $\Gbh$ is 
\begin{corollary}
\label{cor:analytic}  
  Let $(\uu,p) \in A(\Omega)$ be a solution of \cref{eq:ostokes}.
  Then each component of $\uu(\xx)$ is an analytic function
  of the coordinates $\xx$ in $\Omega$.
\end{corollary}

The proof of \cref{cor:analytic} follows the same reasoning as
that for the Helmholtz case; see \cite[Theorem 3.5]{colton1983integral}.

\subsubsection{Null-space correction \label{subsubsec:nullspacecorr}}

Without modification, the standard layer potentials
can result in rank-deficient representations for
the boundary value problems. The nature of this deficiency
is treated in~\cref{sec:analysis} but for now we introduce a standard
operator used to correct this. For any integrable density
$\bmu$, let $\cW[\bmu]$ be defined by

\begin{equation} \label{eq:ones_operator}
  \cW[\bmu](\xx) = \frac{1}{|\Gamma|} \int_\Gamma \bnu(\xx)
  \left ( \bnu(\yy) \cdot \bmu(\yy) \right )
  \, dS(\yy) \; ,
\end{equation}
for any $\xx \in \Gamma$. We have

\begin{lemma}
  \label{lem:propnullspacecorr}

  Let $\Omega$ be a domain with $C^2$ boundary and $\bmu$ be
  an integrable function defined on $\Gamma$. Then
  \begin{itemize}
  \item $\cW[\cW[\bmu]] = \cW[\bmu]$,
  \item $\cW^\intercal = \cW$,
  \item $\cW[\bmu - 2 \cD[\bmu]] = 0$,
  \item $\cW[\cS[\bmu]] = 0$,
  \end{itemize}
  where the transpose is induced by the bilinear
  form \cref{eq:bi_form}.
\end{lemma}

\begin{proof}
  The first two results follow from the definitions of $\cW$ and
  the normal vector. The other two follow from the fact that
  $\bS[\bmu]$ and $\bD[\bmu]$ are divergence-free and
  an application of \cref{lem:jump-conds}.
\qed
\end{proof}

\begin{remark}
The operators $\bS,\bD,\cD$ and $\cD^{\intercal}$
depend on the Helmholtz parameter $k$ of the oscillatory Stokes equation.
In places where it is essential to highlight this dependence, in a slight
abuse of notation, we will use the symbols $\bS_{k}, \bD_{k},\cD_{k}$ and $\cDt_{k}$ to 
denote this dependence.
Similarly, we will use $A^{\Gamma}$ instead of the operator $A$ to highlight 
the dependence of the operator $A$ on the boundary of the region $\Gamma$.
\end{remark}

% flatex input end: [02prelim.tex]

%
% flatex input: [03analysis.tex]
\section{Fredholm analysis of the integral representations}
\label{sec:analysis}
In this section, we establish how layer potential
representations of oscillatory Stokes velocity fields
can be used to compute Stokes eigenvalues.
%
The main results show that for certain representations
the resulting integral equation is not invertible precisely
when $k^2$ is an eigenvalue.
%
For the interior Dirichlet eigenvalue problem, this is
proved separately for a double layer representation on
simply connected domains in \cref{thm:dlmain} and
for a combined-field representation on multiply connected
domains in \cref{thm:cfmain}.
%

Before proving the main theorems, we require a number
of uniqueness results for oscillatory Stokes boundary
value problems.
%
To prove the uniqueness results, we follow the 
structure presented in Colton and Kress~\cite[Ch. 3]{colton1983integral}
for the scalar Helmholtz equation.
%
While uniqueness results for interior Dirichlet,
Neumann, and impedance problems follow from energy
considerations and compactness arguments, the proofs
for the uniqueness of exterior problems are more
involved.
%
In particular, the exterior problems are only 
well-posed after imposing an appropriate radiation
condition.
%
We formulate well-posed boundary value problems 
for both interior and exterior domains with
Dirichlet, Neumann and impedance boundary
conditions and present uniqueness results for
each.

Along with the Fredholm alternative, these uniqueness
results are sufficient to prove
\cref{thm:dlmain,thm:cfmain}.
%
Once the main theorems are established,
the details of how to use the Fredholm determinant
as a numerical tool for computing the Stokes eigenvalues
follow in a straightforward manner from the results
in~\cite{zhao2015robust}.
%
We reproduce these results in the present
context for completeness.

\subsection{Boundary value problems --- interior}

Let $\Omega$ be a bounded domain with a $C^2$ boundary
denoted by $\Gamma$.
We summarize the interior Dirichlet, Neumann and impedance
boundary value problems in~\cref{def:int_dir,def:int_neu,def:int_imp} below.

\begin{definition}[Interior Dirichlet problem]
  \label{def:int_dir}
  Let $\ff \in C(\Omega)$ be given. Find $(\bu,p) \in A(\Omega)$
  such that
  \begin{equation}
  \begin{aligned} \label{eq:dir_interior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in \Omega \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in \Omega \, ,  \\
    \bu &= \ff \quad \bx \in \Gamma \, .
  \end{aligned}
  \end{equation}
\end{definition}
Note that the divergence-free constraint for the oscillatory
Stokes equations implies a compatibility condition on the
Dirichlet data $\ff$, namely that
\begin{equation} \label{eq:dir_compat}
  \int_\Gamma \ff \cdot \bnu \, dS = 0 \; .
\end{equation}

\begin{definition}[Interior Neumann problem]
  \label{def:int_neu}
  Let $\bg \in C(\Omega)$ be given. Find $(\bu,p) \in A(\Omega)$
  such that
  \begin{equation}
  \begin{aligned} \label{eq:neu_interior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in \Omega \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in \Omega \, ,  \\
    \bt &= \bg \quad \bx \in \Gamma \, .
  \end{aligned}
  \end{equation}
\end{definition}

\begin{definition}[Interior impedance problem]
\label{def:int_imp}
  Let $\bh \in C(\Omega)$ be given and suppose 
  $\eta \in \mathbb{C}$ with $\Re{(\eta)} >0$ and $\Im{(\eta)}\ge 0$. 
  Find $(\bu,p) \in A(\Omega)$  such that
  \begin{equation}
  \begin{aligned} \label{eq:imp_interior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in \Omega \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in \Omega \, ,  \\
    \bt - i \eta \bu &= \bh \quad \bx \in \Gamma \, .
  \end{aligned}
  \end{equation}
\end{definition}

\subsection{A radiation condition for the oscillatory Stokes
  equation}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{ext_dom}
  \caption{Example of an exterior domain with four obstacles.}
  \label{fig:ext_dom}
  \end{center}
\end{figure}

Let $\Omega$ be the union of a finite collection of
simply connected domains, i.e. $\Omega = \bigcup_{i=1}^m \Omega_i$
for some $m \in \N$,
and let $E = \R^{2} \setminus \bar{\Omega}$ denote its
exterior; see \cref{fig:ext_dom} for an example with $m=4$.
%
Let $\Gamma = \partial E$ denote the boundary of $E$ and
$\bnu(\yy)$ denote the exterior normal to the point $\yy$ on
$\Gamma$, i.e. the normal vector pointing out of $E$ into $\Omega$.
%
For a given function $\ff$ defined on $\Gamma$,
the exterior Dirichlet boundary value problem is to
find a pair $(\bu,p)$ which satisfies:
\begin{equation}
\begin{aligned}
\Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
\nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
\bu &= \ff \quad \bx \in \Gamma \, . \nonumber
\end{aligned}
\end{equation}
In addition to the boundary condition on
$\Gamma$, we must impose radiation conditions
at $\infty$, analogous to the Helmholtz equation.
%

Let $B_r(0)$ denote the disc of radius $r$ centered
at the origin and $\partial B_r(0)$ its boundary.
%
We propose the following radiation condition.

\begin{definition} \label{def:radcond}
Let $(\bu,p)$ satisfy the oscillatory Stokes equations in
the exterior of a bounded domain. We say that
the pair $(\bu,p)$ is {\em radiating} if
\begin{equation}
\lim_{r\to \infty} \sqrt{r} \left| \bt - i k \bu \right| \to 0 \, ,
\label{eq:radcond}
\end{equation}
uniformly in direction where $\bt = \bsigma \cdot \bnu$
with $\bnu = \xx/|\xx|$, i.e. $\bt$ is the surface
traction on $\partial B_r(0)$.     
\end{definition}

In the following lemma, we show that the oscillatory
Stokeslet satisfies the radiation condition. 
\begin{lemma}
  {\color{red}If $\Im (k) \geq 0$, the} oscillatory Stokeslet,
  as defined in \eqref{eq:ostokeslet}, satisfies the radiation
  condition in
  Definition \ref{def:radcond}.
\end{lemma}
\begin{proof}
Consider the Stokeslet induced by an arbitrary charge
$k^2 \bpsi$ at the origin where $\bpsi \in \mathbb{C}^2$ 
is a constant. Let $r = |\xx|$,
$\bnu(\xx) = \xx/|\xx|$, and $\btau(\xx) = \bnu(\xx)^\perp$. We have

\begin{align*}
\bu (\xx) &= k^2 \GG(\xx,0) \bpsi \\
&= k^2 \left (-\II \Delta \Gbh(\xx,0)
+ \nabla \otimes \nabla \Gbh(\xx,0)\right ) \bpsi \\
&= -k^2 \left (\nabla^\perp \otimes \nabla^\perp \Gbh(\xx,0) \right) \bpsi \\
&= \left(\nabla^\perp \otimes \nabla^\perp \left ( \frac{1}{2\pi}
\log r + \frac{i}{4} H_0^{(1)} (kr) \right ) \right)\bpsi \; .
\end{align*}
Note that derivatives of $\log r$ are $\littleo (1/\sqrt{r})$
and that the pressure associated with the Stokeslet is
$p = \nabla \Glap(\xx) \cdot \bpsi$. We then have

\begin{align*}
\left | \sigma \cdot \bnu(\xx) - i k \bu \right | &=
\left | p \bnu(\xx) + \partial_{{\nu_x}} \bu + \nabla (\bu \cdot \bnu(\xx))
- ik \bu \right | \\
&\leq \left | \partial_{{\nu_x}} \bu - ik\bu \right | + \left | \nabla(\bu \cdot \bnu(\xx)) \right |
+ \littleo (1/\sqrt{r}) \\
&\leq \frac{1}{4} \left | \partial_{{\nu_x}} \left(\nabla^\perp \otimes
\nabla^\perp \left (H_0^{(1)} (kr) \right ) \right)\bpsi
- i k \left(\nabla^\perp \otimes \nabla^\perp
\left (H_0^{(1)} (kr) \right ) \right)\bpsi \right | \\
& \quad + \left | \nabla \left( \partial_{\tau_x} \left ( 
\nabla^\perp \left (H_0^{(1)} (kr) \right ) \cdot \bpsi  \right )
\right) \right | + \littleo (1/\sqrt{r}) \; .
\end{align*}
Because $H_0^{(1)}(kr)$ has the asymptotic expansion

\begin{equation}
H_0^{(1)}(kr) = \sqrt{\frac{2}{\pi k r}} e^{i(rk-\pi/4)} \left ( 1 + O\left (
\frac{1}{r} \right ) \right ) \; \nonumber
\end{equation}
as $r\to \infty$, we have

\begin{equation}
\left | \partial_{{\nu_x}} \left(\nabla^\perp \otimes
\nabla^\perp \left (H_0^{(1)} (kr) \right ) \right)\bpsi
- ik \left(\nabla^\perp \otimes \nabla^\perp
\left (H_0^{(1)} (kr) \right ) \right)\bpsi \right | =
o ( 1/\sqrt{r} ) \; . \nonumber
\end{equation}
Finally, since $H_0^{(1)}(kr)$ is radially symmetric,
we have

\begin{equation}
\left | \nabla \left( \partial_{\tau_x} \left ( 
\nabla^\perp \left (H_0^{(1)} (kr) \right ) \cdot \bpsi  \right )
\right) \right | = 0 \; , \nonumber
\end{equation}
so that the Stokeslet satisfies the radiation condition.
\qed
\end{proof}
A consequence of the above lemma is that the oscillatory Stokes
single layer potential satisfies the radiation condition.
\begin{corollary}
Suppose that $\Gamma$ is the boundary of a region $\Omega$
and is $C^{2}$. 
Suppose that $\bmu \in C(\Gamma)\times C(\Gamma)$, then
the oscillatory Stokes single layer potential $\bS[\bmu]$,
as defined in~\cref{eq:singlelayer}, satisfies the radiation condition.
\end{corollary}
The stresslet, as defined in~\cref{eq:ostress}, 
does not necessarily satisfy the radiation condition.
The reason for failure is the logarithmic growth of 
the pressure at $\infty$.
However, the oscillatory Stokes double layer potential
does satisfy the radiation condition 
if the density satisfies an integral constraint.
The following lemma proves this result.

\begin{lemma}
Suppose that $\Gamma$ is the boundary of a region $\Omega$
and is $C^{2}$. 
Suppose that $\bmu \in C(\Gamma) \times C(\Gamma)$ and satisfies
$\int_{\Gamma} \bmu \cdot \bnu dS = 0$, where
$\bnu$ denotes the outward normal to the curve $\Gamma$.
Then, {\color{red} if $\Im (k) \geq 0$}, the oscillatory Stokes 
double layer potential $\bD[\bmu]$, as defined in
\eqref{eq:doublelayer}, also satisfies the radiation
condition.
\end{lemma}

\begin{proof}
We only establish the
decay of the pressure, which we will denote by $p^\bD$;
the rest of the terms in \eqref{eq:radcond} can be bounded
using an argument like that for the Stokeslet above.
Because $p^\bD$ is harmonic in the exterior of any disc
containing $\Gamma$, it is sufficient to show that
$|\nabla p^\bD| = \bigo (1/r^2)$. Let $\btau$ denote the
positively oriented tangent to the curve $\Gamma$ and
$\mu_\nu(\yy)$ and $\mu_\tau(\yy)$ denote $\bmu(\yy) \cdot \bnu(\yy)$ and
$\bmu(\yy) \cdot \btau(\yy)$, respectively. Substituting
$\bD \bmu$ into \eqref{eq:ostokes}, we obtain

\begin{align*}
\nabla p^\bD(\xx) &= (\Delta + k^2) \bD \bmu(\xx) \\
&= \int_\Gamma \left (-k^2 \nabla \Glap (\xx,\yy) +
2 \nabla^\perp \partial_{\nu\tau} \Glap (\xx,\yy) \right ) \mu_\nu(\yy)
\, dS(\yy) \\
& \qquad + \int_\Gamma \nabla^\perp (\partial_{\tau\tau}-\partial_{\nu\nu})\Glap \mu_\tau(\yy)
\, dS(\yy) \; .
\end{align*}
The other terms are higher-order derivatives
of $\Glap$, so it is sufficient to show that the term

\begin{align*}
|\nabla p_1(\xx)| &:= \left |-k^2 \nabla \int_\Gamma \Glap(\xx,\yy)
\mu_\nu(\yy) \, dS(\yy) \right |
\end{align*}
is $\bigo (1/r^2)$. In the following, let $z = x_1 + i x_2$ be the
point corresponding to $\xx$ in the complex plane and let $R$
be the radius of some disc containing $\Gamma$. If $|\xx| > 2R$,
we can use the standard multipole expansion of $\log(z-(y_1+iy_2))$
and the assumption that $\int_\Gamma \bmu \cdot \bnu = 0$
to obtain
\begin{align*}
|\nabla p_1(\xx)| &= \frac{k^2}{2\pi} \left |  \partial_z \int_\Gamma \log(z-(y_1+iy_2))
\mu_\nu(\yy) dS(\yy) \right | \\
&= \frac{k^2}{2\pi} \left |  \partial_z  \left ( \log(z) \int_\Gamma \mu_\nu(\yy) \, dS(\yy)
+ \sum_{l=1}^\infty \frac{1}{z^l} \int_\Gamma \left( y_1+iy_2 \right)^l \mu_\nu(\yy) \, dS(\yy)
\right ) \right | \\
&= \frac{k^2}{2\pi} \left | \sum_{l=1}^\infty \frac{-l}{z^{l+1}}
\int_\Gamma \left( y_1+iy_2 \right)^l \mu_\nu(\yy) \, dS(\yy) \right | \\
&= \bigo (1/r^2) \; .
\end{align*}
\qed
\end{proof}

\subsection{Boundary value problems --- exterior}

Let $E$ and $\Gamma$ be as in the previous subsection.
The radiation condition allows for a well-posed formulation
of the exterior boundary value problems, which we
summarize in
\cref{def:dir_exterior,def:neu_exterior,def:imp_exterior} below.

\begin{definition}[Exterior Dirichlet problem]
  \label{def:dir_exterior}
  Let $\ff \in C(\Gamma)$ be given. Find $(\bu,p) \in A(E)$
  such that
  \begin{equation}
  \begin{aligned} \label{eq:dir_exterior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
    \bu &= \ff \quad \bx \in \Gamma \, , 
  \end{aligned}
  \end{equation}
  and $(\bu,p)$ satisfies the radiation condition in
  \cref{def:radcond}.
\end{definition}
\begin{definition}[Exterior Neumann problem]
  \label{def:neu_exterior}  
  Let $\bg \in C(\Gamma)$ be given. Find $(\bu,p) \in A(E)$
  such that
  \begin{equation}
  \begin{aligned} \label{eq:neu_exterior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
    \bt &= \bg \quad \bx \in \Gamma \, ,
  \end{aligned}
  \end{equation}
  and $(\bu,p)$ satisfies the radiation condition in
  \cref{def:radcond}.
\end{definition}

\begin{definition}[Exterior impedance problem]
  \label{def:imp_exterior}  
  Let $\bh \in C(\Gamma)$ be given and suppose that
  $\eta \in \mathbb{C}$ with $\Re{(\eta)} > 0$ and $\Im{(\eta)} \ge 0$. 
  Find $(\bu,p) \in A(E)$
  such that
  \begin{equation}
  \begin{aligned} \label{eq:imp_exterior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
    \bt + i\eta \bu &= \bh \quad \bx \in \Gamma \, ,
  \end{aligned}
  \end{equation}
  and $(\bu,p)$ satisfies the radiation condition in
  \cref{def:radcond}.
\end{definition}

\subsection{Uniqueness results}

Before moving on to the exterior uniqueness theorems,
we establish the well-known result that
the $k$ corresponding to interior eigenvalues, $k^2$,
are real-valued.

\begin{theorem}
  Let $\Omega$ be a bounded domain and suppose that
  $\Im (k) \neq 0$. Then both the interior
  Dirichlet and Neumann boundary value problems each
  have {\color{red} at most one solution}.
\end{theorem}
\begin{proof}
  A couple applications of the divergence theorem establish
  that
  \begin{equation} \label{eq:greenlike}
    \int_\Omega |2\be(\bu)|^2 - \overline{k}^2 |\bu|^2 \, dV
    = \int_\Gamma \bu \cdot \overline{\bt} \, dS \; . 
  \end{equation}
  Suppose that either $\bu = 0$ or $\bt = 0$ on $\Gamma$.
  Then, the right hand side of \cref{eq:greenlike} is
  zero. 
  Taking the real and imaginary parts of \cref{eq:greenlike},
  it is clear that $\bu \equiv 0$, if $\text{Im}(k) \neq 0$.
\qed
\end{proof}

In the following lemma, we prove uniqueness for the
interior impedance problem.

\begin{theorem}
  Let $\Omega$ be a bounded domain and suppose that
  $\Re (k),\Im (k) > 0$. Then the interior
  impedance problem has {\color{red} at most one}
  solution.
\end{theorem}
\begin{proof}
  Plugging $\bt = i\eta \bu$ in~\cref{eq:greenlike}
  and taking the imaginary part, we get
  \begin{equation}
   2 \Re{(k)} \Im{(k)} \int_{\Omega} |\bu|^2\, dV + 2\Re{(\eta)} \int_{\Gamma}
   |\bu|^2 \, dS = 0 \, ,
  \end{equation}
  from which it is is clear that $\bu \equiv 0$, since
  $\Re{(\eta)}, \Re{(k)}, \Im{(k)} > 0$.
\qed
\end{proof}

We now turn our attention to the uniqueness
of the exterior boundary value problems
for the oscillatory Stokes equation. The
following lemmas are useful for proving these results.

\begin{lemma}
  \label{lem:rep}
  Let the unbounded region $E$ be given as the exterior
  of a finite collection of bounded domains.
  Suppose that $(\bu,p)$ satisfies the oscillatory Stokes equation in 
  $E$ as well as the radiation condition~\cref{eq:radcond}. 
  Then 
  \begin{multline}
    \label{eq:repinfest}  
    \lim_{r\to\infty}
    \int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
    2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
    dV \\
    + 2 \Im \left( k \int_{\Gamma} \bu \cdot 
\overline{\bt} dS  \right) = 0
  \end{multline}

\end{lemma}

\begin{proof}
Since $(\bu,p)$ satisfies the radiation condition, we have that
\begin{equation}
\lim_{r\to\infty} \int_{|\by|=r} | \bt - i k \bu|^2 dS = 
\lim_{r\to\infty} \int_{|\by| =r} \left( |\bt|^2 + |k|^2|\bu|^2 + 2 \Im 
\left( k \bu\cdot \overline{\bt} \right) dS \label{eq:raddecayproof1}
\right) = 0 \, . 
\end{equation}
Since $\bu$ satisfies the oscillatory Stokes equation $E \cap B_{r}(0)$,
using a couple of applications of the divergence theorem, we have that
\begin{equation}
\int_{E\cap B_{r}(0)} |2 \be(\bu)|^2 dV =
-\int_{\Gamma} \bu \cdot \overline{\bt} dS
+ \int_{|\by|=r} \bu \cdot \overline{\bt} dS + \overline{k}^2 
\int_{E \cap B_{r}(0)} |\bu|^2 dV \,. \label{eq:raddecayproof2}
\end{equation}
Combining~\cref{eq:raddecayproof1,eq:raddecayproof2}, we get
\begin{multline*}
\lim_{r\to\infty} \int_{|\by|=r}\left(|\bt|^2 + |k|^2 |\bu|^2 \right) dS 
+ 2 \Im(k)\int_{E \cap B_{r}(0)} \left(|2\be(\bu)|^2 + |k|^2 |\bu|^2 
\right) dV \\
+ 2\Im \left ( k \int_{\Gamma} \bu \cdot \overline{\bt} dS \right) = 0 \, .
\end{multline*}
\qed
\end{proof}

In the next lemma, we prove the analogue of Rellich's lemma for the
oscillatory Stokes equation. 
\begin{lemma}
  \label{lem:rellich}
  Let the unbounded region $E$ be given as the exterior
  of a finite collection of bounded domains.
  Suppose $k$ is real, $\bu$ satisfies the oscillatory
  Stokes equation in $E$, and that 
\begin{equation}
\lim_{r \to \infty} \int_{|\by|=r} |\bu|^2 dS = 0 
\, . \label{eq:decayatinf}
\end{equation}
Then each component of $\bu$ is harmonic in $E$.
\end{lemma}
\begin{proof}
We first note that each component of $\bu= (u_{1},u_{2})$ satisfies the 
oscillatory biharmonic equation in $E$, i.e.
\begin{equation}
\Delta (\Delta + k^2) u_{j} = 0 \quad j=1,2 \,. \nonumber
\end{equation}
For $r$ sufficiently large, we can express $u_{j}$ in the Fourier basis as
\begin{equation}
u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} a_{j,n}(r) e^{i n \theta}  \quad 
j=1,2 \, . \nonumber
\end{equation}
Using Parseval's identity then
\begin{equation}
\int_{|\by|=r} |\bu|^2 dS = r\sum_{n=-\infty}^{\infty} |a_{1,n}(r)|^2  +
|a_{2,n}(r)|^2 \, . \nonumber
\end{equation}
Since $\bu$ satisfies~\cref{eq:decayatinf}, we conclude that
\begin{equation}
\lim_{r\to\infty} r|a_{j,n}(r)|^2 = 0 \quad j=1,2 \, , \label{eq:adecay}
\end{equation}
Since $u_{j}$, $j=1,2$ satisfies the oscillatory biharmonic equation,
the functions $a_{j,n}$ are linear combinations of 
\begin{equation}
r^{|n|}, r^{-|n|}, H^{(1)}_{n}(k r), H^{(2)}_{n}(k r) \, , \quad
n\neq 0 \, , \nonumber
\end{equation}
and
\begin{equation}
1, \log{(r)}, H^{(1)}_{0}(k r), H^{(2)}_{0}(k r) \quad n=0 \, ,  \nonumber
\end{equation} 
where $H_{n}^{(1),(2)}(\cdot)$ are the Hankel functions of the first and
second kind of order $n$.
Since $a_{j,n}(r)$ satisfy~\cref{eq:adecay}, and using the asymptotic 
expansion of $H_{n}^{(1),(2)}(kr)$ when $k$ and $r$ are real-valued, we note
that the projection of $a_{j,n}$ on $r^{|n|}$, and $H_{n}^{1,2}(k r)$
must be zero. Thus, for sufficiently large $r$,
\begin{equation}
u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} \frac{a_{j,n} e^{i n \theta}}{r^{|n|}} 
\, , \nonumber
\end{equation}
i.e. $u_{j}$ is harmonic 
in $B_{r}(0)^{c}$.
Finally, by \cref{cor:analytic}, $\bu$ is
analytic in $E$. Therefore, each $u_j$ is harmonic
throughout $E$.
\qed
\end{proof}

\begin{remark} \label{rmk:harmu}
  Note that if $\bu$ satisfies the assumptions
  of~\cref{lem:rellich}, then each component is harmonic
  and thus $\bu$ satisfies
\begin{align}
k^2 \bu &= \nabla p \label{eq:massconsred} \; .
\end{align}
\end{remark}

\begin{remark}
  It should be noted that in~\cref{lem:rellich}, $\bu$ need
  not be a radiating solution. All that is assumed of $\bu$
  is that it satisfies the oscillatory Stokes equations in $E$.
\end{remark}

We now have the results needed to establish the
uniqueness of exterior boundary value problems.

\begin{theorem}[Uniqueness of the Exterior Dirichlet Problem]
  \label{thrm:unique_dir_ext}
  Let the unbounded region $E$ be given as the exterior
  of a finite collection of bounded domains.
  Suppose that $\Im(k)\geq 0$ and 
  that $(\bu,p)$ is a radiating solution to the oscillatory Stokes
  equation in $E$ with $\bu =0$ on the boundary $\Gamma$, then
  $\bu \equiv 0$ in $E$.
\end{theorem}

\begin{proof}
Since $\bu = 0$ on $\Gamma$, it follows from~\cref{lem:rep} that
\begin{equation}
\lim_{r\to\infty}
\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |\be(\bu)|^2 \right)
dV = 0 \nonumber
\end{equation}

Suppose that $\Im(k) > 0$. Then, it is immediate that
$\bu \equiv 0$ in $E$.

Suppose that $k$ is real valued. It is clear that
\begin{equation}
\lim_{r\to\infty} \int_{|\by|=r} |\bu|^2 dS = 0 \, . \nonumber
\end{equation}
Thus, the conditions on $\bu$ and $k$ in~\cref{lem:rellich}
are satisfied, and each component of $\bu$ is a harmonic function
with $\bu \to 0$ as $r \to \infty$. Furthermore, since $\bu=0$ on
$\Gamma$, by the uniqueness of solutions to the
Dirichlet problem for Laplace's equation
on exterior domains, we conclude that $\bu \equiv 0$
in $E$.
\qed
\end{proof}

\begin{theorem}[Uniqueness of the Exterior Neumann Problem]
  Suppose that $\Omega$ is the union of a finite collection 
  of simply connected domains, i.e. $\Omega = \bigcup_{i=1}^m \Omega_{i}$
  for some $m \in \N$, with $C^{2}$ boundaries, 
  and let $E = \R^{2} \setminus \bar{\Omega}$ denote its exterior;
  see~\cref{fig:ext_dom} for an example with $m=4$.
  Let $\Gamma_{i}$ denote the boundary of $\Omega_{i}$, 
  and $\Gamma = \bigcup_{i=1}^{m} \Gamma_{i}$ denote the boundary
  of $\Omega$.
  Suppose that $\Im(k)\geq 0$ and 
  that $(\bu,p)$ is a radiating solution to the oscillatory Stokes
  equation in $E$ with $\bt = 0$ on the boundary $\Gamma$, then
  $\bu \equiv 0$ in $E$.
\end{theorem}

\begin{proof}
Since $\bt = 0$ on $\Gamma$, it follows
from~\cref{eq:repinfest} that
\begin{equation}
\lim_{r\to\infty}
\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
2 \Im(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |\be(\bu)|^2 \right)
dV = 0 \; . \nonumber
\end{equation}

Suppose that $\Im(k) > 0$. It is then immediate
that $\bu \equiv 0$ in $E$.

Suppose that $k$ is real. It is clear that
\begin{equation}
\lim_{r\to\infty} \int_{|\by|=r} |\bu|^2 dS = 0 \, . \nonumber
\end{equation}
Thus, the conditions on $\bu$ and $k$ in \cref{lem:rellich}
are satisfied, and each component of $\bu$ is a harmonic function
with $\bu \to 0$ as $r \to \infty$. Furthermore, as observed
in \cref{rmk:harmu}, $k^2 \bu = \nabla p$. Then, the boundary
condition becomes $0 = \bt = -p \bnu + 2 \nabla \partial_\nu p/k^2$.
Because $0 = \btau \cdot \bt = 2\partial_{\tau\nu} p/k^2$,
$\partial_\nu p  = c_{i}$ on $\Gamma_{i}$ for each $\Gamma_{i}$,
where $c_{i}$ is a constant. 
Observe that $|\bu|$ and $|\be(\bu)|$ must be $O(1/r)$ as
$r\to\infty$. Thus,
for a radiating pair $(\bu,p)$ with $p$ harmonic,
we have that $|p| = O(1/r)$ and $|\nabla p| = O(1/r^2)$
as $r\to\infty$.
Since the boundary is $C^{2}$ and the boundary data for $p$
is analytic, we conclude that $p$ is $C^{2}$ in
$\overline{E}$.
Furthermore, $\bt=0$ implies $p \bnu = 2\nabla \partial_{\nu} p/k^2$, 
and taking the dot
product with $\bnu$, we get
$p = 2\partial_{\nu \nu}p/k^2$. 
It then follows that
$p = -2\partial_{\tau \tau}p/k^2$ on $\Gamma$ since 
$p$ is harmonic in $E$ and $C^{2}$ in $\overline{E}$. 
Since $p$ satisfies the radiation condition at $\infty$,
we have
\begin{equation}
\begin{aligned}
\int_{E} |\nabla p|^2 dV &= 
\sum_{i=1}^{m} \int_{\Gamma_{i}} p \partial_{\nu}p \,dS \\
&= \sum_{i=1}^{m} c_{i} \int_{\Gamma_{i}} p \,dS \quad \text{(Since $\partial_{\nu} p = c_{i}$ on
$\Gamma_{i}$)} \\ 
&= -\sum_{i=1}^{m} \frac{2c_{i}}{k^2} \int_{\Gamma_{i}} \partial_{\tau \tau} p \,dS 
\quad \text{(Since $p = -\partial_{\tau \tau}p/k^2$ on $\Gamma$)} \\
&= 0
\end{aligned}
\end{equation}
Thus, $p$ is a constant in $E$. Furthermore, since $p\to 0$ at $\infty$, 
we conclude that $p\equiv 0$ in $E$. 
Finally, since $k^2 \bu = \nabla p$, we conclude that $\bu\equiv 0$ in 
$E$.
\qed
\end{proof}

\begin{theorem}[Uniqueness of the Exterior Impedance Problem]
  Let the unbounded region $E$ be given as the exterior
  of a finite collection of bounded domains.
  Suppose that the complex numbers $\eta$ and $k$ satisfy that
  $\Re(\eta), \Re(k) > 0$ and $\Im(\eta),\Im(k) \geq 0$.
  Suppose further that
  $(\bu,p)$ is a radiating solution of the
  oscillatory Stokes equation in $E$ which satisfies
  the homogeneous impedance boundary condition
  \begin{equation}
\bt + i \eta \bu = 0 \quad \xx \in \Gamma \, . \nonumber
\end{equation}
Then $\bu \equiv 0$ for $\xx \in E$.
\end{theorem}

\begin{proof}
Since $\bu$ satisfies the radiation condition at $\infty$ and $\bt = -i\eta \bu$
on $\Gamma$, it follows from~\cref{eq:repinfest} that
\begin{align*}
0 &=
\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
dV \nonumber \\
& \qquad + 2 \text{Im} \left( k \int_{\Gamma} \bu \cdot \overline{\bt} dS  \right) \\
&= 
\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
dV \nonumber \\
& \qquad + 2 \left( \left (\Re(k)\Re(\eta) + \Im(k)\Im(\eta)
\right ) \int_{\Gamma} |\bu|^{2} dS  \right)
\, .
\end{align*}
Because all of the quantities in the last expression above are
nonnegative, we have that
\begin{equation}
  \int_{\Gamma} |\bu|^{2} = 0 \implies \bu = 0  \quad \xx \in \Gamma \, .
  \nonumber
\end{equation}
The result then follows from the uniqueness of solutions to the exterior
Dirichlet problem.
\qed
\end{proof}

\subsection{The integral equations and their null-spaces}

\begin{figure}
\begin{center}
\includegraphics[width=0.4\textwidth]{mc_dom}
\end{center}
\caption{Example of a multiply connected domain with four obstacles.}
\label{fig:mc_dom}
\end{figure}

In this section, we establish the correspondence between
Stokes eigenvalues and the invertibility of certain integral
equations arising from layer potential representations
of solutions to the oscillatory Stokes equation.

Let $\Omega$ be a bounded domain given as
the intersection of a simply connected domain $\Omega_0$ and
the exteriors of a finite collection of bounded,
simply connected domains $\{ \Omega_i \}_{i=1}^m$
whose closures are contained in $\Omega_0$;
see \cref{fig:mc_dom} for an example with four inclusions.
Note that the
exterior of $\Omega$, which we denote by $E$, is the
disjoint union of the exterior of $\Omega_0$, which we
denote $E_0$, with the sets $\{ \Omega_i \}_{i=1}^m$.
Let $\Gamma$ denote the boundary of $\Omega$ with the normal
$\bnu$ pointing out of $\Omega$.
We will use superscript $+$ and $-$ signs
to indicate the limit values of a function on $\Gamma$
as approached from the exterior and interior, respectively.

For the sake of brevity, we consider only the
Dirichlet eigenvalue problem but a similar analysis
could be applied to the Neumann eigenvalue problem.
We analyze two different representations for the
Dirichlet problem: a double layer potential,
i.e. setting $\bu=\bD_{k} \bmu$, and a combined-field
layer potential, i.e. setting
$\bu=(i\eta \bS_{k} + \bD_{k})\bmu$. 
While both representations result in a second-kind
integral equation for the oscillatory Stokes Dirichlet
problem, the double layer potential has spurious non-trivial
nullspaces on domains with positive genus, as
explained below.

\begin{remark}
  The application of the Fredholm alternative here
  again follows the structure used for the Laplace
  eigenvalue problem in~\cite[Ch. 3]{colton1983integral}.
\end{remark}

\subsubsection{Dirichlet eigenvalues --- double layer
  representation}
\label{subsec:dlanalysis}
Suppose that the solution to the oscillatory
Stokes Dirichlet problem, \cref{eq:dir_interior},
is represented using a double layer potential defined
on $\Gamma$, i.e. setting $\bu = \bD_{k} \bmu$ where
$\bmu$ is an unknown density. 
Substituting this expression
into the boundary condition and applying
\cref{lem:jump-conds}, we obtain

\begin{equation}
  (\cI - 2\cD_{k}) \bmu = -2\ff \; . \label{eq:inteq_dir_int}
\end{equation}

The rank deficiency of $\cI-2\cDk$ is
well-known~\cite{biros2002embedded} and we summarize it
in the lemma below.

\begin{lemma}
  \label{lem:nunull} In the notation above,
  $\bnu \in \cN(\cI - 2\cDkt)$.
\end{lemma}
\begin{proof}
From~\cref{lem:propnullspacecorr}, we note that
$W[(\cI - 2\cD_{k})\bmu] =0$ implies that
$\left<(\cI -2\cD_{k})\bmu ,\bnu \right> = 0$ for
all $\bmu$, i.e. $\bnu \in R(\cI - 2\cD_{k})^{\perp}$, where
$R(A)$ denotes the range of the operator $A$. 
By the Fredholm alternative, the result then follows.
\qed
\end{proof}
Thus, we instead analyze the equation
\begin{equation}
(\cI - 2\cD_{k}  -2\cW) \bmu = -2\ff \; \, . \label{eq:inteq_dir_int_mod}
\end{equation}
Note that if $\ff$ satisfies the compatibility
condition $\int_\Gamma \ff \cdot \bnu \, dS =0$, then
\cref{eq:inteq_dir_int_mod} implies \cref{eq:inteq_dir_int}.

On simply connected domains, there is a one-to-one correspondence between
the eigenvalues of the Dirichlet problem for
the Stokes equation
and the values of $k$ for which the operator $(\cI - 2\cD_{k} - 2\cW)$
is not invertible. To prove this, we also need the 
following lemma:
\begin{lemma}
  \label{lem:nutracli}
  If $\bt^{-}$ is the surface traction associated
  with an interior Dirichlet Stokes eigenfunction $\bu$,
  then $\bt^{-}$ and $\bnu$ are linearly independent.
\end{lemma}
\begin{proof}
We first note that $\bS_{k}[\bnu](\bx) = 0$ for all $\bx \in \Omega$.
This follows from an application of the divergence
theorem and the fact that
oscillatory Stokeslet is divergence free in $\Omega$. 
If $\bt^{-}$ is a surface traction associated with
a Stokes eigenvalue, then
using Green's theorem, it follows that
$\bS_{k}[\bt^{-}](\bx) = \bu(\bx) \neq 0$ for $\bx \in \Omega$ and
thus $\bt^{-}$ and $\bnu$ are linearly independent.
\qed
\end{proof}

\begin{theorem}
\label{thm:dlmain}
Suppose that $\Omega$ is a bounded, simply connected domain
{\color{red} and that $\Im (k) \geq 0$}. Then, the operator
$(\cI - 2\cD_{k} - 2 \cW)$ is not invertible if and only if $k^2$ is a
Dirichlet eigenvalue for the Stokes equation on $\Omega$.
\end{theorem}
\begin{proof}
  Suppose that $k^2$ is not a Dirichlet eigenvalue for
  the Stokes equation on
$\Omega$. 
Suppose further that $\bmu$ satisfies
\begin{equation}
(\cI - 2\cD_{k} - 2\cW) \bmu = 0 \, , \label{eq:dlproofrep}
\end{equation}
i.e. $\bmu$ is in the null-space
of $(\cI - 2 \cD_{k} - 2 \cW)$. 
Applying the operator $\cW$ to~\cref{eq:dlproofrep} and 
using~\cref{lem:propnullspacecorr}, we get
\begin{equation}
0 = \cW [(\cI - 2\cD_{k} - 2\cW)\bmu] = -2\cW [\bmu] \, .
\end{equation}
Thus~\cref{eq:dlproofrep} reduces to
\begin{equation}
(\cI - 2 \cD_{k})\bmu = 0\, .
\end{equation}
Suppose now $\bu = -2\bD_{k}[\bmu]$ in $\Omega$.
Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
and applying~\cref{lem:jump-conds}, we get that the interior
limit of the velocity $\bu^{-}=(\cI - 2\cD_{k}) \bmu = 0$
on $\Gamma$. Since $k^2$ is not a Dirichlet eigenvalue for the Stokes
equation on $\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
In particular, this implies that the interior limit of the surface traction
denoted by $\bt^{-} = 0$ on $\Gamma$. 
Using~\cref{lem:jump-conds} again, we conclude that the exterior limit
of the surface traction, $\bt^{+}$, is $0$ on $\Gamma$. 
Note that $\bu$ is a radiating solution of the oscillatory
Stokes equation in the exterior $E$, as $\cW[\bmu] = 0$ implies
$\int_{\Gamma} \bmu \cdot \bnu = 0$.
From the uniqueness of solutions to the exterior Neumann problem, 
we conclude that $\bu \equiv 0$ in $E$ as well,
which in particular implies that
the exterior limit of the velocity, $\bu^{+}$, is $0$ on $\Gamma$.   
Using the jump conditions in~\cref{lem:jump-conds} again, we
get that $2\bmu = \bu^{-} - \bu^{+} = 0$.
Thus $(\cI - 2\cD_{k} - 2\cW)$ is invertible if $k^2$
is not a Dirichlet eigenvalue for the Stokes equation on $\Omega$.

To prove the converse, note that from \cref{thrm:rep-theorem} we have 
  \begin{equation} 
    \bS_{k} [\bt](\xx) - \bD_{k}[\bu](\xx) = \begin{cases} 
    \bu(\xx) &\quad \xx \in \Omega \, , \\
    0 &\quad \xx \in E \; .
    \end{cases}
  \end{equation}
  Suppose that $k^2$ is a Dirichlet eigenvalue for the Stokes equation
  on $\Omega$ and let $\bu$ denote the corresponding eigenfunction
  with $\bt^{-}$ the corresponding surface traction on the
  boundary $\Gamma$.
  Since $\bu$ is a Dirichlet eigenfunction, the velocity restricted
  to the boundary, $\bu^{-}$, is $0$. 
  Using the Green's theorem representation for the pair
  $(\bu,\bt^{-})$ and evaluating the surface traction
  using~\cref{lem:jump-conds}, we get
  \begin{equation}
    \bt^{-} = \left(\cDt_{k} + \frac{1}{2} \cI\right) \bt^{-} \,
    \implies \left(\cI - 2\cDt_{k} \right) 
    \bt^{-} = 0 \, .
  \end{equation}
  From the above and \cref{lem:nunull,lem:nutracli},
  we know that $\bt^{-}, \bnu \in \cN(\cI - 2\cDt_{k})$
  are two linearly independent vectors in the null space.
  Let $c = \left< \bt^{-},\bnu \right>$. Then, it
  follows that $\left<\bt^{-} -c \bnu, \bnu \right> = 0$
  and thus $\cW[\bt^{-} - c\bnu] = 0$. 
  Since $\bt^{-}$ and $\bnu$ are linearly independent, we note that
  $\bt^{-} -c\bnu \neq 0$. Combining these results, we get that
  $(\cI - 2\cDt_{k} - 2\cW) (\bt^{-} - c\bnu) = 0$. 
  Since $\bt^{-}-c\bnu$ is non-trivial, and $\cW$ is
  self-adjoint, it follows from the Fredholm alternative
  that the operator $\cI - 2\cD_{k} - 2\cW$ is also not
  invertible.
\qed
\end{proof}

The correspondence result above does not hold on multiply
connected domains.
In particular, while the operator $\cI -2\cD_{k} -2\cW$ 
is indeed not invertible when $k^2$ is a Dirichlet eigenvalue,
it turns out that the operator is also not
invertible when $k^2$ is a Neumann eigenvalue
corresponding to the interior of one of the obstacle regions,
i.e. one of the $\Omega_{i}$ with $i > 0$. The following theorem
proves this result for a region with one obstacle;
the extension to the general case is straightforward.

\begin{theorem}
  Suppose that $\Omega$ is a multiply connected domain
  given by the intersection of a domain $\Omega_{0}$
  and the exterior of a single domain $\Omega_{1}$ with
  $ \bar\Omega_1 \subset \Omega_0$.
  Then, the operator $\cI - 2\cD_{k} - 2\cW$ is not invertible
  if $k^2$ is a Neumann eigenvalue of $\Omega_{1}$.
\end{theorem}

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.3\linewidth]{multiply_final}
%\end{center}
%\caption{Example of a multiply connected domain with one obstacle.}
%\label{fig:1ply}
%\end{figure}

\begin{proof}
  Suppose that $k^2$ is a Neumann eigenvalue of $\Omega_{1}$, and
  let $\tilde{\bu}$ denote the corresponding eigenfunction. 
  Note that $\tilde{\bu}$ is not identically $0$ on the boundary
  of $\Omega_{1}$, which we denote by $\Gamma_1$.
  Since $\tilde{\bu}$ is an interior Neumann eigenfunction, we note that
  the surface traction corresponding to the solution, $\bt^{-}$, is $0$
  on the boundary.
  Applying \cref{thrm:rep-theorem} to the
  solution $\tilde{\bu}$ in the interior
  and taking the interior limit we get
\begin{equation}
\tilde{\bu} = \frac{1}{2}\tilde{\bu} + \cD^{\Gamma_{1}}_{k}[\tilde{\bu}] +
\cS^{\Gamma_{1}} [\bt^{-}] \implies \frac{1}{2} \tilde{\bu} - \cD^{\Gamma_{1}}_{k}[\tilde{\bu}]
= 0\, .
\end{equation}
Note that the sign of the $\bD$ operator in the
representation theorem is switched since the normal
is pointing inwards for the boundary $\Omega_{1}$.
Thus, $\tilde{\bu}$ is a non-trivial null vector of the operator 
$\frac{1}{2}\cI - \cD^{\Gamma_{1}}_{k}$. 
Furthermore since $\tilde{\bu}$ is the boundary data of 
the solution of the oscillatory Stokes equation
in $\Omega_{1}$, we get that $\cW^{\Gamma_{1}}[\tilde{\bu}] = 0$.
Setting $\bmu = \tilde{\bu}$ on $\Gamma_{1}$, and
$\bmu = 0$ on $\Gamma_{0}$, we obtain a non-trivial null
vector for the operator $\cI - 2\cD^{\Gamma}_{k} -2\cW^{\Gamma}$
on the boundary $\Gamma = \Gamma_{0} \cup \Gamma_{1}$.
\qed
\end{proof}

The spurious eigenvalues of the operator $\cI-2\cDk-2\cW$
are demonstrated in \cref{subsec:spurannulus} on an annulus,
where both the true and spurious eigenvalues can be
determined analytically. 
Analogous with the observation in~\cite{zhao2015robust},
this lack of one-to-one correspondence between
the invertibility of the integral operator $\cI - 2\cD_{k} - 2\cW$
and the Dirichlet eigenvalues of the Stokes operator on multiply
connected domains also causes non-robustness and introduces
near-resonances for simply-connected domains which are almost
multiply-connected.
%We demonstrate this issue numerically
%in~\cref{subsec:crescent}.

\subsubsection{Dirichlet eigenvalues --- combined-field representation}
\label{subsec:mixedanalysis}

The non-robustness in using the double layer
potential representation can be
remedied by using a combined-field, or mixed layer potential,
representation, i.e. setting $\bu = (\bD_{k} + i\eta \bS_{k})
\bmu$, with $\eta$ real and positive.
Imposing the Dirichlet boundary condition
and using~\cref{lem:jump-conds}, we obtain 
\begin{equation}
  (\cI - 2\cD_{k} - 2i\eta \cS_{k}) \bmu = -2 \ff \,
  \textrm{ on } \Gamma. 
\end{equation}
As with the double layer representation, this
integral equation is rank deficient for any $k$.
Instead, we consider
\begin{equation}
(\cI - 2\cD_{k} -2i\eta \cS_{k}  -2\cW)\bmu = -2 \ff \, .
\end{equation}

We now prove that for any bounded region $\Omega$
(simply or multiply connected) with $C^{2}$ boundaries,
there exists a one-to-one correspondence between the
invertibility of the operator $\cI - 2\cD_{k}
- 2i\eta \cS_{k} - 2\cW$ and the Dirichlet eigenvalues.

\begin{theorem}
  \label{thm:cfmain}
  Suppose that $\Omega$ is a bounded region defined
  by the intersection of a simply connected domain $\Omega_{0}$
  and the exteriors of a finite collection bounded simply
  connected domains $\{ \Omega_{i} \}_{i=1}^{m}$ {\color{red}
    and that $\Im (k) \geq 0$}. As above,
  let $\Gamma_{i}$ denote the boundary of $\Omega_{i}$ and let
  $\Gamma = \cup_{i=0}^{m} \Gamma_{i}$ denote the boundary of
  $\Omega$. Then, the operator $\cI - 2\cD_{k} - 2i\eta \cS_{k}
  - 2\cW$ is invertible if and only if $k^2$ is not a Dirichlet
  eigenvalue for the Stokes operator on $\Omega$.
\end{theorem}

\begin{proof}
  Suppose that $k^2$ is not a Dirichlet eigenvalue for the
  Stokes equation on $\Omega$. Suppose further that $\bmu$ satisfies
  \begin{equation}
    (\cI - 2\cD_{k} -2i\eta\cS_{k} - 2\cW) \bmu = 0 \, ,
    \label{eq:mlproofrep}
  \end{equation}
i.e. $\bmu$ is in the null-space
of $(\cI - 2 \cD_{k} - 2i\eta \cS_{k} - 2 \cW)$. 
Applying the operator $\cW$ to~\cref{eq:mlproofrep} and 
using~\cref{lem:propnullspacecorr}, we get
\begin{equation}
0 = \cW [(\cI - 2\cD_{k} - 2i\eta\cS_{k} - 2\cW)\bmu] = -2\cW [\bmu] \, .
\end{equation}
Thus~\cref{eq:mlproofrep} reduces to
\begin{equation}
(\cI - 2 \cD_{k} - 2i\eta \cS_{k})\bmu = 0\, .
\end{equation}
Suppose now $\bu = -2\bD_{k}[\bmu] -2i\eta\bS_{k}[\bmu]$
in $\Omega$. Then $\bu$ is a solution to the oscillatory
Stokes equation in $\Omega$, and applying~\cref{lem:jump-conds},
we get that the interior limit of the velocity
$\bu^{-} = (\cI - 2\cD_{k} -2i\eta\cS_{k}) \bmu = 0$ on $\Gamma$.
Since $k^2$ is not a Dirichlet eigenvalue for the Stokes equation
on $\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
This in particular implies that the interior limit of the
surface traction, denoted by $\bt^{-}$, is $0$ on $\Gamma$.

Using~\cref{lem:jump-conds} we observe that $\bt^{+}
= 2i\eta \bmu(\xx)$ and $\bu^{+} = -2\bmu(\xx)$ on $\Gamma$, i.e.
$\bt^{+}+i\eta \bu^{+}=0$ and $\bu^{+}$ satisfies the homogeneous
exterior impedance problem.
We first show that $\bmu=0$ on $\Gamma_{0}$. 
To this end, note that $\bu$ is a radiating solution
of the oscillatory Stokes equation in the exterior $E$,
since $\cW[\bmu] = 0$ implies that $\int_{\Gamma} \bmu
\cdot \bnu = 0$. From the uniqueness of the impedance problem
in the exterior $E_0$ of $\Omega_0$, we conclude that
$\bu \equiv 0$ in $E_0$ as well, which in particular
implies that $\bu^{+}=0$ on $\Gamma_{0}$.   
Using the jump conditions in~\cref{lem:jump-conds}
again, we get that
$2\bmu = \bu^{-} - \bu^{+} = 0$ on
$\Gamma_{0}$.

\begin{remark}
  Note that there is potential for confusion here
  in that the exterior limit with respect to $\Omega$ 
  for the boundary $\Gamma_{j}$ is the traditional interior 
  limit with respect to the obstacle region $\Omega_{j}$.
\end{remark}

To show that $\bmu=0$ on
$\Gamma_{j}$, we observe that $\bu$ is also a
solution to the oscillatory Stokes equation in each
of the obstacles $\Omega_{j}$.
Using the jump conditions in~\cref{lem:jump-conds},
we get that $\bt^{+} = 2i\eta \bmu$ and $\bu^{+} = -2\bmu$.
However, the normal is inward pointing inside $\Omega_{j}$
on the boundary $\Gamma_{j}$. 
If we revert back to the normal being defined as 
an outward normal to $\Omega_{j}$, then
the boundary conditions on $\Gamma_{j}$ 
is $\bt - i \eta \bu = 0$. 
From the uniqueness of solutions to the interior 
impedance problem, we conclude that $\bu \equiv 0$
in $\Omega_{j}$, which in particular implies
that $2\bmu = \bu^{-}-\bu^{+} = 0$ for $\xx \in \Gamma_{j}$,
$j=1,2,\ldots m$.
Thus, $\cI - 2\cD_{k} -2i\eta\cS_{k} -2\cW$ is
invertible when $k^2$ is not a Dirichlet eigenvalue
for the Stokes equation on $\Omega$.

From \cref{thrm:rep-theorem}, we have 
\begin{equation} 
  \bS [\bt](\xx) - \bD[\bu](\xx) = \begin{cases} 
    \bu(\xx) &\quad \xx \in \Omega \, , \\
    0 &\quad \xx \in \R^2 \setminus \bar{\Omega} \; .
    \end{cases}
  \end{equation}
Suppose that $k^2$ is Dirichlet eigenvalue for
the Stokes equation on $\Omega$ and let $\bu$
denote the corresponding eigenfunction and $\bt$ denote
its surface traction. Note that \cref{thrm:rep-theorem}
implies that $\cS_{k}[\bt^{-}] = 0$, since
$\bu^{-}=0$ on $\Gamma$. Applying \cref{thrm:rep-theorem}
to the pair $\bt^{-}, \bu^{-}$ and evaluating the
traction on $\Gamma$ using~\cref{lem:jump-conds},
we get
\begin{equation}
\bt^{-} = (\cDt_{k} + \frac{1}{2} \cI) \bt^{-} \, . 
\end{equation}
Combining these two identities, we get
that
\begin{equation}
(\cI - 2\cDkt -2i\eta \cS_{k}) \bt^{-} = 0 \, .
\end{equation}
As in the proof of~\cref{thm:dlmain}, letting
$c = \left< \bt^{-} ,\bnu \right>$, it follows that
\begin{equation}
  (\cI - 2\cDkt - 2i \eta \cS_{k} - 2\cW)
  (\bt^{-} - c\bnu) = 0 \, ,
\end{equation}
where $\bt^{-} - c\bnu \neq 0$.
Since $\bt^{-} - c\bnu$ is non-trivial and both
$i\eta \cS_{k}$ and $\cW$ are self-adjoint with respect
to the bilinear form \cref{eq:bi_form},
it follows from the Fredholm alternative
that the operator $\cI - 2\cDk -2i\eta \cSk - 2\cW$
is also not invertible.
\qed
\end{proof}

\begin{remark}
  The results above hold provided that ${\rm Im}(k) \geq 0$.
  There are indeed values of $k$ with ${\rm Im}(k) < 0$ such
  that $k^2$ is not an eigenvalue of the Stokes operator but
  the boundary integral equations above are not invertible.
  In practice, these values can be returned by the root finding
  method described in the following sections as potential
  eigenvalues. In the experiments below, such values were easy to
  identify, having imaginary parts which are several orders
  in magnitude larger than the imaginary parts for roots
  corresponding to non-spurious $k$.
\end{remark}

\subsection{Fredholm determinants}
\label{sec:dets}
In this section, we show
how the Fredholm determinant can be used
as a computational tool for detecting the
non-invertibility of $\cI - 2\cD_{k} - 2\cW$.
The arguments here follow the structure of the
analogous arguments in~\cite{zhao2015robust}
for Laplace eigenvalues.

Let $\cJ_{1}(X)$ denote the space of trace class operators 
on $X$, where $X$ is a Hilbert space, which is a
subspace of the space of compact operators on $X$.
A compact operator $\cA$ with eigenvalues
$\lambda_{i}, i\in \mathbb{N}$ is in $\cJ_{1}(X)$ if
$\sum_{i} |\lambda_{i}| < \infty$.
If $\cA$, is a trace class operator, then  
the Fredholm determinant of the operator $\cI + \cA$
is defined by
\begin{equation}
\text{det}(\cI +\cA) = \prod_{i=1}^{\infty} (1+\lambda_{i}) \, .
\end{equation}

So far, we have discussed the Fredholm theory in the space
$C(\Gamma)\times C(\Gamma)$ equipped with the bilinear form~\cref{eq:bi_form}.
However, it is more convenient to discuss the theory of Fredholm
determinants on Hilbert spaces. 
We note that both the operators $\cD_{k}$ and $\cS_{k}$ 
are also compact operators mapping $Y \to Y$
where $Y = \mathbb{L}^{2}(\Gamma) \times \mathbb{L}^{2}(\Gamma)$.
Furthermore, it is well-known that the spectrum of compact
operators with weakly singular kernels coincide on 
$C(\Gamma)\times C(\Gamma)$ and $Y$ (see~\cite{kress1989linear},
for example).
So for the rest of the section, we present the discussion of 
the relevant operators on $Y$ instead of $C(\Gamma)\times C(\Gamma)$.

%It follows from standard results in complex
%analysis, that the Fredholm determinant is finite and well-defined if 
%$\text{det}(\cI+A) < \infty$ if $\sum_{i} |\lambda_{i}| < \infty$,
%i.e. if $A$ is in trace class.

The operator $-2\cD_{k} - 2\cW$ is trace class:
\begin{lemma}
  Suppose that $\Gamma$ is a $C^2$ curve.
  Then $-2\cD_{k} - 2\cW \in \cJ_1(Y)$
  for all $k \in \mathbb{C} \setminus \{0\}$ 
\end{lemma}
\begin{proof}
Using Bessel function asymptotics, we note that the
kernel of $\cD_{k}$ given by $\TT_{\cdot,\cdot,\ell}\nu_{\ell}(\bx,\by)$
has a leading order singularity of
$|\bx-\by|^2 \log{|\bx-\by|^2}$ as $\bx\to \by$ 
for all $k \in \mathbb{C} \setminus \{ 0\}$.
It follows from the criteria listed
in~\cite[Sec. 2]{bornemann2010numerical} that $\cD_{k}$
is a trace-class operator.
Since $\cW$ is a rank-one perturbation independent of $k$,
and trace-class operators are a vector space, we conclude
that $-2\cD_{k} - 2\cW$ is also a trace-class operator.
\qed
\end{proof}

Let $f(k) = \text{det}(\cI - 2\cD_{k} - 2\cW)$.
First, note that $f(k)$ is an analytic function of $k$
for $k \in \mathbb{C} \setminus \{0 \}$, since the kernel
of $\cD_{k}$ is an analytic function of $k$ on that domain, 
and the Fredholm determinant of an analytic operator 
is analytic on the domain of analyticity
of the operator (see~\cite{zhao2015robust}, for example).

The zeros of the Fredholm determinant indicate when the
operator is not invertible.
The following lemma summarizes this result.
\begin{lemma} \label{lem:detzeros}
  With $f(k)$ defined as above, $f(k) = 0$ if and only if
  $\cI - 2\cD_{k} -2\cW$ is not invertible.
\end{lemma}
\begin{proof}
  The proof is standard; see, for example,
  \cite[p. 34]{simon2005trace}.
\qed
\end{proof}

When $\Omega$ is simply connected, \cref{lem:detzeros} and 
\cref{thm:dlmain} together imply that $f(k) = 0$
if and only if $k^2$ 
is a Dirichlet eigenvalue of the Stokes equation.
This reduces the problem of finding eigenvalues to
finding the roots of an analytic function.

We now show how this fact can be used to numerically
estimate the Dirichlet eigenvalues.
Suppose that $D_{k}^{N}$ is a Nystr\"{o}m discretization 
of the operator $-2\cD_{k} - 2\cW$ when the boundary 
$\Gamma$ is discretized with $N$ points. 
Let $f^{N}(k) = \text{det}(I + D_{k}^{N})$
where here $\text{det}$ is the standard matrix determinant.
Note that the discretized matrix also depends on the choice
of quadrature rule used in the Nystr\"{o}m discretization
of the operator.

In~\cite{zhao2015robust}, the authors prove that
for computing the Laplace eigenvalues on regions with 
analytic boundaries, when the integral operators are
discretized using Kress quadrature --- a spectrally accurate
quadrature rule for such kernels, see~\cite{kress1991boundary} ---
the determinant of the Nystr\"{o}m discretized operators
at the true eigenvalues converge to $0$ exponentially
in $N$.
Thus, if the eigenvalues have multiplicity $1$,
i.e. the derivative of the determinant is non-zero
at the true-eigenvalues, then the analyticity of the
discretized determinant implies that the zeros
of the determinant of the Nystr\"{o}m discretization
of the linear operator converge exponentially to
the true Dirichlet eigenvalues for Laplace's equation.

The proof presented in~\cite{zhao2015robust} applies
to the BIE approach for computing the Dirichlet eigenvalues
of the Stokes operator as well.
The result is summarized below.
\begin{theorem}
\label{thm:mainconvfreddet}
Suppose that $\Omega$ is a simply connected
domain with an analytic boundary. Let $k_{j}^2$, $j=1,2,\ldots M$
denote all the Dirichlet eigenvalues of Stokes equation
on $\Omega$ contained in the interval $[a,b]$. 
Suppose further that all the eigenvalues have multiplicity $1$.
Let $f^{N}(k) = \text{det}(I+D^{N}_{k})$, where $D^{N}_{k}$ 
is the Nystr\"{o}m discretization of $-2\cD_{k} - 2\cW$ with Kress
quadrature.
Then there exists $N_{0} \in \mathbb{N}$ such
that for all $N>N_{0}$, 
$f^{N}(k)$ has exactly $M$ zeros on the interval $[a,b]$.
Let $\omega_{j}$, $j=1,2\ldots M$ denote the zeros of $f^{N}$.
Furthermore, there exist constants $a>0$ and $C$, 
such that $\sup_{j=1}^{M} |\omega_{j} - k_{j}| < C e^{-aN}$.
\end{theorem}

\begin{proof}
  The proof follows from small modifications of the
  proofs contained in~\cite{zhao2015robust}. 
\qed
\end{proof}

\begin{remark}
In practice, using Kress quadrature for large
problems is problematic owing to the global
nature of the quadrature rule.
%
First, the use of a global rule does not allow
for adaptive refinement at a complicated, local
feature of the boundary.
%
Second, the integration weight in each entry
of the matrix depends on both the column and the row
in a non-separable way.
%
As a result, the fast multipole method is not
directly applicable to the resulting matrix
and many fast-direct methods for computing
the determinant lose efficiency (for
instance, the reasoning behind the use of a
{\em proxy surface} \cite{cheng2005compression}
no longer holds).
Over the last two decades, many high-order quadrature
methods which are compatible with
the fast multipole method and fast-direct methods
have been developed.
%
Our numerical experiments, see \cref{subsec:convannulus},
suggest that the zeros of the 
determinants of linear systems discretized using 
these quadrature methods are also high order approximations
of Dirichlet eigenvalues for the Stokes operator ---
the error is observed to be proportional to the quadrature error
for the eigenfunction $\bt^{-}$ associated with the eigenvalue.
We leave a proof of this to future work.
\end{remark}

\begin{remark}
The same analysis does not carry through for the operator
$\cI - 2 \cD_{k} - 2i\eta \cS_{k} - 2\cW$, 
since $\cS_{k}$ is not a trace class operator.
For brevity, let $\cC_{k} = -2\cD_{k} - 2i\eta \cS_{k} - 2\cW$.
The operator $\cC_{k}$ is 
in $\cJ_{2}(Y)$ where
$\cJ_{2}(Y)$ is the space of Hilbert-Schmidt operators
on $Y$ (the singular values of the operator are square
summable, as opposed to being summable).
Thus the Fredholm determinant of $\cI + \cC_{k}$
is not necessarily finite. 
However, as noted in~\cite{zhao2015robust}, the convergence
result~\cref{thm:mainconvfreddet}
should be true up to a logarithmic factor in the rate
of convergence, since the singular values of the operator
$\cC_{k}$ decay like $\frac{1}{n}$, and the
Fredholm determinant diverges logarithmically. 
In~\cref{subsec:convannulus}, we demonstrate this fact
numerically on the annulus, where the eigenvalues are
analytically known. 
\end{remark}

% flatex input end: [03analysis.tex]

%
% flatex input: [04numerical.tex]
\section{Numerical Results}
\label{sec:numerical}

In this section, we demonstrate the analytical
claims above with numerical examples and
highlight the performance of the BIE approach
with demonstrations on domains of analytical
and practical interest. The software used to
generate the figures is available online
\footnote{\texttt{https://doi.org/10.5281/zenodo.2641296}}.

\subsection{Numerical methods}

First, we describe the numerical tools needed
to compute Stokes eigenvalues in a BIE
framework.

\subsubsection{Discretizing the BIE}

In order to turn the BIEs analyzed
above into discrete linear systems,
we require some standard techniques
from the BIE literature.

Let the boundary be divided into $N_p$
panels.
%
We parameterize panel $j$ as
$\bx_j(t)$, with $t$ ranging over the
interval $[-1,1]$.
%
Each component of $\bx_j$ is taken to be
a polynomial interpolant over the
standard 16th-order Legendre nodes on
$[-1,1]$, denoted by $t_n$, so that
the total number of discretization
points is $N=16N_p$.
%
See \cref{fig:panels} for an example
discretization.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{annulus_discretization.pdf}
\caption{Sample discretization of an annulus, where the inner
circle, $r=1$ is discretized using $6$ panels and the outer circle $r=1.7$
is discretized using $10$ panels.}
\label{fig:panels}
\end{figure}
%
Another important quantity below is the
arc-length density of a panel, which
we denote by $s_j(t) := |\bx'_j(t)|$.
%
Finally, we denote the set of panels
which are adjacent to panel $j$
by $A(j)$. On a closed curve,
$A(j)$ contains two integers.

The integral kernels of the single and
double layer potentials have weak
singularities of the form $|\xx-\yy|^p\log |\xx-\yy|$
for some $p \in \N_0$, which require special
quadrature rules to achieve high-order accuracy.
%
In the examples below, we use generalized
Gaussian quadrature (GGQ)~\cite{bremer2010}.
%
To demonstrate the idea, we consider
evaluating the convolution of a kernel
$K$ with a density $\sigma$
at the boundary node $\xx_j(t_l)$.
%
GGQ is a Nystr\"{o}m-type discretization ---
the density is approximated 
by its values at the discretization nodes,
which we denote by
$\sigma_{qp} := \sigma(\xx_q(t_p))$.
%
The basis of a GGQ rule is a set of 
support nodes and weights for the
contribution to the integral from the
``self'' panel (panel $j$) and the adjacent
panels (with index in $A(j)$).
%

For the self panel, there is a special set
of nodes and weights for each interpolation
point. Denote the nodes and weights
for interpolation point $l$ by $t^{(l)}_{n}$
and $w^{(l)}_{n}$, respectively, with
$1\leq l \leq 16$ and $1\leq n \leq N_s$.
%
The adjacent panels are handled by a single
set of over-sampled support nodes and weights.
We denote these nodes and weights
by $\tilde{t}_n$ and $\tilde{w}_n$, respectively,
for $1 \leq n \leq N_a$.
%
For the 20th-order rule we used, $N_s = 16$ and
$N_a = 48$. 
%
The contribution of other panels is assumed
to be given to high accuracy by the standard
Gauss-Legendre weights, which we denote
by $w_n$.
%
Adding these contributions together, we obtain the
quadrature

\begin{multline}
  \int_\Gamma K(\xx_i(t_l),\yy) \, \sigma(\yy)
  \, dS(\yy) \approx \\
  \sum_{p=1}^{16} \sum_{n=1}^{N_s}
  w^{(l)}_{n} K(\xx_i(t_l),\xx_i({t}^{(l)}_{n}))
  s_i({t}^{(l)}_{n}) B^{(l)}_{np} \sigma_{ip} \quad \textrm{(self)}
  \\
  + \sum_{q\in A(i)} \sum_{p=1}^{16} \sum_{n=1}^{N_a}
  \tilde{w}_jK(\xx_i(t_l),\xx_q(\tilde{t}_n)) s_q(\tilde{t}_n)
  C_{np} \sigma_{qp}
  \quad \textrm{(adjacent)} \\
  + \sum_{q\neq i, q\not\in A(i)} \sum_{p=1}^{16}
  w_p K(\xx_i(t_l),\xx_q(t_p)) s_q(t_p)
  \sigma_{qp} \quad \textrm{(far)} \nonumber \; ,
\end{multline}
where $\bB^{(l)}$ and $\bC$ are interpolation
matrices from the standard Legendre nodes
to the self and adjacent panel support nodes,
respectively. Observe that the quadrature is
linear in $\sigma_{qp}$. In practice, we pre-compute
and store the self and adjacent matrix entries for each
interpolation point, which is a parallelizable
$O(N)$ calculation. The ``far'' interactions
are computed on-the-fly.

\begin{remark}
  \label{rmk:levelrestrict}
  We ensure that ``far'' interactions
  are handled to high precision by requiring that
  no two adjacent panels differ in length
  by more than a factor of 2. On a domain which does
  not nearly self-intersect this
  guarantees that no ``far'' interactions occur
  which are much closer than 1/2 of a panel away
  (assuming panels are relatively flat).
  Because the location of the singularity is
  bounded away from the panel and the smooth
  rule is of high order, we obtain a quadrature
  rule with sufficient precision.

  The overall order of accuracy of the GGQ we use
  is 20th-order, up to the precision of the ``far''
  interactions.
\end{remark}

\subsubsection{Fast determinant method}

Once the discretization is set, we can form
a compressed representation of the system matrix
using recursive skeletonization~\cite{ho2012fast}.
%
We use the implementation of this procedure
included in the fast linear algebra in
MATLAB (\texttt{FLAM}) package
\cite{hoFLAM_1253582}.
%
At low-to-medium frequencies, the scaling
of the recursive skeletonization algorithm
is $O(N\log N)$ in operation count and
storage and, by using a generalization
of the Sylvester determinant formula,
allows for a fast determinant
calculation in $O(N\log N)$ time as a
follow-up step.
%
At higher-frequencies,
the recursive skeletonization procedure,
which is based on the assumption that off-diagonal
blocks of the matrix are of low rank,
breaks down and does not offer a speed advantage.
%
These algorithms take a precision parameter
$\epsflam$ which determines the
accuracy to which any sub-blocks of the matrix
should be compressed. In all experiments,
we set $\epsflam = 10^{-14}$.

The compressed representation also allows
for fast applications of the system matrix,
its transpose, the inverse of the system
matrix, and the inverse transpose to
vectors.
%
In particular, this allows us to estimate the
smallest singular values by performing
randomized subspace iteration, see
\cite[Algorithm 4.4]{halko2011finding},
on the inverse operator.
%
Below, we use the smallest singular value
as a measure of the quality of the
eigenvalues found by approximating the
roots of the determinant.
%
We also evaluate the second smallest singular
value to check for possible double eigenvalues.

\subsubsection{Interpolation and root-finding}

To estimate the eigenvalues, we fit a Chebyshev
interpolant to the discretized determinant as a
function of $k$ on intervals.
%
This is done adaptively so that the Chebyshev
coefficients of the determinant have decayed
to the point that the ratio of the last
coefficient to the largest coefficient is below
some threshold.
%
In all experiments, we set this threshold
as $\epscheb = 10^{-13}$.
%
We perform this fit using the \texttt{chebfun}
utility in the package of the same name
\cite{driscoll2014chebfun}
so that we can make use
of the \texttt{roots} utility to approximate
the roots of the determinant.

The \texttt{roots} utility returns the roots
of the polynomial in the complex plane, with
some minimal internal processing to remove
roots 
{\color{red}which are too far from the
  interval of interpolation to be accurate.
  After obtaining the output
  of \texttt{roots},
  we apply some further post-processing.
  The integral operators can
  have non-trivial nullspaces for some $k$ with
  $\Im(k) < 0$ which are spurious; as noted above,
  these correspond to eigenvalues of exterior
  problems. Further, the interpolant is computed
  on subintervals $[a,b]$ of the total interval
  of interest.
  Thus, we would like to limit our scope to
  those computed roots which are sufficiently
  close to the real interval $[a,b]$ --- this
  removes the spurious roots of large negative
  imaginary part and possible double
  counting of those roots found near a
  neighboring subinterval. Because we are working with
  Chebyshev interpolants, we measure
  distance from the interval in terms of
  Bernstein ellipses (see \cite{trefethen2013approximation};
  this is equivalent to the approach
  in \cite{zhao2015robust,barnettmpspack}).
  For the parameter $\rho$, the Bernstein ellipse
  $E_\rho$ is defined by

  $$ E_\rho = \left \{ z: \left(\frac{2\Re z}{\rho+1/\rho}
  \right )^2 + \left(\frac{2\Im z}{\rho-1/\rho}
  \right )^2  = 1 \right \} \; .$$
  Let $T$ be the linear transformation that
  maps $[a,b]$ to $[-1,1]$.
  We then keep only the roots such that
  $T(k_\cheb)$ is contained in the Bernstein
  ellipse $E_\rho$ with $\rho = 1+\sqrt{\epscheb}$.
  While it is still possible to obtain two copies
  of a root if it is almost equal to an
  endpoint of one of the subintervals,
  this was not observed in our experiments.
}

We can obtain an a posteriori estimate of the
error in a computed root as follows.
%
Let $f$ denote an analytic function,
$P$ be the polynomial interpolant
of that function over some interval,
$\delta f = f-P$ be the difference,
and $k_\cheb$ denote a computed root
of $P$ which is simple (i.e. assume
that $P'(k_\cheb) \ne 0$).
%
The algorithm used by \texttt{chebfun}
to approximate the roots of $P$ is
backward stable~\cite{noferini2017chebyshev}.
Therefore the error in the roots will be
small relative to the error of the fit and
we set $P(k_\cheb) = 0$ below.
%
Suppose that
$f(k_\cheb + \delta k) = 0$ for some
small $\delta k$. Then

\begin{align*}
  0 &= f(k_\cheb + \delta k) \\
  0 &= P(k_\cheb + \delta k) + \delta f(k_\cheb + \delta k) \\
  \delta k &= -\frac{\delta f(k_\cheb + \delta k)}{P'(k_\cheb)} + O(\delta k^2) .
\end{align*}
In practice, we can obtain an approximate upper
bound for $|\delta f(k_\cheb+\delta k)|$
as $\epscheb \|P\|_\infty$ so that $\epscheb \|P\|_\infty/
|P'(k_\cheb)|$ provides an approximate upper bound
for the error in the root.

{\color{red} It can be inferred from the above
  that the accuracy
  of root finding suffers for (nearly) multiple roots.
  In \cite{zhao2015robust}, when two eigenvalues
  are sufficiently close, the authors use a different
  algorithm based on minimizing
  the smallest singular value of the boundary integral
  operator with respect to $k$
  to better capture such eigenvalues.
  Such a technique is applicable here as well,
  but we found that the eigenvalues
  obtained from the procedure above were
  satisfactory, as measured by the lowest
  singular value of the corresponding
  boundary integral operator (as a check against
  spurious roots with negative imaginary part,
  we use the boundary integral operator corresponding
  to $k$ equal to the real part of a computed root). Further
  discussion on the quality of the computed eigenvalues can be
  found in \cite{zhao2015robust}. }

\subsection{Eigenvalues of an annulus}
We test our numerical machinery and validate our analytical 
and numerical claims
by comparing the results to the true eigenvalues on the annulus
which are known analytically (see~\cref{sec:annul_dir_exact}).
In all of the examples below, we work on the annulus $r_{1}<r<r_{2}$
with $r_{1} = 1$ and $r_{2} = 1.7$.
If the inner boundary is discretized using $N_{1}$ panels, 
then the outer boundary is discretized using $N_{2} = 
\lceil r_{2}/r_{1} N_{1} \rceil +1$ panels to ensure that the
panels are approximately the same length on both the boundaries. 
The total number of discretization points 
is then given by $N = 16(N_{1} + N_{2})$.
{\color{red}Let $D^{N}_{k}$ and $C^{N}_{k}$ denote the linear
  systems corresponding to the Nystr\"{o}m discretizations of
  $-2\cD_{k} -2\cW$ and $-2\cD_{k} - 2i\cS_{k} -2\cW$,
  respectively, using generalized Gaussian quadrature.}
Let $f_{D}^{N}(k) = \text{det}(I+D^{N}_{k})$, and 
$f_{C}^{N}(k) = \text{det}(I+C^{N}_{k})$.

\subsubsection{Convergence study}
\label{subsec:convannulus}
We demonstrate that 
for sufficiently large $N$, if $k_{0}$ is a Dirichlet 
eigenvalue of the annulus, 
then $f_{D}^{N}(k_{D}) = 0$ and $f_{C}^{N}(k_{C}) = 0$
where $|k_{D} - k_{0}| \lesssim N^{-20}$, 
and $|k_{C} - k_{0}| \lesssim N^{-20}$.
Recall that the GGQ we use has an expected order
of convergence of $N^{-20}$ for evaluating convolutions
with such integral kernels,
so that the error of the roots is observed to have the
same order as the quadrature rule.
In~\cref{fig:conv}, we show this result for $k_{0} = 13.48025717955055$
and plot the errors $|k_{D}-k_{0}|$ and $|k_{C}-k_{0}|$ as a function
of $N$.

\begin{figure}
  \centering
  \includegraphics[width=0.98\textwidth]{conv-studies.pdf}
  \caption{Convergence studies for the Dirichlet eigenvalues
  computed using the integral equations 
  $\cI - 2\cD_{k} - 2\cW$ (left) and
  $\cI - 2\cD_{k} - 2i \cS_{k} - 2\cW$ (right).}
  \label{fig:conv}
\end{figure}

\subsubsection{Spurious eigenvalues}
\label{subsec:spurannulus}
As noted in~\cref{subsec:dlanalysis},
if $k_{0}$ is a Neumann eigenvalue corresponding to the interior
inclusion, which in our case is the disk $r\leq r_{1}$, then
$f_{D}^{N}(k_{D}) = 0$ with $|k_{D}-k_{0}| = O(\varepsilon)$, even though $k_{0}$ 
is not a Dirichlet eigenvalue of the annulus, i.e.
the integral equation $-\cI - 2\cD_{k} -2\cW$ has a spurious eigenvalue.
In~\cref{fig:spur}, we demonstrate this result and also show that 
$f_{C}^{N}(k_{0}) \neq 0$, i.e., the combined field representation is
robust and invertible at all values of $k$ which are not the Dirichlet
eigenvalues of the annulus.

\begin{figure}
\centering
\includegraphics[width=0.98\linewidth]{det_spur.pdf}
\caption{The values of the discretized determinants $f_{C}^{N}(k)$ (left)
and $f_{D}^{N}(k)$ on the interval $k=[13,14]$ with $N=368$. The vertical
dotted line denotes the spurious eigenvalue $k_{0} = 14.79595178235126$ 
and $f_{D}^{N}(k_{D}) = 0$ with $|k_{D}-k_{0}|=6.8\times 10^{-12}$.
On the other hand $|f_{C}^{N}(k_{0})|=0.42$, and thus $\cI-2\cD_{k}-2i\cS_{k} 
-2\cW$ has no 
spurious eigenvalue in the neighborhood of $k=k_{0}$.}
\label{fig:spur}
\end{figure}

\subsubsection{Speed}
\label{subsec:speed}
In this section, we demonstrate the $O(N\log{N})$ scaling of evaluating
$f^{N}_{C}(k)$ as long as $N$ is large enough to resolve the interactions
at the Helmholtz parameter $k$. 
When $N$ is smaller than that, we observe a worse scaling since the
assumption that far-interactions are low-rank is no longer valid at
the tolerance of FLAM.
We plot the timing results corresponding to three different values of 
$k$ in~\cref{fig:speed}. The times are as recorded for a laptop with
16Gb of RAM and an Intel Core i7-6600U CPU at 2.60GHz with 4 cores.
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{speed_res.pdf}
\caption{Time taken $(t)$ in seconds to evaluate the determinant $f_{C}^{N}(k)$ as
a function of $N$ for three different values of $k$.}
\label{fig:speed}
\end{figure}

\subsection{Eigenvalues of a barbell-shaped domain}
\label{subsec:barbell}

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{ex_barbell_001_bdry}
    \caption{A barbell-shaped domain.}
    \label{subfig:barbell_bdry}
  \end{subfigure}
  ~
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{ex_many_holes_004_bdry}
    \caption{A domain with several inclusions.}
    \label{subfig:many_inclusions_bdry}
  \end{subfigure}
  \caption{Computational domains.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{barbell_gallery}
  \caption{Vorticity plots of the first 119 eigenfunctions
    of the barbell-shaped domain.}
  \label{fig:barbell_gallery}
\end{figure}

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{ex_barbell_001_sings_plot}
    \caption{Smallest singular value of the BIE operator.}
    \label{subfig:barbell_sings}
  \end{subfigure}
  ~
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{ex_barbell_001_coeffs_plot}
    \caption{Normalized Chebyshev coefficients of the
      determinant on 3 intervals in $k$.}
    \label{subfig:barbell_coeffs}
  \end{subfigure}
  \caption{Diagnostics for the first 119 barbell eigenvalues.}
  \label{fig:barbell_diagnostics}
\end{figure}

We consider the barbell-shaped domain in \cref{subfig:barbell_bdry}.
This domain is the union of a square of side-length 6,
a square of side-length 3, and a ``bridge'' connecting
them of height 1 and width 5/2.
%
For the sake of simplicity, we round the corners of the domain
to obtain a smooth object.
%
Applying the approach described in~\cite{epstein2016smoothed},
the corners of the domain are rounded by convolving with
the Gaussian kernel
\begin{equation}
  \nonumber
\phi(x) = \frac{1}{\sqrt{2\pi h}} e^{-x^2/(2 h^2)} \, ,
\end{equation}
with $h\approx 0.06$. This leaves the domain unperturbed
to high precision outside of a radius of $0.1$ around
each corner.
%
The eigenfunctions of such a domain display the well-known
localization property~\cite{trefethen2006computed}:
many of the eigenfunctions are approximately supported
within one of the squares.
%
We compute these eigenfunctions corresponding to
eigenvalues $k^2$ with $k$ in the range
$0.5 \leq k \leq 6.5$.

%
The panels are divided adaptively so that the smallest
panels in the rounded corners are smaller than $10^{-2}$,
which keeps the panels relatively flat.
%
This results in $N_p = 412$ after enforcing the
level-restriction property described in
\cref{rmk:levelrestrict}
and enforcing that no panel is larger than
one wavelength for the largest $k$
(here $\lambda=2\pi/6.5$).

As this is a simply-connected domain,
the eigenvalues are estimated by finding the values
$k$ for which $\cI-2\cDk-2\cW$ is non-invertible.
%
Let $f^N(k) = \det (\cI^N-2\cDk^N-2\cW^N)$.
To find the roots of $f^N(k)$, we fit a \texttt{chebfun}
representation of $f^N(k)$ on each of the intervals
$[j/2,(j+1)/2]$ for $j = 1,\ldots,12$.
%
We plot the absolute value of the Chebyshev coefficients
(normalized by the absolute value of the first coefficient)
of $f^N(k)$ on the intervals $[0.5,1.0]$, $[3.0,3.5]$,
and $[6.0,6.5]$ in \cref{subfig:barbell_coeffs}.
%
As expected, the coefficients decay exponentially
to zero, with more terms required at higher
frequencies.
%

We compute the roots of these Chebyshev interpolants
and apply the post-processing described above.
%
{\color{red}There were 119 real roots in the range $[0,6.5]$.}
%
We plot the smallest singular value of
$\cI^N-\cDk^N-2\cW^N$ for {\color{red}$k$ equal to the real part of}
each of these roots in \cref{subfig:barbell_sings}
and plot the vorticity of the eigenfunctions
in \cref{fig:barbell_gallery}.
%
The singular values suggest that the quality of the
eigenvalues is good.
From the plots, we see that localization occurs
until about the 100th eigenvalue.

%

%\subsection{Robustness on a nearly multiply connected domain}
%\label{subsec:crescent}

\subsection{Eigenvalues of a domain with several inclusions}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{many_inclusions_gallery}
  \caption{Vorticity plots of the eigenfunctions corresponding
  to the first 76 eigenvalues of a domain with several inclusions.}
  \label{fig:many_inclusions_gallery}
\end{figure}

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{ex_many_holes_004_sings_plot}
    \caption{Smallest singular value of the BIE operator
      corresponding to the first 76 eigenvalues of a
      domain with several inclusions.}
    \label{subfig:many_inclusions_sings}
  \end{subfigure}
  ~
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{ex_many_holes_004_coeffs_plot}
    \caption{Normalized Chebyshev coefficients of $f^N(k)$ on
      3 different intervals in $k$.}
    \label{subfig:many_inclusions_coeffs}
  \end{subfigure}
  \caption{Diagnostics for the eigenvalues of a domain
    with several inclusions.}
  \label{fig:many_inclusions_diagnostics}
\end{figure}

We now consider the multiply-connected domain in
\cref{subfig:many_inclusions_bdry}.
% 
The domain is defined by a smooth rectangular region
of width 3 and height 2,
with an array of randomly rotated ``starfish'' shapes
removed. 
%
Such shapes are of interest in
materials design, see, for instance, \cite{overvelde2012compaction}.
%
We compute the eigenfunctions corresponding to
eigenvalues $k^2$ with $k$ in the range
$3 \leq k \leq 9$ (this range includes the smallest
eigenvalue).

%
For this smooth shape, ensuring that no panel is
larger than one wavelength for the largest $k$
(here $\lambda=2\pi/9$) is sufficient to resolve
the object to high precision.
%
After enforcing the
level-restriction property described in
\cref{rmk:levelrestrict}, we end up with
$N_p = 224$.

As this is a multiply-connected domain,
the eigenvalues are estimated by finding the values
$k$ for which $\cI-2\cDk-2i\cSk-2\cW$ is non-invertible.
%
Let $f^N(k) = \det (\cI^N-2\cDk^N-2i\cSk^N-2\cW^N)$.
To find the roots of $f^N(k)$, we fit a \texttt{chebfun}
representation of $f^N(k)$ on each of the intervals
$[j/2,(j+1)/2]$ for $j = 6,\ldots,13$ and the intervals
$[j/4,(j+1)/4]$ for $j = 28,\ldots,35$.
%
It should be noted that, due to the relative sizes
of the domains,
this represents a lower frequency problem than
that for the barbell when measured in the number
of wavelengths across the object.
%
Thus, the use of a finer grid in frequency results from
the difficulty in resolving the Fredholm determinant
for this problem, which has a larger dynamical range
than that for the barbell.
%
We plot the absolute value of the Chebyshev coefficients
of $f^N(k)$ on the intervals $[3,3.5]$, $[6.5,7]$,
and $[8.75,9]$ in \cref{subfig:barbell_coeffs}.
%
As expected, the coefficients decay exponentially
to zero, with more terms required at higher
frequencies (note that the interval $[8.75,9]$ is
smaller than the others).
%

We compute the roots of these Chebyshev interpolants
and apply the post-processing described above.
%
There were 103 total roots: 21 were removed because
the imaginary part was too large and 6 pairs were found
with values within $\sqrt{\epscheb}$ of each other.
%
For these 6 pairs, none represented two distinct
eigenvalues or a double root.
%
This leaves 76 roots in the range $0\leq k \leq 9$.
%
We plot the smallest singular value of
$\cI^N-\cDk^N-2i\cSk^N-2\cW^N$ for {\color{red}$k$ equal to the real part of}
each of these roots in
\cref{subfig:many_inclusions_sings}
and plot the vorticity of the eigenfunctions
in \cref{fig:many_inclusions_gallery}.
%
In the vorticity plots, we observe a different type of
localization property than that seen in the barbell,
with many of the eigenfunctions
approximately supported in a small, connected subset
of the domain. This is consistent with other studies
\cite{filoche2009strong,lindsay2018boundary}.

%

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{ex_many_holes_004_sings_plot_west}
    \caption{Smallest singular value of the BIE operator
      for the computed roots on the original intervals (\textbullet)
      and an estimate of the error (dotted).}
    \label{subfig:many_inclusions_sings_west}
  \end{subfigure}
  ~
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{ex_many_holes_004_sings_plot_ref}
    \caption{Smallest singular value of the BIE operator
      for the computed roots on the original intervals (\textbullet)
      and the values obtained on the refined interval ($\times$).}
    \label{subfig:many_inclusions_sings_ref}
  \end{subfigure}
  \caption{Further diagnostics for the eigenvalues of a domain
    with several inclusions.}
  \label{fig:many_inclusions_diagnostics_2}
\end{figure}

The singular values suggest that the quality of the
eigenvalues is good, with a few outliers.
%
To explain these outliers, we consider two quantities
which affect the singular value at a computed root.
%
As described above, we can approximate the
error in the computed root at $k_\cheb$ by
$\epscheb \|P\|_\infty/|P'(k_\cheb)|$,
where $P$ is the interpolating polynomial.
%
The singular value estimate itself is affected by
the error incurred in applying the inverse of the
compressed BIE matrix, which can be hard to quantify
\cite{ho2012fast}.
%
We approximate this error by $O(\sqrt{N})\epsflam$
and assume this is the order of the error in
the singular value estimate.
We plot the maximum of these two estimates
along with the computed singular values in
\cref{subfig:many_inclusions_sings_west}.
There is a reasonably good correlation between
the maximum of the error estimates and the
observed smallest singular value for the BIE,
especially for larger errors.

The worst outliers are from the left half
of the interval $[4.5,5]$.
%
Because the determinant is much larger on the
right half than the left half of $[4.5,5]$,
we can improve the estimate for the error
in the roots by subdividing the interval. 
We plot the smallest singular value of the
BIE for the {\color{red} real part of the}
roots obtained by fitting a polynomial
on $[4.5,4.75]$ in \cref{subfig:many_inclusions_sings_ref};
the roots on the refined interval
are of significantly higher quality.

\begin{remark}
  The above experience suggests that
  the ratio $\|P\|_\infty/|P'(k_\cheb)|$
  is a useful diagnostic for performing
  automated eigenvalue estimation.
  Note that at a multiple root, this ratio
  will be more difficult to bound.
\end{remark}
%

%

% flatex input end: [04numerical.tex]

%
% flatex input: [05conclusion.tex]
\section{Conclusion}
\label{sec:conclusion}

In the preceding, we have demonstrated a
BIE framework for computing the eigenvalues
of the Stokes operator in the plane which
is robust and scalable.
%
To justify the
approach, we developed a uniqueness theory
for the oscillatory Stokes equations in
exterior domains in analogy with the
discussion of the Helmholtz equation in
\cite{colton1983integral}.
%
This lead to the primary theoretical
results of the paper which show that the
BIEs resulting from double layer and
combined-field representations of the
velocity field are 
not invertible precisely when $k^2$ is
an eigenvalue on simply connected
and multiply connected domains, respectively.
%
As in \cite{zhao2015robust}, the costliness
of performing the nonlinear minimization
associated with computing these eigenvalues
can be alleviated by computing instead the
approximate zeros of the discrete Fredholm
determinant.

The results of this paper can be
extended in a number of ways.
%
The theory
extends directly to three dimensions, where
computational efficiency and numerical
implementation will be the primary concern.
%
In the numerical examples above, we
consider only domains with differentiable
boundaries for simplicity.
%
When using the eigenfunctions as a trial
basis for simulating the Navier--Stokes
equations~\cite{batcho1994generalized},
it is necessary to handle domains
with corners because the domains of interest
arise from domain decomposition, e.g.
dividing a larger domain into 
quadrilaterals.
Fortunately, there has been recent progress
toward efficient discretization of the
layer potentials of elliptic operators
on domains with corners
\cite{helsing2008corner,serkh2016solution,rachh2017solution,helsing2018integral}
which makes the solution of such problems
tractable.
%
Of course, the theoretical considerations
are different for such domains.
%
Computing the Stokes eigenvalues of regions
with corners is the topic of ongoing
research.

{\color{red}
  As noted in the introduction, buckling eigenvalues
are a subset of the Stokes operator
eigenvalues.}
By adapting the approach of \cite{rachh2017integral},
a suitable layer potential representation of the
buckling problem can be derived based on the
oscillatory Stokes layer potentials.
%
This is the subject of a follow-up paper which is in
preparation.

There are some interesting questions to answer
on the use of Fredholm determinants in numerical
calculations.
%
As observed in \cite{zhao2015robust}, the
combined-field representation causes some
difficulty in that the Fredholm determinant
is not defined when the single layer, which
is not trace-class, is included.
%
Zhao and Barnett~\cite{zhao2015robust}
suggest looking into
representations of the form $\cI-2\cD
-2i\eta\cS^2-2\cW$,
which would have a well-defined Fredholm
determinant.
%
The relative performance of
such an approach should be explored.
%
Further, as discussed above, the
convergence of the determinant of
integral equations discretized with
panel-corrected schemes (as described in
\cref{sec:numerical}) is yet to be proved.
%
When addressing high frequency problems,
the fast-direct solver used to evaluate
determinants in this paper will no longer
have near-linear scaling~\cite{ho2012fast}.
%
The design of fast-direct solvers in this
regime is the subject of ongoing research, and
to the best of our knowledge, fast determinant
computation at high frequency is an open
question.
%
Finally, it is worth exploring alternatives
to the Fredholm determinant which perform well
for layer potentials that are not trace class
on the boundary or for problems at higher
frequencies.

% flatex input end: [05conclusion.tex]

%
% flatex input: [06acknowledgements.tex]
\section{Acknowledgements}
The authors would like to thank Alex Barnett, Leslie Greengard, and Shidong Jiang
for many useful discussions.

T. Askham was supported by the Air Force Office of Scientific Research 
under Grant FA9550-17-1-0329.

% flatex input end: [06acknowledgements.tex]

%

\appendix

% flatex input: [appendix.tex]
\section{Dirichlet eigenvalues and eigenfunctions on the annulus \label{sec:annul_dir_exact}}
In this section, we compute some of the Dirichlet eigenvalues
corresponding to a subset of the radially symmetric eigenfunctions
on the annulus. 
In polar coordinates $(r,\theta)$, consider the annulus defined by 
$R_{1}<r<R_{2}$. 
Suppose that $\bu$ is of the form 
\begin{equation}
\bu = \nabla^{\perp}\left( \alpha H_{0}(kr) + \beta J_{0}(kr) \right) \, ,
\label{eq:annulus_direig}
\end{equation}
and $p=0$.

Clearly, this pair satisfies the osciallatory Stokes equation
with parameter $k$, since $J_{0}(kr)$ and $H_{0}(kr)$ 
satisfy the Helmholtz equation on the annulus.

Let $\hat{r},\hat{\theta}$ denote the unit vectors in polar coordinates.
A simple calculation shows that 
\begin{equation}
\begin{aligned}
u_{r} &= \bu \cdot \hat{r}  = 0 \, \\
u_{\theta} &= \bu \cdot \hat{\theta} = k(\alpha  H_{0}'(kr) + \beta J_{0}'(kr)) \, .
\end{aligned}
\end{equation}

This in particular implies that on $r=R_{1}$,
$u_{\theta}$ takes on the constant value,
$k(\alpha H_{0}'(kR_{1}) + \beta J_{0}'(kR_{1}))$.
Similarly, on $r=R_{2}$, 
$u_{\theta}$ takes on the constant value,
$k(\alpha H_{0}'(kR_{2}) + \beta J_{0}'(kR_{2}))$.

Thus, if $k$ satisfies, 
\begin{equation}
H_{0}'(kR_{1}) J_{0}'(kR_{2}) - H_{0}'(kR_{2})J_{0}'(kR_{1}) = 0 \, ,
\end{equation}
and for those values of $k$ if 
$\alpha,\beta$ are non-zero solutions to system of equations 
\begin{equation}
\begin{bmatrix}
H_{0}'(kR_1) & J_{0}'(kR_{1}) \\
H_{0}'(kR_{2}) & J_{0}'(kR_{2}) 
\end{bmatrix}
\begin{bmatrix}
\alpha \\
\beta
\end{bmatrix}
=
\begin{bmatrix}
0 \\
0
\end{bmatrix}
\, ,
\end{equation}
then $k$ is a Dirichlet eigenvalue and $\bu$ 
defined by~\cref{eq:annulus_direig}
is the corresponding eigenfunction.

\section{Neumann eigenvalues and eigenfunctions on the unit disk}
In this section, we derive an analytical expression which
can be used to compute some of the radially symmetric 
Neumann eigenvalues on the unit disk for the Stokes operator.

Suppose that $\bu$ is of the form
\begin{equation}
\bu = \nabla^{\perp} \jkr \, ,
\end{equation}
and the pressure is given by $p=0$, as
$\bu$ satisfies $(\Delta + k^2)\bu = 0$.

Then, the surface traction $\bt$ on the disk of radius $r$ 
is given by
\begin{equation}
\bt = 
\left( -\frac{k}{r^2}\jpkr  + \frac{k^2}{r} \jppkr\right)
\begin{bmatrix}
\sint \\
-\cost
\end{bmatrix} \, .
\end{equation}

Thus, $k$ which satisfies
\begin{equation}
  \label{eq:neu_roots}
-k \jpk + k^2 \jppk = 0 \, ,
\end{equation}
are Neumann eigenvalues on the unit disk.
The first $4$ roots of the \cref{eq:neu_roots} are
in \cref{tab:neu_roots}.
\begin{table}
  \centering
  \begin{tabular}{c}
    k  \\ \hline
    5.135622301840683 \\
    8.417244140399865 \\
    11.61984117214906 \\
    14.79595178235126 
  \end{tabular}
  \caption{Roots of \cref{eq:neu_roots}.}
  \label{tab:neu_roots}
\end{table}

% flatex input end: [appendix.tex]

%\bibliographystyle{plain}
%\bibliography{refs}

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
\bibliography{refs}   % name your BibTeX data base

% Non-BibTeX users please use
%\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
%\bibitem{RefJ}
% Format for Journal Reference
%Author, Article title, Journal, Volume, page numbers (year)
% Format for books
%\bibitem{RefB}
%Author, Book title, page numbers. Publisher, place (year)
% etc
%\end{thebibliography}

\end{document}
% end of file template.tex

### 2019-12-06 chunkie-ver/test/test_greenostokes.m

@@ -59,7 +59,7 @@ scatter(targets(1,:),targets(2,:),'x')
 axis equal 
 
 
-%%
+%
 
 % kernel defs
 

### 2019-12-06 chunkie-ver/test/test_ostokesmatflam.m

@@ -8,151 +8,155 @@ rng(iseed);
 
 addpaths_loc();
 
-cparams = [];
-cparams.eps = 1.0e-10;
-cparams.nover = 3;
-pref = []; 
-pref.k = 30;
-narms = 3;
-amp = 0.25;
-start = tic; chnkr = chunkfunc(@(t) starfish(t,narms,amp),cparams,pref); 
-t1 = toc(start);
+novers = 0:4;
+densebytes = zeros(length(novers),1);
+flambytes = densebytes;
 
-wts = whts(chnkr);
+for i = 1:length(novers)
+    cparams = [];
+    cparams.eps = 1.0e-10;
+    cparams.nover = novers(i);
+    pref = []; 
+    pref.k = 30;
+    narms = 3;
+    amp = 0.25;
+    start = tic; chnkr = chunkfunc(@(t) starfish(t,narms,amp),cparams,pref); 
+    t1 = toc(start);
 
-fprintf('%5.2e s : time to build geo\n',t1)
+    wts = whts(chnkr);
 
-% set up
+    fprintf('%5.2e s : time to build geo\n',t1)
 
-zk = 0.4;
-opdims(1) = 2; opdims(2) = 2;
+    % set up
 
-% sources
+    zk = 0.4;
+    opdims(1) = 2; opdims(2) = 2;
 
-ns = 10;
-ts = 0.0+2*pi*rand(ns,1);
-sources = starfish(ts,narms,amp);
-sources = 3.0*sources;
-strengths = randn(opdims(2)*ns,1);
+    % sources
 
-% targets
+    ns = 10;
+    ts = 0.0+2*pi*rand(ns,1);
+    sources = starfish(ts,narms,amp);
+    sources = 3.0*sources;
+    strengths = randn(opdims(2)*ns,1);
 
-nt = 1;
-ts = 0.0+2*pi*rand(nt,1);
-targets = starfish(ts,narms,amp);
-targets = targets.*repmat(rand(1,nt),2,1);
+    % targets
 
-% plot geo and sources
+    nt = 1;
+    ts = 0.0+2*pi*rand(nt,1);
+    targets = starfish(ts,narms,amp);
+    targets = targets.*repmat(rand(1,nt),2,1);
 
-figure(1)
-clf
-hold off
-plot(chnkr)
-hold on
-scatter(sources(1,:),sources(2,:),'o')
-scatter(targets(1,:),targets(2,:),'x')
-axis equal 
[…]

### 2019-12-06 doc/review-acom/stokes-eig.tex
smaller updates

@@
 solution in the finite element space but this factor
-grows as a function of the frequency $k$
+{\it grows} as a function of the frequency $k$
 \cite{babuska1997pollution}.
@@
 
+{\color{red}
 \begin{remark}
@@
   corresponding to non-spurious $k$.
-\end{remark}
+\end{remark}}
 
@@
 
-Clearly, this pair satisfies the osciallatory Stokes equation
+Clearly, this pair satisfies the oscillatory Stokes equation
 with parameter $k$, since $J_{0}(kr)$ and $H_{0}(kr)$ 
@@
 This in particular implies that on $r=R_{1}$,
-$u_{\theta}$ takes on the constant value,
+$u_{\theta}$ takes on the constant value
 $k(\alpha H_{0}'(kR_{1}) + \beta J_{0}'(kR_{1}))$.
 Similarly, on $r=R_{2}$, 
-$u_{\theta}$ takes on the constant value,
+$u_{\theta}$ takes on the constant value
 $k(\alpha H_{0}'(kR_{2}) + \beta J_{0}'(kR_{2}))$.
@@
 and for those values of $k$ if 
-$\alpha,\beta$ are non-zero solutions to system of equations 
+$\alpha,\beta$ are non-zero solutions to the system of equations 
 \begin{equation}
@@
 
-Thus, $k$ which satisfies
+Thus, the values $k$ which satisfy
 \begin{equation}
@@
 are Neumann eigenvalues on the unit disk.
-The first $4$ roots of the \cref{eq:neu_roots} are
+The first $4$ roots of \cref{eq:neu_roots} are
 in \cref{tab:neu_roots}.

### 2019-12-06 doc/review-acom/response-to-referees.tex
small update

@@
   We have added some references to applications treated using integral
-  equation methods in the literature. 
-  We note that in the original submission this subsection started with
-  a paragraph that cited previous, first kind integral equation
-  formulations for the buckling problem. There were also references to
-  the Laplace eigenvalue problem and alternative root finding methods
-  earlier in the introduction.
+  equation methods in the literature and reworked the section
+  a little.
 

### 2019-12-07 doc/review-acom/response-to-referees.tex
updating response to 3

@@
 
+The question of addressing this problem under weaker assumptions of smoothness of the boundary
+is a very interesting one. To the best of our knowledge, this question hasn't even been addressed 
+Laplace's equation.
+We have a sketch of a proof for the eigenvalues and eigenfunctions
+for the Laplace operator where we can show that the eigenvalues and eigenfunctions
+converge at an algebraic rate (dependent on the smoothness of curves) for $C^{\ell}$, $\ell\geq 2$ boundaries.
+The procedure of using the Fredholm determinant as stated does not work on Lipchitz boundaries, since
+the corresponding operators are not second kind.
+
+However, we feel that the discussion would be fairly technical and take away from the main results of 
+the paper --- demonstrating the use of Fredholm determinants and second kind formulations for 
+computing the Stokes eigenvalues and eigenfunctions.
+For this reason we feel that this analysis should be carried out in a separate note for the use of Fredholm determinants for the computation of eigenvalues and eigenvectors of Laplace's and Stoke's equation.
+
+We've included a sketch of the proof below.
+
+The sketch of the proof goes as follows. The main estimate needed is to show that the error in
+computing the Fredholm determinant at the eigenvalues of the Stokes operator is directly proportional
+to the quadrature error applied to the null vector of the second kind Fredholm equation. 
+Based on Fredholmness of the operator from $C^{m,\alpha} \to C^{m,\alpha}$ for some $m<\ell$ and $\alpha>0$, 
+when the boundary is $C^{\ell}$, one can show that the resulting null vector must be at least in $C^{m,\alpha}$.
+The quadrature error using Kress quadratures converges algebraically when both the boundary and density being
+approximated are $C^{m,\alpha}$.
+
 \item[4.] {\color{blue} In the paper it is not explicitly mentioned that both presented bound-
@@
   5 two functions are given but in the caption only one function is described.}
+
+Apologies about that. The caption for figure 5 has now been fixed. The two curves
+correspond to the real and the imaginary part of the Fredholm determinant.
 

### 2019-12-07 doc/review-acom/stokes-eig.tex
updating response to 3

@@
 \caption{The values of the discretized determinants $f_{C}^{N}(k)$ (left)
-and $f_{D}^{N}(k)$ on the interval $k=[13,14]$ with $N=368$. The vertical
+and $f_{D}^{N}(k)$ on the interval {\color{red} $k=[14,15]$} with $N=368$ 
+{\color{red}(the 
+solid lines are the real parts of the determinant and the dashed lines
+are the imaginary parts of the determinant)}. The vertical
 dotted line denotes the spurious eigenvalue $k_{0} = 14.79595178235126$ 

### 2019-12-09 doc/review-acom/stokes-eig.tex
small updates

--- 2019-12-06 doc/review-acom/stokes-eig.tex
@@
   $T(k_\cheb)$ is contained in the Bernstein
-  ellipse $E_\rho$ with $\rho = 1+\sqrt{\epscheb}$.
+  ellipse $E_\rho$ with $\rho = 1+10\sqrt{\epscheb}$.
   While it is still possible to obtain two copies
@@
 %
-There were 103 total roots: 21 were removed because
-the imaginary part was too large and 6 pairs were found
-with values within $\sqrt{\epscheb}$ of each other.
-%
-For these 6 pairs, none represented two distinct
-eigenvalues or a double root.
-%
-This leaves 76 roots in the range $0\leq k \leq 9$.
+{\color{red} There were 76 roots in the range $0 \leq k \leq 9$.}
 %

### 2019-12-09 matlab/example/example_barbell_001_big_plots.m

@@ -34,7 +34,7 @@ for i = 1:nints
     fmax = norm(f,'inf');
     rtstemp = roots(f,'complex','norecursion');
     rtstemp_trans = (rtstemp-a)*2/(b-a)-1;
-    rho = 1+sqrt(p.chebfuneps); aell = (rho+1/rho)/2; bell = (rho-1/rho)/2;
+    rho = 1+10*sqrt(p.chebfuneps); aell = (rho+1/rho)/2; bell = (rho-1/rho)/2;
     indkeep = and(real(rtstemp_trans).^2/aell^2 + imag(rtstemp_trans).^2/bell^2 <= 1, ...
         and(real(rtstemp) >= chebabs{i}(1),real(rtstemp) <= chebabs{i}(2)));
     rtstemp(~indkeep);

### 2019-12-09 matlab/example/example_many_holes_004_and_005_big_plots_post.m

@@ -35,15 +35,6 @@ end
 
 %
 
-% indimagbig = abs(imag(rts)) > sqrt(p.chebfuneps);
-% nnz(indimagbig)
-% find(indimagbig)
-% sings(indimagbig)
-
-%
-
-[iplot,ichkdbl] = find_unique_evals(rts,sings,1e-5, ...
-    sqrt(p.chebfuneps));
 
 %% 
 
@@ -58,10 +49,10 @@ nsamp=10;
 for ii = 1:mrow*ncol
     axes(ha(ii))
     
-    if ii > length(iplot)
+    if ii > length(rts)
         axis off
     else
-        i = iplot(ii);
+        i = ii;
 
         vort = nan(size(vorts{i}));
 
@@ -93,40 +84,15 @@ end
 
 %%
 
-% Run through and check for double roots at suspicious sings
-
-sings2 = zeros(length(ss),1);
-for i = 1:length(ss)
-    sings2(i) = ss{i}(2);
-end
-
-[sings(ichkdbl(:,1)), sings2(ichkdbl(:,1))]
-
 %%
-
-% compare computed vorticity at suspicious sings
-
-projs = zeros(length(ichkdbl),1);
-projsx = zeros(length(ichkdbl),1);
-
-for ii =  1:length(ichkdbl)
-    i1 = ichkdbl(ii,1); i2 = ichkdbl(ii,2);
-    v1 = vorts{i1}(in); v2 = vorts{i2}(in);
-    x1 = xnulls{i1}(:,1); x2 =xnulls{i2}(:,1);
-    v1 = v1/norm(v1,'fro');
-    projs(ii) = norm(v2-v1*v1'*v2,'fro')/norm(v2,'fro');
-    x1 = x1/norm(x1,'fro');
-    x2 = x2/norm(x2,'fro');
-    projsx(ii) = norm(x2-x1*x1'*x2);
-end
 
 
 %%
 
 fileout = 'ex_many_holes_004_sings.tex';
 fid = fopen(fileout,'w'); 
-fprintf(fid,'%7.4e %7.4e\n',[1.0*(1:length(iplot)); ...
-    reshape(abs(sings(iplot)),1,length(iplot))]);
+fprintf(fid,'%7.4e %7.4e\n',[1.0*(1:length(sings)); ...
+    reshape(abs(sings),1,length(sings))]);
 fclose(fid);
 
 %%
@@ -182,12 +148,10 @@ end
 
 %%
 
[…]

### 2019-12-09 matlab/example/example_many_holes_004_big_plots.m

@@ -18,9 +18,46 @@ load(filein);
 nints = length(detchebs);
 
 rtsc = cell(nints,1);
+frtsc = cell(nints,1);
+dfrtsc = cell(nints,1);
+dfrtsc2 = cell(nints,1);
 
+nremove_imag = 0;
+nremove_real = 0;
+nremove = 0;
 for i = 1:nints
-    rtsc{i} = roots(detchebs{i},'complex');
+    a = chebabs{i}(1);
+    b = chebabs{i}(2);
+    f = detchebs{i};
+    df = diff(f);
+    fmax = norm(f,'inf');
+    rtstemp = roots(f,'complex','norecursion');
+    rtstemp_trans = (rtstemp-a)*2/(b-a)-1;
+    rho = 1+10*sqrt(p.chebfuneps); aell = (rho+1/rho)/2; bell = (rho-1/rho)/2;
+    indkeep = and(real(rtstemp_trans).^2/aell^2 + imag(rtstemp_trans).^2/bell^2 <= 1, ...
+        and(real(rtstemp) >= chebabs{i}(1),real(rtstemp) <= chebabs{i}(2)));
+    rtstemp(~indkeep);
+    
+%     indkeep = and(imag(rtstemp_trans) > -sqrt(p.chebfuneps), ...
+%         and(real(rtstemp) >= chebabs{i}(1),real(rtstemp) <= chebabs{i}(2)));
+%     rtstemp(~indkeep);
+%     
+%     ind_badimag = and(imag(rtstemp_trans) <= -sqrt(p.chebfuneps),...
+%         and(real(rtstemp) >= a,real(rtstemp) <= b));
+%     rtstemp(ind_badimag)
+%     nremove_imag = nnz(and(imag(rtstemp_trans) <= -sqrt(p.chebfuneps),...
+%         and(real(rtstemp) >= a,real(rtstemp) <= b)))+nremove_imag;
+%     nremove_real = nnz(or(real(rtstemp) < chebabs{i}(1),real(rtstemp) ...
+%         > chebabs{i}(2))) + nremove_real;
+%     
+    nremove = nnz(~indkeep)+nremove;
+    rtstemp = rtstemp(indkeep);
+    [~,inds] = sort(real(rtstemp));
+    rtsc{i} = rtstemp(inds);
+    
[…]

### 2019-12-09 matlab/src/checkchunker.m

@@ -15,4 +15,4 @@ assert(numel(chunker.ders)==2*nch*k);
 assert(numel(chunker.ders2)==2*nch*k);
 assert(numel(chunker.adjs)==2*nch);
 assert(numel(chunker.hs)==nch);
-assert(checkadjinfo(chunker)==0);
+%assert(checkadjinfo(chunker)==0);

### 2019-12-09 doc/review-acom/stokes-eig.tex
update quadrature rule order discussion

@@
 of larger eigenvalues. In the original context,
-the term pollution refers to the fact that,
-when solving the Helmholtz equation in dimension
+pollution refers to the following phenomenon.
+When solving the Helmholtz equation in dimension
 greater than one,
 the accuracy of the Galerkin solution of
-a problem does indeed differ by a constant factor from
+a problem is indeed optimal in the sense that it
+differs by a constant factor from
 the error in the best approximation of the true
-solution in the finite element space but this factor
+solution in the finite element space.
+But this factor
 {\it grows} as a function of the frequency $k$
@@
 resolve the solution.
-In constrast, a BIE does not suffer from this
-effect.}
+In constrast, a standard BIE discretization does not
+suffer from this effect.}
 
@@
 double layer potentials have weak
-singularities of the form $|\xx-\yy|^p\log |\xx-\yy|$
+singularities of the form $|\xx-\yy|^{2p}\log |\xx-\yy|$
 for some $p \in \N_0$, which require special
@@
 %
-For the 20th-order rule we used, $N_s = 16$ and
+For the {\color{red} 16th-order} rule we used
+{\color{red} (i.e. a rule which integrates
+  $p(\yy)\log|\xx-\yy| + q(\yy)$ for $p$ and $q$
+  polynomials of degree up to 15)}, $N_s = 16$ and
   $N_a = 48$. 
@@
   The overall order of accuracy of the GGQ we use
-  is 20th-order, up to the precision of the ``far''
+  is {\color{red}16th-order}, up to the precision of the ``far''
   interactions.
@@
 and $|k_{C} - k_{0}| \lesssim N^{-20}$.
-Recall that the GGQ we use has an expected order
-of convergence of $N^{-20}$ for evaluating convolutions
-with such integral kernels,
-so that the error of the roots is observed to have the
-same order as the quadrature rule.
+Recall that the GGQ we use {\color{red} is designed to
+evaluate integrals of the form $p(\yy)\log|\xx-\yy|
++ q(\yy)$ with $p$ and $q$ polynomials of degree up
+to 15, so that the observed convergence rate
+for the roots is of slightly higher order than the
+order of the quadrature rule. In our experience, the $N^{-20}$
+rate is common for these kernels and may be a result of the
+fact that the singularity for these kernels is of the form
+$|\xx-\yy|^2\log|\xx-\yy|$, which is smoother than
+$\log|\xx-\yy|$ itself.}
 In~\cref{fig:conv}, we show this result for $k_{0} = 13.48025717955055$

### 2019-12-09 doc/review-acom/response-to-referees.tex
update quadrature rule language

@@
 are marked in {\color{red} red} in the revised manuscript.
+
+We have also marked in {\color{red} red} a couple of
+changes around the explanation of the order of convergence
+of the generalized Gaussian quadrature rule we used.
+The rule is designed to be 16th order, i.e. it is designed
+to integrate $p(y)\log|x-y| + q(y)$ for $p$ and
+$q$ polynomials of degree up to 15. Our kernel is actually
+smoother than $\log|x-y|$ (with leading order
+singularity $|x-y|^2\log|x-y|$) and in our experience the
+convergence rate is typically higher (20th order in
+the example in the paper). In the revised text, we have clarified
+that the rule is not designed to be 20th order but that this is
+the behavior we observed.
 

### 2019-12-09 doc/review-acom/stokes-eig.tex
update quadrature rule language

@@
 {\color{red} (i.e. a rule which integrates
-  $p(\yy)\log|\xx-\yy| + q(\yy)$ for $p$ and $q$
-  polynomials of degree up to 15)}, $N_s = 16$ and
+  $\Phi(s)\log|t-s| + \Psi(s)$ over $[-1,1]$ exactly
+  for $\Phi$ and $\Psi$ polynomials of degree up
+  to 15)}, $N_s = 16$ and
   $N_a = 48$. 
@@
 %
-We also evaluate the second smallest singular
-value to check for possible double eigenvalues.
 
@@
 and $|k_{C} - k_{0}| \lesssim N^{-20}$.
-Recall that the GGQ we use {\color{red} is designed to
-evaluate integrals of the form $p(\yy)\log|\xx-\yy|
-+ q(\yy)$ with $p$ and $q$ polynomials of degree up
-to 15, so that the observed convergence rate
-for the roots is of slightly higher order than the
-order of the quadrature rule. In our experience, the $N^{-20}$
-rate is common for these kernels and may be a result of the
-fact that the singularity for these kernels is of the form
-$|\xx-\yy|^2\log|\xx-\yy|$, which is smoother than
-$\log|\xx-\yy|$ itself.}
+Recall that the GGQ we use {\color{red} is 16th order
+  for $\log$ singularities, so that the observed convergence
+  rate for the roots is of higher order than the
+  order of the quadrature rule. This behavior is a bit
+  surprising but may owe to the fact that the integral
+  kernels are actually smoother than $\log|\xx-\yy|$
+  (with leading order singularity $|\xx-\yy|^2\log|\xx-\yy|$).
+  Alternatively, the asymptotic convergence rate may simply
+  not be apparent before the maximum precision is reached.}
 In~\cref{fig:conv}, we show this result for $k_{0} = 13.48025717955055$

### 2019-12-09 doc/review-acom/response-to-referees.tex
update response wording

--- 2019-12-06 doc/review-acom/response-to-referees.tex
@@
 
-\item[4.] {\color{blue} In the paper it is not explicitly mentioned that both presented bound-
-ary integral equations may have non-trivial null-spaces for certain $k$
-with ${\rm Im}(k) < 0$. These $k$s correspond to the eigenvalues of some re-
-lated eigenvalue problems in the exterior domain. It is possible that
+The question of addressing this problem under weaker assumptions of smoothness of the boundary
+is a very interesting one. To the best of our knowledge, this
+question hasn't even been addressed for the eigenvalues of the Laplacian.
+We have a sketch of a proof of convergence for the eigenvalues and eigenfunctions
+for the Laplace operator where we can show that the eigenvalues and eigenfunctions
+converge at an algebraic rate (dependent on the smoothness of curves) for $C^{\ell}$,
+with $\ell\geq 2$, boundaries. The procedure of using the Fredholm determinant as
+stated does not work on Lipchitz boundaries, since the corresponding operators are
+not second kind.
+
+However, we feel that the discussion would be fairly technical and distract
+from the main results of the paper --- demonstrating the use of Fredholm determinants
+and second kind formulations for computing the Stokes operator eigenvalues and
+eigenfunctions.  For this reason we feel that this analysis should be carried out in
+a separate work and done for both the Laplace and Stokes cases.
+
+We've included a sketch of the proof below.
+
+The main estimate needed is to show that the error in computing
+the Fredholm determinant at an eigenvalue of the Stokes operator
+is directly proportional to the quadrature error for evaluating
+the convolution of the integral kernel with the true null vector
+of the integral operator with $k$ corresponding to that eigenvalue.
+Based on the second-kind nature of the operator from $C^{m,\alpha} \to C^{m,\alpha}$
+for $m<\ell$ and $\alpha>0$ (when the boundary is $C^{\ell}$) one can show
+that the resulting null vector must be at least in $C^{m,\alpha}$.
+The quadrature error using Kress quadratures converges algebraically
+when both the boundary and density being approximated are $C^{m,\alpha}$.
+
+\item[4.] {\color{blue} In the paper it is not explicitly mentioned that
+  both presented boundary integral equations may have non-trivial null-spaces
+  for certain $k$ with ${\rm Im}(k) < 0$. These $k$s correspond to the eigenvalues of some
+  related eigenvalue problems in the exterior domain. It is possible that
   these $k$s are also be detected by the root search method and that these
   eigenvalues may be some of those “spurious eigenvalues too far from
-real-valued” which are blamed to be caused by “noisy numerical de-
-terminant evaluation” but are actually caused by the used boundary
-integral formulation.}
+  real-valued” which are blamed to be caused by “noisy numerical determinant
+  evaluation” but are actually caused by the used boundary integral formulation.}
 

### 2019-12-09 doc/review-acom/response-to-referees.tex
adding sketch of proof

@@
 the Fredholm determinant at an eigenvalue of the Stokes operator
-is directly proportional to the quadrature error for evaluating
-the convolution of the integral kernel with the true null vector
-of the integral operator with $k$ corresponding to that eigenvalue.
+is directly proportional to the quadrature error in 
+evaluating the integral operator applied to the null vector (A proof of this result for the 
+Laplace case is contained in~\cref{sec:appb}). 
 Based on the second-kind nature of the operator from $C^{m,\alpha} \to C^{m,\alpha}$
@@
 
+\input{../draft-01-stokes/appendix-b}
 \end{itemize}

### 2019-12-09 doc/draft-01-stokes/appendix-b.tex
adding sketch of proof

@@
 Let $T_{n}$ denote the space of trignometric polynomials
-$\{ e^{-inx}, \ldots e^{inx} \}$. Let $K_{n}: T_{n} \to T_{n}$ 
-denote a discretization of the Helmholtz double layer kernel
-using kress quadrature. Let $\phi_{0}$ denote the null vector
-of $I+ K$, and let $\psi_{0}$ denote the null vector
-of $I+K^{\ast}$. 
+$\{ e^{-inx}, \ldots e^{inx} \}$. 
+Let $\mathcal{K}$ denote the Helmholtz double layer integral operator
+given by
+\begin{equation}
+\mathcal{K}[\phi] = \frac{i}{2}\int_{\Gamma} k H_{1}^{1}(k|x-y|) \frac{(x-y)\cdot n(y)}{|x-y|} \phi(y) dS_{y} \,
+\end{equation}
+where $k$ the Helmholtz parameter is assumed to be a dirichlet eigenvalue of the simply connected
+domain $\Omega$ whose boundary is given by $\Gamma$, and $H_{1}^{1}$ is the Hankel function
+of the first kind of order $1$.
+It is well known that if $\Gamma$ is of class $C^{\ell,\alpha}$, then the
+integral operator $\mathcal{K}: C^{\ell-1,\alpha} \to C^{\ell-1,\alpha}$ is a compact operator.
+Furthermore, as shown in Zhao and Barnett, at the simple Dirichlet eigenvalues of the operator
+$I + \mathcal{K}$ is not invertible and has a one dimensional null-space. Let $\phi_{0}$ denote
+the null vector. 
+By Fredholm theory, the adjoint $I + \mathcal{K}^{\ast}$ also has a one-dimensional null space.
+Let $\psi_{0}$ denote the null vector of $I+\mathcal{K}^{\ast}$.
+
+Let $K_{n}: T_{n} \to T_{n}$ 
+denote a discretization of $\mathcal{K}$ 
+using kress quadrature. 
 Let $P_{n}$ denote the orthogonal 
@@
 to $P_{n} \psi_{0}^{\perp}$.
-As $n \to \infty$, $D_{n}$ converges pointwise to the restriction
+The following statement requires a more careful proof.
+{\color{red} As $n \to \infty$, $D_{n}$ converges pointwise to the restriction
 of $I + K: \phi_{0}^{\perp} \to R(I+K)$. Moreover, the collection
@@
 operator, by standard estimates, for $n$ large enough $D_{n}$ is also 
-an invertible operator.
+an invertible operator.}
 
@@
 \end{equation}
+
+First, we observe that $D_{n}$ is the restriction of an operator in trace class
+with a kernel whose leading order singularity is $r^{2} \log{r}$. 
+Thus, $D_{n}$ is itself in trace class, and extending the proof of Bornemann to this case,
+we observe that the discrete determinant of $D_{n}$ converges to the Fredholm determinant
+of $D$ at a rate of at least $O(1/n)$. This in particular implies that
+$\sup_{n} |\det{D_{n}}| <\infty$.
+Using Cauchy-Schwarz, the quantities $A_{n}, C_{n}D_{n}^{-1}B_{n}$ are bounded by
+$|(I_{n} + K_{n})\phi_{n}|$.
+Combining these results together, we get that
+\begin{equation}
+\left| \det{\begin{bmatrix} A_{n} & B_{n} \\ C_{n} & D_{n} \end{bmatrix}} \right| \leq C |(I_{n} + K_{n})\phi_{n}|
+\end{equation}

### 2019-12-10 doc/review-acom/response-to-referees.tex

@@
 
-To explain what had happened, we computed the roots using a rootfinding
+To explain what happened originally, we computed the
+roots using a rootfinding
 utility in another software package, \texttt{chebfun}. In our
@@
 eigenvalues (the imaginary part of the real-valued roots is several
-orders of magnitued smaller than the imaginary part of the
+orders of magnitude smaller than the imaginary part of the
 spurious roots we observed).
@@
 was not observed, i.e. one can imagine a pathological domain for which a
-true spurious root exists that is within, say, $10^{-7}$ of the real line.
+spurious root exists that is within, say, $10^{-7}$ of the real line.
 Such a root would be hard to distinguish from a true root.
@@
 
+  \appendix
 \input{../draft-01-stokes/appendix-b}

### 2019-12-10 doc/draft-01-stokes/appendix-b.tex
minor changes
adding small chnges
finishing appendix b

@@
-\section{Proof of convergence for general case}
-Let $T_{n}$ denote the space of trignometric polynomials
-$\{ e^{-inx}, \ldots e^{inx} \}$. 
+\section{Sketch of proof}
+\label{sec:appb}
+Let $T_{n}$ denote the space of trigonometric polynomials
+$\{ e^{-int}, \ldots e^{int} \}$. 
 Let $\mathcal{K}$ denote the Helmholtz double layer integral operator
@@
 \begin{equation}
-\mathcal{K}[\phi] = \frac{i}{2}\int_{\Gamma} k H_{1}^{1}(k|x-y|) \frac{(x-y)\cdot n(y)}{|x-y|} \phi(y) dS_{y} \,
+\mathcal{K}[\phi] = \frac{i}{2}\int_{\Gamma} k H_{1}^{1}(k|x(t)-y(t)|) \frac{(x(t)-y(t))\cdot n(y(t))}{|x(t)-y(t)|} \phi(y(t)) dS_{y} \,
 \end{equation}
 where $k$ the Helmholtz parameter is assumed to be a dirichlet eigenvalue of the simply connected
-domain $\Omega$ whose boundary is given by $\Gamma$, and $H_{1}^{1}$ is the Hankel function
+domain $\Omega$ whose boundary is given by $\Gamma$, $(x(t),y(t)): [0,2\pi] \to \Gamma$ is
+an arclength parameterization of the boundary, and $H_{1}^{1}$ is the Hankel function
 of the first kind of order $1$.
@@
 Let $\psi_{0}$ denote the null vector of $I+\mathcal{K}^{\ast}$.
+
+In order to prove the regularity of the eigenfunctions, we need to analyze
+the kernels in $C^{\ell-1,\alpha}$ space. 
+However in order to obtain a bound for the magnitude of the Fredholm
+determinant, it is more convenient to work in $L^{2}$. It is well known
+that the integral operator $I + \mathcal{K}$ is a second kind
+Fredholm operator from $L^{2} \to L^{2}$ as well.
+For the remainder of the section, we will work with $L^{2}$.
 
@@
 And finally the operator $C_{n}$ is the restriction of $I_{n} + K_{n}$ as a map from
-$P_{n} \phi_{0} \to P_{n} \psi_{0}^{\perp}$ and is its adjoint is given by
+$P_{n} \phi_{0} \to P_{n} \psi_{0}^{\perp}$ and is given by
 \begin{equation}
-C_{n}^{\ast}\psi = \left( (I_{n} + K_{n}^{\ast}) \left(P_{n} \psi - (P_{n} \psi, P_{n} \psi_{0}) P_{n} \psi_{0} \right), P_{n} \phi_{0} \right)
+C_{n}P_{n} \phi_{0} = (I_{n} + K_{n}) P_{n} \phi_{0} - \left( (I_{n} + K_{n}) \phi_{0}, P_{n} \psi_{0} \right)P_{n} \psi_{0}
 \end{equation}
 
-In this setting, $\phi_{0}$ and $\psi_{0}$ are known to be linearly independent.
-Thus for large enough $n$, 
-$f_{n} = P_{n} \phi_{0} - (P_{n} \phi_{0}, P_{n} \psi_{0}) P_{n} \psi_{0} \neq 0$
-and $f_{n} \in P_{n} \psi_{0}^{\perp}$.
-Similarly $g_{n} = P_{n} \psi_{0} - (P_{n}\phi_{0}, P_{n} \psi_{0}) P_{n} \phi_{0} \neq 0$
-and $g_{n} \in P_{n} \phi_{0}^{\perp}$.
+%Thus for large enough $n$, 
+%$f_{n} = P_{n} \phi_{0} - (P_{n} \phi_{0}, P_{n} \psi_{0}) P_{n} \psi_{0} \neq 0$
+%and $f_{n} \in P_{n} \psi_{0}^{\perp}$.
+%Similarly $g_{n} = P_{n} \psi_{0} - (P_{n}\phi_{0}, P_{n} \psi_{0}) P_{n} \phi_{0} \neq 0$
+%and $g_{n} \in P_{n} \phi_{0}^{\perp}$.
 
@@
 }
-= \det{D_{n}} \cdot (A_{n} - C_{n} D_{n}^{-1} B_{n}) \,.
-\end{equation}
-Note that $C_{n} D_{n}^{-1} B_{n}$ is a number and can be evaluated as 
-\begin{equation}
-\begin{aligned}
-C_{n} D_{n}^{-1} B_{n} &= 
-\left( f_{n} \cdot  C_{n} D_{n}^{-1} B_{n} g_{n} \right) \\
-&= \left( C_{n}^{\ast} f_{n}, D_{n}^{-1} B_{n} g_{n} \right) \\
-&= \left( \left((I_{n} + K_{n}^{\ast})f_{n}, P_{n} \phi_{0}\right) P_{n} \phi_{0}, D_{n}^{-1} B_{n} g_{n} \right) \\
-&= \left(f_{n}, (I_{n} + K_{n})P_{n} \phi_{0} \right) \cdot (P_{n} \phi_{0}, D_{n}^{-1} B_{n} g_{n}) \\
-&= \left(f_{n}, (I_{n} + K_{n})P_{n} \phi_{0} \right) \cdot (P_{n} \phi_{0}, D_{n}^{-1} P_{n} \psi_{0})  \cdot 
-\left((I_{n} + K_{n}^{\ast})P_{n} \psi_{0}, g_{n}  \right) \\
-\end{aligned}
+= \det{D_{n}} \cdot (A_{n} - B_{n} D_{n}^{-1} C_{n}) \,.
 \end{equation}
@@
 with a kernel whose leading order singularity is $r^{2} \log{r}$. 
-Thus, $D_{n}$ is itself in trace class, and extending the proof of Bornemann to this case,
+{\color{red} Thus, $D_{n}$ is itself in trace class, and extending the proof of Bornemann to this case,
 we observe that the discrete determinant of $D_{n}$ converges to the Fredholm determinant
 of $D$ at a rate of at least $O(1/n)$. This in particular implies that
-$\sup_{n} |\det{D_{n}}| <\infty$.
-Using Cauchy-Schwarz, the quantities $A_{n}, C_{n}D_{n}^{-1}B_{n}$ are bounded by
-$|(I_{n} + K_{n})\phi_{n}|$.
+$\sup_{n} |\det{D_{n}}| <\infty$}.
+Using Cauchy-Schwarz, we get that
+\begin{equation}
+\begin{aligned}
+|A_{n}| &\leq |P_{n} \psi_{0}|_{2} |(I_{n} + K_{n})P_{n} \phi_{0}|_{2} \\
+|B_{n}D_{n}^{-1} C_{n}| &\leq |B_{n}||D_{n}^{-1}|(1+ |P_{n} \psi_{0}|^2) |(I_{n} + K_{n})P_{n} \phi_{0}| \,.
+\end{aligned}
+\end{equation}
+$B_{n}$ is a discretized block of a bounded operator and hence is bounded, 
+and $D_{n}^{-1}$ is a bounded operator by the discussion above.
+
 Combining these results together, we get that
 \begin{equation}
-\left| \det{\begin{bmatrix} A_{n} & B_{n} \\ C_{n} & D_{n} \end{bmatrix}} \right| \leq C |(I_{n} + K_{n})\phi_{n}|
+\left| \det{\begin{bmatrix} A_{n} & B_{n} \\ C_{n} & D_{n} \end{bmatrix}} \right| \leq C |(I_{n} + K_{n})\phi_{n}| \, ,
 \end{equation}
+where $C = \det{D_{n}} |B_{n}||D_{n}^{-1}| (1 + |P_{n} \psi_{0}|^2)$.

### 2019-12-11 doc/review-acom/response-to-referees.tex

@@
 is directly proportional to the quadrature error in 
-evaluating the integral operator applied to the null vector (A proof of this result for the 
-Laplace case is contained in~\cref{sec:appb}). 
+evaluating the integral operator applied to the null vector (A proof sketch 
+of this result for the Laplace case is contained in~\cref{sec:appb}. 
+The red text in the appendix denotes results that need to be shown.). 
 Based on the second-kind nature of the operator from $C^{m,\alpha} \to C^{m,\alpha}$
@@
 
-  Thank you for pointing out this ommission. It's been fixed
+  Thank you for pointing out this omission. It's been fixed
   in the revision.

### 2019-12-11 doc/draft-01-stokes/appendix-b.tex

@@
 integral operator $\mathcal{K}: C^{\ell-1,\alpha} \to C^{\ell-1,\alpha}$ is a compact operator.
-Furthermore, as shown in Zhao and Barnett, at the simple Dirichlet eigenvalues of the operator
-$I + \mathcal{K}$ is not invertible and has a one dimensional null-space. Let $\phi_{0}$ denote
+Furthermore, as shown in Zhao and Barnett, at the Dirichlet eigenvalues, the operator
+$I + \mathcal{K}$ is not invertible and has a $p-$dimensional null-space, where
+$p$ is the multiplicity of the eigenvalue. 
+By Fredholm theory, the adjoint $I + \mathcal{K}^{\ast}$ also has a $p$-dimensional null space.
+For convenience, we restrict our attention to the case $p=1$. This
+part of the analysis extends to non-simple eigenvalues as well. 
+Let $\phi_{0}$ denote
 the null vector. 
-By Fredholm theory, the adjoint $I + \mathcal{K}^{\ast}$ also has a one-dimensional null space.
 Let $\psi_{0}$ denote the null vector of $I+\mathcal{K}^{\ast}$.
@@
 In order to prove the regularity of the eigenfunctions, we need to analyze
-the kernels in $C^{\ell-1,\alpha}$ space. 
+the problem in $C^{\ell-1,\alpha}$ space. 
 However in order to obtain a bound for the magnitude of the Fredholm
@@
 \begin{equation}
-C_{n}P_{n} \phi_{0} = (I_{n} + K_{n}) P_{n} \phi_{0} - \left( (I_{n} + K_{n}) \phi_{0}, P_{n} \psi_{0} \right)P_{n} \psi_{0}
+C_{n}P_{n} \phi_{0} = (I_{n} + K_{n}) P_{n} \phi_{0} - \left( (I_{n} + K_{n}) P_{n}\phi_{0}, P_{n} \psi_{0} \right)P_{n} \psi_{0}
 \end{equation}
@@
 $\sup_{n} |\det{D_{n}}| <\infty$}.
+
 Using Cauchy-Schwarz, we get that
@@
 \begin{aligned}
-|A_{n}| &\leq |P_{n} \psi_{0}|_{2} |(I_{n} + K_{n})P_{n} \phi_{0}|_{2} \\
+|A_{n}| &\leq |P_{n} \psi_{0}| |(I_{n} + K_{n})P_{n} \phi_{0}| \\
 |B_{n}D_{n}^{-1} C_{n}| &\leq |B_{n}||D_{n}^{-1}|(1+ |P_{n} \psi_{0}|^2) |(I_{n} + K_{n})P_{n} \phi_{0}| \,.
